\documentclass[11pt]{book}

\usepackage{geometry}
\geometry{paperwidth=8.7cm, paperheight=19cm,left=0.5cm, right=0.5cm, vmargin=1.5cm}

\usepackage{ctex}

\usepackage{paracol}
\columnratio{0.5}
\setlength{\columnsep}{1em}

\usepackage{fontspec}                  %引入字体设置宏包
%\setmainfont{Times New Roman}
%\setmainfont{Book Antiqua}

\usepackage[center]{titlesec}
\titleformat{\section}{\centering\large\textbf}{}{0pt}{}
\titleformat{\subsection}{\centering\huge\textbf}{}{0pt}{}

\usepackage{fancyhdr}
\chead{}


\begin{document}

\section{Taylor's engaged - what we learned and the new details revealed by Travis's dad}

\par

"Your English teacher and your gym teacher are getting married."


With that one-line, five-picture Instagram post, signed off with a fire cracker emoji, Taylor Swift announced her engagement to American football player Travis Kelce, sending the internet into a frenzy.


Tuesday's post by the couple - who have been together for two years - has been liked more than 28 million times on the social media platform.


NFL star Kelce is pictured getting down on one knee to pop the question to the world-famous music superstar, with the pair gazing into each other's eyes and embracing.


In the third picture in the carousel, Swift, wearing a Ralph Lauren halter neck dress and diamond encrusted Cartier watch, flashes her engagement ring - a cushion cut diamond on a gold band.


@TaylorSwift/Instagram Taylor Swift embraces Travis Kelce at her proposal @TaylorSwift/Instagram
According to US reports, the ring was purchased from Artifex Fine Jewelery. Prices for rings on its website start at around \$29,000 (£21,506.26).


Photos show the couple surrounded by roses, anemones, delphiniums and hydrangeas which appear to be set up in woodland with strategically placed urns and an archway, wedding florist Nicola Paul told the BBC.


"It's simple elegance, not too ostentatious," she said. "It's been staged in the woods, so you get that lush greenery look."


Celebrity florist Jeff Leatham, who has worked with the Kardashians, described the design as "beautiful, hidden secret garden with a romantic mix of florals".


The engagement post was not without some elements of an Easter egg hunt - a thing Swift loves doing for her fans around the world.


The caption had the explosion emoji which could also be read as TNT - or T and T: Taylor's and Travis' initials when abbreviated.


Neither Swift nor Kelce have been publicly engaged to anyone before.


\subsection{'Feel so high school'}
Accompanying the Instagram post is Swift's ballad So High School from the Tortured Poets Department album - rumoured to have been written about Kelce.


"I feel so high school every time I look at you," she sings.


The clip of the song finishes on the line "Are you gonna marry, kiss, or kill me?" which apparently is a reference to a 2016 interview in which Kelce chose to kiss Taylor in a game of Kiss, Marry, Kill.


"That was so magical and special to see," said Dr Iona Murphy, an adviser on last year's Victoria and Albert Museum's exhibition on Swift and a superfan who has written about Swift.


"A song that was written about Travis was now being used on the post. It's a nice full circle moment," said Dr Murphy, an English literature lecturer at Huddersfield University.


She said the caption to the Instagram announcement - "your English teacher and your gym teacher are getting married" – is also notable, as it refers to how the fans like to describe the couple.


"That's like a little joke in the fandom. You see it on social media. So it's like that was a little nod to the fans," she said.


In an interview with ABC's News 5 Cleveland station, Kelce's father, Ed, revealed that "Travis actually did the proposal... maybe two weeks, not quite two weeks ago".


He said this happened at a garden in the city of Lee's Summit, Missouri.


"He got her out there, they were about to go out to dinner, and he said, 'let's go out and have a glass of wine'... they got out there, and that's when he asked her, and it was beautiful," Ed Kelce said.


"They started FaceTiming me and their mother and her folks to make sure everybody knew. So, to see them together is great."

\subsection{Fans scream in shock}


The pop emergency has resonated with fans in an extraordinary way.


Videos on social media show groups of friends screaming as they heard the news, while others describe feeling emotional and even teary.


"I thought it was AI when I first opened up Instagram," Chloe, who runs a Swiftie news fan account with 74,000 followers on TikTok, told the BBC.


"I couldn't believe it was real, then I realised it was their accounts that posted it," she said. "I immediately freaked out and text my group chat incoherently. Just excitement and disbelief, really."


As the news broke, many Swift fans were joking on social media that they were happy for their "close friend" Swift.


Swift recognised early on in her career the benefit of connecting with fans, and has carefully crafted a sense of relatability.


And at the same time, many of Swift's original fans - who were teenagers at the same time as Swift was breaking through as an artist - have grown up with her, and are now at the same age when they may also be getting engaged or married.


Explaining why she felt so strongly about the engagement, Chloe said: "I feel in a way we all know her.


"Her music is so personal, and the way she connects to her fans is through the way she talks and sings about her relationships. I just want the best for her and just happy she's found love."


EPA Taylor Swift and Travis Kelce at the Super Bowel LVIIIIEPA
The Prince and Princess of Wales, William and Catherine, were among the millions of fans who liked the engagement post on Instagram.


US President Donald Trump also joined in the fun. "I wish them a lot of luck. I think he's a great player, and he's a great guy, and I think she's a terrific person," he said.


Only last year, Trump wrote on social media "I hate Taylor Swift!", after the singer endorsed his presidential rival Kamala Harris.


Meanwhile, celebrity chef Gordon Ramsay published a photo of himself congratulating Kelce after the Kansas City Chiefs won the NFL championship in 2023.


The caption on his Instagram post reads: "From one ring to the next…congrats @killatrav & @taylorswift ! From your favourite Home Ec Teacher Gx".

\subsection{Fascination with Swift's love life}
The social media frenzy about Swift's engagement news marks yet another high point in the fans' huge interest and fascination in her love life - including her past relationships and heartbreaks.


Indeed, Swift has previously spoken about the media's "fixation on painting me as the psycho serial dater girl".


But it is also something the songwriter has deliberately played into by famously writing about her exes in her song and giving clues to fans about her relationships.


According to Laura Snapes, the Guardian's deputy music editor and a Swift fan, it was "almost like an artform" how she has played into the media speculation around her love life.


"She definitely knows the benefits of a relationship to keep her in the headlines. 1989 is about her relationship with Harry Styles but as far as we can tell that lasted a matter of months", Snapes said on the Today In Focus podcast in 2023.


And interestingly, the engagement announcement came just weeks after Swift's interview with Kelce on his New Heights podcast - which Dr Murphy believed was noteworthy as it was the first time fans saw them interact together in a long interview and how compatible they seemed.


"It was almost like a two-hour interview - we haven't had that much interview content. So it was lovely to watch. We could see the chemistry and how comfortable she felt with him," she said.


It's not just Swift saying yes - the feeling is the same for her fandom, according to Chloe.


"We Swifties have seen a lot of boyfriends over the years, some we've liked and some we definitely have not liked.


"Travis is someone who loves her proudly and doesn't seem intimidated by her success which other suitors might have been," she said.


\end{document}
