\section{Lesson 39 Nothing to worry about}

\begin{paracol}{2}

The rough road across the plain soon became so bad that we tried to get Bruce to drive back to the village we had come from.

\switchcolumn

\chinesetext{穿越平原的道路高低不平，开车走了不远，路面愈加崎岖。我们想劝说布鲁斯把车开回我们出发的那个村庄去。}

\switchcolumn*

Even though the road was littered with boulders and pitted with holes, Bruce was not in the least perturbed.

\switchcolumn

\chinesetext{尽管路面布满石头，坑坑洼洼，但布鲁斯却一点儿不慌乱。}

\switchcolumn*

Glancing at his map, he informed us that the next village was a mere twenty miles away.

\switchcolumn

\chinesetext{他瞥了一眼地图，告诉我们前面再走不到20英里就是一个村庄。}

\switchcolumn*

It was not that Bruce always underestimated difficulties.

\switchcolumn

\chinesetext{这并不是说布鲁斯总是低估困难。}

\switchcolumn*

He simply had no sense of danger at all.

\switchcolumn

\chinesetext{而是他压根儿没有一点儿危险感。}

\switchcolumn*

No matter what the conditions were, he believed that a car should be driven as fast as it could possibly go.

\switchcolumn

\chinesetext{他认为不管路面情况如何，车必须以最高速度前进。}

\switchcolumn*

As we bumped over the dusty track, we swerved to avoid large boulders.

\switchcolumn

\chinesetext{我们在尘士飞扬的道路上颠簸，车子东拐西弯，以躲开那些大圆石。}

\switchcolumn*

The wheels scooped up stones which hammered ominously under the car.

\switchcolumn

\chinesetext{车轮搅起的石块锤击车身，发出不祥的锤击声。}

\switchcolumn*

We felt sure that sooner or later a stone would rip a hole in our petrol tank or damage the engine.

\switchcolumn

\chinesetext{我们想念迟早会飞起一个石块把油箱砸开一个窟窿，或者把发动机砸坏。}

\switchcolumn*

Because of this, we kept looking back, wondering if we were leaving a trail of oil and petrol behind us.

\switchcolumn

\chinesetext{因此，我们不时地掉过头，怀疑车后是否留下了机油和汽油的痕迹。}

\switchcolumn*

What a relief it was when the boulders suddenly disappeared, giving way to a stretch of plain where the only obstacles were clumps bushes.

\switchcolumn

\chinesetext{突然大石块不见了，前面是一片平地，唯一的障碍只有一簇簇灌木丛。这使我们长长地松了口气。}

\switchcolumn*

But there was worse to come.

\switchcolumn

\chinesetext{但是更糟糕的事情在等着我们。}

\switchcolumn*

Just ahead of us there was a huge fissure.

\switchcolumn

\chinesetext{离我们不远处，出现一个大裂缝。}

\switchcolumn*

In response to renewed pleadings, Bruce stopped.

\switchcolumn

\chinesetext{我们再次央求布鲁斯小心，他这才把车停了下来。}

\switchcolumn*

Though we all got out to examine the fissure, he remained in the car.

\switchcolumn

\chinesetext{我们纷纷下车察看那个大裂缝，他却呆在车上。}

\switchcolumn*

We informed him that the fissure extended for fifty yards and was two feet wide and four feet deep.

\switchcolumn

\chinesetext{我们告诉他那个大裂缝长50码，宽2英尺，深4英尺。}

\switchcolumn*

Even this had no effect.

\switchcolumn

\chinesetext{这也没有对他产生任何影响。}

\switchcolumn*

Bruce went into a low gear and drove at a terrifying speed, keeping the front wheels astride the crack as he followed its zigzag course.

\switchcolumn

\chinesetext{布鲁斯挂上慢档，把两只前轮分别搁在裂缝的两边，顺着弯弯曲曲的裂缝，以发疯的速度向前开去。}

\switchcolumn*

Before we had time to worry about what might happen, we were back on the plain again.

\switchcolumn

\chinesetext{我们还未来得及担心后果，车已重新开上了平地。}

\switchcolumn*

Bruce consulted the map once more and told us that the village was now only fifteen miles away.

\switchcolumn

\chinesetext{布鲁斯又看了一眼地图，告诉我们那座村庄离我们只有15英里了。}

\switchcolumn*

Our next obstacle was a shallow pool of water about half a mile across.

\switchcolumn

\chinesetext{下一个障碍是一片约半英里宽的浅水塘。}

\switchcolumn*

Bruce charged at it, but in the middle, the car came to a grinding halt.

\switchcolumn

\chinesetext{布鲁斯向水塘冲去，但车开到水塘当中，嘎吱一声停住了。}

\switchcolumn*

A yellow light on the dashboard flashed angrily and Bruce cheerfully announced that there was no oil in the engine!

\chinesetext{仪表盘一盏黄灯闪着刺眼的光芒，布鲁斯兴致勃勃地宣布发动机里没油了！}

\switchcolumn*

\end{paracol}

\newpage