\section{Lesson 33 A day to remember}

\begin{paracol}{2}

We have all experienced days when everything goes wrong.

\switchcolumn

\chinesetext{我们大家都有过事事不顺心的日子。}

\switchcolumn*

A day may begin well enough, but suddenly everything seems to get out of control.

\switchcolumn

\chinesetext{一天开始时，可能还不错，但突然间似乎一切都失去了控制。}

\switchcolumn*

What invariably happens is that a great number of things choose to go wrong at precisely the same moment.

\switchcolumn

\chinesetext{情况经常是这样的，许许多多的事情都偏偏赶在同一时刻出问题。}

\switchcolumn*

It is as if a single unimportant event set up a chain of reactions.

\switchcolumn

\chinesetext{好像是一件无关紧要的小事引起了一连串的连锁反应。}

\switchcolumn*

Let us suppose that you are preparing a meal and keeping an eye on the baby at the same time.

\switchcolumn

\chinesetext{假设你在做饭，同时又在照看孩子。}

\switchcolumn*

The telephone rings and this marks the prelude to an unforeseen series of catastrophes.

\switchcolumn

\chinesetext{这时电话铃响了。它预示着一连串意想不到的灾难的来临。}

\switchcolumn*

While you are on the phone, the baby pulls the tablecloth off the table, smashing half your best crockery and cutting himself in the process.

\switchcolumn

\chinesetext{就在你接电话时，孩子把桌布从桌子上扯下来，将家中最好的陶瓷餐具半数摔碎，同时也弄伤了他自己。}

\switchcolumn*

You hang up hurriedly and attend to baby, crockery, etc.

\switchcolumn

\chinesetext{你急急忙忙挂上电话，赶去照看孩子和餐具。}

\switchcolumn*

Meanwhile, the meal gets burnt.

\switchcolumn

\chinesetext{这时，饭又烧糊了。}

\switchcolumn*

As if this were not enough to reduce you to tears, your husband arrives, unexpectedly bringing three guests to dinner.

\switchcolumn

\chinesetext{好像这一切还不足以使你急得掉泪，你的丈夫接着回来了，事先没打招呼就带来3个客人吃饭。}

\switchcolumn*

Things can go wrong on a big scale as a number of people recently discovered in Parramatta, a suburb of Sydney.

\switchcolumn

\chinesetext{就像许多人最近在悉尼郊区帕拉马塔发现的那样，有时乱子会闹得很大。}

\switchcolumn*

During the rush hour one evening two cars collided and both drivers began to argue.

\switchcolumn

\chinesetext{一天傍晚交通最拥挤时，一辆汽车撞上前面一辆汽车，两个司机争吵起来。}

\switchcolumn*

The woman immediately behind the two cars happened to be a learner.

\switchcolumn

\chinesetext{紧跟其后的一辆车上的司机碰巧是个初学者。}

\switchcolumn*

She suddenly got into a panic and stopped her car.

\switchcolumn

\chinesetext{她一惊之下突然把车停了下来。}

\switchcolumn*

This made the driver following her brake hard.

\switchcolumn

\chinesetext{她这一停使得跟在后头的司机也来个急刹车。}

\switchcolumn*

His wife was sitting beside him holding a large cake.

\switchcolumn

\chinesetext{司机妻子正坐在他身边，手里托着块大蛋糕。}

\switchcolumn*

As she was thrown forward, the cake went right through the windscreen and landed on the road.

\switchcolumn

\chinesetext{她往前一冲，蛋糕从挡风玻璃飞了出去掉到马路上。}

\switchcolumn*

Seeing a cake flying through the air, a lorry driver who was drawing up alongside the car, pulled up all of a sudden.

\switchcolumn

\chinesetext{此时，一辆卡车正好从后边开到那辆汽车边上，司机看见一块蛋糕从天而降，紧急刹车。}

\switchcolumn*

The lorry was loaded with empty beer bottles and hundreds of them slid off the back of the vehicle and on to the road.

\switchcolumn

\chinesetext{卡车上装着空啤酒瓶。成百只瓶子顺势从卡车后面滑出车外落在马路上。}

\switchcolumn*

This led to yet another angry argument. 

\switchcolumn

\chinesetext{这又引起一场唇枪舌剑的争吵。}

\switchcolumn*

Meanwhile, the traffic piled up behind.

\switchcolumn

\chinesetext{与此同时，后面的车辆排成了长龙。}

\switchcolumn*

It took the police nearly an hour to get the traffic on the move again.

\switchcolumn

\chinesetext{警察花了将近一个小时才使车辆又开起来。}

\switchcolumn*

In the meantime, the lorry driver had to sweep up hundreds of broken bottles.

\switchcolumn

\chinesetext{在这段时间里，卡车司机不得不清扫那几百只破瓶子。}

\switchcolumn*

Only two stray dogs benefited from all this confusion, for they greedily devoured what was left of the cake.

\switchcolumn

\chinesetext{只有两只野狗从这一片混乱中得到好处，它们贪婪地吃掉了剩下的蛋糕。}

\switchcolumn*

It was just one of those days!

\switchcolumn

\chinesetext{这就是事事不顺心的那么一天！}

\switchcolumn*

\end{paracol}

\newpage