\section{Lesson 40 Who's who}

\begin{paracol}{2}

It has never been explained why university students seem to enjoy practical jokes more than anyone else.

\switchcolumn

\chinesetext{谁也弄不清为什么大学生好像比任何人都更喜欢恶作剧。}

\switchcolumn*

Students specialize in a particular type of practical joke: the hoax.

\switchcolumn

\chinesetext{大学生擅长一种特殊的恶作剧--戏弄人。}

\switchcolumn*

Inviting the fire brigade to put out a nonexistent fire is a crude form of deception which no self-respecting student would ever indulde in.

\switchcolumn

\chinesetext{请消防队来扑灭一场根本没有的大火是一种低级骗局，有自尊心的大学生决不会去做。}

\switchcolumn*

Students often create amusing situations which are funny to everyone except the victims.

\switchcolumn

\chinesetext{大学生们常常做的是制造一种可笑的局面，使大家笑上一场，当然受害者是笑不出来的。}

\switchcolumn*

When a student recently saw two workmen using a pneumatic drill outside his university, he immediately telephoned the police and informed them that two students dressed up as workmen were tearing up the road with a pneumatic drill.

\switchcolumn

\chinesetext{最近有个学生看见两个工人在学校门外用风钻干活，马上打电话报告警察，说有两个学生装扮成工人，正在用风钻破坏路面。}

\switchcolumn*

As soon as he had hung up, he went over to the workmen and told them that if a policeman ordered them to go away, they were not to take him seriously.

\switchcolumn

\chinesetext{挂上电话后，他又马上来到工人那儿，告诉他们若有个警察来让他们走开，不要把他当回事。}

\switchcolumn*

He added that a student had dressed up as a policeman and was playing all sorts of silly jokes on people.

\switchcolumn

\chinesetext{还对工人说，有个学生常装扮成警察无聊地同别人开玩笑。}

\switchcolumn*

Both the police and the workmen were grateful to the student for this piece of advance information.

\switchcolumn

\chinesetext{警察与工人都对那个学生事先通报情况表示感谢。}

\switchcolumn*

The student hid in an archway nearby where he could watch and hear everything that went on.

\switchcolumn

\chinesetext{那个学生躲在附近一拱形的门廊里，在那儿可以看见、听到现场发生的一切。}

\switchcolumn*

Sure enough, a policeman arrived on the scene and politely asked the workmen to go away.

\switchcolumn

\chinesetext{果然，警察来了，不礼貌地请工人离开此地。}

\switchcolumn*

When he received a very rude reply from one of the workmen, he threatened to remove them by force.

\switchcolumn

\chinesetext{但其中一个工人粗鲁地回了几句。于是警察威胁要强行使他们离开。}

\switchcolumn*

The workmen told him to do as he pleased and the policeman telephoned for help.

\switchcolumn

\chinesetext{工人说，悉听尊便。警察去打电话叫人。}

\switchcolumn*

Shortly afterwards, 4 more policemen arrived and remonstrated with the workmen.

\switchcolumn

\chinesetext{一会儿工夫，又来了4个警察，规劝工人离开。}

\switchcolumn*

As the men refused to stop working, the police attempted to seize the pneumatic drill.

\switchcolumn

\chinesetext{由于工人拒绝停下手中的活，警察想夺风钻。}

\switchcolumn*

The workmen struggled fiercely and one of them lost his temper.

\switchcolumn

\chinesetext{两个工人奋力抗争，其中一个发了火}

\switchcolumn*

He threatened to call the police.

\switchcolumn

\chinesetext{他威胁说要去叫警察。}

\switchcolumn*

At this, the police pointed out ironically that this would hardly be necessary as the men were already under arrest.

\switchcolumn

\chinesetext{警察听后讥讽地说，这大可不必，因为他俩已被逮捕了。}

\switchcolumn*

Pretending to speak seriously, one of the workmen asked if he might make a telephone call before being taken to the station.

\switchcolumn

\chinesetext{其中一个工人装模作样地问道，在被带往警察局之前，是否可以打一个电话。}

\switchcolumn*

Permission was granted and a policeman accompanied him to a pay phone.

\switchcolumn

\chinesetext{警察同意了，陪他来到一个投币地电话前。}

\switchcolumn*

Only when he saw that the man was actually telephoning the police did he realize that they had all been the victims of a hoax.

\switchcolumn

\chinesetext{当他看到那个工人真的是给警察挂电话，才恍然大悟，原来他们都成一场骗局的受害者。}

\switchcolumn*

\end{paracol}

\newpage