\section{CHAPTER 1 Before Breakfast}

\begin{paracol}{2}
    
"Where's Papa going with that ax?" said Fern to her mother as they were setting the table for breakfast.

\switchcolumn

\switchcolumn*

"Out to the hog house," replied Mrs. Arable. "Some pigs were born last night."

\switchcolumn

\switchcolumn*

"I don't see why he needs an ax," continued Fern, who was only eight.

\switchcolumn

\switchcolumn*

"Well," said her mother, "one of the pigs is a \nw{runt}. It's very small and weak, and it will never amount to anything. So your father has decided to do away with it."

\switchcolumn

\nwe{runt}{rʌnt}{n. 发育不全的矮小动物，矮子;}

\switchcolumn*

"Do away with it?" shrieked Fern." You mean kill it? Just because it's smaller than the others?"

\switchcolumn

\nwe{shriek}{ʃrik}{vt.& vi. 尖叫;引人注意;发出一种类似尖叫的声音;n. 尖叫声;尖锐的声音：一种能使人联想起这种尖叫的声音;}

\switchcolumn*

Mrs. Arable put a pitcher of cream on the table." Don't yell, Fern!"she said. "Your father is right. The pig would probably die anyway."

\switchcolumn

\switchcolumn*

Fern pushed a chair out of the way and ran outdoors. The grass was wet and the earth smelled of springtime. Fern's \nw{sneakers} were \nw{sopping} \ns{by the time} she \ns{caught up with} her father.

\switchcolumn

\nwe{sneakers}{'snikəz}{n. 旅游鞋，运动鞋，球鞋;（帆布胶底）运动鞋( sneaker的名词复数 );}
\nwe{sopping}{ˈsɑpɪŋ}{v. 将（面包等）在液体中蘸或浸泡( sop的现在分词 );用海绵、布等吸起（液体等）;adj. 湿透的;}
\nse{by the time}{}{到…时候为止;等到;比及;}
\nse{catch up with}{}{追上; 赶上;和…算旧账;使…最终尝到苦果;}

\switchcolumn*

"Please don't kill it! "she sobbed. "It's unfair."

\switchcolumn

\switchcolumn*

Mr. Arable stopped walking.

\switchcolumn

\switchcolumn*

"Fern," he said gently," you will have to learn to control yourself."

\switchcolumn

\switchcolumn*

"Control myself?" yelled Fern. "This is a matter of life and death, and you talk about controlling myself." \ns{Tears ran down her cheeks} and she \ns{took hold of} the ax and tried to pull it out of her father's hand.

\switchcolumn

\nse{tears run down one's cheeks}{}{眼泪顺着...的脸颊流了下来}
\nse{take hold of}{}{握住; 控制住; 吸引; 对…有影响力;}

\switchcolumn*

"Fern," said Mr. Arable, "I know more about raising \ns{a \nw{litter} of} pigs than you do. A \nw{weakling} makes trouble. Now run along!"

\switchcolumn

\nwe{litter}{ˈlɪtər}{n. 废弃物，垃圾;杂乱的一堆;一窝幼崽;猫砂;褥草;轿子;v. 使凌乱;乱扔;（猫狗）产仔;}
\nwe{weakling}{ˈwiklɪŋ}{n. 软弱的人或动物;}
\nse{a litter of}{}{一窝}

\switchcolumn*

"But it's unfair," cried Fern. "The pig \ns{couldn't help being} born small, could it? If I had been very small at birth, would you have killed me?"

\switchcolumn

\nse{can't help doing sth}{}{忍不住做某事,不由自主地做某事}

\switchcolumn*

Mr. Arable smiled. "Certainly not," he said, looking down at his daughter with love. "But this is different. A little girl is one thing, a little runty pig is another."

\switchcolumn

\switchcolumn*

"I see no difference," replied Fern, still \ns{hanging on to} the ax. "This is the most terrible case of injustice I ever heard of."

\switchcolumn

\nse{hang on to}{}{v. 紧紧握住;}

\switchcolumn*

A \nw{queer} look came over John Arable's face. He seemed almost ready to cry himself.

\switchcolumn

\nwe{queer}{kwɪr}{adj. 古怪的;异常的;同性恋的;
n. 同性恋者;}

\switchcolumn*

"All right," he said. "You go back to the house and I will bring the runt when I come in. I'll let you start it on a bottle, like a baby. Then you'll see what trouble a pig can be."

\switchcolumn

\switchcolumn*

When Mr.Arable returned to the house half an hour later, he carried a \nw{carton} under his arm. Fern was upstairs changing her sneakers. The kitchen table was set for breakfast, and the room smelled of coffee, \nw{bacon}, \ns{\nw{damp} \nw{plaster}}, and wood smoke from the \nw{stove}.

\switchcolumn

\nwe{carton}{ˈkɑːrtn}{n. （装食物或饮料的）塑料盒，硬纸盒;硬纸箱;}
\nwe{bacon}{ˈbeɪkən}{n. 培根，熏猪肉;}
\nwe{damp}{dæmp}{adj. 潮湿的;n. 湿气;潮湿;v. 弄湿;削弱;抑制;}
\nwe{plaster}{ˈplæstər}{n. 灰泥，涂墙泥;石膏;膏药;vt. 涂以灰泥;在…上敷贴膏药;减轻;黏贴;}
\nwe{stove}{stoʊv}{n. 炉子;厨灶;}
\nse{damp plaster}{}{湿灰泥;}

\switchcolumn*

"Put it on her chair!" said Mrs. Arable. Mr. Arable set the carton down at Fern's place. Then he walked to the sink and washed his hands and dried them on the \ns{roller towel}.

\switchcolumn

\nwe{towel}{ˈtaʊəl}{n. 毛巾，手巾;纸巾;vt. 用毛巾擦;vi. 用毛巾擦干身体;}
\nse{roller towel}{}{n. 套在滚筒上转动的搽手毛巾;}

\switchcolumn*

Fern came slowly down the stairs. Her eyes were red from crying. As she approached her chair, the carton \nw{wobbled}, and there was a \nw{scratching} noise. Fern looked at her father. Then she \nw{lifted} \ns{the lid of} the carton. There, inside, looking up at her, was the newborn pig. It was a white one. The morning light shone through its ears, turning them pink.

\switchcolumn

\nwe{wobble}{ˈwɑːbl}{vt.& vi. <使>晃动;<使>摇摆不定;颤动;n. 摇动，晃动;不稳定;}
\nwe{scratch}{skrætʃ}{v. 挠，搔;划伤，刮坏;勉强维生;取消;n. 划痕，划伤;刮/擦的刺耳声;挠痒;adj. 仓促拼凑的;无让步的;}
\nwe{lift}{lɪft}{v. 提;移动;抬起;撤销;情绪高涨;消散;偷窃;空运;挖出;提高;n. 鼓舞;电梯;搭便车;提高;心情较好;上升;升力;}
\nse{the lid of ...}{}{……的盖子}

\switchcolumn*

"He's yours," said Mr.Arable." Saved from an untimely death. And may the good Lord forgive me for this foolishness."

\switchcolumn

\switchcolumn*

Fern couldn't take her eyes off the tiny pig. "Oh," she whispered. "Oh, look at him! He's absolutely perfect."

\switchcolumn

\switchcolumn*

She closed the carton carefully. First she kissed her father, then she kissed her mother. Then she opened the lid again, lifted the pig out, and held it against her cheek. At this moment her brother Avery came into the room. Avery was ten. He was heavily armed - an air rifle in one hand, a wooden dagger in the other.

\switchcolumn

\switchcolumn*

"What's that?" he demanded. "What's Fern got?"

\switchcolumn

\switchcolumn*

"She's got a guest for breakfast," said Mrs. Arable. "Wash your hands and face, Avery!"

\switchcolumn

\switchcolumn*

"Let's see it!" said Avery, setting his gun down." You call that miserable thing a pig? That's a fine \nw{specimen} of a pig, it's no bigger than a white rat."

\switchcolumn

\nwe{specimen}{ˈspesɪmən}{n. 样品;范例;（化验的）抽样;某种类型的人;}

\switchcolumn*

"Wash up and eat your breakfast, Avery!" said his mother." The school bus will be along in half an hour."

\switchcolumn

\switchcolumn*

"Can I have a pig, too, Pop?" asked Avery.

\switchcolumn

\switchcolumn*

"No, I only distribute pigs to \ns{early risers}," said Mr. Arable. "Fern was up at daylight, trying to \nw{rid} the world of injustice. As a result, she now has a pig. A small one, to be sure, but \nw{nevertheless} a pig. It just shows what can happen if a person gets out of bed \nw{promptly}. Let's eat!"

\switchcolumn
\nwe{rid}{rɪd}{v. （使）去掉，摆脱，消除;adj. 摆脱…的;}
\nwe{nevertheless}{ˌnevərðəˈles}{adv. 然而;尽管如此;不过;}
\nwe{promptly}{ˈprɑmptli}{adv. 敏捷地;迅速地;立即地;毫不迟疑;}
\nse{early risers}{}{习惯早起的人}

\switchcolumn*

But Fern couldn't eat until her pig had had a drink of milk.

\switchcolumn

\switchcolumn*

Mrs. Arable found a baby's \ns{nursing bottle} and a \ns{rubber nipple}. She \ns{poured warm milk into the bottle}, \ns{fitted the nipple over the top}, and \ns{handed it to Fern}. "Give him his breakfast!" she said.

\switchcolumn

\nse{nursing bottle}{}{n. 奶瓶;}
\nse{rubber nipple}{}{橡皮奶头;}
\nse{pour sth. into sth.}{}{将某物倒入/注入某物}
\nse{fit sth. over sth.}{}{将某物套在/盖在另一物之上，强调的是尺寸合适、紧凑地覆盖}
\nse{hand sth. to sb.}{}{递给某人某物}

\switchcolumn*

A minute later, Fern was seated on the floor in the corner of the kitchen with her infant between her knees, teaching it to suck from the bottle. The pig, although tiny, had a good \nw{appetite} and caught on quickly.

\switchcolumn

\nwe{appetite}{ˈæpɪtaɪt}{n. 胃口;食欲;强烈欲望;}

\switchcolumn*

The school bus \nw{honked} from the road.

\switchcolumn

\nwe{honk}{hɑŋk}{n. 雁叫声;汽车的喇叭声;vt.& vi. （使）发出雁叫似的声音，鸣（喇叭），按（喇叭）;}

\switchcolumn*

"Run!" commanded Mrs. Arable, taking the pig from Fern and slipping a \nw{doughnut} into her hand. Avery grabbed his gun and another doughnut.

\switchcolumn

\nwe{doughnut}{ˈdoˌnʌt,-nət}{n. 炸面圈，圈饼;汽车轮胎;环状物;电子回旋加速室;}

\switchcolumn*

The children ran out to the road and climbed into the bus. Fern took no notice of the others in the bus. She just sat and stared out of the window, thinking what a blissful world it was and how lucky she was to have entire charge of a pig. By the time the bus reached school, Fern had named her pet, selecting the most beautiful name she could think of.

\switchcolumn

\switchcolumn*

"Its name is Wilbur," she whispered to herself.

\switchcolumn

\switchcolumn*

She was still thinking about the pig when the teacher said: "Fern, what is the capital of Pennsylvania?"

\switchcolumn

\switchcolumn*

"Wilbur," replied Fern, dreamily. The pupils giggled. Fern blushed.

\switchcolumn

\switchcolumn*

\end{paracol}