\begin{paracol}{2}
	\sense{Scene: Central Perk, Chandler, Joey, Phoebe, and Monica are there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，钱德勒、乔伊、菲比和莫妮卡在场。}
	\switchcolumn*
	\charactername{Monica:} There's nothing to tell! He's just some guy I work with!
	\switchcolumn
	\charactername{莫妮卡：}没什么好说的！他不过是我的同事！
	\switchcolumn*
	\charactername{Joey:} Come on, you're going out with the guy! There's gotta be something wrong with him!
	\switchcolumn
	\charactername{乔伊：}少来了，你和那个人一起出去！拜托，和你交往的男人一定有问题！
	\switchcolumn*
	\charactername{Chandler:} All right Joey, be nice. So does he have a hump? A hump and a hairpiece?
	\switchcolumn
	\charactername{钱德勒：}打住，乔伊，嘴下留德。他驼背？既驼背又带假发？
	\switchcolumn*
	\charactername{Phoebe:} Wait, does he eat chalk?
	\switchcolumn
	\charactername{菲比：}慢着，他吃粉笔吗？
	\switchcolumn*
	\ennotmain{They all stare, bemused.}
	\switchcolumn
	\notmain{众人困惑地盯着她。}
	\switchcolumn*
	\charactername{Phoebe:} Just, 'cause, I don't want her to go through what I went through with Carl- oh!
	\switchcolumn
	\charactername{菲比：}我只是不想你重蹈我和卡尔的覆辙。
	\switchcolumn*
	\charactername{Monica:} Okay, everybody relax. This is not even a date. It's just two people going out to dinner and- not having sex.
	\switchcolumn
	\charactername{莫妮卡：}各位别急，这不算约会。我们不过是出去吃晚餐，而且不做爱。
	\switchcolumn*
	\charactername{Chandler:} Sounds like a date to me.
	\switchcolumn
	\charactername{钱德勒：}听起来好像是说我的约会。
	\switchcolumn*
	\sense{Time Lapse}
	\switchcolumn
	\sense{时间流逝}
	\switchcolumn*
	\charactername{Chandler:} Alright, so I'm back in high school, I'm standing in the middle of the cafeteria, and I realize I am totally naked.
	\switchcolumn
	\charactername{钱德勒：}记得中学时代的梦，我站在自助餐厅，突然发现自己全身赤裸。
	\switchcolumn*
	\charactername{All:} Oh, yeah. Had that dream.
	\switchcolumn
	\charactername{众人：}我做过那样的梦。
	\switchcolumn*
	\charactername{Chandler:} Then I look down, and I realize there's a phone... there.
	\switchcolumn
	\charactername{钱德勒：}我低头一看，看见有一支电话……在那儿。
	\switchcolumn*
	\charactername{Joey:} Instead of...?
	\switchcolumn
	\charactername{乔伊：}而不是……？
	\switchcolumn*
	\charactername{Chandler:} That's right.
	\switchcolumn
	\charactername{钱德勒：}没错。
	\switchcolumn*
	\charactername{Joey:} Never had that dream.
	\switchcolumn
	\charactername{乔伊：}我没做过那样的梦。
	\switchcolumn*
	\charactername{Phoebe:} No.
	\switchcolumn
	\charactername{菲比：}没有。
	\switchcolumn*
	\charactername{Chandler:} All of a sudden, the phone starts to ring. Now I don't know what to do, everybody starts looking at me.
	\switchcolumn
	\charactername{钱德勒：}那支电话突然响起，而我不知道怎么办，每个人都开始望着我。
	\switchcolumn*
	\charactername{Monica:} And they weren't looking at you before?!
	\switchcolumn
	\charactername{莫妮卡：}他们以前不看你吗？！
	\switchcolumn*
	\charactername{Chandler:} Finally, I figure I'd better answer it, and it turns out it's my mother, which is very-very weird, because- she never calls me!
	\switchcolumn
	\charactername{钱德勒：}终于，我认为我应该接，结果是我妈打来，我感到很奇怪，因为我妈不曾打过电话给我！
	\switchcolumn*
	\sense{Time Lapse, Ross has entered.}
	\switchcolumn
	\sense{时间流逝，罗斯走进来。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{mortified} Hi.
	\switchcolumn
	\charactername{罗斯：}\notmain{窘迫地}嗨。
	\switchcolumn*
	\charactername{Joey:} This guy says hello, I wanna kill myself.
	\switchcolumn
	\charactername{乔伊：}这家伙向我打招呼时我就想自杀。
	\switchcolumn*
	\charactername{Monica:} Are you okay, sweetie?
	\switchcolumn
	\charactername{莫妮卡：}你还好吧？
	\switchcolumn*
	\charactername{Ross:} I just feel like someone reached down my throat, grabbed my small intestine, pulled it out of my mouth and tied it around my neck...
	\switchcolumn
	\charactername{罗斯：}我感觉有人把手伸入我的喉咙，抓起我的肠子，从我的口中取出，然后绑在我脖上……
	\switchcolumn*
	\charactername{Chandler:} Cookie?
	\switchcolumn
	\charactername{钱德勒：}饼干？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{explaining to the others} Carol moved her stuff out today.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{向其他人解释}卡罗今天把她的东西搬走了。
	\switchcolumn*
	\charactername{Joey:} Ohh.
	\switchcolumn
	\charactername{乔伊：}哦。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Ross} Let me get you some coffee.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对罗斯}我帮你泡杯咖啡。
	\switchcolumn*
	\charactername{Ross:} Thanks.
	\switchcolumn
	\charactername{罗斯：}谢了。
	\switchcolumn*
	\charactername{Phoebe:} Ooh! Oh! \ennotmain{She starts to pluck at the air just in front of Ross.}
	\switchcolumn
	\charactername{菲比：}哦！哦！\notmain{她开始在罗斯面前的空中轻拨。}
	\switchcolumn*
	\charactername{Ross:} No, no don't! Stop cleansing my aura! No, just leave my aura alone, okay?
	\switchcolumn
	\charactername{罗斯：}不要……别清理我的灵气。可是……别碰我的灵气就是了。
	\switchcolumn*
	\charactername{Phoebe:} Fine! Be murky!
	\switchcolumn
	\charactername{菲比：}好吧，保持晦气！
	\switchcolumn*
	\charactername{Ross:} I'll be fine, alright? Really, everyone. I hope she'll be very happy.
	\switchcolumn
	\charactername{罗斯：}我会没事的，真的，我祝她幸福。
	\switchcolumn*
	\charactername{Monica:} No you don't.
	\switchcolumn
	\charactername{莫妮卡：}不，你不会的。
	\switchcolumn*
	\charactername{Ross:} No I don't, to hell with her, she left me!
	\switchcolumn
	\charactername{罗斯：}我不会的，去她的，她甩掉我！
	\switchcolumn*
	\charactername{Joey:} And you never knew she was a lesbian...
	\switchcolumn
	\charactername{乔伊：}而且你一直都不知道她是女同性恋者。
	\switchcolumn*
	\charactername{Ross:} No!! Okay?! Why does everyone keep fixating on that? She didn't know, how should I know?
	\switchcolumn
	\charactername{罗斯：}没有！！行了吧？！为何大家都围着这个话题打转？连她不知道，我怎会知道。
	\switchcolumn*
	\charactername{Chandler:} Sometimes I wish I was a lesbian... \ennotmain{They all stare at him.} Did I say that out loud?
	\switchcolumn
	\charactername{钱德勒：}有时真希望自己也是个女同志。\notmain{众人盯着他}我刚刚大声说出来了吗？
	\switchcolumn*
	\charactername{Ross:} I told mom and dad last night, they seemed to take it pretty well.
	\switchcolumn
	\charactername{罗斯：}昨晚我告诉我父母，他们好像还挺好。
	\switchcolumn*
	\charactername{Monica:} Oh really, so that hysterical phone call I got from a woman at sobbing 3:00 A.M., "I'll never have grandchildren, I'll never have grandchildren." was what? A wrong number?
	\switchcolumn
	\charactername{莫妮卡：}真的吗？凌晨三点我接到一个电话，一个女人歇斯底里地向我哭诉，“我不能抱孙子了，我不能抱孙子了。”那是什么？打错了？
	\switchcolumn*
	\charactername{Ross:} Sorry.
	\switchcolumn
	\charactername{罗斯：}对不起。
	\switchcolumn*
	\charactername{Joey:} Alright Ross, look. You're feeling a lot of pain right now. You're angry. You're hurting. Can I tell you what the answer is?
	\switchcolumn
	\charactername{乔伊：}别闷闷不乐了，罗斯。你现在很痛苦，一肚子火，心如刀割。能告诉你解决之道吗？
	\switchcolumn*
	\ennotmain{Ross gestures his consent.}
	\switchcolumn
	\notmain{罗斯示意同意。}
	\switchcolumn*
	\charactername{Joey:} Strip joint! C'mon, you're single! Have some hormones!
	\switchcolumn
	\charactername{乔伊：}脱衣舞酒店。你单身，有性需求。
	\switchcolumn*
	\charactername{Ross:} I don't want to be single, okay? I just... I just- I just wanna be married again!
	\switchcolumn
	\charactername{罗斯：}我不想单身的。我只想再结婚。
	\switchcolumn*
	\ennotmain{Rachel enters in a wet wedding dress and starts to search the room.}
	\switchcolumn
	\notmain{瑞秋穿着湿婚纱走进来，开始环顾房间。}
	\switchcolumn*
	\charactername{Chandler:} And I just want a million dollars! \ennotmain{He extends his hand hopefully.}
	\switchcolumn
	\charactername{钱德勒：}我只想要一百万！\notmain{满怀希望地伸出手。}
	\switchcolumn*
	\charactername{Monica:} Rachel?!
	\switchcolumn
	\charactername{莫妮卡：}瑞秋？！
	\switchcolumn*
	\charactername{Rachel:} Oh God Monica hi! Thank God! I just went to your building and you weren't there and then this guy with a big hammer said you might be here and you are, you are!
	\switchcolumn
	\charactername{瑞秋：}天啊，莫妮卡，谢天谢地！我到过你的住处，你不在。有个拿着一根大榔头的人说你可能会在这儿，结果你真的在这儿。
	\switchcolumn*
	\charactername{Waitress:} Can I get you some coffee?
	\switchcolumn
	\charactername{女服务员：}想来杯咖啡吗？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{pointing at Rachel} De-caff. \ennotmain{to All} Okay, everybody, this is Rachel, another Lincoln High survivor. \ennotmain{to Rachel} This is everybody, this is Chandler, and Phoebe, and Joey, and- you remember my brother Ross?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{指着瑞秋}无咖啡因的。各位，她叫瑞秋，另一位从林肯高中毕业的人。\notmain{对瑞秋}这位是钱德勒、菲比、乔伊。还记得我哥罗斯吗？
	\switchcolumn*
	\charactername{Rachel:} Hi, sure!
	\switchcolumn
	\charactername{瑞秋：}当然。
	\switchcolumn*
	\charactername{Ross:} Hi.
	\switchcolumn
	\charactername{罗斯：}嗨。
	\switchcolumn*
	\ennotmain{They go to hug but Ross's umbrella opens. He sits back down defeated again. A moment of silence follows as Rachel sits and the others expect her to explain.}
	\switchcolumn
	\notmain{他们准备拥抱，罗斯的雨伞却突然撑开。他沮丧地坐下。瑞秋坐下后，众人等待她解释，一阵沉默。}
	\switchcolumn*
	\charactername{Monica:} So you wanna tell us now, or are we waiting for four wet bridesmaids?
	\switchcolumn
	\charactername{莫妮卡：}你想现在告诉我们，还是等四位湿淋淋的伴娘来再说？
	\switchcolumn*
	\charactername{Rachel:} Oh God... well, it started about a half hour before the wedding. I was in the room where we were keeping all the presents, and I was looking at this gravy boat. This really gorgeous Lamauge gravy boat. When all of a sudden- \ennotmain{to the waitress that brought her coffee} Sweet 'n' Lo?- I realized that I was more turned on by this gravy boat than by Barry! And then I got really freaked out, and that's when it hit me: how much Barry looks like Mr. Potato Head. Y'know, I mean, I always knew looked familiar, but... Anyway, I just had to get out of there, and I started wondering 'Why am I doing this, and who am I doing this for?'. \ennotmain{to Monica} So anyway I just didn't know where to go, and I know that you and I have kinda drifted apart, but you're the only person I knew who lived here in the city.
	\switchcolumn
	\charactername{瑞秋：}天啊……婚礼前半个小时发生了变数。我在堆放礼物的房间里，看着船形卤肉盘，非常漂亮的船形卤肉盘，突然间……\notmain{对送咖啡的女服务员}有没有代糖？我发现船形卤肉盘比巴瑞更能引起我的“性趣”，我自己都吓了一跳，巴瑞愈看愈像猪头先生。我一直都认为他很眼熟。总之，我必须离开。我开始想，我为何这么做？我为谁这样做？于是我不知该走往何处，我知道你我日渐疏远，但你是我在这个城市认识的唯一一个人。
	\switchcolumn*
	\charactername{Monica:} Who wasn't invited to the wedding.
	\switchcolumn
	\charactername{莫妮卡：}好像是唯一没受邀参加婚礼的人。
	\switchcolumn*
	\charactername{Rachel:} Ooh, I was kinda hoping that wouldn't be an issue...
	\switchcolumn
	\charactername{瑞秋：}这件事就甭提啦。
	\switchcolumn*
	\sense{Scene: Monica's Apartment, everyone is there and watching a Spanish Soap on TV and are trying to figure out what is going on.}
	\switchcolumn
	\sense{场景：莫妮卡的公寓，众人正在看西班牙语肥皂剧，试图弄明白剧情。}
	\switchcolumn*
	\charactername{Monica:} Now I'm guessing that he bought her the big pipe organ, and she's really not happy about it.
	\switchcolumn
	\charactername{莫妮卡：}我猜他送她一台管风琴，她肯定不喜欢。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{imitating the characters} Tuna or egg salad? Decide!
	\switchcolumn
	\charactername{钱德勒：}\notmain{模仿剧中角色}金枪鱼还是鸡蛋沙拉？快决定！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{in a deep voice} I'll have whatever Christine is having.
	\switchcolumn
	\charactername{罗斯：}\notmain{压低声音}我要拥有克莉丝汀拥有的一切。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{on phone} Daddy, I just... I can't marry him! I'm sorry. I just don't love him. Well, it matters to me!
	\switchcolumn
	\charactername{瑞秋：}\notmain{打电话}爸，我不能嫁给他……对不起，我只是不爱他。对，是我的问题！
	\switchcolumn*
	\ennotmain{The scene on TV has changed to show two women, one is holding her hair.}
	\switchcolumn
	\notmain{电视画面切换，出现两个女人，其中一个抓着自己的头发。}
	\switchcolumn*
	\charactername{Phoebe:} If I let go of my hair, my head will fall off.
	\switchcolumn
	\charactername{菲比：}如果我没了头发，还不如去死。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{re TV} Ooh, she should not be wearing those pants.
	\switchcolumn
	\charactername{钱德勒：}\notmain{评论电视}她不该穿那条裤子。
	\switchcolumn*
	\charactername{Joey:} I say push her down the stairs.
	\switchcolumn
	\charactername{乔伊：}我建议推她下楼。
	\switchcolumn*
	\charactername{Phoebe, Ross, Chandler, and Joey:} Push her down the stairs! Push her down the stairs! Push her down the stairs!
	\switchcolumn
	\charactername{菲比、罗斯、钱德勒、乔伊：}推她下楼！推她下楼！推她下楼！
	\switchcolumn*
	\ennotmain{She is pushed down the stairs and everyone cheers.}
	\switchcolumn
	\notmain{剧中女人被推下楼，众人欢呼。}
	\switchcolumn*
	\charactername{Rachel:} C'mon Daddy, listen to me! It's like, it's like, all of my life, everyone has always told me, 'You're a shoe! You're a shoe, you're a shoe, you're a shoe!'. And today I just stopped and I said, 'What if I don't wanna be a shoe? What if I wanna be a- a purse, y'know? Or a- or a hat! No, I'm not saying I want you to buy me a hat, I'm saying I am a ha- It's a metaphor, Daddy!
	\switchcolumn
	\charactername{瑞秋：}爸，你听我说……大家这样评价我这一辈子：你是一只鞋……今天我倒想看看如果我不再是鞋会怎样。我说如果我想当皮包呢？或是帽子呢？不，我不需你帮我买帽子。我说我是一顶帽子。爸，这是一种比喻。
	\switchcolumn*
	\charactername{Ross:} You can see where he'd have trouble.
	\switchcolumn
	\charactername{罗斯：}你看他也有些理解不了。
	\switchcolumn*
	\charactername{Rachel:} Look Daddy, it's my life. Well maybe I'll just stay here with Monica.
	\switchcolumn
	\charactername{瑞秋：}爸，这是我的人生。或许我会和莫妮卡住在这儿。
	\switchcolumn*
	\charactername{Monica:} Well, I guess we've established who's staying here with Monica...
	\switchcolumn
	\charactername{莫妮卡：}我想我们已确定好谁要和莫妮卡住在这儿了。
	\switchcolumn*
	\charactername{Rachel:} Well, maybe that's my decision. Well, maybe I don't need your money. Wait!! Wait, I said maybe!!
	\switchcolumn
	\charactername{瑞秋：}或许那是我的决定。或许我不希罕你的钱。等一下，等一下……我说的是或许！！
	\switchcolumn*
	\sense{Time Lapse, Rachel is breathing into a paper bag.}
	\switchcolumn
	\sense{时间流逝，瑞秋对着纸袋呼吸。}
	\switchcolumn*
	\charactername{Monica:} Just breathe, breathe.. that's it. Just try to think of nice calm things...
	\switchcolumn
	\charactername{莫妮卡：}深呼吸，就这样。试着想着美好的事物……
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{sings} Raindrops on roses and rabbits and kittens, \ennotmain{Rachel and Monica turn to look at her.} bluebells and sleighbells and- something with mittens... La la la la...something and noodles with string. These are a few...
	\switchcolumn
	\charactername{菲比：}\notmain{唱歌}玫瑰上的雨滴，猫嘴上的胡须，门铃和雪橇之类的。啦 啦 啦……还有手套……
	\switchcolumn*
	\charactername{Rachel:} I'm all better now.
	\switchcolumn
	\charactername{瑞秋：}我现在好多了。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{grins and walks to the kitchen and says to Chandler and Joey.} I helped!
	\switchcolumn
	\charactername{菲比：}\notmain{笑着走向厨房，对钱德勒和乔伊说}我的功劳。
	\switchcolumn*
	\charactername{Monica:} Okay, look, this is probably for the best, y'know? Independence. Taking control of your life. The whole, 'hat' thing.
	\switchcolumn
	\charactername{莫妮卡：}或许这样最好，要自立，决定自己的事情。关于那个“帽子”的比喻。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{comforting her} And hey, you need anything, you can always come to Joey. Me and Chandler live across the hall. And he's away a lot.
	\switchcolumn
	\charactername{乔伊：}\notmain{安慰她}有任何需要找乔伊准没错。我和钱德勒就住在对面，而且他经常不在家。
	\switchcolumn*
	\charactername{Monica:} Joey, stop hitting on her! It's her wedding day!
	\switchcolumn
	\charactername{莫妮卡：}乔伊，少趁虚而入了，今天是她大喜的日子。
	\switchcolumn*
	\charactername{Joey:} What, like there's a rule or something?
	\switchcolumn
	\charactername{乔伊：}什么？有规定不能吗？
	\switchcolumn*
	\ennotmain{The door buzzer sounds and Chandler gets it.}
	\switchcolumn
	\notmain{门铃响起，钱德勒去开门。}
	\switchcolumn*
	\charactername{Chandler:} Please don't do that again, it's a horrible sound.
	\switchcolumn
	\charactername{钱德勒：}别再这样，声音很刺耳。
	\switchcolumn*
	\charactername{Paul:} \ennotmain{over the intercom} It's, uh, it's Paul.
	\switchcolumn
	\charactername{保罗：}\notmain{通过对讲机}我是保罗。
	\switchcolumn*
	\charactername{Monica:} Oh God, is it 6:30? Buzz him in!
	\switchcolumn
	\charactername{莫妮卡：}天啊，6:30了吗？让他进来！
	\switchcolumn*
	\charactername{Joey:} Who's Paul?
	\switchcolumn
	\charactername{乔伊：}保罗是谁？
	\switchcolumn*
	\charactername{Ross:} Paul the Wine Guy, Paul?
	\switchcolumn
	\charactername{罗斯：}调酒的那个保罗？
	\switchcolumn*
	\charactername{Monica:} Maybe.
	\switchcolumn
	\charactername{莫妮卡：}或许吧。
	\switchcolumn*
	\charactername{Joey:} Wait. Your 'not a real date' tonight is with Paul the Wine Guy?
	\switchcolumn
	\charactername{乔伊：}等等，你今晚那个“不算真正约会”的约会对象是调酒的保罗？
	\switchcolumn*
	\charactername{Ross:} He finally asked you out?
	\switchcolumn
	\charactername{罗斯：}他终于开口约你了？
	\switchcolumn*
	\charactername{Monica:} Yes!
	\switchcolumn
	\charactername{莫妮卡：}对！
	\switchcolumn*
	\charactername{Chandler:} Ooh, this is a Dear Diary moment.
	\switchcolumn
	\charactername{钱德勒：}终于被你等到了。
	\switchcolumn*
	\charactername{Monica:} Rach, wait, I can cancel...
	\switchcolumn
	\charactername{莫妮卡：}瑞秋，等等，我可以取消约会……
	\switchcolumn*
	\charactername{Rachel:} Please, no, go, that'd be fine!
	\switchcolumn
	\charactername{瑞秋：}不用了，你去吧，我不会有事的。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Ross} Are, are you okay? I mean, do you want me to stay?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对罗斯}罗斯，你没事吧？你要我留下来吗？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{choked voice} That'd be good...
	\switchcolumn
	\charactername{罗斯：}\notmain{哽咽着}那样最好……
	\switchcolumn*
	\charactername{Monica:} \ennotmain{horrified} Really?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{惊讶地}真的吗？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{normal voice} No, go on! It's Paul the Wine Guy!
	\switchcolumn
	\charactername{罗斯：}\notmain{恢复正常语气}假的，去吧！是保罗，调酒师耶！
	\switchcolumn*
	\charactername{Phoebe:} What does that mean? Does he sell it, drink it, or just complain a lot? \ennotmain{Chandler doesn't know.}
	\switchcolumn
	\charactername{菲比：}什么意思？他是卖酒的，喝酒的，还是评酒的？\notmain{钱德勒摇头表示不知道。}
	\switchcolumn*
	\ennotmain{There's a knock on the door and it's Paul.}
	\switchcolumn
	\notmain{敲门声响起，是保罗。}
	\switchcolumn*
	\charactername{Monica:} Hi, come in! Paul, this is.. \ennotmain{They are all lined up next to the door.}... everybody, everybody, this is Paul.
	\switchcolumn
	\charactername{莫妮卡：}请进！保罗，这位是……\notmain{众人在门边排好队}……各位，各位，他就是保罗。
	\switchcolumn*
	\charactername{All:} Hey! Paul! Hi! The Wine Guy! Hey!
	\switchcolumn
	\charactername{众人：}嘿！保罗！嗨！调酒大师！嘿！
	\switchcolumn*
	\charactername{Chandler:} I'm sorry, I didn't catch your name. Paul, was it?
	\switchcolumn
	\charactername{钱德勒：}抱歉，我没听清楚你名字。保罗，是吗？
	\switchcolumn*
	\charactername{Monica:} Okay, umm-umm, I'll just--I'll be right back, I just gotta go ah, go ah...
	\switchcolumn
	\charactername{莫妮卡：}我马上就好，我去，去……
	\switchcolumn*
	\charactername{Ross:} A wandering?
	\switchcolumn
	\charactername{罗斯：}神魂恍惚啦？
	\switchcolumn*
	\charactername{Monica:} Change! Okay, sit down. \ennotmain{Shows Paul in} Two seconds.
	\switchcolumn
	\charactername{莫妮卡：}换衣服！请坐，两秒钟就好。\notmain{示意保罗进屋}
	\switchcolumn*
	\charactername{Phoebe:} Ooh, I just pulled out four eyelashes. That can't be good.
	\switchcolumn
	\charactername{菲比：}我刚拔掉四根睫毛，不妙。
	\switchcolumn*
	\ennotmain{Monica goes to change.}
	\switchcolumn
	\notmain{莫妮卡去换衣服。}
	\switchcolumn*
	\charactername{Joey:} Hey, Paul!
	\switchcolumn
	\charactername{乔伊：}嗨，保罗！
	\switchcolumn*
	\charactername{Paul:} Yeah?
	\switchcolumn
	\charactername{保罗：}嗯，有何指教？
	\switchcolumn*
	\charactername{Joey:} Here's a little tip, she really likes it when you rub her neck in the same spot over and over and over again until it starts to get a little red.
	\switchcolumn
	\charactername{乔伊：}一个小秘密，莫妮卡其实就喜欢这样，你摩擦她脖子的同一个地方，反反复复，直到那里开始有点发红。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{yelling from the bedroom} Shut up, Joey!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{从卧室大喊}乔伊你给我闭嘴！
	\switchcolumn*
	\charactername{Ross:} So Rachel, what're you, uh... what're you up to tonight?
	\switchcolumn
	\charactername{罗斯：}瑞秋，你打算如何渡过今晚？
	\switchcolumn*
	\charactername{Rachel:} Well, I was kinda supposed to be headed for Aruba on my honeymoon, so nothing!
	\switchcolumn
	\charactername{瑞秋：}我应该在前往阿鲁巴渡蜜月的途中，因此没什么安排！
	\switchcolumn*
	\charactername{Ross:} Right, you're not even getting your honeymoon, God.. No, no, although, Aruba, this time of year... talk about your- \ennotmain{thinks} -big lizards... Anyway, if you don't feel like being alone tonight, Joey and Chandler are coming over to help me put together my new furniture.
	\switchcolumn
	\charactername{罗斯：}我懂，你没去成蜜月。虽然阿鲁巴在这个时候……有很多……大蜥蜴。如果你今晚不想独处，乔伊和钱德勒要到我那儿帮我组装新家具。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{deadpan} Yes, and we're very excited about it.
	\switchcolumn
	\charactername{钱德勒：}\notmain{面无表情}对，我们都相当兴奋。
	\switchcolumn*
	\charactername{Rachel:} Well actually thanks, but I think I'm just gonna hang out here tonight. It's been kinda a long day.
	\switchcolumn
	\charactername{瑞秋：}谢谢，但我今晚想待在这儿，我今天真是折腾够了。
	\switchcolumn*
	\charactername{Ross:} Okay, sure.
	\switchcolumn
	\charactername{罗斯：}好吧，当然。
	\switchcolumn*
	\charactername{Joey:} Hey Pheebs, you wanna help?
	\switchcolumn
	\charactername{乔伊：}菲比，想帮忙吗？
	\switchcolumn*
	\charactername{Phoebe:} Oh, I wish I could, but I don't want to.
	\switchcolumn
	\charactername{菲比：}我可以去，但我不想去。
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: The Subway, Phoebe is singing for change.}
	\switchcolumn
	\sense{场景：地铁里，菲比唱歌乞讨。}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{singing} Love is sweet as summer showers, love is a wondrous work of art, but your love oh your love, your love...is like a giant pigeon...crapping on my heart. La-la-la-la-la- \ennotmain{some guy gives her some change and to that guy} Thank you. \ennotmain{sings} La-la-la-la...ohhh!
	\switchcolumn
	\charactername{菲比：}\notmain{唱歌}爱情似炎炎夏日中的阵雨般美妙，爱是一件奇妙的艺术品，但你的爱，哦你的爱，你的爱……就像一只巨大的鸽子……在我心上拉屎。啦-啦-啦-啦-啦-\notmain{有人给她零钱，对那人说}谢谢。\notmain{继续唱}啦-啦-啦-啦……哦！
	\switchcolumn*
	\sense{Scene: Ross's Apartment, the guys are there assembling furniture.}
	\switchcolumn
	\sense{场景：罗斯的公寓，几个男人正在组装家具。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{squatting and reading the instructions} I'm supposed to attach a brackety thing to the side things, using a bunch of these little worm guys. I have no brackety thing, I see no whim guys whatsoever and- I cannot feel my legs.
	\switchcolumn
	\charactername{罗斯：}\notmain{蹲着看说明书}我应该用蜗杆将托架装在侧面，但我没看见托架和蜗杆，而且，我的脚好麻。
	\switchcolumn*
	\ennotmain{Joey and Chandler are finishing assembling the bookcase.}
	\switchcolumn
	\notmain{乔伊和钱德勒快要组装完书架了。}
	\switchcolumn*
	\charactername{Joey:} I'm thinking we've got a bookcase here.
	\switchcolumn
	\charactername{乔伊：}我想我们做好书架了。
	\switchcolumn*
	\charactername{Chandler:} It's a beautiful thing.
	\switchcolumn
	\charactername{钱德勒：}真漂亮。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{picking up a leftover part} What's this?
	\switchcolumn
	\charactername{乔伊：}\notmain{拿起一个多余的零件}这是什么？
	\switchcolumn*
	\charactername{Chandler:} I would have to say that is an 'L'-shaped bracket.
	\switchcolumn
	\charactername{钱德勒：}我只能说这是个“L”型托架。
	\switchcolumn*
	\charactername{Joey:} Which goes where?
	\switchcolumn
	\charactername{乔伊：}是哪儿的？
	\switchcolumn*
	\charactername{Chandler:} I have no idea.
	\switchcolumn
	\charactername{钱德勒：}我也不知道。
	\switchcolumn*
	\ennotmain{Joey checks that Ross is not looking and dumps it in a plant.}
	\switchcolumn
	\notmain{乔伊确认罗斯没注意，把零件扔进了花盆。}
	\switchcolumn*
	\charactername{Joey:} Done with the bookcase!
	\switchcolumn
	\charactername{乔伊：}书架做好了！
	\switchcolumn*
	\charactername{Chandler:} All finished!
	\switchcolumn
	\charactername{钱德勒：}终于做好了！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{clutching a beer can and sniffing} This was Carol's favorite beer. She always drank it out of the can, I should have known.
	\switchcolumn
	\charactername{罗斯：}\notmain{握着啤酒罐闻了闻}这是卡罗最爱喝的啤酒。她总是不用杯子喝，我早应该看出蛛丝马迹。
	\switchcolumn*
	\charactername{Joey:} Hey-hey-hey-hey, if you're gonna start with that stuff we're outta here.
	\switchcolumn
	\charactername{乔伊：}嗨……如果你再这样\notmain{伤春悲秋}，我们就走了。
	\switchcolumn*
	\charactername{Chandler:} Yes, please don't spoil all this fun.
	\switchcolumn
	\charactername{钱德勒：}对啊，请不要破坏这里的乐趣。
	\switchcolumn*
	\charactername{Joey:} Ross, let me ask you a question. She got the furniture, the stereo, the good TV- what did you get?
	\switchcolumn
	\charactername{乔伊：}罗斯，我问你一个问题。她分走了家具、音响和好电视，你分到了什么？
	\switchcolumn*
	\charactername{Ross:} You guys.
	\switchcolumn
	\charactername{罗斯：}你们。
	\switchcolumn*
	\charactername{Chandler:} Oh, God.
	\switchcolumn
	\charactername{钱德勒：}天啊。
	\switchcolumn*
	\charactername{Joey:} You got screwed.
	\switchcolumn
	\charactername{乔伊：}你昏头了吧。
	\switchcolumn*
	\charactername{Chandler:} Oh my God!
	\switchcolumn
	\charactername{钱德勒：}哦天啊！
	\switchcolumn*
	\sense{Scene: A Restaurant, Monica and Paul are eating.}
	\switchcolumn
	\sense{场景：餐厅，莫妮卡和保罗正在吃饭。}
	\switchcolumn*
	\charactername{Monica:} Oh my God!
	\switchcolumn
	\charactername{莫妮卡：}哦天啊！
	\switchcolumn*
	\charactername{Paul:} I know, I know, I'm such an idiot. I guess I should have caught on when she started going to the dentist four and five times a week. I mean, how clean can teeth get?
	\switchcolumn
	\charactername{保罗：}我知道，我是个大白痴。她每周看四五次牙医时我就该明白，牙齿能有多干净？
	\switchcolumn*
	\charactername{Monica:} My brother's going through that right now, he's such a mess. How did you get through it?
	\switchcolumn
	\charactername{莫妮卡：}我哥正承受着这种痛苦，一副失魂落魄的样子。你是怎么熬过来的？
	\switchcolumn*
	\charactername{Paul:} Well, you might try accidentally breaking something valuable of hers, say her-
	\switchcolumn
	\charactername{保罗：}你可以不小心砸烂她贵重的东西，比如她的——
	\switchcolumn*
	\charactername{Monica:} -leg?
	\switchcolumn
	\charactername{莫妮卡：}——腿？
	\switchcolumn*
	\charactername{Paul:} \ennotmain{laughing} That's one way! Me, I- I went for the watch.
	\switchcolumn
	\charactername{保罗：}\notmain{笑着}这样也不赖！我……我砸烂了她的表。
	\switchcolumn*
	\charactername{Monica:} You actually broke her watch? Wow! The worst thing I ever did was, I-I shredded by boyfriend's favorite bath towel.
	\switchcolumn
	\charactername{莫妮卡：}你真的砸烂过她的表？哇！我做过的最坏的事情是，我撕碎了男朋友最喜欢的浴巾。
	\switchcolumn*
	\charactername{Paul:} Ooh, steer clear of you.
	\switchcolumn
	\charactername{保罗：}嗯，机智脱身。
	\switchcolumn*
	\charactername{Monica:} That's right.
	\switchcolumn
	\charactername{莫妮卡：}对啊。
	\switchcolumn*
	\sense{Scene: Monica's Apartment, Rachel is talking on the phone and pacing.}
	\switchcolumn
	\sense{场景：莫妮卡的公寓，瑞秋边踱步边打电话。}
	\switchcolumn*
	\charactername{Rachel:} Barry, I'm sorry... I am so sorry... I know you probably think that this is all about what I said the other day about you making love with your socks on, but it isn't... it isn't, it's about me, and I ju- \ennotmain{She stops talking and dials the phone.} Hi, machine cut me off again... anyway...look, look, I know that some girl is going to be incredibly lucky to become Mrs. Barry Finkel, but it isn't me, it's not me. And not that I have any idea who me is right now, but you just have to give me a chance too... \ennotmain{The machine cuts her off again and she redials.}
	\switchcolumn
	\charactername{瑞秋：}巴瑞，真是对不起……你一定认为此事与我那次说的话有关，关于你做爱时穿着袜子，其实不是，问题出在我身上，我……\notmain{电话被挂断，重新拨号}嗨，答录机又把我挂断了。不管怎样……瞧瞧，我知道某个女孩会不可思议地成为巴瑞·芬克尔太太，但那不是我，不是我。而我现在连我自己是谁都不知道，但你还应该给我一个机会向你……\notmain{又被挂断，再次拨号}
	\switchcolumn*
	\sense{Scene: Ross's Apartment; Ross is pacing while Joey and Chandler are working on some more furniture.}
	\switchcolumn
	\sense{场景：罗斯的公寓；罗斯在踱步，乔伊和钱德勒在组装更多家具。}
	\switchcolumn*
	\charactername{Ross:} I'm divorced! I'm only 26 and I'm divorced!
	\switchcolumn
	\charactername{罗斯：}我离婚啦！我才26岁就离婚啦！
	\switchcolumn*
	\charactername{Joey:} Shut up!
	\switchcolumn
	\charactername{乔伊：}闭嘴！
	\switchcolumn*
	\charactername{Chandler:} You must stop! \ennotmain{Chandler hits what he is working on with a hammer and it collapses.}
	\switchcolumn
	\charactername{钱德勒：}你还是停下来吧！\notmain{钱德勒用锤子砸向正在组装的东西，它散架了。}
	\switchcolumn*
	\charactername{Ross:} That only took me an hour.
	\switchcolumn
	\charactername{罗斯：}我才花了一小时组装的。
	\switchcolumn*
	\charactername{Chandler:} Look, Ross, you gotta understand, between us we haven't had a relationship that has lasted longer than a Mento. You, however have had the love of a woman for four years. Four years of closeness and sharing at the end of which she ripped your heart out, and that is why we don't do it! I don't think that was my point!
	\switchcolumn
	\charactername{钱德勒：}看啊，罗斯，你应该理解，我们认识这么久，却没有一段感情能维持超过一根曼妥思糖的时间。而你，却拥有过一个女人四年的爱。四年的亲密与分享，最后她却伤透了你的心，这就是我们为什么不谈恋爱！我好像不是这个意思！
	\switchcolumn*
	\charactername{Ross:} You know what the scariest part is? What if there's only one woman for everybody, y'know? I mean what if you get one woman- and that's it? Unfortunately in my case, there was only one woman- for her...
	\switchcolumn
	\charactername{罗斯：}你知道最可怕的是什么？万一每个人一生只有一个真爱怎么办？我的意思是如果你遇到了那个唯一的女人——然后就没有然后了？不幸的是，我生命中的那个唯一，却把她的唯一给了别人……
	\switchcolumn*
	\charactername{Joey:} What are you talking about? 'One woman'? That's like saying there's only one flavor of ice cream for you. Lemme tell you something, Ross. There's lots of flavors out there. There's Rocky Road, and Cookie Dough, and Bing! Cherry Vanilla. You could get 'em with Jimmies, or nuts, or whipped cream! This is the best thing that ever happened to you! You got married, you were, like, what, eight? Welcome back to the world! Grab a spoon!
	\switchcolumn
	\charactername{乔伊：}你在说什么？一个女人？那就像在说你只能吃一种口味的冰淇淋。罗斯，告诉你吧，冰淇淋的口味有千百种。有摇滚之路\notmain{巧克力碎坚果口味}、曲奇面团口味、冰沁樱桃香草口味！你可以加上糖针、坚果或者奶油！这是你一生中最美好的事！你多大就结婚了，八岁？欢迎回到自由世界！抓住机会\notmain{拿起勺子}！
	\switchcolumn*
	\charactername{Ross:} I honestly don't know if I'm hungry or horny.
	\switchcolumn
	\charactername{罗斯：}我真的不知道自己是饥渴还是欲火焚身？
	\switchcolumn*
	\charactername{Chandler:} Stay out of my freezer!
	\switchcolumn
	\charactername{钱德勒：}那么就别碰我家的冰箱！
	\switchcolumn*
	\sense{Scene: A Restaurant, Monica and Paul are still eating.}
	\switchcolumn
	\sense{场景：餐厅，莫妮卡和保罗还在吃饭。}
	\switchcolumn*
	\charactername{Paul:} Ever since she walked out on me, I, uh...
	\switchcolumn
	\charactername{保罗：}自从她甩掉我之后，我，呃……
	\switchcolumn*
	\charactername{Monica:} What?..... What, you wanna spell it out with noodles?
	\switchcolumn
	\charactername{莫妮卡：}什么？……什么，你打算边嚼面条边讲？
	\switchcolumn*
	\charactername{Paul:} No, it's, it's more of a fifth date kinda revelation.
	\switchcolumn
	\charactername{保罗：}不，这就像是“第五次约会真情告白”。
	\switchcolumn*
	\charactername{Monica:} Oh, so there is gonna be a fifth date?
	\switchcolumn
	\charactername{莫妮卡：}有第五次约会？
	\switchcolumn*
	\charactername{Paul:} Isn't there?
	\switchcolumn
	\charactername{保罗：}不需要吗？
	\switchcolumn*
	\charactername{Monica:} Yeah... yeah, I think there is. -What were you gonna say?
	\switchcolumn
	\charactername{莫妮卡：}需要，我想需要的。你刚才想说什么？
	\switchcolumn*
	\charactername{Paul:} Well, ever-ev-... ever since she left me, um, I haven't been able to, uh, perform. \ennotmain{Monica takes a sip of her drink.} ...Sexually.
	\switchcolumn
	\charactername{保罗：}这个……呃……自从她离开后，我就一直无法……没做过……性方面的事。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{spitting out her drink in shock} Oh God, oh God, I am sorry... I am so sorry...
	\switchcolumn
	\charactername{莫妮卡：}\notmain{震惊地喷出口中的饮料}天啊，天啊，对不起，对不起。
	\switchcolumn*
	\charactername{Paul:} It's okay...
	\switchcolumn
	\charactername{保罗：}没关系……
	\switchcolumn*
	\charactername{Monica:} I know being spit on is probably not what you need right now. Um... how long?
	\switchcolumn
	\charactername{莫妮卡：}你现在需要的应该不是让人吐口水吧。嗯……多久了？
	\switchcolumn*
	\charactername{Paul:} Two years.
	\switchcolumn
	\charactername{保罗：}两年了。
	\switchcolumn*
	\charactername{Monica:} Wow! I'm-I'm-I'm glad you smashed her watch!
	\switchcolumn
	\charactername{莫妮卡：}哇！真高兴你砸烂了她的表！
	\switchcolumn*
	\charactername{Paul:} So you still think you, um... might want that fifth date?
	\switchcolumn
	\charactername{保罗：}你还想要第五次约会吗？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{pause}...Yeah. Yeah, I do.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{停顿}……当然想。
	\switchcolumn*
	\sense{Scene: Monica's Apartment, Rachel is watching Joanne Loves Chaci.}
	\switchcolumn
	\sense{场景：莫妮卡的公寓，瑞秋在看《乔安妮爱恰奇》。}
	\switchcolumn*
	\charactername{Priest on TV:} We are gathered here today to join Joanne Louise Cunningham and Charles, Chachi-Chachi-Chachi, Arcola in the bound of holy matrimony.
	\switchcolumn
	\charactername{电视里的牧师：}我们今天来这里参加乔安妮·路易丝·坎宁安和查尔斯·恰棋-恰棋-恰棋·阿可勒的神圣婚礼。
	\switchcolumn*
	\charactername{Rachel:} Oh...see... but Joanne loved Chaci! That's the difference!
	\switchcolumn
	\charactername{瑞秋：}哦……看……乔安妮爱的是恰棋。差别就在这儿！
	\switchcolumn*
	\sense{Scene: Ross's Apartment, they're all sitting around and talking.}
	\switchcolumn
	\sense{场景：罗斯的公寓，众人围坐聊天。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{scornful} Grab a spoon. Do you know how long it's been since I've grabbed a spoon? Do the words 'Billy, don't be a hero' mean anything to you?
	\switchcolumn
	\charactername{罗斯：}\notmain{不屑地}抓住勺子。知道我等着“抓住这把勺子”等了多久吗？你对“比利，别逞英雄”这句话有感觉吗？
	\switchcolumn*
	\charactername{Joey:} Great story! But, I uh, I gotta go, I got a date with Andrea--Angela--Andrea... Oh man, \ennotmain{looks to Chandler}
	\switchcolumn
	\charactername{乔伊：}非常精彩的故事！但我要走了，我有个约会，和安德里亚……安吉拉……安德里亚……嗨，\notmain{看向钱德勒}
	\switchcolumn*
	\charactername{Chandler:} Angela's the screamer, Andrea has cats.
	\switchcolumn
	\charactername{钱德勒：}安吉拉喜欢尖叫，安德里亚养猫。
	\switchcolumn*
	\charactername{Joey:} Right. Thanks. It's June. I'm outta here. \ennotmain{Exits.}
	\switchcolumn
	\charactername{乔伊：}对。谢谢。六月份了。我走了。\notmain{离开。}
	\switchcolumn*
	\charactername{Ross:} Y'know, here's the thing. Even if I could get it together enough to- to ask a woman out,... who am I gonna ask? \ennotmain{He gazes out of the window.}
	\switchcolumn
	\charactername{罗斯：}是这样的。就算我鼓起勇气约女人出去，但我要约谁呀？\notmain{望向窗外。}
	\switchcolumn*
	\sense{Cut to Rachel staring out of her window.}
	\switchcolumn
	\sense{切换镜头到瑞秋望向窗外。}
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Monica's Apartment, Rachel is making coffee for Joey and Chandler.}
	\switchcolumn
	\sense{场景：莫妮卡的公寓，瑞秋在给乔伊和钱德勒泡咖啡。}
	\switchcolumn*
	\charactername{Rachel:} Isn't this amazing? I mean, I have never made coffee before in my entire life.
	\switchcolumn
	\charactername{瑞秋：}神奇吧？我这辈子从没泡过咖啡。
	\switchcolumn*
	\charactername{Chandler:} That is amazing.
	\switchcolumn
	\charactername{钱德勒：}真神奇。
	\switchcolumn*
	\charactername{Joey:} Congratulations.
	\switchcolumn
	\charactername{乔伊：}恭喜了。
	\switchcolumn*
	\charactername{Rachel:} Y'know, I figure if I can make coffee, there isn't anything I can't do.
	\switchcolumn
	\charactername{瑞秋：}你看，我觉得只要我会泡咖啡，就没有什么不行。
	\switchcolumn*
	\charactername{Chandler:} If can invade Poland, there isn't anything I can't do.
	\switchcolumn
	\charactername{钱德勒：}如果能侵入波兰，就能征服一切。
	\switchcolumn*
	\charactername{Joey:} Listen, while you're on a roll, if you feel like you gotta make like a Western omelet or something... \ennotmain{Joey and Chandler taste the coffee, grimace, and pour it into a plant pot.} Although actually I'm really not that hungry...
	\switchcolumn
	\charactername{乔伊：}如果你兴致大发想做蛋饼，老实说我不太饿……\notmain{乔伊和钱德勒尝了尝咖啡，做了个鬼脸，把咖啡倒进花盆。}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{entering, to herself} Oh good, Lenny and Squigy are here.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{走进来，自言自语}好啊，伦尼和斯奎吉来啦。\notmain{注：Lenny和Squigy是经典喜剧《拉维恩和雪莉》中的角色，此处钱德勒和乔伊的行为让莫妮卡联想到这两个角色}
	\switchcolumn*
	\charactername{All:} Morning. Good morning.
	\switchcolumn
	\charactername{众人：}早安。早安。
	\switchcolumn*
	\charactername{Paul:} \ennotmain{entering from Monica's room} Morning.
	\switchcolumn
	\charactername{保罗：}\notmain{从莫妮卡的房间走出}早安。
	\switchcolumn*
	\charactername{Joey:} Morning, Paul.
	\switchcolumn
	\charactername{乔伊：}早安，保罗。
	\switchcolumn*
	\charactername{Rachel:} Hello, Paul.
	\switchcolumn
	\charactername{瑞秋：}你好，保罗。
	\switchcolumn*
	\charactername{Chandler:} Hi, Paul, is it?
	\switchcolumn
	\charactername{钱德勒：}嗨，保罗，是吗？
	\switchcolumn*
	\ennotmain{Monica and Paul walk to the door and talk in a low voice so the others can't hear. The others move Monica's table closer to the door so that they can.}
	\switchcolumn
	\notmain{莫妮卡和保罗走到门边低声交谈，不让其他人听见。众人把莫妮卡的桌子挪到门边以便偷听。}
	\switchcolumn*
	\charactername{Paul:} Thank you! Thank you so much!
	\switchcolumn
	\charactername{保罗：}谢谢你！太谢谢你了！
	\switchcolumn*
	\charactername{Monica:} Stop!
	\switchcolumn
	\charactername{莫妮卡：}好了！
	\switchcolumn*
	\charactername{Paul:} No, I'm telling you last night was like umm, all my birthdays, both graduations, plus the barn raising scene in Witness.
	\switchcolumn
	\charactername{保罗：}不行，我要告诉你昨晚就像我所有的生日、毕业典礼和《证人》里的谷仓建造场景加在一起一样美好。
	\switchcolumn*
	\charactername{Monica:} We'll talk later.
	\switchcolumn
	\charactername{莫妮卡：}晚点再说。
	\switchcolumn*
	\charactername{Paul:} Yeah. \ennotmain{They kiss} Thank you. \ennotmain{Exits}
	\switchcolumn
	\charactername{保罗：}好。\notmain{亲吻莫妮卡}谢谢。\notmain{离开}
	\switchcolumn*
	\charactername{Joey:} That wasn't a real date?! What the hell do you do on a real date?
	\switchcolumn
	\charactername{乔伊：}那还不叫约会？！那你真正的约会到底干些什么？
	\switchcolumn*
	\charactername{Monica:} Shut up, and put my table back.
	\switchcolumn
	\charactername{莫妮卡：}闭嘴，把桌子抬回去。
	\switchcolumn*
	\charactername{All:} Okayyy! \ennotmain{They do so.}
	\switchcolumn
	\charactername{众人：}好吧！\notmain{照做。}
	\switchcolumn*
	\charactername{Chandler:} All right, kids, I gotta get to work. If I don't input those numbers,... it doesn't make much of a difference...
	\switchcolumn
	\charactername{钱德勒：}孩子们，我要上班去了。如果我不输入那些数字……也没什么关系……
	\switchcolumn*
	\charactername{Rachel:} So, like, you guys all have jobs?
	\switchcolumn
	\charactername{瑞秋：}你们大伙儿都有工作？
	\switchcolumn*
	\charactername{Monica:} Yeah, we all have jobs. See, that's how we buy stuff.
	\switchcolumn
	\charactername{莫妮卡：}对，我们都有工作。这样才有钱买东西。
	\switchcolumn*
	\charactername{Joey:} Yeah, I'm an actor.
	\switchcolumn
	\charactername{乔伊：}对，我是个演员。
	\switchcolumn*
	\charactername{Rachel:} Wow! Would I have seen you in anything?
	\switchcolumn
	\charactername{瑞秋：}我见过你演的作品吗？
	\switchcolumn*
	\charactername{Joey:} I doubt it. Mostly regional work.
	\switchcolumn
	\charactername{乔伊：}大概没见过吧。我大部份都是在地区性的节目中演出。
	\switchcolumn*
	\charactername{Monica:} Oh wait, wait, unless you happened to catch the Reruns' production of Pinocchio, at the little theater in the park.
	\switchcolumn
	\charactername{莫妮卡：}等等，除非你看过“重播剧团”在公园小剧场演出的《木偶奇遇记》。
	\switchcolumn*
	\charactername{Joey:} Look, it was a job all right?
	\switchcolumn
	\charactername{乔伊：}这也算是工作吧？
	\switchcolumn*
	\charactername{Chandler:} 'Look, Gippetto, I'm a real live boy.'
	\switchcolumn
	\charactername{钱德勒：}“瞧，盖佩多，我是个活生生的小男孩。”
	\switchcolumn*
	\charactername{Joey:} I will not take this abuse. \ennotmain{Walks to the door and opens it to leave.}
	\switchcolumn
	\charactername{乔伊：}我不会理睬这种羞辱。\notmain{走向门口开门准备离开。}
	\switchcolumn*
	\charactername{Chandler:} You're right, I'm sorry. \ennotmain{Burst into song and dances out of the door.} "Once I was a wooden boy, a little wooden boy..."
	\switchcolumn
	\charactername{钱德勒：}你说得对，抱歉。\notmain{突然唱歌跳舞走出门口}“我曾是个小木偶，一个小小的木偶……”
	\switchcolumn*
	\charactername{Joey:} You should both know, that he's a dead man. Oh, Chandler? \ennotmain{Starts after Chandler.}
	\switchcolumn
	\charactername{乔伊：}告诉你们，他死定了。哦，钱德勒？\notmain{追了出去。}
	\switchcolumn*
	\charactername{Monica:} So how you doing today? Did you sleep okay? Talk to Barry? I can't stop smiling.
	\switchcolumn
	\charactername{莫妮卡：}今天感觉如何？睡得还好吧？和巴瑞通过电话吗？我无法停止笑。
	\switchcolumn*
	\charactername{Rachel:} I can see that. You look like you slept with a hanger in your mouth.
	\switchcolumn
	\charactername{瑞秋：}我看得出来。你这样子像是昨晚口中含着衣架睡觉。
	\switchcolumn*
	\charactername{Monica:} I know, he's just so, so... Do you remember you and Tony DeMarco?
	\switchcolumn
	\charactername{莫妮卡：}我知道，他是那么……还记得你和东尼·戴马克吗？
	\switchcolumn*
	\charactername{Rachel:} Oh, yeah.
	\switchcolumn
	\charactername{瑞秋：}记得。
	\switchcolumn*
	\charactername{Monica:} Well, it's like that. With feelings.
	\switchcolumn
	\charactername{莫妮卡：}就像那样。有那种心动的感觉。
	\switchcolumn*
	\charactername{Rachel:} Oh wow. Are you in trouble.
	\switchcolumn
	\charactername{瑞秋：}你惹上麻烦了。
	\switchcolumn*
	\charactername{Monica:} Big time!
	\switchcolumn
	\charactername{莫妮卡：}大麻烦！
	\switchcolumn*
	\charactername{Rachel:} Want a wedding dress? Hardly used.
	\switchcolumn
	\charactername{瑞秋：}需要婚纱吗？几乎没用过的。
	\switchcolumn*
	\charactername{Monica:} I think we are getting a little ahead of selves here. Okay. Okay. I am just going to get up, go to work and not think about him all day. Or else I'm just gonna get up and go to work.
	\switchcolumn
	\charactername{莫妮卡：}我想我们有点不知所以了。好吧。我要清醒，去工作，整天都不想他，或者只是清醒然后去工作。
	\switchcolumn*
	\charactername{Rachel:} Oh, look, wish me luck!
	\switchcolumn
	\charactername{瑞秋：}祝我幸运！
	\switchcolumn*
	\charactername{Monica:} What for?
	\switchcolumn
	\charactername{莫妮卡：}为什么？
	\switchcolumn*
	\charactername{Rachel:} I'm gonna go get one of those \ennotmain{Thinks} job things.
	\switchcolumn
	\charactername{瑞秋：}我要去找工作。
	\switchcolumn*
	\ennotmain{Monica exits.}
	\switchcolumn
	\notmain{莫妮卡离开。}
	\switchcolumn*
	\sense{Scene: Iridium, Monica is working as Frannie enters.}
	\switchcolumn
	\sense{场景：伊里迪姆餐厅，莫妮卡正在工作，法兰妮走进来。}
	\switchcolumn*
	\charactername{Frannie:} Hey, Monica!
	\switchcolumn
	\charactername{法兰妮：}嗨，莫妮卡！
	\switchcolumn*
	\charactername{Monica:} Hey Frannie, welcome back! How was Florida?
	\switchcolumn
	\charactername{莫妮卡：}法兰妮，欢迎回来！佛罗里达之旅如何？
	\switchcolumn*
	\charactername{Frannie:} You had sex, didn't you?
	\switchcolumn
	\charactername{法兰妮：}你们上床了，对不？
	\switchcolumn*
	\charactername{Monica:} How do you do that?
	\switchcolumn
	\charactername{莫妮卡：}你怎么看出来的？
	\switchcolumn*
	\charactername{Frannie:} Oh, I hate you, I'm pushing my Aunt Roz through Parrot Jungle and you're having sex! So? Who?
	\switchcolumn
	\charactername{法兰妮：}哦，我恨你，我推着我的洛兹阿姨经过帕罗丛林，你却在做爱！和谁呀？
	\switchcolumn*
	\charactername{Monica:} You know Paul?
	\switchcolumn
	\charactername{莫妮卡：}认识保罗吗？
	\switchcolumn*
	\charactername{Frannie:} Paul the Wine Guy? Oh yeah, I know Paul.
	\switchcolumn
	\charactername{法兰妮：}保罗，那个调酒的？对，我认识保罗。
	\switchcolumn*
	\charactername{Monica:} You mean you know Paul like I know Paul?
	\switchcolumn
	\charactername{莫妮卡：}你认识保罗像我认识他一样？
	\switchcolumn*
	\charactername{Frannie:} Are you kidding? I take credit for Paul. Y'know before me, there was no snap in his turtle for two years.
	\switchcolumn
	\charactername{法兰妮：}爱说笑，他还得谢我呢。遇到我之前他已有两年无法行房。
	\switchcolumn*
	\sense{Scene: Central Perk, everyone but Rachel is there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，除了瑞秋其他人都在。}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{sitting on the arm of the couch} Of course it was a line!
	\switchcolumn
	\charactername{乔伊：}\notmain{坐在沙发扶手上}显然他是骗你的！
	\switchcolumn*
	\charactername{Monica:} Why?! Why? Why, why would anybody do something like that?
	\switchcolumn
	\charactername{莫妮卡：}为什么？为什么会有人那样做？
	\switchcolumn*
	\charactername{Ross:} I assume we're looking for an answer more sophisticated than 'to get you into bed'.
	\switchcolumn
	\charactername{罗斯：}我想答案比“设法骗你上床”更复杂。
	\switchcolumn*
	\charactername{Monica:} I hate men! I hate men!
	\switchcolumn
	\charactername{莫妮卡：}我恨男人！我恨男人！
	\switchcolumn*
	\charactername{Phoebe:} Oh no, don't hate, you don't want to put that out into the universe.
	\switchcolumn
	\charactername{菲比：}不，别恨，你也不想把他们丢出宇宙吧。
	\switchcolumn*
	\charactername{Monica:} Is it me? Is it like I have some sort of beacon that only dogs and men with severe emotional problems can hear?
	\switchcolumn
	\charactername{莫妮卡：}问题出在我身上？难道我有特殊气味，只有狗和感情有严重问题的男人才闻得到？
	\switchcolumn*
	\charactername{Phoebe:} All right, c'mere, gimme your feet. \ennotmain{She starts massaging them.}
	\switchcolumn
	\charactername{菲比：}过来，脚给我。\notmain{开始给莫妮卡按摩脚。}
	\switchcolumn*
	\charactername{Monica:} I just thought he was nice, y'know?
	\switchcolumn
	\charactername{莫妮卡：}我以为他是个好男人。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{bursts out laughing again} I can't believe you didn't know it was a line!
	\switchcolumn
	\charactername{乔伊：}\notmain{再次大笑}我无法相信你不懂这是骗局。
	\switchcolumn*
	\ennotmain{Monica pushes him off of the sofa as Rachel enters with a shopping bag.}
	\switchcolumn
	\notmain{莫妮卡把乔伊推下沙发，瑞秋提着购物袋走进来。}
	\switchcolumn*
	\charactername{Rachel:} Guess what?
	\switchcolumn
	\charactername{瑞秋：}猜猜看？
	\switchcolumn*
	\charactername{Ross:} You got a job?
	\switchcolumn
	\charactername{罗斯：}你找到工作了？
	\switchcolumn*
	\charactername{Rachel:} Are you kidding? I'm trained for nothing! I was laughed out of twelve interviews today.
	\switchcolumn
	\charactername{瑞秋：}开玩笑？我什么技能都没有！今天的十二个面试全泡汤了。
	\switchcolumn*
	\charactername{Chandler:} And yet you're surprisingly upbeat.
	\switchcolumn
	\charactername{钱德勒：}不过你却异常兴奋。
	\switchcolumn*
	\charactername{Rachel:} You would be too if you found John and David boots on sale, fifty percent off!
	\switchcolumn
	\charactername{瑞秋：}换成是你，如果你遇见约翰和大卫的皮靴打五折，你也会一样。
	\switchcolumn*
	\charactername{Chandler:} Oh, how well you know me...
	\switchcolumn
	\charactername{钱德勒：}你真是太了解我了。
	\switchcolumn*
	\charactername{Rachel:} They're my new 'I don't need a job, I don't need my parents, I've got great boots' boots!
	\switchcolumn
	\charactername{瑞秋：}这是我的新皮靴，我不需要工作，不需要父母，因为我有新皮靴！
	\switchcolumn*
	\charactername{Monica:} How'd you pay for them?
	\switchcolumn
	\charactername{莫妮卡：}你怎么付钱的？
	\switchcolumn*
	\charactername{Rachel:} Uh, credit card.
	\switchcolumn
	\charactername{瑞秋：}信用卡啊。
	\switchcolumn*
	\charactername{Monica:} And who pays for that?
	\switchcolumn
	\charactername{莫妮卡：}卡费谁付？
	\switchcolumn*
	\charactername{Rachel:} Um... my... father.
	\switchcolumn
	\charactername{瑞秋：}我爸。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, everyone is sitting around the kitchen table. Rachel's credit cards are spread out on the table along with a pair of scissors.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，众人围坐在厨房餐桌旁。瑞秋的信用卡和一把剪刀摊在桌上。}
	\switchcolumn*
	\charactername{Rachel:} Oh God, come on you guys, is this really necessary? I mean, I can stop charging anytime I want.
	\switchcolumn
	\charactername{瑞秋：}天啊，好啦，有必要吗？我是说，我可以随时忍住挥霍的。
	\switchcolumn*
	\charactername{Monica:} C'mon, you can't live off your parents your whole life.
	\switchcolumn
	\charactername{莫妮卡：}成熟点，你不能靠你爸一辈子。
	\switchcolumn*
	\charactername{Rachel:} I know that. That's why I was getting married.
	\switchcolumn
	\charactername{瑞秋：}我知道，所以我选择结婚。
	\switchcolumn*
	\charactername{Phoebe:} Give her a break, it's hard being on your own for the first time.
	\switchcolumn
	\charactername{菲比：}饶了她吧，第一次独立并不轻松。
	\switchcolumn*
	\charactername{Rachel:} Thank you.
	\switchcolumn
	\charactername{瑞秋：}谢谢。
	\switchcolumn*
	\charactername{Phoebe:} You're welcome. I remember when I first came to this city. I was fourteen. My mom had just killed herself and my step-dad was back in prison, and I got here, and I didn't know anybody. And I ended up living with this albino guy who was, like, cleaning windshields outside port authority, and then he killed himself, and then I found aromatherapy. So believe me, I know exactly how you feel.
	\switchcolumn
	\charactername{菲比：}不客气。我记得我第一次来到纽约时的情况，当时我十四岁，我妈刚自杀，我继父再度入狱，我在这儿人生地不熟。最后我和患白化症的男人同居，他为港务局的人清洗车窗，后来他自杀了，然后我找到芳香按摩治疗的工作。所以请相信我，你的心情我能体会。
	\switchcolumn*
	\ennotmain{Pause}
	\switchcolumn
	\notmain{停顿}
	\switchcolumn*
	\charactername{Ross:} The word you're looking for is 'Anyway'...
	\switchcolumn
	\charactername{罗斯：}你需要的是“无论如何”……
	\switchcolumn*
	\charactername{Monica:} All right, you ready?
	\switchcolumn
	\charactername{莫妮卡：}好的，准备好了吗？
	\switchcolumn*
	\charactername{Rachel:} No. No, no, I'm not ready! How can I be ready? "Hey, Rach! You ready to jump out the airplane without your parachute?" Come on, I can't do this!
	\switchcolumn
	\charactername{瑞秋：}不。不，不，我没准备好！我怎么会准备好呢？“嗨，瑞秋！你准备好不用降落伞跳出飞机吗？”不行，我不行！
	\switchcolumn*
	\charactername{Monica:} You can, I know you can!
	\switchcolumn
	\charactername{莫妮卡：}你能行的，我知道你能行！
	\switchcolumn*
	\charactername{Rachel:} I don't think so.
	\switchcolumn
	\charactername{瑞秋：}我不觉得。
	\switchcolumn*
	\charactername{Ross:} Come on, you made coffee! You can do anything! \ennotmain{Chandler slowly tries to hide the now dead plant from that morning when he and Joey poured their coffee into it.}
	\switchcolumn
	\charactername{罗斯：}来吧，你会泡咖啡！你就什么都可以！\notmain{钱德勒慢慢把早上被他和乔伊倒了咖啡而枯死的植物藏起来。}
	\switchcolumn*
	\charactername{Ross:} C'mon, cut. Cut, cut, cut,...
	\switchcolumn
	\charactername{罗斯：}来，剪，剪，剪，剪……
	\switchcolumn*
	\charactername{All:} Cut, cut, cut, cut, cut, cut, cut... \ennotmain{She cuts one of them and they cheer.}
	\switchcolumn
	\charactername{众人：}剪，剪，剪，剪，剪，剪，剪……\notmain{瑞秋剪了一张卡，众人欢呼。}
	\switchcolumn*
	\charactername{Rachel:} Y'know what? I think we can just leave it at that. It's kinda like a symbolic gesture...
	\switchcolumn
	\charactername{瑞秋：}你们知道吗？我认为我们可以把它们留在那里。只做个象征性的姿势就可以了。
	\switchcolumn*
	\charactername{Monica:} Rachel! That was a library card!
	\switchcolumn
	\charactername{莫妮卡：}瑞秋！那是借书卡！
	\switchcolumn*
	\charactername{All:} Cut, cut, cut, cut, cut, cut, cut..
	\switchcolumn
	\charactername{众人：}剪，剪，剪，剪，剪，剪，剪……
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{as Rachel is cutting up her cards} Y'know, if you listen closely, you can hear a thousand retailers scream.
	\switchcolumn
	\charactername{钱德勒：}\notmain{瑞秋剪卡时}知道吗，如果你们仔细听，你们会听到上千的商家在尖叫。
	\switchcolumn*
	\ennotmain{She finishes cutting them up and they all cheer.}
	\switchcolumn
	\notmain{瑞秋剪完所有卡，众人欢呼。}
	\switchcolumn*
	\charactername{Monica:} Welcome to the real world! It sucks. You're gonna love it!
	\switchcolumn
	\charactername{莫妮卡：}欢迎来到现实的世界。糟透了，但你会喜欢的！
	\switchcolumn*
	\sense{Time Lapse, Rachel and Ross are watching a TV channel finishes it's broadcast day by playing the national anthem.}
	\switchcolumn
	\sense{时间流逝，瑞秋和罗斯在看电视，频道播放国歌结束当天的播出。}
	\switchcolumn*
	\charactername{Monica:} Well, that's it \ennotmain{To Ross} You gonna crash on the couch?
	\switchcolumn
	\charactername{莫妮卡：}好，就到这。\notmain{对罗斯}你要睡在沙发上吗？
	\switchcolumn*
	\charactername{Ross:} No. No, I gotta go home sometime.
	\switchcolumn
	\charactername{罗斯：}不，我要回家了。
	\switchcolumn*
	\charactername{Monica:} You be okay?
	\switchcolumn
	\charactername{莫妮卡：}你没事吧？
	\switchcolumn*
	\charactername{Ross:} Yeah.
	\switchcolumn
	\charactername{罗斯：}还好。
	\switchcolumn*
	\charactername{Rachel:} Hey Mon, look what I just found on the floor. \ennotmain{Monica smiles.} What?
	\switchcolumn
	\charactername{瑞秋：}嗨，莫妮卡，看我在地板上发现什么？\notmain{莫妮卡微笑。}什么？
	\switchcolumn*
	\charactername{Monica:} That's Paul's watch. You just put it back where you found it. Oh boy. Alright. Goodnight, everybody.
	\switchcolumn
	\charactername{莫妮卡：}那是保罗的手表。放回原地就好了。好。晚安，各位。
	\switchcolumn*
	\charactername{Ross and Rachel:} Goodnight.
	\switchcolumn
	\charactername{罗斯和瑞秋：}晚安。
	\switchcolumn*
	\ennotmain{Monica stomps on Paul's watch and goes into her room.}
	\switchcolumn
	\notmain{莫妮卡用力踩了保罗的手表，走进自己的房间。}
	\switchcolumn*
	\charactername{Ross:} Mmm. \ennotmain{They both reach for the last cookie} Oh, no-
	\switchcolumn
	\charactername{罗斯：}嗯……\notmain{两人同时伸手去拿最后一块饼干}哦，不——
	\switchcolumn*
	\charactername{Rachel:} Sorry-
	\switchcolumn
	\charactername{瑞秋：}抱歉——
	\switchcolumn*
	\charactername{Ross:} No no no, go-
	\switchcolumn
	\charactername{罗斯：}不，不，不，你拿——
	\switchcolumn*
	\charactername{Rachel:} No, you have it, really, I don't want it-
	\switchcolumn
	\charactername{瑞秋：}不，你吃吧，真的，我不饿——
	\switchcolumn*
	\charactername{Ross:} Split it?
	\switchcolumn
	\charactername{罗斯：}分着吃？
	\switchcolumn*
	\charactername{Rachel:} Okay.
	\switchcolumn
	\charactername{瑞秋：}行。
	\switchcolumn*
	\charactername{Ross:} Okay. \ennotmain{They split it.} You know you probably didn't know this, but back in high school, I had a, um, major crush on you.
	\switchcolumn
	\charactername{罗斯：}好。\notmain{两人把饼干掰开。}你大概不知道，我高中时，特别迷你。
	\switchcolumn*
	\charactername{Rachel:} I knew.
	\switchcolumn
	\charactername{瑞秋：}我知道。
	\switchcolumn*
	\charactername{Ross:} You did! Oh.... I always figured you just thought I was Monica's geeky older brother.
	\switchcolumn
	\charactername{罗斯：}你知道？哦……我总想你认为我不过是莫妮卡的书呆子哥哥。
	\switchcolumn*
	\charactername{Rachel:} I did.
	\switchcolumn
	\charactername{瑞秋：}没错。
	\switchcolumn*
	\charactername{Ross:} Oh. Listen, do you think- and try not to let my intense vulnerability become any kind of a factor here- but do you think it would be okay if I asked you out? Sometime? Maybe?
	\switchcolumn
	\charactername{罗斯：}哦。你是否认为——如果抛开我这强烈的脆弱感——我能偶尔约你出去吗？有时？有可能？
	\switchcolumn*
	\charactername{Rachel:} Yeah, maybe...
	\switchcolumn
	\charactername{瑞秋：}好，或许吧……
	\switchcolumn*
	\charactername{Ross:} Okay... okay, maybe I will...
	\switchcolumn
	\charactername{罗斯：}或许我会的……
	\switchcolumn*
	\charactername{Rachel:} Goodnight.
	\switchcolumn
	\charactername{瑞秋：}晚安。
	\switchcolumn*
	\charactername{Ross:} Goodnight.
	\switchcolumn
	\charactername{罗斯：}晚安。
	\switchcolumn*
	\ennotmain{Rachel goes into her room and Monica enters the living room as Ross is leaving.}
	\switchcolumn
	\notmain{瑞秋走进房间，罗斯离开时莫妮卡走进客厅。}
	\switchcolumn*
	\charactername{Monica:} See ya.... Waitwait, what's with you?
	\switchcolumn
	\charactername{莫妮卡：}回头见……等等，你怎么了？
	\switchcolumn*
	\charactername{Ross:} I just grabbed a spoon. \ennotmain{Ross exits and Monica has no idea what that means.}
	\switchcolumn
	\charactername{罗斯：}我刚“抓住了勺子”！\notmain{罗斯离开，莫妮卡完全不明白他的意思。}
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, everyone is there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，众人都在。}
	\switchcolumn*
	\charactername{Joey:} I can't believe what I'm hearing here.
	\switchcolumn
	\charactername{乔伊：}我真不敢相信我的耳朵。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{sings} I can't believe what I'm hearing here...
	\switchcolumn
	\charactername{菲比：}\notmain{唱歌}我真不敢相信我的耳朵……
	\switchcolumn*
	\charactername{Monica:} What? I-I said you had a-
	\switchcolumn
	\charactername{莫妮卡：}什么？我说你有一个——
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{sings} What I said you had...
	\switchcolumn
	\charactername{菲比：}\notmain{唱歌}我说你有一个——
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Phoebe} Would you stop?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对菲比}你有完没完？
	\switchcolumn*
	\charactername{Phoebe:} Oh, was I doing it again?
	\switchcolumn
	\charactername{菲比：}我的老毛病又犯了？
	\switchcolumn*
	\charactername{All:} Yes!
	\switchcolumn
	\charactername{众人：}没错！
	\switchcolumn*
	\charactername{Monica:} I said that you had a nice butt, it's just not a great butt.
	\switchcolumn
	\charactername{莫妮卡：}我是说你有一个不错的屁股，但不是个了不起的屁股。
	\switchcolumn*
	\charactername{Joey:} Oh, you wouldn't know a great butt if it came up and bit ya.
	\switchcolumn
	\charactername{乔伊：}它又没跳起来咬过你，你怎么知道不是了不起的。
	\switchcolumn*
	\charactername{Ross:} There's an image.
	\switchcolumn
	\charactername{罗斯：}只是想象一下。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{walks up with a pot of coffee} Would anybody like more coffee?
	\switchcolumn
	\charactername{瑞秋：}\notmain{提着一壶咖啡走来}谁要喝咖啡？
	\switchcolumn*
	\charactername{Chandler:} Did you make it, or are you just serving it?
	\switchcolumn
	\charactername{钱德勒：}你煮的还是只是端过来而已？
	\switchcolumn*
	\charactername{Rachel:} I'm just serving it.
	\switchcolumn
	\charactername{瑞秋：}端来而已。
	\switchcolumn*
	\charactername{All:} Yeah. Yeah, I'll have a cup of coffee.
	\switchcolumn
	\charactername{众人：}好，好，给我来杯咖啡。
	\switchcolumn*
	\charactername{Chandler:} Kids, new dream... I'm in Las Vegas. \ennotmain{Rachel sits down to hear Chandler's dream.}
	\switchcolumn
	\charactername{钱德勒：}孩子们，新的梦境……我在拉斯维加斯。\notmain{瑞秋坐下听钱德勒讲梦。}
	\switchcolumn*
	\charactername{Customer:} \ennotmain{To Rachel} Ahh, miss? More coffee?
	\switchcolumn
	\charactername{顾客：}\notmain{对瑞秋}嗨，小姐？加点咖啡？
	\switchcolumn*
	\charactername{Rachel:} Ugh. \ennotmain{To another customer that's leaving.} Excuse me, could you give this to that guy over there? \ennotmain{Hands him the coffee pot.} Go ahead. \ennotmain{He does so.} Thank you. \ennotmain{To the gang.} Sorry. Okay, Las Vegas.
	\switchcolumn
	\charactername{瑞秋：}呃。\notmain{对正要离开的另一位顾客}劳驾，请递给那个人？\notmain{把咖啡壶递给对方}去吧。\notmain{对方照做}谢谢。\notmain{对众人}对不起。好，拉斯维加斯的梦。
	\switchcolumn*
	\charactername{Chandler:} Okay, so, I'm in Las Vegas... I'm Liza Minelli-
	\switchcolumn
	\charactername{钱德勒：}我在拉斯维加斯……我是丽莎·明妮莉——
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage