\begin{paracol}{2}
	\sense{Scene: Central Perk, everyone's there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，众人都在。}
	\switchcolumn*
	\charactername{Monica:} What you guys don't understand is, for us, kissing is as important as any part of it.
	\switchcolumn
	\charactername{莫妮卡：}你们男生不懂亲吻对女生的重要性。
	\switchcolumn*
	\charactername{Joey:} Yeah, right!.......Y'serious?
	\switchcolumn
	\charactername{乔伊：}没错，当真？
	\switchcolumn*
	\charactername{Phoebe:} Oh, yeah!
	\switchcolumn
	\charactername{菲比：}当真。
	\switchcolumn*
	\charactername{Rachel:} Everything you need to know is in that first kiss.
	\switchcolumn
	\charactername{瑞秋：}你想了解的一切全在初吻之中。
	\switchcolumn*
	\charactername{Monica:} Absolutely.
	\switchcolumn
	\charactername{莫妮卡：}没错。
	\switchcolumn*
	\charactername{Chandler:} Yeah, I think for us, kissing is pretty much like an opening act, y'know? I mean it's like the stand-up comedian you have to sit through before Pink Floyd comes out.
	\switchcolumn
	\charactername{钱德勒：}对我们而言亲吻就像是开场，就像佛洛依德飞船出场前，你得耐着性子先看完脱口秀。
	\switchcolumn*
	\charactername{Ross:} Yeah, and-and it's not that we don't like the comedian, it's that-that... that's not why we bought the ticket.
	\switchcolumn
	\charactername{罗斯：}对，我们并非讨厌脱口秀，但那不是我们买票的原因。
	\switchcolumn*
	\charactername{Chandler:} The problem is, though, after the concert's over, no matter how great the show was, you girls are always looking for the comedian again, y'know? I mean, we're in the car, we're fighting traffic... basically just trying to stay awake.
	\switchcolumn
	\charactername{钱德勒：}问题出在于演唱会结束后，不论表演有多精采，你们女生总还想再看脱口秀，我们在车上奋力杀出车阵，只是拼命让自己别睡着。
	\switchcolumn*
	\charactername{Rachel:} Yeah, well, word of advice: Bring back the comedian. Otherwise next time you're gonna find yourself sitting at home, listening to that album alone.
	\switchcolumn
	\charactername{瑞秋：}是哦？给你一个建议。叫脱口秀主持人再度上场，否则下次，你们只能坐家里听唱片。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{pause}....Are we still talking about sex?
	\switchcolumn
	\charactername{乔伊：}\notmain{停顿}我们还在谈论性吗？
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Museum of Prehistoric History, Ross and a co-worker \ennotmain{Marsha} are setting up an exhibit which includes some mannequins of cave people.}
	\switchcolumn
	\sense{场景：史前历史博物馆，罗斯和同事玛莎正在布置展品，其中包括一些穴居人模型。}
	\switchcolumn*
	\charactername{Ross:} No, it's good, it is good, it's just that- mm- doesn't she seem a little angry?
	\switchcolumn
	\charactername{罗斯：}不，这样很好，只是她看起来是不是有点生气？
	\switchcolumn*
	\charactername{Marsha:} Well, she has issues.
	\switchcolumn
	\charactername{玛莎：}她有麻烦事。
	\switchcolumn*
	\charactername{Ross:} Does she？
	\switchcolumn
	\charactername{罗斯：}她有吗？
	\switchcolumn*
	\charactername{Marsha:} He's out banging other women over the head with a club, while she sits at home trying to get the mastodon smell out of the carpet!
	\switchcolumn
	\charactername{玛莎：}他在外头乱搞女人，而她却待在家里，设法去除地毯上乳齿象的味道！
	\switchcolumn*
	\charactername{Ross:} Marsha, these are cave people. Okay？
	\switchcolumn
	\charactername{罗斯：}玛莎，他们是穴居人，好吗？
	\switchcolumn*
	\charactername{Marsha:} He's out banging other women over the head with a club, while she sits at home trying to get the mastodon smell out of the carpet!
	\switchcolumn
	\charactername{玛莎：}他在外头乱搞女人，而她却待在家里，设法去除地毯上乳齿象的味道！
	\switchcolumn*
	\charactername{Ross:} Marsha, these are cave people. Okay? They have issues like 'Gee, that glacier's getting kinda close.' See?
	\switchcolumn
	\charactername{罗斯：}玛莎，他们是穴居人，好吗？他们关心的问题是“天啊，冰河愈来愈接近了”，懂吗？
	\switchcolumn*
	\charactername{Marsha:} Speaking of issues, isn't that your ex-wife?
	\switchcolumn
	\charactername{玛莎：}谈到问题，那不是你前妻吗？
	\switchcolumn*
	\ennotmain{Carol, Ross's ex-wife, has entered behind them and is standing outside the exhibit.}
	\switchcolumn
	\notmain{罗斯的前妻卡萝走进来，站在展品外。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{trying to ignore her} No. No.
	\switchcolumn
	\charactername{罗斯：}\notmain{试图无视她}不是，不是。
	\switchcolumn*
	\charactername{Marsha:} Yes, it is. Carol! Hi!
	\switchcolumn
	\charactername{玛莎：}是的，她是。卡萝！嗨！
	\switchcolumn*
	\charactername{Ross:} Okay, okay, yes, it is. \ennotmain{waves} How about I'll, uh, catch up with you in the Ice Age.
	\switchcolumn
	\charactername{罗斯：}好吧，好吧，是她。\notmain{挥手}我到冰河期展区找你。
	\switchcolumn*
	\ennotmain{Marsha exits and Ross waves Carol into the exhibit.}
	\switchcolumn
	\notmain{玛莎离开，罗斯示意卡萝进入展品区。}
	\switchcolumn*
	\charactername{Ross:} Hi.
	\switchcolumn
	\charactername{罗斯：}嗨。
	\switchcolumn*
	\charactername{Carol:} So.
	\switchcolumn
	\charactername{卡萝：}嗯。
	\switchcolumn*
	\charactername{Ross:} You look great. I, uh... I hate that.
	\switchcolumn
	\charactername{罗斯：}你的气色好极了，我讨厌看到这样。
	\switchcolumn*
	\charactername{Carol:} Sorry. You look good too.
	\switchcolumn
	\charactername{卡萝：}抱歉，你气色也很好。
	\switchcolumn*
	\charactername{Ross:} Ah, well, in here, anyone who... stands erect... So what's new? Still, uh...
	\switchcolumn
	\charactername{罗斯：}啊，在这儿，任何直立的人……最近如何？还是……
	\switchcolumn*
	\charactername{Carol:} A lesbian?
	\switchcolumn
	\charactername{卡萝：}女同志？
	\switchcolumn*
	\charactername{Ross:} Well... you never know. How's, um.. how's the family?
	\switchcolumn
	\charactername{罗斯：}问问无妨嘛，家庭生活如何？
	\switchcolumn*
	\charactername{Carol:} Marty's still totally paranoid. Oh, and, uh-
	\switchcolumn
	\charactername{卡萝：}玛蒂的疑心病还是很重。哦，还有，呃——
	\switchcolumn*
	\charactername{Ross:} Why- why are you here, Carol?
	\switchcolumn
	\charactername{罗斯：}卡萝，你为什么来这儿？
	\switchcolumn*
	\charactername{Carol:} I'm pregnant.
	\switchcolumn
	\charactername{卡萝：}我怀孕了。
	\switchcolumn*
	\charactername{Ross:} Pregnant?!
	\switchcolumn
	\charactername{罗斯：}怀孕了？！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Chandler, Joey, Phoebe, and Monica are watching Three's Company.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，钱德勒、乔伊、菲比和莫妮卡正在看《三人行》。}
	\switchcolumn*
	\charactername{Chandler:} Oh, I think this is the episode of Three's Company where there's some kind of misunderstanding.
	\switchcolumn
	\charactername{钱德勒：}她似乎不急着离开，人和人之间，让人讨厌的就是有误会，他们之间有误会。
	\switchcolumn*
	\charactername{Phoebe:}...Then I've already seen this one! \ennotmain{Turns off the TV.}
	\switchcolumn
	\charactername{菲比：}我看过这一集！\notmain{关掉电视。}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{taking a drink from Joey} Are you through with that?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{从乔伊手中拿过饮料}你喝完没？
	\switchcolumn*
	\charactername{Joey:} Yeah, sorry, the swallowing slowed me down.
	\switchcolumn
	\charactername{乔伊：}抱歉，吞下去的时间太慢了。
	\switchcolumn*
	\charactername{Monica:} Whose little ball of paper is this?!
	\switchcolumn
	\charactername{莫妮卡：}这是谁的小纸团？！
	\switchcolumn*
	\charactername{Chandler:} Oh, uh, that would be mine. See, I wrote a note to myself, and then I realised I didn't need it, so I balled it up and... \ennotmain{sees that Monica is glaring at him} ...now I wish I was dead.
	\switchcolumn
	\charactername{钱德勒：}我的。我写给自己一张便条，后来觉得不需要，于是揉成纸团，现在我不想活了。
	\switchcolumn*
	\ennotmain{Monica starts to fluff a pillow.}
	\switchcolumn
	\notmain{莫妮卡开始拍松枕头。}
	\switchcolumn*
	\charactername{Phoebe:} She's already fluffed that pillow... Monica, you know, you've already fluffed that- \ennotmain{Monica glares at her.} -but, it's fine!
	\switchcolumn
	\charactername{菲比：}她已经拍松过那个枕头了……摩妮卡，你已经拍过那个枕头了——\notmain{莫妮卡瞪着她}——不过，没关系！
	\switchcolumn*
	\charactername{Monica:} Look, I'm sorry, guys, I just don't wanna give them any more ammunition than they already have.
	\switchcolumn
	\charactername{莫妮卡：}抱歉，各位，我只是不想让他们有藉题发挥的机会。
	\switchcolumn*
	\charactername{Chandler:} Yes, and we all know how cruel a parent can be about the flatness of a child's pillow.
	\switchcolumn
	\charactername{钱德勒：}没错，我们都知道父母对孩子的枕头要求有多苛刻。
	\switchcolumn*
	\charactername{Phoebe:} Monica- Hi! Um, Monica, you're scaring me. I mean, you're like, you're like all chaotic and twirly. And not-not in a good way.
	\switchcolumn
	\charactername{菲比：}摩妮卡——嗨！嗯，摩妮卡，你吓到我了。你慌慌张张的，而且不是那种好的慌张。
	\switchcolumn*
	\charactername{Joey:} Yeah, calm down. You don't see Ross getting all chaotic and twirly every time they come.
	\switchcolumn
	\charactername{乔伊：}冷静点，你没见过每次他们来，罗斯有慌张的样子。
	\switchcolumn*
	\charactername{Monica:} That's because as far as my parents are concerned, Ross can do no wrong. Y'see, he's the Prince. Apparently they had some big ceremony before I was born.
	\switchcolumn
	\charactername{莫妮卡：}因为在我爸妈心目中，罗斯不可能犯错。他是个王子，显然他们在我出生前有个大型仪式。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{looking out the window} Ew, ew, ew, ew ew ew ew ew!
	\switchcolumn
	\charactername{钱德勒：}\notmain{看向窗外}呃，呃，呃，呃呃呃呃呃！
	\switchcolumn*
	\charactername{Monica:} What?
	\switchcolumn
	\charactername{莫妮卡：}什么？
	\switchcolumn*
	\charactername{Chandler:} Ugly Naked Guy got a Thighmaster!
	\switchcolumn
	\charactername{钱德勒：}丑陋裸男有个“美腿器”！
	\switchcolumn*
	\charactername{All:} Eeaagh!
	\switchcolumn
	\charactername{众人：}呃啊！
	\switchcolumn*
	\ennotmain{Rachel enters from her room.}
	\switchcolumn
	\notmain{瑞秋从房间走进来。}
	\switchcolumn*
	\charactername{Rachel:} Has anybody seen my engagement ring?
	\switchcolumn
	\charactername{瑞秋：}有人看见我的订婚戒指吗？
	\switchcolumn*
	\charactername{Phoebe:} Yeah, it's beautiful.
	\switchcolumn
	\charactername{菲比：}有，很漂亮。
	\switchcolumn*
	\charactername{Rachel:} Oh God, oh God, oh God oh God oh God oh God.... \ennotmain{Starts to look under the couch cushions.}
	\switchcolumn
	\charactername{瑞秋：}天啊，天啊，天啊天啊天啊天啊……\notmain{开始在沙发垫下寻找。}
	\switchcolumn*
	\charactername{Phoebe:} No, look, don't touch that!
	\switchcolumn
	\charactername{菲比：}嘿，不要动它们！
	\switchcolumn*
	\charactername{Rachel:} Oh, like I wasn't dreading tomorrow enough, having to give it back to him... 'Hi Barry! Remember me? I'm the girl in the veil who stomped on your heart in front of your entire family!' Oh God and now I'm gonna have to return the ring, without the ring, which makes it so much harder...
	\switchcolumn
	\charactername{瑞秋：}明天就要还他戒指，我似乎还不够担心。嗨，巴瑞！记得我吗？我是那个穿白纱，在你全家面前伤透你心的女孩！天啊，如今我必须还他戒指，可戒指不见了，这让事情难上加难……
	\switchcolumn*
	\charactername{Monica:} Easy Rach, we'll find it. \ennotmain{To all} Won't we!
	\switchcolumn
	\charactername{莫妮卡：}别急，瑞秋，我们会找到的。\notmain{对众人}对不对！
	\switchcolumn*
	\charactername{Chandler and Joey:} Oh! Yeah!
	\switchcolumn
	\charactername{钱德勒和乔伊：}哦！对！
	\switchcolumn*
	\charactername{Joey:} Alright, when'd'ya have it on last?
	\switchcolumn
	\charactername{乔伊：}最后一次戴是在什么时候？
	\switchcolumn*
	\charactername{Phoebe:} Doy! Probably right before she lost it!
	\switchcolumn
	\charactername{菲比：}“孩仔”，大概是在遗失之前！
	\switchcolumn*
	\charactername{Chandler:} You don't get a lot of 'doy' these days...
	\switchcolumn
	\charactername{钱德勒：}这年头说“孩仔”的人不多了……
	\switchcolumn*
	\charactername{Rachel:} I know I had it this morning, and I know I had it when I was in the kitchen with...
	\switchcolumn
	\charactername{瑞秋：}我今天早上还戴着它，我在厨房戴着做……
	\switchcolumn*
	\charactername{Chandler:} ...Dinah?
	\switchcolumn
	\charactername{钱德勒：}……面条？
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{looks at the lasagne and realizes something} Ohhhhh, don't be mad...
	\switchcolumn
	\charactername{瑞秋：}\notmain{看着千层面，突然意识到}哦——，别生气……
	\switchcolumn*
	\charactername{Monica:} You didn't.
	\switchcolumn
	\charactername{莫妮卡：}你不会吧。
	\switchcolumn*
	\charactername{Rachel:} Oh, I am sorry...
	\switchcolumn
	\charactername{瑞秋：}对不起……
	\switchcolumn*
	\charactername{Monica:} I gave you one job! \ennotmain{Starts to examine the lasagne through the bottom of the glass pan.}
	\switchcolumn
	\charactername{莫妮卡：}我就让你做了这么一件事！\notmain{开始透过玻璃烤盘底部检查千层面。}
	\switchcolumn*
	\charactername{Rachel:} Oh, but look how straight those noodles are!
	\switchcolumn
	\charactername{瑞秋：}你看面条现在变得多直！
	\switchcolumn*
	\charactername{Chandler:} Now, Monica, you know that's not how you look for an engagement ring in a lasagne...
	\switchcolumn
	\charactername{钱德勒：}摩妮卡，在千层面中找订婚戒指不是那样找的……
	\switchcolumn*
	\charactername{Monica:} \ennotmain{puts down the lasagne} I just... can't do it.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{放下千层面}我办不到。
	\switchcolumn*
	\charactername{Chandler:} Boys? We're going in.
	\switchcolumn
	\charactername{钱德勒：}兄弟们？我们上。
	\switchcolumn*
	\ennotmain{Chandler, Joey, and Phoebe start to pick through the lasagne as there's a knock on the door which Monica answers.}
	\switchcolumn
	\notmain{钱德勒、乔伊和菲比开始翻找千层面，这时有人敲门，莫妮卡去开门。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{standing outside the door}.....Hi.
	\switchcolumn
	\charactername{罗斯：}\notmain{站在门外}……嗨。
	\switchcolumn*
	\charactername{Monica:} Wow. That is not a happy hi.
	\switchcolumn
	\charactername{莫妮卡：}哇，这可不是开心的问候。
	\switchcolumn*
	\charactername{Ross:} Carol's pregnant.
	\switchcolumn
	\charactername{罗斯：}卡萝怀孕了。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{while everyone else is stunned} Ooh! I found it!
	\switchcolumn
	\charactername{菲比：}\notmain{众人都愣住时}哦！我找到了！
	\switchcolumn*
	\charactername{Monica:} W-w-wh-... wha-... w-w-w-...
	\switchcolumn
	\charactername{莫妮卡：}什、什、什……什……什、什、什……
	\switchcolumn*
	\charactername{Ross:} Yeah. Do that for another two hours, you might be where I am right about now. \ennotmain{He enters.}
	\switchcolumn
	\charactername{罗斯：}对。你再这样持续两小时，就会变成我现在这样。\notmain{走进来。}
	\switchcolumn*
	\charactername{Chandler:} Kinda puts that whole pillow thing in perspective, huh, Mon?
	\switchcolumn
	\charactername{钱德勒：}如此一来，枕头的事就可以先放一放了，对吧，摩妮卡？
	\switchcolumn*
	\charactername{Rachel:} Well now, how-how do you fit into this whole thing?
	\switchcolumn
	\charactername{瑞秋：}那你现在要怎么融入这件事？
	\switchcolumn*
	\charactername{Ross:} Well, Carol says she and Susan want me to be involved, but if I'm not comfortable with it, I don't have to be involved basically it's entirely up to me.
	\switchcolumn
	\charactername{罗斯：}卡萝说她和苏珊想让我加入，但如果我对此感到不舒服，也可以不加入，基本上一切由我决定。
	\switchcolumn*
	\charactername{Phoebe:} She is so great! I miss her.
	\switchcolumn
	\charactername{菲比：}她人真好！我真想念她。
	\switchcolumn*
	\charactername{Monica:} What does she mean by 'involved'?
	\switchcolumn
	\charactername{莫妮卡：}她所谓的“加入”是什么意思？
	\switchcolumn*
	\charactername{Chandler:} I mean presumably, the biggest part of your job is done.
	\switchcolumn
	\charactername{钱德勒：}我猜，你大部分的“工作”已经完成了。
	\switchcolumn*
	\charactername{Ross:} Anyway, they want me to go down to this- sonogram thing with them tomorrow.
	\switchcolumn
	\charactername{罗斯：}总之，她们想让我明天和她们一起去做超音波检查。
	\switchcolumn*
	\charactername{Rachel:} So what are you gonna do?
	\switchcolumn
	\charactername{瑞秋：}你打算怎么做？
	\switchcolumn*
	\charactername{Ross:} I have no idea. No matter what I do, though, I'm still gonna be a father.
	\switchcolumn
	\charactername{罗斯：}我不知道。但不管我怎么做，我还是孩子的爹。
	\switchcolumn*
	\ennotmain{Joey starts to eat the rest of the lasagne and everyone turns and stares at him.}
	\switchcolumn
	\notmain{乔伊开始吃剩下的千层面，众人都转头盯着他。}
	\switchcolumn*
	\charactername{Joey:} .....Well, this is still ruined, right?
	\switchcolumn
	\charactername{乔伊：}……嗯，这面已经被搅乱了，不是吗？
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Monica and Ross are pouring wine for their parents.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，莫妮卡和罗斯正在给父母倒酒。}
	\switchcolumn*
	\charactername{Mrs. Geller:} Oh, Martha Ludwin's daughter is gonna call you. \ennotmain{Tastes a snack} Mmm! What's that curry taste?
	\switchcolumn
	\charactername{盖勒太太：}玛莎·路金的女儿会打电话给你。\notmain{尝了一口小吃}嗯！怎么会有咖哩味？
	\switchcolumn*
	\charactername{Monica:} Curry.
	\switchcolumn
	\charactername{莫妮卡：}因为放了咖哩。
	\switchcolumn*
	\charactername{Mrs. Geller:} Mmmm!
	\switchcolumn
	\charactername{盖勒太太：}嗯！真好吃！
	\switchcolumn*
	\charactername{Ross:} I- I think they're great! I, I really do.
	\switchcolumn
	\charactername{罗斯：}我觉得这东西很好吃！真的。
	\switchcolumn*
	\charactername{Mr. Geller:} \ennotmain{To Ross} Do you remember the Ludwins? The big one had a thing for you, didn't she?
	\switchcolumn
	\charactername{盖勒先生：}\notmain{对罗斯}你还记得路金一家人吗？他们的大女儿喜欢你，对不对？
	\switchcolumn*
	\charactername{Mrs. Geller:} They all had a thing for him.
	\switchcolumn
	\charactername{盖勒太太：}他们家的女儿都喜欢他。
	\switchcolumn*
	\charactername{Ross:} Aw, Mom...
	\switchcolumn
	\charactername{罗斯：}哎呀，妈……
	\switchcolumn*
	\charactername{Monica:} I'm sorry, why is this girl going to call me?
	\switchcolumn
	\charactername{莫妮卡：}抱歉，她为什么要打电话给我？
	\switchcolumn*
	\charactername{Mrs. Geller:} Oh, she just graduated, and she wants to be something in cooking, or food, or.... I don't know. Anyway, I told her you had a restaurant-
	\switchcolumn
	\charactername{盖勒太太：}她刚毕业，想找份和烹饪、美食相关的工作吧，我不太清楚。总之，我告诉她你开了一家餐馆——
	\switchcolumn*
	\charactername{Monica:} No Mom, I don't have a restaurant, I work in a restaurant.
	\switchcolumn
	\charactername{莫妮卡：}不，妈，我没开餐馆，我在餐厅工作。
	\switchcolumn*
	\charactername{Mrs. Geller:} Well, they don't have to know that... \ennotmain{She starts to fluff the same pillow Monica fluffed multiple times earlier.}
	\switchcolumn
	\charactername{盖勒太太：}他们不需要知道……\notmain{她开始拍松莫妮卡之前已经拍过好几次的那个枕头。}
	\switchcolumn*
	\charactername{Monica:} Ross, could you come and help me with the spaghetti, please?
	\switchcolumn
	\charactername{莫妮卡：}罗斯，能帮我做义大利面吗？
	\switchcolumn*
	\charactername{Ross:} Yeah. \ennotmain{They go to the kitchen.}
	\switchcolumn
	\charactername{罗斯：}好。\notmain{两人走向厨房。}
	\switchcolumn*
	\charactername{Mrs. Geller:} Oh, we're having spaghetti! That's.... easy.
	\switchcolumn
	\charactername{盖勒太太：}哦，我们吃义大利面呀？这也……太简单了。
	\switchcolumn*
	\charactername{Monica:} I know this is going to sound unbelievably selfish, but, were you planning on bringing up the whole baby/lesbian thing? Because I think it might take some of the heat off me.
	\switchcolumn
	\charactername{莫妮卡：}我知道这样说会显得非常自私，但你打算和他们说一下孩子/女同性恋之类的事吗？因为这样可以让我喘口气。
	\switchcolumn*
	\sense{Time Lapse, everyone is now eating.}
	\switchcolumn
	\sense{时间流逝，众人开始用餐。}
	\switchcolumn*
	\charactername{Mrs. Geller:} What that Rachel did to her life.... We ran into her parents at the club, they were not playing very well.
	\switchcolumn
	\charactername{盖勒太太：}瑞秋把自己的人生搞成什么样了……我们在俱乐部遇见她父母，他们心情糟透了。
	\switchcolumn*
	\charactername{Mr. Geller:} I'm not gonna tell you what they spent on that wedding... but forty thousand dollars is a lot of money!
	\switchcolumn
	\charactername{盖勒先生：}我不想说他们为那场婚礼花了多少钱……但四万美元可不是个小数目！
	\switchcolumn*
	\charactername{Mrs. Geller:} Well, at least she had the chance to leave a man at the altar...
	\switchcolumn
	\charactername{盖勒太太：}至少她有机会把一个男人留在教堂的圣坛前……
	\switchcolumn*
	\charactername{Monica:} What's that supposed to mean?
	\switchcolumn
	\charactername{莫妮卡：}你这话是什么意思？
	\switchcolumn*
	\charactername{Mrs. Geller:} Nothing! It's an expression.
	\switchcolumn
	\charactername{盖勒太太：}没什么！只是随便说说。
	\switchcolumn*
	\charactername{Monica:} No it's not.
	\switchcolumn
	\charactername{莫妮卡：}不，不是的。
	\switchcolumn*
	\charactername{Mr. Geller:} Don't listen to your mother. You're independent, and you always have been! Even when you were a kid... and you were chubby, and you had no friends, you were just fine! And you would read alone in your room, and your puzzles...
	\switchcolumn
	\charactername{盖勒先生：}别听你妈乱讲。你一直都很独立，从来都是！就连你小时候，胖嘟嘟的，一个朋友也没有，你还是活得好好的！你会一个人待在房间里看书、玩拼图……
	\switchcolumn*
	\sense{Time Lapse.}
	\switchcolumn
	\sense{时间流逝。}
	\switchcolumn*
	\charactername{Mr. Geller:} Look, there are people like Ross who need to shoot for the stars, with his museum, and his papers getting published. Other people are satisfied with staying where they are- I'm telling you, these are the people who never get cancer.
	\switchcolumn
	\charactername{盖勒先生：}你看，有些人像罗斯一样，需要追求卓越，比如他的博物馆工作、发表论文。另一些人则安于现状——我跟你说，这种人从来不会得癌症。
	\switchcolumn*
	\sense{Time Lapse.}
	\switchcolumn
	\sense{时间流逝。}
	\switchcolumn*
	\charactername{Mr. Geller:} ...And I read about these women trying to have it all, and I thank God 'Our Little Harmonica' doesn't seem to have that problem.
	\switchcolumn
	\charactername{盖勒先生：}……我还看到有些女人想拥有一切，真庆幸我们家的“小摩妮卡”似乎没有这种问题。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{trying desperately to change the subject} So, Ross, what's going on with you? Any stories? \ennotmain{Digs her elbow into his hand.} No news, no little anecdotes to share with the folks?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{拼命想转移话题}那么，罗斯，你呢？最近有什么新鲜事？\notmain{用胳膊肘戳他的手。}没什么新闻、没什么小趣事要跟爸妈分享吗？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{pulls his hand away} Okay! Okay. \ennotmain{To his parents} Look, I, uh- I realise you guys have been wondering what exactly happened between Carol and me, and, so, well, here's the deal. Carol's a lesbian. She's living with a woman named Susan. She's pregnant with my child, and she and Susan are going to raise the baby.
	\switchcolumn
	\charactername{罗斯：}\notmain{抽回手}好吧！好吧。\notmain{对父母}听着，我知道你们一直想知道我和卡萝之间到底怎么了，事情是这样的：卡萝是个女同志，她和一个叫苏珊的女人同居，她怀了我的孩子，并且打算和苏珊一起抚养这个孩子。
	\switchcolumn*
	\ennotmain{Stunned silence ensues.}
	\switchcolumn
	\notmain{一阵令人震惊的沉默。}
	\switchcolumn*
	\charactername{Mrs. Geller:} \ennotmain{To Monica} And you knew about this?!
	\switchcolumn
	\charactername{盖勒太太：}\notmain{对莫妮卡}这些你全都知道？！
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Central Perk, everyone's there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，众人都在。}
	\switchcolumn*
	\charactername{Joey:} Your folks are really that bad, huh?
	\switchcolumn
	\charactername{乔伊：}你爸妈真的那么糟吗？
	\switchcolumn*
	\charactername{Ross:} Well, y'know, these people are pros. They know what they're doing, they take their time, they get the job done.
	\switchcolumn
	\charactername{罗斯：}你要知道，这些人可专业了，他们知道自己在做什么，慢慢来，总能达到目的。
	\switchcolumn*
	\charactername{Monica:} Boy, I know they say you can't change your parents,... boy, if you could- \ennotmain{To Ross} -I'd want yours.
	\switchcolumn
	\charactername{莫妮卡：}常言道，父母是无法选择的……可如果可以，\notmain{对罗斯}我真想换你的父母。
	\switchcolumn*
	\charactername{Ross:} Must pee. \ennotmain{Goes to pee.}
	\switchcolumn
	\charactername{罗斯：}我要去尿尿了。\notmain{起身离开。}
	\switchcolumn*
	\charactername{Phoebe:} Y'know, it's even worse when you're twins.
	\switchcolumn
	\charactername{菲比：}如果你是双胞胎，情况会更糟。
	\switchcolumn*
	\charactername{Rachel:} You're twins?
	\switchcolumn
	\charactername{瑞秋：}你是双胞胎？
	\switchcolumn*
	\charactername{Phoebe:} Yeah. We don't speak. She's like this high-powered, driven career type.
	\switchcolumn
	\charactername{菲比：}对，我们不往来。她是那种一心扑在事业上、野心勃勃的人。
	\switchcolumn*
	\charactername{Chandler:} What does she do?
	\switchcolumn
	\charactername{钱德勒：}她从事什么工作？
	\switchcolumn*
	\charactername{Phoebe:} She's a waitress.
	\switchcolumn
	\charactername{菲比：}服务生。
	\switchcolumn*
	\charactername{Rachel:} All right, you guys, I kinda gotta clean up now. \ennotmain{They all start to leave.}
	\switchcolumn
	\charactername{瑞秋：}好了，各位，我得打扫了。\notmain{众人开始起身离开。}
	\switchcolumn*
	\charactername{Monica:} Chandler, you're an only child, right? You don't have any of this.
	\switchcolumn
	\charactername{莫妮卡：}钱德勒，你是独生子，对不对？你没有这些烦恼吧。
	\switchcolumn*
	\charactername{Chandler:} Well, no, although I did have an imaginary friend, who... my parents actually preferred.
	\switchcolumn
	\charactername{钱德勒：}嗯，是没有。不过我以前有个想象中的朋友，而我爸妈其实更喜欢他。
	\switchcolumn*
	\charactername{Rachel:} The lights, please..
	\switchcolumn
	\charactername{瑞秋：}麻烦关灯……
	\switchcolumn*
	\ennotmain{Joey turns off the lights, and they all leave as Rachel starts to clean up. Ross enters from the bathroom.}
	\switchcolumn
	\notmain{乔伊关掉灯，众人离开，瑞秋开始打扫。罗斯从洗手间走进来。}
	\switchcolumn*
	\charactername{Ross:} ...How long was I in there?
	\switchcolumn
	\charactername{罗斯：}……我在里面待了多久？
	\switchcolumn*
	\charactername{Rachel:} I'm just cleaning up.
	\switchcolumn
	\charactername{瑞秋：}我只是在打扫。
	\switchcolumn*
	\charactername{Ross:} D'ya.. uh.. Do you need any help?
	\switchcolumn
	\charactername{罗斯：}你……呃……需要帮忙吗？
	\switchcolumn*
	\charactername{Rachel:} Uh.. okay, sure! Thanks! \ennotmain{She hands him the broom and sits down.}
	\switchcolumn
	\charactername{瑞秋：}呃……好呀，谢谢！\notmain{把扫帚递给她，自己坐了下来。}
	\switchcolumn*
	\charactername{Ross:} Anyway.. um.. \ennotmain{Starts to sweep.} So, you- uh- you nervous about Barry tomorrow?
	\switchcolumn
	\charactername{罗斯：}那个……嗯……\notmain{开始扫地。}所以，你……呃……明天见巴瑞，会紧张吗？
	\switchcolumn*
	\charactername{Rachel:} Oh.. a little..
	\switchcolumn
	\charactername{瑞秋：}哦……有一点……
	\switchcolumn*
	\charactername{Ross:} Mm-hmm..
	\switchcolumn
	\charactername{罗斯：}嗯……
	\switchcolumn*
	\charactername{Rachel:} A lot.
	\switchcolumn
	\charactername{瑞秋：}非常紧张。
	\switchcolumn*
	\charactername{Ross:} Mm.
	\switchcolumn
	\charactername{罗斯：}嗯。
	\switchcolumn*
	\charactername{Rachel:} So, got any advice? Y'know, as someone who's recently been- dumped?
	\switchcolumn
	\charactername{瑞秋：}那你有什么建议吗？作为一个最近刚被甩的人？
	\switchcolumn*
	\charactername{Ross:} Well, you may wanna steer clear of the word 'dumped'. Chances are he's gonna be this, this broken shell of a man, y'know, so you should try not to look too terrific, I know it'll be hard. Or, y'know, uh, hey!, I'll go down there, and I'll give Barry back his ring, and you can go with Carol and Susan to the OB/GYN...
	\switchcolumn
	\charactername{罗斯：}嗯，你或许应该避免用“甩”这个字眼。他现在可能已经心碎成渣了，所以你尽量别显得太光彩照人，我知道这很难。或者，呃，要不这样！我去把戒指还给巴瑞，你陪卡萝和苏珊去妇产科……
	\switchcolumn*
	\charactername{Rachel:} Oh, you've got Carol tomorrow.. When did it get so complicated?
	\switchcolumn
	\charactername{瑞秋：}哦，你明天要陪卡萝……事情怎么变得这么复杂？
	\switchcolumn*
	\charactername{Ross:} Got me.
	\switchcolumn
	\charactername{罗斯：}你可问倒我了。
	\switchcolumn*
	\charactername{Rachel:} Remember when we were in high school together?
	\switchcolumn
	\charactername{瑞秋：}还记得我们高中时一起上学的日子吗？
	\switchcolumn*
	\charactername{Ross:} Yeah.
	\switchcolumn
	\charactername{罗斯：}记得。
	\switchcolumn*
	\charactername{Rachel:} I mean, didn't you think you were just gonna meet someone, fall in love- and that'd be it? \ennotmain{Ross gazes at her.} ..Ross?
	\switchcolumn
	\charactername{瑞秋：}我是说，你没想过自己会遇见一个人，坠入爱河——然后就一辈子在一起吗？\notmain{罗斯凝视着她。}……罗斯？
	\switchcolumn*
	\charactername{Ross:} Yes, yes!
	\switchcolumn
	\charactername{罗斯：}想过，当然想过！
	\switchcolumn*
	\charactername{Rachel:} Oh! Man, I never thought I'd be here.. \ennotmain{She leans back onto his hand.}
	\switchcolumn
	\charactername{瑞秋：}哦！天啊，我从没想过自己会沦落到这种地步……\notmain{她向后靠，碰到了罗斯的手。}
	\switchcolumn*
	\charactername{Ross:} Me either... \ennotmain{He pulls up a stool so that he doesn't have to move his hand.}
	\switchcolumn
	\charactername{罗斯：}我也没想过……\notmain{他拉过一张凳子坐下，这样就不用挪开手了。}
	\switchcolumn*
	\sense{Scene: Carol's OB/GYN, Carol is waiting.}
	\switchcolumn
	\sense{场景：卡萝的妇产科诊所，卡萝正在等候。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{entering} Sorry I'm late, I was stuck at work. There was this big dinosaur.. thing.. anyway.
	\switchcolumn
	\charactername{罗斯：}\notmain{走进来}抱歉我迟到了，工作上有点事脱不开身，是关于一具大型恐龙……之类的，总之就是耽误了。
	\switchcolumn*
	\ennotmain{Susan enters holding a drink.}
	\switchcolumn
	\notmain{苏珊拿着一杯饮料走进来。}
	\switchcolumn*
	\charactername{Susan:} Hi.
	\switchcolumn
	\charactername{苏珊：}嗨。
	\switchcolumn*
	\charactername{Carol:} Ross, you remember Susan.
	\switchcolumn
	\charactername{卡萝：}罗斯，你还记得苏珊吧。
	\switchcolumn*
	\charactername{Ross:} How could I forget?
	\switchcolumn
	\charactername{罗斯：}我怎能忘得了？
	\switchcolumn*
	\charactername{Susan:} Ross.
	\switchcolumn
	\charactername{苏珊：}罗斯。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{they shake hands} Hello, Susan. \ennotmain{To Carol} Good shake. Good shake. So, uh, we're just waiting for...?
	\switchcolumn
	\charactername{罗斯：}\notmain{两人握手}苏珊，你好。\notmain{对卡萝}她握手真有力。那么，我们在等……？
	\switchcolumn*
	\charactername{Carol:} Dr. Oberman.
	\switchcolumn
	\charactername{卡萝：}欧伯曼大夫。
	\switchcolumn*
	\charactername{Ross:} ..Dr. Oberman. Okay. And is he-
	\switchcolumn
	\charactername{罗斯：}……欧伯曼大夫。好的。他是——
	\switchcolumn*
	\charactername{Susan:} She.
	\switchcolumn
	\charactername{苏珊：}她。
	\switchcolumn*
	\charactername{Ross:} -she, of course, she- uh- familiar with our.. special situation?
	\switchcolumn
	\charactername{罗斯：}——她，当然是她——呃——她了解我们的……特殊情况吗？
	\switchcolumn*
	\charactername{Carol:} Yes, and she's very supportive.
	\switchcolumn
	\charactername{卡萝：}了解，而且她非常支持我们。
	\switchcolumn*
	\charactername{Ross:} Okay, that's great. \ennotmain{Susan gives her drink to Carol.} No, I'm- Oh.
	\switchcolumn
	\charactername{罗斯：}好，那太好了。\notmain{苏珊把饮料递给卡萝。}不，我只是——哦。
	\switchcolumn*
	\charactername{Carol:} Thanks.
	\switchcolumn
	\charactername{卡萝：}谢谢。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{picks up a surgical instrument and mimes a duck with it} Quack, quack..
	\switchcolumn
	\charactername{罗斯：}\notmain{拿起一件手术器械，模仿鸭子叫}嘎嘎……
	\switchcolumn*
	\charactername{Carol:} Ross? That opens my cervix. \ennotmain{He drops it in horror.}
	\switchcolumn
	\charactername{卡萝：}罗斯？那是用来打开我的子宫颈的。\notmain{罗斯惊恐地扔掉器械。}
	\switchcolumn*
	\sense{Scene: Barry's office, Barry is working on patient, Robbie, as Rachel enters.}
	\switchcolumn
	\sense{场景：巴瑞的诊所，巴瑞正在给病人罗比治疗，瑞秋走进来。}
	\switchcolumn*
	\charactername{Rachel:} Barry?
	\switchcolumn
	\charactername{瑞秋：}巴瑞？
	\switchcolumn*
	\charactername{Barry:} Come in.
	\switchcolumn
	\charactername{巴瑞：}进来吧。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{hesitates} Are you sure?
	\switchcolumn
	\charactername{瑞秋：}\notmain{犹豫}这样没问题吗？
	\switchcolumn*
	\charactername{Barry:} Yeah! It's fine, it's fine. Robbie's gonna be here for hours.
	\switchcolumn
	\charactername{巴瑞：}没问题！真的没事，罗比得在这儿待好几个小时。
	\switchcolumn*
	\charactername{Robbie:} Huh?!
	\switchcolumn
	\charactername{罗比：}啊？！
	\switchcolumn*
	\charactername{Barry:} So, how ya doin?
	\switchcolumn
	\charactername{巴瑞：}最近好吗？
	\switchcolumn*
	\charactername{Rachel:} I'm- uh- I'm okay... You look great!
	\switchcolumn
	\charactername{瑞秋：}我——呃——我还好……你气色好极了！
	\switchcolumn*
	\charactername{Barry:} Yeah, well..
	\switchcolumn
	\charactername{巴瑞：}嗯，还好啦……
	\switchcolumn*
	\charactername{Bernice:} \ennotmain{over intercom} Dr. Farber, Jason Greenstein's gagging.
	\switchcolumn
	\charactername{伯妮斯：}\notmain{通过对讲机}法伯大夫，杰森·格林斯坦快窒息了。
	\switchcolumn*
	\charactername{Barry:} \ennotmain{answering the intercom} Be right there. \ennotmain{To Robbie and Rachel} Be back in a sec.
	\switchcolumn
	\charactername{巴瑞：}\notmain{回应对讲机}马上到。\notmain{对罗比和瑞秋}我马上回来。
	\switchcolumn*
	\ennotmain{As Barry exits Robbie stares at Rachel.}
	\switchcolumn
	\notmain{巴瑞离开后，罗比盯着瑞秋看。}
	\switchcolumn*
	\charactername{Rachel:} I dumped him.
	\switchcolumn
	\charactername{瑞秋：}我甩了他。
	\switchcolumn*
	\charactername{Robbie:} Okay.
	\switchcolumn
	\charactername{罗比：}哦。
	\switchcolumn*
	\sense{Scene: Carol's OB/GYN, they're talking about how this is going to work.}
	\switchcolumn
	\sense{场景：卡萝的妇产科诊所，三人在讨论后续该如何安排。}
	\switchcolumn*
	\charactername{Ross:} So, um- so how's this, uh, how's this gonna work? Y'know, with us? Y'know, when, like, important decisions have to be made?
	\switchcolumn
	\charactername{罗斯：}那么，嗯——我们该如何处理这件事？比如遇到需要做重大决定的时候？
	\switchcolumn*
	\charactername{Carol:} Give me a 'for instance'.
	\switchcolumn
	\charactername{卡萝：}举个例子？
	\switchcolumn*
	\charactername{Ross:} Well, uh, uh, I don't know, okay, okay, how about with the, uh, with the baby's name?
	\switchcolumn
	\charactername{罗斯：}嗯，呃，我不知道，好吧，比如孩子的名字？
	\switchcolumn*
	\charactername{Carol:} Marlon-
	\switchcolumn
	\charactername{卡萝：}马龙——
	\switchcolumn*
	\charactername{Ross:} Marlon?!
	\switchcolumn
	\charactername{罗斯：}马龙？！
	\switchcolumn*
	\charactername{Carol:} -if it's a boy, Minnie if it's a girl.
	\switchcolumn
	\charactername{卡萝：}——如果是男孩就叫马龙，如果是女孩就叫米妮。
	\switchcolumn*
	\charactername{Ross:} ...As in Mouse?
	\switchcolumn
	\charactername{罗斯：}……和米奇的女友米妮同名？
	\switchcolumn*
	\charactername{Carol:} As in my grandmother.
	\switchcolumn
	\charactername{卡萝：}和我奶奶同名。
	\switchcolumn*
	\charactername{Ross:} Still, you- you say Minnie, you hear Mouse. Um, how about, um.. how about Julia?
	\switchcolumn
	\charactername{罗斯：}不管怎样，听到米妮还是会想到老鼠。嗯，朱莉亚怎么样？
	\switchcolumn*
	\charactername{Carol:} Julia..
	\switchcolumn
	\charactername{卡萝：}朱莉亚……
	\switchcolumn*
	\charactername{Susan:} We agreed on Minnie.
	\switchcolumn
	\charactername{苏珊：}我们已经决定用米妮了。
	\switchcolumn*
	\charactername{Ross:} 'S'funny, um, uh, we agreed we'd spend the rest of our lives together. Things change, roll with the punches. I believe Julia's on the table..?
	\switchcolumn
	\charactername{罗斯：}真有意思，我们曾约定要共度余生，世事难料，兵来将挡。我觉得朱莉亚也可以考虑一下……？
	\switchcolumn*
	\sense{Scene: Barry's office, Rachel is doing her makeup in the mirror on Barry's lamp as Barry enters.}
	\switchcolumn
	\sense{场景：巴瑞的诊所，瑞秋对着巴瑞台灯上的镜子补妆，巴瑞走进来。}
	\switchcolumn*
	\charactername{Barry:} Sorry about that. So. What have you been up to?
	\switchcolumn
	\charactername{巴瑞：}刚才不好意思。对了，你最近在忙什么？
	\switchcolumn*
	\charactername{Rachel:} Oh, not much. I-I got a job.
	\switchcolumn
	\charactername{瑞秋：}没什么特别的，我找到工作了。
	\switchcolumn*
	\charactername{Barry:} Oh, that's great.
	\switchcolumn
	\charactername{巴瑞：}哦，那太好了。
	\switchcolumn*
	\charactername{Rachel:} Why are- why are you so tanned?
	\switchcolumn
	\charactername{瑞秋：}你为什么晒得这么黑？
	\switchcolumn*
	\charactername{Barry:} Oh, I, uh- I went to Aruba.
	\switchcolumn
	\charactername{巴瑞：}哦，我——呃——我去阿鲁巴了。
	\switchcolumn*
	\charactername{Rachel:} Oh no. You went on our honeymoon alone?
	\switchcolumn
	\charactername{瑞秋：}哦不，你自己一个人去了我们的蜜月地？
	\switchcolumn*
	\charactername{Barry:} No. I went with, uh.. Now, this may hurt.
	\switchcolumn
	\charactername{巴瑞：}不是，我和……呃……你听了可能会不好受。
	\switchcolumn*
	\charactername{Robbie:} Me?!
	\switchcolumn
	\charactername{罗比：}我？！
	\switchcolumn*
	\charactername{Barry:} No! \ennotmain{To Rachel} I went with Mindy.
	\switchcolumn
	\charactername{巴瑞：}不是！\notmain{对瑞秋}我和明蒂一起去的。
	\switchcolumn*
	\charactername{Rachel:} Mindy?! My maid of honour, Mindy?!
	\switchcolumn
	\charactername{瑞秋：}明蒂？！我的伴娘明蒂？！
	\switchcolumn*
	\charactername{Barry:} Yeah, well, uh, we're kind of a thing now.
	\switchcolumn
	\charactername{巴瑞：}对，嗯，我们现在是认真的。
	\switchcolumn*
	\charactername{Rachel:} Oh! Well, um.. \ennotmain{Grabs his forehead} You've got plugs!
	\switchcolumn
	\charactername{瑞秋：}哦！嗯……\notmain{摸他的额头}你去做植发了！
	\switchcolumn*
	\charactername{Barry:} Careful! They haven't quite taken yet.
	\switchcolumn
	\charactername{巴瑞：}小心！还没完全固定好。
	\switchcolumn*
	\charactername{Rachel:} And you've got lenses! But you hate sticking your finger in your eye!
	\switchcolumn
	\charactername{瑞秋：}你还戴了隐形眼镜！可你以前讨厌把手指放进眼睛里的！
	\switchcolumn*
	\charactername{Barry:} Not for her. Listen, I really wanted to thank you.
	\switchcolumn
	\charactername{巴瑞：}为了她就不讨厌了。其实，我真的很感谢你。
	\switchcolumn*
	\charactername{Rachel:} Okay..
	\switchcolumn
	\charactername{瑞秋：}哦……
	\switchcolumn*
	\charactername{Barry:} See, about a month ago, I wanted to hurt you. More than I've ever wanted to hurt anyone in my life. And I'm an orthodontist.
	\switchcolumn
	\charactername{巴瑞：}大概一个月前，我特别想伤害你，比我这辈子想伤害任何人的欲望都强烈。要知道，我可是个整牙医师。
	\switchcolumn*
	\charactername{Rachel:} Wow.
	\switchcolumn
	\charactername{瑞秋：}哇。
	\switchcolumn*
	\charactername{Barry:} You know, you were right? I mean, I thought we were happy. We weren't happy. But with Mindy, now I'm happy. Spit.
	\switchcolumn
	\charactername{巴瑞：}你说得对，我以前以为我们很幸福，但其实并没有。不过和明蒂在一起，我现在很幸福。吐掉。
	\switchcolumn*
	\charactername{Rachel:} What?
	\switchcolumn
	\charactername{瑞秋：}什么？
	\switchcolumn*
	\charactername{Robbie:} Me. \ennotmain{Spits.}
	\switchcolumn
	\charactername{罗比：}跟我说的。\notmain{吐出口中物品。}
	\switchcolumn*
	\charactername{Rachel:} Anyway, um, \ennotmain{Gets the ring out of her purse.} I guess this belongs to you. And thank you for giving it to me.
	\switchcolumn
	\charactername{瑞秋：}总之，嗯，\notmain{从包里拿出戒指}这个应该还给你。谢谢你当初送给我。
	\switchcolumn*
	\charactername{Barry:} Well, thank you for giving it back.
	\switchcolumn
	\charactername{巴瑞：}也谢谢你还给我。
	\switchcolumn*
	\ennotmain{Barry and Rachel look at each other.}
	\switchcolumn
	\notmain{巴瑞和瑞秋对视。}
	\switchcolumn*
	\charactername{Robbie:} Hello?!
	\switchcolumn
	\charactername{罗比：}喂？！
	\switchcolumn*
	\sense{Scene: Carol's OB/GYN, they're still arguing about what to name the baby.}
	\switchcolumn
	\sense{场景：卡萝的妇产科诊所，三人还在为孩子的名字争论。}
	\switchcolumn*
	\charactername{Susan:} Oh, please! What's wrong with Helen?
	\switchcolumn
	\charactername{苏珊：}拜托！海伦有什么不好？
	\switchcolumn*
	\charactername{Ross:} Helen Geller? I don't think so.
	\switchcolumn
	\charactername{罗斯：}海伦·盖勒？不行。
	\switchcolumn*
	\charactername{Carol:} Hello? It's not gonna be Helen Geller.
	\switchcolumn
	\charactername{卡萝：}拜托？她不会姓盖勒的。
	\switchcolumn*
	\charactername{Ross:} Thank you!
	\switchcolumn
	\charactername{罗斯：}谢谢！
	\switchcolumn*
	\charactername{Carol:} No, I mean it's not Geller.
	\switchcolumn
	\charactername{卡萝：}不，我是说她不姓盖勒。
	\switchcolumn*
	\charactername{Ross:} What, it's gonna be Helen Willick?
	\switchcolumn
	\charactername{罗斯：}那难道姓威利克？海伦·威利克？
	\switchcolumn*
	\charactername{Carol:} No, actually, um, we talked about Helen Willick-Bunch.
	\switchcolumn
	\charactername{卡萝：}其实，我们考虑用海伦·威利克-班奇。
	\switchcolumn*
	\charactername{Ross:} Well, wait a minute, wha- why is she in the title?
	\switchcolumn
	\charactername{罗斯：}等等，为什么有她的姓？
	\switchcolumn*
	\charactername{Susan:} It's my baby too.
	\switchcolumn
	\charactername{苏珊：}这也是我的孩子。
	\switchcolumn*
	\charactername{Ross:} Oh, 's'funny, really? Um, I don't remember you making any sperm.
	\switchcolumn
	\charactername{罗斯：}哦，真的吗？我可不记得你会制造精子。
	\switchcolumn*
	\charactername{Susan:} Yeah, and we all know what a challenge that is!
	\switchcolumn
	\charactername{苏珊：}是呀，我们都知道那对你来说有多难！
	\switchcolumn*
	\charactername{Carol:} All right, you two, stop it!
	\switchcolumn
	\charactername{卡萝：}够了，你们两个别吵了！
	\switchcolumn*
	\charactername{Ross:} No no no, she gets a credit, hey, I'm in there too.
	\switchcolumn
	\charactername{罗斯：}不行，功劳全让她占了，我也有份啊。
	\switchcolumn*
	\charactername{Carol:} Ross. You're not actually suggesting Helen Willick-Bunch-Geller? 'Cause I think that borders on child abuse.
	\switchcolumn
	\charactername{卡萝：}罗斯，你该不会想让她叫海伦·威利克-班奇-盖勒吧？这简直是虐待儿童。
	\switchcolumn*
	\charactername{Ross:} Of course not, I'm... suggesting Geller-Willick-Bunch.
	\switchcolumn
	\charactername{罗斯：}当然不是，我是说盖勒-威利克-班奇。
	\switchcolumn*
	\charactername{Susan:} Oh, no, nonononono, you see what he's doing? He knows no-one's gonna say all those names, so they'll wind up calling her Geller, then he gets his way!
	\switchcolumn
	\charactername{苏珊：}哦，不，不行不行不行，你看他的心思！他知道没人会叫她全名，最后大家都会叫她盖勒，这样他就得逞了！
	\switchcolumn*
	\charactername{Ross:} My way?! You-you think this is my way? Believe me, of all the ways I ever imagined this moment in my life being, this is not my way- y'know what? Uh, um, this is too hard. I'm not, I can't do-
	\switchcolumn
	\charactername{罗斯：}我得逞？你觉得这是我想要的结果？相信我，我这辈子设想过无数种此刻的场景，绝对不是现在这样——算了，这太难了，我做不到——
	\switchcolumn*
	\charactername{Dr. Oberman:} \ennotmain{entering} Knock knock! How are we today? Any nausea?
	\switchcolumn
	\charactername{欧伯曼大夫：}\notmain{走进来}有人在吗？今天感觉怎么样？想呕吐吗？
	\switchcolumn*
	\charactername{All:} Yeah. Yeah. A little.
	\switchcolumn
	\charactername{众人：}嗯，有一点。
	\switchcolumn*
	\charactername{Dr. Oberman:} Well, I was just wondering about the mother-to-be, but.. thanks for sharing. \ennotmain{To Carol} Uh, lie back..
	\switchcolumn
	\charactername{欧伯曼大夫：}我只是问准妈妈，不过还是谢谢你们分享。\notmain{对卡萝}躺好……
	\switchcolumn*
	\charactername{Ross:} You- uh- y'know what, I'm gonna go. I don't- I don't think I can be involved in this particular thing right now.
	\switchcolumn
	\charactername{罗斯：}那个……我还是走吧。我觉得我现在还没法接受这件事。
	\switchcolumn*
	\ennotmain{He turns to go, but the sound of the sonogram catches his ear. He returns and stares at it.}
	\switchcolumn
	\notmain{他转身要走，但超音波的声音吸引了他。他走回来，盯着屏幕。}
	\switchcolumn*
	\charactername{Ross:} Oh my God.
	\switchcolumn
	\charactername{罗斯：}我的天啊。
	\switchcolumn*
	\charactername{Susan:} Look at that.
	\switchcolumn
	\charactername{苏珊：}看啊。
	\switchcolumn*
	\charactername{Carol:} I know.
	\switchcolumn
	\charactername{卡萝：}我知道。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's apartment, everyone is watching the tape of the sonogram. Rachel is on the phone.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，众人正在看超音波录像带。瑞秋在打电话。}
	\switchcolumn*
	\charactername{Ross:} Well? Isn't that amazing?
	\switchcolumn
	\charactername{罗斯：}怎么样？很神奇吧？
	\switchcolumn*
	\charactername{Joey:} What are we supposed to be seeing here?
	\switchcolumn
	\charactername{乔伊：}我们该看到什么？
	\switchcolumn*
	\charactername{Chandler:} I don't know, but.. I think it's about to attack the Enterprise.
	\switchcolumn
	\charactername{钱德勒：}我不知道，但我觉得它好像要攻击“企业号”\notmain{《星舰迷航记》中的飞船}。
	\switchcolumn*
	\charactername{Phoebe:} You know, if you tilt your head to the left, and relax your eyes, it kinda looks like an old potato.
	\switchcolumn
	\charactername{菲比：}如果你们把头稍微向左偏，两眼放轻松，它看起来就像一颗老马铃薯。
	\switchcolumn*
	\charactername{Ross:} Then don't do that, alright?
	\switchcolumn
	\charactername{罗斯：}那你们就别那么看，好吗？
	\switchcolumn*
	\charactername{Phoebe:} Okay!
	\switchcolumn
	\charactername{菲比：}好！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{walks over to where Monica is standing} Monica. What do you think?
	\switchcolumn
	\charactername{罗斯：}\notmain{走到莫妮卡身边}摩妮卡，你觉得怎么样？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{welling up} Mm-hmm.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{热泪盈眶}嗯。
	\switchcolumn*
	\charactername{Ross:} Wh- are you welling up?
	\switchcolumn
	\charactername{罗斯：}你——你在哭吗？
	\switchcolumn*
	\charactername{Monica:} No.
	\switchcolumn
	\charactername{莫妮卡：}没有。
	\switchcolumn*
	\charactername{Ross:} You are, you're welling up.
	\switchcolumn
	\charactername{罗斯：}你有，你在流泪。
	\switchcolumn*
	\charactername{Monica:} Am not!
	\switchcolumn
	\charactername{莫妮卡：}没有！
	\switchcolumn*
	\charactername{Ross:} You're gonna be an aunt.
	\switchcolumn
	\charactername{罗斯：}你就要成为阿姨了。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{pushes him and starts to cry} Oh shut up!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{推了他一下，开始哭}闭嘴！
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{on phone} Hi, Mindy. Hi, it-it's Rachel. Yeah, I'm fine. I-I saw Barry today. Oh, yeah, yeah he-he told me. No, no, it's okay. I hope you two are very happy, I really do. Oh, oh, and Mindy, y'know, if-if everything works out, and you guys end up getting married and having kids- and everything- I just hope they have his old hairline and your old nose. \ennotmain{Slams the phone down.} \ennotmain{To everyone} Okay, I know it was a cheap shot, but I feel so much better now.
	\switchcolumn
	\charactername{瑞秋：}\notmain{打电话}嗨，明蒂。嗨，我是瑞秋。对，我很好。我今天见到巴瑞了。哦，对，他都告诉我了。没事，真的没事。我真心祝福你们幸福快乐。哦，还有，明蒂，要是一切顺利，你们结婚生子的话——我只希望孩子们能遗传他以前的发线和你以前的鼻子。\notmain{挂掉电话。}\notmain{对众人}我知道这招很贱，但我现在感觉好多了。
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage