\begin{paracol}{2}
	\sense{Scene: Central Perk, everyone is there except Joey.} 
	\switchcolumn
	\sense{场景：中央公园咖啡馆，除乔伊外全员在场}
	\switchcolumn*
	\charactername{Monica:} Alright. Phoebe?
	\switchcolumn
	\charactername{莫妮卡：}好了，菲比？
	\switchcolumn*
	\charactername{Phoebe:} Okay, okay. If I were omnipotent for a day, I would want, um, world peace, no more hunger, good things for the rain-forest...And bigger boobs!
	\switchcolumn
	\charactername{菲比：}好啦好啦。如果我有一天全能，我想要，嗯，世界和平，不再有饥饿，热带雨林能好好的…… 还有更大的胸部！
	\switchcolumn*
	\charactername{Ross:} Yeah, see.. you took mine. Chandler, what about you?
	\switchcolumn
	\charactername{罗斯：}看吧，你把我的愿望说光了。钱德勒，你呢？
	\switchcolumn*
	\charactername{Chandler:} Uh, if I were omnipotent for a day, I'd.. make myself omnipotent forever.
	\switchcolumn
	\charactername{钱德勒：}呃，如果我有一天全能，我会…… 让自己永远全能。
	\switchcolumn*
	\charactername{Rachel:} See, there's always one guy. \ennotmain{Mocking} "If I had a wish, I'd wish for three more wishes."
	\switchcolumn
	\charactername{瑞秋：}看吧，总有这种人。\notmain{模仿}“如果我能许愿，我要再许三个愿望。”
	\switchcolumn*
	\ennotmain{Joey enters.}
	\switchcolumn
	\notmain{乔伊走进来}
	\switchcolumn*
	\charactername{All:} Hey Joey. Hi. Hey, buddy.
	\switchcolumn
	\charactername{众人：}嘿，乔伊！嗨！嘿，兄弟。
	\switchcolumn*
	\charactername{Monica:} Hey, Joey, what would you do if you were omnipotent?
	\switchcolumn
	\charactername{莫妮卡：}嘿，乔伊，如果你全能的话会做什么？
	\switchcolumn*
	\charactername{Joey:} Probably kill myself!
	\switchcolumn
	\charactername{乔伊：}可能会自杀吧！
	\switchcolumn*
	\charactername{Monica:} ..Excuse me?
	\switchcolumn
	\charactername{莫妮卡：}…… 你说什么？
	\switchcolumn*
	\charactername{Joey:} Hey, if Little Joey's dead, then I got no reason to live!
	\switchcolumn
	\charactername{乔伊：}嘿，如果小乔伊都没了，我活着还有什么意义！
	\switchcolumn*
	\charactername{Ross:} Joey, uh- OMnipotent.
	\switchcolumn
	\charactername{罗斯：}乔伊，是 “全 - 能”\notmain{纠正发音}。
	\switchcolumn*
	\charactername{Joey:} You are? Ross, I'm sorry..
	\switchcolumn
	\charactername{乔伊：}你是全能的？罗斯，对不起啊……
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, Ross and Monica are watching Phoebe sleep.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，罗斯和莫妮卡看着菲比睡觉}
	\switchcolumn*
	\charactername{Monica:} How does she do that?
	\switchcolumn
	\charactername{莫妮卡：}她怎么能这样\notmain{在公共场合睡着}？
	\switchcolumn*
	\charactername{Ross:} I cannot sleep in a public place.
	\switchcolumn
	\charactername{罗斯：}我可没法在公共场所睡觉。
	\switchcolumn*
	\charactername{Monica:} Would you look at her? She is so peaceful.
	\switchcolumn
	\charactername{莫妮卡：}你看看她，多安详啊。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{waking and startling them} Oh! What what what! ...Hi.
	\switchcolumn
	\charactername{菲比：}\notmain{惊醒，吓了他们一跳}哦！怎么了怎么了怎么了！…… 嗨。
	\switchcolumn*
	\charactername{Ross:} It's okay, y'know, you just nodded off again.
	\switchcolumn
	\charactername{罗斯：}没事，你只是又打了个盹。
	\switchcolumn*
	\charactername{Monica:} What's going on with you?
	\switchcolumn
	\charactername{莫妮卡：}你怎么回事啊？
	\switchcolumn*
	\charactername{Phoebe:} I got no sleep last night!
	\switchcolumn
	\charactername{菲比：}我昨晚一整晚都没睡！
	\switchcolumn*
	\charactername{Ross:} Why?
	\switchcolumn
	\charactername{罗斯：}为什么啊？
	\switchcolumn*
	\charactername{Phoebe:} My grandmother has this new boyfriend, and they're both kind of insecure in bed. Oh, and deaf. So they're constantly, like, having to reassure each other that they're having a good time. You have no idea how loud they are!
	\switchcolumn
	\charactername{菲比：}我奶奶交了个新男友，他俩在床上都有点不自信。而且他俩还耳背。所以他们得一直跟对方确认自己玩得很开心。你们根本想象不到他们有多吵！
	\switchcolumn*
	\charactername{Monica:} Well, if you want, you can stay with Rachel and me tonight.
	\switchcolumn
	\charactername{莫妮卡：}如果你愿意，今晚可以跟我和瑞秋住。
	\switchcolumn*
	\charactername{Phoebe:} Thanks.
	\switchcolumn
	\charactername{菲比：}谢谢。
	\switchcolumn*
	\ennotmain{Chandler and Joey enter. Joey is counting his steps.}
	\switchcolumn
	\notmain{钱德勒和乔伊走进来，乔伊在数步数}
	\switchcolumn*
	\charactername{Joey:} ...Ninety-five, ninety-six, ninety-seven. See, I told you! Less than a hundred steps from our place to here.
	\switchcolumn
	\charactername{乔伊：}…… 九十五，九十六，九十七。看吧，我就说！从我们公寓到这儿不到一百步。
	\switchcolumn*
	\charactername{Chandler:} You got waaaay too much free time.
	\switchcolumn
	\charactername{钱德勒：}你真是闲得发慌。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{to Ross} Hey! Here's the birthday boy! Ross, check it out: hockey tickets, Rangers-Penguins, tonight at the Garden, and we're taking you.
	\switchcolumn
	\charactername{乔伊：}\notmain{对罗斯说}嘿！寿星在这儿呢！罗斯，快看这个：冰球比赛门票，流浪者队对企鹅队，今晚在麦迪逊广场花园，我们带你去。
	\switchcolumn*
	\charactername{Chandler:} Happy birthday, pal!
	\switchcolumn
	\charactername{钱德勒：}生日快乐，伙计！
	\switchcolumn*
	\charactername{Joey:} We love you, man. \ennotmain{Kisses Ross}
	\switchcolumn
	\charactername{乔伊：}我们爱你啊，兄弟。\notmain{亲了罗斯一下}
	\switchcolumn*
	\charactername{Ross:} Funny, my birthday was seven months ago.
	\switchcolumn
	\charactername{罗斯：}有意思，我的生日七个月前就过了。
	\switchcolumn*
	\charactername{Joey:} So?
	\switchcolumn
	\charactername{乔伊：}那又怎样？
	\switchcolumn*
	\charactername{Ross:} So, I'm guessing you had an extra ticket and couldn't decide which one of you got to bring a date?
	\switchcolumn
	\charactername{罗斯：}所以，我猜你们是多了一张票，又不知道谁该带约会对象去吧？
	\switchcolumn*
	\charactername{Chandler:} Well, aren't we Mr. "The glass is half empty."
	\switchcolumn
	\charactername{钱德勒：}哟，你还真是个 “悲观主义者” 啊。
	\switchcolumn*
	\charactername{Ross:} Oh my God, oh- is today the twentieth, October twentieth?
	\switchcolumn
	\charactername{罗斯：}哦我的天，今天是二十号吗？十月二十号？
	\switchcolumn*
	\charactername{Monica:} Oh, I was hoping you wouldn't remember.
	\switchcolumn
	\charactername{莫妮卡：}哦，我还希望你忘了呢。
	\switchcolumn*
	\charactername{Ross:} Ohhh.
	\switchcolumn
	\charactername{罗斯：}哦……
	\switchcolumn*
	\charactername{Joey:} What's wrong with the twentieth?
	\switchcolumn
	\charactername{乔伊：}二十号怎么了？
	\switchcolumn*
	\charactername{Chandler:} Eleven days before Halloween.. all the good costumes are gone?
	\switchcolumn
	\charactername{钱德勒：}万圣节前十一天…… 好看的服装都被抢光了？
	\switchcolumn*
	\charactername{Ross:} Today's the day Carol and I first.. consummated our physical relationship. \ennotmain{Joey is puzzled.} Sex. ..You know what, I-I'd better pass on the game. I think I'm just gonna go home and think about my ex-wife and her lesbian lover.
	\switchcolumn
	\charactername{罗斯：}今天是卡罗尔和我第一次…… 发生肉体关系的日子。\notmain{乔伊一脸困惑}就是上床。…… 算了，这比赛我还是不去了。我想回家想想我的前妻和她的女同性恋伴侣。
	\switchcolumn*
	\charactername{Joey:} The hell with hockey, let's all do that!
	\switchcolumn
	\charactername{乔伊：}冰球算个屁，我们都跟你一起想！
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{trying to stop Ross leaving} C'mon, Ross! You, me, Joey, ice, guys' night out, c'mon, whaddya say, big guy, \ennotmain{Pretending to punch him in the stomach.} Huh? Huh? Huh?
	\switchcolumn
	\charactername{钱德勒：}\notmain{试图拦住罗斯}别啊，罗斯！你、我、乔伊，冰场，男生之夜，来吧，怎么样，大个子？\notmain{假装捶他肚子}嗯？嗯？嗯？
	\switchcolumn*
	\charactername{Ross:} What are you doing?
	\switchcolumn
	\charactername{罗斯：}你干嘛呢？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{stops} I have no idea.
	\switchcolumn
	\charactername{钱德勒：}\notmain{停下}我也不知道。
	\switchcolumn*
	\charactername{Joey:} C'mon, Ross!
	\switchcolumn
	\charactername{乔伊：}来吧，罗斯！
	\switchcolumn*
	\charactername{Ross:} Alright, alright, maybe it'll take my mind off it. Do you promise to buy me a big thumb finger?
	\switchcolumn
	\charactername{罗斯：}好吧好吧，也许能让我分心。你们能答应给我买个大手指道具吗？
	\switchcolumn*
	\charactername{Chandler:} You got it.
	\switchcolumn
	\charactername{钱德勒：}没问题。
	\switchcolumn*
	\ennotmain{Rachel runs up clutching an envelope.}
	\switchcolumn
	\notmain{瑞秋攥着一个信封跑过来}
	\switchcolumn*
	\charactername{Rachel:} Look-look-look-look-look, my first pay check! Look at the window, there's my name! Hi, me!
	\switchcolumn
	\charactername{瑞秋：}快看快看快看快看，我的第一份薪水！看这栏，有我的名字！嗨，自己！
	\switchcolumn*
	\charactername{Phoebe:} I remember the day I got my first pay check. There was a cave in in one of the mines, and eight people were killed.
	\switchcolumn
	\charactername{菲比：}我还记得我拿第一份薪水那天。有个矿井塌方了，八个人死了。
	\switchcolumn*
	\charactername{Monica:} Wow, you worked in a mine?
	\switchcolumn
	\charactername{莫妮卡：}哇，你以前在矿井工作？
	\switchcolumn*
	\charactername{Phoebe:} I worked in a Dairy Queen, why?
	\switchcolumn
	\charactername{菲比：}我在冰雪皇后打工啊，不然呢？
	\switchcolumn*
	\charactername{Rachel:} God, isn't this exciting? I earned this. I wiped tables for it, I steamed milk for it, and it was totally—\ennotmain{opens envelope}—not worth it. Who's FICA? Why's he getting all my money? I mean, what- Chandler, look at that.
	\switchcolumn
	\charactername{瑞秋：}天啊，这难道不激动人心吗？这是我挣来的。我擦桌子挣的，我热牛奶挣的，结果这完全 ——\notmain{打开信封}—— 不值啊。谁是联邦保险捐税法案\notmain{FICA}？他凭什么拿走我所有的钱？我是说，钱德勒，你看看。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{looking} Oh, this is not that bad.
	\switchcolumn
	\charactername{钱德勒：}\notmain{看了看}哦，没那么糟啦。
	\switchcolumn*
	\charactername{Joey:} Oh, you're fine, yeah, for a first job.
	\switchcolumn
	\charactername{乔伊：}哦，你这挺好的，对第一份工作来说。
	\switchcolumn*
	\charactername{Ross:} You can totally, totally live on this.
	\switchcolumn
	\charactername{罗斯：}你完全完全能靠这个活下去。
	\switchcolumn*
	\charactername{Monica:} Yeah, yeah.
	\switchcolumn
	\charactername{莫妮卡：}是啊是啊。
	\switchcolumn*
	\charactername{Ross:} Oh, by the way, great service tonight.
	\switchcolumn
	\charactername{罗斯：}哦对了，今晚服务超棒。
	\switchcolumn*
	\charactername{All:} Oh! Yeah!
	\switchcolumn
	\charactername{众人：}哦！是啊！
	\switchcolumn*
	\ennotmain{They all get their wallets out and give generous tips.}
	\switchcolumn
	\notmain{所有人都拿出钱包，给了丰厚的小费}
	\switchcolumn*
	\charactername{Guys:} Hockey! \ennotmain{They go to leave but are blocked by three of Rachel's friends, Leslie, Kiki, and Joanne. The guys pause to stare at them.} Hockey! Hockey. \ennotmain{The guys.}
	\switchcolumn
	\charactername{男生们：}冰球！\notmain{他们正要走，却被瑞秋的三个朋友莱斯利、琪琪和乔安妮拦住。男生们停下来盯着她们看。}冰球！冰球！\notmain{赶紧离开}
	\switchcolumn*
	\charactername{Leslie:} \ennotmain{looking around} Rachel?
	\switchcolumn
	\charactername{莱斯利：}\notmain{四处张望}瑞秋？
	\switchcolumn*
	\charactername{Rachel:} Oh my God! \ennotmain{Rachel, Leslie, Kiki, and Joanne all scream and hug each other.}
	\switchcolumn
	\charactername{瑞秋：}哦我的天！\notmain{瑞秋、莱斯利、琪琪和乔安妮尖叫着拥抱在一起}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Phoebe} I swear I've seen birds do this on Wild Kingdom.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对菲比说}我发誓我在《动物世界》里见过鸟这么做。
	\switchcolumn*
	\charactername{Rachel:} What are you guys doing here?
	\switchcolumn
	\charactername{瑞秋：}你们怎么在这儿？
	\switchcolumn*
	\charactername{Kiki:} Well, we were in the city shopping, and your mom said you work here, aaand it's true!
	\switchcolumn
	\charactername{琪琪：}我们来城里逛街，你妈妈说你在这儿上班，而且居然是真的！
	\switchcolumn*
	\charactername{Joanne:} Look at you in the apron. You look like you're in a play.
	\switchcolumn
	\charactername{乔安妮：}看你穿围裙的样子，好像在演话剧哦。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{to a pregnant Leslie} Look at you, you are so big I can't believe it!
	\switchcolumn
	\charactername{瑞秋：}\notmain{对怀孕的莱斯利说}看你，肚子都这么大了，真不敢相信！
	\switchcolumn*
	\charactername{Leslie:} I know. I know! I'm a duplex.
	\switchcolumn
	\charactername{莱斯利：}我知道！我知道！我简直像个双层公寓。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{to Joanne} So what's going on with you?
	\switchcolumn
	\charactername{瑞秋：}\notmain{对乔安妮说}你最近怎么样？
	\switchcolumn*
	\charactername{Joanne:} Well, guess who my dad's making partner in his firm? \ennotmain{She points to herself and they all scream again.}
	\switchcolumn
	\charactername{乔安妮：}猜猜我爸爸要让谁当他公司的合伙人？\notmain{她指着自己，几人又尖叫起来}
	\switchcolumn*
	\charactername{Kiki:} And while we're on the subject of news.. \ennotmain{She holds up her finger to show off her engagement ring and they all scream again.}
	\switchcolumn
	\charactername{琪琪：}既然说到新闻……\notmain{她举起手指炫耀订婚戒指，几人再次尖叫}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{to Monica} Look, look, I have elbows! \ennotmain{They scream.}
	\switchcolumn
	\charactername{菲比：}\notmain{对莫妮卡说}快看快看，我有胳膊肘！\notmain{两人也跟着尖叫}
	\switchcolumn*
	\sense{Scene: A Street, Chandler and Joey are kicking a can to each other.}
	\switchcolumn
	\sense{场景：一条街上，钱德勒和乔伊互相踢着一个罐子}
	\switchcolumn*
	\charactername{Chandler:} ...Poulet passes it up to Leetch! \ennotmain{Passes it to Joey.}
	\switchcolumn
	\charactername{钱德勒：}…… 普莱耶把球传给利奇！\notmain{把罐子踢给乔伊}
	\switchcolumn*
	\charactername{Joey:} Leetch spots Messier in the crease- there's the pass! \ennotmain{He kicks it to Ross, but Ross is staring into a shop window.}
	\switchcolumn
	\charactername{乔伊：}利奇看到米西耶在球门区 —— 传球！\notmain{他把罐子踢给罗斯，但罗斯正盯着商店橱窗}
	\switchcolumn*
	\charactername{Chandler:} We'll take a brief time out while Messier stops to look at some women's shoes.
	\switchcolumn
	\charactername{钱德勒：}暂停一下，米西耶\notmain{罗斯}停下来看女鞋了。
	\switchcolumn*
	\charactername{Ross:} Carol was wearing boots just like those the night that we- we first- y'know. Fact, she, uh- she never took'em off, 'cause we-we- \ennotmain{off Chandler's look} Sorry. Sorry.
	\switchcolumn
	\charactername{罗斯：}卡罗尔那晚穿的靴子就跟这个一模一样 —— 我们第一次 —— 你懂的。其实，她，呃 —— 她一直没脱下来，因为我们 ——\notmain{看到钱德勒的表情}抱歉，抱歉。
	\switchcolumn*
	\ennotmain{They walk on. Chandler and Joey start to talk but Ross stops and whines.}
	\switchcolumn
	\notmain{他们继续往前走，钱德勒和乔伊正要说话，罗斯却停下来抱怨}
	\switchcolumn*
	\charactername{Joey:} What?
	\switchcolumn
	\charactername{乔伊：}怎么了？
	\switchcolumn*
	\charactername{Ross:} Peach pit.
	\switchcolumn
	\charactername{罗斯：}桃核。
	\switchcolumn*
	\charactername{Chandler:} Yes, Bunny?
	\switchcolumn
	\charactername{钱德勒：}怎么了，小兔子？\notmain{调侃}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{points} Peach pit. That night we, uh- we had-
	\switchcolumn
	\charactername{罗斯：}\notmain{指着}桃核。那晚我们，呃 —— 我们吃了 ——
	\switchcolumn*
	\charactername{Joey:} -Peaches?
	\switchcolumn
	\charactername{乔伊：}—— 桃子？
	\switchcolumn*
	\charactername{Ross:} Actually, nectarines, but basically...
	\switchcolumn
	\charactername{罗斯：}其实是油桃，但差不多……
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{to Joey} Could've been a peach.
	\switchcolumn
	\charactername{钱德勒：}\notmain{对乔伊说}说不定就是桃子呢。
	\switchcolumn*
	\charactername{Ross:} Then, uh, then we got dressed, and I-I... I walked her to the- \ennotmain{looks up, realises, and points} -the bus stop... I'm fine.
	\switchcolumn
	\charactername{罗斯：}然后，呃，然后我们穿好衣服，我 —— 我送她到 ——\notmain{抬头意识到，指着}—— 公交站…… 我没事。
	\switchcolumn*
	\charactername{Joey:} Hey, that woman's got an ass like Carol's! \ennotmain{They turn to stare at him.} What? Thought we were trying to find stuff.
	\switchcolumn
	\charactername{乔伊：}嘿，那个女人的屁股跟卡罗尔的好像！\notmain{两人转头瞪着他}怎么了？我以为我们在找跟她有关的东西呢。
	\switchcolumn*
	\sense{Scene: Central Perk, Rachel, Leslie, Kiki, and Joanne are talking.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，瑞秋、莱斯利、琪琪和乔安妮在聊天}
	\switchcolumn*
	\charactername{Rachel:} So c'mon, you guys, tell me all the dirt!
	\switchcolumn
	\charactername{瑞秋：}快，你们快告诉我所有八卦！
	\switchcolumn*
	\charactername{Kiki:} Well, the biggest news is still you dumping Barry at the altar!
	\switchcolumn
	\charactername{琪琪：}最大的新闻还是你在圣坛上甩了巴里那件事！
	\switchcolumn*
	\charactername{Joanne:} Alright. Let's talk reality for a second.
	\switchcolumn
	\charactername{乔安妮：}好了，咱们说点实际的。
	\switchcolumn*
	\charactername{Rachel:} Okay.
	\switchcolumn
	\charactername{瑞秋：}好啊。
	\switchcolumn*
	\charactername{Joanne:} When are you coming home?
	\switchcolumn
	\charactername{乔安妮：}你什么时候回家啊？
	\switchcolumn*
	\charactername{Rachel:} What? Guys, I'm not.
	\switchcolumn
	\charactername{瑞秋：}什么？我不回去了。
	\switchcolumn*
	\charactername{Joanne:} C'mon, this is us.
	\switchcolumn
	\charactername{乔安妮：}别这样，我们可是好姐妹啊。
	\switchcolumn*
	\charactername{Rachel:} I'm not! This is what I'm doing now. I've got this job-
	\switchcolumn
	\charactername{瑞秋：}我真不回去了！这就是我现在要做的事。我有工作了 ——
	\switchcolumn*
	\charactername{Kiki:} Waitressing?
	\switchcolumn
	\charactername{琪琪：}服务员？
	\switchcolumn*
	\charactername{Rachel:} Okay, I'm not just waitressing. I'm.. I, um... I write the specials on the specials board, and, uh... and I, uh... I take the uh dead flowers out of the vase... Oh, and, um, sometimes Artelle lets me put the little chocolate blobbies on the cookies.
	\switchcolumn
	\charactername{瑞秋：}好吧，我不只是服务员。我还…… 我，嗯…… 我会在特色菜单板上写当日特色，还有，呃…… 我会把花瓶里的枯花换掉…… 哦对了，有时候阿特尔会让我在饼干上放巧克力小碎块。
	\switchcolumn*
	\charactername{Leslie:} Well. Your mom didn't tell us about the blobbies.
	\switchcolumn
	\charactername{莱斯利：}好吧。你妈妈可没跟我们说巧克力碎块这事。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Phoebe and Monica are in pajamas and Monica is making something in the blender as Rachel enters.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，菲比和莫妮卡穿着睡衣，莫妮卡在搅拌机里做东西，瑞秋走进来}
	\switchcolumn*
	\charactername{Monica:} Hey, Rach. How was it with your friends? \ennotmain{She and Phoebe scream.} Okay! How would you like some Tiki Death Punch? \ennotmain{She pours the contents of the blender into some glasses.}
	\switchcolumn
	\charactername{莫妮卡：}嘿，瑞秋。跟你朋友玩得怎么样？\notmain{她和菲比尖叫}好了！来点提基夺命潘趣酒怎么样？\notmain{她把搅拌机里的东西倒进杯子里}
	\switchcolumn*
	\charactername{Rachel:} What's that?
	\switchcolumn
	\charactername{瑞秋：}这是什么？
	\switchcolumn*
	\charactername{Monica:} Weeeell, it's rum, and-
	\switchcolumn
	\charactername{莫妮卡：}嗯，是朗姆酒，还有 ——
	\switchcolumn*
	\charactername{Rachel:} Okay. \ennotmain{Grabs the blender and starts to drink.}
	\switchcolumn
	\charactername{瑞秋：}行。\notmain{拿起搅拌机直接喝起来}
	\switchcolumn*
	\charactername{Monica:} We thought since Phoebe was staying over tonight we'd have kinda like a slumber party thing. We got some trashy magazines, we got cookie dough, we got Twister... \ennotmain{The phone rings and Monica answers it.}
	\switchcolumn
	\charactername{莫妮卡：}我们想着菲比今晚住这儿，就搞个睡衣派对。我们买了些八卦杂志，还有曲奇面团，还有扭扭乐……\notmain{电话响了，莫妮卡接起}
	\switchcolumn*
	\charactername{Phoebe:} Ooh! Ooh! And I brought Operation! But, um, I lost the tweezers, so we can't operate. But we can prep the guy!
	\switchcolumn
	\charactername{菲比：}哦！哦！我还带了 “外科手术” 游戏！不过，嗯，我把镊子弄丢了，所以没法做手术。但我们可以给病人做术前准备！
	\switchcolumn*
	\charactername{Monica:} Uh, Rach, it's the Visa card people.
	\switchcolumn
	\charactername{莫妮卡：}呃，瑞秋，是信用卡公司的人。
	\switchcolumn*
	\charactername{Rachel:} Oh, God, ask them what they want.
	\switchcolumn
	\charactername{瑞秋：}哦天啊，问问他们有什么事。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{on phone} Could you please tell me what this is in reference to? \ennotmain{Listens} Yes, hold on. \ennotmain{To Rachel} Um, they say there's been some unusual activity on your account.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对着电话}能请问一下这是关于什么事吗？\notmain{听着}好的，稍等。\notmain{对瑞秋说}嗯，他们说你的账户有异常交易。
	\switchcolumn*
	\charactername{Rachel:} But I haven't used my card in weeks!
	\switchcolumn
	\charactername{瑞秋：}可我好几个星期都没⽤过卡了！
	\switchcolumn*
	\charactername{Monica:} That is the unusual activity. Look, they just wanna see if you're okay.
	\switchcolumn
	\charactername{莫妮卡：}这就是异常交易啊。他们就是想确认你是否安好。
	\switchcolumn*
	\charactername{Rachel:} They wanna know if I'm okay. Okay.. they wanna know if I'm okay, okay, let's see. Well, let's see, the FICA guys took all my money, everyone I know is either getting married, or getting promoted, or getting pregnant, and I'm getting coffee! And it's not even for me! So if that sounds like I'm okay, okay, then you can tell them I'm okay, okay?
	\switchcolumn
	\charactername{瑞秋：}他们想知道我好不好？好吧…… 他们想知道我好不好，行，那我说说。联邦保险捐税法案的人把我钱都拿走了，我认识的人不是结婚就是升职，要么就是怀孕，而我却在端咖啡！还不是给我自己端！所以如果这听起来算好的话，那你就告诉他们我很好，行吗？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{pauses then on the phone} Uh- Rachel has left the building, can you call back?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{停顿了一下，对着电话}呃 —— 瑞秋现在不在，你能稍后再打来吗？
	\switchcolumn*
	\charactername{Rachel:} Alright, c'mon! \ennotmain{Miserably} Let's play Twister!
	\switchcolumn
	\charactername{瑞秋：}好了，来吧！\notmain{沮丧地}我们玩扭扭乐！
	\switchcolumn*
	\sense{Scene: Madison Square Garden, the guys are trying to find their seats.}
	\switchcolumn
	\sense{场景：麦迪逊广场花园，男生们在找座位}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{squeezing past people} Sorry, sorry... Uh-oh.
	\switchcolumn
	\charactername{罗斯：}\notmain{挤过人群}抱歉，抱歉…… 哦不。
	\switchcolumn*
	\charactername{Chandler:} What? There was ice there that night with Carol? Plastic seats? Four thousand angry Pittsburgh fans?
	\switchcolumn
	\charactername{钱德勒：}怎么了？那晚你和卡罗尔也在有冰的地方？还是塑料座位？还有四千个愤怒的匹兹堡球迷？
	\switchcolumn*
	\charactername{Ross:} No, actually I was just saying it looks like we're not sitting together. But now you mention it, there was ice there that night... It was the first frost...
	\switchcolumn
	\charactername{罗斯：}不是，我只是说我们好像不能坐在一起。不过你这么一说，那晚确实有冰…… 那是第一次霜冻……
	\switchcolumn*
	\charactername{Joey:} C'mon, sit. Just sit down, sit.
	\switchcolumn
	\charactername{乔伊：}来吧，坐下。赶紧坐下。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, they're all hanging out in the living room.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，三人在客厅里待着}
	\switchcolumn*
	\charactername{Monica:} You should feel great about yourself! You're doing this amazing independence thing!
	\switchcolumn
	\charactername{莫妮卡：}你应该为自己感到骄傲！你正在实现了不起的独立呢！
	\switchcolumn*
	\charactername{Rachel:} Monica, what is so amazing? I gave up, like, everything. And for what?
	\switchcolumn
	\charactername{瑞秋：}莫妮卡，有什么了不起的？我放弃了所有的一切。结果呢？
	\switchcolumn*
	\charactername{Phoebe:} You are just like Jack.
	\switchcolumn
	\charactername{菲比：}你就像杰克。
	\switchcolumn*
	\charactername{Rachel:} ...Jack from downstairs?
	\switchcolumn
	\charactername{瑞秋：}…… 楼下的杰克？
	\switchcolumn*
	\charactername{Phoebe:} No, Jack and the Beanstalk.
	\switchcolumn
	\charactername{菲比：}不是，《杰克与魔豆》里的杰克。
	\switchcolumn*
	\charactername{Monica:} Ah, the other Jack.
	\switchcolumn
	\charactername{莫妮卡：}啊，另一个杰克。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, right! See, he gave up something, but then he got those magic beans. And then he woke up, and there was this, this big plant outside his window, full of possibilities and stuff.. And he lived in a village, and you live in the Village..
	\switchcolumn
	\charactername{菲比：}对呀！你看，他放弃了一样东西，但后来得到了魔豆。然后他醒来，窗外就长出了一棵大树，充满了各种可能…… 而且他住在村子里，你住在格林威治村\notmain{纽约的一个区}……
	\switchcolumn*
	\charactername{Rachel:} Okay, but Pheebs, Pheebs, Jack gave up a cow, I gave up an orthodontist. Okay, I-I-I know, I know I didn't love him-
	\switchcolumn
	\charactername{瑞秋：}好吧，但是菲比，杰克放弃的是一头牛，我放弃的是一个牙医。好吧，我知道我不爱他 ——
	\switchcolumn*
	\charactername{Phoebe:} Oh, see, Jack did love the cow.
	\switchcolumn
	\charactername{菲比：}哦，可杰克爱那头牛啊。
	\switchcolumn*
	\charactername{Rachel:} But see, it was a plan. Y'know, it was clear. It was figured out, and now everything's just kinda like...
	\switchcolumn
	\charactername{瑞秋：}但那是一个计划啊。你懂的，一切都很明确，都安排好了，可现在一切都变得……
	\switchcolumn*
	\charactername{Phoebe:} Floopy?
	\switchcolumn
	\charactername{菲比：}乱糟糟的？
	\switchcolumn*
	\charactername{Rachel:} Yeah.
	\switchcolumn
	\charactername{瑞秋：}对。
	\switchcolumn*
	\charactername{Monica:} So what, you're not the only one. I mean, half the time we don't know where we're going. You've just gotta figure at some point it's all gonna come together, and it's just gonna be... un-floopy.
	\switchcolumn
	\charactername{莫妮卡：}那又怎样，不止你一个人这样。我们大部分时间也不知道自己要往哪儿去。你只要相信，总有一天一切都会好起来，变得…… 不那么乱糟糟的。
	\switchcolumn*
	\charactername{Phoebe:} Oh, like that's a word.
	\switchcolumn
	\charactername{菲比：}哦，这也算个词啊。
	\switchcolumn*
	\charactername{Rachel:} Okay, but Monica, what if- what if it doesn't come together?
	\switchcolumn
	\charactername{瑞秋：}好吧，但是莫妮卡，如果 —— 如果一切都好不起来怎么办？
	\switchcolumn*
	\charactername{Monica:} ...Pheebs?
	\switchcolumn
	\charactername{莫妮卡：}…… 菲比？
	\switchcolumn*
	\charactername{Phoebe:} Oh, well... 'cause.... you just... I don't like this question.
	\switchcolumn
	\charactername{菲比：}哦，这个嘛…… 因为…… 你就是…… 我不喜欢这个问题。
	\switchcolumn*
	\charactername{Rachel:} Okay, see, see, you guys, what if we don't get magic beans? I mean, what if all we've got are.. beans?
	\switchcolumn
	\charactername{瑞秋：}好吧，你们看，如果我们得不到魔豆怎么办？我的意思是，如果我们只有…… 普通的豆子呢？
	\switchcolumn*
	\sense{Scene: Madison Square Garden, the guys are watching the game.}
	\switchcolumn
	\sense{场景：麦迪逊广场花园，男生们在看比赛}
	\switchcolumn*
	\charactername{Ross:} Get him! GET HIM! Get him! Get- YESSS! Not laughing now, are ya pal!
	\switchcolumn
	\charactername{罗斯：}拦住他！拦住他！拦住他！好 —— 耶！现在不笑了吧，伙计！
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{to Ross} See buddy, that's all you need, a bunch of toothless guys hitting each other with sticks.
	\switchcolumn
	\charactername{钱德勒：}\notmain{对罗斯说}看吧兄弟，你就需要这个，一群没牙的家伙拿着棍子互相打。
	\switchcolumn*
	\charactername{Ross:} Pass it! Pass it!
	\switchcolumn
	\charactername{罗斯：}传球！传球！
	\switchcolumn*
	\charactername{Chandler:} He's open!
	\switchcolumn
	\charactername{钱德勒：}没人防守他！
	\switchcolumn*
	\charactername{All:} Shoot! Shoot! Shoot!
	\switchcolumn
	\charactername{众人：}射门！射门！射门！
	\switchcolumn*
	\ennotmain{The player shoots and the puck flies off the rink and hits Ross in the face. Chandler looks concerned until he notices...}
	\switchcolumn
	\notmain{球员射门，冰球飞出场外，砸在了罗斯脸上。钱德勒一开始很担心，后来注意到……}
	\switchcolumn*
	\charactername{Chandler:} Hey, look, we're on that TV thing!
	\switchcolumn
	\charactername{钱德勒：}嘿，快看，我们上电视了！
	\switchcolumn*
	\ennotmain{Chandler and Joey hold the puck and wave at the TV thing.}
	\switchcolumn
	\notmain{钱德勒和乔伊举着冰球对着电视挥手}
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: An Emergency Room, Chandler and Joey are leading Ross in.}
	\switchcolumn
	\sense{场景：急诊室，钱德勒和乔伊扶着罗斯走进来}
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{to the receptionist}'Scuse me.
	\switchcolumn
	\charactername{钱德勒：}\notmain{对 receptionist 说}打扰一下。
	\switchcolumn*
	\charactername{Receptionist:} \ennotmain{holds up her hand—she is on the phone} It says to call this number if you're not completely satisfied with this candy bar. Well, I'm not completely satisfied.
	\switchcolumn
	\charactername{接待员：}\notmain{举起手，她正在打电话}包装上说如果对这根巧克力棒不完全满意就打这个电话。好吧，我确实不完全满意。
	\switchcolumn*
	\charactername{Chandler:} Listen, it's kind of an emergency. Well, I guess you know that, or we'd be in the predicament room. \ennotmain{The receptionist glares at him.}
	\switchcolumn
	\charactername{钱德勒：}听着，情况有点紧急。我猜你也看出来了，不然我们就去 “困境室” 了\notmain{调侃急诊室 emergency room}。\notmain{接待员瞪了他一眼}
	\switchcolumn*
	\charactername{Receptionist:} \ennotmain{on phone} Hold on. \ennotmain{To Chandler} Fill these out, sit over there. \ennotmain{Tosses him some forms.}
	\switchcolumn
	\charactername{接待员：}\notmain{对着电话}稍等。\notmain{对钱德勒说}填了这些表，坐在那边。\notmain{扔给他一些表格}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{jumping to his feet} Look, I don't wanna make any trouble, okay, but I'm in a lot of pain here, alright? My face is dented.
	\switchcolumn
	\charactername{罗斯：}\notmain{跳起来}听着，我不想找麻烦，但是我现在超级疼，好吗？我的脸都凹进去了。
	\switchcolumn*
	\charactername{Receptionist:} Well, you'll have to wait your turn.
	\switchcolumn
	\charactername{接待员：}那你也得排队等。
	\switchcolumn*
	\charactername{Joey:} Well, how long do you think it'll be?
	\switchcolumn
	\charactername{乔伊：}那你觉得要等多久？
	\switchcolumn*
	\charactername{Receptionist:} \ennotmain{sarcastic} Any minute now.
	\switchcolumn
	\charactername{接待员：}\notmain{讽刺地}马上就好。
	\switchcolumn*
	\charactername{Ross:} Hey, this- \ennotmain{she gives him a look and the guys back off} Heyy...
	\switchcolumn
	\charactername{罗斯：}嘿，你 ——\notmain{她瞪了他一眼，男生们退缩了}嘿……
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the slumber party continues.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，睡衣派对还在继续}
	\switchcolumn*
	\charactername{Rachel:} I'm so sorry, you guys. I didn't mean to bring you down.
	\switchcolumn
	\charactername{瑞秋：}对不起啊，你们。我不是故意扫大家兴的。
	\switchcolumn*
	\charactername{Monica:} No, you were right. I don't have a plan. \ennotmain{There's a knock on the door.}
	\switchcolumn
	\charactername{莫妮卡：}不，你说得对。我也没有计划。\notmain{有人敲门}
	\switchcolumn*
	\charactername{Pizza Guy:} \ennotmain{yelling from outside} Pizza guy!
	\switchcolumn
	\charactername{披萨外卖员：}\notmain{从外面大喊}披萨外卖！
	\switchcolumn*
	\charactername{Rachel:} Thank God. Food. \ennotmain{She goes to answer the door.}
	\switchcolumn
	\charactername{瑞秋：}谢天谢地，有吃的了。\notmain{她去开门}
	\switchcolumn*
	\charactername{Monica:} Phoebe?
	\switchcolumn
	\charactername{莫妮卡：}菲比？
	\switchcolumn*
	\charactername{Phoebe:} What?
	\switchcolumn
	\charactername{菲比：}怎么了？
	\switchcolumn*
	\charactername{Monica:} Do you have a plan?
	\switchcolumn
	\charactername{莫妮卡：}你有计划吗？
	\switchcolumn*
	\charactername{Phoebe:} I don't even have a 'pl'.
	\switchcolumn
	\charactername{菲比：}我连 “计” 都没有\notmain{调侃计划的 “计”}。
	\switchcolumn*
	\charactername{Pizza Guy:} Hi, one, uh, mushroom, green pepper and onion?
	\switchcolumn
	\charactername{披萨外卖员：}嗨，一份蘑菇、青椒和洋葱的披萨？
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{miserably} No, no, that's not what we ordered... We ordered a fat-free crust with extra cheese.
	\switchcolumn
	\charactername{瑞秋：}\notmain{沮丧地}不，不是，我们不是点的这个…… 我们点的是无脂饼底加双倍奶酪。
	\switchcolumn*
	\charactername{Pizza Guy:} Wait, you're not 'G.Stephanopoulos?' Man, my dad's gonna kill me!
	\switchcolumn
	\charactername{披萨外卖员：}等等，你不是乔治・斯特凡诺普洛斯？天啊，我爸会杀了我的！
	\switchcolumn*
	\charactername{Monica:} \ennotmain{leaping off of the couch and runs up} Wait! Did you say 'G.Stephanopoulos?'
	\switchcolumn
	\charactername{莫妮卡：}\notmain{从沙发上跳起来跑过去}等等！你说乔治・斯特凡诺普洛斯？
	\switchcolumn*
	\charactername{Pizza Guy:} Yeah. This one goes across the street, I must have given him yours. Oh, bonehead, bonehead!
	\switchcolumn
	\charactername{披萨外卖员：}对啊。这份是对面的，我肯定是把你的给他了。哦，我真是个笨蛋，笨蛋！
	\switchcolumn*
	\charactername{Monica:} Wait, was this a-a small mediterranean guy with curiously intelligent good looks?
	\switchcolumn
	\charactername{莫妮卡：}等等，是不是一个地中海长相、看起来特别聪明帅气的小个子男人？
	\switchcolumn*
	\charactername{Pizza Guy:} Yeah, that sounds about right.
	\switchcolumn
	\charactername{披萨外卖员：}是啊，差不多就是那样。
	\switchcolumn*
	\charactername{Monica:} Was he wearing a stunning blue suit?
	\switchcolumn
	\charactername{莫妮卡：}他是不是穿了一套超帅的蓝色西装？
	\switchcolumn*
	\charactername{Phoebe:} And-and a power tie?
	\switchcolumn
	\charactername{菲比：}还有 —— 还有一条权力领带？
	\switchcolumn*
	\charactername{Pizza Guy:} No, pretty much just a towel.
	\switchcolumn
	\charactername{披萨外卖员：}没有，基本上就只穿了条毛巾。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{staggered} Oh God.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{震惊地}哦天啊。
	\switchcolumn*
	\charactername{Pizza Guy:} So you guys want me to take this back?
	\switchcolumn
	\charactername{披萨外卖员：}那你们要我把这份拿回去吗？
	\switchcolumn*
	\charactername{Monica:} Are you nuts?! We've got George Stephanopoulos' pizza! \ennotmain{Rachel pays him, Monica grabs some binoculars, and runs to the window.}
	\switchcolumn
	\charactername{莫妮卡：}你疯了吗？！这可是乔治・斯特凡诺普洛斯的披萨！\notmain{瑞秋付钱，莫妮卡抓起望远镜跑到窗边}
	\switchcolumn*
	\charactername{Rachel:} Uh, Pheebs? Who's George Snuffalopagus?
	\switchcolumn
	\charactername{瑞秋：}呃，菲比？乔治・斯纳夫拉帕格斯是谁啊？\notmain{把名字说错了，说成了芝麻街里的角色}
	\switchcolumn*
	\charactername{Phoebe:} Big Bird's friend.
	\switchcolumn
	\charactername{菲比：}大鸟的朋友啊\notmain{芝麻街里的角色}。
	\switchcolumn*
	\charactername{Monica:} I see pizza!
	\switchcolumn
	\charactername{莫妮卡：}我看到披萨了！
	\switchcolumn*
	\charactername{Phoebe:} Oh, I wanna see! Lemme see! Lemme see! \ennotmain{She runs up and takes the binoculars.}
	\switchcolumn
	\charactername{菲比：}哦，我也想看！让我看看！让我看看！\notmain{她跑过去抢过望远镜}
	\switchcolumn*
	\charactername{Rachel:} Hello? Who are we spying on?
	\switchcolumn
	\charactername{瑞秋：}等等？我们在偷窥谁啊？
	\switchcolumn*
	\charactername{Monica:} White House adviser? Clinton's campaign guy? The one with the great hair, sexy smile, really cute butt?
	\switchcolumn
	\charactername{莫妮卡：}白宫顾问啊？克林顿的竞选顾问？那个头发超棒、笑容性感、屁股超可爱的家伙？
	\switchcolumn*
	\charactername{Rachel:} Oh, him, the little guy? Oh, I love him!
	\switchcolumn
	\charactername{瑞秋：}哦，是他啊，那个小个子？哦，我超喜欢他的！
	\switchcolumn*
	\charactername{Phoebe:} Ooh, wait.. wait, I see a woman.
	\switchcolumn
	\charactername{菲比：}哦，等等…… 等等，我看到一个女人。
	\switchcolumn*
	\charactername{Monica:} Please tell me it's his mother.
	\switchcolumn
	\charactername{莫妮卡：}拜托告诉我那是他妈妈。
	\switchcolumn*
	\charactername{Phoebe:} Definitely not his mother.
	\switchcolumn
	\charactername{菲比：}绝对不是他妈妈。
	\switchcolumn*
	\charactername{Monica:} Oh, no...
	\switchcolumn
	\charactername{莫妮卡：}哦，不……
	\switchcolumn*
	\charactername{Phoebe:} Oh, wait, she's walking across the floor.. she's walking.. she's walking.. she's going for the pizza- \ennotmain{Yelling} Hey, that's not for you, bitch! \ennotmain{Phoebe covers her mouth with her hand walks away from the window.}
	\switchcolumn
	\charactername{菲比：}哦，等等，她正穿过房间…… 她走着…… 走着…… 她要去拿披萨了 ——\notmain{大喊}嘿，那不是给你的，贱人！\notmain{菲比用手捂住嘴，离开窗边}
	\switchcolumn*
	\sense{Scene: The Emergency Room, Joey is miming hockey pucks hitting foreheads. Chandler realises it's getting tense and goes to the receptionist again.}
	\switchcolumn
	\sense{场景：急诊室，乔伊在模仿冰球砸到额头的样子。钱德勒觉得气氛有点紧张，又走向接待员}
	\switchcolumn*
	\charactername{Chandler:} Excuse me, look, we've been here for over an hour, and a lot of people less sick than my friend have gone in. I mean, that guy with the toe thing? Who's he sleeping with? \ennotmain{She slides the glass panel over and Chandler talks through it in a loud voice.} Oh, c'mon Dora, don't be mad... I know we both said some things we didn't mean, but that doesn't mean we still don't love each other. \ennotmain{To the waiting room.} Y'know, I feel like I've lost her.. \ennotmain{She slides the panel back, he turns, and it takes him by surprise.} Ba-!
	\switchcolumn
	\charactername{钱德勒：}打扰一下，我们已经在这儿等了一个多小时了，好多没我朋友严重的人都进去了。我是说，那个脚趾有问题的家伙？他是跟谁有关系啊？\notmain{她把玻璃挡板滑过来，钱德勒对着挡板大声说}哦，别这样，多拉\notmain{随便编的名字}，别生气嘛…… 我知道我们都说了些不该说的话，但这不代表我们不爱对方了。\notmain{对着候诊室的人说}你们知道吗，我感觉我失去她了……\notmain{她把挡板滑回去，他转过身，吓了一跳}啊！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the girls are all out on the balcony.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，三个女孩都在阳台上}
	\switchcolumn*
	\charactername{Monica:} Light still out?
	\switchcolumn
	\charactername{莫妮卡：}灯还关着吗？
	\switchcolumn*
	\charactername{Rachel:} Yeah.
	\switchcolumn
	\charactername{瑞秋：}嗯。
	\switchcolumn*
	\charactername{Monica:} Oh. Maybe they're- napping.
	\switchcolumn
	\charactername{莫妮卡：}哦。也许他们在 —— 打盹。
	\switchcolumn*
	\charactername{Rachel:} Oh please, they're having sex.
	\switchcolumn
	\charactername{瑞秋：}拜托，他们明明在做爱。
	\switchcolumn*
	\charactername{Monica and Phoebe:} Shut up!
	\switchcolumn
	\charactername{莫妮卡和菲比：}闭嘴！
	\switchcolumn*
	\charactername{Rachel:} So, whaddya think George is like?
	\switchcolumn
	\charactername{瑞秋：}你们觉得乔治怎么样？
	\switchcolumn*
	\charactername{Monica:} I think he's shy.
	\switchcolumn
	\charactername{莫妮卡：}我觉得他很害羞。
	\switchcolumn*
	\charactername{Phoebe:} Yeah?
	\switchcolumn
	\charactername{菲比：}是吗？
	\switchcolumn*
	\charactername{Monica:} Yeah. I think you have to draw him out. And then- when you do- he's a preppy animal.
	\switchcolumn
	\charactername{莫妮卡：}嗯。我觉得你得主动点引导他。然后 —— 等你引导他之后 —— 他就是个学院风的 “野兽”\notmain{意思是很会来事}。
	\switchcolumn*
	\sense{Scene: The Emergency Room, Ross is still going on about his first night with Carol.}
	\switchcolumn
	\sense{场景：急诊室，罗斯还在说他和卡罗尔第一次的那晚}
	\switchcolumn*
	\charactername{Ross:} I remember the moonlight coming through the window- and her face had the most incredible glow.
	\switchcolumn
	\charactername{罗斯：}我记得月光从窗户照进来 —— 她的脸散发着迷人的光芒。
	\switchcolumn*
	\charactername{Chandler:} Yes, the moon, the glow, the magical feeling, you did this part- Could I get some painkillers over here, please?
	\switchcolumn
	\charactername{钱德勒：}是啊，月光，光芒，神奇的感觉，这部分你已经说过了 —— 能给我来点止痛药吗？
	\switchcolumn*
	\charactername{Joey:} He's right, enough, already. What is the big deal about today? So you slept with her for the first time, so what? You slept with her for seven years after that.
	\switchcolumn
	\charactername{乔伊：}他说得对，够了，别说了。今天有什么大不了的？你第一次跟她上床而已，那又怎样？之后你们在一起七年呢。
	\switchcolumn*
	\charactername{Ross:} Look, it's just a little more complicated...
	\switchcolumn
	\charactername{罗斯：}情况没那么简单……
	\switchcolumn*
	\charactername{Chandler:} Well, what? What? What is it? That she left you? That she likes women? That she left you for another woman that likes women?
	\switchcolumn
	\charactername{钱德勒：}那到底是什么？是什么啊？她甩了你？她喜欢女人？她甩了你跟另一个喜欢女人的女人在一起？
	\switchcolumn*
	\charactername{Ross:} Little louder, okay, I think there's a man on the twelfth floor in a coma that didn't quite hear you...
	\switchcolumn
	\charactername{罗斯：}再大声点，好吗？我觉得十二楼有个昏迷的病人还没听清呢……
	\switchcolumn*
	\charactername{Chandler:} Then what?
	\switchcolumn
	\charactername{钱德勒：}那到底是什么？
	\switchcolumn*
	\charactername{Ross:} My first time with Carol was... \ennotmain{He mumbles the last part}
	\switchcolumn
	\charactername{罗斯：}我和卡罗尔的第一次……\notmain{最后几个字含糊不清}
	\switchcolumn*
	\charactername{Joey:} What?
	\switchcolumn
	\charactername{乔伊：}什么？
	\switchcolumn*
	\charactername{Ross:} It was my first time.
	\switchcolumn
	\charactername{罗斯：}那也是我的第一次\notmain{做爱}。
	\switchcolumn*
	\charactername{Joey:} With Carol? \ennotmain{Ross gives him a look.} Oh.
	\switchcolumn
	\charactername{乔伊：}和卡罗尔？\notmain{罗斯瞪了他一眼}哦。
	\switchcolumn*
	\charactername{Chandler:} So in your whole life, you've only been with one—\ennotmain{He gets a look too}—oh.
	\switchcolumn
	\charactername{钱德勒：}所以你这辈子，只和一个 ——\notmain{也收到罗斯的眼神}—— 哦。
	\switchcolumn*
	\charactername{Joey:} Whoah, boy, hockey was a big mistake! There was a whole bunch of stuff we could've done tonight!
	\switchcolumn
	\charactername{乔伊：}哇哦，兄弟，今晚去看冰球真是大错特错！我们今晚本来可以做很多别的事的！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the girls are still out on the balcony.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，女孩们还在阳台上}
	\switchcolumn*
	\charactername{Monica:} Okay. Okay, I got one. Do you remember that vegetarian pate that I made that you loved so much?
	\switchcolumn
	\charactername{莫妮卡：}好吧。好吧，我有件事要说。还记得我做的那个素肉酱吗？你们以前超爱吃的。
	\switchcolumn*
	\charactername{Phoebe:} Uh-huh.
	\switchcolumn
	\charactername{菲比：}嗯。
	\switchcolumn*
	\charactername{Monica:} Well, unless goose is a vegetable...ha haaaah!
	\switchcolumn
	\charactername{莫妮卡：}其实里面有鹅肉，除非鹅是蔬菜…… 哈哈哈！
	\switchcolumn*
	\charactername{Phoebe:} Oh! Oh! Oh! Okay, fine, fine. Now I don't feel so bad about sleeping with Jason Hurley.
	\switchcolumn
	\charactername{菲比：}哦！哦！哦！好吧，算你狠。那我跟杰森・赫利上床的事，现在也不用觉得愧疚了。
	\switchcolumn*
	\charactername{Monica:} What?! You slept with Jason?
	\switchcolumn
	\charactername{莫妮卡：}什么？！你跟杰森上床了？
	\switchcolumn*
	\charactername{Phoebe:} You'd already broken up.
	\switchcolumn
	\charactername{菲比：}你们那时候已经分手了啊。
	\switchcolumn*
	\charactername{Rachel:} How long?
	\switchcolumn
	\charactername{瑞秋：}分手多久之后？
	\switchcolumn*
	\charactername{Phoebe:} A couple hours.
	\switchcolumn
	\charactername{菲比：}几个小时吧。
	\switchcolumn*
	\charactername{Monica:} Oh, that's nice!
	\switchcolumn
	\charactername{莫妮卡：}哦，可真够意思的！
	\switchcolumn*
	\charactername{Rachel:} Okay, okay, okay, I got one! \ennotmain{She sits up and the cushion she was leaning against falls off of the balcony.} Anyway- The valentine Tommy Rollerson left in your locker was really from me.
	\switchcolumn
	\charactername{瑞秋：}好了好了好了，我也有件事要说！\notmain{她坐起来，靠着的垫子从阳台掉了下去}不管怎样 —— 汤米・罗勒森放在你储物柜里的情人节卡片，其实是我送的。
	\switchcolumn*
	\charactername{Monica:} Excuse me?!
	\switchcolumn
	\charactername{莫妮卡：}你说什么？！
	\switchcolumn*
	\charactername{Rachel:} Hello? Like he was really gonna send you one? \ennotmain{To Phoebe} She was a big girl.
	\switchcolumn
	\charactername{瑞秋：}拜托？你觉得他真的会给你送卡片吗？\notmain{对菲比说}她那时候块头可大了。
	\switchcolumn*
	\charactername{Monica:} Really. Well, at least 'big girls' don't pee in their pants in seventh grade!
	\switchcolumn
	\charactername{莫妮卡：}是吗。至少 “大块头女生” 不会在七年级尿裤子！
	\switchcolumn*
	\charactername{Rachel:} I was laughing! You made me laugh! \ennotmain{Monica and Rachel start to squabble}
	\switchcolumn
	\charactername{瑞秋：}我是因为笑才尿的！是你让我笑成那样的！\notmain{莫妮卡和瑞秋开始吵起来}
	\switchcolumn*
	\charactername{Phoebe:} There he is! There he is!
	\switchcolumn
	\charactername{菲比：}他在那儿！他在那儿！
	\switchcolumn*
	\charactername{Monica:} Where?
	\switchcolumn
	\charactername{莫妮卡：}哪儿？
	\switchcolumn*
	\charactername{Phoebe:} Right- where we've been looking all night!
	\switchcolumn
	\charactername{菲比：}就在 —— 我们看了一整晚的地方！
	\switchcolumn*
	\charactername{Rachel:} He is so cute!
	\switchcolumn
	\charactername{瑞秋：}他太帅了！
	\switchcolumn*
	\charactername{Monica:} Oh, George, baby, drop the towel!
	\switchcolumn
	\charactername{莫妮卡：}哦，乔治，宝贝，把毛巾拿掉！
	\switchcolumn*
	\charactername{All:} Yeah, drop it! Drop the towel! Please drop the—\ennotmain{pause}—wowww.
	\switchcolumn
	\charactername{众人：}是啊，拿掉！把毛巾拿掉！拜托拿掉 ——\notmain{停顿}—— 哇哦。
	\switchcolumn*
	\sense{Scene: The Emergency Room, Ross is absent.}
	\switchcolumn
	\sense{场景：急诊室，罗斯不在}
	\switchcolumn*
	\charactername{Joey:} Man. Can you believe he's only had sex with one woman?
	\switchcolumn
	\charactername{乔伊：}天呐。你能相信他这辈子只跟一个女人上过床吗？
	\switchcolumn*
	\charactername{Chandler:} I think it's great. Y'know, it's sweet, it's romantic...
	\switchcolumn
	\charactername{钱德勒：}我觉得挺好的。很甜蜜，很浪漫……
	\switchcolumn*
	\charactername{Joey:} Really?
	\switchcolumn
	\charactername{乔伊：}真的吗？
	\switchcolumn*
	\charactername{Chandler:} No, you kidding? The guy's a freak.. \ennotmain{Ross enters off camera}
	\switchcolumn
	\charactername{钱德勒：}不，你开玩笑呢？这家伙简直是个怪胎……\notmain{罗斯从镜头外走进来}
	\switchcolumn*
	\charactername{Both:} Hey, buddy.
	\switchcolumn
	\charactername{两人：}嘿，兄弟。
	\switchcolumn*
	\charactername{Ross:} Hi. \ennotmain{He is wearing a piece of steel bandaged to his nose. He tosses some forms onto reception desk.}
	\switchcolumn
	\charactername{罗斯：}嗨。\notmain{他鼻子上缠着一块金属片绷带，把一些表格扔到接待台上}
	\switchcolumn*
	\charactername{Receptionist:} \ennotmain{sarcastic} Oh, that's attractive.
	\switchcolumn
	\charactername{接待员：}\notmain{讽刺地}哦，真帅气。
	\switchcolumn*
	\charactername{Chandler:} Oh, I thought you were great in Silence of the Lambs. Oh come on, admit it! All things considered, you had fun tonight.
	\switchcolumn
	\charactername{钱德勒：}哦，我觉得你在《沉默的羔羊》里演得超棒\notmain{调侃他的造型像汉尼拔}。拜托，承认吧！总的来说，你今晚玩得挺开心的。
	\switchcolumn*
	\charactername{Ross:} Fun? Where was the fun? Tell me specifically, which part was the fun part? Where's my puck?
	\switchcolumn
	\charactername{罗斯：}开心？开心在哪儿？具体说说，哪部分开心了？我的冰球呢？
	\switchcolumn*
	\charactername{Joey:} Oh, ah- the kid has it.
	\switchcolumn
	\charactername{乔伊：}哦，啊 —— 被那个小孩拿走了。
	\switchcolumn*
	\charactername{Ross:} The kid...? \ennotmain{To the kid} Excuse me, uh, that's, that's my puck.
	\switchcolumn
	\charactername{罗斯：}小孩……？\notmain{对小孩说}打扰一下，那个，那个是我的冰球。
	\switchcolumn*
	\charactername{Kid:} I found it. Finders keepers, losers weepers. \ennotmain{Ross looks at Chandler for help.}
	\switchcolumn
	\charactername{小孩：}我找到的。谁找到就是谁的，输家哭鼻子。\notmain{罗斯看向钱德勒求助}
	\switchcolumn*
	\charactername{Chandler:} You gotta do it, man.
	\switchcolumn
	\charactername{钱德勒：}你得自己要回来，兄弟。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{to the kid} Oh yeah? Well, I'm rubber, you're glue, whatever—\ennotmain{to Chandler}—can't do it. \ennotmain{to the kid} Listen, uh- gimme back my puck.
	\switchcolumn
	\charactername{罗斯：}\notmain{对小孩说}哦是吗？那我是橡胶，你是胶水，所有的坏话都 ——\notmain{对钱德勒说}我说不出口。\notmain{对小孩说}听着，呃 —— 把冰球还给我。
	\switchcolumn*
	\charactername{Kid:} No.
	\switchcolumn
	\charactername{小孩：}不。
	\switchcolumn*
	\charactername{Ross:} 'Yes', how about. C'mere. Gimme!
	\switchcolumn
	\charactername{罗斯：}“好” 怎么样。过来。给我！
	\switchcolumn*
	\charactername{Kid:} No! No! \ennotmain{They start to fight over it.}
	\switchcolumn
	\charactername{小孩：}不！不！\notmain{两人开始争抢冰球}
	\switchcolumn*
	\charactername{Receptionist:} Hey! Hey! No rough holding in my ER!
	\switchcolumn
	\charactername{接待员：}嘿！嘿！在我的急诊室里不准打闹！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{tries to snatch it from the kid} GIVE ME MY PUCK!! \ennotmain{but it flies out of his grasp and knocks out the receptionist}
	\switchcolumn
	\charactername{罗斯：}\notmain{试图从小孩手里抢过来}把我的冰球还给我！！\notmain{但冰球从他手里飞出去，砸晕了接待员}
	\switchcolumn*
	\charactername{Ross:} ...Now that was fun.
	\switchcolumn
	\charactername{罗斯：}…… 现在这才叫开心。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Joey and the girls are playing Twister.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，乔伊和女孩们在玩扭扭乐}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{Doing the spinning} Okay, Monica: Right foot red.
	\switchcolumn
	\charactername{罗斯：}\notmain{转转盘}好了，莫妮卡：右脚踩红色。
	\switchcolumn*
	\charactername{Monica:} Could've played Monopoly, but nooooo.
	\switchcolumn
	\charactername{莫妮卡：}本来可以玩大富翁的，偏不……
	\switchcolumn*
	\ennotmain{There's a knock on the door, Chandler opens it, and silently hands back the cushion.}
	\switchcolumn
	\notmain{有人敲门，钱德勒打开门，默默地把之前掉下去的垫子还回去}
	\switchcolumn*
	\charactername{Chandler:} Thanks. \ennotmain{The guy nods and leaves}
	\switchcolumn
	\charactername{钱德勒：}谢谢。\notmain{对方点点头离开}
	\switchcolumn*
	\charactername{Ross:} Okay, Pheebs: Right hand blue. \ennotmain{Phoebe has to bend over.} Good. \ennotmain{Joey stares at her butt appreciatively}
	\switchcolumn
	\charactername{罗斯：}好了，菲比：右手踩蓝色。\notmain{菲比不得不弯下腰}很好。\notmain{乔伊赞赏地盯着她的屁股}
	\switchcolumn*
	\ennotmain{The phone rings and Chandler answers it.}
	\switchcolumn
	\notmain{电话响了，钱德勒接起}
	\switchcolumn*
	\charactername{Chandler:} Hello? Oh, uh, Rachel, it's the Visa card people.
	\switchcolumn
	\charactername{钱德勒：}喂？哦，呃，瑞秋，是信用卡公司的人。
	\switchcolumn*
	\charactername{Rachel:} Oh, okay. Will you take my place?
	\switchcolumn
	\charactername{瑞秋：}哦，好。你能替我一下吗？
	\switchcolumn*
	\charactername{Chandler:} Alright. \ennotmain{on phone} Yes, this is Rachel.
	\switchcolumn
	\charactername{钱德勒：}好。\notmain{对着电话}是的，我是瑞秋。
	\switchcolumn*
	\charactername{Rachel:} Nooo! \ennotmain{She grabs the phone and Chandler takes her place on the mat.} \ennotmain{On phone} Hello? \ennotmain{Listens} Oh, yeah, no, I know, I-I haven't been using it much. \ennotmain{Listens} Oh, well, thanks, but, I'm okay, really.
	\switchcolumn
	\charactername{瑞秋：}不！\notmain{她抢过电话，钱德勒在垫子上替她的位置}\notmain{对着电话}喂？\notmain{听着}哦，是啊，我知道，我不怎么用这张卡。\notmain{听着}哦，谢谢关心，不过我没事，真的。
	\switchcolumn*
	\charactername{Ross:} Green. To the green.
	\switchcolumn
	\charactername{罗斯：}绿色。踩绿色。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{on phone} I've got magic beans. \ennotmain{Listens} Never-never mind.
	\switchcolumn
	\charactername{瑞秋：}\notmain{对着电话}我有魔豆哦。\notmain{听着}当我没说，当我没说。
	\switchcolumn*
	\charactername{Chandler:} To the left, to the left- aww! \ennotmain{They all collapse}
	\switchcolumn
	\charactername{钱德勒：}往左，往左 —— 啊！\notmain{所有人都倒在地上}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{on phone} Ohhh... I'm fine.
	\switchcolumn
	\charactername{瑞秋：}\notmain{对着电话}哦…… 我没事。
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage