\begin{paracol}{2}
	\sense{Scene: Central Perk, all six are there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，六人悉数在场}
	\switchcolumn*
	\charactername{Monica:} Would you let it go? It's not that big a deal.
	\switchcolumn
	\charactername{莫妮卡：}别纠结了行不行？没那么大不了的。
	\switchcolumn*
	\charactername{Ross:} Not that big a deal? It's amazing. Ok, you just reach in there, there's one little maneuver, and bam, a bra right out the sleeve. All right, as far as I'm concerned, there is nothing a guy can do that even comes close. Am I right?
	\switchcolumn
	\charactername{罗斯：}没那么大不了？这简直太神了好吗！你就伸手进去，稍微动一下，砰，内衣就从袖子里出来了。反正我觉得，男人做的任何事都没法比这个厉害。我说得对不对？
	\switchcolumn*
	\charactername{Rachel:} Come on! You guys can pee standing up.
	\switchcolumn
	\charactername{瑞秋：}拜托！你们男人能站着尿尿啊。
	\switchcolumn*
	\charactername{Chandler:} We can? All right, I'm tryin' that.
	\switchcolumn
	\charactername{钱德勒：}我们可以？行，我这就试试去。
	\switchcolumn*
	\charactername{Joey:} Ok, you know what blows my mind? Women can see breasts any time they want. You just look down and there they are. How you get any work done is beyond me.
	\switchcolumn
	\charactername{乔伊：}好吧，你们知道什么让我震惊吗？女人随时都能看到自己的胸。低头一看就有了。我真搞不懂你们怎么还能好好工作。
	\switchcolumn*
	\charactername{Phoebe:} Oh, ok, you know what I don't get? The way guys can do so many mean things, and then not even care.
	\switchcolumn
	\charactername{菲比：}哦，那你们知道我搞不懂什么吗？男人能做那么多刻薄的事，然后居然毫不在乎。
	\switchcolumn*
	\ennotmain{Long pause.}
	\switchcolumn
	\notmain{长时间沉默}
	\switchcolumn*
	\charactername{Ross:} Multiple orgasms!
	\switchcolumn
	\charactername{罗斯：}多重高潮啊！
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, all are there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，众人仍在}
	\switchcolumn*
	\charactername{Chandler:} So, Saturday night, the big night, date night, Saturday night, Sat-ur-day night!
	\switchcolumn
	\charactername{钱德勒：}周六晚上啊，重要的夜晚，约会之夜，周六晚上，周——六——晚——上！
	\switchcolumn*
	\charactername{Joey:} No plans, huh?
	\switchcolumn
	\charactername{乔伊：}没安排啊？
	\switchcolumn*
	\charactername{Chandler:} Not a one.
	\switchcolumn
	\charactername{钱德勒：}毛都没有。
	\switchcolumn*
	\charactername{Ross:} Not even, say, breaking up with Janice?
	\switchcolumn
	\charactername{罗斯：}比如说……跟詹妮丝分手也没安排？
	\switchcolumn*
	\charactername{Chandler:} Oh, right, right, shut up.
	\switchcolumn
	\charactername{钱德勒：}哦对哦对，闭嘴吧你。
	\switchcolumn*
	\charactername{Monica:} Chandler, nobody likes breaking up with someone. You just gotta do it.
	\switchcolumn
	\charactername{莫妮卡：}钱德勒，没人喜欢跟别人分手。但你总得去做啊。
	\switchcolumn*
	\charactername{Chandler:} No, I know, but it's just so hard, you know? I mean, you're sitting there with her, she has no idea what's happening, and then you finally get up the courage to do it, and there's the horrible awkward moment when you've handed her the note.
	\switchcolumn
	\charactername{钱德勒：}我知道，但真的太难了，你懂吗？你跟她坐在一起，她完全不知道要发生什么，然后你终于鼓起勇气说了，递完分手纸条那尴尬的瞬间简直要命。
	\switchcolumn*
	\charactername{Joey:} Why do you have to break up with her? Be a man, just stop calling.
	\switchcolumn
	\charactername{乔伊：}干嘛非得跟她分手啊？像个男人点，别再联系她不就行了。
	\switchcolumn*
	\charactername{Phoebe:} You know, if you want, I'll do it with you.
	\switchcolumn
	\charactername{菲比：}如果你愿意，我可以陪你一起。
	\switchcolumn*
	\charactername{Chandler:} Oh, thanks, but I think she'd feel like we're gangin' up on her.
	\switchcolumn
	\charactername{钱德勒：}哦谢谢，但我觉得她会觉得我们在联手欺负她。
	\switchcolumn*
	\charactername{Phoebe:} No, I mean you break up with Janice and I'll break up with Tony.
	\switchcolumn
	\charactername{菲比：}不是，我的意思是你跟詹妮丝分手，我跟托尼分手。
	\switchcolumn*
	\charactername{Ross:} Tony?
	\switchcolumn
	\charactername{罗斯：}托尼？
	\switchcolumn*
	\charactername{Monica:} Oh, you're breaking up with Tony?
	\switchcolumn
	\charactername{莫妮卡：}哦，你要跟托尼分手啊？
	\switchcolumn*
	\charactername{Phoebe:} Yeah, I know, he's sweet, but it's just not fun anymore, you know? I don't know if it's me, or his hunger strike, or, I don't know.
	\switchcolumn
	\charactername{菲比：}是啊，他是挺好的，但就是没意思了，懂吗？我不知道是我的问题，还是他在绝食的缘故，或者别的什么。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{waitressing} Does anybody want anything else?
	\switchcolumn
	\charactername{瑞秋：}\notmain{端着盘子}有人还想要点什么吗？
	\switchcolumn*
	\charactername{Ross:} Oh, yeah, last week you had a wonderful, nutty, chocolatey kind of a cakey pie thing. \ennotmain{Rachel gives him a dirty look} Nothing, just, just, I'm fine.
	\switchcolumn
	\charactername{罗斯：}哦对了，上周你们有一款超好吃的，有坚果味、巧克力味的，像蛋糕又像派的东西。\notmain{瑞秋恶狠狠地瞪了他一眼}没什么没什么，我没事。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{to Rachel} What's the matter? Why so scrunchy?
	\switchcolumn
	\charactername{菲比：}\notmain{对瑞秋}怎么了？脸怎么皱成一团？
	\switchcolumn*
	\charactername{Rachel:} It's my father. He wants to give me a Mercedes convertible.
	\switchcolumn
	\charactername{瑞秋：}是我爸。他想给我一辆奔驰敞篷车。
	\switchcolumn*
	\charactername{Ross:} That guy, he burns me up.
	\switchcolumn
	\charactername{罗斯：}那家伙，真让我气炸了。
	\switchcolumn*
	\charactername{Rachel:} Yeah, well, it's a Mercedes if I move back home. Oh, it was horrible. He called me young lady.
	\switchcolumn
	\charactername{瑞秋：}是啊，但前提是我得搬回家住。太过分了，他居然叫我“小姑娘”。
	\switchcolumn*
	\charactername{Chandler:} Ooh, I hate when my father calls me that.
	\switchcolumn
	\charactername{钱德勒：}哦，我爸这么叫我时我也超讨厌。
	\switchcolumn*
	\charactername{Monica:} Did he give you that whole "You're-not-up-to-this" thing again?
	\switchcolumn
	\charactername{莫妮卡：}他又跟你说那套“你根本不行”的鬼话了？
	\switchcolumn*
	\charactername{Rachel:} Oh, yeah, yeah. Actually, I got the extended disco version, with three choruses of "You'll never make it on your own".
	\switchcolumn
	\charactername{瑞秋：}可不是嘛。而且还是迪斯科加长版，反复唱三遍“你一个人根本活不下去”。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{rhythmically} Uh-huh, uh-huh.
	\switchcolumn
	\charactername{菲比：}\notmain{跟着节奏}嗯嗯，嗯嗯。
	\switchcolumn*
	\ennotmain{Angela, a beautiful woman in a tight dress, enters.}
	\switchcolumn
	\notmain{安吉拉，一位穿紧身裙的美女走进来}
	\switchcolumn*
	\charactername{Angela:} Hi, Joey.
	\switchcolumn
	\charactername{安吉拉：}嗨，乔伊。
	\switchcolumn*
	\charactername{Joey:} My god, Angela.
	\switchcolumn
	\charactername{乔伊：}我的天，安吉拉。
	\switchcolumn*
	\ennotmain{Angela takes a seat at the counter.}
	\switchcolumn
	\notmain{安吉拉在吧台旁坐下}
	\switchcolumn*
	\charactername{Monica:} Wow, being dumped by you obviously agrees with her.
	\switchcolumn
	\charactername{莫妮卡：}哇，被你甩了之后她过得明显更好了嘛。
	\switchcolumn*
	\charactername{Phoebe:} Are you gonna go over there?
	\switchcolumn
	\charactername{菲比：}你要过去吗？
	\switchcolumn*
	\charactername{Joey:} No, yeah, no, ok, but not yet. I don't wanna seem too eager. One Mississippi, two Mississippi, three Mississippi. That seems pretty cool. \ennotmain{he walks over to her} Hey, Angela.
	\switchcolumn
	\charactername{乔伊：}不，要去，不过再等等。我可不想显得太急切。一密西西比，二密西西比，三密西西比。这样显得酷多了。\notmain{走向她}嘿，安吉拉。
	\switchcolumn*
	\charactername{Angela:} \ennotmain{casually} Joey.
	\switchcolumn
	\charactername{安吉拉：}\notmain{漫不经心}乔伊。
	\switchcolumn*
	\charactername{Joey:} You look good.
	\switchcolumn
	\charactername{乔伊：}你气色不错。
	\switchcolumn*
	\charactername{Angela:} That's because I'm wearing a dress that accents my boobs.
	\switchcolumn
	\charactername{安吉拉：}那是因为我穿了件能凸显胸部的裙子。
	\switchcolumn*
	\charactername{Joey:} You don't say.
	\switchcolumn
	\charactername{乔伊：}是吗。
	\switchcolumn*
	\ennotmain{Cut to Ross and Rachel, talking next to one of the tables.}
	\switchcolumn
	\notmain{镜头切到罗斯和瑞秋，在一张桌子旁交谈}
	\switchcolumn*
	\charactername{Ross:} So, uh, Rachel, what are you, uh, what're you doing tonight?
	\switchcolumn
	\charactername{罗斯：}那个，瑞秋，你今晚……今晚有什么安排吗？
	\switchcolumn*
	\charactername{Rachel:} Oh, big glamour night. Me and Monica at Laundorama.
	\switchcolumn
	\charactername{瑞秋：}哦，超迷人的夜晚呢。我和莫妮卡要去自助洗衣店。
	\switchcolumn*
	\charactername{Ross:} Oh, you uh, you wanna hear a freaky coincidence? Guess who's doing laundry there too?
	\switchcolumn
	\charactername{罗斯：}哦，那个，你想听听一个诡异的巧合吗？猜猜谁也要去那儿洗衣服？
	\switchcolumn*
	\charactername{Rachel:} Who?
	\switchcolumn
	\charactername{瑞秋：}谁啊？
	\switchcolumn*
	\charactername{Ross:} Me. Was that not clear? Hey, why don't, um, why don't I just join you both, here?
	\switchcolumn
	\charactername{罗斯：}我啊。不够明显吗？那个，要不我跟你们一起去？
	\switchcolumn*
	\charactername{Rachel:} Don't you have a laundry room in your building?
	\switchcolumn
	\charactername{瑞秋：}你公寓楼里没有洗衣房吗？
	\switchcolumn*
	\charactername{Ross:} Yes, I do have a laundry room in my building, um, but there's a.... rat problem. Apparently they're attracted to the dryer sheets, and they're goin' in fine, but they're comin' out all.... fluffy. Anyway, say, sevenish?
	\switchcolumn
	\charactername{罗斯：}有啊，我楼里是有洗衣房，但是……有老鼠问题。显然老鼠被烘干纸吸引了，进去的时候好好的，出来的时候全……毛茸茸的。不管怎样，七点左右怎么样？
	\switchcolumn*
	\charactername{Rachel:} Sure.
	\switchcolumn
	\charactername{瑞秋：}行啊。
	\switchcolumn*
	\ennotmain{Cut back to Joey and Angela at the counter.}
	\switchcolumn
	\notmain{镜头切回吧台旁的乔伊和安吉拉}
	\switchcolumn*
	\charactername{Angela:} Forget it Joey. I'm with Bob now.
	\switchcolumn
	\charactername{安吉拉：}别想了乔伊，我现在跟鲍勃在一起了。
	\switchcolumn*
	\charactername{Joey:} Bob? Who the hell's Bob?
	\switchcolumn
	\charactername{乔伊：}鲍勃？鲍勃是谁啊？
	\switchcolumn*
	\charactername{Angela:} Bob is great. He's smart, he's sophisticated, and he has a real job. You, you go on three auditions a month and you call yourself an actor, but Bob...
	\switchcolumn
	\charactername{安吉拉：}鲍勃超棒的。他聪明、有品位，还有一份正经工作。你呢，一个月就三次试镜，还自称演员，而鲍勃……
	\switchcolumn*
	\charactername{Joey:} Come on, we were great together. And not just at the fun stuff, but like, talking too.
	\switchcolumn
	\charactername{乔伊：}拜托，我们以前多好啊。不只是玩得开心，聊天也很投机啊。
	\switchcolumn*
	\charactername{Angela:} Yeah, well, sorry, Joe. You said let's just be friends, so guess what?
	\switchcolumn
	\charactername{安吉拉：}是啊，抱歉了乔。是你说我们只做朋友的，所以你猜怎么着？
	\switchcolumn*
	\charactername{Joey:} What?
	\switchcolumn
	\charactername{乔伊：}怎么着？
	\switchcolumn*
	\charactername{Angela:} We're just friends.
	\switchcolumn
	\charactername{安吉拉：}我们现在就只是朋友。
	\switchcolumn*
	\charactername{Joey:} Fine, fine, so, why don't the four of us go out and have dinner together tonight? You know, as friends?
	\switchcolumn
	\charactername{乔伊：}行吧行吧，那我们四个今晚一起吃个饭怎么样？就当朋友聚会？
	\switchcolumn*
	\charactername{Angela:} What four of us?
	\switchcolumn
	\charactername{安吉拉：}哪四个人？
	\switchcolumn*
	\charactername{Joey:} You know, you and Bob, and me and my girlfriend, uh, uh, Monica.
	\switchcolumn
	\charactername{乔伊：}就是你和鲍勃，还有我和我女朋友，那个……那个莫妮卡。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's apartment, Joey is there, trying to convince Monica to pose as his girlfriend. His plan is to hook Monica up with Angela's boyfriend Bob and then take Angela back for himself.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，乔伊在这儿，试图说服莫妮卡假扮他的女朋友。他的计划是把莫妮卡介绍给安吉拉的男友鲍勃，然后自己重新追回安吉拉}
	\switchcolumn*
	\charactername{Joey:} Monica, I'm tellin' you, this guy is perfect for you.
	\switchcolumn
	\charactername{乔伊：}莫妮卡，我跟你说，这家伙超适合你。
	\switchcolumn*
	\charactername{Monica:} Forget it. Not after your cousin who could belch the alphabet.
	\switchcolumn
	\charactername{莫妮卡：}免了吧。自从上次你那个能打嗝背字母表的表弟之后，我可不敢了。
	\switchcolumn*
	\charactername{Joey:} Come on. This guy's great. His name's Bob. He's Angela's... brother. He's smart, he's sophisticated, and he has a real job. Me, I go on three auditions a month and call myself an actor, but Bob is...
	\switchcolumn
	\charactername{乔伊：}拜托。这家伙真的很棒。他叫鲍勃，是安吉拉的……弟弟。他聪明、有品位，还有一份正经工作。我呢，一个月三次试镜就自称演员，但鲍勃他……
	\switchcolumn*
	\charactername{Monica:} \ennotmain{looking out window} Oh, god help us.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{看向窗外}哦，我的天。
	\switchcolumn*
	\charactername{Joey:} What?
	\switchcolumn
	\charactername{乔伊：}怎么了？
	\switchcolumn*
	\charactername{Monica:} Ugly Naked Guy's laying kitchen tile. Eww!
	\switchcolumn
	\charactername{莫妮卡：}裸体丑男在铺厨房瓷砖呢。呃！
	\switchcolumn*
	\charactername{Joey:} Eww! Look, I'm asking a favor here. If I do this for her brother, maybe Angela will come back to me.
	\switchcolumn
	\charactername{乔伊：}呃！拜托，我在求你帮忙呢。如果我帮了她弟弟，也许安吉拉就会回到我身边了。
	\switchcolumn*
	\charactername{Monica:} What's going on here? You go out with tons of girls.
	\switchcolumn
	\charactername{莫妮卡：}你搞什么啊？你平时约会的女生多了去了。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{proud} I know, but, I made a huge mistake. I never should have broken up with her. Will you help me? Please?
	\switchcolumn
	\charactername{乔伊：}\notmain{得意地}我知道，但我犯了个大错。我当初就不该跟她分手的。你帮帮我好吗？求你了？
	\switchcolumn*
	\sense{Scene: Ross' apartment, Chandler is over.}
	\switchcolumn
	\sense{场景：罗斯的公寓，钱德勒在这儿}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{on phone} Ok, bye. \ennotmain{hangs up} Well, Monica's not coming, it's just gonna be me and Rachel.
	\switchcolumn
	\charactername{罗斯：}\notmain{打电话}好的，再见。\notmain{挂电话}莫妮卡不来了，就我和瑞秋两个人。
	\switchcolumn*
	\charactername{Chandler:} Oh. Well, hold on camper, are you sure you've thought this thing through?
	\switchcolumn
	\charactername{钱德勒：}哦。等等啊小伙子，你确定你想清楚了？
	\switchcolumn*
	\charactername{Ross:} It's laundry. The thinking through is minimal.
	\switchcolumn
	\charactername{罗斯：}就是洗个衣服而已，没什么好想的。
	\switchcolumn*
	\charactername{Chandler:} It's just you and Rachel, just the two of you? This is a date. You're going on a date.
	\switchcolumn
	\charactername{钱德勒：}就你和瑞秋，就你们俩？这就是约会啊。你这是去约会呢。
	\switchcolumn*
	\charactername{Ross:} Nuh-uh.
	\switchcolumn
	\charactername{罗斯：}才不是。
	\switchcolumn*
	\charactername{Chandler:} Yuh-huh.
	\switchcolumn
	\charactername{钱德勒：}就是。
	\switchcolumn*
	\charactername{Ross:} So what're you saying here? I should shave again, pick up some wine, what?
	\switchcolumn
	\charactername{罗斯：}那你意思是我该再刮个胡子，买点红酒什么的？
	\switchcolumn*
	\charactername{Chandler:} Well, you may wanna rethink the dirty underwear. This is basically the first time she's gonna see your underwear—you want it to be dirty?
	\switchcolumn
	\charactername{钱德勒：}嗯，你可能得重新考虑下那条脏内裤。这基本上是她第一次看到你的内裤——你想让她看到脏的？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{sheepish} No.
	\switchcolumn
	\charactername{罗斯：}\notmain{不好意思地}不想。
	\switchcolumn*
	\charactername{Chandler:} Oh, and uh, the fabric softener?
	\switchcolumn
	\charactername{钱德勒：}哦对了，还有衣物柔顺剂？
	\switchcolumn*
	\charactername{Ross:} Ok, ok, now what is wrong with my Snuggles? What, it says I'm a sensitive, warm kinda guy, you know, like a warm, fuzzy bear. Ok, I can pick something else up on the way.
	\switchcolumn
	\charactername{罗斯：}好好好，我的舒洁柔顺剂怎么了？这说明我是个敏感又温暖的人，就像一只毛茸茸的暖熊。行吧，我路上再买点别的。
	\switchcolumn*
	\charactername{Chandler:} There you go.
	\switchcolumn
	\charactername{钱德勒：}这就对了。
	\switchcolumn*
	\sense{Scene: A fancy restaurant, Joey and Monica are there, meeting Angela and Bob, who Monica thinks is Angela's brother.}
	\switchcolumn
	\sense{场景：一家高档餐厅，乔伊和莫妮卡在此等候安吉拉和鲍勃——莫妮卡以为鲍勃是安吉拉的弟弟}
	\switchcolumn*
	\charactername{Monica:} Thank you. So what does this Bob guy look like? Is he tall? Short?
	\switchcolumn
	\charactername{莫妮卡：}谢谢。那这个鲍勃长什么样啊？高还是矮？
	\switchcolumn*
	\charactername{Joey:} Yep.
	\switchcolumn
	\charactername{乔伊：}嗯。
	\switchcolumn*
	\charactername{Monica:} Which?
	\switchcolumn
	\charactername{莫妮卡：}哪个啊？
	\switchcolumn*
	\charactername{Joey:} Which what?
	\switchcolumn
	\charactername{乔伊：}哪个什么？
	\switchcolumn*
	\charactername{Monica:} You've never met Bob, have you?
	\switchcolumn
	\charactername{莫妮卡：}你根本没见过鲍勃，对吧？
	\switchcolumn*
	\charactername{Joey:} No, but he's...
	\switchcolumn
	\charactername{乔伊：}没见过，但他……
	\switchcolumn*
	\charactername{Monica:} Oh my god, Joey, for all we know this guy could be horribly...
	\switchcolumn
	\charactername{莫妮卡：}我的天乔伊，说不定这家伙超级……
	\switchcolumn*
	\ennotmain{Angela and Bob walk in. Bob is good-looking.}
	\switchcolumn
	\notmain{安吉拉和鲍勃走进来，鲍勃长得很帅气}
	\switchcolumn*
	\charactername{Angela:} Hey, Joey.
	\switchcolumn
	\charactername{安吉拉：}嘿，乔伊。
	\switchcolumn*
	\charactername{Monica:} ...horribly attractive. I'll be shutting up now.
	\switchcolumn
	\charactername{莫妮卡：}……超级帅。我还是闭嘴吧。
	\switchcolumn*
	\sense{Scene: Central Perk, Chandler and Phoebe are there, both ready to break up with their significant others.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，钱德勒和菲比都准备好跟各自的伴侣分手}
	\switchcolumn*
	\charactername{Chandler:} Where are they? Where are they?
	\switchcolumn
	\charactername{钱德勒：}他们在哪儿？他们在哪儿？
	\switchcolumn*
	\charactername{Phoebe:} This is nice. We never do anything just the two of us.
	\switchcolumn
	\charactername{菲比：}这样挺好的。我们从来没就两个人一起做过什么事。
	\switchcolumn*
	\charactername{Chandler:} It's great. Maybe tomorrow we can rent a car and run over some puppies.
	\switchcolumn
	\charactername{钱德勒：}是啊，棒极了。说不定明天我们可以租辆车去轧小狗。
	\switchcolumn*
	\charactername{Phoebe:} Eww, I don't wanna do that.
	\switchcolumn
	\charactername{菲比：}呃，我可不想干这个。
	\switchcolumn*
	\ennotmain{Janice and Phoebe's boyfriend, Tony, walk in.}
	\switchcolumn
	\notmain{詹妮丝和菲比的男友托尼走进来}
	\switchcolumn*
	\charactername{Chandler:} Here we go.
	\switchcolumn
	\charactername{钱德勒：}来了来了。
	\switchcolumn*
	\charactername{Phoebe:} Ok, have a good break-up.
	\switchcolumn
	\charactername{菲比：}祝你分手顺利。
	\switchcolumn*
	\charactername{Chandler:} Hey, Janice.
	\switchcolumn
	\charactername{钱德勒：}嘿，詹妮丝。
	\switchcolumn*
	\charactername{Janice:} Oh, my god, I am so glad you called me. I had the most supremely awful day.
	\switchcolumn
	\charactername{詹妮丝：}哦我的天，你能打电话给我真是太好了。我今天过得糟透了。
	\switchcolumn*
	\charactername{Chandler:} Hey, that's not good. Can I get an espresso and a latte over here, please?
	\switchcolumn
	\charactername{钱德勒：}哦，那太糟了。麻烦给我来一杯浓缩咖啡和一杯拿铁，谢谢。
	\switchcolumn*
	\charactername{Janice:} We got the proofs back from that photo shoot, you know, the one with the little vegetables. Anyway, they pretty much sucked, so, I blew off the rest of the day, and I went shopping...\ennotmain{looks through her bags}... and I got you, I'm looking, I'm looking, I'm looking, I got you...
	\switchcolumn
	\charactername{詹妮丝：}我们拿到上次拍照的样片了，就是那个有小蔬菜道具的。反正拍得超级烂，所以我剩下的时间就翘班了，然后去购物了……\notmain{翻包里的东西}我给你买了个礼物，我找找，找找，找找，我给你买了……
	\switchcolumn*
	\ennotmain{Chandler sees Phoebe breaking up with Tony. She talks to him for a few seconds, hugs him, and then he leaves. Chandler is amazed how easy it was for her.}
	\switchcolumn
	\notmain{钱德勒看到菲比在跟托尼分手。她跟托尼说了几秒话，抱了抱他，然后托尼就走了。钱德勒惊讶于她分手居然这么容易}
	\switchcolumn*
	\charactername{Chandler:} What?
	\switchcolumn
	\charactername{钱德勒：}什么？
	\switchcolumn*
	\charactername{Janice:} What?
	\switchcolumn
	\charactername{詹妮丝：}怎么了？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{covering} What... did you get me there?
	\switchcolumn
	\charactername{钱德勒：}\notmain{掩饰}你……你给我买了什么？
	\switchcolumn*
	\charactername{Janice:} I got you...these. \ennotmain{pulls out a pair of socks}
	\switchcolumn
	\charactername{詹妮丝：}我给你买了……这个。\notmain{掏出一双袜子}
	\switchcolumn*
	\charactername{Chandler:} Bullwinkle socks. That's so sweet.
	\switchcolumn
	\charactername{钱德勒：}布尔温克尔\notmain{卡通角色}袜子。太贴心了。
	\switchcolumn*
	\charactername{Janice:} Well, I knew you had the Rockys, and so I figured, you know, you can wear Bullwinkle and Bullwinkle, or you can wear Rocky and Rocky,or, you can mix and match, moose and squirrel. Whatever you want.
	\switchcolumn
	\charactername{詹妮丝：}我知道你有洛奇\notmain{卡通角色}的袜子，所以我想，你可以穿两只布尔温克尔，或者两只洛奇，或者混搭，驼鹿和松鼠\notmain{两者为卡通搭档}。随你喜欢。
	\switchcolumn*
	\charactername{Chandler:} That's great.
	\switchcolumn
	\charactername{钱德勒：}真不错。
	\switchcolumn*
	\ennotmain{The drinks arrive, and Chandler downs his espresso in one gulp.}
	\switchcolumn
	\notmain{饮品端上来了，钱德勒一口干了浓缩咖啡}
	\switchcolumn*
	\charactername{Chandler:} Well, I'm gonna get another espresso. Can I get you another latte?
	\switchcolumn
	\charactername{钱德勒：}那个，我再去来一杯浓缩咖啡。你要再来一杯拿铁吗？
	\switchcolumn*
	\charactername{Janice:} \ennotmain{holding the full cup} No, no, I'm still working on mine.
	\switchcolumn
	\charactername{詹妮丝：}\notmain{举着还满的杯子}不用不用，我这杯还没喝完呢。
	\switchcolumn*
	\ennotmain{Chandler walks over to the counter where Phoebe is, and is asking her about the break-up.}
	\switchcolumn
	\notmain{钱德勒走到菲比所在的吧台，问她分手的事}
	\switchcolumn*
	\charactername{Chandler:} That's it?
	\switchcolumn
	\charactername{钱德勒：}就这样？
	\switchcolumn*
	\charactername{Phoebe:} Yeah, it was really hard.
	\switchcolumn
	\charactername{菲比：}是啊，可难了。
	\switchcolumn*
	\charactername{Chandler:} Oh, yeah, that hug looked pretty brutal.
	\switchcolumn
	\charactername{钱德勒：}哦是吗，那个拥抱看起来可“残忍”了。
	\switchcolumn*
	\charactername{Phoebe:} Ok, you weren't there.
	\switchcolumn
	\charactername{菲比：}好吧，你又不在场。
	\switchcolumn*
	\sense{Scene: The Launderama, Rachel is there, waiting for Ross. An old woman takes Rachel's clothes off the machine and begins loading it with her things.}
	\switchcolumn
	\sense{场景：自助洗衣店，瑞秋在等罗斯。一位老太太把瑞秋放在洗衣机上的衣服拿下来，开始往里面放自己的东西}
	\switchcolumn*
	\charactername{Woman:} Comin' through. Move, move.
	\switchcolumn
	\charactername{老太太：}借过借过。让让，让让。
	\switchcolumn*
	\charactername{Rachel:} Oh, 'scuse me. I was kinda using that machine.
	\switchcolumn
	\charactername{瑞秋：}哦，不好意思。我刚才正在用这台洗衣机呢。
	\switchcolumn*
	\charactername{Woman:} Yeah, well, now you're kinda not.
	\switchcolumn
	\charactername{老太太：}是啊，不过现在不用了。
	\switchcolumn*
	\charactername{Rachel:} But I saved it. I put my basket on top.
	\switchcolumn
	\charactername{瑞秋：}但我占了位置啊，我把洗衣篮放在上面了。
	\switchcolumn*
	\charactername{Woman:} Oh, I'm sorry, is that your basket? It's really pretty. Unfortunately, I don't see suds.
	\switchcolumn
	\charactername{老太太：}哦抱歉，这是你的篮子啊？真好看。可惜啊，我没看到泡沫。
	\switchcolumn*
	\charactername{Rachel:} What?
	\switchcolumn
	\charactername{瑞秋：}什么？
	\switchcolumn*
	\charactername{Woman:} No suds, no save. Ok?
	\switchcolumn
	\charactername{老太太：}没泡沫，就不算占位置。懂吗？
	\switchcolumn*
	\ennotmain{Ross arrives.}
	\switchcolumn
	\notmain{罗斯到了}
	\switchcolumn*
	\charactername{Ross:} What's goin' on?
	\switchcolumn
	\charactername{罗斯：}怎么回事？
	\switchcolumn*
	\charactername{Rachel:} Hi, uh, nothing. That horrible woman just took my machine.
	\switchcolumn
	\charactername{瑞秋：}嗨，没什么。那个讨厌的老太太抢了我的洗衣机。
	\switchcolumn*
	\charactername{Ross:} Was your basket on top?
	\switchcolumn
	\charactername{罗斯：}你把洗衣篮放在上面了吗？
	\switchcolumn*
	\charactername{Rachel:} Yeah, but, there were no suds.
	\switchcolumn
	\charactername{瑞秋：}放了啊，但就是没有泡沫嘛。
	\switchcolumn*
	\charactername{Ross:} So?
	\switchcolumn
	\charactername{罗斯：}那又怎样？
	\switchcolumn*
	\charactername{Rachel:} Well, you know, no suds, no save.
	\switchcolumn
	\charactername{瑞秋：}她说没泡沫就不算占位置。
	\switchcolumn*
	\charactername{Ross:} No suds? Excuse me, hold on a second. \ennotmain{to woman} That's my friend's machine.
	\switchcolumn
	\charactername{罗斯：}没泡沫？不好意思，等一下。\notmain{对老太太}这是我朋友的洗衣机。
	\switchcolumn*
	\charactername{Woman:} Hey, hey, hey, her stuff wasn't in it.
	\switchcolumn
	\charactername{老太太：}嘿，嘿，嘿，她的东西又没在里面。
	\switchcolumn*
	\charactername{Ross:} Hey, hey, hey, that's not the rule and you know it.
	\switchcolumn
	\charactername{罗斯：}嘿，嘿，嘿，这可不是规矩，你心里清楚。
	\switchcolumn*
	\ennotmain{The woman and Ross stare at each other. Finally she takes her stuff out of the machine and leaves.}
	\switchcolumn
	\notmain{老太太和罗斯对视了一会儿。最后她把自己的东西从洗衣机里拿出来走了}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{to the crowd in the laundromat} All right, show's over. Nothing to see here. \ennotmain{to Rachel} Ok, let's do laundry.
	\switchcolumn
	\charactername{罗斯：}\notmain{对洗衣店里的众人}好了，好戏结束了，没什么好看的。\notmain{对瑞秋}好了，我们洗衣服吧。
	\switchcolumn*
	\charactername{Rachel:} That was amazing. I can't even send back soup.
	\switchcolumn
	\charactername{瑞秋：}你太厉害了。我连退个汤都不敢。
	\switchcolumn*
	\charactername{Ross:} Well, that's because you're such a sweet, gentle, uh...Do you, uh, do you...Oh, hey, uh you must need detergent.
	\switchcolumn
	\charactername{罗斯：}那是因为你太善良太温柔了，那个……你是不是……哦对了，你肯定需要洗衣粉吧。
	\switchcolumn*
	\ennotmain{Ross pulls out a huge box of laundry detergent.}
	\switchcolumn
	\notmain{罗斯掏出一大盒洗衣粉}
	\switchcolumn*
	\charactername{Rachel:} What's that?
	\switchcolumn
	\charactername{瑞秋：}这是什么啊？
	\switchcolumn*
	\charactername{Ross:} Uberveiss. It's new, it's German, it's extra-tough.
	\switchcolumn
	\charactername{罗斯：}优倍洁\notmain{音译}。新款德国货，去污超强。
	\switchcolumn*
	\ennotmain{Rachel starts to load her clothes.}
	\switchcolumn
	\notmain{瑞秋开始往洗衣机里放衣服}
	\switchcolumn*
	\charactername{Ross:} Rach, do you uh, are you gonna separate those?
	\switchcolumn
	\charactername{罗斯：}瑞秋，你要……你要把衣服分开洗吗？
	\switchcolumn*
	\charactername{Rachel:} Oh god. Oh, am I being like a total laundry spaz? I mean, am I supposed to use like one machine for shirts and another machine for pants?
	\switchcolumn
	\charactername{瑞秋：}哦我的天。我是不是看起来像个洗衣小白？我的意思是，是不是得用一台洗衣机洗衬衫，另一台洗裤子啊？
	\switchcolumn*
	\charactername{Ross:} Rach, have you never done this before?
	\switchcolumn
	\charactername{罗斯：}瑞秋，你以前从没自己洗过衣服吗？
	\switchcolumn*
	\charactername{Rachel:} Well, not myself, but I know other people that have. Ok, you caught me. I'm a laundry virgin.
	\switchcolumn
	\charactername{瑞秋：}嗯，没自己洗过，但我知道别人会洗。好吧，被你发现了。我是洗衣处子\notmain{从没自己洗过衣服}。
	\switchcolumn*
	\charactername{Ross:} Uh, well, don't worry, I'll use the gentle cycle. Ok, um, basically you wanna use one machine for all your whites, a whole nother machine for colors, and a third for your uh, your uh, delicates, and that would be your bras and your under-panty things.
	\switchcolumn
	\charactername{罗斯：}哦，别担心，我用轻柔模式。那个，基本上你要把白色衣服放一台洗衣机，彩色衣服放另一台，第三台用来洗……洗贴身衣物，就是你的内衣和内裤之类的。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{holds a pair of panties in front of Ross} Ok, Well, what about these are white cotton panties. Would they go with whites or delicates?
	\switchcolumn
	\charactername{瑞秋：}\notmain{拿着一条白色棉质内裤在罗斯面前}那这个呢？白色棉质内裤。应该放白色衣服那堆还是贴身衣物那堆？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{visibly nervous} Uh, that, that, that would be a judgment call.
	\switchcolumn
	\charactername{罗斯：}\notmain{明显紧张}那个，那个，那个得看情况定。
	\switchcolumn*
	\sense{Scene: Fancy restaurant, Monica, Joey, Angela, and Bob are seated at the table.}
	\switchcolumn
	\sense{场景：高档餐厅，莫妮卡、乔伊、安吉拉和鲍勃已入座}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Joey} He is so cute. \ennotmain{to Angela and Bob} So, where did you guys grow up?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对乔伊}他太帅了。\notmain{对安吉拉和鲍勃}你们是在哪儿长大的啊？
	\switchcolumn*
	\charactername{Angela:} Brooklyn Heights.
	\switchcolumn
	\charactername{安吉拉：}布鲁克林高地。
	\switchcolumn*
	\charactername{Bob:} Cleveland.
	\switchcolumn
	\charactername{鲍勃：}克利夫兰。
	\switchcolumn*
	\charactername{Monica:} How, how did that happen?
	\switchcolumn
	\charactername{莫妮卡：}怎么……怎么会一个在那儿一个在这儿啊？
	\switchcolumn*
	\charactername{Joey:} Oh my god.
	\switchcolumn
	\charactername{乔伊：}我的天。
	\switchcolumn*
	\charactername{Monica:} What?
	\switchcolumn
	\charactername{莫妮卡：}怎么了？
	\switchcolumn*
	\charactername{Joey:} I suddenly had the feeling that I was falling. But I'm not.
	\switchcolumn
	\charactername{乔伊：}我突然有种要摔倒的感觉，但其实没有。
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Fancy restaurant, Joey and Bob are talking.}
	\switchcolumn
	\sense{场景：高档餐厅，乔伊和鲍勃在聊天}
	\switchcolumn*
	\charactername{Joey:} So, you and Angela, huh?
	\switchcolumn
	\charactername{乔伊：}你和安吉拉，是吧？
	\switchcolumn*
	\charactername{Bob:} Yep. Pretty much.
	\switchcolumn
	\charactername{鲍勃：}嗯，差不多吧。
	\switchcolumn*
	\charactername{Joey:} You're a lucky man. You know what I miss the most about her? That cute nibbly noise when she eats. Like a happy little squirrel, or a weasel.
	\switchcolumn
	\charactername{乔伊：}你真是个幸运的人。你知道我最怀念她什么吗？她吃东西时那种可爱的小口咀嚼声。就像一只开心的小松鼠，或者黄鼠狼。
	\switchcolumn*
	\charactername{Bob:} Huh, I never really noticed.
	\switchcolumn
	\charactername{鲍勃：}哈，我从来没注意过。
	\switchcolumn*
	\charactername{Joey:} Oh, yeah, yeah, listen for it.
	\switchcolumn
	\charactername{乔伊：}哦，真的，你仔细听听。
	\switchcolumn*
	\charactername{Bob:} Monica, Monica is great.
	\switchcolumn
	\charactername{鲍勃：}莫妮卡，莫妮卡人超好的。
	\switchcolumn*
	\charactername{Joey:} Yeah, but it's not gonna last. She's too much for me in bed. Sexually.
	\switchcolumn
	\charactername{乔伊：}是啊，但我们长不了。她在床上太热情了，我招架不住。性生活方面的。
	\switchcolumn*
	\sense{Scene: The ladies' bathroom at the restaurant, Monica and Angela are talking.}
	\switchcolumn
	\sense{场景：餐厅女洗手间，莫妮卡和安吉拉在聊天}
	\switchcolumn*
	\charactername{Monica:} I've gotta tell you, Bob is terrific.
	\switchcolumn
	\charactername{莫妮卡：}我得跟你说，鲍勃真的超棒。
	\switchcolumn*
	\charactername{Angela:} Yeah, isn't he?
	\switchcolumn
	\charactername{安吉拉：}是啊，可不是嘛？
	\switchcolumn*
	\charactername{Monica:} It is so great to meet a guy who is smart and funny, and has an emotional age beyond, like eight.
	\switchcolumn
	\charactername{莫妮卡：}能遇到一个聪明风趣、心理年龄超过八岁的男人真是太不容易了。
	\switchcolumn*
	\charactername{Angela:} You know what else? He's unbelievable in bed.
	\switchcolumn
	\charactername{安吉拉：}还有呢？他床上功夫超棒的。
	\switchcolumn*
	\charactername{Monica:} Wow. My brother never even told me when he lost his virginity.
	\switchcolumn
	\charactername{莫妮卡：}哇哦。我哥连他什么时候破处的都没跟我说过。
	\switchcolumn*
	\charactername{Angela:} Huh. That's nice.
	\switchcolumn
	\charactername{安吉拉：}哈，挺好的。
	\switchcolumn*
	\sense{Scene: Central Perk, Phoebe is coaching Chandler on how to break up with Janice.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，菲比在指导钱德勒怎么跟詹妮丝分手}
	\switchcolumn*
	\charactername{Phoebe:} Ok, you can do this. It's just like pulling off a Band-aid. Just do it really fast, and then the wound is exposed.
	\switchcolumn
	\charactername{菲比：}你可以的。就像撕创可贴一样，快刀斩乱麻，然后伤口就暴露出来了\notmain{比喻分手要干脆}。
	\switchcolumn*
	\ennotmain{Chandler walks back to couch, where Janice is.}
	\switchcolumn
	\notmain{钱德勒走回詹妮丝所在的沙发}
	\switchcolumn*
	\charactername{Chandler:} Janice. Hi, Janice. Ok, here we go. I don't think we should go out anymore. Janice.
	\switchcolumn
	\charactername{钱德勒：}詹妮丝。嗨，詹妮丝。好了，我要说了。我觉得我们不该再约会了。詹妮丝。
	\switchcolumn*
	\charactername{Janice:} All right. Well, there you go. \ennotmain{she gets extremely wound up, and begins to try and calm herself down} Stop it, stop it, stop it.
	\switchcolumn
	\charactername{詹妮丝：}好吧。行吧。\notmain{她情绪变得异常激动，开始试着平复自己}别这样，别这样，别这样。
	\switchcolumn*
	\sense{Scene: The laundromat.}
	\switchcolumn
	\sense{场景：自助洗衣店}
	\switchcolumn*
	\charactername{Rachel:} Ok, I know this is gonna sound really stupid, but I feel that if I can do this, you know, if I can actually do my own laundry, there isn't anything I can't do.
	\switchcolumn
	\charactername{瑞秋：}我知道这听起来可能很傻，但我觉得如果我能做到这个——如果我能自己洗好衣服，那我就没什么做不到的了。
	\switchcolumn*
	\charactername{Ross:} That does not sound stupid to me. You know, it's like the first time I had to make dinner for myself, after Carol left me? \ennotmain{the buzzer on the washer goes off} I'm sorry, that's all the time we have. Next on Ross...\ennotmain{opens up the washer} Uh-oh.
	\switchcolumn
	\charactername{罗斯：}这一点都不傻。你知道吗，就像卡萝离开我之后，我第一次自己做饭的时候？\notmain{洗衣机的蜂鸣器响了}抱歉，时间到。接下来请收看罗斯……\notmain{打开洗衣机}哦不。
	\switchcolumn*
	\charactername{Rachel:} What uh-oh?
	\switchcolumn
	\charactername{瑞秋：}怎么了？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{not wanting to tell her} Uh-oh, uh-oh, the laundry's done. It's, uh, it's a song. The laundry song that we sing. \ennotmain{singing} Uh-oh the laundry's done, uh-oh, uh-oh.
	\switchcolumn
	\charactername{罗斯：}\notmain{不想告诉她}哦啦哦啦，衣服洗好啦。这是……这是一首歌。我们唱的洗衣歌。\notmain{唱}哦啦衣服洗好啦，哦啦哦啦。
	\switchcolumn*
	\charactername{Rachel:} Ross, what's the matter?
	\switchcolumn
	\charactername{瑞秋：}罗斯，到底怎么了？
	\switchcolumn*
	\charactername{Ross:} Nothing, nothing. Lee-lo, the laundry's done.
	\switchcolumn
	\charactername{罗斯：}没什么没什么。哩咯，衣服洗好啦。
	\switchcolumn*
	\charactername{Rachel:} Come on, show me.
	\switchcolumn
	\charactername{瑞秋：}别装了，给我看看。
	\switchcolumn*
	\charactername{Ross:} All right, all right, it's just that you left a red sock in with all your whites, and now, everything's kinda pink.
	\switchcolumn
	\charactername{罗斯：}好吧好吧，就是你把一只红袜子和白色衣服放在一起洗了，现在所有衣服都有点粉了。
	\switchcolumn*
	\charactername{Rachel:} Oh, everything's pink.
	\switchcolumn
	\charactername{瑞秋：}哦，所有衣服都变粉了。
	\switchcolumn*
	\charactername{Ross:} Yeah, uh, except for the red sock, which is still red. I'm sorry, please don't be upset, it could happen to anyone.
	\switchcolumn
	\charactername{罗斯：}是啊，除了那只红袜子，它还是红的。对不起，别生气嘛，谁都可能遇到这种事。
	\switchcolumn*
	\charactername{Rachel:} Except it didn't. It happened to me. Oh, god, I'm gonna look like a big marshmallow peep. What am I doing? What am I doing? My father's right. I can't live on my own! I can't even do laundry!
	\switchcolumn
	\charactername{瑞秋：}可别人没遇到，偏偏我遇到了。哦我的天，我穿这些衣服看起来会像个巨型棉花糖。我在干什么啊？我在干什么？我爸说得对，我根本没法自己生活！我连衣服都洗不好！
	\switchcolumn*
	\ennotmain{The woman who had tried to steal the washing machine walks by, and laughs.}
	\switchcolumn
	\notmain{之前试图抢洗衣机的老太太路过，笑了起来}
	\switchcolumn*
	\sense{Scene: The fancy restaurant, Angela has her hand in Bob's shirt, and Monica is very uncomfortable.}
	\switchcolumn
	\sense{场景：高档餐厅，安吉拉的手伸进了鲍勃的衬衫里，莫妮卡感到非常不自在}
	\switchcolumn*
	\charactername{Monica:} Something went wrong with Underdog, and they couldn't get his head to inflate. So anyway, um, his head is like flopping down Broadway, right, and I'm just thinking... how inappropriate this is. Um, I've got something in my eye, uh, Joey, could we check it in the light, please?
	\switchcolumn
	\charactername{莫妮卡：}超级英雄狗\notmain{卡通角色}出问题了，他的头没法充气。所以呢，他的头就耷拉着在百老汇大街上晃，对吧，我就觉得……这也太不合时宜了。那个，我眼睛里进东西了，乔伊，能陪我去灯光下看看吗？
	\switchcolumn*
	\ennotmain{Her and Joey walk away from the table.}
	\switchcolumn
	\notmain{她和乔伊离开餐桌}
	\switchcolumn*
	\charactername{Monica:} Oh my god.
	\switchcolumn
	\charactername{莫妮卡：}我的天。
	\switchcolumn*
	\charactername{Joey:} What?
	\switchcolumn
	\charactername{乔伊：}怎么了？
	\switchcolumn*
	\charactername{Monica:} Hello! Were we at the same table? It's like... cocktails in Appalachia.
	\switchcolumn
	\charactername{莫妮卡：}拜托！我们不是在同一张桌子吗？他们那样子简直……就像在阿巴拉契亚山区喝鸡尾酒\notmain{比喻举止粗鲁无礼}。
	\switchcolumn*
	\charactername{Joey:} Come on, they're close.
	\switchcolumn
	\charactername{乔伊：}拜托，他们感情好嘛。
	\switchcolumn*
	\charactername{Monica:} Close? She's got her tongue in his ear.
	\switchcolumn
	\charactername{莫妮卡：}感情好？她的舌头都伸进他耳朵里了！
	\switchcolumn*
	\charactername{Joey:} Oh, like you've never gotten a little rambunctious with Ross.
	\switchcolumn
	\charactername{乔伊：}哦，说得好像你没跟罗斯亲热过似的。
	\switchcolumn*
	\charactername{Monica:} Joey, this is sick, it's disgusting, it's, it's—not really true, is it?
	\switchcolumn
	\charactername{莫妮卡：}乔伊，这太恶心了，太反胃了，这……这不是真的，对吧？
	\switchcolumn*
	\charactername{Joey:} Well, who's to say what's true? I mean...
	\switchcolumn
	\charactername{乔伊：}嗯，谁知道什么是真的呢？我是说……
	\switchcolumn*
	\charactername{Monica:} Oh my god, what were you thinking?
	\switchcolumn
	\charactername{莫妮卡：}我的天，你当时在想什么啊？
	\switchcolumn*
	\charactername{Joey:} All right, look, I'm not proud of this, ok? Well, maybe I am a little.
	\switchcolumn
	\charactername{乔伊：}好吧，我承认我这事做得不光彩，行了吧？不过，也许我还是有点小得意的。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{hits him lightly} Oh!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{轻轻打了他一下}哦！
	\switchcolumn*
	\charactername{Joey:} Ow!
	\switchcolumn
	\charactername{乔伊：}哎哟！
	\switchcolumn*
	\charactername{Monica:} \ennotmain{leaving} I'm outta here.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{准备走}我走了。
	\switchcolumn*
	\charactername{Joey:} Wait, wait, wait. You want him, I want her. He likes you.
	\switchcolumn
	\charactername{乔伊：}等等等等。你喜欢他，我喜欢她。他也喜欢你啊。
	\switchcolumn*
	\charactername{Monica:} Really?
	\switchcolumn
	\charactername{莫妮卡：}真的吗？
	\switchcolumn*
	\charactername{Joey:} Yeah. I'm thinking, if we put our heads together, between the two of us, we can break them up.
	\switchcolumn
	\charactername{乔伊：}真的。我在想，我们联手的话，一定能把他们拆散。
	\switchcolumn*
	\sense{Time lapse, Monica accidentally spilled her drink on Bob's shirt and is wiping it off. Joey is making eyes at Angela.}
	\switchcolumn
	\sense{时间快进，莫妮卡不小心把饮料洒在鲍勃的衬衫上，正在帮他擦拭。乔伊在对安吉拉抛媚眼}
	\switchcolumn*
	\charactername{Monica:} I'm so sorry, I can't believe I did this, but I couldn't stop laughing at your Norman Mailer story.
	\switchcolumn
	\charactername{莫妮卡：}太对不起了，我真不敢相信我居然这么不小心，主要是你讲的诺曼·梅勒\notmain{美国作家}的故事太好笑了，我忍不住。
	\switchcolumn*
	\ennotmain{Angela is eating chicken wings and making the weasel-like noise Joey had told Bob about.}
	\switchcolumn
	\notmain{安吉拉在吃鸡翅，发出了乔伊跟鲍勃说过的那种黄鼠狼似的声音}
	\switchcolumn*
	\charactername{Joey:} Uh, waiter, one more plate of chicken wings over here.
	\switchcolumn
	\charactername{乔伊：}服务员，再来一盘鸡翅！
	\switchcolumn*
	\sense{Scene: Central Perk, Chandler is still trying to ease things over with Janice, and there are about a dozen empty Espresso cups in front of him. He is extremely wired.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，钱德勒还在试着跟詹妮丝缓和气氛，他面前大概有十几个空浓缩咖啡杯。他已经极度亢奋了}
	\switchcolumn*
	\charactername{Chandler:} Here's the thing, Janice. You know, I mean, it's like we're different. I'm like the bing, bing, bing. You're like the boom, boom, \ennotmain{Chandler flails his hand out and hits Janice in the eye}... boom.
	\switchcolumn
	\charactername{钱德勒：}是这样的，詹妮丝。你知道吗，我是说，我们俩不一样。我就像那种叮叮叮的感觉，你就像那种砰砰砰的\notmain{钱德勒挥动手臂不小心打到了詹妮丝的眼睛}……砰。
	\switchcolumn*
	\charactername{Janice:} Ow!
	\switchcolumn
	\charactername{詹妮丝：}哎哟！
	\switchcolumn*
	\charactername{Chandler:} Oh, my god, I'm so sorry. Are you ok?
	\switchcolumn
	\charactername{钱德勒：}哦我的天，对不起对不起。你还好吗？
	\switchcolumn*
	\charactername{Janice:} Ow. Um, it's just my lens. It's just my lens. I'll be right back.
	\switchcolumn
	\charactername{詹妮丝：}哎哟。没事，就是隐形眼镜移位了。我马上回来。
	\switchcolumn*
	\ennotmain{She leaves.}
	\switchcolumn
	\notmain{她离开了}
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{to Phoebe} I hit her in the eye! I hit her in the eye! This is the worst break-up in the history of the world.
	\switchcolumn
	\charactername{钱德勒：}\notmain{对菲比}我打到她眼睛了！我打到她眼睛了！这是史上最糟糕的分手！
	\switchcolumn*
	\charactername{Phoebe:} Oh my god. \ennotmain{Chandler downs another espresso.} How many of those have you had?
	\switchcolumn
	\charactername{菲比：}我的天。\notmain{钱德勒又喝了一杯浓缩咖啡}你到底喝了多少杯啊？
	\switchcolumn*
	\charactername{Chandler:} Oh, I don't know, a million?
	\switchcolumn
	\charactername{钱德勒：}不知道，一百万杯？
	\switchcolumn*
	\charactername{Phoebe:} Chandler, easy, easy. Go to your happy place. La la la la la la la.
	\switchcolumn
	\charactername{菲比：}钱德勒，冷静冷静。想想开心的事情。啦啦啦啦啦啦啦。
	\switchcolumn*
	\charactername{Chandler:} I'm fine.
	\switchcolumn
	\charactername{钱德勒：}我没事。
	\switchcolumn*
	\charactername{Phoebe:} All right.
	\switchcolumn
	\charactername{菲比：}好吧。
	\switchcolumn*
	\ennotmain{Janice returns from the bathroom.}
	\switchcolumn
	\notmain{詹妮丝从洗手间回来}
	\switchcolumn*
	\charactername{Chandler:} I'm not fine. Here she comes.
	\switchcolumn
	\charactername{钱德勒：}我有事。她回来了。
	\switchcolumn*
	\charactername{Phoebe:} Wait here. Breathe.
	\switchcolumn
	\charactername{菲比：}待在这儿别动。深呼吸。
	\switchcolumn*
	\ennotmain{Phoebe goes over to speak to Janice. She talks to her for a few seconds, and then Janice immediately smiles, hugs her, waves to Chandler, and leaves.}
	\switchcolumn
	\notmain{菲比走过去跟詹妮丝说话。说了几秒后，詹妮丝立刻笑了起来，抱了抱菲比，跟钱德勒挥了挥手就走了}
	\switchcolumn*
	\charactername{Chandler:} How do you do that?
	\switchcolumn
	\charactername{钱德勒：}你怎么做到的？
	\switchcolumn*
	\charactername{Phoebe:} It's like a gift.
	\switchcolumn
	\charactername{菲比：}天赋异禀吧。
	\switchcolumn*
	\charactername{Chandler:} We should always always break up together.
	\switchcolumn
	\charactername{钱德勒：}我们以后分手都要一起！
	\switchcolumn*
	\charactername{Phoebe:} Oh, I'd like that.
	\switchcolumn
	\charactername{菲比：}好啊，我愿意。
	\switchcolumn*
	\sense{Scene: The Launderama. Rachel is sorting her now-pink clothes.}
	\switchcolumn
	\sense{场景：自助洗衣店。瑞秋在整理她现在全是粉色的衣服}
	\switchcolumn*
	\charactername{Ross:} You got the clothes clean. Now that's the important part.
	\switchcolumn
	\charactername{罗斯：}衣服洗干净了呀，这才是最重要的。
	\switchcolumn*
	\charactername{Rachel:} Oh, I guess. Except everything looks like jammies now.
	\switchcolumn
	\charactername{瑞秋：}嗯，好像是。不过现在所有衣服看起来都像睡衣了。
	\switchcolumn*
	\ennotmain{The same woman walks over and takes Rachel's laundry cart.}
	\switchcolumn
	\notmain{之前那个老太太走过来，拿走了瑞秋的洗衣篮}
	\switchcolumn*
	\charactername{Rachel:} Whoa, I'm sorry. Excuse me. We had this cart.
	\switchcolumn
	\charactername{瑞秋：}喂，不好意思。这是我们的洗衣篮。
	\switchcolumn*
	\charactername{Woman:} Yeah, well, I had a 24-inch waist. You lose things. Now come on, get outta my way.
	\switchcolumn
	\charactername{老太太：}是啊，我以前腰围才61厘米呢，还不是照样没了。让开让开。
	\switchcolumn*
	\ennotmain{Rachel looks at Ross, who motions to her to get the cart back.}
	\switchcolumn
	\notmain{瑞秋看向罗斯，罗斯示意她把洗衣篮拿回来}
	\switchcolumn*
	\charactername{Rachel:} I'm sorry, you know, maybe I wasn't being clear. Uh, this is our cart.
	\switchcolumn
	\charactername{瑞秋：}不好意思，可能我刚才没说清楚。这是我们的洗衣篮。
	\switchcolumn*
	\charactername{Woman:} Hey, hey, hey there aren't any clothes in it.
	\switchcolumn
	\charactername{老太太：}嘿，嘿，嘿，这里面又没衣服。
	\switchcolumn*
	\charactername{Rachel:} Hey, hey, hey, hey, quit making up rules!
	\switchcolumn
	\charactername{瑞秋：}嘿，嘿，嘿，别乱编规矩！
	\switchcolumn*
	\charactername{Woman:} Let go!
	\switchcolumn
	\charactername{老太太：}放手！
	\switchcolumn*
	\ennotmain{They struggle for the cart. Finally, Rachel climbs inside of it.}
	\switchcolumn
	\notmain{她们争抢起洗衣篮。最后瑞秋爬进了洗衣篮里}
	\switchcolumn*
	\charactername{Rachel:} All right, listen, missy. If you want this cart, you're gonna have to take me with it!
	\switchcolumn
	\charactername{瑞秋：}好吧，听着，老太婆。你要是想要这个洗衣篮，就得连我一起搬走！
	\switchcolumn*
	\ennotmain{She thinks it over, and then walks away.}
	\switchcolumn
	\notmain{老太太想了想，然后走了}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{to Ross} Yes! Did you see that?
	\switchcolumn
	\charactername{瑞秋：}\notmain{对罗斯}太棒了！你看到了吗？
	\switchcolumn*
	\charactername{Ross:} You were incredible! Brand new woman, ladies and gentlemen.
	\switchcolumn
	\charactername{罗斯：}你太厉害了！各位，这是一个全新的瑞秋！
	\switchcolumn*
	\charactername{Rachel:} I could not have done this without you.
	\switchcolumn
	\charactername{瑞秋：}没有你我肯定做不到。
	\switchcolumn*
	\ennotmain{Rachel stands up and kisses Ross. He is stunned. A moment of silence follows.}
	\switchcolumn
	\notmain{瑞秋站起来吻了罗斯。罗斯惊呆了。一阵沉默}
	\switchcolumn*
	\charactername{Ross:} Ok, um, uh, more clothes in the dryer? \ennotmain{Ross turns and bangs his head on an open dryer door.} I'm fine, I'm fine.
	\switchcolumn
	\charactername{罗斯：}那个，要不要……再往烘干机里放些衣服？\notmain{罗斯转身时头撞到了打开的烘干机门上}我没事，我没事。
	\switchcolumn*
	\charactername{Rachel:} Are you sure?
	\switchcolumn
	\charactername{瑞秋：}你真的没事吗？
	\switchcolumn*
	\charactername{Ross:} No.
	\switchcolumn
	\charactername{罗斯：}有事。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, Ross, Rachel, and Phoebe are there. Ross has an icepack to his head.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，罗斯、瑞秋和菲比在这儿。罗斯头上敷着冰袋}
	\switchcolumn*
	\charactername{Rachel:} Oh, are you sure you're ok?
	\switchcolumn
	\charactername{瑞秋：}你真的没事吗？
	\switchcolumn*
	\charactername{Ross:} Yeah.
	\switchcolumn
	\charactername{罗斯：}没事。
	\switchcolumn*
	\charactername{Rachel:} Does it still hurt?
	\switchcolumn
	\charactername{瑞秋：}还疼吗？
	\switchcolumn*
	\charactername{Ross:} Yeah.
	\switchcolumn
	\charactername{罗斯：}疼。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{seeing Rachel's clothes} What a neat idea. All your clothes match. I'm gonna do this.
	\switchcolumn
	\charactername{菲比：}\notmain{看到瑞秋的衣服}这主意真棒！所有衣服都成套了。我以后也要这么洗。
	\switchcolumn*
	\ennotmain{Monica and Joey enter.}
	\switchcolumn
	\notmain{莫妮卡和乔伊走进来}
	\switchcolumn*
	\charactername{Monica:} Hi.
	\switchcolumn
	\charactername{莫妮卡：}嗨。
	\switchcolumn*
	\charactername{Phoebe:} Hey, how'd it go?
	\switchcolumn
	\charactername{菲比：}嘿，怎么样了？
	\switchcolumn*
	\charactername{Joey:} Excellent.
	\switchcolumn
	\charactername{乔伊：}超顺利。
	\switchcolumn*
	\charactername{Monica:} We ripped that couple apart, and kept the pieces for ourselves.
	\switchcolumn
	\charactername{莫妮卡：}我们把那对情侣拆散了，然后各取所需。
	\switchcolumn*
	\charactername{Ross:} What a beautiful story. Hey, I'm fine by the way.
	\switchcolumn
	\charactername{罗斯：}真是个“美好”的故事啊。对了，我没事哦。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{notices his head} Oh, I'm sorry.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{注意到他的头}哦，对不起。
	\switchcolumn*
	\charactername{Rachel:} Where's Chandler?
	\switchcolumn
	\charactername{瑞秋：}钱德勒呢？
	\switchcolumn*
	\charactername{Phoebe:} Oh, he needed some time to grieve.
	\switchcolumn
	\charactername{菲比：}哦，他需要点时间“疗伤”。
	\switchcolumn*
	\ennotmain{Chandler runs by the window outside, joyous.}
	\switchcolumn
	\notmain{钱德勒从外面的窗户边跑过，兴高采烈}
	\switchcolumn*
	\charactername{Chandler:} I'm free! I'm free!
	\switchcolumn
	\charactername{钱德勒：}我自由了！我自由了！
	\switchcolumn*
	\charactername{Phoebe:} That oughta do it.
	\switchcolumn
	\charactername{菲比：}看来疗完伤了。
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage