\begin{paracol}{2}
	\sense{Scene: A Theater, the gang is in the audience wating for a play of Joey's to start.}
	\switchcolumn
	\sense{场景：剧院，众人坐在观众席上，等待乔伊的话剧开场}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{reading the program} Ooh! Look! Look! Look! Look, there's Joey's picture! This is so exciting!
	\switchcolumn
	\charactername{瑞秋：}\notmain{看着节目单}哦！快看！快看！快看！乔伊的照片在这儿呢！太激动人心了！
	\switchcolumn*
	\charactername{Chandler:} You can always spot someone who's never seen one of his plays before. Notice, no fear, no sense of impending doom...
	\switchcolumn
	\charactername{钱德勒：}一看就知道谁是第一次看他演话剧。瞧见没，毫无畏惧，也完全没意识到大难临头……
	\switchcolumn*
	\charactername{Phoebe:} The exclamation point in the title scares me. \ennotmain{Gesturing} Y'know, it's not just Freud, it's Freud!
	\switchcolumn
	\charactername{菲比：}标题里的感叹号吓着我了。\notmain{比划着}你懂的，不只是“弗洛伊德”，是“弗洛伊德！”\notmain{加重语气}
	\switchcolumn*
	\ennotmain{The lights dim.}
	\switchcolumn
	\notmain{灯光渐暗}
	\switchcolumn*
	\charactername{Ross:} Oh, shhh, shh. Magic is about to happen.
	\switchcolumn
	\charactername{罗斯：}哦，嘘，嘘。奇迹即将上演。
	\switchcolumn*
	\ennotmain{The lights go up on the stage, Joey, as Freud, is talking to a female patient.}
	\switchcolumn
	\notmain{舞台灯光亮起，乔伊饰演弗洛伊德，正在和一位女病人交谈}
	\switchcolumn*
	\charactername{Joey:} well, Eva, we've done some excellent work here, and I would have to say, your problem is quite clear. \ennotmain{He goes into a song and dance number.}
	\switchcolumn
	\charactername{乔伊：}好吧，伊娃，我们已经取得了很大进展，我得说，你的问题很明显。\notmain{他开始载歌载舞}
	\switchcolumn*
	All you want is a dingle,
	\switchcolumn
	你想要的不过是个小玩意儿，
	\switchcolumn*
	What you envy's a schwang,
	\switchcolumn
	你羡慕的是那话儿，
	\switchcolumn*
	A thing through which you can tinkle,
	\switchcolumn
	一个能用来小便的东西，
	\switchcolumn*
	Or play with, or simply let hang...
	\switchcolumn
	或是把玩，或是就让它耷拉着……
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: The Theater, the play has ended and everyone is applauding. As soon as the cast leaves, the gang all groan and sit down heavily.}
	\switchcolumn
	\sense{场景：剧院，话剧结束，众人正在鼓掌。演员一退场，大家立刻叹气，重重地坐回座位}
	\switchcolumn*
	\charactername{Rachel:} God. I feel violated.
	\switchcolumn
	\charactername{瑞秋：}天啊。我感觉被冒犯了。
	\switchcolumn*
	\charactername{Monica:} Did anybody else feel they just wanted to peel the skin off their body, to have something else to do?
	\switchcolumn
	\charactername{莫妮卡：}有没有人跟我一样，只想把自己的皮扒下来，找点别的事做？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{staring at a woman across the room} Ross, ten o'clock.
	\switchcolumn
	\charactername{钱德勒：}\notmain{盯着房间另一头的女人}罗斯，十点钟方向。
	\switchcolumn*
	\charactername{Ross:} Is it? Feels like two.
	\switchcolumn
	\charactername{罗斯：}是吗？我觉得都快凌晨两点了\notmain{形容话剧难熬}。
	\switchcolumn*
	\charactername{Chandler:} No, ten o'clock.
	\switchcolumn
	\charactername{钱德勒：}不是，是十点钟方向\notmain{指美女位置}。
	\switchcolumn*
	\charactername{Ross:} What?
	\switchcolumn
	\charactername{罗斯：}什么？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{sighs and gestures to explain} There's a beautiful woman at eight, nine, ten o'clock!
	\switchcolumn
	\charactername{钱德勒：}\notmain{叹气并比划着解释}八点、九点、十点方向有个美女！
	\switchcolumn*
	\charactername{Ross:} Oh. Hel-lo!
	\switchcolumn
	\charactername{罗斯：}哦。嗨～\notmain{打招呼的语气}
	\switchcolumn*
	\charactername{Chandler:} She's amazing! She makes the women that I dream about look like short, fat, bald men!
	\switchcolumn
	\charactername{钱德勒：}她太迷人了！跟她比起来，我梦里的女人都像又矮又胖的光头男！
	\switchcolumn*
	\charactername{Monica:} Well, go over to her! She's not with anyone.
	\switchcolumn
	\charactername{莫妮卡：}那快去啊！她身边没人。
	\switchcolumn*
	\charactername{Chandler:} Oh yeah, and what would my opening line be? 'Excuse me. Blarrglarrghh.'
	\switchcolumn
	\charactername{钱德勒：}是啊，那我开场白该说啥？“不好意思。呃呃呃呃呃。”\notmain{模仿语无伦次的样子}
	\switchcolumn*
	\charactername{Rachel:} Oh, c'mon. She's a person, you can do it!
	\switchcolumn
	\charactername{瑞秋：}拜托。她也是普通人，你可以的！
	\switchcolumn*
	\charactername{Chandler:} Oh please, could she be more out of my league? Ross, back me up here.
	\switchcolumn
	\charactername{钱德勒：}得了吧，她跟我简直不是一个世界的人好吗？罗斯，帮我说句公道话。
	\switchcolumn*
	\charactername{Ross:} He could never get a woman like that in a million years.
	\switchcolumn
	\charactername{罗斯：}他再过一百万年也追不到这种级别的女人。
	\switchcolumn*
	\charactername{Chandler:} Thank you, buddy.
	\switchcolumn
	\charactername{钱德勒：}谢了，兄弟。
	\switchcolumn*
	\charactername{Phoebe:} Oh, oh, but y'know, you always see these really beautiful women with these really nothing guys, you could be one of those guys.
	\switchcolumn
	\charactername{菲比：}哦，哦，不过你看啊，总有些超级美女会跟平平无奇的男生在一起，你也可以成为那种男生啊。
	\switchcolumn*
	\charactername{Monica:} You could do that!
	\switchcolumn
	\charactername{莫妮卡：}你肯定行！
	\switchcolumn*
	\charactername{Chandler:} Y'think?
	\switchcolumn
	\charactername{钱德勒：}你们觉得？
	\switchcolumn*
	\charactername{All:} Yeah!
	\switchcolumn
	\charactername{众人：}对啊！
	\switchcolumn*
	\charactername{Chandler:} Oh God, I can't believe I'm even considering this... I'm very very aware of my tongue...
	\switchcolumn
	\charactername{钱德勒：}天啊，我真不敢相信自己居然在考虑这事……我感觉舌头都不是自己的了……
	\switchcolumn*
	\charactername{Ross:} C'mon! C'mon!
	\switchcolumn
	\charactername{罗斯：}快去！快去！
	\switchcolumn*
	\charactername{Chandler:} Here goes. \ennotmain{He walks over to her but just stands there.}
	\switchcolumn
	\charactername{钱德勒：}豁出去了。\notmain{他走向美女，却只是站在那儿}
	\switchcolumn*
	\charactername{Aurora:} ...Yes?
	\switchcolumn
	\charactername{奥罗拉：}……有事吗？
	\switchcolumn*
	\charactername{Chandler:} Hi.... um... okay, next word... would be... Chandler! Chandler is my name, and, uh...\ennotmain{He clears his throat noisily}...hi.
	\switchcolumn
	\charactername{钱德勒：}嗨……嗯……好吧，下一个词……是……钱德勒！我叫钱德勒，然后，呃……\notmain{大声清嗓子}……嗨。
	\switchcolumn*
	\charactername{Aurora:} Yes, you said that.
	\switchcolumn
	\charactername{奥罗拉：}嗯，你已经说过“嗨”了。
	\switchcolumn*
	\charactername{Chandler:} Yes, yes I did, but what I didn't say was what I was about to say, what I wanted to say was, uh... would you like to go out with me sometime, thankyou, goodnight. \ennotmain{He walks back to the others but she calls him back.}
	\switchcolumn
	\charactername{钱德勒：}对，对，我说过了，但我没说的是我本来想说的，我真正想说的是，呃……你愿意改天跟我约会吗，谢谢，晚安。\notmain{他走回众人身边，却被她叫住}
	\switchcolumn*
	\charactername{Aurora:} Chandler?
	\switchcolumn
	\charactername{奥罗拉：}钱德勒？
	\switchcolumn*
	\ennotmain{Joey enters from behind a curtain. The others all talk at once.}
	\switchcolumn
	\notmain{乔伊从幕布后走出来。众人立刻七嘴八舌地说话}
	\switchcolumn*
	\charactername{All:} Hey! You're in a play! I didn't know you could dance! You had a beard!
	\switchcolumn
	\charactername{众人：}嘿！你居然演话剧！没想到你还会跳舞！你留胡子了！
	\switchcolumn*
	\charactername{Joey:} Whadja think?
	\switchcolumn
	\charactername{乔伊：}你们觉得咋样？
	\switchcolumn*
	\ennotmain{Pause}
	\switchcolumn
	\notmain{停顿}
	\switchcolumn*
	\charactername{All:} ...Hey! You're in a play! I didn't know you could dance! You had a beard!
	\switchcolumn
	\charactername{众人：}……嘿！你居然演话剧！没想到你还会跳舞！你留胡子了！
	\switchcolumn*
	\charactername{Joey:} C'mon, you guys, it wasn't that bad. It was better than that thing I did with the trolls, at least you got to see my head.
	\switchcolumn
	\charactername{乔伊：}拜托，没那么糟吧。至少比我上次演的那部矮人剧强，这次你们好歹能看到我的头。
	\switchcolumn*
	\charactername{All:} \ennotmain{admitting} Saw your head. Saw your head.
	\switchcolumn
	\charactername{众人：}\notmain{不情愿地承认}看到头了。看到头了。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{running back} She said yes!! She said yes!! \ennotmain{To Joey} Awful play, man. Whoah. \ennotmain{To All} Her name's Aurora, and she's Italian, and she pronounces my name 'Chand-lrr'. 'Chand-lrr'. I think I like it better that way. \ennotmain{To Joey} Oh, listen, the usher gave me this to give to you. \ennotmain{He fishes a card out of his pocket.}
	\switchcolumn
	\charactername{钱德勒：}\notmain{跑回来}她答应了！她答应了！\notmain{对乔伊}这话剧真烂，兄弟。哇哦。\notmain{对众人}她叫奥罗拉，意大利人，她把我的名字念成“钱德-勒”。“钱德-勒”，我觉得这样念更好听。\notmain{对乔伊}哦对了，引座员让我把这个交给你。\notmain{从口袋里掏出一张卡片}
	\switchcolumn*
	\charactername{Rachel:} What is it?
	\switchcolumn
	\charactername{瑞秋：}这是什么？
	\switchcolumn*
	\charactername{Joey:} The Estelle Leonard Talent Agency. Wow, an agency left me its card! Maybe they wanna sign me!
	\switchcolumn
	\charactername{乔伊：}埃斯特尔·伦纳德经纪公司。哇，居然有经纪公司给我留名片！说不定他们想签我！
	\switchcolumn*
	\charactername{Phoebe:} Based on this play? ...Based on this play!
	\switchcolumn
	\charactername{菲比：}就凭这部话剧？……居然凭这部话剧！
	\switchcolumn*
	\sense{Scene: Central Perk, everyone else is there as Chandler enters.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，钱德勒走进来，其他人都在}
	\switchcolumn*
	\charactername{Chandler:} Hey, kids.
	\switchcolumn
	\charactername{钱德勒：}嘿，大伙儿。
	\switchcolumn*
	\charactername{All:} Hey.
	\switchcolumn
	\charactername{众人：}嘿。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{reading Monica's palm} No, 'cause this line is passion, and this is... just a line.
	\switchcolumn
	\charactername{菲比：}\notmain{看着莫妮卡的手掌}不对，这条线是感情线，而这条……就是条普通的线。
	\switchcolumn*
	\charactername{Chandler:} Well, I can't believe I've been here almost seven seconds and you haven't asked me how my date went.
	\switchcolumn
	\charactername{钱德勒：}真不敢相信我都来了快七秒了，你们居然没问我约会咋样。
	\switchcolumn*
	\charactername{Monica:} Oh, right, right. How was your date, 'Chand-lrr'?
	\switchcolumn
	\charactername{莫妮卡：}哦对哦对。你的约会咋样啊，“钱德-勒”？
	\switchcolumn*
	\charactername{Chandler:} It was unbelievable. I-I've never met anyone like her. She's had the most amazing life! She was in the Israeli army...
	\switchcolumn
	\charactername{钱德勒：}简直不可思议。我从没遇到过她这样的人。她的人生太传奇了！她当过以色列女兵……
	\switchcolumn*
	\ennotmain{A flashback of Aurora and Chandler on their date in Central Perk is denoted by italics.}
	\switchcolumn
	\notmain{以下斜体部分为闪回：奥罗拉和钱德勒在中央公园咖啡馆约会的场景}
	\switchcolumn*
	\charactername{Aurora:} ...Luckily none of the bullets hit the engine block. So, we made it to the border, but just barely, and I- ...I've been talking about myself all night long, I'm sorry. What about you? Tell me one of your stories.
	\switchcolumn
	\charactername{奥罗拉：}……幸运的是，子弹都没打中发动机缸体。所以我们勉强冲到了边境，然后我——……我一整晚都在说自己，抱歉。你呢？跟我说说你的事呗。
	\switchcolumn*
	\charactername{Chandler:} Alright. Once I got on the subway, right, and it was at night, and I rode it all the way to Brooklyn... just for the hell of it.
	\switchcolumn
	\charactername{钱德勒：}好吧。有一次我坐地铁，晚上的时候，一路坐到了布鲁克林……就是闲得没事干。
	\switchcolumn*
	\charactername{Chandler:} We talked 'til like two. It was this perfect evening... more or less.
	\switchcolumn
	\charactername{钱德勒：}我们聊到快两点。那真是个完美的夜晚……差不多算是吧。
	\switchcolumn*
	\charactername{Aurora:} ...All of a sudden we realised we were in Yammon.
	\switchcolumn
	\charactername{奥罗拉：}……突然我们发现自己到了也门。
	\switchcolumn*
	\charactername{Chandler:} Oh, I'm sorry, so 'we' is?
	\switchcolumn
	\charactername{钱德勒：}哦，抱歉，这里的“我们”是指？
	\switchcolumn*
	\charactername{Aurora:} 'We' would be me and Rick.
	\switchcolumn
	\charactername{奥罗拉：}“我们”是我和里克。
	\switchcolumn*
	\charactername{Joey:} Who's Rick?
	\switchcolumn
	\charactername{乔伊：}里克是谁？
	\switchcolumn*
	\charactername{Chandler:} Who's Rick?
	\switchcolumn
	\charactername{钱德勒：}里克是谁？
	\switchcolumn*
	\charactername{Aurora:} My husband.
	\switchcolumn
	\charactername{奥罗拉：}我丈夫。
	\switchcolumn*
	\charactername{All:} Ooooohhh.
	\switchcolumn
	\charactername{众人：}哦——\notmain{恍然大悟又惊讶的语气}
	\switchcolumn*
	\charactername{Chandler:} Oh, so you're divorced?
	\switchcolumn
	\charactername{钱德勒：}哦，所以你离婚了？
	\switchcolumn*
	\charactername{Aurora:} No.
	\switchcolumn
	\charactername{奥罗拉：}没有。
	\switchcolumn*
	\charactername{Chandler:} Oh, I'm sorry, then you're widowed?...Hopefully?
	\switchcolumn
	\charactername{钱德勒：}哦，抱歉，那你是丧偶了？……希望是这样？
	\switchcolumn*
	\charactername{Aurora:} No, I'm still married.
	\switchcolumn
	\charactername{奥罗拉：}不是，我还在婚姻中。
	\switchcolumn*
	\charactername{Chandler:} So tell me, how do- how do you think your husband would feel about you sitting here with me?...Sliding your foot so far up my pant leg you can count the change in my pocket?
	\switchcolumn
	\charactername{钱德勒：}那跟我说说，你觉得你丈夫知道你跟我坐在这里……把脚伸到我裤腿里都能数清我口袋里的零钱，他会怎么想？
	\switchcolumn*
	\charactername{Aurora:} Don't worry. I imagine he'd be okay with you because really, he's okay with Ethan.
	\switchcolumn
	\charactername{奥罗拉：}别担心。我觉得他会接受你的，因为他连伊桑都接受了。
	\switchcolumn*
	\charactername{Chandler:} Ethan? There's, there's an Ethan?
	\switchcolumn
	\charactername{钱德勒：}伊桑？还有个伊桑？
	\switchcolumn*
	\charactername{Aurora:} Mmmm... Ethan is my... boyfriend.
	\switchcolumn
	\charactername{奥罗拉：}嗯……伊桑是我的……男朋友。
	\switchcolumn*
	\charactername{All:} What?!
	\switchcolumn
	\charactername{众人：}什么？！
	\switchcolumn*
	\charactername{Chandler:} So explain something to me here, uh, what kind of a relationship do you imagine us having if you already have a husband and a boyfriend?
	\switchcolumn
	\charactername{钱德勒：}那你跟我说说，如果你已经有丈夫还有男朋友了，你觉得我们之间能是什么关系？
	\switchcolumn*
	\charactername{Aurora:} I suppose mainly sexual.
	\switchcolumn
	\charactername{奥罗拉：}我觉得主要是性关系吧。
	\switchcolumn*
	\charactername{Chandler:} ...Hm.
	\switchcolumn
	\charactername{钱德勒：}……嗯。
	\switchcolumn*
	\charactername{Monica:} Oh. I'm sorry it didn't work out.
	\switchcolumn
	\charactername{莫妮卡：}哦。真遗憾没成。
	\switchcolumn*
	\charactername{Chandler:} What 'not work out'? I'm seeing her again on Thursday. Didn't you listen to the story?
	\switchcolumn
	\charactername{钱德勒：}什么叫“没成”？我们周四还要见面呢。你们没听我把故事说完吗？
	\switchcolumn*
	\charactername{Monica:} Didn't you listen to the story? I mean, this is twisted! How could you get involved with a woman like this?
	\switchcolumn
	\charactername{莫妮卡：}明明是你没听懂重点吧？这也太离谱了！你怎么会跟这种女人纠缠不清？
	\switchcolumn*
	\charactername{Chandler:} Well, y'know, I had some trouble with it at first too, but the way I look at it is, I get all the good stuff: all the fun, all the talking, all the sex; and none of the responsibility. I mean, this is every guy's fantasy!
	\switchcolumn
	\charactername{钱德勒：}一开始我也觉得不太对劲，但我是这么想的：我能得到所有好处——所有的乐趣、聊天、性生活，却不用承担任何责任。这可是每个男人的梦想啊！
	\switchcolumn*
	\charactername{Phoebe:} Oh, yeah. That is not true. Ross, is this your fantasy?
	\switchcolumn
	\charactername{菲比：}哦，才不是呢。罗斯，这是你的梦想吗？
	\switchcolumn*
	\charactername{Ross:} No, of course not! \ennotmain{Thinks} ...Yeah, yeah, it is.
	\switchcolumn
	\charactername{罗斯：}不，当然不是！\notmain{想了想}……是，是啊，确实是。
	\switchcolumn*
	\charactername{Monica:} What? So you guys don't mind going out with someone else who's going out with someone else?
	\switchcolumn
	\charactername{莫妮卡：}什么？所以你们不介意跟有伴侣的人约会？
	\switchcolumn*
	\charactername{Joey:} I couldn't do it.
	\switchcolumn
	\charactername{乔伊：}我可做不到。
	\switchcolumn*
	\charactername{Monica:} Good for you, Joey.
	\switchcolumn
	\charactername{莫妮卡：}乔伊，你真不错。
	\switchcolumn*
	\charactername{Joey:} When I'm with a woman, I need to know that I'm going out with more people than she is.
	\switchcolumn
	\charactername{乔伊：}我跟女人在一起的时候，得确保我约会的人数比她多。
	\switchcolumn*
	\charactername{Ross:} Well, y'know, monogamy can be a, uh, tricky concept. I mean, anthropologically speaking-
	\switchcolumn
	\charactername{罗斯：}其实呢，一夫一妻制这概念，呃，挺复杂的。我是说，从人类学的角度来看——
	\switchcolumn*
	\ennotmain{They all pretend to fall asleep.}
	\switchcolumn
	\notmain{众人假装睡着}
	\switchcolumn*
	\charactername{Ross:} Fine. Fine, alright, now you'll never know.
	\switchcolumn
	\charactername{罗斯：}行吧。行，那你们永远别想知道了。
	\switchcolumn*
	\charactername{Monica:} We're kidding. C'mon, tell us!
	\switchcolumn
	\charactername{莫妮卡：}我们逗你的。快说嘛！
	\switchcolumn*
	\charactername{All:} Yeah! C'mon!
	\switchcolumn
	\charactername{众人：}对啊！快说！
	\switchcolumn*
	\charactername{Ross:} Alright. There's a theory, put forth by Richard Leakey-
	\switchcolumn
	\charactername{罗斯：}好吧。有个理论，是理查德·利基\notmain{著名人类学家}提出的——
	\switchcolumn*
	\ennotmain{They all fall asleep again.}
	\switchcolumn
	\notmain{众人再次假装睡着}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Rachel is there as enter except Joey enter.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，除了乔伊，其他人都进来了}
	\switchcolumn*
	\charactername{Rachel:} Tah-daaah!
	\switchcolumn
	\charactername{瑞秋：}哒-哒-哒！\notmain{展示成果的语气}
	\switchcolumn*
	\charactername{Chandler:} Are we greeting each other this way now? 'Cause I like that.
	\switchcolumn
	\charactername{钱德勒：}我们现在都这么打招呼了吗？我喜欢。
	\switchcolumn*
	\charactername{Rachel:} Look! I cleaned! I did the windows, I did the floors... I even used all the attachments on the vacuum, except that little round one with the bristles, I don't know what that's for.
	\switchcolumn
	\charactername{瑞秋：}快看！我打扫卫生了！擦了窗户，拖了地板……吸尘器的所有配件我都用了，除了那个带刷毛的小圆头，我不知道那是干嘛的。
	\switchcolumn*
	\charactername{Ross:} Oh yeah, nobody knows. And we're not supposed to ask.
	\switchcolumn
	\charactername{罗斯：}是啊，没人知道。而且我们也不该问。
	\switchcolumn*
	\charactername{Rachel:} Well, whaddya think?
	\switchcolumn
	\charactername{瑞秋：}怎么样？
	\switchcolumn*
	\charactername{All:} Very clean! It looks great! Terrific!
	\switchcolumn
	\charactername{众人：}太干净了！真好看！太棒了！
	\switchcolumn*
	\charactername{Monica:} ...Oh! I-I see you moved the green ottoman.
	\switchcolumn
	\charactername{莫妮卡：}……哦！我——我看到你把绿色脚凳挪位置了。
	\switchcolumn*
	\charactername{All:} Uh-oh...
	\switchcolumn
	\charactername{众人：}哦豁……\notmain{预感不妙的语气}
	\switchcolumn*
	\charactername{Monica:} How-how did that happen?
	\switchcolumn
	\charactername{莫妮卡：}怎-怎么回事？
	\switchcolumn*
	\charactername{Rachel:} I dunno.. I-I thought it looked better there. And I- and also, it's an extra seat around the coffee table.
	\switchcolumn
	\charactername{瑞秋：}我不知道……我觉得放那儿更好看。而且，咖啡桌旁边还能多一个座位。
	\switchcolumn*
	\charactername{Monica:} Yeah, yeah, it's interesting.. but y'know what? Just for fun, let's see what it looked like in the old spot. \ennotmain{She moves it.} Alright, just to compare. Let's see. Well, it looks good there too. Let's just leave it there for a while.
	\switchcolumn
	\charactername{莫妮卡：}是，是，挺有意思的……不过你知道吗？就当好玩，咱们看看放回原来的位置咋样。\notmain{她把脚凳挪回去}好了，就对比一下。嗯，放这儿也好看。先放这儿一阵子吧。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{to Rachel} I can't believe you tried to move the green ottoman.
	\switchcolumn
	\charactername{菲比：}\notmain{对瑞秋}真不敢相信你居然敢动绿色脚凳。
	\switchcolumn*
	\charactername{Chandler:} Thank God you didn't try to fan out the magazines. I mean, she'll scratch your eyes right out.
	\switchcolumn
	\charactername{钱德勒：}幸好你没敢把杂志摊开摆。不然她能把你眼睛挠出来。
	\switchcolumn*
	\charactername{Monica:} You guys, I am not that bad!
	\switchcolumn
	\charactername{莫妮卡：}你们太夸张了！我没那么过分！
	\switchcolumn*
	\charactername{Phoebe:} Yeah, you are, Monica. Remember when I lived with you? You were like, a little, y'know, \ennotmain{psycho} Ree! Ree! Ree! Ree!
	\switchcolumn
	\charactername{菲比：}不，你就是这么过分，莫妮卡。记得我跟你住的时候吗？你就像个小疯子，“瑞！瑞！瑞！瑞！”\notmain{模仿神经质的叫声}
	\switchcolumn*
	\charactername{Monica:} That is so unfair!
	\switchcolumn
	\charactername{莫妮卡：}太不公平了！
	\switchcolumn*
	\charactername{Ross:} Oh c'mon! When we were kids, yours was the only Raggedy Ann doll that wasn't raggedy!
	\switchcolumn
	\charactername{罗斯：}拜托！我们小时候，你的“破烂安”娃娃是唯一一个不破烂的！\notmain{“破烂安”是经典布娃娃，设计初衷就是略显破旧}
	\switchcolumn*
	\charactername{Monica:} Okay, so I'm responsible, I'm organised. But hey, I can be a kook.
	\switchcolumn
	\charactername{莫妮卡：}好吧，我是负责任、有条理。但我也可以很疯癫啊。
	\switchcolumn*
	\charactername{Ross:} Alright, you madcap gal. Try to imagine this. The phone bill arrives, but you don't pay it right away.
	\switchcolumn
	\charactername{罗斯：}行吧，你这个疯丫头。试着想象一下：电话账单来了，但你不马上付钱。
	\switchcolumn*
	\charactername{Monica:} Why not?
	\switchcolumn
	\charactername{莫妮卡：}为什么不付？
	\switchcolumn*
	\charactername{Ross:} Because you're a kook! Instead you wait until they send you a notice.
	\switchcolumn
	\charactername{罗斯：}因为你疯癫啊！你要等到他们发催款通知才付。
	\switchcolumn*
	\charactername{Monica:} I could do that.
	\switchcolumn
	\charactername{莫妮卡：}我可以试试。
	\switchcolumn*
	\charactername{Rachel:} Okay, uh, you let me go grocery shopping, and I buy laundry detergent, but it's not the one with the easy-pour spout.
	\switchcolumn
	\charactername{瑞秋：}那好，我去买日用品，我买的洗衣粉不是那种易倾倒出口的。
	\switchcolumn*
	\charactername{Monica:} Why would someone do that?! ...One might wonder.
	\switchcolumn
	\charactername{莫妮卡：}谁会这么做啊？！……真是让人费解。
	\switchcolumn*
	\charactername{Chandler:} Someone's left a glass on the coffee table. There's no coaster. It's a cold drink, it's a hot day. Little beads of condensation are inching their way closer and closer to the surface of the wood...
	\switchcolumn
	\charactername{钱德勒：}有人把杯子放咖啡桌上了，还没垫杯垫。天这么热，饮料又冰。小水珠正一点点往木头桌面上渗……
	\switchcolumn*
	\charactername{Monica:} STOP IT!! ...Oh my God. It's true! Who am I?
	\switchcolumn
	\charactername{莫妮卡：}别说了！……天啊。是真的！我到底是谁啊？
	\switchcolumn*
	\charactername{Ross:} Monica? You're Mom.
	\switchcolumn
	\charactername{罗斯：}莫妮卡？你就是咱们妈\notmain{的翻版}。
	\switchcolumn*
	\ennotmain{Monica gasps.}
	\switchcolumn
	\notmain{莫妮卡倒吸一口凉气}
	\switchcolumn*
	\charactername{Phoebe:} Ree! Ree! Ree! Ree! Ree!
	\switchcolumn
	\charactername{菲比：}瑞！瑞！瑞！瑞！瑞！
	\switchcolumn*
	\ennotmain{Joey enters and he's on the phone.}
	\switchcolumn
	\notmain{乔伊走进来，正在打电话}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{on phone} Uh huh.. uh huh... oh my God! Okay! Okay, I'll be there! \ennotmain{He hangs up and to all.} That was my agent. \ennotmain{He tosses and catches the phone.} My agent has just gotten me a job...in the new Al Pacino movie!
	\switchcolumn
	\charactername{乔伊：}\notmain{打电话}嗯嗯……嗯嗯……天啊！好！好，我马上到！\notmain{挂电话对众人说}是我的经纪人。\notmain{抛接手机}我的经纪人刚给我找了个活儿……在阿尔·帕西诺的新电影里！
	\switchcolumn*
	\charactername{All:} Oh my God! Whoah!
	\switchcolumn
	\charactername{众人：}天啊！哇哦！
	\switchcolumn*
	\charactername{Monica:} Well, what's the part?
	\switchcolumn
	\charactername{莫妮卡：}那是什么角色？
	\switchcolumn*
	\charactername{Joey:} Can you believe this? Al Pacino! This guy's the reason I became an actor! "I'm out of order? Pfeeeh. You're out of order! This whole courtroom's out of order!"
	\switchcolumn
	\charactername{乔伊：}不敢相信吧？阿尔·帕西诺！我就是因为他才当演员的！“是我不讲规矩？呵。是你不讲规矩！整个法庭都不讲规矩！”\notmain{模仿阿尔·帕西诺经典台词}
	\switchcolumn*
	\charactername{Phoebe:} Seriously, what-what's the part?
	\switchcolumn
	\charactername{菲比：}说真的，到底是什么角色？
	\switchcolumn*
	\charactername{Joey:} "Just when I thought I was out, they pull me back in!"
	\switchcolumn
	\charactername{乔伊：}“我本想金盆洗手，他们却又把我拉了回来！”\notmain{继续模仿经典台词}
	\switchcolumn*
	\charactername{Ross:} C'mon, seriously, Joey, what's the part?
	\switchcolumn
	\charactername{罗斯：}别闹了，说真的，乔伊，到底是什么角色？
	\switchcolumn*
	\charactername{Joey:} ...I'm his \ennotmain{mumbles}
	\switchcolumn
	\charactername{乔伊：}……我是他的\notmain{含糊不清}
	\switchcolumn*
	\charactername{Rachel:} ..You're, you're 'mah mah mah' what?
	\switchcolumn
	\charactername{瑞秋：}你是……你是“嘛嘛嘛”什么？
	\switchcolumn*
	\charactername{Joey:} ...I'm his butt double. 'Kay? I play Al Pacino's butt. Alright? He goes into the shower, and then- I'm his butt.
	\switchcolumn
	\charactername{乔伊：}……我是他的臀部替身。行了吧？我演阿尔·帕西诺的屁股。懂吗？他进浴室洗澡，然后——我就是他的屁股。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{trying not to laugh} Oh my God.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{忍住不笑}天啊。
	\switchcolumn*
	\charactername{Joey:} C'mon, you guys. This is a real movie, and Al Pacino's in it, and that's big!
	\switchcolumn
	\charactername{乔伊：}拜托，这可是正经电影，还有阿尔·帕西诺参演，这机会多难得啊！
	\switchcolumn*
	\charactername{Chandler:} Oh no, it's terrific, it's... it's... y'know, you deserve this, after all your years of struggling, you've finally been able to crack your way into show business.
	\switchcolumn
	\charactername{钱德勒：}哦不，这太棒了，这……这……你懂的，这么多年的努力总算没白费，你终于成功闯进演艺圈了\notmain{反讽语气}。
	\switchcolumn*
	\charactername{Joey:} Okay, okay, fine! Make jokes, I don't care! This is a big break for me!
	\switchcolumn
	\charactername{乔伊：}好吧好吧，随便你们笑话！这对我来说可是个大机会！
	\switchcolumn*
	\charactername{Ross:} You're right, you're right, it is...So you gonna invite us all to the big opening?
	\switchcolumn
	\charactername{罗斯：}你说得对，说得对，确实是……那你会邀请我们去参加盛大的首映礼吗？
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the next morning, Monica is getting the door.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，第二天早上，莫妮卡去开门}
	\switchcolumn*
	\charactername{Monica:} Alright, alright, alright...
	\switchcolumn
	\charactername{莫妮卡：}来了来了来了……
	\switchcolumn*
	\ennotmain{Joey enters with Monica's paper and hands it to her.}
	\switchcolumn
	\notmain{乔伊走进来，递给莫妮卡一份报纸}
	\switchcolumn*
	\charactername{Joey:} Here. I need to borrow some moisturizer.
	\switchcolumn
	\charactername{乔伊：}给。我要借点保湿霜。
	\switchcolumn*
	\charactername{Monica:} For what?
	\switchcolumn
	\charactername{莫妮卡：}干嘛用？
	\switchcolumn*
	\charactername{Joey:} What do you think? Today's the big day!
	\switchcolumn
	\charactername{乔伊：}你说呢？今天可是大日子！
	\switchcolumn*
	\charactername{Monica:} Oh my God. Okay, go into the bathroom, use whatever you want, just don't ever tell me what you did in there.
	\switchcolumn
	\charactername{莫妮卡：}天啊。行吧，去浴室拿，想用啥用啥，就是别告诉我你用它干嘛了。
	\switchcolumn*
	\charactername{Joey:} Thank you! \ennotmain{He goes into the bathroom.}
	\switchcolumn
	\charactername{乔伊：}谢谢！\notmain{走进浴室}
	\switchcolumn*
	\ennotmain{Chandler enters with the phone.}
	\switchcolumn
	\notmain{钱德勒拿着电话走进来}
	\switchcolumn*
	\charactername{Chandler:} Where's Joey? His mom's on the phone.
	\switchcolumn
	\charactername{钱德勒：}乔伊呢？他妈妈打电话来了。
	\switchcolumn*
	\charactername{Monica:} He's in the bathroom. I don't think you wanna go in there!
	\switchcolumn
	\charactername{莫妮卡：}他在浴室呢。我觉得你最好别进去！
	\switchcolumn*
	\charactername{Chandler:} C'mon, we're roommates! \ennotmain{He goes into the bathroom, screams, and runs back out.} My eyes!! My eyes!!
	\switchcolumn
	\charactername{钱德勒：}拜托，我们可是室友！\notmain{走进浴室，尖叫着跑出来}我的眼睛！我的眼睛！
	\switchcolumn*
	\charactername{Monica:} I warned you...
	\switchcolumn
	\charactername{莫妮卡：}我警告过你了……
	\switchcolumn*
	\ennotmain{Rachel enters from her room.}
	\switchcolumn
	\notmain{瑞秋从房间里出来}
	\switchcolumn*
	\charactername{Rachel:} Who is being loud?
	\switchcolumn
	\charactername{瑞秋：}谁这么吵啊？
	\switchcolumn*
	\charactername{Chandler:} Oh, that would be Monica. Hey, listen, I wanna borrow a coupla things, Aurora spent the night, I really wanna make her breakfast.
	\switchcolumn
	\charactername{钱德勒：}哦，是莫妮卡\notmain{调侃}。嘿，对了，我想借点东西，奥罗拉昨晚在我那儿过夜，我想给她做早餐。
	\switchcolumn*
	\charactername{Monica:} Oh, you got the whole night, huh?
	\switchcolumn
	\charactername{莫妮卡：}哦，你们待了一整晚啊？
	\switchcolumn*
	\charactername{Chandler:} Yeah, well, I only have twenty minutes until Ethan, so, y'know.. \ennotmain{He starts to raid the fridge.}
	\switchcolumn
	\charactername{钱德勒：}是啊，不过再过二十分钟伊桑就要来了，所以……\notmain{开始在冰箱里翻找}
	\switchcolumn*
	\charactername{Rachel:} Ooh, do I sense a little bit of resentment?
	\switchcolumn
	\charactername{瑞秋：}哦，我怎么感觉你有点不爽啊？
	\switchcolumn*
	\charactername{Chandler:} No, no resentment, believe me, it's worth it. 'Kay? Y'know in a relationship you have these key moments that you know you'll remember for the rest of your life? Well, every- single- second is like that with Aurora.. and I've just wasted about thirty-five of them talking to you people, so, uh.. Monica, can you help me with the door? \ennotmain{He has armloads of stuff.}
	\switchcolumn
	\charactername{钱德勒：}没有，我才没不爽呢，相信我，这一切都值得。对吧？你知道吗，感情里总有一些关键时刻，让你觉得一辈子都忘不了？跟奥罗拉在一起的每——一——秒都是这种时刻……我已经跟你们浪费了大概三十五秒了，所以，呃……莫妮卡，能帮我开下门吗？\notmain{他怀里抱满了东西}
	\switchcolumn*
	\charactername{Monica:} Sure. Oh, um, Chandler? Y'know, the-the old Monica would-would remind you to scrub that Teflon pan with a plastic brush...But I'm not gonna do that.
	\switchcolumn
	\charactername{莫妮卡：}当然。哦，对了，钱德勒？以前的我肯定会提醒你，要用塑料刷子刷不粘锅……但现在我不会了。
	\switchcolumn*
	\ennotmain{She opens the door and he leaves.}
	\switchcolumn
	\notmain{她打开门，钱德勒离开了}
	\switchcolumn*
	\sense{Scene: A Film Set, Joey is entering for his scene.}
	\switchcolumn
	\sense{场景：电影片场，乔伊来拍他的戏份}
	\switchcolumn*
	\charactername{Director:} \ennotmain{on phone}...Dammit, hire the girl! \ennotmain{He hangs up the phone.} Okay, everybody ready?
	\switchcolumn
	\charactername{导演：}\notmain{打电话}……该死，就雇那个女孩！\notmain{挂电话}好了，大家都准备好了吗？
	\switchcolumn*
	\charactername{Joey:} Uh, listen, I just wanna thank you for this great opportunity.
	\switchcolumn
	\charactername{乔伊：}呃，那个，我想谢谢你们给我这个宝贵的机会。
	\switchcolumn*
	\charactername{Director:} Lose the robe.
	\switchcolumn
	\charactername{导演：}把浴袍脱了。
	\switchcolumn*
	\charactername{Joey:} Me?
	\switchcolumn
	\charactername{乔伊：}我吗？
	\switchcolumn*
	\charactername{Director:} That would work.
	\switchcolumn
	\charactername{导演：}不然呢。
	\switchcolumn*
	\charactername{Joey:} Right. Okay. Losing the robe. \ennotmain{He takes off the robe.} And the robe is lost.
	\switchcolumn
	\charactername{乔伊：}好的好的。脱浴袍。\notmain{脱掉浴袍}浴袍脱完了。
	\switchcolumn*
	\charactername{Director:} Okay, everybody, we'd like to get this in one take, please. Let's roll it.. water's working \ennotmain{The shower starts}.. and... action.
	\switchcolumn
	\charactername{导演：}好了各位，争取一条过。开拍……水开了\notmain{淋浴喷头开始出水}……开始！
	\switchcolumn*
	\ennotmain{Joey starts to the shower with a grim, determined look on his face.}
	\switchcolumn
	\notmain{乔伊表情严肃、坚定地走向淋浴间}
	\switchcolumn*
	\charactername{Director:} And cut. Hey, Butt Guy, what the hell are you doing?
	\switchcolumn
	\charactername{导演：}停。嘿，屁股替身，你搞什么鬼？
	\switchcolumn*
	\charactername{Joey:} Well, I'm- I'm showering.
	\switchcolumn
	\charactername{乔伊：}我……我在洗澡啊。
	\switchcolumn*
	\charactername{Director:} No, that was clenching.
	\switchcolumn
	\charactername{导演：}不，你那是在紧绷\notmain{臀部肌肉}。
	\switchcolumn*
	\charactername{Joey:} Oh. Well, the way I see it, the guy's upset here, y'know? I mean, his wife's dead, his brother's missing... I think his butt would be angry here.
	\switchcolumn
	\charactername{乔伊：}哦。可是我觉得，这个角色现在很伤心啊，对吧？他妻子死了，弟弟失踪了……我觉得他的屁股也该很愤怒。
	\switchcolumn*
	\charactername{Director:} I think his butt would like to get this shot before lunch. Once again, rolling... water working... and action....and cut. What was that?
	\switchcolumn
	\charactername{导演：}我觉得他的屁股更想在午饭前拍完这场戏。再来一次，开拍……水开了……开始！……停。又搞什么？
	\switchcolumn*
	\charactername{Joey:} I was going for quiet desperation. But if you have to ask...
	\switchcolumn
	\charactername{乔伊：}我这是在演绎无声的绝望。不过既然你问了，说明我演得还不够明显……
	\switchcolumn*
	\sense{Scene: Chandler and Joey's, Aurora and Chandler are in bed in Chandler's room.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，奥罗拉和钱德勒躺在床上}
	\switchcolumn*
	\charactername{Chandler:} God, I love these fingers...
	\switchcolumn
	\charactername{钱德勒：}天啊，我太爱这几根手指了……
	\switchcolumn*
	\charactername{Aurora:} Thank you.
	\switchcolumn
	\charactername{奥罗拉：}谢谢。
	\switchcolumn*
	\charactername{Chandler:} No, actually I meant my fingers. Look at 'em, look at how happy they are.
	\switchcolumn
	\charactername{钱德勒：}不，其实我说的是我的手指。你看它们，多开心啊。
	\switchcolumn*
	\charactername{Aurora:} \ennotmain{moves Chandler's arm and look at his watch.} Oh my God, I'm late. \ennotmain{She starts to get up.}
	\switchcolumn
	\charactername{奥罗拉：}\notmain{挪开钱德勒的胳膊看了看他的手表}天啊，我迟到了。\notmain{开始起身}
	\switchcolumn*
	\charactername{Chandler:} Oh no nonononononnononono, don't go.. \ennotmain{He kisses her and pulls her back down.}
	\switchcolumn
	\charactername{钱德勒：}哦不不要不要不要不要，别走……\notmain{吻了吻她，把她拉回床上}
	\switchcolumn*
	\charactername{Aurora:} Okay.
	\switchcolumn
	\charactername{奥罗拉：}好吧。
	\switchcolumn*
	\charactername{Chandler:} Don't go.
	\switchcolumn
	\charactername{钱德勒：}别走嘛。
	\switchcolumn*
	\charactername{Aurora:} Okay. Oh no, I have to.
	\switchcolumn
	\charactername{奥罗拉：}好吧。不行，我真得走了。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{to himself} Too bad, she's leaving.
	\switchcolumn
	\charactername{钱德勒：}\notmain{自言自语}真可惜，她要走了。
	\switchcolumn*
	\charactername{Aurora:} \ennotmain{getting up and dressing} I'm sorry. He'll be waiting for me.
	\switchcolumn
	\charactername{奥罗拉：}\notmain{起身穿衣}抱歉。他会等我的。
	\switchcolumn*
	\charactername{Chandler:} Well, I thought- I thought you talked to Rick.
	\switchcolumn
	\charactername{钱德勒：}我以为——我以为你跟里克说过了。
	\switchcolumn*
	\charactername{Aurora:} It's not Rick.
	\switchcolumn
	\charactername{奥罗拉：}不是里克。
	\switchcolumn*
	\charactername{Chandler:} What, Ethan? He got to spend the whole day with you!
	\switchcolumn
	\charactername{钱德勒：}什么，是伊桑？他都跟你待了一整天了！
	\switchcolumn*
	\charactername{Aurora:} No, it's-it's Andrew.
	\switchcolumn
	\charactername{奥罗拉：}不是，是——是安德鲁。
	\switchcolumn*
	\charactername{Chandler:} I know there'll be many moments in the years to come when I'll regret asking the following question, but- And Andrew is?
	\switchcolumn
	\charactername{钱德勒：}我知道以后肯定会后悔问这个问题，但——安德鲁是谁？
	\switchcolumn*
	\charactername{Aurora:} He's... new.
	\switchcolumn
	\charactername{奥罗拉：}他是……新的\notmain{伴侣}。
	\switchcolumn*
	\charactername{Chandler:} Oh, so what you're saying is you're not completely fulfilled by Rick, Ethan and myself?
	\switchcolumn
	\charactername{钱德勒：}哦，所以你的意思是，有了里克、伊桑和我，你还不满足？
	\switchcolumn*
	\charactername{Aurora:} No, that's not exactly what I was..
	\switchcolumn
	\charactername{奥罗拉：}不是，我不是那个意思……
	\switchcolumn*
	\charactername{Chandler:} Well, y'know, most women would kill for three guys like us.
	\switchcolumn
	\charactername{钱德勒：}大多数女人要是能有我们三个这样的伴侣，做梦都得笑醒。
	\switchcolumn*
	\charactername{Aurora:} So what do you want?
	\switchcolumn
	\charactername{奥罗拉：}那你想要什么？
	\switchcolumn*
	\charactername{Chandler:} You.
	\switchcolumn
	\charactername{钱德勒：}我想要你。
	\switchcolumn*
	\charactername{Aurora:} You have me!
	\switchcolumn
	\charactername{奥罗拉：}你已经拥有我了啊！
	\switchcolumn*
	\charactername{Chandler:} Nono, just you.
	\switchcolumn
	\charactername{钱德勒：}不，我想要只有你\notmain{只属于我}。
	\switchcolumn*
	\charactername{Aurora:} Whaddyou mean?
	\switchcolumn
	\charactername{奥罗拉：}你什么意思？
	\switchcolumn*
	\charactername{Chandler:} Lose the other guys.
	\switchcolumn
	\charactername{钱德勒：}跟其他人断了。
	\switchcolumn*
	\charactername{Aurora:} ...Like, ...all of them?
	\switchcolumn
	\charactername{奥罗拉：}……所-所有的人？
	\switchcolumn*
	\charactername{Chandler:} C'mon, we're great together, why not?
	\switchcolumn
	\charactername{钱德勒：}拜托，我们在一起多好啊，为什么不呢？
	\switchcolumn*
	\charactername{Aurora:} Why can't we just have what we have now? Why can't we just talk, and laugh, and make love, without feeling obligated to one another... and up until tonight I thought that's what you wanted too.
	\switchcolumn
	\charactername{奥罗拉：}为什么不能保持现在这样？为什么我们不能只是聊天、欢笑、做爱，不用对彼此负责……而且我一直以为这也是你想要的。
	\switchcolumn*
	\charactername{Chandler:} ...Well, y'know, part of me wants that, but it's like I'm two guys, y'know? I mean, one guy's going 'Shut up! This is great!' But there's this other guy. Actually it's the same guy that wells up every time that Grinch's heart grows three sizes and breaks that measuring device... And he's saying, y'know, 'This is too hard! Get out! Get out!'
	\switchcolumn
	\charactername{钱德勒：}……其实呢，我内心一部分是想要那样的，但我好像有两个自己，懂吗？一个声音在说“闭嘴！这多好啊！”但还有另一个声音。其实每次看《圣诞怪杰》里，怪杰的心脏变大三倍撑破测量仪时，就是这个声音让我热泪盈眶……这个声音在说“这太煎熬了！快逃！快逃！”
	\switchcolumn*
	\charactername{Aurora:} So... which one of the two guys will you listen to?
	\switchcolumn
	\charactername{奥罗拉：}那……你会听哪个声音的？
	\switchcolumn*
	\charactername{Chandler:} I don't know, I-I have to listen to both of them, they don't exactly let each other finish...
	\switchcolumn
	\charactername{钱德勒：}我不知道，我——我两个都得听，它们根本不让对方把话说完……
	\switchcolumn*
	\charactername{Aurora:} Which one?
	\switchcolumn
	\charactername{奥罗拉：}到底听哪个？
	\switchcolumn*
	\charactername{Chandler:} ...The second guy.
	\switchcolumn
	\charactername{钱德勒：}……第二个。
	\switchcolumn*
	\charactername{Aurora:} \ennotmain{gets up to leave} Well, call me if you change your mind.
	\switchcolumn
	\charactername{奥罗拉：}\notmain{起身准备离开}好吧，想通了给我打电话。
	\switchcolumn*
	\ennotmain{She kisses him, he holds her, and kisses her passionately.}
	\switchcolumn
	\notmain{她吻了吻他，他抱住她，深情地回吻}
	\switchcolumn*
	\charactername{Chandler:} Sorry, the first guy runs the lips.
	\switchcolumn
	\charactername{钱德勒：}抱歉，嘴唇归第一个声音管。
	\switchcolumn*
	\ennotmain{She leaves, Chandler sighs, and falls back on his bed.}
	\switchcolumn
	\notmain{她离开了，钱德勒叹了口气，倒回床上}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Ross is trying to comfort Chandler.  Joey is absent.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，罗斯在安慰钱德勒。乔伊不在}
	\switchcolumn*
	\charactername{Ross:} Look at it this way: you dumped her. Right? I mean, this woman was unbelievably sexy, and beautiful, intelligent, unattainable... Tell me why you did this again?
	\switchcolumn
	\charactername{罗斯：}换个角度想：是你甩了她。对吧？她那么性感、漂亮、聪明，还遥不可及……再跟我说说你为啥要这么做？
	\switchcolumn*
	\ennotmain{Joey enters.}
	\switchcolumn
	\notmain{乔伊走进来}
	\switchcolumn*
	\charactername{All:} Hey!
	\switchcolumn
	\charactername{众人：}嘿！
	\switchcolumn*
	\charactername{Monica:} Hey, waitwait, aren't you the guy that plays the butt in the new Al Pacino movie?
	\switchcolumn
	\charactername{莫妮卡：}嘿，等等，你不就是那个在阿尔·帕西诺新电影里演屁股的人吗？
	\switchcolumn*
	\charactername{Joey:} Nope.
	\switchcolumn
	\charactername{乔伊：}不是了。
	\switchcolumn*
	\charactername{Ross:} No? What happened, big guy?
	\switchcolumn
	\charactername{罗斯：}不是了？怎么了，兄弟？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{to Ross} "Big guy?"
	\switchcolumn
	\charactername{钱德勒：}\notmain{对罗斯}“兄弟”？
	\switchcolumn*
	\charactername{Ross:} It felt like a 'big guy' moment.
	\switchcolumn
	\charactername{罗斯：}这场景就适合说“兄弟”。
	\switchcolumn*
	\charactername{Joey:} I got fired.
	\switchcolumn
	\charactername{乔伊：}我被解雇了。
	\switchcolumn*
	\charactername{All:} Oh!
	\switchcolumn
	\charactername{众人：}哦！
	\switchcolumn*
	\charactername{Joey:} Yeah, they said I acted too much with it. I told everybody about this! Now everybody's gonna go to the theatre, expecting to see me, and...
	\switchcolumn
	\charactername{乔伊：}是啊，他们说我用屁股“演得太用力”了。我到处跟人说了这事！现在大家都会去电影院，期待看到我，结果……
	\switchcolumn*
	\charactername{Rachel:} Oh, Joey, you know what, no-one is gonna be able to tell.
	\switchcolumn
	\charactername{瑞秋：}哦乔伊，没事的，没人会发现的。
	\switchcolumn*
	\charactername{Joey:} My mom will.
	\switchcolumn
	\charactername{乔伊：}我妈会发现的。
	\switchcolumn*
	\charactername{Chandler:} Something so sweet and...disturbing about that.
	\switchcolumn
	\charactername{钱德勒：}这话听着又暖心又……让人毛骨悚然。
	\switchcolumn*
	\charactername{Joey:} Y'know, I've done nothing but crappy plays for six years. And I finally get my shot, and I blow it!
	\switchcolumn
	\charactername{乔伊：}我六年来演的全是烂话剧。好不容易得到这么个机会，还被我搞砸了！
	\switchcolumn*
	\charactername{Monica:} Maybe this wasn't your shot.
	\switchcolumn
	\charactername{莫妮卡：}也许这根本就不是你的机会。
	\switchcolumn*
	\charactername{Ross:} Yeah, I mean... I think when it's your shot, y'know, you-you know it's your shot. Did it... feel like your shot..?
	\switchcolumn
	\charactername{罗斯：}对啊，我是说……真正属于你的机会，你是能感觉到的。你当时……觉得这是你的机会吗？
	\switchcolumn*
	\charactername{Joey:} Hard to tell, I was naked.
	\switchcolumn
	\charactername{乔伊：}不好说，我当时光着身子呢。
	\switchcolumn*
	\charactername{Phoebe:} No, I don't think this was your shot. I mean, I don't even think you just get one shot. I really believe big things are gonna happen for you, I do! You've gotta just keep thinking about the day that some kid is gonna run up to his friends and go 'I got the part! I got the part! I'm gonna be Joey Tribbiani's ass!'
	\switchcolumn
	\charactername{菲比：}不，我觉得这不是你的机会。而且我觉得人生也不止一次机会。我真的相信你以后一定会有大成就的！你要记住，总有一天会有个小孩跑去找他朋友，兴奋地说“我拿到角色了！我拿到角色了！我要演乔伊·崔比安尼的屁股啦！”
	\switchcolumn*
	\charactername{Joey:} Yeah? That's so nice! \ennotmain{They hug.}
	\switchcolumn
	\charactername{乔伊：}真的吗？你真好！\notmain{两人拥抱}
	\switchcolumn*
	\ennotmain{Ross and Chandler look at each other and hug as well.}
	\switchcolumn
	\notmain{罗斯和钱德勒对视一眼，也拥抱了一下}
	\switchcolumn*
	\charactername{Monica:} I'm sorry, Joey. I'm gonna go to bed, guys.
	\switchcolumn
	\charactername{莫妮卡：}乔伊，真为你难过。我要去睡觉了，大伙儿。
	\switchcolumn*
	\charactername{All:} Night.
	\switchcolumn
	\charactername{众人：}晚安。
	\switchcolumn*
	\charactername{Rachel:} Uh, Mon, you-you gonna leave your shoes out here?
	\switchcolumn
	\charactername{瑞秋：}呃，莫妮卡，你要把鞋子放这儿吗？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{determined} Uh-huh!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{坚定地}对啊！
	\switchcolumn*
	\charactername{Rachel:} Really? Just casually strewn about in that reckless haphazard manner?
	\switchcolumn
	\charactername{瑞秋：}真的吗？就这么随意乱摆在这儿，不管不顾？
	\switchcolumn*
	\charactername{Monica:} Doesn't matter, I'll get 'em tomorrow. Or not. Whenever. \ennotmain{He goes to her room.}
	\switchcolumn
	\charactername{莫妮卡：}无所谓，明天再拿。或者不拿。什么时候想拿再说。\notmain{走进自己的房间}
	\switchcolumn*
	\charactername{Ross:} She is a kook.
	\switchcolumn
	\charactername{罗斯：}她真的很疯癫。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica's Bedroom, she's lying in bed wide awake.}
	\switchcolumn
	\sense{场景：莫妮卡的卧室，她躺在床上毫无睡意}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{hums for a while, then gives up, and in her head} If it bothers you that much, just go out and get the shoes. No. Don't do this. This is stupid! I don't have to prove anything, I'm gonna go get them...But then everyone will know. Unless I get them, and then wake up really early and put them back! ...I need help! \ennotmain{She buries her head in her pillow.}
	\switchcolumn
	\charactername{莫妮卡：}\notmain{哼了一会儿歌，然后放弃，在心里想}既然这么难受，就出去把鞋子拿进来啊。不行。别这么做。太傻了！我不用向任何人证明什么，我要去拿……但那样大家就都知道了。除非我现在去拿，然后明天一早再摆回去！……我需要帮助！\notmain{把头埋进枕头里}
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage