\begin{paracol}{2}
	\sense{Scene: Central Perk, Rachel is introducing Phoebe, who is playing her guitar for the crowd.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，瑞秋正在为众人介绍弹吉他的菲比}
	\switchcolumn*
	\charactername{Rachel:} Everybody? Shh, shhh. Uhhh... Central Perk is proud to present the music of Miss Phoebe Buffay.
	\switchcolumn
	\charactername{瑞秋：}大家注意一下？嘘，嘘。呃……中央公园咖啡馆荣幸为大家带来菲比·布菲小姐的音乐表演。
	\switchcolumn*
	\ennotmain{applause}
	\switchcolumn
	\notmain{掌声}
	\switchcolumn*
	\charactername{Phoebe:} Hi. Um, I want to start with a song thats about that moment when you suddenly realize what life is all about. OK, here we go. \ennotmain{plays a chord, then the lights go out} OK, thank you very much.
	\switchcolumn
	\charactername{菲比：}嗨。嗯，我想先唱一首关于那个瞬间的歌——当你突然明白人生的意义是什么的瞬间。好，开始了。\notmain{弹了一个和弦，然后灯灭了}好的，非常感谢大家。
	\switchcolumn*
	\sense{Scene: The ATM vestibule of a bank, Chandler is inside. The lights go out, and he realizes he is trapped inside.}
	\switchcolumn
	\sense{场景：银行的ATM机房，钱德勒在里面。灯灭了，他意识到自己被困住了}
	\switchcolumn*
	\charactername{Chandler:} Oh, great. This is just...
	\switchcolumn
	\charactername{钱德勒：}哦，太棒了。这简直是……
	\switchcolumn*
	\ennotmain{Chandler sees that there is a gorgeous model inside the vestibule with him. He makes a gesture of quiet exuberance.}
	\switchcolumn
	\notmain{钱德勒看到机房里还有一位美艳的模特。他暗自兴奋地做了个手势}
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Monica is on the phone with her mother. Phoebe, Rachel, and Ross are there.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，莫妮卡正在和妈妈打电话。菲比、瑞秋和罗斯都在}
	\switchcolumn*
	\charactername{Rachel:} Wow, this is so cool, you guys. The entire city is blacked out!
	\switchcolumn
	\charactername{瑞秋：}哇，太酷了伙计们。整个城市都停电了！
	\switchcolumn*
	\charactername{Monica:} Mom says it's all of Manhattan, parts of Brooklyn and Queens, and they have no idea when it's coming back on.
	\switchcolumn
	\charactername{莫妮卡：}妈妈说曼哈顿全片区、布鲁克林和皇后区的部分地区都停了，而且他们完全不知道什么时候会恢复供电。
	\switchcolumn*
	\charactername{Rachel:} Wow, you guys, this is big.
	\switchcolumn
	\charactername{瑞秋：}哇，这事儿可真大。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{into phone} Pants and a sweater? Why, mom? Who am I gonna meet in a blackout? Power company guys? Eligible looters? Could we talk about this later? OK. \ennotmain{hangs up}
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对着电话}穿裤子和毛衣？为什么啊妈妈？停电的时候我能遇到谁？电力公司的人？合适的抢劫犯？我们能晚点再说这个吗？好的。\notmain{挂电话}
	\switchcolumn*
	\charactername{Phoebe:} Can I borrow the phone? I want to call my apartment and check on my grandma. \ennotmain{to Monica} What's my number?
	\switchcolumn
	\charactername{菲比：}我能借下电话吗？我想打给我的公寓，看看奶奶怎么样了。\notmain{对莫妮卡}我的电话号码是多少来着？
	\switchcolumn*
	\ennotmain{Monica and Rachel look at Phoebe strangely.}
	\switchcolumn
	\notmain{莫妮卡和瑞秋奇怪地看着菲比}
	\switchcolumn*
	\charactername{Phoebe:} Well, I never call me.
	\switchcolumn
	\charactername{菲比：}好吧，我从来没给自己打过电话。
	\switchcolumn*
	\sense{Scene: ATM vestibule, Jill Goodacre is on the cellular phone. Chandler's thoughts are in italics.}
	\switchcolumn
	\sense{场景：ATM机房，吉尔·古达克正在用手机打电话。钱德勒的内心想法用斜体表示}
	\switchcolumn*
	\charactername{Chandler:} Oh my God, it's that Victoria's Secret model. Something... something Goodacre.
	\switchcolumn
	\charactername{钱德勒：}天啊，是那位维多利亚的秘密模特。叫什么……古达克什么的。
	\switchcolumn*
	\charactername{Jill:} \ennotmain{on phone} Hi Mom, it's Jill.
	\switchcolumn
	\charactername{吉尔：}\notmain{打电话}嗨妈妈，是我吉尔。
	\switchcolumn*
	\charactername{Chandler:} She's right, it's Jill. Jill Goodacre. Oh my God. I am trapped in an ATM vestibule with Jill Goodacre! \ennotmain{pause} Is it a vestibule? Maybe it's an atrium. Oh, yeah, that is the part to focus on, you idiot!
	\switchcolumn
	\charactername{钱德勒：}她说得对，是吉尔。吉尔·古达克。天啊。我居然和吉尔·古达克一起被困在ATM机房里了！\notmain{停顿}这地方叫机房吗？也许叫中庭？哦对，现在重点是这个，你个白痴！
	\switchcolumn*
	\charactername{Jill:} \ennotmain{on phone} Yeah, I'm fine. I'm just stuck at the bank, in an ATM vestibule.
	\switchcolumn
	\charactername{吉尔：}\notmain{打电话}嗯，我没事。我就是被困在银行的ATM机房里了。
	\switchcolumn*
	\charactername{Chandler:} Jill says vestibule... I'm going with vestibule.
	\switchcolumn
	\charactername{钱德勒：}吉尔说叫机房……那我就叫它机房吧。
	\switchcolumn*
	\charactername{Jill:} \ennotmain{on phone} I'm fine. No, I'm not alone... I don't know, some guy.
	\switchcolumn
	\charactername{吉尔：}\notmain{打电话}我没事。不，我不是一个人……不知道，就某个男的。
	\switchcolumn*
	\charactername{Chandler:} Oh! Some guy. Some guy. 'Hey Jill, I saw you with some guy last night. Yes, he was some guy.
	\switchcolumn
	\charactername{钱德勒：}哦！某个男的。某个男的。“嘿吉尔，我昨晚看到你和某个男的在一起。对，就是某个男的。”
	\switchcolumn*
	\ennotmain{Chandler strides proudly across the vestibule and Jill stares at him.}
	\switchcolumn
	\notmain{钱德勒骄傲地大步穿过机房，吉尔盯着他看}
	\switchcolumn*
	\sense{Scene: Monica's apartment, Joey enters with a menorah, the candles lit.}
	\switchcolumn
	\sense{场景：莫妮卡的公寓，乔伊举着点燃蜡烛的 menorah\notmain{犹太教光明节烛台}走进来}
	\switchcolumn*
	\charactername{Joey:} Hi everyone.
	\switchcolumn
	\charactername{乔伊：}大家好。
	\switchcolumn*
	\charactername{Ross:} And officiating at tonight's blackout, is Rabbi Tribbiani.
	\switchcolumn
	\charactername{罗斯：}今晚停电仪式的主持者，是崔比安尼拉比\notmain{对乔伊的调侃}。
	\switchcolumn*
	\charactername{Joey:} Well, Chandler's old roomate was Jewish, and these are the only candles we have, so... Happy Chanukah, everyone.
	\switchcolumn
	\charactername{乔伊：}嗯，钱德勒以前的室友是犹太人，而且这是我们仅有的蜡烛了，所以……大家光明节快乐。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{at window} Eww, look. Ugly Naked Guy lit a bunch of candles.
	\switchcolumn
	\charactername{菲比：}\notmain{在窗边}呃，快看。裸体丑男点了一堆蜡烛。
	\switchcolumn*
	\ennotmain{They all look at the window, grossed out, then flinch in pain.}
	\switchcolumn
	\notmain{他们都看向窗户，觉得恶心，然后痛苦地抽搐了一下}
	\switchcolumn*
	\charactername{Rachel:} That had to hurt!
	\switchcolumn
	\charactername{瑞秋：}那肯定很疼吧！
	\switchcolumn*
	\sense{Scene: ATM vestibule.}
	\switchcolumn
	\sense{场景：ATM机房}
	\switchcolumn*
	\charactername{Chandler:} Alright, alright, alright. It's been fourteen and a half minutes and you still have not said one word. Oh God, do something. Just make contact, smile!
	\switchcolumn
	\charactername{钱德勒：}好了好了好了。已经十四分半钟了，你还是一句话都没跟我说。天啊，做点什么吧。哪怕只是对视一下，笑一笑也好！
	\switchcolumn*
	\ennotmain{Chandler smiles at her, she smiles back sweetly.}
	\switchcolumn
	\notmain{钱德勒对她笑了笑，她温柔地回笑}
	\switchcolumn*
	\charactername{Chandler:} There you go!
	\switchcolumn
	\charactername{钱德勒：}这就对了！
	\switchcolumn*
	\ennotmain{He continues to smile like an idiot, and she looks frightened.}
	\switchcolumn
	\notmain{他继续像个白痴一样傻笑，她看起来有点害怕了}
	\switchcolumn*
	\charactername{Chandler:} You're definitely scaring here.
	\switchcolumn
	\charactername{钱德勒：}你绝对把她吓到了。
	\switchcolumn*
	\charactername{Jill:} \ennotmain{awkwardly} Would you like to call somebody? \ennotmain{offering phone}
	\switchcolumn
	\charactername{吉尔：}\notmain{尴尬地}你想给别人打个电话吗？\notmain{递过手机}
	\switchcolumn*
	\charactername{Chandler:} Yeah, about 300 guys I went to high school with. Yeah, thanks. \ennotmain{takes phone}
	\switchcolumn
	\charactername{钱德勒：}想啊，我想打给我高中时的大概三百个同学。好，谢谢。\notmain{接过手机}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, The phone rings; it's Chandler.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，电话响了，是钱德勒打来的}
	\switchcolumn*
	\charactername{Monica:} Hello?
	\switchcolumn
	\charactername{莫妮卡：}喂？
	\switchcolumn*
	\charactername{Chandler:} Hey, it's me.
	\switchcolumn
	\charactername{钱德勒：}嘿，是我。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to everyone} It's Chandler! \ennotmain{on phone} Are you OK?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对大家}是钱德勒！\notmain{对着电话}你还好吗？
	\switchcolumn*
	\charactername{Chandler:} Yeah, I'm fine. \ennotmain{trying to cover up what he is saying} I'm trppd in an ATM vstbl wth Jll Gdcr.
	\switchcolumn
	\charactername{钱德勒：}嗯，我没事。\notmain{试图掩饰自己说的话}我被困在ATM机房里了，和吉尔·古达克一起。
	\switchcolumn*
	\charactername{Monica:} What?
	\switchcolumn
	\charactername{莫妮卡：}什么？
	\switchcolumn*
	\charactername{Chandler:} I'm trppd... in an ATM vstbl... wth Jll Gdcr!
	\switchcolumn
	\charactername{钱德勒：}我被困……在ATM机房……和吉尔·古达克一起！
	\switchcolumn*
	\charactername{Monica:} I have no idea what you just said.
	\switchcolumn
	\charactername{莫妮卡：}我完全听不懂你在说什么。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{angry} Put Joey on the phone.
	\switchcolumn
	\charactername{钱德勒：}\notmain{生气地}让乔伊接电话。
	\switchcolumn*
	\charactername{Joey:} What's up man?
	\switchcolumn
	\charactername{乔伊：}怎么了兄弟？
	\switchcolumn*
	\charactername{Chandler:} I'm trppd... in an ATM vstbl... wth JLL GDCR.
	\switchcolumn
	\charactername{钱德勒：}我被困……在ATM机房……和吉尔·古达克一起！
	\switchcolumn*
	\charactername{Joey:} \ennotmain{to everyone} Oh my God! He's trapped in an ATM vestibule with Jill Goodacre! \ennotmain{on phone} Chandler, listen. \ennotmain{says something intentionally garbled}
	\switchcolumn
	\charactername{乔伊：}\notmain{对大家}天啊！他和吉尔·古达克一起被困在ATM机房里了！\notmain{对着电话}钱德勒，听着。\notmain{故意说些含混不清的话}
	\switchcolumn*
	\charactername{Chandler:} Yeah, like that thought never entered my mind.
	\switchcolumn
	\charactername{钱德勒：}是啊，我可从来没这么想过\notmain{反讽}。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, time has passed. The five are sitting around the coffee table talking.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，过了一会儿。五个人围坐在咖啡桌旁聊天}
	\switchcolumn*
	\charactername{Rachel:} Alright, somebody.
	\switchcolumn
	\charactername{瑞秋：}快来个人说啊。
	\switchcolumn*
	\charactername{Monica:} OK, I'll go. OK, senior year of college... on a pool table.
	\switchcolumn
	\charactername{莫妮卡：}好，我来说。嗯，大学四年级……在台球桌上。
	\switchcolumn*
	\charactername{All:} Whoooaa!
	\switchcolumn
	\charactername{众人：}哇哦！
	\switchcolumn*
	\charactername{Ross:} That's my sister.
	\switchcolumn
	\charactername{罗斯：}这可是我妹妹啊。
	\switchcolumn*
	\charactername{Joey:} OK... my weirdest place would have to be... the women's room on the second floor of the New York CIty public library.
	\switchcolumn
	\charactername{乔伊：}好……我最奇怪的地方是……纽约公共图书馆二楼的女厕所。
	\switchcolumn*
	\charactername{Monica:} Oh my God! What were you doing in a library?
	\switchcolumn
	\charactername{莫妮卡：}天啊！你去图书馆干嘛？
	\switchcolumn*
	\charactername{Ross:} Pheebs, what about you?
	\switchcolumn
	\charactername{罗斯：}菲比，你呢？
	\switchcolumn*
	\charactername{Phoebe:} Oh... Milwaukee.
	\switchcolumn
	\charactername{菲比：}哦……密尔沃基\notmain{美国城市}。
	\switchcolumn*
	\charactername{Rachel:} Um... Ross?
	\switchcolumn
	\charactername{瑞秋：}嗯……罗斯？
	\switchcolumn*
	\charactername{Ross:} Disneyland, 1989, 'It's a Small World After All.'
	\switchcolumn
	\charactername{罗斯：}1989年，迪士尼乐园，“小小世界”游乐设施里。
	\switchcolumn*
	\charactername{All:} No way!
	\switchcolumn
	\charactername{众人：}不会吧！
	\switchcolumn*
	\charactername{Ross:} The ride broke down. So, Carol and I went behind a couple of those mechanical Dutch children... then they fixed the ride, and we were asked never to return to the Magic Kingdom.
	\switchcolumn
	\charactername{罗斯：}游乐设施坏了。所以我和卡萝就躲到了几个荷兰机械娃娃后面……然后他们修好了设施，我们被要求永远不准再回到魔法王国。
	\switchcolumn*
	\charactername{Phoebe:} Oh, Rachel.
	\switchcolumn
	\charactername{菲比：}哦，瑞秋。
	\switchcolumn*
	\charactername{Rachel:} Oh come on, I already went.
	\switchcolumn
	\charactername{瑞秋：}拜托，我已经说过了。
	\switchcolumn*
	\charactername{Monica:} You did not go!
	\switchcolumn
	\charactername{莫妮卡：}你根本没说！
	\switchcolumn*
	\charactername{All:} Come on.
	\switchcolumn
	\charactername{众人：}快说嘛。
	\switchcolumn*
	\charactername{Rachel:} Oh, alright. The weirdest place would have to be... \ennotmain{sigh}... oh, the foot of the bed.
	\switchcolumn
	\charactername{瑞秋：}哦，好吧。我最奇怪的地方是……\notmain{叹气}……哦，床脚边。
	\switchcolumn*
	\charactername{Ross:} Step back.
	\switchcolumn
	\charactername{罗斯：}厉害啊\notmain{表示惊叹}。
	\switchcolumn*
	\charactername{Joey:} We have a winner!
	\switchcolumn
	\charactername{乔伊：}冠军诞生了！
	\switchcolumn*
	\sense{Time lapse, Ross and Rachel are talking, Joey is on the couch, and Monica and Phoebe are out of the room.}
	\switchcolumn
	\sense{时间快进，罗斯和瑞秋在聊天，乔伊坐在沙发上，莫妮卡和菲比不在房间里}
	\switchcolumn*
	\charactername{Rachel:} I just never had a relationship with that kind of passion, you know, where you have to have somebody right there, in the middle of a theme park.
	\switchcolumn
	\charactername{瑞秋：}我从来没有过那种充满激情的感情，你知道吗，就是那种在主题公园中间，就迫不及待要和对方在一起的感觉。
	\switchcolumn*
	\charactername{Ross:} Well, it was the only thing to do there that didn't have a line.
	\switchcolumn
	\charactername{罗斯：}嗯，那地方也就只有这件事不用排队了。
	\switchcolumn*
	\charactername{Rachel:} There, well, see? Barry wouldn't even kiss me on a miniature golf course.
	\switchcolumn
	\charactername{瑞秋：}你看，对吧？巴里连在迷你高尔夫球场都不肯吻我。
	\switchcolumn*
	\charactername{Ross:} Come on.
	\switchcolumn
	\charactername{罗斯：}不会吧。
	\switchcolumn*
	\charactername{Rachel:} No, he said we were holding up the people behind us.
	\switchcolumn
	\charactername{瑞秋：}真的，他说我们耽误后面的人了。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{sarcastically} And you didn't marry him because...?
	\switchcolumn
	\charactername{罗斯：}\notmain{讽刺地}那你没嫁给她是因为……？
	\switchcolumn*
	\charactername{Rachel:} I mean, do you think there are people who go through life never having that kind of...
	\switchcolumn
	\charactername{瑞秋：}我是说，你觉得有没有人一辈子都没有过那种……
	\switchcolumn*
	\charactername{Ross:} Probably. But you know, I'll tell you something. Passion is way overrated.
	\switchcolumn
	\charactername{罗斯：}可能有吧。不过我告诉你，激情被高估了。
	\switchcolumn*
	\charactername{Rachel:} Yeah right.
	\switchcolumn
	\charactername{瑞秋：}才怪。
	\switchcolumn*
	\charactername{Ross:} It is. Eventually, it kind of... burns out. But hopefully, what you're left with is trust, and security, and... well, in the case of my ex-wife, lesbianism. So, you know, for all of those people who miss out on that passion... thing, there's all that other good stuff.
	\switchcolumn
	\charactername{罗斯：}真的。最终，激情总会……消退的。但希望剩下的是信任、安全感，还有……嗯，就我的前妻来说，是女同性恋倾向。所以，那些没体验过激情……这玩意儿的人，也能拥有其他美好的东西。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{sigh} OK.
	\switchcolumn
	\charactername{瑞秋：}\notmain{叹气}好吧。
	\switchcolumn*
	\charactername{Ross:} But, um... I don't think that's going to be you.
	\switchcolumn
	\charactername{罗斯：}不过，嗯……我觉得你不会是那样的人。
	\switchcolumn*
	\charactername{Rachel:} You don't.
	\switchcolumn
	\charactername{瑞秋：}你觉得不会？
	\switchcolumn*
	\charactername{Ross:} Uh-uh. See, I see.... big passion in your future.
	\switchcolumn
	\charactername{罗斯：}嗯。我看到……你的未来充满了激情。
	\switchcolumn*
	\charactername{Rachel:} Really?
	\switchcolumn
	\charactername{瑞秋：}真的吗？
	\switchcolumn*
	\charactername{Ross:} Mmmm.
	\switchcolumn
	\charactername{罗斯：}嗯。
	\switchcolumn*
	\charactername{Rachel:} You do?
	\switchcolumn
	\charactername{瑞秋：}你真这么觉得？
	\switchcolumn*
	\charactername{Ross:} I do.
	\switchcolumn
	\charactername{罗斯：}真的。
	\switchcolumn*
	\charactername{Rachel:} Oh Ross, you're so great. \ennotmain{she playfully rubs his head and gets up}
	\switchcolumn
	\charactername{瑞秋：}哦罗斯，你真好。\notmain{她开玩笑地揉了揉他的头，然后站起来}
	\switchcolumn*
	\ennotmain{Ross gets up, pleased with himself.}
	\switchcolumn
	\notmain{罗斯站起来，对自己很满意}
	\switchcolumn*
	\charactername{Joey:} It's never gonna happen.
	\switchcolumn
	\charactername{乔伊：}这事儿永远不会成的。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{innocently} What?
	\switchcolumn
	\charactername{罗斯：}\notmain{无辜地}什么？
	\switchcolumn*
	\charactername{Joey:} You and Rachel.
	\switchcolumn
	\charactername{乔伊：}你和瑞秋啊。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{acts surprised} What? \ennotmain{pause} Why not?
	\switchcolumn
	\charactername{罗斯：}\notmain{装作惊讶}什么？\notmain{停顿}为什么不会？
	\switchcolumn*
	\charactername{Joey:} Because you waited too long to make your move, and now you're in the friend zone.
	\switchcolumn
	\charactername{乔伊：}因为你迟迟不行动，现在你已经被划入朋友区了。
	\switchcolumn*
	\charactername{Ross:} No, no, no. I'm not in the zone.
	\switchcolumn
	\charactername{罗斯：}不，不，不。我没在朋友区。
	\switchcolumn*
	\charactername{Joey:} Ross, you're mayor of the zone.
	\switchcolumn
	\charactername{乔伊：}罗斯，你都是朋友区的市长了。
	\switchcolumn*
	\charactername{Ross:} I'm taking my time, alright? I'm laying the groundwork. Yeah. I mean, every day I get just a little bit closer to...
	\switchcolumn
	\charactername{罗斯：}我这是在循序渐进，好吧？我在打基础。是啊。我是说，我每天都离……
	\switchcolumn*
	\charactername{Joey:} Priesthood! Look Ross, I'm telling you, she has no idea what you're thinking. If you don't ask her out soon you're going to end up stuck in the zone forever.
	\switchcolumn
	\charactername{乔伊：}神职人员\notmain{调侃他会一直单身}！听着罗斯，我跟你说，她完全不知道你在想什么。如果你再不约她，你就永远困在朋友区里了。
	\switchcolumn*
	\charactername{Ross:} I will, I will. See, I'm waiting for the right moment. \ennotmain{Joey looks at him} What? What, now?
	\switchcolumn
	\charactername{罗斯：}我会的，我会的。你看，我在等合适的时机。\notmain{乔伊看着他}怎么了？现在就是时机？
	\switchcolumn*
	\charactername{Joey:} Yeeeeaaaahhh! What's messing you up? The wine? The candles? The moonlight? You've just got to go up to her and say, 'Rachel, I think that...' \ennotmain{Rachel comes into the room behind them}
	\switchcolumn
	\charactername{乔伊：}对——啊！有什么好纠结的？有酒有蜡烛还有月光？你只要走到她面前说，“瑞秋，我觉得……”\notmain{瑞秋从他们身后走进房间}
	\switchcolumn*
	\charactername{Ross:} Shhhh!
	\switchcolumn
	\charactername{罗斯：}嘘！
	\switchcolumn*
	\charactername{Rachel:} What are you shushing?
	\switchcolumn
	\charactername{瑞秋：}你们嘘什么呢？
	\switchcolumn*
	\charactername{Ross:} We're shushing... because... we're trying to hear something. Listen. \ennotmain{everyone is silent} Don't you hear that?
	\switchcolumn
	\charactername{罗斯：}我们嘘……是因为……我们在试着听某个声音。听。\notmain{大家都安静下来}你没听到吗？
	\switchcolumn*
	\charactername{Rachel:} Ahhhh!
	\switchcolumn
	\charactername{瑞秋：}啊！\notmain{配合他假装听到}
	\switchcolumn*
	\charactername{Ross:} See?
	\switchcolumn
	\charactername{罗斯：}你看？
	\switchcolumn*
	\charactername{Rachel:} Huh. \ennotmain{she agrees, but looks very confused}
	\switchcolumn
	\charactername{瑞秋：}嗯。\notmain{她表示同意，但看起来很困惑}
	\switchcolumn*
	\sense{Scene: ATM vestibule.}
	\switchcolumn
	\sense{场景：ATM机房}
	\switchcolumn*
	\charactername{Jill:} Would you like some gum?
	\switchcolumn
	\charactername{吉尔：}你想吃口香糖吗？
	\switchcolumn*
	\charactername{Chandler:} Um, is it sugarless?
	\switchcolumn
	\charactername{钱德勒：}嗯，是无糖的吗？
	\switchcolumn*
	\charactername{Jill:} \ennotmain{checks} Sorry, it's not.
	\switchcolumn
	\charactername{吉尔：}\notmain{看了看}抱歉，不是。
	\switchcolumn*
	\charactername{Chandler:} Oh, then no thanks. What the hell was that? Mental note: If Jill Goodacre offers you gum, you take it. If she offers you mangled animal carcass, you take it.
	\switchcolumn
	\charactername{钱德勒：}哦，那算了谢谢。我刚才到底在干嘛？心理笔记：如果吉尔·古达克给你口香糖，你就拿着。就算她给你一具残缺的动物尸体，你也得拿着。
	\switchcolumn*
	\sense{Scene: Monica's apartment, Phoebe is singing.}
	\switchcolumn
	\sense{场景：莫妮卡的公寓，菲比在唱歌}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{singing} New York City has no power, and the milk is getting sour. But to me it is not scary, 'cause I stay away from dairy.... la la la, la la, la la... \ennotmain{she writes the lyrics down}
	\switchcolumn
	\charactername{菲比：}\notmain{唱}纽约城停了电，牛奶都变酸。但我一点不害怕，因为我不吃奶制品……啦啦啦，啦啦，啦啦……\notmain{她把歌词写下来}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{to Joey} OK, here goes.
	\switchcolumn
	\charactername{罗斯：}\notmain{对乔伊}好了，我要上了。
	\switchcolumn*
	\charactername{Joey:} Are you going to do it?
	\switchcolumn
	\charactername{乔伊：}你真要去？
	\switchcolumn*
	\charactername{Ross:} I'm going to do it.
	\switchcolumn
	\charactername{罗斯：}真要去。
	\switchcolumn*
	\charactername{Joey:} Do you want any help?
	\switchcolumn
	\charactername{乔伊：}需要帮忙吗？
	\switchcolumn*
	\charactername{Ross:} You come out there, you're a dead man.
	\switchcolumn
	\charactername{罗斯：}你敢出来，就死定了。
	\switchcolumn*
	\charactername{Joey:} Good luck, man.
	\switchcolumn
	\charactername{乔伊：}祝你好运，兄弟。
	\switchcolumn*
	\charactername{Ross:} Thanks. \ennotmain{Joey hugs him} OK.
	\switchcolumn
	\charactername{罗斯：}谢谢。\notmain{乔伊拥抱他}好了。
	\switchcolumn*
	\charactername{Joey:} OK. \ennotmain{Ross goes out on the balcony to talk to Rachel}
	\switchcolumn
	\charactername{乔伊：}好。\notmain{罗斯走到阳台上去找瑞秋说话}
	\switchcolumn*
	\ennotmain{Monica walks in, starts to go out on the balcony.}
	\switchcolumn
	\notmain{莫妮卡走进来，准备去阳台}
	\switchcolumn*
	\charactername{Joey:} Hey, where are you going?
	\switchcolumn
	\charactername{乔伊：}嘿，你要去哪儿？
	\switchcolumn*
	\charactername{Monica:} Outside.
	\switchcolumn
	\charactername{莫妮卡：}外面。
	\switchcolumn*
	\charactername{Joey:} You can't go out there.
	\switchcolumn
	\charactername{乔伊：}你不能去那儿。
	\switchcolumn*
	\charactername{Monica:} Why not?
	\switchcolumn
	\charactername{莫妮卡：}为什么不能？
	\switchcolumn*
	\charactername{Joey:} Because of... the reason.
	\switchcolumn
	\charactername{乔伊：}因为……某个原因。
	\switchcolumn*
	\charactername{Monica:} And that would be?
	\switchcolumn
	\charactername{莫妮卡：}什么原因？
	\switchcolumn*
	\charactername{Joey:} I, um, can't tell you.
	\switchcolumn
	\charactername{乔伊：}我，嗯，不能告诉你。
	\switchcolumn*
	\charactername{Monica:} Joey, what's going on?
	\switchcolumn
	\charactername{莫妮卡：}乔伊，到底怎么了？
	\switchcolumn*
	\charactername{Joey:} OK, you've got to promise that you'll never, ever tell Ross that I told you.
	\switchcolumn
	\charactername{乔伊：}好吧，你得保证永远永远不要告诉罗斯是我说的。
	\switchcolumn*
	\charactername{Monica:} About what?
	\switchcolumn
	\charactername{莫妮卡：}说什么？
	\switchcolumn*
	\charactername{Joey:} He's planning your birthday party.
	\switchcolumn
	\charactername{乔伊：}他在给你策划生日派对。
	\switchcolumn*
	\charactername{Monica:} Oh my God! I love him!
	\switchcolumn
	\charactername{莫妮卡：}天啊！我爱死他了！
	\switchcolumn*
	\charactername{Joey:} \ennotmain{as Phoebe enters} You'd better act surprised.
	\switchcolumn
	\charactername{乔伊：}\notmain{菲比走进来}你最好表现得惊讶点。
	\switchcolumn*
	\charactername{Phoebe:} About what?
	\switchcolumn
	\charactername{菲比：}惊讶什么？
	\switchcolumn*
	\charactername{Monica:} My surprise party!
	\switchcolumn
	\charactername{莫妮卡：}我的惊喜派对！
	\switchcolumn*
	\charactername{Phoebe:} What surprise party?
	\switchcolumn
	\charactername{菲比：}什么惊喜派对？
	\switchcolumn*
	\charactername{Monica:} Oh stop it. Joey already told me.
	\switchcolumn
	\charactername{莫妮卡：}哦别装了。乔伊都告诉我了。
	\switchcolumn*
	\charactername{Phoebe:} Well, he didn't tell me.
	\switchcolumn
	\charactername{菲比：}可他没告诉我啊。
	\switchcolumn*
	\charactername{Joey:} Hey, don't look at me. This is Ross's thing.
	\switchcolumn
	\charactername{乔伊：}嘿，别看我。这是罗斯的主意。
	\switchcolumn*
	\charactername{Phoebe:} This is so typical. I'm always the last one to know everything.
	\switchcolumn
	\charactername{菲比：}真是太典型了。什么事我都是最后一个知道。
	\switchcolumn*
	\charactername{Monica:} No, you are not. We tell you stuff.
	\switchcolumn
	\charactername{莫妮卡：}才不是呢。我们什么都告诉你啊。
	\switchcolumn*
	\charactername{Phoebe:} Yuh-huh! I was the last one to know when Chandler got bitten by the peacock at the zoo. I was the last one to know when you had a crush on Joey when he was moving in. \ennotmain{Monica gestures at Phoebe to shut up; Joey looks surprised but pleased} Looks like I was second to last.
	\switchcolumn
	\charactername{菲比：}就是！钱德勒在动物园被孔雀咬了，我是最后一个知道的。乔伊搬进来的时候你对他有好感，我也是最后一个知道的。\notmain{莫妮卡示意菲比闭嘴；乔伊看起来很惊讶但又很得意}看来这次我是倒数第二个知道的。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's Balcony, Ross and Rachel are talking.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的阳台，罗斯和瑞秋在聊天}
	\switchcolumn*
	\charactername{Rachel:} Hmmm... this is so nice.
	\switchcolumn
	\charactername{瑞秋：}嗯……真舒服。
	\switchcolumn*
	\charactername{Ross:} OK, I have a question. Well, actually, it's not so much a question as.. more of a general wondering... ment.
	\switchcolumn
	\charactername{罗斯：}好吧，我有个问题。嗯，其实也算不上问题，更像是一种……普遍的疑惑。
	\switchcolumn*
	\charactername{Rachel:} OK.
	\switchcolumn
	\charactername{瑞秋：}好啊。
	\switchcolumn*
	\charactername{Ross:} OK. Here goes. For a while now, I've been wanting to, um....
	\switchcolumn
	\charactername{罗斯：}好。那我问了。其实有一阵子了，我一直想，嗯……
	\switchcolumn*
	\charactername{Rachel:} Ohhh!!!! \ennotmain{looking at something behind Ross}
	\switchcolumn
	\charactername{瑞秋：}哦！！！\notmain{看着罗斯身后的某个东西}
	\switchcolumn*
	\charactername{Ross:} Yes, yes, that's right...
	\switchcolumn
	\charactername{罗斯：}对，对，就是……
	\switchcolumn*
	\charactername{Rachel:} Oh, look at the little cat! \ennotmain{a small kitten is on the roof behind Ross}
	\switchcolumn
	\charactername{瑞秋：}哦，快看那只小猫！\notmain{罗斯身后的屋顶上有一只小猫}
	\switchcolumn*
	\charactername{Ross:} What? \ennotmain{the cat jumps on his shoulders} Ow!
	\switchcolumn
	\charactername{罗斯：}什么？\notmain{小猫跳到了他的肩膀上}哎哟！
	\switchcolumn*
	\sense{Cut to inside. Monica, Joey and Phoebe are singing while outside, Ross and Rachel are trying to get the cat off of Ross' shoulder.}
	\switchcolumn
	\sense{切到室内。莫妮卡、乔伊和菲比在唱歌，而外面罗斯和瑞秋正试着把小猫从罗斯的肩膀上弄下来}
	\switchcolumn*
	\charactername{Monica, Joey, and Phoebe:} \ennotmain{singing} I'm on top of the world, looking down on creation and the only explanation I can find, is the wonders I've found ever since...
	\switchcolumn
	\charactername{莫妮卡、乔伊、菲比：}\notmain{唱}我站在世界之巅，俯瞰世间万物，我能找到的唯一解释，就是自从我发现了那些奇迹之后……
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Phoebe is holding the cat, Monica is treating the scratches on Ross' back. Joey is holding the menorah over the wound.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，菲比抱着小猫，莫妮卡正在处理罗斯背上的抓痕。乔伊举着 menorah 照亮伤口}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Ross} This is just Bactine. It won't hurt.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对罗斯}这只是巴克汀\notmain{一种外用抗菌剂}。不会疼的。
	\switchcolumn*
	\ennotmain{Ross flinches in pain.}
	\switchcolumn
	\notmain{罗斯疼得抽搐了一下}
	\switchcolumn*
	\charactername{Joey:} Sorry, that was wax.
	\switchcolumn
	\charactername{乔伊：}抱歉，那是蜡烛油。
	\switchcolumn*
	\charactername{Phoebe:} Oh, poor little Tooty is scared to death. We should find his owner.
	\switchcolumn
	\charactername{菲比：}哦，可怜的小图图吓得要死。我们得找到它的主人。
	\switchcolumn*
	\charactername{Ross:} Why don't we just put 'poor little Tooty' out in the hall?
	\switchcolumn
	\charactername{罗斯：}我们为什么不把“可怜的小图图”放到走廊里去？
	\switchcolumn*
	\charactername{Rachel:} During a blackout? He'd get trampled!
	\switchcolumn
	\charactername{瑞秋：}停电的时候放出去？它会被踩扁的！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{nonchalantly} Yeah?
	\switchcolumn
	\charactername{罗斯：}\notmain{无所谓地}是吗？
	\switchcolumn*
	\sense{Scene: ATM vestibule.}
	\switchcolumn
	\sense{场景：ATM机房}
	\switchcolumn*
	\charactername{Chandler:} You know, on second thought, gum would be perfection. \ennotmain{Jill gives him a stick of gum, and a strange look} 'Gum would be perfection'? 'Gum would be perfection.' Could have said 'gum would be nice,' or 'I'll have a stick,' but no, no, no, no. For me, gum is perfection. I loathe myself.
	\switchcolumn
	\charactername{钱德勒：}你知道吗，我再想想，口香糖简直完美。\notmain{吉尔给了他一片口香糖，并用奇怪的眼神看着他}“口香糖简直完美”？“口香糖简直完美”。我本来可以说“口香糖挺好的”，或者“给我一片”，但不，偏不。对我来说，口香糖就是完美。我真讨厌自己。
	\switchcolumn*
	\sense{Scene: The hallway of Monica's building. Phoebe and Rachel are trying to find the cat's owner.}
	\switchcolumn
	\sense{场景：莫妮卡公寓楼的走廊。菲比和瑞秋正在找小猫的主人}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{stops at a door} Oh no, the Mendels, they hate all living things, right?
	\switchcolumn
	\charactername{菲比：}\notmain{在一扇门前停下}哦不，是门德尔一家，他们讨厌所有活物，对吧？
	\switchcolumn*
	\charactername{Rachel:} Oh. \ennotmain{they knock at the next door, Mr. Heckles answers} Hi. We just found this cat and we're looking for the owner.
	\switchcolumn
	\charactername{瑞秋：}哦。\notmain{她们敲下一扇门，赫克尔斯先生开了门}嗨。我们刚发现这只猫，正在找它的主人。
	\switchcolumn*
	\charactername{Mr. Heckles:} Er, yeah, it's mine.
	\switchcolumn
	\charactername{赫克尔斯先生：}呃，嗯，是我的。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{trying to hold back the struggling cat} He seems to hate you. Are you sure?
	\switchcolumn
	\charactername{菲比：}\notmain{努力按住挣扎的小猫}它好像很讨厌你啊。你确定是你的？
	\switchcolumn*
	\charactername{Mr. Heckles:} Yeah, it's my cat. Give me my cat.
	\switchcolumn
	\charactername{赫克尔斯先生：}是啊，是我的猫。把猫给我。
	\switchcolumn*
	\charactername{Phoebe:} Wait a minute. What's his name?
	\switchcolumn
	\charactername{菲比：}等一下。它叫什么名字？
	\switchcolumn*
	\charactername{Mr. Heckles:} Ehhhh... B-Buttons.
	\switchcolumn
	\charactername{赫克尔斯先生：}呃……巴-巴特斯。
	\switchcolumn*
	\charactername{Rachel:} Bob Buttons?
	\switchcolumn
	\charactername{瑞秋：}鲍勃·巴特斯？
	\switchcolumn*
	\charactername{Mr. Heckles:} Mmm. Bob Buttons. Here, Bob Buttons.
	\switchcolumn
	\charactername{赫克尔斯先生：}嗯。鲍勃·巴特斯。过来，鲍勃·巴特斯。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{the cat runs away from her} Oooh! You are a very bad man!
	\switchcolumn
	\charactername{菲比：}\notmain{小猫从她怀里跑掉了}哦！你真是个坏人！
	\switchcolumn*
	\charactername{Mr. Heckles:} \ennotmain{as Phoebe and Rachel leave} You owe me a cat.
	\switchcolumn
	\charactername{赫克尔斯先生：}\notmain{菲比和瑞秋离开时}你们欠我一只猫。
	\switchcolumn*
	\sense{Scene: Rachel has gone off on her own to look for the cat's owner.}
	\switchcolumn
	\sense{场景：瑞秋一个人去找小猫的主人}
	\switchcolumn*
	\charactername{Rachel:} Here, kitty-kitty. Here kitty-kitty. Where did you go, little kitty-kitty-kitty? Here kitty-kitty-kitty-kitty...
	\switchcolumn
	\charactername{瑞秋：}过来呀小猫咪。过来小猫咪。你去哪儿了呀，小小猫咪？过来呀小小猫咪……
	\switchcolumn*
	\ennotmain{While looking at the floor for the cat, Rachel runs into a pair of legs. She slowly gets up and sees a gorgeous Italian hunk holding the cat. Who, by the way, you'll hate very, very soon. The man. Not the cat.}
	\switchcolumn
	\notmain{瑞秋低头找猫的时候，撞到了一双腿。她慢慢抬起头，看到一个帅气的意大利帅哥抱着那只猫。顺便说一句，你很快就会非常非常讨厌这个男人。是男人，不是猫。}
	\switchcolumn*
	\charactername{Paolo:} \ennotmain{something Italian}
	\switchcolumn
	\charactername{保罗：}\notmain{说了句意大利语}
	\switchcolumn*
	\charactername{Rachel:} Wow. \ennotmain{she exhales in amazement, blowing the candle out}
	\switchcolumn
	\charactername{瑞秋：}哇。\notmain{她惊讶地呼出一口气，把蜡烛吹灭了}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Ross, Monica, and Joey are playing Monopoly.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，罗斯、莫妮卡和乔伊正在玩大富翁游戏}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{rolling} Lucky sixes....
	\switchcolumn
	\charactername{罗斯：}\notmain{掷骰子}幸运的六点……
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{entering with Paolo, arm in arm} Everybody, this is Paolo. Paolo, I want you to meet my friends. This is Monica.
	\switchcolumn
	\charactername{瑞秋：}\notmain{和保罗手挽手走进来}大家，这是保罗。保罗，我来给你介绍我的朋友们。这是莫妮卡。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{smitten} Hi!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{被迷住了}嗨！
	\switchcolumn*
	\charactername{Rachel:} And Joey....
	\switchcolumn
	\charactername{瑞秋：}这是乔伊……
	\switchcolumn*
	\charactername{Monica:} Hi!
	\switchcolumn
	\charactername{莫妮卡：}嗨！
	\switchcolumn*
	\charactername{Rachel:} And Ross.
	\switchcolumn
	\charactername{瑞秋：}这是罗斯。
	\switchcolumn*
	\charactername{Monica:} Hi!
	\switchcolumn
	\charactername{莫妮卡：}嗨！
	\switchcolumn*
	\charactername{Paolo:} \ennotmain{something in Italian}
	\switchcolumn
	\charactername{保罗：}\notmain{说了句意大利语}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{proudly} He doesn't speak much English.
	\switchcolumn
	\charactername{瑞秋：}\notmain{骄傲地}他不太会说英语。
	\switchcolumn*
	\charactername{Paolo:} \ennotmain{pointing at game} Monopoly!
	\switchcolumn
	\charactername{保罗：}\notmain{指着游戏}大富翁！
	\switchcolumn*
	\charactername{Rachel:} Look at that!
	\switchcolumn
	\charactername{瑞秋：}你看他居然知道！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{jealous} So, um... where did Paolo come from?
	\switchcolumn
	\charactername{罗斯：}\notmain{嫉妒地}那个，嗯……保罗是哪儿来的？
	\switchcolumn*
	\charactername{Rachel:} Oh... Italy, I think.
	\switchcolumn
	\charactername{瑞秋：}哦……我想是意大利吧。
	\switchcolumn*
	\charactername{Ross:} No, I mean tonight, in the building. Suddenly. Into our lives.
	\switchcolumn
	\charactername{罗斯：}不，我是说今晚，在这栋楼里。突然就闯进了我们的生活。
	\switchcolumn*
	\charactername{Rachel:} Well, the cat... the cat turned out to be Paolo's cat!
	\switchcolumn
	\charactername{瑞秋：}嗯，因为这只猫……这只猫原来是保罗的！
	\switchcolumn*
	\charactername{Ross:} That, that is funny... \ennotmain{to Joey}.... and Rachel keeps touching him.
	\switchcolumn
	\charactername{罗斯：}那，那可真有意思……\notmain{对乔伊}……而且瑞秋一直碰他。
	\switchcolumn*
	\ennotmain{Phoebe enters.}
	\switchcolumn
	\notmain{菲比走进来}
	\switchcolumn*
	\charactername{Phoebe:} Alright. I looked all over the building and I couldn't find the kitty anywhere.
	\switchcolumn
	\charactername{菲比：}好了。我把整栋楼都找遍了，都没找到那只小猫。
	\switchcolumn*
	\charactername{Rachel:} Oh, I found him. He was Paolo's cat.
	\switchcolumn
	\charactername{瑞秋：}哦，我找到它了。它是保罗的猫。
	\switchcolumn*
	\charactername{Phoebe:} Ah! Well! There you go! Last to know again! And I'm guessing... since nobody told me... this is Paolo.
	\switchcolumn
	\charactername{菲比：}啊！好吧！又是最后一个知道！我猜……既然没人告诉我……这就是保罗吧。
	\switchcolumn*
	\charactername{Rachel:} Ah, Paolo, this is Phoebe.
	\switchcolumn
	\charactername{瑞秋：}啊，保罗，这是菲比。
	\switchcolumn*
	\charactername{Paolo:} \ennotmain{something in Italian, he is apparently attracted to Phoebe}
	\switchcolumn
	\charactername{保罗：}\notmain{说了句意大利语，显然是被菲比吸引了}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{smiling} You betcha!
	\switchcolumn
	\charactername{菲比：}\notmain{微笑着}那当然啦！
	\switchcolumn*
	\sense{Scene: ATM vestibule.}
	\switchcolumn
	\sense{场景：ATM机房}
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{chewing gum} Ah, let's see. What next? Blow a bubble. A bubble's good. It's got a... boyish charm, it's impish. Here we go.
	\switchcolumn
	\charactername{钱德勒：}\notmain{嚼着口香糖}啊，想想接下来做什么。吹个泡泡吧。吹泡泡挺好的。有种……孩子气的魅力，很调皮。开始了。
	\switchcolumn*
	\ennotmain{Chandler waits until Jill is looking, then starts to blow a bubble. But instead of blow one, he accidentally spits the gum out of his mouth and hits the wall.}
	\switchcolumn
	\notmain{钱德勒等吉尔看过来，然后开始吹泡泡。但他没吹出来，反而不小心把口香糖从嘴里吐了出来，粘到了墙上。}
	\switchcolumn*
	\charactername{Chandler:} Nice going, imp. OK, it's OK. All I need to do is reach over and put it in my mouth. \ennotmain{Chandler slyly grabs the gum from the wall and slides it back in his mouth.}
	\switchcolumn
	\charactername{钱德勒：}干得好，小调皮。好吧，没事。我只要伸手把它拿下来放进嘴里就行了。\notmain{钱德勒偷偷地从墙上抠下口香糖，塞回嘴里。}
	\switchcolumn*
	\charactername{Chandler:} Good save! We're back on track, and I'm... \ennotmain{grimacing} ..chewing someone else's gum. This is not my gum. Oh my God! Oh my God! And now you're choking.
	\switchcolumn
	\charactername{钱德勒：}救场成功！我们又回到正轨了，而且我……\notmain{做鬼脸}……在嚼别人的口香糖。这不是我的口香糖。天啊！天啊！现在你还呛到了。
	\switchcolumn*
	\ennotmain{Chandler starts to choke.}
	\switchcolumn
	\notmain{钱德勒开始呛咳}
	\switchcolumn*
	\charactername{Jill:} Are you alright?
	\switchcolumn
	\charactername{吉尔：}你还好吗？
	\switchcolumn*
	\ennotmain{Chandler tries to save face and makes the 'OK' sign with his hands, while obviously unable to breathe.}
	\switchcolumn
	\notmain{钱德勒试图挽回面子，用手比了个“OK”的手势，但显然已经喘不上气了。}
	\switchcolumn*
	\charactername{Jill:} My God, you're choking! \ennotmain{she runs over and gives him the Heimlich, the gum flies from his mouth} That better?
	\switchcolumn
	\charactername{吉尔：}天啊，你呛到了！\notmain{她跑过去给他做海姆立克急救法，口香糖从他嘴里飞了出来}好点了吗？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{gasping} Yes... thank you. That was... that was....
	\switchcolumn
	\charactername{钱德勒：}\notmain{喘气}嗯……谢谢。那真是……那真是……
	\switchcolumn*
	\charactername{Jill:} Perfection?
	\switchcolumn
	\charactername{吉尔：}完美？
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Rachel and Paolo are at the window. Ross and Joey are watching disgustedly.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，瑞秋和保罗在窗边。罗斯和乔伊厌恶地看着他们}
	\switchcolumn*
	\charactername{Paolo:} \ennotmain{something romantic in Italian about Rachel and the stars}
	\switchcolumn
	\charactername{保罗：}\notmain{用意大利语说了句关于瑞秋和星星的浪漫情话}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{mocking Paolo} Blah blah blah, blah blah blah... blah blaaaaaah....
	\switchcolumn
	\charactername{罗斯：}\notmain{模仿保罗}巴拉巴拉巴拉，巴拉巴拉巴拉……巴拉布拉——啊……
	\switchcolumn*
	\ennotmain{Rachel walks away from Paolo, laughing.}
	\switchcolumn
	\notmain{瑞秋笑着从保罗身边走开}
	\switchcolumn*
	\charactername{Ross:} Wha-What did he say that was so funny?
	\switchcolumn
	\charactername{罗斯：}什-他说了什么这么好笑？
	\switchcolumn*
	\charactername{Rachel:} I have absolutely no idea.
	\switchcolumn
	\charactername{瑞秋：}我完全不知道。
	\switchcolumn*
	\charactername{Ross:} That's... that's classic.
	\switchcolumn
	\charactername{罗斯：}那可真是……太经典了\notmain{反讽}。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{to Monica and Phoebe} Oh my God, you guys, what am I doing? What am I doing? This is so un-me!
	\switchcolumn
	\charactername{瑞秋：}\notmain{对莫妮卡和菲比}天啊，伙计们，我在干什么？我在干什么？这太不像我了！
	\switchcolumn*
	\charactername{Monica:} If you want, I'll do it.
	\switchcolumn
	\charactername{莫妮卡：}如果你不想，我来替你\notmain{和他在一起}。
	\switchcolumn*
	\ennotmain{Ross looks at Joey.}
	\switchcolumn
	\notmain{罗斯看向乔伊}
	\switchcolumn*
	\charactername{Phoebe:} I know, I just want to bite his bottom lip. \ennotmain{Rachel looks at her} But I won't.
	\switchcolumn
	\charactername{菲比：}我懂，我只想咬他的下嘴唇。\notmain{瑞秋看向她}不过我不会的。
	\switchcolumn*
	\charactername{Rachel:} God, the first time he smiled at me... those three seconds were more exciting than three weeks in Bermuda with Barry.
	\switchcolumn
	\charactername{瑞秋：}天啊，他第一次对我笑的时候……那三秒钟比和巴里在百慕大待三周还让人兴奋。
	\switchcolumn*
	\charactername{Phoebe:} You know, did you ride mopeds? 'Cause I've heard... \ennotmain{they stare at her}... oh, I see... it's not about that right now. OK.
	\switchcolumn
	\charactername{菲比：}对了，你们骑摩托艇了吗？因为我听说……\notmain{她们盯着她看}……哦，我懂了……现在不是说这个的时候。好吧。
	\switchcolumn*
	\charactername{Rachel:} Y'know, I know it's totally superficial and we have absolutely nothing in common, and we don't even speak the same language but Goooooooddddddd....
	\switchcolumn
	\charactername{瑞秋：}我知道这完全是看脸，我们根本没有共同点，甚至语言都不通，但是真的太……太赞了……
	\switchcolumn*
	\sense{Cut to the other side of the apartment, Ross has gone over to straighten things out with Paolo.}
	\switchcolumn
	\sense{切到公寓的另一边，罗斯走过去想和保罗说清楚}
	\switchcolumn*
	\charactername{Ross:} Paolo. Hi.
	\switchcolumn
	\charactername{罗斯：}保罗。嗨。
	\switchcolumn*
	\charactername{Paolo:} Ross!
	\switchcolumn
	\charactername{保罗：}罗斯！
	\switchcolumn*
	\ennotmain{Ross notices that Paolo is standing on a step, which makes him taller. Ross gets up on the same step so he can look down at Paolo.}
	\switchcolumn
	\notmain{罗斯注意到保罗站在一个台阶上，这样显得他更高。罗斯也站到那个台阶上，这样就能俯视保罗了。}
	\switchcolumn*
	\charactername{Ross:} Listen. Um, listen. Something you should... know... um, Rachel and I... we're kind of a thing.
	\switchcolumn
	\charactername{罗斯：}听着。嗯，听着。有件事你应该……知道……嗯，我和瑞秋……我们算是一对。
	\switchcolumn*
	\charactername{Paolo:} Thing?
	\switchcolumn
	\charactername{保罗：}一对？
	\switchcolumn*
	\charactername{Ross:} Thing, yes. Thing.
	\switchcolumn
	\charactername{罗斯：}对，一对。
	\switchcolumn*
	\charactername{Paolo:} Ah, you... have the sex?
	\switchcolumn
	\charactername{保罗：}啊，你们……上床了？
	\switchcolumn*
	\charactername{Ross:} No, no, no. Technically the... sex is not... being had, but that's... see, that's not the point. See, um, the point is that... Rachel and I should be, er, together. You know, and if you get in the.... um...
	\switchcolumn
	\charactername{罗斯：}不，不，不。严格来说……还没有……上床，但那不是……你看，重点不是这个。重点是……我和瑞秋应该在一起。你知道，如果你要是妨碍……嗯……
	\switchcolumn*
	\charactername{Paolo:} Bed?
	\switchcolumn
	\charactername{保罗：}上床？
	\switchcolumn*
	\charactername{Ross:} No, no, that's not where I was going. Er, if you get in the... way, of us becoming a thing, then I would be, well, very sad.
	\switchcolumn
	\charactername{罗斯：}不，不，我不是那个意思。呃，如果你要是妨碍我们成为一对，那我会……嗯，非常难过。
	\switchcolumn*
	\charactername{Paolo:} Oh!
	\switchcolumn
	\charactername{保罗：}哦！
	\switchcolumn*
	\charactername{Ross:} Yeah! Se vice?
	\switchcolumn
	\charactername{罗斯：}对！明白吗？\notmain{用意大利语问}
	\switchcolumn*
	\charactername{Paolo:} Si.
	\switchcolumn
	\charactername{保罗：}明白。\notmain{用意大利语回答}
	\switchcolumn*
	\charactername{Ross:} So you do know a little English.
	\switchcolumn
	\charactername{罗斯：}所以你还是懂一点英语的。
	\switchcolumn*
	\charactername{Paolo:} Poco... a leetle.
	\switchcolumn
	\charactername{保罗：}一点点……就一点点。
	\switchcolumn*
	\charactername{Ross:} Do you know the word crapweasel?
	\switchcolumn
	\charactername{罗斯：}你知道“混蛋”这个词吗？
	\switchcolumn*
	\charactername{Paolo:} No.
	\switchcolumn
	\charactername{保罗：}不知道。
	\switchcolumn*
	\charactername{Ross:} That's funny, because you know, you are a huge crapweasel!
	\switchcolumn
	\charactername{罗斯：}真有意思，因为你就是个超级大混蛋！
	\switchcolumn*
	\ennotmain{They hug.}
	\switchcolumn
	\notmain{他们拥抱了一下}
	\switchcolumn*
	\sense{Scene: ATM vestibule, Chandler and Jill are sitting below the counter with two pens dangling from their chains in front of them. Jill is showing Chandler how to swing the pen around his head.}
	\switchcolumn
	\sense{场景：ATM机房，钱德勒和吉尔坐在柜台下面，面前有两支挂在链子上的笔。吉尔在教钱德勒怎么把笔绕着头转。}
	\switchcolumn*
	\charactername{Jill:} Chandler, we've been here for an hour doing this! Now watch, it's easy.
	\switchcolumn
	\charactername{吉尔：}钱德勒，我们已经在这儿玩了一个小时了！看好了，很简单的。
	\switchcolumn*
	\charactername{Chandler:} OK.
	\switchcolumn
	\charactername{钱德勒：}好。
	\switchcolumn*
	\charactername{Jill:} Ready? \ennotmain{she swings the pen around her head in a circle}
	\switchcolumn
	\charactername{吉尔：}准备好了吗？\notmain{她把笔绕着头转了一圈}
	\switchcolumn*
	\ennotmain{Chandler tries to do the same thing but the pen hits him in the head.}
	\switchcolumn
	\notmain{钱德勒试着照做，但笔打到了他的头。}
	\switchcolumn*
	\charactername{Jill:} No, you've got to whip it.
	\switchcolumn
	\charactername{吉尔：}不对，你得用力甩。
	\switchcolumn*
	\ennotmain{He swings the pen hard, and it snaps back and almost hits him again.}
	\switchcolumn
	\notmain{他用力甩笔，笔弹了回来，差点又打到他。}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the gang is all sitting around the table.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，大家都围坐在桌子旁}
	\switchcolumn*
	\charactername{Phoebe:} Oh, look look look. The last candle's about to burn out. 10, 9, 8, 7... \ennotmain{time lapse}... negative 46, negative 47, negative 48.... \ennotmain{someone blows it out, the room gets completely dark}
	\switchcolumn
	\charactername{菲比：}哦，快看快看快看。最后一根蜡烛要烧完了。10，9，8，7……\notmain{时间快进}……负46，负47，负48……\notmain{有人吹灭了蜡烛，房间完全变黑了}
	\switchcolumn*
	\charactername{Ross:} Thank you.
	\switchcolumn
	\charactername{罗斯：}谢谢\notmain{终于吹灭了}。
	\switchcolumn*
	\charactername{Phoebe:} Thanks.
	\switchcolumn
	\charactername{菲比：}谢谢。
	\switchcolumn*
	\charactername{Ross:} Kinda... spooky without any lights.
	\switchcolumn
	\charactername{罗斯：}没有灯……有点吓人。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{does a maniacal laugh} Bwah-hah-hah!
	\switchcolumn
	\charactername{乔伊：}\notmain{发出疯狂的笑声}哇哈-哈-哈！
	\switchcolumn*
	\ennotmain{Everyone starts to imitate him.}
	\switchcolumn
	\notmain{大家都开始模仿他笑}
	\switchcolumn*
	\charactername{Ross:} OK, guys, guys? I have the definitive one. Mwwwooooo-hah-hah...
	\switchcolumn
	\charactername{罗斯：}好了，伙计们，听我的。呜——哈-哈……\notmain{模仿更吓人的笑声}
	\switchcolumn*
	\ennotmain{The lights come back on, and Rachel and Paolo are making out. Ross clutches his chest.}
	\switchcolumn
	\notmain{灯突然亮了，瑞秋和保罗正在亲热。罗斯捂住胸口。}
	\switchcolumn*
	\charactername{Ross:} Oh.. oh... oh.
	\switchcolumn
	\charactername{罗斯：}哦……哦……哦。
	\switchcolumn*
	\charactername{Joey:} Hey Ross. This probably isn't the best time to bring it up, but you have to throw a party for Monica.
	\switchcolumn
	\charactername{乔伊：}嘿罗斯。现在说可能不是时候，但你得给莫妮卡办个派对。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: ATM vestibule, the power has come back on.}
	\switchcolumn
	\sense{场景：ATM机房，电力恢复了}
	\switchcolumn*
	\charactername{Jill:} Well, this has been fun.
	\switchcolumn
	\charactername{吉尔：}嗯，今天挺开心的。
	\switchcolumn*
	\charactername{Chandler:} Yes. Yes, thanks for letting me use your phone... and for saving my life.
	\switchcolumn
	\charactername{钱德勒：}是啊。是啊，谢谢你借我手机……还救了我的命。
	\switchcolumn*
	\charactername{Jill:} Well, goodbye Chandler. I had a great blackout. \ennotmain{she kisses him on the cheek} See ya.
	\switchcolumn
	\charactername{吉尔：}好吧，再见钱德勒。这个停电夜我过得很开心。\notmain{她吻了吻他的脸颊}回头见。
	\switchcolumn*
	\ennotmain{She leaves. Chandler presses his face to the glass door after her, stroking the window lovingly. He then turns to the security camera and starts talking to it.}
	\switchcolumn
	\notmain{她离开了。钱德勒把脸贴在玻璃门上看着她，温柔地抚摸着窗户。然后他转向监控摄像头，开始对着它说话。}
	\switchcolumn*
	\charactername{Chandler:} Hi, um, I'm account number 7143457. And, uh, I don't know if you got any of that, but I would really like a copy of the tape.
	\switchcolumn
	\charactername{钱德勒：}嗨，嗯，我的账户号码是7143457。那个，嗯，我不知道你们有没有拍到刚才的画面，但我真的很想要一份录像带副本。
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage