\begin{paracol}{2}
	\sense{Scene: Chandler's Office, Chandler is on a coffee break. Shelley enters.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，钱德勒正在喝咖啡休息。谢莉走进来。}
	\switchcolumn*
	\charactername{Shelley:} Hey gorgeous, how's it going?
	\switchcolumn
	\charactername{谢莉：}嘿，帅哥，最近怎么样？
	\switchcolumn*
	\charactername{Chandler:} Dehydrated Japanese noodles under fluorescent lights... does it get better than this?
	\switchcolumn
	\charactername{钱德勒：}荧光灯下的脱水日式泡面……还有比这更惬意的吗？\notmain{反讽语气}
	\switchcolumn*
	\charactername{Shelley:} Question. You're not dating anybody, are you, because I met somebody who would be perfect for you.
	\switchcolumn
	\charactername{谢莉：}问你个事。你现在没在约会吧？因为我认识个人，跟你简直是天造地设。
	\switchcolumn*
	\charactername{Chandler:} Ah, y'see, perfect might be a problem. Had you said 'co-dependent', or 'self-destructive'...
	\switchcolumn
	\charactername{钱德勒：}啊，你看，“天造地设”可能就麻烦了。要是你说“依赖型”或者“自毁型”……\notmain{调侃自己}
	\switchcolumn*
	\charactername{Shelley:} Do you want a date Saturday?
	\switchcolumn
	\charactername{谢莉：}周六要不要约个会？
	\switchcolumn*
	\charactername{Chandler:} Yes please.
	\switchcolumn
	\charactername{钱德勒：}好呀，麻烦啦。
	\switchcolumn*
	\charactername{Shelley:} Okay. He's cute, he's funny, he's-
	\switchcolumn
	\charactername{谢莉：}好嘞。他人帅又风趣，而且他——
	\switchcolumn*
	\charactername{Chandler:} He's a he?
	\switchcolumn
	\charactername{钱德勒：}他是个男的？
	\switchcolumn*
	\charactername{Shelley:} Well yeah! ...Oh God. I- just- I thought- Good, Shelley. I'm just gonna go flush myself down the toilet now...\ennotmain{backs out of the room} Okay, goodbye...
	\switchcolumn
	\charactername{谢莉：}对啊！……哦天啊。我——只是——我以为——好吧，谢莉你真行。我现在就去把自己冲进马桶里……\notmain{退着走出房间}那再见啦……
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, everyone is there.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，所有人都在。}
	\switchcolumn*
	\charactername{Chandler:} ...Couldn't enjoy a cup of noodles after that. I mean, is that ridiculous? Can you believe she actually thought that?
	\switchcolumn
	\charactername{钱德勒：}……经历了这事，我连泡面都吃不下了。我是说，这也太离谱了吧？你们敢信她居然那么想我？
	\switchcolumn*
	\charactername{Rachel:} Um... yeah. Well, I mean, when I first met you, y'know, I thought maybe, possibly, you might be...
	\switchcolumn
	\charactername{瑞秋：}嗯……是啊。其实，我刚认识你的时候，你知道的，我也觉得可能、说不定，你或许是……
	\switchcolumn*
	\charactername{Chandler:} You did?
	\switchcolumn
	\charactername{钱德勒：}你也这么想？
	\switchcolumn*
	\charactername{Rachel:} Yeah, but then you spent Phoebe's entire birthday party talking to my breasts, so then I figured maybe not.
	\switchcolumn
	\charactername{瑞秋：}对啊，但后来菲比的生日派对上，你全程都在跟我的胸说话，所以我就觉得可能不是了。
	\switchcolumn*
	\charactername{Chandler:} Huh. Did, uh... any of the rest of you guys think that when you first met me?
	\switchcolumn
	\charactername{钱德勒：}哈。那……你们其他人刚认识我的时候，也这么想过吗？
	\switchcolumn*
	\charactername{Monica:} I did.
	\switchcolumn
	\charactername{莫妮卡：}我想过。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, I think so, yeah.
	\switchcolumn
	\charactername{菲比：}嗯，我觉得是，对。
	\switchcolumn*
	\charactername{Joey:} Not me.
	\switchcolumn
	\charactername{乔伊：}我没有。
	\switchcolumn*
	\charactername{Ross:} Nono, me neither. Although, uh, y'know, back in college, Susan Sallidor did.
	\switchcolumn
	\charactername{罗斯：}不，我也没有。不过，呃，你知道吗，大学的时候，苏珊·萨利多就这么想过。
	\switchcolumn*
	\charactername{Chandler:} You're kidding! Did you tell her I wasn't?
	\switchcolumn
	\charactername{钱德勒：}你开玩笑吧！你没跟她说我不是吗？
	\switchcolumn*
	\charactername{Ross:} No. No, it's just 'cause, uh, I kinda wanted to go out with her too, so I told her, actually, you were seeing Bernie Spellman... who also liked her, so...
	\switchcolumn
	\charactername{罗斯：}没有。因为，呃，我当时也想跟她约会，所以我就跟她说，其实你在跟伯尼·斯佩尔曼交往……而伯尼也喜欢她，所以……
	\switchcolumn*
	\ennotmain{Joey congratulates Ross, sees Chandler's look and abruptly stops.}
	\switchcolumn
	\notmain{乔伊向罗斯表示祝贺，看到钱德勒的表情后突然停了下来。}
	\switchcolumn*
	\charactername{Chandler:} Well, this is fascinating. So, uh, what is it about me?
	\switchcolumn
	\charactername{钱德勒：}哇，这可真有意思。那……我到底哪点让人这么想啊？
	\switchcolumn*
	\charactername{Phoebe:} I dunno, 'cause you're smart, you're funny...
	\switchcolumn
	\charactername{菲比：}我不知道啊，可能因为你又聪明又风趣……
	\switchcolumn*
	\charactername{Chandler:} Ross is smart and funny, d'you ever think that about him?
	\switchcolumn
	\charactername{钱德勒：}罗斯也又聪明又风趣啊，你们会这么想他吗？
	\switchcolumn*
	\charactername{All:} Yeah! Right!
	\switchcolumn
	\charactername{众人：}会啊！对啊！
	\switchcolumn*
	\charactername{Chandler:} WHAT IS IT?!
	\switchcolumn
	\charactername{钱德勒：}到底是为什么啊？！
	\switchcolumn*
	\charactername{Monica:} Okay, I-I d'know, you-you just- you have a quality.
	\switchcolumn
	\charactername{莫妮卡：}好吧，我——我不知道，你——你就是——有种特质。
	\switchcolumn*
	\charactername{All:} Yes. Absolutely. A quality.
	\switchcolumn
	\charactername{众人：}对。没错。就是一种特质。
	\switchcolumn*
	\charactername{Chandler:} Oh, oh, a quality, good, because I was worried you guys were gonna be vague about this.
	\switchcolumn
	\charactername{钱德勒：}哦，哦，一种特质，行吧，我还担心你们会说得含糊其辞呢。\notmain{反讽}
	\switchcolumn*
	\ennotmain{Phone rings; Monica gets it}
	\switchcolumn
	\notmain{电话铃响；莫妮卡接起电话}
	\switchcolumn*
	\charactername{Monica:} Hello? Hello? Oh! Rachel, it's Paolo calling from Rome.
	\switchcolumn
	\charactername{莫妮卡：}喂？喂？哦！瑞秋，是保罗从罗马打来的。
	\switchcolumn*
	\charactername{Rachel:} Oh my God! Calling from Rome! \ennotmain{Takes phone} Bon giorno, caro mio.
	\switchcolumn
	\charactername{瑞秋：}天啊！从罗马打来的！\notmain{接过电话}日安，我亲爱的。\notmain{意大利语}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{to Joey} So he's calling from Rome. I could do that. Just gotta go to Rome.
	\switchcolumn
	\charactername{罗斯：}\notmain{对乔伊}他居然从罗马打电话来。我也能啊，只要去趟罗马就行了。
	\switchcolumn*
	\charactername{Rachel:} Monica, your dad just beeped in, but can you make it quick? Talking to Rome. \ennotmain{Showing off to Phoebe and Chandler} I'm talking to Rome.
	\switchcolumn
	\charactername{瑞秋：}莫妮卡，你爸爸的电话插进来了，但能快点吗？我在跟罗马通话呢。\notmain{向菲比和钱德勒炫耀}我在跟罗马通话哦。
	\switchcolumn*
	\charactername{Monica:} Hey dad, what's up? \ennotmain{Listens} Oh God. Ross, it's Nana.
	\switchcolumn
	\charactername{莫妮卡：}嘿爸爸，怎么了？\notmain{听电话}天啊。罗斯，是奶奶出事了。
	\switchcolumn*
	\sense{Scene: The Hospital, Mr. and Mrs. Geller are there, along with Aunt Lillian. Ross and Monica enter and everyone says hi and kisses.}
	\switchcolumn
	\sense{场景：医院，盖勒夫妇和莉莲姑姑都在。罗斯和莫妮卡走进来，大家互相问候、亲吻。}
	\switchcolumn*
	\charactername{Ross:} So, uh, how's she doing?
	\switchcolumn
	\charactername{罗斯：}那，呃，奶奶她怎么样了？
	\switchcolumn*
	\charactername{Aunt Lillian:} The doctor says it's a matter of hours.
	\switchcolumn
	\charactername{莉莲姑姑：}医生说就剩几个小时了。
	\switchcolumn*
	\charactername{Monica:} How-how are you, Mom?
	\switchcolumn
	\charactername{莫妮卡：}妈——你还好吗？
	\switchcolumn*
	\charactername{Mrs. Geller:} Me? I'm fine, fine. I'm glad you're here. ...What's with your hair?
	\switchcolumn
	\charactername{盖勒夫人：}我？我没事，没事。你们来了就好。……你这头发怎么回事？
	\switchcolumn*
	\charactername{Monica:} What?
	\switchcolumn
	\charactername{莫妮卡：}什么？
	\switchcolumn*
	\charactername{Mrs. Geller:} What's different?
	\switchcolumn
	\charactername{盖勒夫人：}哪里不一样了？
	\switchcolumn*
	\charactername{Monica:} Nothing.
	\switchcolumn
	\charactername{莫妮卡：}没什么啊。
	\switchcolumn*
	\charactername{Mrs. Geller:} Oh, maybe that's it.
	\switchcolumn
	\charactername{盖勒夫人：}哦，可能就是没什么变化才奇怪。
	\switchcolumn*
	\ennotmain{Monica strides over to Ross, who is making coffee, and talks to him aside.}
	\switchcolumn
	\notmain{莫妮卡大步走到正在冲咖啡的罗斯身边，凑到他耳边说话。}
	\switchcolumn*
	\charactername{Monica:} She is unbelievable, our mother is...
	\switchcolumn
	\charactername{莫妮卡：}她真是太离谱了，我们妈……
	\switchcolumn*
	\charactername{Ross:} Okay, relax, relax. We are gonna be here for a while, it looks like, and we still have boyfriends and your career to cover.
	\switchcolumn
	\charactername{罗斯：}好了，别激动，别激动。看样子我们得在这儿待一阵子了，她待会儿还得问你的男朋友、你的工作呢。
	\switchcolumn*
	\charactername{Monica:} Oh God!
	\switchcolumn
	\charactername{莫妮卡：}天啊！
	\switchcolumn*
	\ennotmain{They hug.}
	\switchcolumn
	\notmain{两人拥抱了一下。}
	\switchcolumn*
	\sense{Cut to the hospital, later. Everyone is talking about Nana.}
	\switchcolumn
	\sense{镜头切换到医院，过了一会儿。大家都在谈论奶奶。}
	\switchcolumn*
	\charactername{Monica:} The fuzzy little mints at the bottom of her purse.
	\switchcolumn
	\charactername{莫妮卡：}她钱包底部那些毛茸茸的小薄荷糖。
	\switchcolumn*
	\charactername{Ross:} Oh! ...Yeah, they were gross. Oh, you know what I loved? Her Sweet 'n' Los. How she was always stealing them from- from restaurants.
	\switchcolumn
	\charactername{罗斯：}哦！……对啊，那些糖超恶心的。不过你知道我最喜欢她什么吗？她的代糖包。她总爱从餐厅里偷——偷那些代糖包。
	\switchcolumn*
	\charactername{Mr. Geller:} Not just restaurants, from our house.
	\switchcolumn
	\charactername{盖勒先生：}不只是餐厅，还从我们家偷。
	\switchcolumn*
	\ennotmain{The nurse comes out of Nana's room.}
	\switchcolumn
	\notmain{护士从奶奶的病房里走出来。}
	\switchcolumn*
	\charactername{Nurse:} Mrs. Geller?
	\switchcolumn
	\charactername{护士：}盖勒夫人？
	\switchcolumn*
	\ennotmain{Everyone stands up. Cut to Ross and Monica in Nana's room.}
	\switchcolumn
	\notmain{所有人都站了起来。镜头切换到病房里的罗斯和莫妮卡。}
	\switchcolumn*
	\charactername{Ross:} She looks so small.
	\switchcolumn
	\charactername{罗斯：}她看起来好瘦小。
	\switchcolumn*
	\charactername{Monica:} I know.
	\switchcolumn
	\charactername{莫妮卡：}我知道。
	\switchcolumn*
	\charactername{Ross:} Well, at least she's with Pop-Pop and Aunt Phyllis now.
	\switchcolumn
	\charactername{罗斯：}不过，至少她现在能和爷爷、菲莉丝姑姑团聚了。
	\switchcolumn*
	\charactername{Monica:} G'bye, Nana. \ennotmain{She kisses her on the forehead.}
	\switchcolumn
	\charactername{莫妮卡：}再见，奶奶。\notmain{亲吻奶奶的额头。}
	\switchcolumn*
	\charactername{Ross:} Bye, Nana.
	\switchcolumn
	\charactername{罗斯：}再见，奶奶。
	\switchcolumn*
	\ennotmain{He goes to kiss her but she moves. Monica screams. Ross shouts and stares in disbelief. Monica runs out of the room.}
	\switchcolumn
	\notmain{他正要亲吻奶奶，奶奶却动了一下。莫妮卡尖叫起来。罗斯大喊一声，不敢相信地盯着奶奶。莫妮卡跑出了病房。}
	\switchcolumn*
	\charactername{Monica:} Ross!
	\switchcolumn
	\charactername{莫妮卡：}罗斯！
	\switchcolumn*
	\ennotmain{Ross runs out too.}
	\switchcolumn
	\notmain{罗斯也跟着跑了出去。}
	\switchcolumn*
	\charactername{Mrs. Geller:} What is going on?!
	\switchcolumn
	\charactername{盖勒夫人：}怎么回事啊？！
	\switchcolumn*
	\charactername{Ross:} Y'know how-how the nurse said that-that Nana had passed? Well, she's not, quite..
	\switchcolumn
	\charactername{罗斯：}你知道护士说奶奶已经……过世了吗？其实，她还没，完全没……
	\switchcolumn*
	\charactername{Mrs. Geller:} What?
	\switchcolumn
	\charactername{盖勒夫人：}什么？
	\switchcolumn*
	\charactername{Ross:} She's not- past, she's present, she's back.
	\switchcolumn
	\charactername{罗斯：}她没——过世，她还在，她活过来了。
	\switchcolumn*
	\charactername{Aunt Lillian:} \ennotmain{reentering} What's going on?
	\switchcolumn
	\charactername{莉莲姑姑：}\notmain{走进来}怎么了？
	\switchcolumn*
	\charactername{Mr. Geller:} She may have died.
	\switchcolumn
	\charactername{盖勒先生：}她可能刚才去世了。
	\switchcolumn*
	\charactername{Aunt Lillian:} She may have died?
	\switchcolumn
	\charactername{莉莲姑姑：}可能去世了？
	\switchcolumn*
	\charactername{Mr. Geller:} We're looking into it.
	\switchcolumn
	\charactername{盖勒先生：}我们正在核实。
	\switchcolumn*
	\ennotmain{Monica returns with the nurse and they go into Nana's room.}
	\switchcolumn
	\notmain{莫妮卡带着护士回来，一起走进了病房。}
	\switchcolumn*
	\charactername{Ross:} I, uh, I'll go see. \ennotmain{He goes in}
	\switchcolumn
	\charactername{罗斯：}我，呃，我去看看。\notmain{走进病房}
	\switchcolumn*
	\charactername{Nurse:} This almost never happens!
	\switchcolumn
	\charactername{护士：}这种情况几乎从来不会发生！
	\switchcolumn*
	\ennotmain{Nana passes for the second time and the nurse pulls the blanket over her. Ross and Monica go to tell the family}
	\switchcolumn
	\notmain{奶奶第二次过世，护士把毯子盖到了她身上。罗斯和莫妮卡出去告诉家人}
	\switchcolumn*
	\charactername{Ross:} Now she's passed.
	\switchcolumn
	\charactername{罗斯：}现在她真的过世了。
	\switchcolumn*
	\sense{Scene: Central Perk, Chandler, Phoebe, Joey, and Rachel are there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，钱德勒、菲比、乔伊和瑞秋都在。}
	\switchcolumn*
	\charactername{Chandler:} I just have to know, okay. Is it my hair?
	\switchcolumn
	\charactername{钱德勒：}我必须得知道，好吧。是因为我的头发吗？
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{exasperated} Yes, Chandler, that's exactly what it is. It's your hair.
	\switchcolumn
	\charactername{瑞秋：}\notmain{不耐烦地}对，钱德勒，就是因为你的头发。全是头发的问题。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, you have homosexual hair.
	\switchcolumn
	\charactername{菲比：}对啊，你长着一头同性恋的头发。
	\switchcolumn*
	\ennotmain{Monica and Ross enter.}
	\switchcolumn
	\notmain{莫妮卡和罗斯走进来。}
	\switchcolumn*
	\charactername{Rachel:} So, um, did she...
	\switchcolumn
	\charactername{瑞秋：}那，呃，她……\notmain{没说完}
	\switchcolumn*
	\charactername{Ross:} Twice.
	\switchcolumn
	\charactername{罗斯：}过世了两次。
	\switchcolumn*
	\charactername{Joey:} Twice?
	\switchcolumn
	\charactername{乔伊：}两次？
	\switchcolumn*
	\charactername{Phoebe:} Oh, that sucks!
	\switchcolumn
	\charactername{菲比：}哦，太糟了！
	\switchcolumn*
	\charactername{Joey:} You guys okay?
	\switchcolumn
	\charactername{乔伊：}你们还好吗？
	\switchcolumn*
	\charactername{Ross:} I dunno, it's weird. I mean, I know she's gone, but I just don't feel, uh...
	\switchcolumn
	\charactername{罗斯：}我不知道，感觉怪怪的。我是说，我知道她已经不在了，但我就是没感觉到，呃……
	\switchcolumn*
	\charactername{Phoebe:} Maybe that's 'cause she's not really gone.
	\switchcolumn
	\charactername{菲比：}可能是因为她并没有真的离开。
	\switchcolumn*
	\charactername{Ross:} Nono, she's gone.
	\switchcolumn
	\charactername{罗斯：}不，她真的走了。
	\switchcolumn*
	\charactername{Monica:} We checked. A lot.
	\switchcolumn
	\charactername{莫妮卡：}我们确认过很多次了。
	\switchcolumn*
	\charactername{Phoebe:} Hm, I mean maybe no-one ever really goes. Ever since my mom died, every now and then, I get the feeling that she's like right here, y'know? \ennotmain{She circles her hand around her right shoulder. Chandler, sitting on her right, draws back nervously} Oh! And Debbie, my best friend from junior high- got struck by lightning on a miniature golf course- I always get this really strong Debbie vibe whenever I use one of those little yellow pencils, y'know? ...I miss her.
	\switchcolumn
	\charactername{菲比：}嗯，我是说可能没有人会真的离开。自从我妈妈去世后，我时不时就会觉得她就在我身边，你知道吗？\notmain{她用手在右肩周围画了个圈。坐在她右边的钱德勒紧张地往后缩了缩}哦！还有黛比，我初中最好的朋友——在迷你高尔夫球场被闪电击中了——每次我用那种黄色小铅笔的时候，都能强烈感觉到她的存在，你知道吗？……我好想她。
	\switchcolumn*
	\charactername{Rachel:} Aw. Hey, Pheebs, want this? \ennotmain{Gives her a pencil}
	\switchcolumn
	\charactername{瑞秋：}唉。嘿，菲比，要这个吗？\notmain{递给她一支铅笔}
	\switchcolumn*
	\charactername{Phoebe:} Thanks!
	\switchcolumn
	\charactername{菲比：}谢谢！
	\switchcolumn*
	\charactername{Rachel:} Sure. I just sharpened her this morning.
	\switchcolumn
	\charactername{瑞秋：}不客气。我今早刚削过它。
	\switchcolumn*
	\charactername{Joey:} Now, see, I don't believe any of that. I think once you're dead, you're dead! You're gone! You're worm food! \ennotmain{realises his tactlessness} ...So Chandler looks gay, huh?
	\switchcolumn
	\charactername{乔伊：}你看，我才不信这些呢。我觉得人一旦死了，就真的死了！彻底消失了！变成虫子的食物了！\notmain{意识到自己说话没分寸}……所以钱德勒看起来像同性恋，是吧？
	\switchcolumn*
	\charactername{Phoebe:} Y'know, I dunno who this is, but it's not Debbie. \ennotmain{Hands back the pencil}
	\switchcolumn
	\charactername{菲比：}你知道吗，我不知道这是谁的能量，但肯定不是黛比的。\notmain{把铅笔递了回去}
	\switchcolumn*
	\sense{Scene: Nana's house, Ross, Mrs. Geller and Aunt Lillian are going through clothes.}
	\switchcolumn
	\sense{场景：奶奶家，罗斯、盖勒夫人和莉莲姑姑正在整理衣服。}
	\switchcolumn*
	\charactername{Ross:} I thought it was gonna be a closed casket.
	\switchcolumn
	\charactername{罗斯：}我还以为会用密封的棺材呢。
	\switchcolumn*
	\charactername{Mrs. Geller:} Well, that doesn't mean she can't look nice!
	\switchcolumn
	\charactername{盖勒夫人：}但这并不意味着她不能穿得好看点啊！
	\switchcolumn*
	\ennotmain{They open a cupboard which, amongst other things, contains a chest of drawers}
	\switchcolumn
	\notmain{她们打开一个橱柜，里面有一个五斗柜，还有其他东西}
	\switchcolumn*
	\charactername{Mrs. Geller:} Sweetie, you think you can get in there?
	\switchcolumn
	\charactername{盖勒夫人：}亲爱的，你能钻进去拿吗？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{sarcastic} I don't see why not.
	\switchcolumn
	\charactername{罗斯：}\notmain{讽刺地}我觉得没什么不可以的。
	\switchcolumn*
	\ennotmain{He tries pushing against the chest of drawers. Then he opens one of the drawers and climbs into the closet using that; he falls behind the chest of drawers with a shout.}
	\switchcolumn
	\notmain{他试着推了推五斗柜。然后打开其中一个抽屉，踩着抽屉爬进壁橱；他大喊一声，摔倒在五斗柜后面。}
	\switchcolumn*
	\charactername{Ross:} Here's my retainer!
	\switchcolumn
	\charactername{罗斯：}我的牙齿矫正器在这儿呢！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Monica is talking to her father.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，莫妮卡正在和爸爸打电话。}
	\switchcolumn*
	\charactername{Mr. Geller:} I was just thinking. When my time comes-
	\switchcolumn
	\charactername{盖勒先生：}我刚才在想。等我走的那天——
	\switchcolumn*
	\charactername{Monica:} Dad!
	\switchcolumn
	\charactername{莫妮卡：}爸爸！
	\switchcolumn*
	\charactername{Mr. Geller:} Listen to me! When my time comes, I wanna be buried at sea.
	\switchcolumn
	\charactername{盖勒先生：}听我说！等我走的那天，我想海葬。
	\switchcolumn*
	\charactername{Monica:} You what?
	\switchcolumn
	\charactername{莫妮卡：}你说什么？
	\switchcolumn*
	\charactername{Mr. Geller:} I wanna be buried at sea, it looks like fun.
	\switchcolumn
	\charactername{盖勒先生：}我想海葬，看起来挺有意思的。
	\switchcolumn*
	\charactername{Monica:} Define fun.
	\switchcolumn
	\charactername{莫妮卡：}你给“有意思”下个定义。
	\switchcolumn*
	\charactername{Mr. Geller:} C'mon, you'll make a day of it! You'll rent a boat, pack a lunch...
	\switchcolumn
	\charactername{盖勒先生：}拜托，你们可以把它当成一天的活动！租艘船，带上午餐……
	\switchcolumn*
	\charactername{Monica:} ...And then we throw your body in the water... Gee, that does sound fun.
	\switchcolumn
	\charactername{莫妮卡：}……然后把你的尸体扔进水里……天啊，听起来可真有意思。\notmain{反讽}
	\switchcolumn*
	\charactername{Mr. Geller:} Everyone thinks they know me. Everyone says 'Jack Geller, so predictable'. Maybe after I'm gone, they'll say 'Buried at sea! Huh!'.
	\switchcolumn
	\charactername{盖勒先生：}所有人都觉得他们了解我。所有人都说“杰克·盖勒啊，太循规蹈矩了”。也许我走了之后，他们会说“居然是海葬！真没想到！”
	\switchcolumn*
	\charactername{Monica:} That's probably what they'll say.
	\switchcolumn
	\charactername{莫妮卡：}他们大概率会这么说的。
	\switchcolumn*
	\charactername{Mr. Geller:} I'd like that.
	\switchcolumn
	\charactername{盖勒先生：}我希望如此。
	\switchcolumn*
	\sense{Scene: Chandler's Office, Shelley is drinking coffee; Chandler enters.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，谢莉正在喝咖啡；钱德勒走进来。}
	\switchcolumn*
	\charactername{Chandler:} Hey, gorgeous.
	\switchcolumn
	\charactername{钱德勒：}嘿，美女。
	\switchcolumn*
	\charactername{Shelley:} \ennotmain{sheepish} Hey. Look, I'm sorry about yesterday, I, um-
	\switchcolumn
	\charactername{谢莉：}\notmain{不好意思地}嘿。那个，昨天的事对不起，我，呃——
	\switchcolumn*
	\charactername{Chandler:} No, nono, don't- don't worry about it. Believe me, apparently other people have made the same mistake.
	\switchcolumn
	\charactername{钱德勒：}不，不不，别——别放在心上。相信我，显然还有别人也犯过同样的错。
	\switchcolumn*
	\charactername{Shelley:} Oh! Okay! Phew!
	\switchcolumn
	\charactername{谢莉：}哦！好的！呼！
	\switchcolumn*
	\charactername{Chandler:} So, uh... what do you think it is about me?
	\switchcolumn
	\charactername{钱德勒：}那，呃……你觉得我到底哪点让人误会啊？
	\switchcolumn*
	\charactername{Shelley:} I dunno, uh... you just have a-a...
	\switchcolumn
	\charactername{谢莉：}我不知道，呃……你就是有一种——一种……
	\switchcolumn*
	\charactername{Chandler:} ...Quality, right, great.
	\switchcolumn
	\charactername{钱德勒：}……特质，对吧，行。
	\switchcolumn*
	\charactername{Shelley:} Y'know, it's a shame, because you and Lowell would've made a great couple.
	\switchcolumn
	\charactername{谢莉：}说真的，挺可惜的，因为你和洛厄尔会是一对很棒的伴侣。
	\switchcolumn*
	\charactername{Chandler:} Lowell? Financial Services' Lowell, that's who you saw me with?
	\switchcolumn
	\charactername{钱德勒：}洛厄尔？财务部门的洛厄尔？你就想把我介绍给她？
	\switchcolumn*
	\charactername{Shelley:} What? He's cute!
	\switchcolumn
	\charactername{谢莉：}怎么了？他很可爱啊！
	\switchcolumn*
	\charactername{Chandler:} Well, yeah... 's'no Brian in Payroll.
	\switchcolumn
	\charactername{钱德勒：}嗯，是挺可爱的……但他不是薪资部门的布莱恩啊。
	\switchcolumn*
	\charactername{Shelley:} Is Brian...?
	\switchcolumn
	\charactername{谢莉：}布莱恩他……\notmain{没说完}
	\switchcolumn*
	\charactername{Chandler:} No! Uh, I d'know! The point is, if you were gonna set me up with someone, I'd like to think you'd set me up with someone like him.
	\switchcolumn
	\charactername{钱德勒：}不是！呃，我也不知道！重点是，如果你要给我介绍对象，我觉得你至少该介绍个像他那样的人吧。
	\switchcolumn*
	\charactername{Shelley:} Well, I think Brian's a little out of your league.
	\switchcolumn
	\charactername{谢莉：}嗯，我觉得布莱恩对你来说有点高不可攀。
	\switchcolumn*
	\charactername{Chandler:} Excuse me? You don't think I could get a Brian? Because I could get a Brian. Believe you me. ...I'm really not.
	\switchcolumn
	\charactername{钱德勒：}你说什么？你觉得我配不上布莱恩？我明明可以追到他的。相信我。……其实我追不到。
	\switchcolumn*
	\sense{Scene: Nana's Bedroom, Ross is holding a dress out from inside the closet.}
	\switchcolumn
	\sense{场景：奶奶的卧室，罗斯从壁橱里拿出一件连衣裙。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{holding a dress out from inside the closet} This one?
	\switchcolumn
	\charactername{罗斯：}\notmain{从壁橱里拿出一件连衣裙}这件怎么样？
	\switchcolumn*
	\charactername{Aunt Lillian:} No.
	\switchcolumn
	\charactername{莉莲姑姑：}不行。
	\switchcolumn*
	\charactername{Ross:} I have shown you everything we have. Unless you want your mother to spend eternity in a lemon yellow pant-suit, go with the burgundy.
	\switchcolumn
	\charactername{罗斯：}我已经把所有衣服都给你看过了。除非你想让你妈妈穿着柠檬黄的裤装套装度过余生，否则就选那件酒红色的。
	\switchcolumn*
	\charactername{Aunt Lillian:} You know, whatever we pick, she would've told us it's the wrong one.
	\switchcolumn
	\charactername{莉莲姑姑：}你知道吗，不管我们选哪件，她都会说选错了。
	\switchcolumn*
	\charactername{Mrs. Geller:} You're right. We'll go with the burgundy.
	\switchcolumn
	\charactername{盖勒夫人：}你说得对。就选酒红色的吧。
	\switchcolumn*
	\charactername{Ross:} Oh! A fine choice. I'm coming out. \ennotmain{Starts to climb over the furniture}
	\switchcolumn
	\charactername{罗斯：}哦！明智的选择。我要出来了。\notmain{开始爬过家具}
	\switchcolumn*
	\charactername{Aunt Lillian:} Wait! We need shoes!
	\switchcolumn
	\charactername{莉莲姑姑：}等等！还得选鞋子！
	\switchcolumn*
	\ennotmain{Ross falls back inside}
	\switchcolumn
	\notmain{罗斯又摔回了壁橱里}
	\switchcolumn*
	\charactername{Ross:} Okay. Um, how about these? \ennotmain{Holds out a pair}
	\switchcolumn
	\charactername{罗斯：}好吧。嗯，这双怎么样？\notmain{拿出一双鞋子}
	\switchcolumn*
	\charactername{Mrs. Geller:} That's really a day shoe.
	\switchcolumn
	\charactername{盖勒夫人：}这明显是白天穿的鞋子。
	\switchcolumn*
	\charactername{Ross:} And where she's going everyone else'll be dressier?
	\switchcolumn
	\charactername{罗斯：}那她要去的地方，其他人都会穿得更正式吗？
	\switchcolumn*
	\charactername{Aunt Lillian:} Could we see something in a slimmer heel?
	\switchcolumn
	\charactername{莉莲姑姑：}能看看鞋跟更细一点的吗？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{forages around} Okay, I have nothing in an evening shoe in the burgundy. I can show you something in a silver that may work.
	\switchcolumn
	\charactername{罗斯：}\notmain{在里面翻找}好吧，酒红色的晚宴鞋没有了。我可以给你们看看一双银色的，说不定能用。
	\switchcolumn*
	\charactername{Aunt Lillian:} No, it really should be burgundy.
	\switchcolumn
	\charactername{莉莲姑姑：}不行，必须得是酒红色的。
	\switchcolumn*
	\charactername{Mrs. Geller:} Mm. Unless we go with a different dress?
	\switchcolumn
	\charactername{盖勒夫人：}嗯。要不我们换件连衣裙？
	\switchcolumn*
	\charactername{Ross:} No! Nonono, wait a sec. I may have something in the back.
	\switchcolumn
	\charactername{罗斯：}不！不不不，等一下。我或许在最里面还有别的。
	\switchcolumn*
	\ennotmain{He finds a shoebox \ennotmain{out of shot}, pulls it down and opens it. It is full of Sweet 'n' Lo's.}
	\switchcolumn
	\notmain{他找到一个鞋盒\notmain{镜头外}，把它拿下来打开。里面装满了代糖包。}
	\switchcolumn*
	\charactername{Ross:} Oh my God..
	\switchcolumn
	\charactername{罗斯：}天啊……
	\switchcolumn*
	\charactername{Mrs. Geller:} Is everything all right, dear?
	\switchcolumn
	\charactername{盖勒夫人：}亲爱的，没事吧？
	\switchcolumn*
	\charactername{Ross:} Yeah, just... just Nana stuff.
	\switchcolumn
	\charactername{罗斯：}没事，就是……都是奶奶的东西。
	\switchcolumn*
	\ennotmain{He reaches up higher and knocks down another shoebox lid. Sweet 'n' Lo's rain down on him}
	\switchcolumn
	\notmain{他伸手往上够，又碰掉了另一个鞋盒盖。代糖包像雨点一样落在他身上}
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Monica and Rachel are preparing to leave for the funeral.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，莫妮卡和瑞秋正在准备去参加葬礼。}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{entering} How we doing, you guys ready?
	\switchcolumn
	\charactername{罗斯：}\notmain{走进来}怎么样，你们准备好了吗？
	\switchcolumn*
	\charactername{Monica:} Mom already called this morning to remind me not to wear my hair up. Did you know my ears are not my best feature?
	\switchcolumn
	\charactername{莫妮卡：}妈妈今早已经打电话来提醒我，别把头发扎起来。你知道吗，我的耳朵不是我最好看的部位？
	\switchcolumn*
	\charactername{Ross:} Some days it's all I can think about.
	\switchcolumn
	\charactername{罗斯：}有时候我满脑子想的都是这个。\notmain{调侃}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{entering} Hi, sorry I'm late, I couldn't find my bearings.
	\switchcolumn
	\charactername{菲比：}\notmain{走进来}嗨，抱歉我来晚了，我找不到我的耳环了。\notmain{把“earrings”说成了“bearings”}
	\switchcolumn*
	\charactername{Rachel:} Oh, you-you mean your earrings?
	\switchcolumn
	\charactername{瑞秋：}哦，你——你是说你的耳环吧？
	\switchcolumn*
	\charactername{Phoebe:} What'd I say?
	\switchcolumn
	\charactername{菲比：}我刚才说什么了？
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{sticking her foot out} Hm-m.
	\switchcolumn
	\charactername{瑞秋：}\notmain{伸出脚}嗯哼。\notmain{展示自己的鞋子}
	\switchcolumn*
	\charactername{Monica:} Are these the shoes?
	\switchcolumn
	\charactername{莫妮卡：}这就是那双鞋？
	\switchcolumn*
	\charactername{Rachel:} Yes. Paolo sent them from Italy.
	\switchcolumn
	\charactername{瑞秋：}对啊。保罗从意大利寄来的。
	\switchcolumn*
	\charactername{Ross:} What, we-uh- we don't have shoes here, or...?
	\switchcolumn
	\charactername{罗斯：}什么，我们——呃——我们这儿没有鞋子吗，还是……？
	\switchcolumn*
	\charactername{Joey:} \ennotmain{entering with Chandler} Morning. We ready to go?
	\switchcolumn
	\charactername{乔伊：}\notmain{和钱德勒一起走进来}早上好。我们可以走了吗？
	\switchcolumn*
	\charactername{Chandler:} Well, don't we look nice all dressed up?...It's stuff like that, isn't it?
	\switchcolumn
	\charactername{钱德勒：}哇，我们穿得这么正式，看起来真不错呢……就是这种话让人误会，对吧？
	\switchcolumn*
	\ennotmain{They all leave.}
	\switchcolumn
	\notmain{所有人都离开了。}
	\switchcolumn*
	\sense{Scene: The cemetary, after the funeral.}
	\switchcolumn
	\sense{场景：墓地，葬礼结束后。}
	\switchcolumn*
	\charactername{Monica:} It was a really beautiful service.
	\switchcolumn
	\charactername{莫妮卡：}葬礼办得真不错。
	\switchcolumn*
	\charactername{Mrs. Geller:} It really was. Oh, c'mere, sweetheart. \ennotmain{Hugs her} Y'know, I think it might be time for you to start using night cream.
	\switchcolumn
	\charactername{盖勒夫人：}确实不错。哦，过来，亲爱的。\notmain{拥抱她}你知道吗，我觉得你该开始用晚霜了。
	\switchcolumn*
	\ennotmain{Joey listens to his overcoat for a second and sighs, then notices Chandler watching}
	\switchcolumn
	\notmain{乔伊对着自己的大衣听了一会儿，叹了口气，然后注意到钱德勒在看他}
	\switchcolumn*
	\charactername{Joey:} What?
	\switchcolumn
	\charactername{乔伊：}怎么了？
	\switchcolumn*
	\charactername{Chandler:} Nothing, just your overcoat sounds remarkably like Brent Mussberger.
	\switchcolumn
	\charactername{钱德勒：}没什么，就是你的大衣听起来特别像布伦特·马斯伯格\notmain{知名体育解说员}。
	\switchcolumn*
	\charactername{Joey:} Check it out, Giants-Cowboys. \ennotmain{He has a pocket TV}
	\switchcolumn
	\charactername{乔伊：}你看，巨人队对牛仔队的比赛。\notmain{他有一台袖珍电视}
	\switchcolumn*
	\charactername{Chandler:} You're watching a football game at a funeral?
	\switchcolumn
	\charactername{钱德勒：}你居然在葬礼上看橄榄球比赛？
	\switchcolumn*
	\charactername{Joey:} No, it's the pre-game. I'm gonna watch it at the reception.
	\switchcolumn
	\charactername{乔伊：}不是，这是赛前预热。我打算在招待会上看正赛。
	\switchcolumn*
	\charactername{Chandler:} You are a frightening, frightening man.
	\switchcolumn
	\charactername{钱德勒：}你真是个太可怕、太可怕的人了。
	\switchcolumn*
	\ennotmain{Rachel steps in a patch of mud}
	\switchcolumn
	\notmain{瑞秋踩到了一滩泥}
	\switchcolumn*
	\charactername{Rachel:} Oh no! My new Paolo shoes!
	\switchcolumn
	\charactername{瑞秋：}哦不！我的新鞋子，保罗寄来的！
	\switchcolumn*
	\charactername{Ross:} Oh, I hope they're not ruined.
	\switchcolumn
	\charactername{罗斯：}哦，希望没弄坏。
	\switchcolumn*
	\charactername{Phoebe:} God, what a great day. ...What? Weather-wise!
	\switchcolumn
	\charactername{菲比：}天啊，今天真是美好的一天。……怎么了？我是说天气方面！
	\switchcolumn*
	\charactername{Ross:} I know, uh, the air, the-the trees... even though Nana's gone there's, there's something almost, uh- I dunno, almost life-aff- \ennotmain{Not looking where he is going he falls into an open grave}
	\switchcolumn
	\charactername{罗斯：}我知道，呃，这空气，这树木……虽然奶奶不在了，但总觉得有某种，呃——我不知道，某种生命的——\notmain{没看路，掉进了一个敞开的墓穴里}
	\switchcolumn*
	\charactername{All:} God! Ross!
	\switchcolumn
	\charactername{众人：}天啊！罗斯！
	\switchcolumn*
	\charactername{Ross:} I'm fine. Just-just... having my worst fear realised...
	\switchcolumn
	\charactername{罗斯：}我没事。只是——只是……我最害怕的事成真了……
	\switchcolumn*
	\sense{Scene: The Wake, at the Gellers' house. Ross is lying on his back, with Phoebe squatting over him, checking to see if he's injured.}
	\switchcolumn
	\sense{场景：盖勒家的追悼会。罗斯平躺在地上，菲比蹲在他身边，检查他有没有受伤。}
	\switchcolumn*
	\charactername{Phoebe:} Okay, don't worry, I'm just checking to see if the muscle's in spasm...huh.
	\switchcolumn
	\charactername{菲比：}好了，别担心，我只是检查一下肌肉有没有痉挛……嗯。
	\switchcolumn*
	\charactername{Ross:} What, what is it?
	\switchcolumn
	\charactername{罗斯：}怎么了，怎么了？
	\switchcolumn*
	\charactername{Phoebe:} You missed a belt loop.
	\switchcolumn
	\charactername{菲比：}你腰带扣没扣好一个环。
	\switchcolumn*
	\charactername{Ross:} Oh! No-n-
	\switchcolumn
	\charactername{罗斯：}哦！不——不——
	\switchcolumn*
	\charactername{Phoebe:} Okay, it's in spasm.
	\switchcolumn
	\charactername{菲比：}好吧，确实痉挛了。
	\switchcolumn*
	\charactername{Mrs. Geller:} Here, sweetie, here. I took these when I had my golfing accident. \ennotmain{Hands Ross a bottle of pills. Then turns to Monica and pats her hair over her ears}
	\switchcolumn
	\charactername{盖勒夫人：}来，亲爱的，拿着。我上次打高尔夫受伤的时候就吃这个。\notmain{递给罗斯一瓶药。然后转向莫妮卡，用头发盖住她的耳朵}
	\switchcolumn*
	\ennotmain{Cut to Chandler and a woman, Andrea, reaching for the same slice of meat}
	\switchcolumn
	\notmain{镜头切换到钱德勒和一个女人安德里亚同时去拿同一片肉}
	\switchcolumn*
	\charactername{Chandler:} Oh, no-
	\switchcolumn
	\charactername{钱德勒：}哦，不——
	\switchcolumn*
	\charactername{Andrea:} Sorry- Hi, I'm Dorothy's daughter.
	\switchcolumn
	\charactername{安德里亚：}抱歉——嗨，我是桃乐丝的女儿。
	\switchcolumn*
	\charactername{Chandler:} Hi, I'm Chandler, and I have no idea who Dorothy is.
	\switchcolumn
	\charactername{钱德勒：}嗨，我是钱德勒，我不知道桃乐丝是谁。
	\switchcolumn*
	\ennotmain{They shake hands. Cut to Ross emerging from a hallway, grinning inanely. He is obviously very stoned}
	\switchcolumn
	\notmain{两人握手。镜头切换到罗斯从走廊里走出来，傻笑个不停。显然他嗑药嗑嗨了}
	\switchcolumn*
	\charactername{Phoebe:} Hey, look who's up! How do you feel?
	\switchcolumn
	\charactername{菲比：}嘿，看看谁起来了！感觉怎么样？
	\switchcolumn*
	\charactername{Ross:} I feel great. I feel- great, I fleel great.
	\switchcolumn
	\charactername{罗斯：}我感觉太棒了。我感觉——太棒了，我超——级棒。\notmain{发音含糊}
	\switchcolumn*
	\charactername{Monica:} Wow, those pills really worked, huh?
	\switchcolumn
	\charactername{莫妮卡：}哇，那些药效果也太好了吧？
	\switchcolumn*
	\charactername{Ross:} Not the first two, but the second two- woooo! ...I love you guys. You guys are the greatest. I love my sister \ennotmain{Kisses Monica}, I love Pheebs... \ennotmain{Hugs her}
	\switchcolumn
	\charactername{罗斯：}前两颗没效果，但后两颗——哇哦！……我爱你们。你们都是最棒的。我爱我妹妹\notmain{亲吻莫妮卡}，我爱菲比……\notmain{拥抱她}
	\switchcolumn*
	\charactername{Phoebe:} Ooh! That's so nice...
	\switchcolumn
	\charactername{菲比：}哦！太暖心了……
	\switchcolumn*
	\charactername{Ross:} ...Chandler!
	\switchcolumn
	\charactername{罗斯：}……钱德勒！
	\switchcolumn*
	\charactername{Chandler:} Hey.
	\switchcolumn
	\charactername{钱德勒：}嘿。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{hugs him} And listen, man, if you wanna be gay, be gay. Doesn't matter to me.
	\switchcolumn
	\charactername{罗斯：}\notmain{拥抱他}听着，兄弟，如果你想做同性恋，那就做吧。我不在乎。
	\switchcolumn*
	\charactername{Andrea:} \ennotmain{turns to a friend} You were right. \ennotmain{They walk off and leave Chandler.}
	\switchcolumn
	\charactername{安德里亚：}\notmain{对朋友说}你说得对。\notmain{两人走开，留下钱德勒}
	\switchcolumn*
	\charactername{Ross:} Rachel. Rachel Rachel. \ennotmain{Sits down beside her} I love you the most.
	\switchcolumn
	\charactername{罗斯：}瑞秋。瑞秋瑞秋。\notmain{坐在她身边}我最爱你了。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{humouring him} Oh, well you know who I love the most?
	\switchcolumn
	\charactername{瑞秋：}\notmain{迁就他}哦，那你知道我最爱谁吗？
	\switchcolumn*
	\charactername{Ross:} No.
	\switchcolumn
	\charactername{罗斯：}不知道。
	\switchcolumn*
	\charactername{Rachel:} You!
	\switchcolumn
	\charactername{瑞秋：}你呀！
	\switchcolumn*
	\charactername{Ross:} Oh.. you don't get it! \ennotmain{Passes out and slumps across her}
	\switchcolumn
	\charactername{罗斯：}哦……你不懂！\notmain{昏了过去，瘫倒在她身上}
	\switchcolumn*
	\ennotmain{Cut to Joey watching TV in the corner. He makes an extravagant gesture of disappointment.}
	\switchcolumn
	\notmain{镜头切换到乔伊在角落里看电视。他夸张地做出失望的手势。}
	\switchcolumn*
	\charactername{Mr. Geller:} Whaddya got there?
	\switchcolumn
	\charactername{盖勒先生：}你那儿是什么？
	\switchcolumn*
	\charactername{Joey:} \ennotmain{hides the TV, but he still has an earphone} Just a, uh... hearing disability.
	\switchcolumn
	\charactername{乔伊：}\notmain{把电视藏起来，但还戴着耳机}没什么，就是，呃……听力有点问题。
	\switchcolumn*
	\charactername{Mr. Geller:} What's the score?
	\switchcolumn
	\charactername{盖勒先生：}比分多少？
	\switchcolumn*
	\charactername{Joey:} Seventeen-fourteen Giants... three minutes to go in the third.
	\switchcolumn
	\charactername{乔伊：}巨人队17比14……第三节还剩三分钟。
	\switchcolumn*
	\charactername{Mr. Geller:} Beautiful! \ennotmain{Turns to watch with him}
	\switchcolumn
	\charactername{盖勒先生：}太棒了！\notmain{凑过去跟他一起看}
	\switchcolumn*
	\ennotmain{Time lapse. A large crowd of men are now watching the game}
	\switchcolumn
	\notmain{时间快进。现在一大群男人都在看比赛}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{still trapped under Ross} Pheebs, could you maybe hand me a cracker?
	\switchcolumn
	\charactername{瑞秋：}\notmain{还被罗斯压着}菲比，能递给我一块饼干吗？
	\switchcolumn*
	\charactername{Mrs. Geller:} \ennotmain{to Monica} Your grandmother would have hated this.
	\switchcolumn
	\charactername{盖勒夫人：}\notmain{对莫妮卡}你奶奶肯定会讨厌这样的。
	\switchcolumn*
	\charactername{Monica:} Well, sure, what with it being her funeral and all.
	\switchcolumn
	\charactername{莫妮卡：}嗯，那是当然，毕竟这是她的葬礼啊。
	\switchcolumn*
	\charactername{Mrs. Geller:} No, I'd be hearing about 'Why didn't I get the honey-glazed ham?', I didn't spend enough on flowers, and if I spent more she'd be saying 'Why are you wasting your money? I don't need flowers, I'm dead'.
	\switchcolumn
	\charactername{盖勒夫人：}不是，她肯定会念叨“为什么没有蜜汁火腿？”“花买得太少了”，可要是我多花点钱买花，她又会说“你为什么浪费钱？我都死了，不需要花”。
	\switchcolumn*
	\charactername{Monica:} That sounds like Nana.
	\switchcolumn
	\charactername{莫妮卡：}这听起来确实像奶奶会说的话。
	\switchcolumn*
	\charactername{Mrs. Geller:} Do you know what it's like to grow up with someone who is critical of every single thing you say?
	\switchcolumn
	\charactername{盖勒夫人：}你知道在一个对你所说的每一件事都吹毛求疵的人身边长大是什么感觉吗？
	\switchcolumn*
	\charactername{Monica:} ...I can imagine.
	\switchcolumn
	\charactername{莫妮卡：}……我能想象到。
	\switchcolumn*
	\charactername{Mrs. Geller:} I'm telling you, it's a wonder your mother turned out to be the positive, life-affirming person that she is.
	\switchcolumn
	\charactername{盖勒夫人：}我跟你说，你妈妈能长成这么积极、乐观向上的人，真是个奇迹。
	\switchcolumn*
	\charactername{Monica:} That is a wonder. So tell me something, Mom. If you had to do it all over again, I mean, if she was here right now, would you tell her?
	\switchcolumn
	\charactername{莫妮卡：}确实是个奇迹。那妈妈，跟我说说。如果能重来一次，我是说，如果她现在就在这儿，你会跟她说吗？
	\switchcolumn*
	\charactername{Mrs. Geller:} Tell her what?
	\switchcolumn
	\charactername{盖勒夫人：}跟她说什么？
	\switchcolumn*
	\charactername{Monica:} How she drove you crazy, picking on every little detail, like your hair... for example.
	\switchcolumn
	\charactername{莫妮卡：}跟她说她以前有多让你抓狂，对每一件小事都吹毛求疵，比如对你的头发……之类的。
	\switchcolumn*
	\charactername{Mrs. Geller:} I'm not sure I know what you're getting at.
	\switchcolumn
	\charactername{盖勒夫人：}我不太明白你的意思。
	\switchcolumn*
	\charactername{Monica:} Do you think things would have been better if you'd just told her the truth?
	\switchcolumn
	\charactername{莫妮卡：}你觉得如果当初你跟她说实话，事情会不会好一点？
	\switchcolumn*
	\charactername{Mrs. Geller:} ...No. I think some things are better left unsaid. I think it's nicer when people just get along.
	\switchcolumn
	\charactername{盖勒夫人：}……不会。我觉得有些话还是不说为好。大家和睦相处不是更好吗？
	\switchcolumn*
	\charactername{Monica:} Huh.
	\switchcolumn
	\charactername{莫妮卡：}嗯。
	\switchcolumn*
	\charactername{Mrs. Geller:} More wine, dear?
	\switchcolumn
	\charactername{盖勒夫人：}再来点酒吗，亲爱的？
	\switchcolumn*
	\charactername{Monica:} Oh, I think so.
	\switchcolumn
	\charactername{莫妮卡：}哦，好啊。
	\switchcolumn*
	\charactername{Mrs. Geller:} \ennotmain{reaches out to fiddle with Monica's hair again, and realises} Those earrings look really lovely on you.
	\switchcolumn
	\charactername{盖勒夫人：}\notmain{伸手又想摆弄莫妮卡的头发，然后意识到什么}这对耳环你戴着真好看。
	\switchcolumn*
	\charactername{Monica:} Thank you. They're yours.
	\switchcolumn
	\charactername{莫妮卡：}谢谢。这是你的耳环啊。
	\switchcolumn*
	\charactername{Mrs. Geller:} Actually they were Nana's.
	\switchcolumn
	\charactername{盖勒夫人：}其实这是你奶奶的。
	\switchcolumn*
	\ennotmain{There is a cry of disappointment from the crowd of men.}
	\switchcolumn
	\notmain{男人们发出一阵失望的叫喊声。}
	\switchcolumn*
	\charactername{Mr. Geller:} Now I'm depressed! ...\ennotmain{To everyone} Even more than I was.
	\switchcolumn
	\charactername{盖勒先生：}现在我更郁闷了！……\notmain{对所有人说}比之前还郁闷。
	\switchcolumn*
	\sense{Scene: Central Perk, the gang are looking at old photos.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，大家正在看老照片。}
	\switchcolumn*
	\charactername{Rachel:} Hey, who's this little naked guy?
	\switchcolumn
	\charactername{瑞秋：}嘿，这个光着身子的小家伙是谁啊？
	\switchcolumn*
	\charactername{Ross:} That little naked guy would be me.
	\switchcolumn
	\charactername{罗斯：}这个光着身子的小家伙就是我啊。
	\switchcolumn*
	\charactername{Rachel:} Aww, look at the little thing.
	\switchcolumn
	\charactername{瑞秋：}哇，看看这小东西。\notmain{调侃罗斯小时候}
	\switchcolumn*
	\charactername{Ross:} Yes, yes, fine, that is my penis. Can we be grown-ups now?
	\switchcolumn
	\charactername{罗斯：}是是是，行了，那是我的小弟弟。我们能成熟一点吗？
	\switchcolumn*
	\charactername{Chandler:} Who are those people?
	\switchcolumn
	\charactername{钱德勒：}这些人是谁啊？
	\switchcolumn*
	\charactername{Ross:} Got me.
	\switchcolumn
	\charactername{罗斯：}不知道。
	\switchcolumn*
	\charactername{Monica:} Oh, that's Nana, right there in the middle. \ennotmain{Reads the back} 'Me and the gang at Java Joe's'.
	\switchcolumn
	\charactername{莫妮卡：}哦，中间那个是奶奶。\notmain{看照片背面}“我和朋友们在爪哇乔咖啡馆”。
	\switchcolumn*
	\charactername{Rachel:} Wow, Monica, you look just like your grandmother. How old was she there?
	\switchcolumn
	\charactername{瑞秋：}哇，莫妮卡，你跟你奶奶长得真像。她那时候多大啊？
	\switchcolumn*
	\charactername{Monica:} Let's see, 1939... yeah, 24, 25?
	\switchcolumn
	\charactername{莫妮卡：}我看看，1939年……嗯，24、25岁左右吧？
	\switchcolumn*
	\charactername{Ross:} Looks like a fun gang. \ennotmain{They all look at each other and smile}
	\switchcolumn
	\charactername{罗斯：}看起来是一群很有趣的人。\notmain{大家对视一笑}
	\switchcolumn*
	\charactername{Joey:} Ooh, look-look-look-look-look! I got Monica naked!
	\switchcolumn
	\charactername{乔伊：}哦，快看快看快看快看快看！我找到莫妮卡光着身子的照片了！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{looking} Nono, that would be me again. I'm, uh, just trying something.
	\switchcolumn
	\charactername{罗斯：}\notmain{看了看}不不，那还是我。我那时候，呃，只是在尝试点新造型。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Chandler's Office, Chandler is on a coffee break as Lowell enters.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，钱德勒正在喝咖啡休息，洛厄尔走进来。}
	\switchcolumn*
	\charactername{Chandler:} Hey, Lowell.
	\switchcolumn
	\charactername{钱德勒：}嘿，洛厄尔。
	\switchcolumn*
	\charactername{Lowell:} Hey, Chandler.
	\switchcolumn
	\charactername{洛厄尔：}嘿，钱德勒。
	\switchcolumn*
	\charactername{Chandler:} So how's it going there in Financial Services?
	\switchcolumn
	\charactername{钱德勒：}财务部门那边怎么样啊？
	\switchcolumn*
	\charactername{Lowell:} It's like Mardi Gras without the paper mache heads. How 'bout you?
	\switchcolumn
	\charactername{洛厄尔：}就像狂欢节，就是没有纸糊的头套。你呢？
	\switchcolumn*
	\charactername{Chandler:} Good, good. Listen, heh, I dunno what Shelley told you about me, but, uh... I'm not.
	\switchcolumn
	\charactername{钱德勒：}挺好的，挺好的。那个，嘿，我不知道谢莉跟你说了我什么，但是，呃……我不是同性恋。
	\switchcolumn*
	\charactername{Lowell:} I know. That's what I told her.
	\switchcolumn
	\charactername{洛厄尔：}我知道。我也是这么跟她说的。
	\switchcolumn*
	\charactername{Chandler:} Really.
	\switchcolumn
	\charactername{钱德勒：}真的吗。
	\switchcolumn*
	\charactername{Lowell:} Yeah.
	\switchcolumn
	\charactername{洛厄尔：}对啊。
	\switchcolumn*
	\charactername{Chandler:} So- you can tell?
	\switchcolumn
	\charactername{钱德勒：}那——你能看出来？
	\switchcolumn*
	\charactername{Lowell:} Pretty much, most of the time. We have a kind of... radar.
	\switchcolumn
	\charactername{洛厄尔：}差不多，大多数时候都能。我们有种……雷达一样的直觉。
	\switchcolumn*
	\charactername{Chandler:} So you don't think I have a, a quality?
	\switchcolumn
	\charactername{钱德勒：}那你不觉得我有种，那种特质？
	\switchcolumn*
	\charactername{Lowell:} Speaking for my people, I'd have to say no. By the way, your friend Brian from Payroll, he is.
	\switchcolumn
	\charactername{洛厄尔：}站在我们同性恋的角度来说，我得说没有。对了，你薪资部门的朋友布莱恩，他才是同性恋。
	\switchcolumn*
	\charactername{Chandler:} He is?
	\switchcolumn
	\charactername{钱德勒：}他是？
	\switchcolumn*
	\charactername{Lowell:} Yup, and waaay out of your league. \ennotmain{Exits}
	\switchcolumn
	\charactername{洛厄尔：}对啊，而且你跟他完全不是一个档次的。\notmain{离开}
	\switchcolumn*
	\charactername{Chandler:} Out of my league. I could get a Brian. \ennotmain{Brian enters behind him} If I wanted to get a Brian, I could get a Brian. \ennotmain{Sees him} Hey, Brian.
	\switchcolumn
	\charactername{钱德勒：}不是一个档次的。我明明能追到布莱恩。\notmain{布莱恩从他身后走进来}如果我想追布莱恩，我就能追到。\notmain{看到布莱恩}嘿，布莱恩。
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage