\begin{paracol}{2}
	\sense{Scene: Central Perk, Rachel is confronting her boss, Terry.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，瑞秋正在跟老板特里沟通}
	\switchcolumn*
	\charactername{Rachel:} Terry, I, I, I know that I haven't worked here very long, but I was wondering, do you think it would be possible if I got a \$100 advance in my salary?
	\switchcolumn
	\charactername{瑞秋：}特里，我，我知道我在这儿工作没多久，但我想问问，你能不能先预支我100美元薪水？
	\switchcolumn*
	\charactername{Terry:} An advance?
	\switchcolumn
	\charactername{特里：}预支薪水？
	\switchcolumn*
	\charactername{Rachel:} It's so that I can spend Thanksgiving with my family. See, every year we go skiing in Vail, and normally my father pays for my ticket, but I sort of started the whole independence thing, you know, which is actually why I took this job.
	\switchcolumn
	\charactername{瑞秋：}我想回家跟家人过感恩节。你看，我们每年都去韦尔滑雪，以前都是我爸给我买机票，但我现在想独立生活了，这也是我来这儿工作的原因。
	\switchcolumn*
	\charactername{Terry:} Rachel, Rachel, sweetheart. You're a terrible, terrible waitress. Really, really awful.
	\switchcolumn
	\charactername{特里：}瑞秋，瑞秋，亲爱的。你真是个糟糕透顶的服务员。真的，差得离谱。
	\switchcolumn*
	\charactername{Rachel:} Ok, I, I hear what you're sayin'. I'm with you. Um, but I, but I'm trying really hard. And I think I'm doing better. I really do. Does anybody need coffee? \ennotmain{everyone in the place raises their hand} Oh, look at that.
	\switchcolumn
	\charactername{瑞秋：}好的，我，我明白你的意思。你说得对。但我，我真的很努力在学了。而且我觉得我进步了，真的。有人要喝咖啡吗？\notmain{店里所有人都举起了手}哦，你看。
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, Rachel is approaching a customer.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，瑞秋走向一位顾客}
	\switchcolumn*
	\charactername{Rachel:} Excuse me, sir. Hi, you come in here all time. I was just wondering, do you think there's a possibility that you could give me an advance on my tips?
	\switchcolumn
	\charactername{瑞秋：}打扰一下，先生。嗨，你经常来这儿。我想问问，你能不能先预支我一些小费？
	\switchcolumn*
	\charactername{Guy:} Huh?
	\switchcolumn
	\charactername{顾客：}啊？
	\switchcolumn*
	\charactername{Rachel:} Ok, ok, that's fine. Fine. Hey, I'm sorry about that spill before. \ennotmain{picks up the tip he leaves} Only \$98.50 to go.
	\switchcolumn
	\charactername{瑞秋：}好的好的，没关系。没关系。嘿，刚才打翻东西真不好意思。\notmain{拿起他留下的小费}还剩98.5美元就够了。
	\switchcolumn*
	\ennotmain{Monica enters.}
	\switchcolumn
	\notmain{莫妮卡走进来}
	\switchcolumn*
	\charactername{Monica:} Hey. Ross, did you know Mom and Dad are going to Puerto Rico for Thanksgiving?
	\switchcolumn
	\charactername{莫妮卡：}嘿。罗斯，你知道爸妈要去波多黎各过感恩节吗？
	\switchcolumn*
	\charactername{Ross:} No, they're not.
	\switchcolumn
	\charactername{罗斯：}不，他们不会去的。
	\switchcolumn*
	\charactername{Monica:} Yes, they are. The Blymens invited them.
	\switchcolumn
	\charactername{莫妮卡：}会的，布莱曼一家邀请他们了。
	\switchcolumn*
	\charactername{Ross:} You're wrong.
	\switchcolumn
	\charactername{罗斯：}你错了。
	\switchcolumn*
	\charactername{Monica:} I am not wrong.
	\switchcolumn
	\charactername{莫妮卡：}我没说错。
	\switchcolumn*
	\charactername{Ross:} You're wrong.
	\switchcolumn
	\charactername{罗斯：}你就是错了。
	\switchcolumn*
	\charactername{Monica:} No, I just talked to them.
	\switchcolumn
	\charactername{莫妮卡：}我刚跟他们通完电话。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{getting up, upset} I'm calling Mom.
	\switchcolumn
	\charactername{罗斯：}\notmain{生气地站起来}我给妈打电话问问。
	\switchcolumn*
	\ennotmain{Joey enters. His face looks abnormally colorful.}
	\switchcolumn
	\notmain{乔伊走进来，脸上妆容异常鲜艳}
	\switchcolumn*
	\charactername{Joey:} Hey, hey.
	\switchcolumn
	\charactername{乔伊：}嘿，嘿。
	\switchcolumn*
	\charactername{Chandler:} Hey.
	\switchcolumn
	\charactername{钱德勒：}嘿。
	\switchcolumn*
	\charactername{Phoebe:} Hey.
	\switchcolumn
	\charactername{菲比：}嘿。
	\switchcolumn*
	\charactername{Chandler:} And this from the cry-for-help department. Are you wearing makeup?
	\switchcolumn
	\charactername{钱德勒：}这是要求救的节奏啊。你化妆了？
	\switchcolumn*
	\charactername{Joey:} Yes, I am. As of today, I am officially Joey Tribbiani, actor slash model.
	\switchcolumn
	\charactername{乔伊：}对啊。从今天起，我正式成为乔伊·崔比安尼，演员兼模特。
	\switchcolumn*
	\charactername{Chandler:} That's so funny, 'cause I was thinking you look more like Joey Tribbiani, man slash woman.
	\switchcolumn
	\charactername{钱德勒：}真搞笑，我还以为你更像乔伊·崔比安尼，男人兼女人呢。
	\switchcolumn*
	\charactername{Phoebe:} What were you modeling for?
	\switchcolumn
	\charactername{菲比：}你拍的是什么广告啊？
	\switchcolumn*
	\charactername{Joey:} You know those posters for the city free clinic?
	\switchcolumn
	\charactername{乔伊：}就是城市免费诊所的那些海报啊？
	\switchcolumn*
	\charactername{Monica:} Oh, wow, so you're gonna be one of those "healthy, healthy, healthy guys"?
	\switchcolumn
	\charactername{莫妮卡：}哦哇，所以你要当那些“健康、健康、超健康”的模特之一？
	\switchcolumn*
	\charactername{Phoebe:} You know, the asthma guy was really cute.
	\switchcolumn
	\charactername{菲比：}我记得那个哮喘病主题的模特超帅的。
	\switchcolumn*
	\charactername{Chandler:} Do you know which one you're gonna be?
	\switchcolumn
	\charactername{钱德勒：}你知道你要拍哪个主题吗？
	\switchcolumn*
	\charactername{Joey:} No, but I hear lyme disease is open, so... \ennotmain{crosses fingers}
	\switchcolumn
	\charactername{乔伊：}不知道，但我听说莱姆病那个主题还缺人，所以……\notmain{交叉手指祈祷}
	\switchcolumn*
	\charactername{Chandler:} Good luck, man. I hope you get it.
	\switchcolumn
	\charactername{钱德勒：}祝你好运，兄弟。希望你能选上。
	\switchcolumn*
	\charactername{Joey:} Thanks.
	\switchcolumn
	\charactername{乔伊：}谢了。
	\switchcolumn*
	\ennotmain{Ross comes back to the couch.}
	\switchcolumn
	\notmain{罗斯回到沙发上}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{to Monica} Well, you were right. How can they do this to us, huh? It's Thanksgiving.
	\switchcolumn
	\charactername{罗斯：}\notmain{对莫妮卡}好吧，你说得对。他们怎么能这么对我们啊？这可是感恩节。
	\switchcolumn*
	\charactername{Monica:} Ok, I'll tell you what. How about I cook dinner at my place? I'll make it just like Mom's.
	\switchcolumn
	\charactername{莫妮卡：}好吧，我有个主意。我在我家做晚餐怎么样？我会做得跟妈做的一样。
	\switchcolumn*
	\charactername{Ross:} Will you make the mashed potatoes with the lumps?
	\switchcolumn
	\charactername{罗斯：}你会做带颗粒的土豆泥吗？
	\switchcolumn*
	\charactername{Monica:} You know, they're not actually supposed to have... \ennotmain{Ross looks at her sheepishly} I'll work on the lumps. Joey, you're going home, right?
	\switchcolumn
	\charactername{莫妮卡：}其实土豆泥本来不该有……\notmain{罗斯不好意思地看着她}我会特意做带颗粒的。乔伊，你要回家过节对吧？
	\switchcolumn*
	\charactername{Joey:} Yeah.
	\switchcolumn
	\charactername{乔伊：}对啊。
	\switchcolumn*
	\charactername{Monica:} And I assume, Chandler, you are still boycotting all the pilgrim holidays.
	\switchcolumn
	\charactername{莫妮卡：}钱德勒，我猜你还在抵制所有清教徒相关的节日吧。
	\switchcolumn*
	\charactername{Chandler:} Yes, every single one of them.
	\switchcolumn
	\charactername{钱德勒：}对，每个都抵制。
	\switchcolumn*
	\charactername{Monica:} Phoebe, you're gonna be with your grandma?
	\switchcolumn
	\charactername{莫妮卡：}菲比，你要跟奶奶一起过？
	\switchcolumn*
	\charactername{Phoebe:} Yes, and her boyfriend. But we're celebrating Thanksgiving in December 'cause he is lunar.
	\switchcolumn
	\charactername{菲比：}对啊，还有她男朋友。但我们十二月份才过感恩节，因为他过的是农历。
	\switchcolumn*
	\charactername{Monica:} So you're free Thursday, then.
	\switchcolumn
	\charactername{莫妮卡：}所以你周四有空咯。
	\switchcolumn*
	\charactername{Phoebe:} Yeah. Oh, can I come?
	\switchcolumn
	\charactername{菲比：}对啊。哦，我能去你家过节吗？
	\switchcolumn*
	\charactername{Monica:} Yeah. Rach, are you thinking you're gonna make it to Vail?
	\switchcolumn
	\charactername{莫妮卡：}可以啊。瑞秋，你能去成韦尔吗？
	\switchcolumn*
	\charactername{Rachel:} Absolutely. Shoop, shoop, shoop. Only a hundred and two dollars to go.
	\switchcolumn
	\charactername{瑞秋：}当然能。咻咻咻。还剩102美元就够买机票了。
	\switchcolumn*
	\charactername{Chandler:} I thought it was \$98.50.
	\switchcolumn
	\charactername{钱德勒：}我记得你刚才说还剩98.5美元啊。
	\switchcolumn*
	\charactername{Rachel:} Yeah, well it was. I, I broke a cup.
	\switchcolumn
	\charactername{瑞秋：}本来是，但我，我打碎了一个杯子。
	\switchcolumn*
	\charactername{Ross:} Well, I'm off to Carol's.
	\switchcolumn
	\charactername{罗斯：}好了，我要去卡萝家了。
	\switchcolumn*
	\charactername{Phoebe:} Ooh, ooh! Why don't we invite her?
	\switchcolumn
	\charactername{菲比：}哦，哦！我们为什么不邀请她一起来啊？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{mimicking} Ooh, ooh. Because she's my ex-wife, and will probably want to bring her, ooh, ooh, lesbian life partner.
	\switchcolumn
	\charactername{罗斯：}\notmain{模仿菲比的语气}哦，哦。因为她是我的前妻，而且她很可能会带上她的，哦，哦，女同性恋伴侣。
	\switchcolumn*
	\sense{Scene: Carol and Susan's apartment, Susan is there. Ross enters.}
	\switchcolumn
	\sense{场景：卡萝和苏珊的公寓，苏珊在那儿。罗斯走进来}
	\switchcolumn*
	\charactername{Ross:} Hi, is uh, is Carol here?
	\switchcolumn
	\charactername{罗斯：}嗨，卡萝在吗？
	\switchcolumn*
	\charactername{Susan:} No, she's at a faculty meeting.
	\switchcolumn
	\charactername{苏珊：}不在，她去开教职工会议了。
	\switchcolumn*
	\charactername{Ross:} Oh, I uh, just came by to pick up my skull. Well, not mine, but...
	\switchcolumn
	\charactername{罗斯：}哦，我，我就是过来拿我的头骨模型。嗯，不是我的头骨，是……
	\switchcolumn*
	\charactername{Susan:} Come in.
	\switchcolumn
	\charactername{苏珊：}进来吧。
	\switchcolumn*
	\charactername{Ross:} Thanks. Yeah, Carol borrowed it for a class, and I have to get it back to the museum.
	\switchcolumn
	\charactername{罗斯：}谢了。卡萝借去上课用的，我得还给博物馆。
	\switchcolumn*
	\charactername{Susan:} What's it look like?
	\switchcolumn
	\charactername{苏珊：}它长什么样啊？
	\switchcolumn*
	\charactername{Ross:} Kinda like a big face without skin.
	\switchcolumn
	\charactername{罗斯：}就像一张没皮肤的大脸。
	\switchcolumn*
	\charactername{Susan:} Yes, I'm familiar with the concept. We can just look for it.
	\switchcolumn
	\charactername{苏珊：}嗯，我知道那东西。我们找找看吧。
	\switchcolumn*
	\charactername{Ross:} Ok. \ennotmain{browsing the apartment} Wow, you guys sure have a lot of books about bein' a lesbian.
	\switchcolumn
	\charactername{罗斯：}好。\notmain{浏览公寓}哇，你们居然有这么多关于女同性恋的书。
	\switchcolumn*
	\charactername{Susan:} Well, you know, you have to take a course. Otherwise, they don't let you do it.
	\switchcolumn
	\charactername{苏珊：}嗯，你知道吗，这得上课学习才行。不然他们不让你当女同性恋的。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{picking up a book} Hey, hey, Yertle the Turtle. A classic.
	\switchcolumn
	\charactername{罗斯：}\notmain{拿起一本书}嘿，嘿，《乌龟耶尔特》。经典名著啊。
	\switchcolumn*
	\charactername{Susan:} Actually, I'm reading it to the baby.
	\switchcolumn
	\charactername{苏珊：}其实我是读给宝宝听的。
	\switchcolumn*
	\charactername{Ross:} The uh, the baby that hasn't been born yet? Wouldn't that mean you're... crazy?
	\switchcolumn
	\charactername{罗斯：}那，那个还没出生的宝宝？你这样不会显得……很疯狂吗？
	\switchcolumn*
	\charactername{Susan:} What, you don't think they can hear sounds in there?
	\switchcolumn
	\charactername{苏珊：}怎么，你觉得宝宝在肚子里听不到声音吗？
	\switchcolumn*
	\charactername{Ross:} You're not serious, I mean, you really... you really talk to it?
	\switchcolumn
	\charactername{罗斯：}你不是认真的吧，我是说，你真的……真的会跟它说话？
	\switchcolumn*
	\charactername{Susan:} Yeah, all the time. I want the baby to know my voice.
	\switchcolumn
	\charactername{苏珊：}对啊，一直都在说。我想让宝宝熟悉我的声音。
	\switchcolumn*
	\charactername{Ross:} Do you uh, do you talk about me?
	\switchcolumn
	\charactername{罗斯：}那你，你会提到我吗？
	\switchcolumn*
	\charactername{Susan:} Yeah, yeah, all the time.
	\switchcolumn
	\charactername{苏珊：}会啊，经常提到。
	\switchcolumn*
	\charactername{Ross:} Really?
	\switchcolumn
	\charactername{罗斯：}真的吗？
	\switchcolumn*
	\charactername{Susan:} But um, we just refer to you as Bobo the Sperm Guy.
	\switchcolumn
	\charactername{苏珊：}不过，我们都叫你“精子哥波波”。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, everyone is there but Rachel.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，除了瑞秋其他人都在}
	\switchcolumn*
	\charactername{Ross:} Look, if she's talking to it, I just think that I should get some belly time too. Not that I believe any of this.
	\switchcolumn
	\charactername{罗斯：}你看，如果她都跟宝宝说话，我觉得我也该有“贴肚子交流时间”。虽然我根本不信这一套。
	\switchcolumn*
	\charactername{Phoebe:} Oh, I believe it. I think the baby can totally hear everything. I can show you. Look, this will seem a little weird, but you put your head inside this turkey, and then we'll all talk, and you'll hear everything we say.
	\switchcolumn
	\charactername{菲比：}哦，我信。我觉得宝宝什么都能听到。我可以证明给你看。你看，这可能有点奇怪，但你把脑袋伸进火鸡里，然后我们说话，你就能听到我们说的所有话了。
	\switchcolumn*
	\charactername{Chandler:} I'd just like to say that I'm totally behind this experiment. In fact, I'd very much like to butter your head.
	\switchcolumn
	\charactername{钱德勒：}我只想说我全力支持这个实验。其实，我很想在你头上抹点黄油。
	\switchcolumn*
	\ennotmain{Rachel enters.}
	\switchcolumn
	\notmain{瑞秋走进来}
	\switchcolumn*
	\charactername{Monica:} Hey, Rach, did you make your money?
	\switchcolumn
	\charactername{莫妮卡：}嘿，瑞秋，凑够钱了吗？
	\switchcolumn*
	\charactername{Rachel:} No, not even close. Forget Vail, forget seeing my family, forget shoop, shoop, shoop.
	\switchcolumn
	\charactername{瑞秋：}没有，差远了。去不成韦尔了，见不到家人了，咻咻咻也没用了。
	\switchcolumn*
	\charactername{Monica:} Rach, here's your mail.
	\switchcolumn
	\charactername{莫妮卡：}瑞秋，你的邮件。
	\switchcolumn*
	\charactername{Rachel:} Thanks, you can just put it on the table.
	\switchcolumn
	\charactername{瑞秋：}谢了，放桌子上就行。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{insistently} No, here's your mail.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{坚持道}不，这是你的邮件，拿着。
	\switchcolumn*
	\charactername{Rachel:} Thanks, you can just put it on the table.
	\switchcolumn
	\charactername{瑞秋：}谢了，放桌子上就行。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{gives her an envelope} Would you just open it?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{递给她一个信封}你就打开看看嘛？
	\switchcolumn*
	\ennotmain{Rachel opens it. Inside is the money she needed.}
	\switchcolumn
	\notmain{瑞秋打开信封，里面是她需要的钱}
	\switchcolumn*
	\charactername{Rachel:} Oh my god, oh, you guys are great.
	\switchcolumn
	\charactername{瑞秋：}天啊，你们太好了。
	\switchcolumn*
	\charactername{Monica:} We all chipped in.
	\switchcolumn
	\charactername{莫妮卡：}我们大家凑的。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{to Monica} We did?
	\switchcolumn
	\charactername{乔伊：}\notmain{对莫妮卡}我们凑钱了？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Joey} You owe me 20 bucks.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对乔伊}你欠我20美元。
	\switchcolumn*
	\charactername{Rachel:} Thank you. Thank you so much!
	\switchcolumn
	\charactername{瑞秋：}谢谢你们。太感谢了！
	\switchcolumn*
	\charactername{Monica:} \ennotmain{hands Chandler a bag} Chandler, here you go, got your traditional Thanksgiving feast, you got your tomato soup, your grilled cheese fixin's, and your family size bag of Funyuns.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{递给钱德勒一个袋子}钱德勒，给你，这是你的传统感恩节大餐，有番茄汤、烤芝士的配料，还有家庭装的洋葱圈脆片。
	\switchcolumn*
	\charactername{Rachel:} Wait, wait, Chandler, this is what you're havin' for Thanksgiving dinner? What, what, what is it with you and this holiday?
	\switchcolumn
	\charactername{瑞秋：}等等，钱德勒，这就是你感恩节的晚餐？你跟这个节日到底有什么过节啊？
	\switchcolumn*
	\charactername{Chandler:} All right, I'm nine years old.
	\switchcolumn
	\charactername{钱德勒：}那时候我九岁。
	\switchcolumn*
	\charactername{Ross:} Oh, I hate this story.
	\switchcolumn
	\charactername{罗斯：}哦，我最讨厌这个故事了。
	\switchcolumn*
	\charactername{Chandler:} We just finished this magnificent Thanksgiving dinner. I have--and I remember this part vividly--a mouthful of pumpkin pie, and this is the moment my parents choose to tell me they're getting divorced.
	\switchcolumn
	\charactername{钱德勒：}我们刚吃完一顿超棒的感恩节晚餐。我嘴里还含着南瓜派——这一幕我记得特别清楚——就在这时候，我爸妈告诉我他们要离婚了。
	\switchcolumn*
	\charactername{Rachel:} Oh my god.
	\switchcolumn
	\charactername{瑞秋：}天啊。
	\switchcolumn*
	\charactername{Chandler:} Yes. It's very difficult to appreciate a Thanksgiving dinner once you've seen it in reverse.
	\switchcolumn
	\charactername{钱德勒：}是啊。一旦你经历过这种“反转”的感恩节晚餐，就很难再喜欢这个节日了。
	\switchcolumn*
	\sense{Scene: The subway, Joey spots a gorgeous woman waiting. He goes up to her.}
	\switchcolumn
	\sense{场景：地铁里，乔伊看到一位美女在等车，走上前去}
	\switchcolumn*
	\charactername{Joey:} Uh, hi. We uh, we used to work together.
	\switchcolumn
	\charactername{乔伊：}呃，嗨。我们，我们以前一起工作过。
	\switchcolumn*
	\charactername{Girl:} We did?
	\switchcolumn
	\charactername{美女：}是吗？
	\switchcolumn*
	\charactername{Joey:} Yeah, at Macy's. You were the Obsession girl, right? I was the Aramis guy. \ennotmain{pretends to spray cologne} Aramis? Aramis?
	\switchcolumn
	\charactername{乔伊：}对啊，在梅西百货。你是“迷惑”香水的模特，对吧？我是“雅男士”香水的模特。\notmain{假装喷香水}雅男士？雅男士？
	\switchcolumn*
	\charactername{Girl:} Yeah, right.
	\switchcolumn
	\charactername{美女：}哦，对哦。
	\switchcolumn*
	\charactername{Joey:} I gotta tell you. You're the best in the business.
	\switchcolumn
	\charactername{乔伊：}我得跟你说，你是这行里最棒的。
	\switchcolumn*
	\charactername{Girl:} Get out.
	\switchcolumn
	\charactername{美女：}别逗了。
	\switchcolumn*
	\charactername{Joey:} I'm serious. You're amazing. You know when to spritz, when to lay back.
	\switchcolumn
	\charactername{乔伊：}我是认真的。你太厉害了。你知道什么时候该喷香水，什么时候该低调。
	\switchcolumn*
	\charactername{Girl:} Really? You don't know what that means to me.
	\switchcolumn
	\charactername{美女：}真的吗？你不知道这对我来说意义多大。
	\switchcolumn*
	\charactername{Joey:} Ooh, you smell great tonight. What're you wearing?
	\switchcolumn
	\charactername{乔伊：}哦，你今晚闻起来真香。你喷的什么香水？
	\switchcolumn*
	\charactername{Girl:} \ennotmain{provocatively} Nothing.
	\switchcolumn
	\charactername{美女：}\notmain{挑逗地}什么都没喷。
	\switchcolumn*
	\charactername{Joey:} Listen, uh, you wanna go get a drink or something?
	\switchcolumn
	\charactername{乔伊：}那个，你想不想去喝一杯或者做点别的？
	\switchcolumn*
	\charactername{Girl:} Yeah. \ennotmain{she gets up, notices something behind Joey} Oh.
	\switchcolumn
	\charactername{美女：}好啊。\notmain{她站起来，看到乔伊身后的东西}哦。
	\switchcolumn*
	\charactername{Joey:} What's wrong?
	\switchcolumn
	\charactername{乔伊：}怎么了？
	\switchcolumn*
	\charactername{Girl:} I just remembered, I have to do something.
	\switchcolumn
	\charactername{美女：}我突然想起我有事要做。
	\switchcolumn*
	\charactername{Joey:} Oh. What?
	\switchcolumn
	\charactername{乔伊：}哦。什么事？
	\switchcolumn*
	\charactername{Girl:} Um, leave.
	\switchcolumn
	\charactername{美女：}嗯，离开这儿。
	\switchcolumn*
	\charactername{Joey:} Wait, wait, wait!
	\switchcolumn
	\charactername{乔伊：}等等，等等！
	\switchcolumn*
	\ennotmain{Joey turns around and sees his face on a poster in the subway. The poster says: What Mario isn't telling you...V.D., you never know who might have it. A variety of scenes are shown with the poster displayed all over New York City.}
	\switchcolumn
	\notmain{乔伊转过身，看到地铁里的海报上是自己的脸。海报上写着：马里奥没告诉你的事……性病，你永远不知道谁会染上。镜头展示了这张海报在纽约市各处张贴的场景。}
	\switchcolumn*
	\sense{Scene: Central Perk, Joey enters, amongst snickers from the gang.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，乔伊走进来，众人偷笑}
	\switchcolumn*
	\charactername{Joey:} So I guess you all saw it.
	\switchcolumn
	\charactername{乔伊：}我猜你们都看到了吧。
	\switchcolumn*
	\charactername{Rachel:} Saw what?
	\switchcolumn
	\charactername{瑞秋：}看到什么？
	\switchcolumn*
	\charactername{Phoebe:} No, we were just laughing. You know, how laughter can be infectious.
	\switchcolumn
	\charactername{菲比：}没有，我们就是在笑而已。你知道，笑声是会传染的。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Joey enters, upset.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，乔伊沮丧地走进来}
	\switchcolumn*
	\charactername{Joey:} Set another place for Thanksgiving. My entire family thinks I have VD.
	\switchcolumn
	\charactername{乔伊：}感恩节多准备一个人的位置吧。我全家都以为我得了性病。
	\switchcolumn*
	\charactername{Chandler:} Tonight, on a very special Blossom.
	\switchcolumn
	\charactername{钱德勒：}今晚，《 blossom》特别节目\notmain{调侃乔伊的遭遇像电视剧剧情}。
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Monica is cooking Thanksgiving dinner. Chandler is standing in the doorway, not wanting to participate in the festivities.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，莫妮卡正在做感恩节晚餐。钱德勒站在门口，不想加入庆祝活动}
	\switchcolumn*
	\charactername{Monica:} Mmm, looking good. Ok, cider's mulling, turkey's turking, yams are yamming. \ennotmain{notices Ross is depressed} What?
	\switchcolumn
	\charactername{莫妮卡：}嗯，看起来不错。苹果酒在加热，火鸡在烤，红薯在煮。\notmain{注意到罗斯情绪低落}怎么了？
	\switchcolumn*
	\charactername{Ross:} I don't know. It's just not the same without Mom in the kitchen.
	\switchcolumn
	\charactername{罗斯：}不知道。厨房没有妈在，感觉就是不一样。
	\switchcolumn*
	\charactername{Monica:} All right, that's it. You know what? Just get out of my way and stop moping.
	\switchcolumn
	\charactername{莫妮卡：}好了，够了。你知道吗？别挡道，也别闷闷不乐了。
	\switchcolumn*
	\charactername{Ross:} That's closer.
	\switchcolumn
	\charactername{罗斯：}这还差不多\notmain{有点妈当年的感觉了}。
	\switchcolumn*
	\ennotmain{Rachel enters, excited.}
	\switchcolumn
	\notmain{瑞秋兴奋地走进来}
	\switchcolumn*
	\charactername{Rachel:} I got the tickets! I got the tickets! Five hours from now, shoop, shoop, shoop.
	\switchcolumn
	\charactername{瑞秋：}我买到机票了！我买到机票了！五个小时后，咻咻咻，就能出发了。
	\switchcolumn*
	\charactername{Chandler:} Oh, you must stop shooping.
	\switchcolumn
	\charactername{钱德勒：}哦，你别再“咻咻咻”了。
	\switchcolumn*
	\charactername{Rachel:} Ok, I'm gonna get my stuff.
	\switchcolumn
	\charactername{瑞秋：}好，我去收拾东西。
	\switchcolumn*
	\charactername{Joey:} Chandler, will you just come in already?
	\switchcolumn
	\charactername{乔伊：}钱德勒，你就进来嘛？
	\switchcolumn*
	\charactername{Chandler:} No, I prefer to keep a safe distance from all this merriment.
	\switchcolumn
	\charactername{钱德勒：}不了，我宁愿跟这些欢乐的氛围保持安全距离。
	\switchcolumn*
	\ennotmain{Phoebe takes a slice of pumpkin pie and waves it in front of Chandler's face.}
	\switchcolumn
	\notmain{菲比拿起一块南瓜派，在钱德勒面前晃}
	\switchcolumn*
	\charactername{Phoebe:} Look out, incoming pumpkin pie!
	\switchcolumn
	\charactername{菲比：}小心，南瓜派来啦！
	\switchcolumn*
	\charactername{Chandler:} Ok, we all laughed when you did it with the stuffing, but that's not funny anymore.
	\switchcolumn
	\charactername{钱德勒：}好吧，你用填料那么逗我的时候我们都笑了，但现在这就不好笑了。
	\switchcolumn*
	\ennotmain{Chandler leaves.}
	\switchcolumn
	\notmain{钱德勒离开了}
	\switchcolumn*
	\charactername{Joey:} Hey, Monica, I got a question. I don't see any tater tots.
	\switchcolumn
	\charactername{乔伊：}嘿，莫妮卡，我有个问题。怎么没看到土豆 tots\notmain{土豆块}啊？
	\switchcolumn*
	\charactername{Monica:} That's not a question.
	\switchcolumn
	\charactername{莫妮卡：}这不算问题。
	\switchcolumn*
	\charactername{Joey:} But my mom always makes them. It's like a tradition. You get a little piece of turkey on your fork, a little cranberry sauce, and a tot! It's bad enough I can't be with my family because of my disease.
	\switchcolumn
	\charactername{乔伊：}但我妈每次都做啊。这是传统。叉子上叉一小块火鸡，一点蔓越莓酱，再配一个土豆块！我因为“病”不能跟家人过节已经够惨了。
	\switchcolumn*
	\charactername{Monica:} All right, fine. Tonight's potatoes will be both mashed with lumps, and in the form of tots.
	\switchcolumn
	\charactername{莫妮卡：}好吧好吧。今晚的土豆既有带颗粒的土豆泥，也有土豆块。
	\switchcolumn*
	\charactername{Ross:} Ok, I'm off to talk to my unborn child.
	\switchcolumn
	\charactername{罗斯：}好，我要去跟我未出生的宝宝说话了。
	\switchcolumn*
	\ennotmain{Ross grabs for some food, Monica slaps his hand away.}
	\switchcolumn
	\notmain{罗斯伸手去拿吃的，莫妮卡拍掉了他的手}
	\switchcolumn*
	\charactername{Monica:} Ah!
	\switchcolumn
	\charactername{莫妮卡：}啊！
	\switchcolumn*
	\charactername{Ross:} Ok, Mom never hit.
	\switchcolumn
	\charactername{罗斯：}好吧，妈从来不会打我。
	\switchcolumn*
	\ennotmain{Ross exits.}
	\switchcolumn
	\notmain{罗斯离开了}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{stirring pot} Ok, all done.
	\switchcolumn
	\charactername{菲比：}\notmain{搅拌锅}好了，搞定了。
	\switchcolumn*
	\charactername{Monica:} What, Phoebe, did you whip the potatoes? Ross needs lumps!
	\switchcolumn
	\charactername{莫妮卡：}什么，菲比，你把土豆打成泥了？罗斯需要带颗粒的！
	\switchcolumn*
	\charactername{Phoebe:} Oh, I'm sorry, oh, I just, I thought we could have them whipped and then add some peas and onions.
	\switchcolumn
	\charactername{菲比：}哦，对不起，我只是觉得我们可以把土豆打成泥，然后加点豌豆和洋葱。
	\switchcolumn*
	\charactername{Monica:} Why would we do that?
	\switchcolumn
	\charactername{莫妮卡：}我们为什么要这么做？
	\switchcolumn*
	\charactername{Phoebe:} Well, 'cause then they'd be like my mom used to make them, you know, before she died.
	\switchcolumn
	\charactername{菲比：}因为这样就像我妈以前做的那样了，你知道，她去世之前经常这么做。
	\switchcolumn*
	\charactername{Monica:} Ok, three kinds of potatoes coming up.
	\switchcolumn
	\charactername{莫妮卡：}好吧，三种土豆马上就好。
	\switchcolumn*
	\charactername{Rachel:} Ok, good-bye you guys. Thanks for everything. \ennotmain{she starts to leave, and hits everyone with her skis} Oh, sorry! Oh, sorry!
	\switchcolumn
	\charactername{瑞秋：}好了，再见各位。谢谢你们所做的一切。\notmain{她准备离开，滑雪板撞到了每个人}哦，对不起！哦，对不起！
	\switchcolumn*
	\ennotmain{Chandler enters, running.}
	\switchcolumn
	\notmain{钱德勒跑着走进来}
	\switchcolumn*
	\charactername{Chandler:} The most unbelievable thing has happened. Underdog has just gotten away.
	\switchcolumn
	\charactername{钱德勒：}出大事了！超级英雄狗\notmain{卡通角色}跑了！
	\switchcolumn*
	\charactername{Joey:} The balloon?
	\switchcolumn
	\charactername{乔伊：}气球？
	\switchcolumn*
	\charactername{Chandler:} No, no, the actual cartoon character. Of course the balloon. It's all over the news. Right before he reached Macy's, he broke free and was spotted flying over Washington Square Park. I'm goin' to the roof, who's with me?
	\switchcolumn
	\charactername{钱德勒：}不，不，是真的卡通角色。当然是气球啦。新闻都在报道。就在它快飞到梅西百货的时候，绳子断了，有人看到它飞过华盛顿广场公园。我要去屋顶看，谁跟我一起？
	\switchcolumn*
	\charactername{Rachel:} I can't, I gotta go.
	\switchcolumn
	\charactername{瑞秋：}我不行，我得走了。
	\switchcolumn*
	\charactername{Chandler:} Come on. An 80-foot inflatable dog let loose over the city. How often does that happen?
	\switchcolumn
	\charactername{钱德勒：}拜托。一个80英尺高的充气狗在城市上空乱飞。这种事多久才发生一次啊？
	\switchcolumn*
	\charactername{Phoebe:} Almost never.
	\switchcolumn
	\charactername{菲比：}几乎从不发生。
	\switchcolumn*
	\charactername{Monica:} Got the keys? or Got the keys!
	\switchcolumn
	\charactername{莫妮卡：}带钥匙了吗？还是“我带钥匙了！”\notmain{两种语气，一种疑问一种肯定}
	\switchcolumn*
	\charactername{Rachel:} Ok.
	\switchcolumn
	\charactername{瑞秋：}好。
	\switchcolumn*
	\ennotmain{Everyone leaves the apartment.}
	\switchcolumn
	\notmain{所有人都离开了公寓}
	\switchcolumn*
	\sense{Scene: Carol and Susan's, Ross is preparing to talk to her belly.}
	\switchcolumn
	\sense{场景：卡萝和苏珊的公寓，罗斯准备跟她的肚子说话}
	\switchcolumn*
	\charactername{Carol:} Anytime you're ready.
	\switchcolumn
	\charactername{卡萝：}你准备好了就可以开始了。
	\switchcolumn*
	\charactername{Ross:} Ok, ok, here we go. \ennotmain{he crouches down near her stomach} Ok, where am I talking to, here? I mean, uh, well, there is one way that seems to offer a certain acoustical advantage, but...
	\switchcolumn
	\charactername{罗斯：}好，好，开始了。\notmain{他蹲在她肚子旁边}那个，我该对着哪个位置说啊？我的意思是，呃，有个位置好像声学效果更好，但是……
	\switchcolumn*
	\charactername{Carol:} Just aim for the bump.
	\switchcolumn
	\charactername{卡萝：}就对着肚子凸起的地方说就行。
	\switchcolumn*
	\charactername{Ross:} Ok, ok, ok, ok, here goes. You know, I, you know, can't do this. Uh, this is too weird. I feel stupid.
	\switchcolumn
	\charactername{罗斯：}好，好，好，好，开始了。那个，我，我做不到。这太奇怪了。我觉得好傻。
	\switchcolumn*
	\charactername{Carol:} So don't do it, it's fine. You don't have to do it just because Susan does it.
	\switchcolumn
	\charactername{卡萝：}那就别做了，没关系。不用因为苏珊这么做你就必须做。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{quickly talking} Hello, baby. Hello, hello.
	\switchcolumn
	\charactername{罗斯：}\notmain{快速说道}嗨，宝宝。嗨，嗨。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the group is coming back from the roof.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，众人从屋顶回来}
	\switchcolumn*
	\charactername{Rachel:} I loved the moment when you first saw the giant dog shadow all over the park.
	\switchcolumn
	\charactername{瑞秋：}我最喜欢看到那只大狗的影子笼罩整个公园的那一刻了。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, but did they have to shoot him down? I mean, that was just mean.
	\switchcolumn
	\charactername{菲比：}是啊，但他们非得把它打下来吗？太残忍了。
	\switchcolumn*
	\charactername{Monica:} Ok, right about now the turkey should be crispy on the outside, juicy on the inside. Why are we standing here?
	\switchcolumn
	\charactername{莫妮卡：}好了，现在火鸡应该外酥里嫩了。我们站在这儿干嘛？
	\switchcolumn*
	\charactername{Rachel:} We're waiting for you to open the door. You got the keys.
	\switchcolumn
	\charactername{瑞秋：}我们在等你开门啊。你带钥匙了。
	\switchcolumn*
	\charactername{Monica:} No I don't.
	\switchcolumn
	\charactername{莫妮卡：}我没带。
	\switchcolumn*
	\charactername{Rachel:} Yes, you do. When we left, you said, "got the keys."
	\switchcolumn
	\charactername{瑞秋：}你带了。我们走的时候你说“我带钥匙了”。
	\switchcolumn*
	\charactername{Monica:} No I didn't. I asked, "got the ke-eys?"
	\switchcolumn
	\charactername{莫妮卡：}我没说。我是问“带钥匙了吗？”
	\switchcolumn*
	\charactername{Rachel:} No, no, no, you said, "got the keys".
	\switchcolumn
	\charactername{瑞秋：}不，不，不，你说的是“我带钥匙了”。
	\switchcolumn*
	\charactername{Chandler:} Do either of you have the keys?
	\switchcolumn
	\charactername{钱德勒：}你们俩到底谁带钥匙了？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{panicked} The oven is on.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{惊慌地}烤箱还开着！
	\switchcolumn*
	\charactername{Rachel:} Oh, I gotta get my ticket!
	\switchcolumn
	\charactername{瑞秋：}哦，我的机票！
	\switchcolumn*
	\charactername{Joey:} Wait, wait, we have a copy of your key.
	\switchcolumn
	\charactername{乔伊：}等等，等等，我们有你们的备用钥匙。
	\switchcolumn*
	\charactername{Monica:} Well then get it, get it!
	\switchcolumn
	\charactername{莫妮卡：}那快去拿，快去拿！
	\switchcolumn*
	\charactername{Joey:} That tone will not make me go any faster.
	\switchcolumn
	\charactername{乔伊：}你这种语气可不会让我走得更快。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{angry} Joey!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{生气地}乔伊！
	\switchcolumn*
	\charactername{Joey:} That one will.
	\switchcolumn
	\charactername{乔伊：}这个语气会。
	\switchcolumn*
	\ennotmain{Joey leaves to get the copy of the key.}
	\switchcolumn
	\notmain{乔伊去拿备用钥匙了}
	\switchcolumn*
	\sense{Scene: Carol and Susan's, Carol is reading, Ross is talking to her stomach.}
	\switchcolumn
	\sense{场景：卡萝和苏珊的公寓，卡萝在看书，罗斯在跟她的肚子说话}
	\switchcolumn*
	\charactername{Ross:} And everyone's telling me, you gotta pick a major, you gotta pick a major. So, on a dare, I picked paleontology. And you have no idea what I'm saying, because, let's face it, you're a fetus. You're just happy you don't have gills anymore.
	\switchcolumn
	\charactername{罗斯：}所有人都跟我说，你得选个专业，你得选个专业。然后我一时冲动，选了古生物学。你根本不知道我在说什么，因为说实话，你还只是个胎儿。你现在只庆幸自己没有鳃了吧。
	\switchcolumn*
	\charactername{Carol:} Look, you don't have to talk to it. You can sing to it if you want.
	\switchcolumn
	\charactername{卡萝：}其实你不用非得说话。如果你想，唱歌也行。
	\switchcolumn*
	\charactername{Ross:} Oh, please. I am not singing to your stomach, ok?
	\switchcolumn
	\charactername{罗斯：}哦，拜托。我才不要对着你的肚子唱歌，好吗？
	\switchcolumn*
	\ennotmain{Susan enters.}
	\switchcolumn
	\notmain{苏珊走进来}
	\switchcolumn*
	\charactername{Susan:} Hi, how's it goin?
	\switchcolumn
	\charactername{苏珊：}嗨，怎么样了？
	\switchcolumn*
	\charactername{Ross:} Shh! \ennotmain{singing} Here we come, walkin' down the street, get the funniest looks from, everyone we meet. Hey, hey! \ennotmain{to Carol} Hey, uh, did you just feel that?
	\switchcolumn
	\charactername{罗斯：}嘘！\notmain{唱歌}我们走在大街上，每个人都用奇怪的眼神看我们。嘿，嘿！\notmain{对卡萝}嘿，你刚才感觉到了吗？
	\switchcolumn*
	\charactername{Carol:} I did.
	\switchcolumn
	\charactername{卡萝：}感觉到了。
	\switchcolumn*
	\charactername{Ross:} Does it always, uh--?
	\switchcolumn
	\charactername{罗斯：}它经常这样，呃——？
	\switchcolumn*
	\charactername{Carol:} No, no that was the first.
	\switchcolumn
	\charactername{卡萝：}不，不，这是第一次。
	\switchcolumn*
	\charactername{Susan:} Keep singing! Keep singing!
	\switchcolumn
	\charactername{苏珊：}继续唱！继续唱！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{singing} Hey, hey, you're my baby, and I can't wait to meet you. When you come out I'll buy you a bagel, and then we'll go to the zoo.
	\switchcolumn
	\charactername{罗斯：}\notmain{唱歌}嘿，嘿，你是我的宝宝，我等不及要见到你了。你出生后我给你买贝果，然后我们去动物园。
	\switchcolumn*
	\charactername{Susan:} I felt it!
	\switchcolumn
	\charactername{苏珊：}我感觉到了！
	\switchcolumn*
	\charactername{Ross:} \ennotmain{singin} Hey, hey, I'm your daddy. I'm the one without any breasts.
	\switchcolumn
	\charactername{罗斯：}\notmain{唱歌}嘿，嘿，我是你爸爸。我就是那个没有胸的人。
	\switchcolumn*
	\sense{Scene: The Hallway, Joey has a tray full of keys, and is trying each one in the lock.}
	\switchcolumn
	\sense{场景：走廊里，乔伊拿着一托盘钥匙，正在试着一把把开锁}
	\switchcolumn*
	\charactername{Joey:} Nope, not that one.
	\switchcolumn
	\charactername{乔伊：}不是这把。
	\switchcolumn*
	\charactername{Monica:} Can you go any faster with that?
	\switchcolumn
	\charactername{莫妮卡：}你能快点吗？
	\switchcolumn*
	\charactername{Joey:} Hey, I got one keyhole and about a zillion keys. You do the math.
	\switchcolumn
	\charactername{乔伊：}嘿，就一个锁孔，却有一大堆钥匙。你自己算算吧。
	\switchcolumn*
	\charactername{Monica:} Why do you guys have so many keys in there anyway?
	\switchcolumn
	\charactername{莫妮卡：}你们那儿怎么会有这么多钥匙啊？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{sarcastic} For an emergency just like this.
	\switchcolumn
	\charactername{钱德勒：}\notmain{讽刺地}就是为了应对这种紧急情况啊。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{grabs Chandler by the shirt} All right, listen, smirky. If it wasn't for you and your stupid balloon, I would be on a plane watching a woman do this \ennotmain{makes a gesture like a stewardess pointing out exits} right now. But I'm not.
	\switchcolumn
	\charactername{瑞秋：}\notmain{抓住钱德勒的衬衫}好了，听着，爱傻笑的家伙。要不是你和你那愚蠢的气球，我现在已经在飞机上，看着空姐做这个动作\notmain{模仿空姐指示逃生出口的手势}了。但我现在却在这儿。
	\switchcolumn*
	\charactername{Monica:} I swear you said you had the keys.
	\switchcolumn
	\charactername{莫妮卡：}我发誓你说过你带钥匙了。
	\switchcolumn*
	\charactername{Rachel:} No, I didn't. I wouldn't say I had the keys unless I had the keys, and I obviously didn't have the keys.
	\switchcolumn
	\charactername{瑞秋：}我没说。我没带钥匙就不会说带了，很明显我没带。
	\switchcolumn*
	\charactername{Phoebe:} Ooh, ok, that's it. Enough with the keys. No one say keys.
	\switchcolumn
	\charactername{菲比：}哦，好了，够了。别再提钥匙了。谁都不准说“钥匙”这两个字。
	\switchcolumn*
	\ennotmain{Short pause.}
	\switchcolumn
	\notmain{短暂停顿}
	\switchcolumn*
	\charactername{Monica:} Why would I have the keys?
	\switchcolumn
	\charactername{莫妮卡：}我为什么要带钥匙啊？
	\switchcolumn*
	\charactername{Rachel:} Aside from the fact that you said you had them?
	\switchcolumn
	\charactername{瑞秋：}除了你说过你带了之外？
	\switchcolumn*
	\charactername{Monica:} But I didn't.
	\switchcolumn
	\charactername{莫妮卡：}但我没说。
	\switchcolumn*
	\charactername{Rachel:} Well, you should have.
	\switchcolumn
	\charactername{瑞秋：}但你本该带的。
	\switchcolumn*
	\charactername{Monica:} Why?
	\switchcolumn
	\charactername{莫妮卡：}为什么？
	\switchcolumn*
	\charactername{Rachel:} Because!
	\switchcolumn
	\charactername{瑞秋：}因为！
	\switchcolumn*
	\charactername{Monica:} Why?
	\switchcolumn
	\charactername{莫妮卡：}为什么？
	\switchcolumn*
	\charactername{Rachel:} Because!
	\switchcolumn
	\charactername{瑞秋：}因为！
	\switchcolumn*
	\charactername{Monica:} Why? Because everything is my responsibility? Isn't it enough that I'm making Thanksgiving dinner for everyone? You know, everyone wants a different kind of potatoes, so I'm making different kinds of potatoes. Does anybody care what kind of potatoes I want? Nooooo, no, no! \ennotmain{starting to cry} Just as long as Phoebe gets her peas and onions, and Mario gets his tots, and it's my first Thanksgiving, and it's all burned, and, and I... I...
	\switchcolumn
	\charactername{莫妮卡：}为什么？就因为所有事都该我负责吗？我给所有人做感恩节晚餐还不够吗？每个人都想要不同的土豆做法，我就做了好几种。有人关心我想吃什么样的土豆吗？没——有，没有！\notmain{开始哭}只要菲比能吃到加豌豆和洋葱的土豆，马里奥\notmain{调侃乔伊}能吃到土豆块就行，这可是我第一次做感恩节晚餐，结果全烧焦了，而且我……我……
	\switchcolumn*
	\charactername{Chandler:} Ok, Monica, only dogs can hear you now, so, look, the door's open. Here we go.
	\switchcolumn
	\charactername{钱德勒：}好了，莫妮卡，现在只有狗能听到你说话了，你看，门开了。我们进去吧。
	\switchcolumn*
	\ennotmain{They walk in. Smoke fills the apartment.}
	\switchcolumn
	\notmain{他们走进来，公寓里浓烟弥漫}
	\switchcolumn*
	\charactername{Monica:} Well, the turkey's burnt. \ennotmain{checking pots} Potatoes are ruined, potatoes are ruined, potatoes are ruined.
	\switchcolumn
	\charactername{莫妮卡：}好吧，火鸡烧焦了。\notmain{检查锅}土豆也毁了，土豆也毁了，土豆也毁了。
	\switchcolumn*
	\ennotmain{Ross enters, singing.}
	\switchcolumn
	\notmain{罗斯唱着歌走进来}
	\switchcolumn*
	\charactername{Ross:} Here we come, walkin' down the—this doesn't smell like Mom's.
	\switchcolumn
	\charactername{罗斯：}我们走在大街上——这味道可不像妈做的。
	\switchcolumn*
	\charactername{Monica:} No, it doesn't, does it? But you wanted lumps, Ross? \ennotmain{picks up the pan of badly burnt potatoes} Well, here you go, buddy, ya got one.
	\switchcolumn
	\charactername{莫妮卡：}是啊，不像，对吧？但你想要带颗粒的土豆泥，罗斯？\notmain{拿起一锅烤得焦黑的土豆}给你，兄弟，这下有“颗粒”了。
	\switchcolumn*
	\charactername{Rachel:} Oh, god, this is great! The plane is gone, so it looks like I'm stuck here with you guys.
	\switchcolumn
	\charactername{瑞秋：}哦，天啊，太棒了！飞机已经飞走了，看来我只能跟你们待在一起了。
	\switchcolumn*
	\charactername{Joey:} Hey, we all had better plans. This was nobody's first choice.
	\switchcolumn
	\charactername{乔伊：}嘿，我们本来都有更好的计划。这儿谁都不想来。
	\switchcolumn*
	\charactername{Monica:} Oh, really? So why was I busting my ass to make this delicious Thanksgiving dinner?
	\switchcolumn
	\charactername{莫妮卡：}哦，是吗？那我这么辛苦做这顿美味的感恩节晚餐是为了什么？
	\switchcolumn*
	\charactername{Joey:} You call that delicious?
	\switchcolumn
	\charactername{乔伊：}你把这叫美味？
	\switchcolumn*
	\ennotmain{all shouting}
	\switchcolumn
	\notmain{所有人都大喊起来}
	\switchcolumn*
	\charactername{Monica:} Stop it, stop it, stop it!
	\switchcolumn
	\charactername{莫妮卡：}别吵了，别吵了，别吵了！
	\switchcolumn*
	\charactername{Chandler:} Now this feels like Thanksgiving.
	\switchcolumn
	\charactername{钱德勒：}现在这才像感恩节嘛。
	\switchcolumn*
	\sense{Time lapse. Everyone is upset with each other. Phoebe is at the window.}
	\switchcolumn
	\sense{时间快进。所有人都在生彼此的气。菲比站在窗边}
	\switchcolumn*
	\charactername{Phoebe:} Ooh.
	\switchcolumn
	\charactername{菲比：}哦。
	\switchcolumn*
	\charactername{Rachel:} What?
	\switchcolumn
	\charactername{瑞秋：}怎么了？
	\switchcolumn*
	\charactername{Phoebe:} Ugly Naked Guy's taking his turkey out of the oven. Oh my god. He's not alone. Ugly Naked Guy's having Thanksgiving dinner with Ugly Naked Gal.
	\switchcolumn
	\charactername{菲比：}裸体丑男正在把火鸡从烤箱里拿出来。天啊。他不是一个人。裸体丑男在跟裸体丑女一起过感恩节晚餐。
	\switchcolumn*
	\ennotmain{They all run to the window.}
	\switchcolumn
	\notmain{所有人都跑到窗边}
	\switchcolumn*
	\charactername{Joey:} I've gotta see this. All right Ugly Naked Guy!
	\switchcolumn
	\charactername{乔伊：}我得看看。好了，裸体丑男！
	\switchcolumn*
	\charactername{Monica:} Ooh, Ugly Naked Dancing!
	\switchcolumn
	\charactername{莫妮卡：}哦，裸体丑男在跳舞！
	\switchcolumn*
	\charactername{Phoebe:} It's nice that he has someone.
	\switchcolumn
	\charactername{菲比：}他能有人陪伴真好。
	\switchcolumn*
	\sense{Time lapse. The gang is around the table, eating grilled cheese sandwiches.}
	\switchcolumn
	\sense{时间快进。众人围坐在桌子旁，吃着烤芝士三明治}
	\switchcolumn*
	\charactername{Chandler:} Shall I carve?
	\switchcolumn
	\charactername{钱德勒：}我来“切”怎么样？
	\switchcolumn*
	\charactername{Rachel:} By all means.
	\switchcolumn
	\charactername{瑞秋：}当然可以。
	\switchcolumn*
	\charactername{Chandler:} Ok, who wants light cheese, and who wants dark cheese?
	\switchcolumn
	\charactername{钱德勒：}好，谁要浅色芝士，谁要深色芝士？
	\switchcolumn*
	\charactername{Ross:} I don't even wanna know about the dark cheese.
	\switchcolumn
	\charactername{罗斯：}我连深色芝士是什么都不想知道。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{holding sandwich} Does anybody wanna split this with me?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{拿着三明治}有人想跟我分这个吗？
	\switchcolumn*
	\charactername{Joey:} Oh, I will.
	\switchcolumn
	\charactername{乔伊：}哦，我来。
	\switchcolumn*
	\charactername{Phoebe:} Ooh, you guys have to make a wish.
	\switchcolumn
	\charactername{菲比：}哦，你们得许愿。
	\switchcolumn*
	\charactername{Monica:} Make a wish?
	\switchcolumn
	\charactername{莫妮卡：}许愿？
	\switchcolumn*
	\charactername{Phoebe:} Come on, you know, Thanksgiving. Ooh, you got the bigger half. What'd you wish for?
	\switchcolumn
	\charactername{菲比：}拜托，感恩节要许愿的啊。哦，你拿到了大的那一半。你许了什么愿？
	\switchcolumn*
	\charactername{Joey:} The bigger half.
	\switchcolumn
	\charactername{乔伊：}我许愿要大的那一半。
	\switchcolumn*
	\charactername{Chandler:} I'd like to propose a toast. Little toast here, ding ding. I know this isn't the kind of Thanksgiving that all of you all planned, but for me, this has been really great, you know, I think because it didn't involve divorce or projectile vomiting. Anyway, I was just thinking, I mean, if you'd gone to Vail, and if you guys'd been with your family, if you didn't have syphilis and stuff, we wouldn't be all together, you know? So I guess what I'm trying to say is that I'm very thankful that all of your Thanksgivings sucked.
	\switchcolumn
	\charactername{钱德勒：}我想敬大家一杯。小小地敬一下，叮叮当。我知道这不是你们每个人计划中的感恩节，但对我来说，这真的很棒，因为这次没有离婚，也没有呕吐。不管怎样，我在想，要是你去了韦尔，要是你们跟家人在一起，要是你没得梅毒之类的病，我们就不会聚在一起了，对吧？所以我想说的是，我很庆幸你们的感恩节都过得很糟糕。
	\switchcolumn*
	\charactername{All:} That's so sweet.
	\switchcolumn
	\charactername{众人：}你真贴心。
	\switchcolumn*
	\charactername{Ross:} And hey, here's to a lousy Christmas.
	\switchcolumn
	\charactername{罗斯：}来，为糟糕的圣诞节干杯。
	\switchcolumn*
	\charactername{Rachel:} And a crappy New Year.
	\switchcolumn
	\charactername{瑞秋：}为糟糕的新年干杯。
	\switchcolumn*
	\charactername{Chandler:} Here, here!
	\switchcolumn
	\charactername{钱德勒：}干杯，干杯！
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: The Subway, Joey sees his poster and he peels off the caption on his poster, revealing more posters underneath. The captions read, as follows: Bladder Control Problem Stop Wife Beating Hemorrhoids? Winner of 3 Tony Awards... He's finally happy with that and walks away.}
	\switchcolumn
	\sense{场景：地铁里，乔伊看到自己的海报，撕掉了上面的文字，露出了下面更多的海报。文字内容如下：膀胱控制问题 停止家暴 痔疮困扰？ 三项托尼奖得主……他终于满意了，然后走开了。}
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage