\begin{paracol}{2}
	\sense{Scene: Monica and Rachel's, Ross is entering.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，罗斯走进来}
	\switchcolumn*
	\charactername{Ross:} Guys? There's a somebody I'd like you to meet.
	\switchcolumn
	\charactername{罗斯：}伙计们？我想给你们介绍个人。
	\switchcolumn*
	\ennotmain{A monkey jumps on to his shoulder.}
	\switchcolumn
	\notmain{一只猴子跳到他肩膀上}
	\switchcolumn*
	\charactername{All:} Oooh!
	\switchcolumn
	\charactername{众人：}哦！
	\switchcolumn*
	\charactername{Monica:} W-wait. What is that?
	\switchcolumn
	\charactername{莫妮卡：}等-等一下。那是什么？
	\switchcolumn*
	\charactername{Ross:} 'That' would be Marcel. You wanna say hi?
	\switchcolumn
	\charactername{罗斯：}“那”是马塞尔。你们想跟它打招呼吗？
	\switchcolumn*
	\charactername{Monica:} No, no, I don't.
	\switchcolumn
	\charactername{莫妮卡：}不，不了，不想。
	\switchcolumn*
	\charactername{Rachel:} Oh, he is precious! Where did you get him?
	\switchcolumn
	\charactername{瑞秋：}哦，它太可爱了！你从哪儿弄来的？
	\switchcolumn*
	\charactername{Ross:} My friend Bethel rescued him from some lab.
	\switchcolumn
	\charactername{罗斯：}我的朋友贝瑟尔从某个实验室把它救出来的。
	\switchcolumn*
	\charactername{Phoebe:} That is so cruel! Why? Why would a parent name their child Bethel?
	\switchcolumn
	\charactername{菲比：}太残忍了！为什么？父母怎么会给孩子取名叫贝瑟尔？
	\switchcolumn*
	\charactername{Chandler:} Hey, that monkey's got a Ross on its ass!
	\switchcolumn
	\charactername{钱德勒：}嘿，这猴子屁股上长得跟罗斯似的！
	\switchcolumn*
	\charactername{Monica:} Ross, is he gonna live with you, like, in your apartment?
	\switchcolumn
	\charactername{莫妮卡：}罗斯，它要跟你一起住，住在你的公寓里吗？
	\switchcolumn*
	\charactername{Ross:} Yeah. I mean, it's been kinda quiet since Carol left, so...
	\switchcolumn
	\charactername{罗斯：}对啊。卡萝离开后，公寓里挺安静的，所以……
	\switchcolumn*
	\charactername{Monica:} Why don't you just get a roommate?
	\switchcolumn
	\charactername{莫妮卡：}那你为什么不找个室友呢？
	\switchcolumn*
	\charactername{Ross:} Nah, I dunno... I think you reach a certain age, having a roommate is kinda pathe- \ennotmain{Realises} ....sorry, that's, that's 'pathet', which is Sanskrit for 'really cool way to live'.
	\switchcolumn
	\charactername{罗斯：}不了，我不知道……我觉得人到了一定年纪，找室友就有点可悲——\notmain{意识到说错话}……抱歉，那是“帕特”，梵语里是“超酷的生活方式”的意思。
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, Phoebe is getting ready to sing. Joey is not there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，菲比准备唱歌。乔伊不在场}
	\switchcolumn*
	\charactername{Phoebe:} So you guys, I'm doing all new material tonight. I have twelve new songs about my mother's suicide, and one about a snowman.
	\switchcolumn
	\charactername{菲比：}伙计们，我今晚要唱全新的歌。有十二首是关于我妈妈自杀的，还有一首是关于雪人的。
	\switchcolumn*
	\charactername{Chandler:} Might wanna open with the snowman.
	\switchcolumn
	\charactername{钱德勒：}或许应该先唱雪人那首。
	\switchcolumn*
	\ennotmain{Enter Joey}
	\switchcolumn
	\notmain{乔伊走进来}
	\switchcolumn*
	\charactername{All:} Hey, Joey. Hey, buddy.
	\switchcolumn
	\charactername{众人：}嘿，乔伊。嘿，兄弟。
	\switchcolumn*
	\charactername{Monica:} So, how'd it go?
	\switchcolumn
	\charactername{莫妮卡：}怎么样了？
	\switchcolumn*
	\charactername{Joey:} Ahhhhhh, I didn't get the job.
	\switchcolumn
	\charactername{乔伊：}唉——，我没得到那份工作。
	\switchcolumn*
	\charactername{Ross:} How could you not get it? You were Santa last year.
	\switchcolumn
	\charactername{罗斯：}怎么会没得到？你去年可是圣诞老人啊。
	\switchcolumn*
	\charactername{Joey:} I dunno. Some fat guy's sleeping with the store manager. He's not even jolly, it's all political.
	\switchcolumn
	\charactername{乔伊：}不知道。某个胖子跟商店经理有一腿。他连点喜气都没有，全是靠关系。
	\switchcolumn*
	\charactername{Monica:} So what are you gonna be?
	\switchcolumn
	\charactername{莫妮卡：}那你要扮演什么？
	\switchcolumn*
	\charactername{Joey:} Ah, I'm gonna be one of his helpers. It's just such a slap in the face, y'know?
	\switchcolumn
	\charactername{乔伊：}唉，我要当他的助手之一。这简直是打脸，你知道吗？
	\switchcolumn*
	\charactername{Rachel:} Hey, do you guys know what you're doing for New Year's? \ennotmain{They all protest and hit her with cushions} Gee, what?! What is wrong with New Year's?
	\switchcolumn
	\charactername{瑞秋：}嘿，你们新年夜有什么安排吗？\notmain{众人抗议，用靠垫打她}天啊，怎么了？新年夜有什么问题吗？
	\switchcolumn*
	\charactername{Chandler:} Nothing for you, you have Paolo. You don't have to face the horrible pressures of this holiday: desperate scramble to find anything with lips just so you can have someone to kiss when the ball drops!! Man, I'm talking loud!
	\switchcolumn
	\charactername{钱德勒：}对你来说没问题，你有保罗。你不用面对这个节日的可怕压力：拼命找个有嘴的人，就为了球落下的时候有人可吻！天啊，我声音太大了！
	\switchcolumn*
	\charactername{Rachel:} Well, for your information, Paolo is gonna be in Rome this New Year, so I'll be just as pathetic as the rest of you.
	\switchcolumn
	\charactername{瑞秋：}跟你们说，保罗新年要去罗马，所以我会跟你们一样可怜。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, you wish!
	\switchcolumn
	\charactername{菲比：}是啊，你想得美！
	\switchcolumn*
	\charactername{Chandler:} It's just that I'm sick of being a victim of this Dick Clark holiday. I say this year, no dates, we make a pact. Just the six of us- dinner.
	\switchcolumn
	\charactername{钱德勒：}我只是受够了当这个迪克·克拉克\notmain{新年晚会主持人}节日的受害者。我说今年，不约会，我们约定好。就我们六个人——一起吃晚饭。
	\switchcolumn*
	\charactername{All:} Yeah, okay. Alright.
	\switchcolumn
	\charactername{众人：}好啊，行。
	\switchcolumn*
	\charactername{Chandler:} Y'know, I was hoping for a little more enthusiasm.
	\switchcolumn
	\charactername{钱德勒：}我还以为你们会更兴奋点呢。
	\switchcolumn*
	\charactername{All:} Woooo! Yeah!
	\switchcolumn
	\charactername{众人：}哇哦！好耶！
	\switchcolumn*
	\charactername{Rachel:} Phoebe, you're on.
	\switchcolumn
	\charactername{瑞秋：}菲比，该你了。
	\switchcolumn*
	\charactername{Phoebe:} Oh, oh, good.
	\switchcolumn
	\charactername{菲比：}哦，哦，好的。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{Into microphone} Okay, hi. Ladies and gentlemen, back by popular demand, Miss Phoebe Buffay. Wooh!
	\switchcolumn
	\charactername{瑞秋：}\notmain{对着麦克风}好了，嗨。女士们先生们，应大家的热烈要求，有请菲比·布菲小姐。哇哦！
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Takes mike} Thanks, hi. Um, I wanna start with a song that means a lot to me this time of year. \ennotmain{Shakes bell as an introduction} \ennotmain{Sung:}
	\switchcolumn
	\charactername{菲比：}\notmain{接过麦克风}谢谢，嗨。嗯，我想先唱一首在这个时节对我意义重大的歌。\notmain{摇铃作为前奏}\notmain{唱道：}
	\switchcolumn*
	I made a man with eyes of coal
	\switchcolumn
	我做了个眼睛像煤炭的雪人，
	\switchcolumn*
	And a smile so bewitchin',
	\switchcolumn
	笑容迷人又销魂，
	\switchcolumn*
	How was I supposed to know
	\switchcolumn
	我怎会料到啊，
	\switchcolumn*
	That my mom was dead in the kitchen?
	\switchcolumn
	我妈妈死在了厨房中？
	\switchcolumn*
	\ennotmain{shakes bell} La lalala la la la la lalala la la...
	\switchcolumn
	\notmain{摇铃}啦 啦啦啦 啦啦啦 啦啦啦 啦啦……
	\switchcolumn*
	\ennotmain{Cut to later. Everyone is totally depressed by now.}
	\switchcolumn
	\notmain{镜头切换到稍后。众人现在都彻底郁闷了}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Sung}
	\switchcolumn
	\charactername{菲比：}\notmain{唱道}
	\switchcolumn*
	...My mother's ashes
	\switchcolumn
	……我妈妈的骨灰啊，
	\switchcolumn*
	Even her eyelashes
	\switchcolumn
	连她的睫毛呀，
	\switchcolumn*
	Are resting in a little yellow jar,
	\switchcolumn
	都安放在小小的黄色罐子里，
	\switchcolumn*
	And sometimes when it's breezy...
	\switchcolumn
	有时候微风一吹……
	\switchcolumn*
	\ennotmain{Over the sound of Phoebe singing we hear two scientists, Max and David, having a noisy discussion}
	\switchcolumn
	\notmain{菲比唱歌的同时，能听到两位科学家麦克斯和大卫在大声讨论}
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Sung}
	\switchcolumn
	\charactername{菲比：}\notmain{唱道}
	\switchcolumn*
	...I feel a little sneezy
	\switchcolumn
	……我就有点想打喷嚏，
	\switchcolumn*
	And now I- \ennotmain{abruptly stops}
	\switchcolumn
	而现在我——\notmain{突然停下}
	\switchcolumn*
	Excuse me, excuse me! Yeah, noisy boys! \ennotmain{They stop talking and look up} Is it something that you would like to share with the entire group?
	\switchcolumn
	不好意思，不好意思！喂，吵闹的小子们！\notmain{他们停止讨论，抬头看}有什么事想跟大家分享吗？
	\switchcolumn*
	\charactername{Max:} No. No, that's- that's okay.
	\switchcolumn
	\charactername{麦克斯：}没有。不，没什么。
	\switchcolumn*
	\charactername{Phoebe:} Well, c'mon, if it's important enough to discuss while I'm playing, then I assume it's important enough for everyone else to hear!
	\switchcolumn
	\charactername{菲比：}拜托，如果这事重要到能在我唱歌的时候讨论，那我觉得也值得让其他人听听！
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Quietly, to the others} That guy's going home with a note!
	\switchcolumn
	\charactername{钱德勒：}\notmain{小声对其他人说}那家伙要被记“小本本”了！
	\switchcolumn*
	\charactername{David:} Noth- I was- I was just saying to my-
	\switchcolumn
	\charactername{大卫：}没-我只是-我只是跟我朋友说——
	\switchcolumn*
	\charactername{Phoebe:} Could you speak up please?
	\switchcolumn
	\charactername{菲比：}能大点声吗？
	\switchcolumn*
	\charactername{David:} \ennotmain{Stands up and speaks more loudly} Sorry, I wa- I was just saying to my friend that I thought you were the most beautiful woman that I'd ever seen in my- in my life. And then he said that- you said you thought
	\switchcolumn
	\charactername{大卫：}\notmain{站起来，大声说}抱歉，我-我只是跟我朋友说，我觉得你是我这辈子见过最美的女人。然后他说——你说你觉得
	\switchcolumn*
	\charactername{Max:} Daryl Hannah.
	\switchcolumn
	\charactername{麦克斯：}达丽尔·汉纳\notmain{好莱坞女星}。
	\switchcolumn*
	\charactername{David:} Daryl Hannah was the most beautiful woman that he'd ever seen in his life and I said yeah, I liked her in Splash, a lot, but not so much in- in Wall Street, I thought she had kind of a
	\switchcolumn
	\charactername{大卫：}达丽尔·汉纳是他这辈子见过最美的女人，我说对啊，我很喜欢她演的《美人鱼》，但不太喜欢《华尔街》里的她，我觉得她有点
	\switchcolumn*
	\charactername{Max:} Hard quality.
	\switchcolumn
	\charactername{麦克斯：}硬朗的气质。
	\switchcolumn*
	\charactername{David:} -hard quality. And uh, while Daryl Hannah is beautiful in a conventional way, you are luminous with a kind of a delicate grace. Then, uh, that-that-that's when you started yelling. \ennotmain{Sits down}
	\switchcolumn
	\charactername{大卫：}——硬朗的气质。而且，达丽尔·汉纳的美是传统意义上的美，但你身上有一种柔和优雅的光彩。然后，呃，就在这时你开始大喊了。\notmain{坐下}
	\switchcolumn*
	\charactername{Phoebe:} Okay, we're gonna take a short break. \ennotmain{Goes over to their table}
	\switchcolumn
	\charactername{菲比：}好吧，我们休息一会儿。\notmain{走向他们的桌子}
	\switchcolumn*
	\charactername{Joey:} Hey, that guy's going home with more than a note!
	\switchcolumn
	\charactername{乔伊：}嘿，那家伙可不止能拿到“小本本”\notmain{还能拿到菲比的青睐}！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, everyone except Joey is decorating for Christmas.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，除了乔伊，其他人都在装饰圣诞节}
	\switchcolumn*
	\charactername{Ross:} Come here, Marcel. Sit here. \ennotmain{Marcel wanders off}
	\switchcolumn
	\charactername{罗斯：}过来，马塞尔。坐这儿。\notmain{马塞尔走开了}
	\switchcolumn*
	\charactername{Rachel:} Pheebs, I can't believe he hasn't kissed you yet. I mean God, by my sixth date with Paolo, I mean he had already named both my breasts! ...Ooh. Did I just share too much?
	\switchcolumn
	\charactername{瑞秋：}菲比，我真不敢相信他还没吻你。天啊，我跟保罗约会第六次的时候，他都已经给我的两个胸起好名字了！……哦。我是不是说得太多了？
	\switchcolumn*
	\charactername{Ross:} Just a smidge.
	\switchcolumn
	\charactername{罗斯：}就一点点。
	\switchcolumn*
	\charactername{Phoebe:} David's like, y'know, Scientist Guy. He's very methodical.
	\switchcolumn
	\charactername{菲比：}大卫就是那种，你知道的，科学家型的人。他做事很有条理。
	\switchcolumn*
	\charactername{Monica:} I think it's romantic.
	\switchcolumn
	\charactername{莫妮卡：}我觉得这很浪漫。
	\switchcolumn*
	\charactername{Phoebe:} Me too! Oh! Did you ever see An Officer and a Gentleman?
	\switchcolumn
	\charactername{菲比：}我也觉得！哦！你们看过《军官与绅士》吗？
	\switchcolumn*
	\charactername{Rachel:} Yeah!
	\switchcolumn
	\charactername{瑞秋：}看过！
	\switchcolumn*
	\charactername{Phoebe:} Well, he's kinda like the guy I went to see that with. Except, except he-he's smarter, and gentler, and sweeter... I just- I just wanna be with him all the time. Day and night, and night and day... and special occasions...
	\switchcolumn
	\charactername{菲比：}他有点像跟我一起去看那部电影的人。不过，不过他更聪明、更温柔、更体贴……我就是-我就是想一直跟他待在一起。白天黑夜，黑夜白天……还有各种特殊的日子……
	\switchcolumn*
	\charactername{Chandler:} Wait a minute, wait a minute, I see where this is going, you're gonna ask him to New Year's, aren't you. You're gonna break the pact. She's gonna break the pact.
	\switchcolumn
	\charactername{钱德勒：}等一下，等一下，我知道你要干嘛了，你要邀请他去新年夜，对吧？你要破坏约定。她要破坏约定了。
	\switchcolumn*
	\charactername{Phoebe:} No, no, no, no, no, no. Yeah, could I just?
	\switchcolumn
	\charactername{菲比：}不，不，不，不，不，不。好吧，我能邀请他吗？
	\switchcolumn*
	\charactername{Chandler:} Yeah, 'cause I already asked Janice.
	\switchcolumn
	\charactername{钱德勒：}行啊，反正我已经邀请詹妮丝了。
	\switchcolumn*
	\charactername{Monica:} What?!
	\switchcolumn
	\charactername{莫妮卡：}什么？！
	\switchcolumn*
	\charactername{Ross:} C'mon, this was a pact! This was your pact!
	\switchcolumn
	\charactername{罗斯：}拜托，这是约定好的！这是你提出来的约定！
	\switchcolumn*
	\charactername{Chandler:} I snapped, okay? I couldn't handle the pressure and I snapped.
	\switchcolumn
	\charactername{钱德勒：}我崩溃了，好吧？我承受不了压力，崩溃了。
	\switchcolumn*
	\charactername{Monica:} Yeah, but Janice? That-that was like the worst breakup in history!
	\switchcolumn
	\charactername{莫妮卡：}可那是詹妮丝啊？那可是史上最糟糕的分手！
	\switchcolumn*
	\charactername{Chandler:} I'm not saying it was a good idea, I'm saying I snapped!
	\switchcolumn
	\charactername{钱德勒：}我没说这是个好主意，我是说我崩溃了！
	\switchcolumn*
	\sense{Joey enters, his shoes have bells on, which jingle as he walks. He is wearing a long coat.}
	\switchcolumn
	\sense{乔伊走进来，鞋子上挂着铃铛，走路时叮当作响。他穿着一件长外套}
	\switchcolumn*
	\charactername{Joey:} Hi. Hi, sorry I'm late.
	\switchcolumn
	\charactername{乔伊：}嗨。嗨，抱歉我来晚了。
	\switchcolumn*
	\ennotmain{He removes the coat to reveal an elf costume}
	\switchcolumn
	\notmain{他脱掉外套，露出精灵服装}
	\switchcolumn*
	\charactername{Chandler:} Too many jokes... must mock Joey!
	\switchcolumn
	\charactername{钱德勒：}笑点太多了……必须调侃乔伊！
	\switchcolumn*
	\charactername{Joey:} Nice shoes, huh? \ennotmain{He wiggles his foot and the bells tinkle}
	\switchcolumn
	\charactername{乔伊：}鞋子不错吧？\notmain{他晃了晃脚，铃铛叮当作响}
	\switchcolumn*
	\charactername{Chandler:} Aah, y'killing me!
	\switchcolumn
	\charactername{钱德勒：}啊，笑死我了！
	\switchcolumn*
	\ennotmain{Marcel knocks over some kitchen tools}
	\switchcolumn
	\notmain{马塞尔打翻了一些厨房用具}
	\switchcolumn*
	\charactername{Monica:} Ross! He's playing with my spatulas again!
	\switchcolumn
	\charactername{莫妮卡：}罗斯！它又在玩我的锅铲了！
	\switchcolumn*
	\charactername{Ross:} Okay, look, he's not gonna hurt them, right?
	\switchcolumn
	\charactername{罗斯：}好吧，它不会弄坏它们的，对吧？
	\switchcolumn*
	\charactername{Monica:} Do you always have to bring him here?
	\switchcolumn
	\charactername{莫妮卡：}你非得每次都把它带来吗？
	\switchcolumn*
	\charactername{Ross:} I didn't wanna leave him alone. Alright? We- we had our first fight this morning. I think it has to do with my working late. I said some things that I didn't mean, and he- he threw some faeces...
	\switchcolumn
	\charactername{罗斯：}我不想把它一个人留在家里。好吧？我们-我们今早第一次吵架了。我觉得是因为我加班晚归。我说了些不该说的话，然后它-它扔了些粪便……
	\switchcolumn*
	\charactername{Chandler:} Y'know, if you're gonna work late, I could look in on him for you.
	\switchcolumn
	\charactername{钱德勒：}如果你要加班，我可以帮你照看它。
	\switchcolumn*
	\charactername{Ross:} Oh, that'd be great! Okay, but if you do, make sure it seems like you're there to see him, okay, and you're not like doing it as a favour to me.
	\switchcolumn
	\charactername{罗斯：}哦，那太好了！不过如果你去的话，一定要让它觉得你是特意去看它的，而不是帮我的忙。
	\switchcolumn*
	\charactername{Chandler:} Okay, but if he asks, I'm not going to lie.
	\switchcolumn
	\charactername{钱德勒：}好吧，但如果它问起来，我可不会撒谎。
	\switchcolumn*
	\sense{Scene: Max and David's lab, David is explaining something to Phoebe with the aid of a whiteboard.}
	\switchcolumn
	\sense{场景：麦克斯和大卫的实验室，大卫借助白板给菲比解释事情}
	\switchcolumn*
	\charactername{David:} ...But, you can't actually test this theory, because today's particle accelerators are nowhere near powerful enough to simulate these conditions.
	\switchcolumn
	\charactername{大卫：}……但是，你实际上无法测试这个理论，因为现在的粒子加速器功率远远不够模拟这些条件。
	\switchcolumn*
	\charactername{Phoebe:} Okay, alright, I have a question, then.
	\switchcolumn
	\charactername{菲比：}好吧，那我有个问题。
	\switchcolumn*
	\charactername{David:} Yuh.
	\switchcolumn
	\charactername{大卫：}你说。
	\switchcolumn*
	\charactername{Phoebe:} Um, were you planning on kissing me ever?
	\switchcolumn
	\charactername{菲比：}嗯，你打算过要吻我吗？
	\switchcolumn*
	\charactername{David:} Uh, that's definitely a, uh, valid question. And, uh, the answer would be \ennotmain{Writes YES on the board} yes. Yes I was. But, see, I wanted it to be this phenomenal kiss that happened at this phenomenal moment, because, well, 'cause it's you.
	\switchcolumn
	\charactername{大卫：}呃，这绝对是个，呃，合理的问题。而且，呃，答案是\notmain{在白板上写下“是”}是的。我打算过。但是，你看，我想让它成为一个非凡的吻，发生在非凡的时刻，因为，嗯，因为是你。
	\switchcolumn*
	\charactername{Phoebe:} Sure.
	\switchcolumn
	\charactername{菲比：}好吧。
	\switchcolumn*
	\charactername{David:} Right. But, see, the longer I waited, the more phenomenal the kiss had to be, and now we've reached a place where it's just gotta be one of those things where I just like... sweep everything off the table and throw you down on it. And, uh, I'm not really a, uh, sweeping sorta fella.
	\switchcolumn
	\charactername{大卫：}对。但是，你看，我等得越久，这个吻就必须越非凡，现在已经到了那种地步，我得……把桌上所有东西都扫掉，然后把你按在桌上吻。而且，呃，我其实不是那种，呃，会“横扫桌面”的人。
	\switchcolumn*
	\charactername{Phoebe:} Oh, David, I, I think you are a sweeping sorta fella. I mean, you're a sweeper! ...trapped inside a physicist's body.
	\switchcolumn
	\charactername{菲比：}哦，大卫，我觉得你就是那种会“横扫桌面”的人。我是说，你骨子里就是个“横扫型”的！……只是被困在了物理学家的身体里。
	\switchcolumn*
	\charactername{David:} Rrrreally.
	\switchcolumn
	\charactername{大卫：}真-真的吗。
	\switchcolumn*
	\charactername{Phoebe:} Oh, yeah, oh, I'm sure of it. You should just do it, just sweep and throw me.
	\switchcolumn
	\charactername{菲比：}哦，是啊，我确定。你就这么做吧，扫掉东西，把我按在桌上。
	\switchcolumn*
	\charactername{David:} ...Now? Now?
	\switchcolumn
	\charactername{大卫：}……现在？就现在？
	\switchcolumn*
	\charactername{Phoebe:} Oh yeah, right now.
	\switchcolumn
	\charactername{菲比：}哦对啊，就现在。
	\switchcolumn*
	\charactername{David:} Okay, okay, okay. \ennotmain{Gets ready to sweep, and then picks up a laptop computer} Y'know what, this was just really expensive. \ennotmain{Puts it down elsewhere. Then picks up a microscope} And I'll take- this was a gift. \ennotmain{Moves it}
	\switchcolumn
	\charactername{大卫：}好，好，好。\notmain{准备扫东西，然后拿起一台笔记本电脑}这个太贵了。\notmain{把它放到别的地方。然后拿起一台显微镜}这个是礼物，我得收好。\notmain{移开它}
	\switchcolumn*
	\charactername{Phoebe:} Okay, now you're just kinda tidying.
	\switchcolumn
	\charactername{菲比：}好吧，你现在只是在整理而已。
	\switchcolumn*
	\charactername{David:} Okay, what the hell, what the hell. \ennotmain{Sweeps the remaining papers off the desk and grabs Phoebe} You want me to actually throw you or you-you wanna just hop?
	\switchcolumn
	\charactername{大卫：}好吧，管他呢，管他呢。\notmain{把桌上剩下的纸扫掉，抓住菲比}你想让我真的把你按下去，还是你自己跳上去？
	\switchcolumn*
	\charactername{Phoebe:} I can hop. \ennotmain{She hops onto the table}
	\switchcolumn
	\charactername{菲比：}我自己跳吧。\notmain{她跳到桌上}
	\switchcolumn*
	\ennotmain{They kiss, finally}
	\switchcolumn
	\notmain{他们终于吻在了一起}
	\switchcolumn*
	\sense{Scene: Central Perk, everyone is there.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，众人都在}
	\switchcolumn*
	\charactername{Ross:} So tell me something. What does the phrase 'no date pact' mean to you?
	\switchcolumn
	\charactername{罗斯：}跟我说说。“不约会约定”这个短语对你来说是什么意思？
	\switchcolumn*
	\charactername{Monica:} I'm sorry, okay. It's just that Chandler has somebody, and Phoebe has somebody- I thought I'd ask Fun Bobby.
	\switchcolumn
	\charactername{莫妮卡：}对不起，好吧。只是钱德勒有伴了，菲比也有伴了——我想我可以邀请欢乐波比\notmain{莫妮卡的前男友}。
	\switchcolumn*
	\charactername{Chandler:} Fun Bobby? Your ex-boyfriend Fun Bobby?
	\switchcolumn
	\charactername{钱德勒：}欢乐波比？你的前男友欢乐波比？
	\switchcolumn*
	\charactername{Monica:} Yeah.
	\switchcolumn
	\charactername{莫妮卡：}对啊。
	\switchcolumn*
	\charactername{Joey:} You know more than one Fun Bobby?
	\switchcolumn
	\charactername{乔伊：}你认识不止一个欢乐波比？
	\switchcolumn*
	\charactername{Chandler:} I happen to know a Fun Bob.
	\switchcolumn
	\charactername{钱德勒：}我倒是认识一个欢乐鲍勃。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{Brings Joey a mug of coffee} Okay, here we go...
	\switchcolumn
	\charactername{瑞秋：}\notmain{给乔伊端来一杯咖啡}好了，给你……
	\switchcolumn*
	\charactername{Joey:} Ooh ooh ooh ooh, there's no room for milk!
	\switchcolumn
	\charactername{乔伊：}哦哦哦哦，没地方加牛奶了！
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{Glances at Joey and then sips his coffee} There. Now there is.
	\switchcolumn
	\charactername{瑞秋：}\notmain{看了乔伊一眼，然后喝了一口他的咖啡}现在有了。
	\switchcolumn*
	\charactername{Ross:} Okay, so on our no-date evening, three of you now have dates.
	\switchcolumn
	\charactername{罗斯：}好吧，我们的“不约会之夜”，现在已经有三个人有伴了。
	\switchcolumn*
	\charactername{Joey:} Uh, four.
	\switchcolumn
	\charactername{乔伊：}呃，四个。
	\switchcolumn*
	\charactername{Ross:} Four.
	\switchcolumn
	\charactername{罗斯：}四个。
	\switchcolumn*
	\charactername{Rachel:} Five.
	\switchcolumn
	\charactername{瑞秋：}五个。
	\switchcolumn*
	\charactername{Ross:} Five. \ennotmain{Buries his head in his hands}
	\switchcolumn
	\charactername{罗斯：}五个。\notmain{双手抱头}
	\switchcolumn*
	\charactername{Rachel:} Sorry. Paolo's catching an earlier flight.
	\switchcolumn
	\charactername{瑞秋：}对不起。保罗要赶早一点的航班。
	\switchcolumn*
	\charactername{Joey:} Yeah, and I met this really hot single mom at the store. What's an elf to do?
	\switchcolumn
	\charactername{乔伊：}是啊，我在商店遇到一个超辣的单身妈妈。一个精灵能怎么办呢？
	\switchcolumn*
	\charactername{Ross:} Okay, so I'm gonna be the only one standing there alone when the ball drops?
	\switchcolumn
	\charactername{罗斯：}好吧，球落下的时候，我会是唯一一个独自站着的人？
	\switchcolumn*
	\charactername{Rachel:} Oh, c'mon. We'll have, we'll have a big party, and no-one'll know who's with who.
	\switchcolumn
	\charactername{瑞秋：}哦，拜托。我们会办个大派对，没人会知道谁跟谁是一对。
	\switchcolumn*
	\charactername{Ross:} Hey, y'know, this is so not what I needed right now.
	\switchcolumn
	\charactername{罗斯：}嘿，你知道吗，我现在最不需要的就是这个。
	\switchcolumn*
	\charactername{Monica:} What's the matter?
	\switchcolumn
	\charactername{莫妮卡：}怎么了？
	\switchcolumn*
	\charactername{Ross:} Oh, it's-it's Marcel. He keeps shutting me out, y'know? He's walking around all the time dragging his hands...
	\switchcolumn
	\charactername{罗斯：}哦，是马塞尔。它总是把我拒之门外，你知道吗？它整天耷拉着爪子走来走去……
	\switchcolumn*
	\charactername{Chandler:} That's so weird, I had such a blast with him the other night.
	\switchcolumn
	\charactername{钱德勒：}太奇怪了，前几天晚上我跟它玩得可开心了。
	\switchcolumn*
	\charactername{Ross:} Really.
	\switchcolumn
	\charactername{罗斯：}真的吗。
	\switchcolumn*
	\charactername{Chandler:} Yeah, we played, we watched TV.. that juggling thing is amazing.
	\switchcolumn
	\charactername{钱德勒：}是啊，我们一起玩，一起看电视……它抛东西的绝技太厉害了。
	\switchcolumn*
	\charactername{Ross:} What, uh... what juggling thing?
	\switchcolumn
	\charactername{罗斯：}什么，呃……什么抛东西的绝技？
	\switchcolumn*
	\charactername{Chandler:} With the balled-up socks? I figured you taught him that.
	\switchcolumn
	\charactername{钱德勒：}用揉成团的袜子抛接啊？我以为是你教它的。
	\switchcolumn*
	\charactername{Ross:} No.
	\switchcolumn
	\charactername{罗斯：}不是我。
	\switchcolumn*
	\charactername{Chandler:} Y'know, it wasn't that big a deal. He just balled up socks... and a melon...
	\switchcolumn
	\charactername{钱德勒：}其实也没什么大不了的。它就是抛揉成团的袜子……还有一个甜瓜……
	\switchcolumn*
	\ennotmain{Max runs in}
	\switchcolumn
	\notmain{麦克斯跑进来}
	\switchcolumn*
	\charactername{Max:} Phoebe. Hi.
	\switchcolumn
	\charactername{麦克斯：}菲比。嗨。
	\switchcolumn*
	\charactername{Phoebe:} Oh, hi Max! Hey, do you know everybody?
	\switchcolumn
	\charactername{菲比：}哦，嗨麦克斯！嘿，你认识大家吗？
	\switchcolumn*
	\charactername{Max:} No. Have you seen David?
	\switchcolumn
	\charactername{麦克斯：}不认识。你看到大卫了吗？
	\switchcolumn*
	\charactername{Phoebe:} No, no, he hasn't been around.
	\switchcolumn
	\charactername{菲比：}没有，他没来过。
	\switchcolumn*
	\charactername{Max:} Well, if you see him, tell him to pack his bags. We are going to Minsk.
	\switchcolumn
	\charactername{麦克斯：}如果你看到他，告诉他收拾行李。我们要去明斯克。
	\switchcolumn*
	\charactername{Phoebe:} Minsk?
	\switchcolumn
	\charactername{菲比：}明斯克？
	\switchcolumn*
	\charactername{Max:} Minsk. It's in Russia.
	\switchcolumn
	\charactername{麦克斯：}明斯克。在俄罗斯。
	\switchcolumn*
	\charactername{Phoebe:} I know where Minsk is.
	\switchcolumn
	\charactername{菲比：}我知道明斯克在哪儿。
	\switchcolumn*
	\charactername{Max:} We got the grant. Three years, all expenses paid.
	\switchcolumn
	\charactername{麦克斯：}我们拿到资助了。三年，所有费用都包了。
	\switchcolumn*
	\charactername{Phoebe:} So when, when do you leave?
	\switchcolumn
	\charactername{菲比：}那你们什么时候走？
	\switchcolumn*
	\charactername{Max:} January first.
	\switchcolumn
	\charactername{麦克斯：}一月一号。
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Max and David's lab, they are working. Phoebe knocks on the door}
	\switchcolumn
	\sense{场景：麦克斯和大卫的实验室，他们正在工作。菲比敲门}
	\switchcolumn*
	\charactername{Phoebe:} Hello?
	\switchcolumn
	\charactername{菲比：}有人吗？
	\switchcolumn*
	\charactername{David:} Hey!
	\switchcolumn
	\charactername{大卫：}嘿！
	\switchcolumn*
	\charactername{Phoebe:} Hi.
	\switchcolumn
	\charactername{菲比：}嗨。
	\switchcolumn*
	\charactername{David:} Hi! \ennotmain{Kisses her} What-what're you doing here?
	\switchcolumn
	\charactername{大卫：}嗨！\notmain{吻她}你-你怎么来了？
	\switchcolumn*
	\charactername{Phoebe:} Um, well, Max told me about Minsk, so \ennotmain{Puts on a fake cheery voice} congratulations! This is so exciting!
	\switchcolumn
	\charactername{菲比：}嗯，麦克斯跟我说了明斯克的事，所以\notmain{假装高兴地说}恭喜你们！太令人兴奋了！
	\switchcolumn*
	\charactername{Max:} It'd be even more exciting if we were going.
	\switchcolumn
	\charactername{麦克斯：}如果我们俩都去的话，会更令人兴奋。
	\switchcolumn*
	\charactername{Phoebe:} Oh, you're not going? \ennotmain{Fake disappointed voice} Oh, why?
	\switchcolumn
	\charactername{菲比：}哦，你不去吗？\notmain{假装失望地说}哦，为什么？
	\switchcolumn*
	\charactername{Max:} Tell her, David. 'I don't wanna go to Minsk and work with Lifson and Yamaguchi and Flench, on nonononononono. I wanna stay here and make out with my girlfriend!!' \ennotmain{Storms out}
	\switchcolumn
	\charactername{麦克斯：}跟她说啊，大卫。“我不想去明斯克跟利夫森、山口和弗伦奇一起工作，不，不，不。我想留在这里跟我的女朋友亲热！！”\notmain{怒气冲冲地离开}
	\switchcolumn*
	\charactername{David:} Thank you, Max. Thank you.
	\switchcolumn
	\charactername{大卫：}谢谢你，麦克斯。太谢谢你了。
	\switchcolumn*
	\charactername{Phoebe:} So-so you're really not going?
	\switchcolumn
	\charactername{菲比：}所以-所以你真的不去？
	\switchcolumn*
	\charactername{David:} I don't know. I don't know what I'm gonna do. I just- you decide.
	\switchcolumn
	\charactername{大卫：}我不知道。我不知道该怎么办。我只是-你来决定。
	\switchcolumn*
	\charactername{Phoebe:} Oh don't do that.
	\switchcolumn
	\charactername{菲比：}哦，别这样。
	\switchcolumn*
	\charactername{David:} Please.
	\switchcolumn
	\charactername{大卫：}拜托。
	\switchcolumn*
	\charactername{Phoebe:} Oh no no.
	\switchcolumn
	\charactername{菲比：}哦，不行不行。
	\switchcolumn*
	\charactername{David:} No, but I'm asking-
	\switchcolumn
	\charactername{大卫：}不，我在求你——
	\switchcolumn*
	\charactername{Phoebe:} Oh, but I can't do that-
	\switchcolumn
	\charactername{菲比：}哦，我不能替你决定——
	\switchcolumn*
	\charactername{David:} No, but I can't-
	\switchcolumn
	\charactername{大卫：}不，我无法——
	\switchcolumn*
	\charactername{Phoebe:} It's your thing, and-
	\switchcolumn
	\charactername{菲比：}这是你的事，而且——
	\switchcolumn*
	\charactername{David:} -make the decision-
	\switchcolumn
	\charactername{大卫：}——无法自己做决定——
	\switchcolumn*
	\charactername{Phoebe:} Okay, um, stay.
	\switchcolumn
	\charactername{菲比：}好吧，嗯，留下来。
	\switchcolumn*
	\charactername{David:} Stay.
	\switchcolumn
	\charactername{大卫：}留下来。
	\switchcolumn*
	\charactername{Phoebe:} Stay.
	\switchcolumn
	\charactername{菲比：}留下来。
	\switchcolumn*
	\ennotmain{He thinks for a moment and sweeps the stuff off the table}
	\switchcolumn
	\notmain{他想了一会儿，然后把桌上的东西扫掉}
	\switchcolumn*
	\charactername{Phoebe:} Getting so good at that! \ennotmain{She hops on}
	\switchcolumn
	\charactername{菲比：}越来越熟练了！\notmain{她跳上桌子}
	\switchcolumn*
	\charactername{David:} It was Max's stuff. \ennotmain{They kiss}
	\switchcolumn
	\charactername{大卫：}这些是麦克斯的东西。\notmain{他们接吻}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the party has started.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，派对已经开始}
	\switchcolumn*
	\charactername{Janice:} I love this artichoke thing! Oh, don't tell me what's in it, the diet starts tomorrow! \ennotmain{Laughs her Janice laugh}
	\switchcolumn
	\charactername{詹妮丝：}我太爱这个洋蓟小吃了！哦，别告诉我里面有什么，减肥从明天开始！\notmain{发出詹妮丝标志性的笑声}
	\switchcolumn*
	\charactername{Chandler:} You remember Janice.
	\switchcolumn
	\charactername{钱德勒：}你们还记得詹妮丝吧。
	\switchcolumn*
	\charactername{Monica:} Vividly.
	\switchcolumn
	\charactername{莫妮卡：}印象深刻。
	\switchcolumn*
	\ennotmain{Someone knocks on the door; Monica gets it}
	\switchcolumn
	\notmain{有人敲门；莫妮卡去开门}
	\switchcolumn*
	\charactername{Monica:} Hi.
	\switchcolumn
	\charactername{莫妮卡：}嗨。
	\switchcolumn*
	\charactername{Sandy:} Hi, I'm Sandy.
	\switchcolumn
	\charactername{桑迪：}嗨，我是桑迪。
	\switchcolumn*
	\charactername{Joey:} Sandy! Hi! C'mon in! \ennotmain{She enters, followed by a young boy and a younger girl}...You brought your kids.
	\switchcolumn
	\charactername{乔伊：}桑迪！嗨！进来吧！\notmain{她走进来，后面跟着一个小男孩和一个小女孩}……你把孩子带来了。
	\switchcolumn*
	\charactername{Sandy:} Yeah. That's okay, right?
	\switchcolumn
	\charactername{桑迪：}是啊。可以吧？
	\switchcolumn*
	\ennotmain{Joey and Monica look at each other and shrug. Ross enters with Marcel on his shoulder}
	\switchcolumn
	\notmain{乔伊和莫妮卡对视一眼，耸了耸肩。罗斯肩膀上扛着马塞尔走进来}
	\switchcolumn*
	\charactername{Ross:} Par-tay!
	\switchcolumn
	\charactername{罗斯：}派对开始啦！
	\switchcolumn*
	\charactername{Monica:} That thing is not coming in here.
	\switchcolumn
	\charactername{莫妮卡：}那东西不能进来。
	\switchcolumn*
	\charactername{Ross:} 'That thing'? This is how you greet guests at a party? Let me ask you something, if I showed up here with my new girlfriend, she wouldn't be welcome in your home?
	\switchcolumn
	\charactername{罗斯：}“那东西”？你派对上就是这么招待客人的？我问问你，如果我带我的新女朋友来，她也不受欢迎吗？
	\switchcolumn*
	\charactername{Monica:} I'm guessing your new girlfriend wouldn't urinate on my coffee table.
	\switchcolumn
	\charactername{莫妮卡：}我猜你的新女朋友不会在我的咖啡桌上撒尿。
	\switchcolumn*
	\charactername{Ross:} Okay. He was more embarrassed about that than anyone. Okay? And for him to have the courage to walk back in here like nothing happened...
	\switchcolumn
	\charactername{罗斯：}好吧。他自己比谁都尴尬。好吧？他能有勇气像什么都没发生过一样走进来……
	\switchcolumn*
	\charactername{Monica:} Alright. Just keep him away from me.
	\switchcolumn
	\charactername{莫妮卡：}好吧。别让它靠近我就行。
	\switchcolumn*
	\charactername{Ross:} Thank you. \ennotmain{She walks off} C'mon, Marcel, whaddya say you and I do a little mingling? \ennotmain{Marcel runs off} Alright, I'll, uh... catch up with you later.
	\switchcolumn
	\charactername{罗斯：}谢谢。\notmain{她走开了}来吧，马塞尔，我们去跟大家打个招呼怎么样？\notmain{马塞尔跑开了}好吧，我稍后……再找你。
	\switchcolumn*
	\ennotmain{The door opens. Rachel is standing there. Her coat is muddy and torn, her hair is dishevelled and her face is bruised. Everyone turns to look}
	\switchcolumn
	\notmain{门开了。瑞秋站在门口。她的外套又脏又破，头发凌乱，脸上还有瘀伤。所有人都转头看她}
	\switchcolumn*
	\charactername{Monica:} Oh my gosh! Rachel, honey.. are you okay? Where-where's Paolo?
	\switchcolumn
	\charactername{莫妮卡：}天啊！瑞秋，亲爱的……你还好吗？保-保罗呢？
	\switchcolumn*
	\charactername{Rachel:} Rome. Jerk missed his flight.
	\switchcolumn
	\charactername{瑞秋：}罗马。那个混蛋误了航班。
	\switchcolumn*
	\charactername{Phoebe:} And then... your face is bloated?
	\switchcolumn
	\charactername{菲比：}那你的脸……是肿了吗？
	\switchcolumn*
	\charactername{Rachel:} No. Okay. I was at the airport, getting into a cab, when this woman- this blonde planet with a pocketbook- starts yelling at me. Something about how it was her cab first. And then the next thing I know she just starts- starts pulling me out by my hair! So I'm blowing my attack whistle thingy and three more cabs show up, and as I'm going to get into a cab she tackles me. And I hit my head on the kerb and cut my lip on my whistle...oh...everybody having fun at the party? \ennotmain{To Monica} Are people eating my dip?
	\switchcolumn
	\charactername{瑞秋：}不是。好吧。我在机场正要上出租车，有个女人——一个拿着手提包的金发大块头——开始对我大喊大叫。说那辆出租车是她先拦到的。然后她突然开始——开始扯我的头发！我就吹我的防狼哨，又过来三辆出租车，我正要上其中一辆，她把我扑倒了。我的头撞到了路缘石，嘴唇被哨子划破了……哦……大家在派对上玩得开心吗？\notmain{对莫妮卡}有人吃我做的蘸酱吗？
	\switchcolumn*
	\sense{Time lapse. Monica and Rachel, fixed up somewhat, emerge from a bedroom}
	\switchcolumn
	\sense{时间快进。莫妮卡和瑞秋稍微整理了一下，从卧室里出来}
	\switchcolumn*
	\charactername{Sandy:} Y'know, when I saw you at the store last week, it was probably the first time I ever mentally undressed an elf.
	\switchcolumn
	\charactername{桑迪：}你知道吗，上周在商店看到你的时候，可能是我第一次在脑子里把一个精灵扒光衣服。
	\switchcolumn*
	\charactername{Joey:} Wow, that's, uh, dirty.
	\switchcolumn
	\charactername{乔伊：}哇，这，呃，有点污。
	\switchcolumn*
	\charactername{Sandy:} Yeah.
	\switchcolumn
	\charactername{桑迪：}是啊。
	\switchcolumn*
	\ennotmain{They almost kiss and then Joey realises her kids are staring at them}
	\switchcolumn
	\notmain{他们差点吻上，然后乔伊意识到她的孩子在盯着他们看}
	\switchcolumn*
	\charactername{Joey:} Hey, kids...
	\switchcolumn
	\charactername{乔伊：}嘿，孩子们……
	\switchcolumn*
	\charactername{Ross:} \ennotmain{Watching Marcel play with Phoebe. To Chandler} Look at him. I'm not saying he has to spend the whole evening with me, but at least check in.
	\switchcolumn
	\charactername{罗斯：}\notmain{看着马塞尔和菲比玩。对钱德勒说}你看它。我不是说它一整晚都得陪着我，但至少也该跟我打个招呼吧。
	\switchcolumn*
	\charactername{Janice:} \ennotmain{Startles them} There you are! Haaah, you got away from me!
	\switchcolumn
	\charactername{詹妮丝：}\notmain{突然出现}你在这儿！哈，你居然跑掉了！
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Imitating} But you found me!
	\switchcolumn
	\charactername{钱德勒：}\notmain{模仿她的语气}但你找到我了！
	\switchcolumn*
	\charactername{Janice:} Here, Ross, take our picture. \ennotmain{Hands him a camera and he starts snapping} Smile! You're on Janice Camera!
	\switchcolumn
	\charactername{詹妮丝：}来，罗斯，给我们拍张照。\notmain{递给她一部相机，罗斯开始拍照}笑一个！你在詹妮丝相机里哦！
	\switchcolumn*
	\charactername{Chandler:} Kill me. Kill me now.
	\switchcolumn
	\charactername{钱德勒：}杀了我吧。现在就杀了我。
	\switchcolumn*
	\ennotmain{Someone else knocks on the door. Monica looks through the spyhole}
	\switchcolumn
	\notmain{又有人敲门。莫妮卡透过猫眼往外看}
	\switchcolumn*
	\charactername{Monica:} Hey everybody! It's Fun Bobby!
	\switchcolumn
	\charactername{莫妮卡：}嘿，大家！是欢乐波比！
	\switchcolumn*
	\ennotmain{Everyone cheers. Monica opens the door. Bobby is obviously very depressed}
	\switchcolumn
	\notmain{众人欢呼。莫妮卡打开门。波比显然非常沮丧}
	\switchcolumn*
	\charactername{Fun Bobby:} Hey, sorry I'm late. But my, uh, grandfather, he- died about two hours ago. But I-I-I couldn't get a flight out 'til tomorrow, so here I am!
	\switchcolumn
	\charactername{欢乐波比：}嘿，抱歉我来晚了。我的，呃，爷爷，他-大约两小时前去世了。但我-我-我明天才能订到航班离开，所以我就来了！
	\switchcolumn*
	\charactername{Joey:} \ennotmain{Approaching} Hey Fun Bobby! Whoah! Who died?
	\switchcolumn
	\charactername{乔伊：}\notmain{走过去}嘿，欢乐波比！哇哦！谁去世了？
	\switchcolumn*
	\ennotmain{Monica gestures wildly behind Fun Bobby's back}
	\switchcolumn
	\notmain{莫妮卡在欢乐波比身后疯狂使眼色}
	\switchcolumn*
	\sense{Time lapse. Bobby is talking about his grandfather. Everyone else is virtually in tears}
	\switchcolumn
	\sense{时间快进。波比在谈论他的爷爷。其他人几乎都要哭了}
	\switchcolumn*
	\charactername{Fun Bobby:} It's gonna be an open casket, y'know, so at least I'll- I get to see him again.
	\switchcolumn
	\charactername{欢乐波比：}会有一个开放式棺材的葬礼，所以至少我能-能再见到他一面。
	\switchcolumn*
	\charactername{Janice:} \ennotmain{Ross is still taking their photo} Oh, I'm gonna blow this one up, and I'm gonna write 'Reunited' in glitter.
	\switchcolumn
	\charactername{詹妮丝：}\notmain{罗斯还在给他们拍照}哦，我要把这张照片放大，然后用闪光笔写上“破镜重圆”。
	\switchcolumn*
	\charactername{Chandler:} Alright, Janice, that's it! Janice... Janice... Hey, Janice, when I invited you to this party I didn't necessarily think that it meant that we-
	\switchcolumn
	\charactername{钱德勒：}好了，詹妮丝，够了！詹妮丝……詹妮丝……嘿，詹妮丝，我邀请你来参加派对，并不意味着我们——
	\switchcolumn*
	\charactername{Janice:} Oh, no. Oh, no.
	\switchcolumn
	\charactername{詹妮丝：}哦，不。哦，不。
	\switchcolumn*
	\charactername{Chandler:} I'm sorry you misunderstood...
	\switchcolumn
	\charactername{钱德勒：}很抱歉你误会了……
	\switchcolumn*
	\charactername{Janice:} Oh my God. You listen to me, Chandler, you listen to me. One of these times is just gonna be your last chance with me. \ennotmain{She runs off}
	\switchcolumn
	\charactername{詹妮丝：}天啊。你听我说，钱德勒，你听我说。总有一天，这会是你最后一次拥有我的机会。\notmain{她跑开了}
	\switchcolumn*
	\ennotmain{Ross is still taking photos}
	\switchcolumn
	\notmain{罗斯还在拍照}
	\switchcolumn*
	\charactername{Chandler:} Oh, will you give me the thing. \ennotmain{Snatches the camera}
	\switchcolumn
	\charactername{钱德勒：}哦，把那玩意儿给我。\notmain{抢过相机}
	\switchcolumn*
	\ennotmain{David is feeding Phoebe popcorn. Max walks up}
	\switchcolumn
	\notmain{大卫在给菲比喂爆米花。麦克斯走过来}
	\switchcolumn*
	\charactername{Phoebe:} Hi, Max!
	\switchcolumn
	\charactername{菲比：}嗨，麦克斯！
	\switchcolumn*
	\charactername{Max:} Yoko. \ennotmain{To David} I've decided to go to Minsk without you.
	\switchcolumn
	\charactername{麦克斯：}洋子\notmain{指菲比像拆散披头士的洋子}。\notmain{对大卫说}我决定一个人去明斯克了。
	\switchcolumn*
	\charactername{David:} Wow.
	\switchcolumn
	\charactername{大卫：}哇。
	\switchcolumn*
	\charactername{Max:} It won't be the same- but it'll still be Minsk. Happy New Year.\ennotmain{Walks off}
	\switchcolumn
	\charactername{麦克斯：}虽然会不一样——但那依然是明斯克。新年快乐。\notmain{走开了}
	\switchcolumn*
	\charactername{Phoebe:} Are you alright?
	\switchcolumn
	\charactername{菲比：}你还好吗？
	\switchcolumn*
	\charactername{David:} Yeah, I'm fine, I'm fine.
	\switchcolumn
	\charactername{大卫：}嗯，我没事，我没事。
	\switchcolumn*
	\ennotmain{Phoebe leads David into a bedroom}
	\switchcolumn
	\notmain{菲比把大卫带进卧室}
	\switchcolumn*
	\charactername{Phoebe:} You're going to Minsk.
	\switchcolumn
	\charactername{菲比：}你要去明斯克。
	\switchcolumn*
	\charactername{David:} No, I'm... not going to Minsk.
	\switchcolumn
	\charactername{大卫：}不，我……不去明斯克。
	\switchcolumn*
	\charactername{Phoebe:} Oh, you are so going to Minsk. You belong in Minsk. You can't stay here just 'cause of me.
	\switchcolumn
	\charactername{菲比：}哦，你必须去明斯克。你属于明斯克。你不能因为我就留在这里。
	\switchcolumn*
	\charactername{David:} Yes I can. Because if I go it means I have to break up with you, and I can't break up with you.
	\switchcolumn
	\charactername{大卫：}我可以。因为如果我去了，就意味着我必须跟你分手，而我不能跟你分手。
	\switchcolumn*
	\charactername{Phoebe:} Oh yes, yes, yes you can. Just say, um, 'Phoebe, my work is my life and that's what I have to do right now'. And I say 'your work?! Your work?! How can you say that?!'. And then you say, um, 'it's tearing me apart, but I have no choice. Can't you understand that?'. And I say \ennotmain{Hits him} 'no! No! I can't understand that!'.
	\switchcolumn
	\charactername{菲比：}哦，不，你可以的。你就说，嗯，“菲比，我的工作就是我的生命，这是我现在必须做的事”。然后我说“你的工作？！你的工作？！你怎么能这么说？！”。然后你说，嗯，“这让我心如刀割，但我别无选择。你不能理解吗？”。然后我说\notmain{打他一下}“不！不！我不能理解！”。
	\switchcolumn*
	\charactername{David:} Uh, ow.
	\switchcolumn
	\charactername{大卫：}呃，哎哟。
	\switchcolumn*
	\charactername{Phoebe:} Ooh, sorry. Um, and, and then you put your arms around me. And then you put your arms around me. \ennotmain{He does so} And, um, and then you tell me that you love me and you'll never forget me.
	\switchcolumn
	\charactername{菲比：}哦，对不起。嗯，然后你抱住我。你抱住我。\notmain{他照做了}然后，嗯，你告诉我你爱我，永远不会忘记我。
	\switchcolumn*
	\charactername{David:} I'll never forget you.
	\switchcolumn
	\charactername{大卫：}我永远不会忘记你。
	\switchcolumn*
	\charactername{Phoebe:} And then you say that it's almost midnight and you have to go because you don't wanna start the new year with me if you can't finish it. \ennotmain{They kiss} I'm gonna miss you. You scientist guy.
	\switchcolumn
	\charactername{菲比：}然后你说快到午夜了，你必须走了，因为如果你不能陪我过完这一年，就不想跟我一起开始新的一年。\notmain{他们接吻}我会想你的。你这个科学家小子。
	\switchcolumn*
	\charactername{Dick Clark:} \ennotmain{on TV} Hi, this is Dick Clark, live in Times Square. We're in a virtual snowstorm of confetti here in Times Square...
	\switchcolumn
	\charactername{迪克·克拉克：}\notmain{电视上}嗨，我是迪克·克拉克，在时代广场现场直播。时代广场现在简直是五彩纸屑的暴风雪……
	\switchcolumn*
	\ennotmain{Joey puts a blanket over Sandy's kids}
	\switchcolumn
	\notmain{乔伊给桑迪的孩子盖上毯子}
	\switchcolumn*
	\charactername{Joey:} There y'go, kids.
	\switchcolumn
	\charactername{乔伊：}好了，孩子们。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{To a woman who he has clearly just met} And then the peacock bit me. \ennotmain{Laughs} Please kiss me at midnight. \ennotmain{She leaves}
	\switchcolumn
	\charactername{钱德勒：}\notmain{对一个显然刚认识的女人说}然后那只孔雀咬了我。\notmain{笑}午夜的时候吻我一下吧。\notmain{她走开了}
	\switchcolumn*
	\charactername{Joey:} You seen Sandy?
	\switchcolumn
	\charactername{乔伊：}你看到桑迪了吗？
	\switchcolumn*
	\charactername{Chandler:} Ooh. Uh, I don't know how to tell you this, but she's in Monica's bedroom, getting it on with Max, that scientist geek. Ooh, look at that, I did know how to tell you.
	\switchcolumn
	\charactername{钱德勒：}哦。呃，我不知道该怎么跟你说，但她在莫妮卡的卧室里，跟那个科学怪咖麦克斯搞在一起了。哦，你看，我还是知道怎么跟你说的。
	\switchcolumn*
	\charactername{Rachel:} Vrrbddy, the bll is drrbing.
	\switchcolumn
	\charactername{瑞秋：}大-大家，球-球要落-落下了。\notmain{说话含糊，因为嘴唇受伤}
	\switchcolumn*
	\charactername{All:} \ennotmain{in the kitchen} What?
	\switchcolumn
	\charactername{众人：}\notmain{在厨房}什么？
	\switchcolumn*
	\charactername{Rachel:} The bll is drrbing!
	\switchcolumn
	\charactername{瑞秋：}球-球要落-落下了！
	\switchcolumn*
	\charactername{Dick Clark:} \ennotmain{on TV} In twenty seconds it'll be midnight...
	\switchcolumn
	\charactername{迪克·克拉克：}\notmain{电视上}还有二十秒就到午夜了……
	\switchcolumn*
	\charactername{Chandler:} And the moment of joy is upon us.
	\switchcolumn
	\charactername{钱德勒：}欢乐时刻即将到来。
	\switchcolumn*
	\charactername{Joey:} Looks like that no date pact thing worked out.
	\switchcolumn
	\charactername{乔伊：}看来那个“不约会约定”还挺成功的嘛。
	\switchcolumn*
	\charactername{Phoebe:} Everybody looks so happy. I hate that.
	\switchcolumn
	\charactername{菲比：}大家看起来都好开心。我讨厌这样。
	\switchcolumn*
	\charactername{Monica:} Not everybody's happy. Hey Bobby!
	\switchcolumn
	\charactername{莫妮卡：}不是所有人都开心。嘿，波比！
	\switchcolumn*
	\ennotmain{Bobby waves and then bursts into tears. Midnight comes and everyone at the party except for the gang cheers and kisses}
	\switchcolumn
	\notmain{波比挥了挥手，然后突然哭了起来。午夜到来，派对上除了六人组之外的所有人都欢呼着接吻}
	\switchcolumn*
	\charactername{Chandler:} Y'know, I uh.. just thought I'd throw this out here. I'm no math whiz, but I do believe there are three girls and three guys right here. \ennotmain{Makes kiss noise}
	\switchcolumn
	\charactername{钱德勒：}你知道吗，我呃……我只是想说。我虽然不是数学天才，但我确实觉得这里正好有三个女生和三个男生。\notmain{发出亲吻的声音}
	\switchcolumn*
	\charactername{Phoebe:} I dunno. I don't feel like kissing anyone tonight.
	\switchcolumn
	\charactername{菲比：}我不知道。我今晚不想吻任何人。
	\switchcolumn*
	\charactername{Rachel:} I can't kiss anyone.
	\switchcolumn
	\charactername{瑞秋：}我不能吻任何人\notmain{嘴唇受伤}。
	\switchcolumn*
	\charactername{Monica:} So I'm kissing everyone?
	\switchcolumn
	\charactername{莫妮卡：}所以我要吻所有人？
	\switchcolumn*
	\charactername{Joey:} Nonono, you can't kiss Ross, that's your brother.
	\switchcolumn
	\charactername{乔伊：}不不不，你不能吻罗斯，那是你哥哥。
	\switchcolumn*
	\charactername{Ross:} Perfect. Perfect. So now everybody's getting kissed but me.
	\switchcolumn
	\charactername{罗斯：}太好了。太好了。现在所有人都有人吻，就我没有。
	\switchcolumn*
	\charactername{Chandler:} Alright, somebody kiss me. Somebody kiss me, it's midnight! Somebody kiss me!
	\switchcolumn
	\charactername{钱德勒：}好了，谁来吻我一下。谁来吻我一下，午夜了！谁来吻我一下！
	\switchcolumn*
	\charactername{Joey:} Alrightalrightalright. \ennotmain{Kisses him. Ross takes a photo} There.
	\switchcolumn
	\charactername{乔伊：}好了好了好了。\notmain{吻了他一下。罗斯拍下照片}好了。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, time lapse.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，时间快进}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{Watching Marcel and talking to Rachel} I wanted this to work so much. I mean I'm still in there, changing his diapers, pickin' his fleas... but he's just phoning it in. Just so hard to accept the fact that something you love so much doesn't love you back.
	\switchcolumn
	\charactername{罗斯：}\notmain{看着马塞尔，对瑞秋说}我真的很想让我们好好相处。我还在照顾它，给它换尿布，给它抓跳蚤……但它只是敷衍了事。真的很难接受，你那么爱的东西，却不爱你。
	\switchcolumn*
	\charactername{Rachel:} ...I think that bitch cracked my tooth.
	\switchcolumn
	\charactername{瑞秋：}……我觉得那个贱人把我的牙磕裂了。
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage