\begin{paracol}{2}
	\sense{Scene: A Street: Monica and Phoebe are walking to a newsstand.}
	\switchcolumn
	\sense{场景：街道上，莫妮卡和菲比走向报刊亭}
	\switchcolumn*
	\charactername{Phoebe:} Do you think they have yesterday's daily news?
	\switchcolumn
	\charactername{菲比：}你觉得他们有昨天的《每日新闻》吗？
	\switchcolumn*
	\charactername{Monica:} Why?
	\switchcolumn
	\charactername{莫妮卡：}为什么要找昨天的？
	\switchcolumn*
	\charactername{Phoebe:} Just wanna check my horoscope, see if it was right.
	\switchcolumn
	\charactername{菲比：}就是想看看我的星座运势，准不准。
	\switchcolumn*
	\charactername{Monica:} Oh my God. \ennotmain{Grabs Phoebe and turns her away} Phoebe. Don't look now, but behind us is a guy who has the potential to break our hearts and plunge us into a pit of depression.
	\switchcolumn
	\charactername{莫妮卡：}天啊。\notmain{拉住菲比转过身}菲比。现在别回头，但我们身后有个男人，他有可能伤透我们的心，把我们扔进抑郁的深渊。
	\switchcolumn*
	\charactername{Phoebe:} Where? \ennotmain{Turns to face him} Ooh, come to Momma.
	\switchcolumn
	\charactername{菲比：}在哪儿？\notmain{转身面向那个男人}哦，来妈妈这儿。
	\switchcolumn*
	\charactername{Monica:} He's coming. Be cool, be cool, be cool.
	\switchcolumn
	\charactername{莫妮卡：}他过来了。冷静，冷静，冷静。
	\switchcolumn*
	\ennotmain{The guy walks past them}
	\switchcolumn
	\notmain{男人从她们身边走过}
	\switchcolumn*
	\charactername{Guy:} Nice hat.
	\switchcolumn
	\charactername{男人：}帽子挺好看的。
	\switchcolumn*
	\charactername{Monica and Phoebe:} \ennotmain{in unison} Thanks.
	\switchcolumn
	\charactername{莫妮卡和菲比：}\notmain{异口同声}谢谢。
	\switchcolumn*
	\ennotmain{The guy walks on}
	\switchcolumn
	\notmain{男人继续往前走}
	\switchcolumn*
	\charactername{Phoebe:} We should do something. Whistle.
	\switchcolumn
	\charactername{菲比：}我们得做点什么。吹口哨吧。
	\switchcolumn*
	\charactername{Monica:} We are not going to whistle.
	\switchcolumn
	\charactername{莫妮卡：}我们才不吹口哨呢。
	\switchcolumn*
	\charactername{Phoebe:} Come on, do it.
	\switchcolumn
	\charactername{菲比：}拜托，吹嘛。
	\switchcolumn*
	\charactername{Monica:} No!
	\switchcolumn
	\charactername{莫妮卡：}不！
	\switchcolumn*
	\charactername{Phoebe:} Do it!
	\switchcolumn
	\charactername{菲比：}吹嘛！
	\switchcolumn*
	\charactername{Monica:} No!
	\switchcolumn
	\charactername{莫妮卡：}不！
	\switchcolumn*
	\charactername{Phoebe:} Do it do it do it!
	\switchcolumn
	\charactername{菲比：}吹嘛吹嘛吹嘛！
	\switchcolumn*
	\charactername{Monica:} \ennotmain{Shouts to the guy} Woo-woo!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对男人大喊}呜——呜！
	\switchcolumn*
	\ennotmain{The guy turns round, startled. Monica points to Phoebe. The guy gets hit by a truck}
	\switchcolumn
	\notmain{男人受惊转身。莫妮卡指向菲比。男人被一辆卡车撞了}
	\switchcolumn*
	\charactername{Phoebe:} I can't believe you did that!
	\switchcolumn
	\charactername{菲比：}我真不敢相信你居然这么做！
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Hospital, the guy is in a coma and Mon and Pheebs are visiting.}
	\switchcolumn
	\sense{场景：医院，男人处于昏迷状态，莫妮卡和菲比来看他}
	\switchcolumn*
	\charactername{Monica:} Why did I 'woo-hoo'? I mean, what was I hoping would happen? That-that he'd turn round and say 'I love that sound, I must have you now'?
	\switchcolumn
	\charactername{莫妮卡：}我为什么要喊“呜——呜”啊？我当时在想什么？难道指望他转过身说“我喜欢这个声音，我现在就要你”吗？
	\switchcolumn*
	\charactername{Phoebe:} I just wish there was something we could do. \ennotmain{Bends down and talks to him} Hello. Hello, Coma Guy. GET UP, YOU GIRL SCOUT! UP! UP! UP!
	\switchcolumn
	\charactername{菲比：}真希望我们能做点什么。\notmain{弯下腰对他说}嗨。嗨，昏迷哥。起来，你这个女童子军！起来！起来！起来！
	\switchcolumn*
	\charactername{Monica:} Phoebe, what are you doing?
	\switchcolumn
	\charactername{莫妮卡：}菲比，你在干嘛？
	\switchcolumn*
	\charactername{Phoebe:} Maybe nobody's tried this.
	\switchcolumn
	\charactername{菲比：}说不定没人这么试过呢。
	\switchcolumn*
	\charactername{Monica:} I wish we at least knew his name... Look at that face. I mean, even sleeping, he looks smart. I bet he's a lawyer.
	\switchcolumn
	\charactername{莫妮卡：}真希望我们至少知道他的名字……你看他这张脸。就算睡着了，看起来也很聪明。我打赌他是个律师。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, but did you see the dents in his knuckles? That means he's artistic.
	\switchcolumn
	\charactername{菲比：}是啊，但你看到他指关节上的茧了吗？说明他有艺术细胞。
	\switchcolumn*
	\charactername{Monica:} Okay, he's a lawyer, who teaches sculpting on the side. And- he can dance!
	\switchcolumn
	\charactername{莫妮卡：}好吧，他是个律师，还兼职教雕塑。而且——他还会跳舞！
	\switchcolumn*
	\charactername{Phoebe:} Oh! And, he's the kinda guy who, when you're talking, he's listening, y'know, and not saying 'Yeah, I understand' but really wondering what you look like naked.
	\switchcolumn
	\charactername{菲比：}哦！而且他是那种你说话时会认真听的人，不是随口说“我懂”，而是真的在好奇你 naked 的样子。
	\switchcolumn*
	\charactername{Monica:} I wish all guys could be like him.
	\switchcolumn
	\charactername{莫妮卡：}真希望所有男人都能像他这样。
	\switchcolumn*
	\charactername{Phoebe:} I know.
	\switchcolumn
	\charactername{菲比：}我懂。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Monica and Phoebe are telling everyone about their coma guy.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，莫妮卡和菲比在跟大家说昏迷哥的事}
	\switchcolumn*
	\charactername{Chandler:} Are there no conscious men in the city for you two?
	\switchcolumn
	\charactername{钱德勒：}这城市里就没有清醒的男人给你们俩选了吗？
	\switchcolumn*
	\charactername{Monica:} He doesn't have anyone.
	\switchcolumn
	\charactername{莫妮卡：}他身边没人照顾。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, we-we feel kinda responsible.
	\switchcolumn
	\charactername{菲比：}是啊，我们觉得有点责任。
	\switchcolumn*
	\charactername{Joey:} I can't believe you said woowoo. I don't even say woowoo.
	\switchcolumn
	\charactername{乔伊：}真不敢相信你居然喊“呜——呜”。我都不这么喊。
	\switchcolumn*
	\charactername{Rachel:} Oh, she's coming up! She's coming up! \ennotmain{Turns on the TV}
	\switchcolumn
	\charactername{瑞秋：}哦，她要出场了！她要出场了！\notmain{打开电视}
	\switchcolumn*
	\charactername{Jay Leno:} \ennotmain{on TV} Folks, when we come back we'll be talking about her new book, 'Euphoria Unbound': the always interesting Nora Tyler Bing. You might wanna put the kids to bed for this one.
	\switchcolumn
	\charactername{杰·雷诺：}\notmain{电视上}观众朋友们，稍后我们将邀请诺拉·泰勒·宾聊聊她的新书《无拘无束的狂喜》。这位女士总是很有意思。建议家长们先把孩子哄睡哦。
	\switchcolumn*
	\ennotmain{Everyone has settled down to watch, except Chandler}
	\switchcolumn
	\notmain{所有人都坐下来准备看，除了钱德勒}
	\switchcolumn*
	\charactername{Chandler:} Y'know, we don't have to watch this. Weekend At Bernie's is on Showtime, HBO, and Cinemax.
	\switchcolumn
	\charactername{钱德勒：}其实我们不一定非要看这个。《老板度假去》在Showtime、HBO和Cinemax都在播呢。
	\switchcolumn*
	\charactername{Rachel:} No way, forget it.
	\switchcolumn
	\charactername{瑞秋：}不行，别想了。
	\switchcolumn*
	\charactername{Joey:} C'mon, she's your mom!
	\switchcolumn
	\charactername{乔伊：}拜托，那是你妈妈！
	\switchcolumn*
	\charactername{Chandler:} Exactly. Weekend At Bernie's! Dead guy getting hit in the groin twenty, thirty times! No?
	\switchcolumn
	\charactername{钱德勒：}正因为是我妈才不想看。《老板度假去》啊！一个死人的胯部被撞了二三十次！不看吗？
	\switchcolumn*
	\charactername{Rachel:} Chandler, I gotta tell you, I love your mom's books! I love her books! I cannot get on a plane without one! I mean, this is so cool!
	\switchcolumn
	\charactername{瑞秋：}钱德勒，我得跟你说，我超爱你妈妈的书！我离不开她的书！坐飞机必带一本！这太酷了！
	\switchcolumn*
	\charactername{Chandler:} Yeah, well, you wouldn't think it was cool if you're eleven years old and all your friends are passing around page 79 of 'Mistress Bitch.'
	\switchcolumn
	\charactername{钱德勒：}是吗？如果你11岁，所有朋友都在传阅《泼妇情妇》的第79页，你就不会觉得酷了。
	\switchcolumn*
	\charactername{Ross:} C'mon, Chandler, I love your mom. I think she's a blast.
	\switchcolumn
	\charactername{罗斯：}拜托，钱德勒，我挺喜欢你妈妈的。她很有意思。
	\switchcolumn*
	\charactername{Chandler:} You can say that because she's not your mom.
	\switchcolumn
	\charactername{钱德勒：}你当然可以这么说，因为她不是你妈。
	\switchcolumn*
	\charactername{Ross:} Oh, please...
	\switchcolumn
	\charactername{罗斯：}哦，拜托……
	\switchcolumn*
	\ennotmain{Rachel opens the door to Paolo}
	\switchcolumn
	\notmain{瑞秋给保罗开门}
	\switchcolumn*
	\charactername{Paolo:} Bona sera.
	\switchcolumn
	\charactername{保罗：}晚上好。\notmain{意大利语}
	\switchcolumn*
	\charactername{Rachel:} Oh, hi sweetie. \ennotmain{They kiss}
	\switchcolumn
	\charactername{瑞秋：}哦，嗨亲爱的。\notmain{两人接吻}
	\switchcolumn*
	\charactername{Ross:} When did Rigatoni get back from Rome?
	\switchcolumn
	\charactername{罗斯：}意大利面\notmain{调侃保罗}什么时候从罗马回来的？
	\switchcolumn*
	\charactername{Monica:} Last night.
	\switchcolumn
	\charactername{莫妮卡：}昨晚。
	\switchcolumn*
	\charactername{Ross:} Ah, so then his plane didn't explode in a big ball of fire?... Just a dream I had- but, phew.
	\switchcolumn
	\charactername{罗斯：}啊，所以他的飞机没炸成一团火球？……只是我做的梦而已——还好还好。
	\switchcolumn*
	\charactername{Phoebe:} Hey hey hey! She's on!
	\switchcolumn
	\charactername{菲比：}嘿！她出场了！
	\switchcolumn*
	\charactername{Paolo:} Ah! Nora Bing!
	\switchcolumn
	\charactername{保罗：}啊！诺拉·宾！
	\switchcolumn*
	\charactername{Jay Leno:} \ennotmain{on TV} ...Now what is this about you-you being arrested i-in London? What is that all about?
	\switchcolumn
	\charactername{杰·雷诺：}\notmain{电视上}……听说你在伦敦被捕了？这是怎么回事？
	\switchcolumn*
	\charactername{Phoebe:} Your mom was arrested?
	\switchcolumn
	\charactername{菲比：}你妈妈被捕过？
	\switchcolumn*
	\charactername{Chandler:} Shhh, busy beaming with pride.
	\switchcolumn
	\charactername{钱德勒：}嘘，正忙着为她骄傲呢。\notmain{反讽}
	\switchcolumn*
	\charactername{Mrs. Bing:} \ennotmain{on TV} ...This is kind of embarrassing, but occasionally after I've been intimate with a man...
	\switchcolumn
	\charactername{宾夫人：}\notmain{电视上}……这有点尴尬，但有时候我和男人亲密之后……
	\switchcolumn*
	\charactername{Chandler:} Now why would she say that's embarrassing?
	\switchcolumn
	\charactername{钱德勒：}她为什么会觉得这尴尬啊？
	\switchcolumn*
	\charactername{All:} Shhh.
	\switchcolumn
	\charactername{众人：}嘘。
	\switchcolumn*
	\charactername{Mrs. Bing:} \ennotmain{on TV} ...I just get this craving for Kung Pow Chicken.
	\switchcolumn
	\charactername{宾夫人：}\notmain{电视上}……我就特别想吃宫保鸡丁。
	\switchcolumn*
	\charactername{Chandler:} THAT'S TOO MUCH INFORMATION!!
	\switchcolumn
	\charactername{钱德勒：}这信息也太多余了吧！！
	\switchcolumn*
	\charactername{Jay Leno:} \ennotmain{on TV} Alright, so now you're doing this whole book tour thing, how is that going?
	\switchcolumn
	\charactername{杰·雷诺：}\notmain{电视上}好的，现在你在做新书巡回宣传，进展怎么样？
	\switchcolumn*
	\charactername{Mrs. Bing:} \ennotmain{on TV} Oh, fine. I'm leaving for New York tomorrow, which I hate- but I get to see my son, who I love...
	\switchcolumn
	\charactername{宾夫人：}\notmain{电视上}哦，挺好的。我明天要去纽约，虽然我讨厌那地方——但能见到我儿子，我很爱他……
	\switchcolumn*
	\charactername{All:} Awww!
	\switchcolumn
	\charactername{众人：}哇哦！\notmain{感动}
	\switchcolumn*
	\charactername{Chandler:} This is the way that I find out. Most moms use the phone.
	\switchcolumn
	\charactername{钱德勒：}我居然是这么知道的。大多数妈妈都会打电话通知吧。
	\switchcolumn*
	\charactername{Jay Leno:} \ennotmain{on TV} Y'know, don't take this wrong, I-I just don't see you a-as a mom, somehow.. I don't mean that, I don't mean that bad...
	\switchcolumn
	\charactername{杰·雷诺：}\notmain{电视上}你别误会，我只是觉得你不太像个妈妈……我不是那个意思，没恶意的……
	\switchcolumn*
	\charactername{Mrs. Bing:} \ennotmain{on TV} Oh no, I am a fabulous mom! I bought my son his first condoms.
	\switchcolumn
	\charactername{宾夫人：}\notmain{电视上}哦不，我是个超棒的妈妈！我儿子的第一盒避孕套就是我买的。
	\switchcolumn*
	\ennotmain{The gang turn to look at Chandler}
	\switchcolumn
	\notmain{众人转头看向钱德勒}
	\switchcolumn*
	\charactername{Chandler:} ...And then he burst into flames.
	\switchcolumn
	\charactername{钱德勒：}……然后他就自燃了。\notmain{尴尬地转移话题}
	\switchcolumn*
	\sense{Scene: The Hospital, it's a montage of Monica and Phoebe's visit to the hospital with My Guy playing in the background. It starts with Monica reading a newspaper to him.}
	\switchcolumn
	\sense{场景：医院，蒙太奇片段，背景音乐是《My Guy》，展现莫妮卡和菲比的探病日常。开头是莫妮卡给他读报纸}
	\switchcolumn*
	\charactername{Monica:} Let's see. Congress is debating a new deficit reduction bill... the mayor wants to raise subway fares again... the high today was forty-five... and- oh, teams played sports.
	\switchcolumn
	\charactername{莫妮卡：}看看啊。国会正在讨论一项新的减赤法案……市长又想提高地铁票价了……今天最高气温45华氏度\notmain{约7摄氏度}……还有——哦，有球队打比赛了。
	\switchcolumn*
	\sense{Next is a shot of them dragging an enormous plant into the room, then Monica knitting a sweater, then Phoebe singing, then Phoebe shaving him and chatting to Monica}
	\switchcolumn
	\sense{接下来的镜头：她们拖着一盆巨大的植物进病房，然后是莫妮卡给他织毛衣，菲比给他唱歌，菲比给他刮胡子并和莫妮卡聊天}
	\switchcolumn*
	\charactername{Phoebe:} What about Glen? He could be a Glen.
	\switchcolumn
	\charactername{菲比：}叫格伦怎么样？他可能叫格伦。
	\switchcolumn*
	\charactername{Monica:} Nah... not-not special enough.
	\switchcolumn
	\charactername{莫妮卡：}不行……不够特别。
	\switchcolumn*
	\charactername{Phoebe:} Ooh! How about Agamemnon?
	\switchcolumn
	\charactername{菲比：}哦！阿伽门农\notmain{希腊神话人物}怎么样？
	\switchcolumn*
	\charactername{Monica:} Waaay too special.
	\switchcolumn
	\charactername{莫妮卡：}太特别了点。
	\switchcolumn*
	\sense{Scene: A Mexican Restaurant, Monica, Phoebe, Joey, Chandler and his mom are there.}
	\switchcolumn
	\sense{场景：一家墨西哥餐厅，莫妮卡、菲比、乔伊、钱德勒和他妈妈都在}
	\switchcolumn*
	\charactername{Mrs. Bing:} I am famished. What do I want... \ennotmain{Looks at Chandler's menu}
	\switchcolumn
	\charactername{宾夫人：}我饿死了。我想吃点什么呢……\notmain{看钱德勒的菜单}
	\switchcolumn*
	\charactername{Chandler:} Please God don't let it be Kung Pow Chicken.
	\switchcolumn
	\charactername{钱德勒：}拜托上帝，别让她点宫保鸡丁。
	\switchcolumn*
	\charactername{Mrs. Bing:} Oh, you watched the show! What'd you think?
	\switchcolumn
	\charactername{宾夫人：}哦，你看节目了！觉得怎么样？
	\switchcolumn*
	\charactername{Chandler:} Well, I think you need to come out of your shell just a little.
	\switchcolumn
	\charactername{钱德勒：}嗯，我觉得你可以再外向一点点。\notmain{反讽}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{Entering} What is this dive? Only you could've picked this place.
	\switchcolumn
	\charactername{罗斯：}\notmain{走进来}这破地方是哪儿啊？也就你能选这种地方。
	\switchcolumn*
	\charactername{Mrs. Bing:} Oooh, c'mon, shut up, it's fun. Gimme a hug. \ennotmain{They both sit down} Well, I think we're ready for some tequila.
	\switchcolumn
	\charactername{宾夫人：}哦，拜托，闭嘴吧，挺有意思的。来抱一个。\notmain{两人坐下}好了，我们来点龙舌兰吧。
	\switchcolumn*
	\charactername{Chandler:} I know I am.
	\switchcolumn
	\charactername{钱德勒：}我反正要喝。
	\switchcolumn*
	\charactername{Mrs. Bing:} Who's doing shots?
	\switchcolumn
	\charactername{宾夫人：}谁要喝 shots\notmain{小杯烈酒}？
	\switchcolumn*
	\charactername{Monica:} Yeah.
	\switchcolumn
	\charactername{莫妮卡：}我要。
	\switchcolumn*
	\charactername{Phoebe:} I'm in.
	\switchcolumn
	\charactername{菲比：}算我一个。
	\switchcolumn*
	\charactername{Mrs. Bing:} There y'go. Ross?
	\switchcolumn
	\charactername{宾夫人：}这就对了。罗斯？
	\switchcolumn*
	\charactername{Ross:} Uh, I'm not really a shot drinking kinda guy.
	\switchcolumn
	\charactername{罗斯：}呃，我不是那种喝小杯烈酒的人。
	\switchcolumn*
	\ennotmain{Enter Rachel and Paolo. They are both somewhat flustered}
	\switchcolumn
	\notmain{瑞秋和保罗走进来，两人都有些慌乱}
	\switchcolumn*
	\charactername{Rachel:} Hi! Sorry- sorry we're late, we, uh, kinda just, y'know, lost track of time.
	\switchcolumn
	\charactername{瑞秋：}嗨！抱歉——抱歉来晚了，我们，呃，有点，你知道的，忘了时间。
	\switchcolumn*
	\charactername{Ross:} ...But a man can change. \ennotmain{Downs a shot}
	\switchcolumn
	\charactername{罗斯：}……但人是会变的。\notmain{干了一杯 shot}
	\switchcolumn*
	\sense{Time lapse. Ross is now clearly drunk. He is holding up a shot glass to his eye like a jeweller's eye.}
	\switchcolumn
	\sense{时间快进。罗斯明显喝醉了。他拿着一个小酒杯凑到眼睛前，像珠宝商的放大镜一样}
	\switchcolumn*
	\charactername{Ross:} Anyone want me to appraise anything?
	\switchcolumn
	\charactername{罗斯：}有人想让我鉴定点什么吗？
	\switchcolumn*
	\ennotmain{Rachel feeds something to Paolo. He eats it and licks her hand}
	\switchcolumn
	\notmain{瑞秋喂保罗吃东西。保罗吃完后舔了舔她的手}
	\switchcolumn*
	\charactername{Rachel:} Mrs. Bing, I have to tell you, I've read everything you've ever written. No, I mean it! I mean, when I read Euphoria at Midnight, all I wanted to do was become a writer.
	\switchcolumn
	\charactername{瑞秋：}宾夫人，我得跟你说，你写的所有书我都读过。真的！我是说，我读《午夜狂喜》的时候，满脑子都想成为一名作家。
	\switchcolumn*
	\charactername{Mrs. Bing:} Oh, please, honey, listen, if I can do it, anybody can. You just start with half a dozen European cities, throw in thirty euphemisms for male genitalia, and bam! You have got yourself a book.
	\switchcolumn
	\charactername{宾夫人：}哦，拜托，亲爱的，听着，我都能做到，谁都行。你只需要写六七个欧洲城市，再加点三十个男性生殖器的委婉说法，砰！一本书就成了。
	\switchcolumn*
	\charactername{Chandler:} Myyy mother, ladies and gentlemen.
	\switchcolumn
	\charactername{钱德勒：}这就是我妈妈，女士们先生们。
	\switchcolumn*
	\sense{Cut to Mrs. Bing on the telephone.}
	\switchcolumn
	\sense{镜头切换到宾夫人在打电话}
	\switchcolumn*
	\charactername{Mrs. Bing:} Yeah, any messages for room 226?
	\switchcolumn
	\charactername{宾夫人：}喂，226房间有留言吗？
	\switchcolumn*
	\ennotmain{Ross emerges from a toilet marked 'Chicas'}
	\switchcolumn
	\notmain{罗斯从标着“女士”的厕所里走出来}
	\switchcolumn*
	\charactername{Mrs. Bing:} You okay there, slugger?
	\switchcolumn
	\charactername{宾夫人：}你没事吧，小伙子？
	\switchcolumn*
	\charactername{Ross:} Yeah, I'm fine, I'm fine. \ennotmain{A woman emerges from the toilet behind him and he tries to pretend he was in the other one}
	\switchcolumn
	\charactername{罗斯：}没事，我没事，我没事。\notmain{一个女人从他身后的厕所里走出来，他试图假装自己是从另一个厕所出来的}
	\switchcolumn*
	\charactername{Mrs. Bing:} What is with you tonight?
	\switchcolumn
	\charactername{宾夫人：}你今晚怎么回事？
	\switchcolumn*
	\charactername{Ross:} Nothing. Nothing nothing nothing.
	\switchcolumn
	\charactername{罗斯：}没什么。没什么没什么没什么。
	\switchcolumn*
	\charactername{Mrs. Bing:} \ennotmain{To phone} Okay, thank you. \ennotmain{To Ross} It's the Italian Hand-Licker, isn't it.
	\switchcolumn
	\charactername{宾夫人：}\notmain{对着电话}好的，谢谢。\notmain{对罗斯}是那个舔手的意大利人，对吧？
	\switchcolumn*
	\charactername{Ross:} No. It's the one he's licking.
	\switchcolumn
	\charactername{罗斯：}不是。是他舔的那个人\notmain{指瑞秋}。
	\switchcolumn*
	\charactername{Mrs. Bing:} She's supposed to be with you.
	\switchcolumn
	\charactername{宾夫人：}她本该和你在一起的。
	\switchcolumn*
	\charactername{Ross:} You're good.
	\switchcolumn
	\charactername{罗斯：}你真厉害。
	\switchcolumn*
	\charactername{Mrs. Bing:} Oh, Ross, listen to me. I have sold a hundred million copies of my books, and y'know why?
	\switchcolumn
	\charactername{宾夫人：}哦，罗斯，听我说。我的书卖了一亿本，你知道为什么吗？
	\switchcolumn*
	\charactername{Ross:} The girl on the cover with her nipples showing?
	\switchcolumn
	\charactername{罗斯：}因为封面上的女孩露了乳头？
	\switchcolumn*
	\charactername{Mrs. Bing:} No. Because I know how to write men that women fall in love with. Believe me, I cannot sell a Paolo. People will not turn three hundred twenty-five pages for a Paolo. C'mon, the guy's a secondary character, a, y'know, complication you eventually kill off.
	\switchcolumn
	\charactername{宾夫人：}不是。因为我知道怎么写让女人爱上的男人。相信我，保罗这种角色可卖不出去。没人会为了保罗翻三百二十五页书。拜托，他就是个次要角色，一个最终会被解决掉的麻烦。
	\switchcolumn*
	\charactername{Ross:} When?
	\switchcolumn
	\charactername{罗斯：}什么时候解决？
	\switchcolumn*
	\charactername{Mrs. Bing:} He's not a hero. ...You know who our hero is.
	\switchcolumn
	\charactername{宾夫人：}他不是主角。……你知道谁是我们的主角。
	\switchcolumn*
	\charactername{Ross:} The guy on the cover with his nipples showing?
	\switchcolumn
	\charactername{罗斯：}封面上露乳头的那个男人？
	\switchcolumn*
	\charactername{Mrs. Bing:} No, it's you!
	\switchcolumn
	\charactername{宾夫人：}不是，是你！
	\switchcolumn*
	\charactername{Ross:} Please.
	\switchcolumn
	\charactername{罗斯：}拜托。
	\switchcolumn*
	\charactername{Mrs. Bing:} No, really, c'mon. You're smart, you're sexy...
	\switchcolumn
	\charactername{宾夫人：}不，真的，拜托。你聪明、性感……
	\switchcolumn*
	\charactername{Ross:} Right.
	\switchcolumn
	\charactername{罗斯：}是吗。
	\switchcolumn*
	\charactername{Mrs. Bing:} You are gonna be fine, believe me.
	\switchcolumn
	\charactername{宾夫人：}你会没事的，相信我。
	\switchcolumn*
	\ennotmain{She kisses him on the cheek}
	\switchcolumn
	\notmain{她吻了吻他的脸颊}
	\switchcolumn*
	\charactername{Ross:} Uh-oh...
	\switchcolumn
	\charactername{罗斯：}哦不……
	\switchcolumn*
	\ennotmain{...Then full on the mouth}
	\switchcolumn
	\notmain{……然后吻上了他的嘴}
	\switchcolumn*
	\ennotmain{Enter Joey}
	\switchcolumn
	\notmain{乔伊走进来}
	\switchcolumn*
	\charactername{Joey:} Uhhhh.... I'll just pee in the street.
	\switchcolumn
	\charactername{乔伊：}呃……我还是去街上尿吧。
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Chandler and Joey's, the next morning. Joey is getting the door in his dressing gown—it's Ross.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，第二天早上。乔伊穿着睡袍去开门——是罗斯}
	\switchcolumn*
	\charactername{Ross:} Hey, is Chandler here?
	\switchcolumn
	\charactername{罗斯：}嘿，钱德勒在吗？
	\switchcolumn*
	\charactername{Joey:} Yeah.
	\switchcolumn
	\charactername{乔伊：}在。
	\switchcolumn*
	\ennotmain{Ross drags Joey into the hall and slams the door}
	\switchcolumn
	\notmain{罗斯把乔伊拉到走廊，关上房门}
	\switchcolumn*
	\charactername{Ross:} Okay, uh, about last night, um, Chandler.. you didn't tell... \ennotmain{Joey shakes his head} Okay, 'cause I'm thinking- we don't need to tell Chandler, I mean, it was just a kiss, right? One kiss? No big deal? Right?
	\switchcolumn
	\charactername{罗斯：}好了，呃，关于昨晚的事，呃，钱德勒……你没告诉他吧……\notmain{乔伊摇头}好，因为我在想——我们没必要告诉钱德勒，只是一个吻而已，对吧？就一个吻？没什么大不了的？对吧？
	\switchcolumn*
	\charactername{Joey:} Right. No big deal.
	\switchcolumn
	\charactername{乔伊：}对。没什么大不了的。
	\switchcolumn*
	\charactername{Ross:} Okay.
	\switchcolumn
	\charactername{罗斯：}好。
	\switchcolumn*
	\charactername{Joey:} In Bizarro World!! You broke the code!
	\switchcolumn
	\charactername{乔伊：}在反转世界里才没什么大不了！你违反规矩了！
	\switchcolumn*
	\charactername{Ross:} What code?
	\switchcolumn
	\charactername{罗斯：}什么规矩？
	\switchcolumn*
	\charactername{Joey:} You don't kiss your friend's mom! Sisters are okay, maybe a hot-lookin' aunt... but not a mom, never a mom!
	\switchcolumn
	\charactername{乔伊：}你不能吻朋友的妈妈！姐妹还行，或许性感的阿姨也可以……但妈妈不行，绝对不行！
	\switchcolumn*
	\ennotmain{Chandler opens the door and startles them. He picks up the paper}
	\switchcolumn
	\notmain{钱德勒开门，吓了他们一跳。他拿起报纸}
	\switchcolumn*
	\charactername{Chandler:} What are you guys doing out here?
	\switchcolumn
	\charactername{钱德勒：}你们俩在外面干嘛？
	\switchcolumn*
	\charactername{Ross:} Uh.. uh.. Well, Joey and I had discussed getting in an early morning racquetball game. But, um, apparently, somebody overslept.
	\switchcolumn
	\charactername{罗斯：}呃……呃……乔伊和我本来约好早上打壁球的。但显然，有人睡过头了。
	\switchcolumn*
	\charactername{Joey:} Yeah, well, you don't have your racket.
	\switchcolumn
	\charactername{乔伊：}是啊，而且你没带球拍。
	\switchcolumn*
	\charactername{Ross:} No, no I don't, because it's being restrung, somebody was supposed to bring me one.
	\switchcolumn
	\charactername{罗斯：}我没带是因为球拍在重新穿线，本来该有人给我带一个的。
	\switchcolumn*
	\charactername{Joey:} Yeah, well you didn't call and leave your grip size.
	\switchcolumn
	\charactername{乔伊：}是啊，可你没打电话说你的握把尺寸。
	\switchcolumn*
	\charactername{Chandler:} Okay, you guys spend waaaay too much time together. \ennotmain{Goes back inside and shuts the door}
	\switchcolumn
	\charactername{钱德勒：}好吧，你们俩待在一起的时间也太长了。\notmain{回到公寓，关上房门}
	\switchcolumn*
	\charactername{Ross:} Okay, I'm scum, I'm scum.
	\switchcolumn
	\charactername{罗斯：}好吧，我是混蛋，我是混蛋。
	\switchcolumn*
	\charactername{Joey:} Ross, how could you let this happen?
	\switchcolumn
	\charactername{乔伊：}罗斯，你怎么能让这种事发生？
	\switchcolumn*
	\charactername{Ross:} I don't know, God, I... well, it's not like she's a regular mom, y'know? She's, she's sexy, she's...
	\switchcolumn
	\charactername{罗斯：}我不知道，天啊，我……她又不是普通的妈妈，你知道吗？她性感、她……
	\switchcolumn*
	\charactername{Joey:} You don't think my mom's sexy?
	\switchcolumn
	\charactername{乔伊：}你觉得我妈妈不性感？
	\switchcolumn*
	\charactername{Ross:} Well... not in the same way...
	\switchcolumn
	\charactername{罗斯：}呃……不是同一种性感……
	\switchcolumn*
	\charactername{Joey:} I'll have you know that Gloria Tribbiani was a handsome woman in her day, alright? You think it's easy giving birth to seven children?
	\switchcolumn
	\charactername{乔伊：}我告诉你，格洛丽亚·崔比安尼当年可是个大美女，好吗？你以为生七个孩子容易吗？
	\switchcolumn*
	\charactername{Ross:} Okay, I think we're getting into a weird area here...
	\switchcolumn
	\charactername{罗斯：}好吧，我们聊得有点跑偏了……
	\switchcolumn*
	\ennotmain{Monica and Rachel's door opens and Rachel and Paolo emerge}
	\switchcolumn
	\notmain{莫妮卡和瑞秋的房门打开，瑞秋和保罗走出来}
	\switchcolumn*
	\charactername{Rachel:} Hey.
	\switchcolumn
	\charactername{瑞秋：}嘿。
	\switchcolumn*
	\charactername{Ross:} Hey.
	\switchcolumn
	\charactername{罗斯：}嘿。
	\switchcolumn*
	\charactername{Rachel:} What're you guys doing out here?
	\switchcolumn
	\charactername{瑞秋：}你们俩在外面干嘛？
	\switchcolumn*
	\charactername{Ross:} Well, not playing raquetball!
	\switchcolumn
	\charactername{罗斯：}还能干嘛，没打成壁球呗！
	\switchcolumn*
	\charactername{Joey:} He forgot to leave his grip size!
	\switchcolumn
	\charactername{乔伊：}他没说握把尺寸！
	\switchcolumn*
	\charactername{Ross:} He didn't get the goggles!
	\switchcolumn
	\charactername{罗斯：}他没带护目镜！
	\switchcolumn*
	\charactername{Rachel:} Well,sounds like you two have issues.
	\switchcolumn
	\charactername{瑞秋：}听起来你们俩有矛盾啊。
	\switchcolumn*
	\ennotmain{She and Paolo walk a little way down the hall}
	\switchcolumn
	\notmain{她和保罗沿着走廊走了几步}
	\switchcolumn*
	\charactername{Rachel:} Goodbye, baby.
	\switchcolumn
	\charactername{瑞秋：}再见，宝贝。
	\switchcolumn*
	\charactername{Paolo:} Ciao, bela.
	\switchcolumn
	\charactername{保罗：}再见，美女。\notmain{意大利语}
	\switchcolumn*
	\ennotmain{They kiss. Ross is watching them}
	\switchcolumn
	\notmain{两人接吻。罗斯看着他们}
	\switchcolumn*
	\charactername{Ross:} Do they wait for me to do this?
	\switchcolumn
	\charactername{罗斯：}他们非得等我在这儿的时候做这个吗？
	\switchcolumn*
	\ennotmain{Joey and Ross go into Monica and Rachel's apartment}
	\switchcolumn
	\notmain{乔伊和罗斯走进莫妮卡和瑞秋的公寓}
	\switchcolumn*
	\charactername{Joey:} So are you gonna tell him?
	\switchcolumn
	\charactername{乔伊：}你打算告诉他吗？
	\switchcolumn*
	\charactername{Ross:} Why would I tell him?
	\switchcolumn
	\charactername{罗斯：}我为什么要告诉他？
	\switchcolumn*
	\charactername{Joey:} How about 'cause if you don't, his mother might.
	\switchcolumn
	\charactername{乔伊：}因为如果你不说，他妈妈可能会说啊。
	\switchcolumn*
	\charactername{Ross:} Oh...
	\switchcolumn
	\charactername{罗斯：}哦……
	\switchcolumn*
	\charactername{Monica:} \ennotmain{Entering} What are you guys doing here?
	\switchcolumn
	\charactername{莫妮卡：}\notmain{走进来}你们俩在这儿干嘛？
	\switchcolumn*
	\charactername{Joey:} Uhhhh.... he's not even wearing a jockstrap!
	\switchcolumn
	\charactername{乔伊：}呃……他连运动护裆都没穿！
	\switchcolumn*
	\charactername{Monica:} ...What did I ask?
	\switchcolumn
	\charactername{莫妮卡：}……我问的是什么来着？
	\switchcolumn*
	\sense{Scene: Hospital. Phoebe is there stroking Coma Guy's hair, when Monica enters with a bunch of balloons.}
	\switchcolumn
	\sense{场景：医院。菲比正在抚摸昏迷哥的头发，莫妮卡拿着一束气球走进来}
	\switchcolumn*
	\charactername{Monica:} Hi.
	\switchcolumn
	\charactername{莫妮卡：}嗨。
	\switchcolumn*
	\charactername{Phoebe:} Hi.
	\switchcolumn
	\charactername{菲比：}嗨。
	\switchcolumn*
	\charactername{Monica:} What are you doing here?
	\switchcolumn
	\charactername{莫妮卡：}你在这儿干嘛？
	\switchcolumn*
	\charactername{Phoebe:} Nothing, I just thought I'd stop by.. y'know, after the uh... that I.. y'know, so what are you doing here?
	\switchcolumn
	\charactername{菲比：}没什么，就是顺道过来看看……你知道，在……之后……那个我……你知道，那你在这儿干嘛？
	\switchcolumn*
	\charactername{Monica:} I'm not really here. Just thought I'd drop these off...on the way.. my way... Do you come here a lot? Without me?
	\switchcolumn
	\charactername{莫妮卡：}我也不是特意来的。就是顺道把这些气球送来……在我去……的路上……你经常来这儿吗？不跟我说一声？
	\switchcolumn*
	\charactername{Phoebe:} No. \ennotmain{Monica brushes Coma Guy's hair in the other direction} No! No! ...So, um, do you think he's doing any better than he was this morning?
	\switchcolumn
	\charactername{菲比：}没有。\notmain{莫妮卡把昏迷哥的头发往另一个方向梳}不！不！……那，呃，你觉得他比早上好多了吗？
	\switchcolumn*
	\charactername{Monica:} How would I know? I-I wasn't here.
	\switchcolumn
	\charactername{莫妮卡：}我怎么知道？我——我没来过。
	\switchcolumn*
	\charactername{Phoebe:} Really? Not even to, um, change his PAJAMAS?! \ennotmain{Whips back the sheet to reveal him wearing new pajamas.}
	\switchcolumn
	\charactername{菲比：}真的吗？甚至没过来给他换……睡衣？！\notmain{掀开床单，露出他身上的新睡衣}
	\switchcolumn*
	\sense{Scene: Chandler and Joey's, Ross is talking to Chandler. Joey is making a snack at the bar.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，罗斯在跟钱德勒说话。乔伊在吧台做零食}
	\switchcolumn*
	\charactername{Chandler:} Oh my God.
	\switchcolumn
	\charactername{钱德勒：}天啊。
	\switchcolumn*
	\charactername{Ross:} You're my friend. I-I had to tell you.
	\switchcolumn
	\charactername{罗斯：}你是我的朋友。我——我必须告诉你。
	\switchcolumn*
	\charactername{Chandler:} I can't believe it. Paolo kissed my mom?
	\switchcolumn
	\charactername{钱德勒：}真不敢相信。保罗吻了我妈妈？
	\switchcolumn*
	\charactername{Ross:} Yeah, um, I don't know if you noticed, but he had a lot to drink, and you know how he gets when he's drun..uh... \ennotmain{He has caught sight of Joey scowling at him} I can't do this, I did it, it was me, I'm sorry, I kissed your mom.
	\switchcolumn
	\charactername{罗斯：}是啊，呃，你可能没注意到，他喝了很多酒，你知道他喝醉了之后就会……呃……\notmain{看到乔伊怒视着他}我瞒不下去了，是我，对不起，是我吻了你妈妈。
	\switchcolumn*
	\charactername{Chandler:} What?
	\switchcolumn
	\charactername{钱德勒：}什么？
	\switchcolumn*
	\charactername{Ross:} I was really upset about Rachel and Paolo, and I think I had too much tequila, and Nora- um, Mrs. Mom- your Bing- was just being nice, y'know, and- But nothing happened, nothing- Ask Joey, Joey, uh, came in-
	\switchcolumn
	\charactername{罗斯：}我当时因为瑞秋和保罗的事特别难过，而且我喝了太多龙舌兰，诺拉——呃，妈妈——你的宾夫人——只是人太好了，你知道吗，而且——但什么都没发生，真的没发生——问乔伊，乔伊当时进来了——
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{To Joey} You knew about this?
	\switchcolumn
	\charactername{钱德勒：}\notmain{对乔伊}你早就知道？
	\switchcolumn*
	\charactername{Joey:} Uh... y'know, knowledge is a tricky thing.
	\switchcolumn
	\charactername{乔伊：}呃……知识这东西，挺微妙的。
	\switchcolumn*
	\charactername{Chandler:} I spent the entire day with you, why didn't you tell me?!
	\switchcolumn
	\charactername{钱德勒：}我跟你待了一整天，你为什么不告诉我？！
	\switchcolumn*
	\charactername{Joey:} Hey, hey, hey, you're lucky I caught them when I did, or else who knows what woulda happened.
	\switchcolumn
	\charactername{乔伊：}嘿，嘿，嘿，你该庆幸我及时撞见了，不然谁知道会发生什么。
	\switchcolumn*
	\charactername{Ross:} Thanks, man, big help.
	\switchcolumn
	\charactername{罗斯：}谢了啊，真是帮大忙了。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{To Ross} I can't believe this! What the hell were you thinking?
	\switchcolumn
	\charactername{钱德勒：}\notmain{对罗斯}我真不敢相信！你当时脑子在想什么？
	\switchcolumn*
	\charactername{Ross:} I wasn't- I mean, I-
	\switchcolumn
	\charactername{罗斯：}我没在想——我是说，我——
	\switchcolumn*
	\charactername{Chandler:} Y'know, of all my friends, no-one knows the crap I go through with my mom more than you.
	\switchcolumn
	\charactername{钱德勒：}你知道吗，在我所有朋友里，没人比你更清楚我跟我妈妈之间的那些破事。
	\switchcolumn*
	\charactername{Ross:} I know-
	\switchcolumn
	\charactername{罗斯：}我知道——
	\switchcolumn*
	\charactername{Chandler:} I can't believe you did this. \ennotmain{Walks toward the door}
	\switchcolumn
	\charactername{钱德勒：}我真不敢相信你居然这么做。\notmain{走向门口}
	\switchcolumn*
	\charactername{Ross:} Chandler-
	\switchcolumn
	\charactername{罗斯：}钱德勒——
	\switchcolumn*
	\charactername{Joey:} Me neither, y'know what-
	\switchcolumn
	\charactername{乔伊：}我也不敢相信，你知道吗——
	\switchcolumn*
	\charactername{Chandler:} I'm still mad at you for not telling me.
	\switchcolumn
	\charactername{钱德勒：}你没告诉我，我还在生你的气。
	\switchcolumn*
	\charactername{Joey:} What are you mad at me for?!
	\switchcolumn
	\charactername{乔伊：}你生我的气干嘛？！
	\switchcolumn*
	\charactername{Ross:} Chandler-
	\switchcolumn
	\charactername{罗斯：}钱德勒——
	\switchcolumn*
	\charactername{Chandler:} You gotta let me slam the door! \ennotmain{Leaves; slams the door}
	\switchcolumn
	\charactername{钱德勒：}你得让我摔一次门！\notmain{离开，摔上门}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{Shouting after him} Chandler, I didn't kiss her, he did! \ennotmain{To Ross} See what happens when you break the code?
	\switchcolumn
	\charactername{乔伊：}\notmain{对着他的背影大喊}钱德勒，不是我吻的，是他！\notmain{对罗斯}看到违反规矩的下场了吧？
	\switchcolumn*
	\charactername{Ross:} Joey-
	\switchcolumn
	\charactername{罗斯：}乔伊——
	\switchcolumn*
	\charactername{Joey:} Ah! \ennotmain{Points to door} Huh? \ennotmain{Leaves and slams the door}
	\switchcolumn
	\charactername{乔伊：}啊！\notmain{指向门}看到了吧？\notmain{离开，摔上门}
	\switchcolumn*
	\sense{Scene: Central Perk, everyone is there except for Chandler. Rachel is writing something and Monica walks up.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，除了钱德勒所有人都在。瑞秋在写东西，莫妮卡走过去}
	\switchcolumn*
	\charactername{Monica:} Hey.
	\switchcolumn
	\charactername{莫妮卡：}嘿。
	\switchcolumn*
	\charactername{Rachel:} Hey.
	\switchcolumn
	\charactername{瑞秋：}嘿。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{Reading} 'A Woman Undone, by Rachel Karen Green'.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{读}《一个崩溃的女人》，作者瑞秋·卡伦·格林。
	\switchcolumn*
	\charactername{Rachel:} Yeah. Thought I'd give it a shot. I'm still on the first chapter. Now, do you think his 'love stick can be liberated from its denim prison'?
	\switchcolumn
	\charactername{瑞秋：}是啊。想试试写小说。还在写第一章。你觉得“他的爱棍能从牛仔牢笼中解放出来”这句话怎么样？
	\switchcolumn*
	\charactername{Monica:} \ennotmain{Reads} Yeah, I'd say so. And there's no 'j' in 'engorged'.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{读了一遍}嗯，还行。而且“充血的”\notmain{engorged}这个词里没有字母j。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Walks up with her guitar} Hey Rach.
	\switchcolumn
	\charactername{菲比：}\notmain{拿着吉他走过来}嘿，瑞秋。
	\switchcolumn*
	\charactername{Rachel:} Hey.
	\switchcolumn
	\charactername{瑞秋：}嘿。
	\switchcolumn*
	\charactername{Phoebe:} Hello.
	\switchcolumn
	\charactername{菲比：}嗨。
	\switchcolumn*
	\charactername{Monica:} Hello.
	\switchcolumn
	\charactername{莫妮卡：}嗨。
	\switchcolumn*
	\charactername{Phoebe:} Going to the hospital tonight?
	\switchcolumn
	\charactername{菲比：}今晚去医院吗？
	\switchcolumn*
	\charactername{Monica:} No, you?
	\switchcolumn
	\charactername{莫妮卡：}不去，你呢？
	\switchcolumn*
	\charactername{Phoebe:} No, you?
	\switchcolumn
	\charactername{菲比：}不去，你呢？
	\switchcolumn*
	\charactername{Monica:} You just asked me.
	\switchcolumn
	\charactername{莫妮卡：}你刚问过我了。
	\switchcolumn*
	\charactername{Phoebe:} Okay, maybe it was a trick question. \ennotmain{Plays a few chords} Um, Rachel can we do this now?
	\switchcolumn
	\charactername{菲比：}好吧，可能是个陷阱问题。\notmain{弹了几个和弦}呃，瑞秋，现在可以开始了吗？
	\switchcolumn*
	\charactername{Rachel:} Okay. \ennotmain{Writes a little more} I am so hot!
	\switchcolumn
	\charactername{瑞秋：}好。\notmain{又写了几句}我太性感了！
	\switchcolumn*
	\charactername{Joey:} \ennotmain{To Ross, on the couch} Now, here's a picture of my mother and father on their wedding day. Now you tell me she's not a knockout.
	\switchcolumn
	\charactername{乔伊：}\notmain{对沙发上的罗斯说}看，这是我爸妈结婚那天的照片。现在你还说她不是大美女？
	\switchcolumn*
	\charactername{Ross:} I cannot believe we're having this conversation.
	\switchcolumn
	\charactername{罗斯：}我真不敢相信我们在聊这个。
	\switchcolumn*
	\charactername{Joey:} C'mon! Just try to picture her not pregnant, that's all.
	\switchcolumn
	\charactername{乔伊：}拜托！你就想象一下她没怀孕的样子，仅此而已。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{Into microphone} Central Perk is proud to present Miss Phoebe Buffay.
	\switchcolumn
	\charactername{瑞秋：}\notmain{对着麦克风}中央公园咖啡馆荣幸为大家带来菲比·布菲小姐的表演。
	\switchcolumn*
	\charactername{Phoebe:} Thanks. Hi, um, 'kay. I'd like to start with a song that's about a man that I recently met, who's, um, come to be very important to me. \ennotmain{Monica gives her a look} 'Kay. \ennotmain{Sung:}
	\switchcolumn
	\charactername{菲比：}谢谢。嗨，嗯，好。我想先唱一首关于我最近认识的一个男人的歌，他，嗯，对我来说越来越重要了。\notmain{莫妮卡瞪了她一眼}好。\notmain{唱道：}
	\switchcolumn*
	You don't have to be awake to be my man,
	\switchcolumn
	你不必清醒着才能做我的男人，
	\switchcolumn*
	As long as you have brainwaves I'll be there to hold your hand.
	\switchcolumn
	只要你还有脑电波，我就会在你身边握紧你的手。
	\switchcolumn*
	Though we just met the other day,
	\switchcolumn
	虽然我们前几天才相遇，
	\switchcolumn*
	There's something I have got to say...
	\switchcolumn
	但有些话我必须对你说……
	\switchcolumn*
	\ennotmain{She sees Monica sneaking out} Okay, thank you very much, I'm gonna take a short break! \ennotmain{Runs out, knocking over the mike stand}
	\switchcolumn
	\notmain{看到莫妮卡偷偷溜走}好吧，非常感谢大家，我要休息一下！\notmain{跑出去，撞翻了麦克风支架}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{Into mike} Okay, that was Phoebe Buffay, everybody. Woo!
	\switchcolumn
	\charactername{瑞秋：}\notmain{对着麦克风}好了，刚才是菲比·布菲的表演，大家掌声鼓励！哇哦！
	\switchcolumn*
	\ennotmain{Enter Chandler}
	\switchcolumn
	\notmain{钱德勒走进来}
	\switchcolumn*
	\charactername{Chandler:} What was that?
	\switchcolumn
	\charactername{钱德勒：}刚才那是什么？
	\switchcolumn*
	\charactername{Ross:} Oh, uh, Phoebe just started a...
	\switchcolumn
	\charactername{罗斯：}哦，呃，菲比刚开始……
	\switchcolumn*
	\charactername{Chandler:} Yeah, I believe I was talking to Joey, alright there, Mother-Kisser? \ennotmain{Goes to the counter}
	\switchcolumn
	\charactername{钱德勒：}是啊，我想我是在跟乔伊说话，怎么样啊，吻妈狂魔？\notmain{走向吧台}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{Laughing} Mother-Kisser... \ennotmain{Sees Ross's look} I'll shut up.
	\switchcolumn
	\charactername{乔伊：}\notmain{笑着}吻妈狂魔……\notmain{看到罗斯的表情}我闭嘴。
	\switchcolumn*
	\charactername{Ross:} Chandler, can I just say something? I-I know you're still mad at me, I just wanna say that there were two people there that night. Okay? Two sets of lips.
	\switchcolumn
	\charactername{罗斯：}钱德勒，我能说句话吗？我知道你还在生我的气，我只想说那天晚上有两个人。好吧？两双唇。
	\switchcolumn*
	\charactername{Chandler:} Yes, well, I expect this from her. Okay? She's always been a Freudian nightmare.
	\switchcolumn
	\charactername{钱德勒：}是啊，但我对她这种行为早就见怪不怪了。好吧？她一直就是个弗洛伊德式的噩梦。
	\switchcolumn*
	\charactername{Ross:} Okay, well, if she always behaves like this, why don't you say something?
	\switchcolumn
	\charactername{罗斯：}好吧，如果她一直这样，你为什么不说她？
	\switchcolumn*
	\charactername{Chandler:} Because it's complicated, it's complex- Hey, you kissed my mom!
	\switchcolumn
	\charactername{钱德勒：}因为这很复杂，很纠结——嘿，你吻了我妈妈！
	\switchcolumn*
	\ennotmain{People turn to look}
	\switchcolumn
	\notmain{周围的人转头看过来}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{To the rest of Central Perk} We're rehearsing a Greek play.
	\switchcolumn
	\charactername{罗斯：}\notmain{对中央公园咖啡馆的其他人说}我们在排练一部希腊戏剧。
	\switchcolumn*
	\charactername{Chandler:} That's very funny. We done now?
	\switchcolumn
	\charactername{钱德勒：}真有意思。说完了吗？
	\switchcolumn*
	\charactername{Ross:} No! Okay, you mean, you're not gonna talk to her, you're not gonna tell her how you feel?
	\switchcolumn
	\charactername{罗斯：}没有！好吧，你的意思是，你不会跟她谈，不会告诉她你的感受？
	\switchcolumn*
	\charactername{Chandler:} That would be no. Look, just because you played tonsil tennis with my mom doesn't mean you know her. Alright? Trust me, you can't talk to her.
	\switchcolumn
	\charactername{钱德勒：}没错。听着，你跟我妈妈亲嘴不代表你了解她。好吧？相信我，你跟她沟通不了。
	\switchcolumn*
	\charactername{Ross:} Okay, 'you' can't, or \ennotmain{Points to Chandler} you can't? \ennotmain{Chandler grabs his finger} Okay, that's my finger. \ennotmain{Chandler twists it and Ross goes down on one knee} That's, that's my knee. \ennotmain{To Central Perk} Still doing the play. Aaah!
	\switchcolumn
	\charactername{罗斯：}好吧，是“你”沟通不了，还是\notmain{指向钱德勒}你沟通不了？\notmain{钱德勒抓住他的手指}好吧，那是我的手指。\notmain{钱德勒扭了扭他的手指，罗斯单膝跪地}那是我的膝盖。\notmain{对中央公园咖啡馆的人说}还在排练戏剧呢。啊！
	\switchcolumn*
	\sense{Scene: The Coma Guy's Room, Monica bursts in, closely followed by Phoebe. There is no sign of Coma Guy. His bed is empty.}
	\switchcolumn
	\sense{场景：昏迷哥的病房，莫妮卡冲进来，菲比紧随其后。病房里没有昏迷哥的身影，病床是空的}
	\switchcolumn*
	\charactername{Phoebe:} Alright, whadyou do with him?
	\switchcolumn
	\charactername{菲比：}好吧，你把他弄哪儿去了？
	\switchcolumn*
	\ennotmain{There is the sound of a flushing toilet and Coma Guy emerges from the bathroom}
	\switchcolumn
	\notmain{传来冲马桶的声音，昏迷哥从洗手间走出来}
	\switchcolumn*
	\charactername{Monica:} Oh! You're awake!
	\switchcolumn
	\charactername{莫妮卡：}哦！你醒了！
	\switchcolumn*
	\charactername{Phoebe:} Look at you! How, how do you feel?
	\switchcolumn
	\charactername{菲比：}看看你！感觉怎么样？
	\switchcolumn*
	\charactername{Coma Guy:} Uh, a little woozy, but basically okay.
	\switchcolumn
	\charactername{昏迷哥：}呃，有点头晕，但总体还好。
	\switchcolumn*
	\charactername{Monica:} You look good!
	\switchcolumn
	\charactername{莫妮卡：}你看起来状态不错！
	\switchcolumn*
	\charactername{Coma Guy:} I feel good! ...Who are you?
	\switchcolumn
	\charactername{昏迷哥：}我感觉也挺好！……你们是谁？
	\switchcolumn*
	\charactername{Monica:} Oh, sorry.
	\switchcolumn
	\charactername{莫妮卡：}哦，抱歉。
	\switchcolumn*
	\charactername{Phoebe:} I'm Phoebe Buffay.
	\switchcolumn
	\charactername{菲比：}我是菲比·布菲。
	\switchcolumn*
	\charactername{Monica:} I'm Monica Geller. I've been taking care of you.
	\switchcolumn
	\charactername{莫妮卡：}我是莫妮卡·盖勒。一直是我在照顾你。
	\switchcolumn*
	\charactername{Phoebe:} Well, we both have.
	\switchcolumn
	\charactername{菲比：}好吧，我们俩都有照顾你。
	\switchcolumn*
	\charactername{Coma Guy:} So, the Etch-a-Sketch is from you guys?
	\switchcolumn
	\charactername{昏迷哥：}所以，那个画板是你们送的？
	\switchcolumn*
	\charactername{Phoebe:} Well, actually it's just from me.
	\switchcolumn
	\charactername{菲比：}其实就我一个人送的。
	\switchcolumn*
	\charactername{Monica:} I got you the foot massager.
	\switchcolumn
	\charactername{莫妮卡：}足部按摩器是我送的。
	\switchcolumn*
	\charactername{Phoebe:} You know who shaved you? That was me.
	\switchcolumn
	\charactername{菲比：}你知道谁给你刮的胡子吗？是我。
	\switchcolumn*
	\charactername{Monica:} I read to you.
	\switchcolumn
	\charactername{莫妮卡：}我给你读报纸。
	\switchcolumn*
	\charactername{Phoebe:} I sang. \ennotmain{To Monica} Hah!
	\switchcolumn
	\charactername{菲比：}我给你唱歌。\notmain{对莫妮卡}哈！
	\switchcolumn*
	\charactername{Coma Guy:} Well,... thanks.
	\switchcolumn
	\charactername{昏迷哥：}好吧……谢谢你们。
	\switchcolumn*
	\charactername{Monica:} Oh, my pleasure.
	\switchcolumn
	\charactername{莫妮卡：}哦，不客气。
	\switchcolumn*
	\charactername{Phoebe:} You're welcome.
	\switchcolumn
	\charactername{菲比：}不客气。
	\switchcolumn*
	\charactername{Coma Guy:} So. I guess I'll see you around.
	\switchcolumn
	\charactername{昏迷哥：}那。以后再见吧。
	\switchcolumn*
	\charactername{Phoebe:} What, that's it?
	\switchcolumn
	\charactername{菲比：}什么，就这样？
	\switchcolumn*
	\charactername{Monica:} "See you around?"
	\switchcolumn
	\charactername{莫妮卡：}“以后再见”？
	\switchcolumn*
	\charactername{Coma Guy:} Well, what do you want me to say?
	\switchcolumn
	\charactername{昏迷哥：}不然你们想让我说什么？
	\switchcolumn*
	\charactername{Monica:} Oh, I don't know. Maybe, um, "That was nice?" Admit something to me? "I'll call you?"
	\switchcolumn
	\charactername{莫妮卡：}哦，我不知道。比如，“那段时间谢谢你们”？跟我坦白点什么？“我会给你打电话”？
	\switchcolumn*
	\charactername{Coma Guy:} Alright, I'll call you.
	\switchcolumn
	\charactername{昏迷哥：}好吧，我会给你打电话。
	\switchcolumn*
	\charactername{Phoebe:} I don't think you mean that.
	\switchcolumn
	\charactername{菲比：}我觉得你不是真心的。
	\switchcolumn*
	\charactername{Monica:} This is so typical. Y'know, we give, and we give, and we give. And then- we just get nothing back! And then one day, y'know, it's just, you wake up, and "See you around!" Let's go, Phoebe.
	\switchcolumn
	\charactername{莫妮卡：}真是太典型了。你知道吗，我们一味地付出，付出，付出。然后——什么回报都没有！有一天你醒了，就一句“以后再见”！走吧，菲比。
	\switchcolumn*
	\charactername{Phoebe:} Y'know what? We thought you were different. But I guess it was just the coma.
	\switchcolumn
	\charactername{菲比：}你知道吗？我们以为你与众不同。但看来只是因为你昏迷了而已。
	\switchcolumn*
	\sense{Scene: Chandler and Joey's Chandler is talking with his mom.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，钱德勒在跟他妈妈说话}
	\switchcolumn*
	\charactername{Mrs. Bing:} Car's waiting downstairs, I just wanted to drop off these copies of my book for your friends. Anything you want from Lisbon?
	\switchcolumn
	\charactername{宾夫人：}车在楼下等着呢，我只是来给你的朋友们送几本我的书。想让我从里斯本给你带点什么吗？
	\switchcolumn*
	\charactername{Chandler:} No, just knowing you're gonna be there is enough.
	\switchcolumn
	\charactername{钱德勒：}不用，知道你要去那儿就够了。\notmain{反讽}
	\switchcolumn*
	\charactername{Mrs. Bing:} Alright, well, be good, I love you. \ennotmain{Kisses him and goes to leave}
	\switchcolumn
	\charactername{宾夫人：}好吧，乖，我爱你。\notmain{吻了吻他，准备离开}
	\switchcolumn*
	\charactername{Chandler:} You kissed my best Ross! ...Or something to that effect.
	\switchcolumn
	\charactername{钱德勒：}你吻了我最好的朋友罗斯！……大概是这个意思。
	\switchcolumn*
	\charactername{Mrs. Bing:} \ennotmain{Reentering} O-kay. Look, it, it was stupid.
	\switchcolumn
	\charactername{宾夫人：}\notmain{走回来}好——吧。听着，那是件蠢事。
	\switchcolumn*
	\charactername{Chandler:} Really stupid.
	\switchcolumn
	\charactername{钱德勒：}非常蠢。
	\switchcolumn*
	\charactername{Mrs. Bing:} Really stupid. And I don't even know how it happened. I'm sorry, honey, I promise it will never happen again. Are we okay now?
	\switchcolumn
	\charactername{宾夫人：}非常蠢。我都不知道怎么会发生这种事。对不起，亲爱的，我保证不会再发生了。我们现在和好了吗？
	\switchcolumn*
	\charactername{Chandler:} Yeah. No. No...
	\switchcolumn
	\charactername{钱德勒：}和好。没有。没有……
	\switchcolumn*
	\sense{Cut to the hallway, Joey is listening to Chandler and his mom's conversation through the door as Ross walks up.}
	\switchcolumn
	\sense{镜头切换到走廊，乔伊正贴在门上听钱德勒和他妈妈说话，罗斯走过来}
	\switchcolumn*
	\charactername{Ross:} Ah, the forbidden love of a man and his door.
	\switchcolumn
	\charactername{罗斯：}啊，一个男人和他的门之间的禁忌之爱。\notmain{调侃乔伊偷听}
	\switchcolumn*
	\charactername{Joey:} Shh. He did it. He told her off, and not just about the kiss, about everything.
	\switchcolumn
	\charactername{乔伊：}嘘。他做到了。他跟她摊牌了，不只是关于那个吻，还有所有事。
	\switchcolumn*
	\charactername{Ross:} You're kidding.
	\switchcolumn
	\charactername{罗斯：}你在开玩笑吧。
	\switchcolumn*
	\charactername{Joey:} No, no. He said "When are you gonna grow up and start being a mom?"
	\switchcolumn
	\charactername{乔伊：}没有，真的。他说“你什么时候才能长大，像个真正的妈妈？”
	\switchcolumn*
	\charactername{Ross:} Wow!
	\switchcolumn
	\charactername{罗斯：}哇！
	\switchcolumn*
	\charactername{Joey:} Then she came back with "The question is, when are you gonna grow up and realise I have a bomb?"
	\switchcolumn
	\charactername{乔伊：}然后她回了一句“问题是，你什么时候才能长大，意识到我有一颗炸弹？”
	\switchcolumn*
	\charactername{Ross:} 'Kay, wait a minute, are you sure she didn't say "When are you gonna grow up and realise I am your mom?"
	\switchcolumn
	\charactername{罗斯：}好吧，等一下，你确定她不是说“问题是，你什么时候才能长大，意识到我是你妈妈？”
	\switchcolumn*
	\charactername{Joey:} That makes more sense.
	\switchcolumn
	\charactername{乔伊：}这样更合理。
	\switchcolumn*
	\charactername{Ross:} So, what's going on now?
	\switchcolumn
	\charactername{罗斯：}那现在怎么样了？
	\switchcolumn*
	\charactername{Joey:} I dunno, I've been standing here spelling it out for you! \ennotmain{Goes back to the door} I don't hear anything. Oh, wait, wait, wait. \ennotmain{Looks through the spyhole}
	\switchcolumn
	\charactername{乔伊：}我不知道，我一直站在这儿跟你解释呢！\notmain{回到门前}没声音了。哦，等等，等等。\notmain{透过猫眼往里看}
	\switchcolumn*
	\charactername{Ross:} Whaddya see?
	\switchcolumn
	\charactername{罗斯：}你看到什么了？
	\switchcolumn*
	\charactername{Joey:} Hard to tell, they're so tiny and upside-down. Wait, wait. They're walking away... they're walking away... No, no they're not, they're coming right at us! Run! Run!
	\switchcolumn
	\charactername{乔伊：}看不太清，里面的人又小又倒过来。等等，等等。他们在走开……他们在走开……不，不对，他们正朝我们走来！跑！跑！
	\switchcolumn*
	\ennotmain{Joey runs off down the hall. Ross tries Monica and Rachel's apartment, but it is locked so he has to stand in the hall and pretend he wasn't listening. Chandler and his mom come out}
	\switchcolumn
	\notmain{乔伊沿着走廊跑掉了。罗斯试图进莫妮卡和瑞秋的公寓，但门锁着，所以他只能站在走廊里，假装没偷听。钱德勒和他妈妈走出来}
	\switchcolumn*
	\charactername{Mrs. Bing:} You okay, kiddo?
	\switchcolumn
	\charactername{宾夫人：}你没事吧，孩子？
	\switchcolumn*
	\charactername{Chandler:} Yeah, okay.
	\switchcolumn
	\charactername{钱德勒：}嗯，没事。
	\switchcolumn*
	\charactername{Mrs. Bing:} Alright. \ennotmain{Kisses him}
	\switchcolumn
	\charactername{宾夫人：}好吧。\notmain{吻了吻他}
	\switchcolumn*
	\charactername{Chandler:} Nice save.
	\switchcolumn
	\charactername{钱德勒：}圆场救得不错。
	\switchcolumn*
	\ennotmain{She walks down the hall}
	\switchcolumn
	\notmain{她沿着走廊走开}
	\switchcolumn*
	\charactername{Ross:} \ennotmain{Very politely} Mrs. Bing.
	\switchcolumn
	\charactername{罗斯：}\notmain{非常礼貌地}宾夫人。
	\switchcolumn*
	\charactername{Mrs. Bing:} Mr. Geller.
	\switchcolumn
	\charactername{宾夫人：}盖勒先生。
	\switchcolumn*
	\ennotmain{She leaves}
	\switchcolumn
	\notmain{她离开了}
	\switchcolumn*
	\ennotmain{Ross knocks on Monica and Rachel's door}
	\switchcolumn
	\notmain{罗斯敲莫妮卡和瑞秋的门}
	\switchcolumn*
	\charactername{Chandler:} Hey.
	\switchcolumn
	\charactername{钱德勒：}嘿。
	\switchcolumn*
	\charactername{Ross:} You mean that?
	\switchcolumn
	\charactername{罗斯：}你是认真的吗？\notmain{指和好}
	\switchcolumn*
	\charactername{Chandler:} Yeah, why not. \ennotmain{They shake hands} So I told her.
	\switchcolumn
	\charactername{钱德勒：}是啊，为什么不呢。\notmain{两人握手}我跟她谈了。
	\switchcolumn*
	\charactername{Ross:} Yeah? How'd it go?
	\switchcolumn
	\charactername{罗斯：}是吗？怎么样？
	\switchcolumn*
	\charactername{Chandler:} Awful. Awful. Couldn'ta gone worse.
	\switchcolumn
	\charactername{钱德勒：}糟透了。糟透了。不能更糟了。
	\switchcolumn*
	\charactername{Ross:} Well, howdya feel?
	\switchcolumn
	\charactername{罗斯：}那你感觉怎么样？
	\switchcolumn*
	\charactername{Chandler:} Pretty good! I told her.
	\switchcolumn
	\charactername{钱德勒：}挺不错的！我跟她谈了。
	\switchcolumn*
	\charactername{Ross:} Well, see? So, maybe it wasn't such a bad idea, y'know, me kissing your mom, uh? Huh? \ennotmain{Wags his finger at Chandler, then puts it down} But.. we don't have to go down that road.
	\switchcolumn
	\charactername{罗斯：}你看？所以，或许我吻你妈妈也不是什么坏事，对吧？对吧？\notmain{对着钱德勒摇了摇手指，然后放下}不过……我们不用再提这事了。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Rachel is handing out copies of her book to the gang.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，瑞秋给大家分发她写的书}
	\switchcolumn*
	\charactername{Rachel:} Okay. Now this is just the first chapter, and I want your absolute honest opinion. Oh, oh, and on page two, he's not 'reaching for her heaving beasts'.
	\switchcolumn
	\charactername{瑞秋：}好了。这只是第一章，我想要你们最真实的意见。哦，对了，第二章里，他不是在“伸手去摸她起伏的猛兽”\notmain{指胸部，用词不当}。
	\switchcolumn*
	\charactername{Monica:} What's a 'niffle'?
	\switchcolumn
	\charactername{莫妮卡：}“niffle”是什么意思？\notmain{拼写错误}
	\switchcolumn*
	\charactername{Joey:} You usually find them on the 'heaving beasts'.
	\switchcolumn
	\charactername{乔伊：}通常在“起伏的猛兽”上能找到。
	\switchcolumn*
	\charactername{Rachel:} Alright, alright, so I'm not a great typist...
	\switchcolumn
	\charactername{瑞秋：}好吧，好吧，我打字不太好……
	\switchcolumn*
	\charactername{Ross:} Wait, did you get to the part about his 'huge throbbing pens'? Tell ya, you don't wanna be around when he starts writing with those!
	\switchcolumn
	\charactername{罗斯：}等等，你们看到“他那巨大跳动的钢笔”那段了吗？跟你们说，他用那些钢笔写字的时候，你们可别在旁边！\notmain{调侃瑞秋用词不当，pens应指男性器官}
	\switchcolumn*
	\charactername{Rachel:} Alright, that's it! Give it back! That's it!
	\switchcolumn
	\charactername{瑞秋：}好了，够了！还给我！到此为止！
	\switchcolumn*
	\charactername{All:} Nooo!
	\switchcolumn
	\charactername{众人：}不要啊！
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage