\begin{paracol}{2}
	\sense{Scene: Monica and Rachel's, Chandler walks in and starts raiding the fridge. Then Rachel comes out of the shower with a towel wrapped round her waist, drying herself with another towel. Chandler and Rachel startle each other and she drops the towel for a second and snatches the rug off the couch.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，钱德勒走进来开始翻冰箱。随后瑞秋裹着浴巾从浴室出来，正用另一条毛巾擦身体。钱德勒和瑞秋吓了对方一跳，她的浴巾掉了一瞬间，接着她一把扯过沙发上的小毯子裹住自己。}
	\switchcolumn*
	\charactername{Rachel:} That is IT! You just barge in here, you don't knock
	\switchcolumn
	\charactername{瑞秋：}够了！你就这么闯进来，连门都不敲！
	\switchcolumn*
	\charactername{Chandler:} I'm sorry!
	\switchcolumn
	\charactername{钱德勒：}对不起！
	\switchcolumn*
	\charactername{Rachel:} You have no respect for anybody's privacy!
	\switchcolumn
	\charactername{瑞秋：}你根本不尊重别人的隐私！
	\switchcolumn*
	\charactername{Chandler:} Rachel, wait, wait.
	\switchcolumn
	\charactername{钱德勒：}瑞秋，等等，等等。
	\switchcolumn*
	\charactername{Rachel:} No, you wait! This is ridiculous!
	\switchcolumn
	\charactername{瑞秋：}不，该你等！这太荒谬了！
	\switchcolumn*
	\charactername{Chandler:} Can I just say one thing?
	\switchcolumn
	\charactername{钱德勒：}我能说一句话吗？
	\switchcolumn*
	\charactername{Rachel:} What? What?!
	\switchcolumn
	\charactername{瑞秋：}什么？什么话？！
	\switchcolumn*
	\charactername{Chandler:} That's a relatively open weave and I can still see your... nipular areas.
	\switchcolumn
	\charactername{钱德勒：}这毯子的编织孔还挺大的，我还能看到你的……两点部位。
	\switchcolumn*
	\charactername{Rachel:} Oh!!
	\switchcolumn
	\charactername{瑞秋：}哦！！
	\switchcolumn*
	\ennotmain{She storms off}
	\switchcolumn
	\notmain{她怒气冲冲地走开}
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, Phoebe is there with her boyfriend Roger, talking to Rachel and Monica.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，菲比和她的男朋友罗杰在一起，正和瑞秋、莫妮卡聊天。}
	\switchcolumn*
	\charactername{Phoebe:} Oh, honey, honey, tell them the story about your patient who thinks things are, like, other things. Y'know? Like, the phone rings and she takes a shower.
	\switchcolumn
	\charactername{菲比：}哦，亲爱的，亲爱的，跟她们说说你那个病人的事，她总把东西看成别的东西。你知道吗？比如电话响了，她却去洗澡。
	\switchcolumn*
	\charactername{Roger:} That's pretty much it.
	\switchcolumn
	\charactername{罗杰：}差不多就是这样。
	\switchcolumn*
	\charactername{Phoebe:} Oops!
	\switchcolumn
	\charactername{菲比：}哎呀！
	\switchcolumn*
	\charactername{Roger:} But you tell it really well, sweetie.
	\switchcolumn
	\charactername{罗杰：}不过你讲得真的很好，亲爱的。
	\switchcolumn*
	\charactername{Phoebe:} Thanks. Okay, now go away so we can talk about you.
	\switchcolumn
	\charactername{菲比：}谢谢。好了，你先走开，我们要聊聊你。
	\switchcolumn*
	\charactername{Roger:} Okay. I'll miss you.
	\switchcolumn
	\charactername{罗杰：}好的。我会想你的。
	\switchcolumn*
	\charactername{Phoebe:} Isn't he great?
	\switchcolumn
	\charactername{菲比：}他是不是超棒？
	\switchcolumn*
	\charactername{Rachel:} He's so cute! And he seems to like you so much.
	\switchcolumn
	\charactername{瑞秋：}他好可爱！而且看起来超级喜欢你的。
	\switchcolumn*
	\charactername{Phoebe:} I know, I know. So sweet... and so complicated. And for a shrink, he's not too shrinky, y'know?
	\switchcolumn
	\charactername{菲比：}我知道，我知道。人超好的……而且还挺复杂的。作为一个心理医生，他倒不会显得太“心理医生范儿”，你懂吧？
	\switchcolumn*
	\charactername{Monica:} So, you think you'll do it on his couch?
	\switchcolumn
	\charactername{莫妮卡：}那你打算在他的诊疗沙发上那个吗？
	\switchcolumn*
	\charactername{Phoebe:} Oh, I don't know, I don't know. I think that's a little weird, y'know? Vinyl.
	\switchcolumn
	\charactername{菲比：}哦，我不知道，我不知道。我觉得有点怪，你懂吗？那沙发是乙烯基材质的。
	\switchcolumn*
	\charactername{Rachel:} Okaaay. \ennotmain{To the guys, on the couch} Any of you guys want anything else?
	\switchcolumn
	\charactername{瑞秋：}好吧。\notmain{对沙发上的男生们说}你们谁还想再要点什么吗？
	\switchcolumn*
	\charactername{Chandler:} Oh, yes, could I have one of those. \ennotmain{Points}
	\switchcolumn
	\charactername{钱德勒：}哦，要的，能给我一个那个吗？\notmain{指了指}
	\switchcolumn*
	\charactername{Rachel:} No, I'm sorry, we're all out of those. Anybody else?
	\switchcolumn
	\charactername{瑞秋：}不行哦，不好意思，那个已经卖完了。其他人还要吗？
	\switchcolumn*
	\charactername{Chandler:} Okay.
	\switchcolumn
	\charactername{钱德勒：}好吧。
	\switchcolumn*
	\charactername{Roger:} Did I, uh, did I miss something?
	\switchcolumn
	\charactername{罗杰：}我……我是不是错过了什么？
	\switchcolumn*
	\charactername{Chandler:} No, she's still upset because I saw her boobies.
	\switchcolumn
	\charactername{钱德勒：}也没什么，她还在为我看到她的胸部生气呢。
	\switchcolumn*
	\charactername{Ross:} You what? Wh what were you doing seeing her boobies?
	\switchcolumn
	\charactername{罗斯：}你什么？你怎么会看到她的胸部？
	\switchcolumn*
	\charactername{Chandler:} It was an accident. Not like I was across the street with a telescope and a box of donuts.
	\switchcolumn
	\charactername{钱德勒：}纯属意外。又不是我拿着望远镜和一盒甜甜圈躲在街对面偷看。
	\switchcolumn*
	\charactername{Rachel:} Okay, okay, could we change the subject, please?
	\switchcolumn
	\charactername{瑞秋：}好了好了，我们能换个话题吗？拜托了？
	\switchcolumn*
	\charactername{Phoebe:} Yeah, 'cause hello, these are not her boobies, these are her breasts.
	\switchcolumn
	\charactername{菲比：}对啊，话说回来，这可不是“胸部”的随便说法，这叫“乳房”。
	\switchcolumn*
	\charactername{Rachel:} Okay, Pheebs, I was hoping for more of a change.
	\switchcolumn
	\charactername{瑞秋：}好吧，菲比，我希望换个更彻底的话题。
	\switchcolumn*
	\charactername{Chandler:} Y'know, I don't know why you're so embarrassed, they were very nice boobies.
	\switchcolumn
	\charactername{钱德勒：}说真的，我不明白你有什么好尴尬的，那对胸部挺好看的啊。
	\switchcolumn*
	\charactername{Rachel:} Nice? They were nice. I mean, that's it? I mean, mittens are nice.
	\switchcolumn
	\charactername{瑞秋：}好看？就只是好看？我的意思是，仅此而已？连手套都能说“好看”呢。
	\switchcolumn*
	\charactername{Chandler:} Okaaay, \ennotmain{Gestures} rock, hard place, me.
	\switchcolumn
	\charactername{钱德勒：}好吧，\notmain{做手势}我这是进退两难啊。
	\switchcolumn*
	\charactername{Roger:} You're so funny! He's really funny! I wouldn't wanna be there when when the laughter stops.
	\switchcolumn
	\charactername{罗杰：}你太搞笑了！他真的好幽默！不过我可不想等到他不搞笑的时候待在他身边。
	\switchcolumn*
	\charactername{Chandler:} Whoah whoah, back up there, Sparky. What'd you mean by that?
	\switchcolumn
	\charactername{钱德勒：}喂喂喂，等一下，小家伙。你这话什么意思？
	\switchcolumn*
	\charactername{Roger:} Oh, just seems as though that maybe you have intimacy issues. Y'know, that you use your humour as a way of keeping people at a distance.
	\switchcolumn
	\charactername{罗杰：}哦，我只是觉得你可能有亲密关系障碍。你知道吗？你用幽默来和别人保持距离。
	\switchcolumn*
	\charactername{Chandler:} Huh.
	\switchcolumn
	\charactername{钱德勒：}哈。
	\switchcolumn*
	\charactername{Roger:} I mean hey! I just met you, I don't know you from Adam. ...Only child, right? Parents divorced before you hit puberty.
	\switchcolumn
	\charactername{罗杰：}我是说！我刚认识你，对你一无所知。……独生子，对吧？青春期前父母就离婚了。
	\switchcolumn*
	\charactername{Chandler:} Uhhuh, how did you know that?
	\switchcolumn
	\charactername{钱德勒：}嗯……你怎么知道的？
	\switchcolumn*
	\charactername{Roger:} It's textbook.
	\switchcolumn
	\charactername{罗杰：}这都是教科书级别的案例。
	\switchcolumn*
	\ennotmain{Joey enters with his dad}
	\switchcolumn
	\notmain{乔伊和他爸爸一起走进来}
	\switchcolumn*
	\charactername{Joey:} Hey you guys. Hey, you all know my dad, right?
	\switchcolumn
	\charactername{乔伊：}嘿，大家好。嘿，你们都认识我爸爸吧？
	\switchcolumn*
	\charactername{All:} Hey! Hey, Mr. Trib!
	\switchcolumn
	\charactername{众人：}嘿！嘿，崔布先生！
	\switchcolumn*
	\charactername{Monica:} Hey, how long are you in the city?
	\switchcolumn
	\charactername{莫妮卡：}嘿，你要在城里待多久？
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Just for a coupla days. I got a job midtown. I figure I'm better off staying with the kid than hauling my ass back and forth on the ferry. \ennotmain{Sees Roger} I don't know this one.
	\switchcolumn
	\charactername{崔布亚尼先生：}就待几天。我在市中心有份工作。我觉得住在这孩子这儿比来回坐渡轮折腾好多了。\notmain{看到罗杰}这位我不认识。
	\switchcolumn*
	\charactername{Phoebe:} Oh, this is my friend Roger.
	\switchcolumn
	\charactername{菲比：}哦，这是我的朋友罗杰。
	\switchcolumn*
	\charactername{Roger:} Hi.
	\switchcolumn
	\charactername{罗杰：}你好。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Hey, hey. Good to meet you, Roger.
	\switchcolumn
	\charactername{崔布亚尼先生：}嘿，嘿。很高兴认识你，罗杰。
	\switchcolumn*
	\charactername{Roger:} You too, sir.
	\switchcolumn
	\charactername{罗杰：}我也很高兴认识你，先生。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} \ennotmain{To Phoebe} What happened to the, uh, puppet guy?
	\switchcolumn
	\charactername{崔布亚尼先生：}\notmain{对菲比说}之前那个玩木偶的家伙呢？
	\switchcolumn*
	\charactername{Joey:} Dad, dad. \ennotmain{Shakes his head}
	\switchcolumn
	\charactername{乔伊：}爸，爸。\notmain{摇摇头}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Oh, 'scuse me. So Ross, uh, how's the wife? \ennotmain{Ross whines and lays his head on Chandler's shoulder} Off there too, uh? Uh, Chandler, quick, say something funny!
	\switchcolumn
	\charactername{崔布亚尼先生：}哦，抱歉。那罗斯，呃，你妻子怎么样了？\notmain{罗斯哼了一声，把头靠在钱德勒的肩膀上}也吹了，是吧？呃，钱德勒，快，说点好笑的！
	\switchcolumn*
	\ennotmain{Chandler stays stonefaced}
	\switchcolumn
	\notmain{钱德勒面无表情}
	\switchcolumn*
	\sense{Scene: Chandler and Joey's, Mr. Tribbiani is on the phone.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，崔布亚尼先生正在打电话。}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Gotta go. I miss you too, I love you, but it's getting real late now
	\switchcolumn
	\charactername{崔布亚尼先生：}得挂了。我也想你，我爱你，但现在真的很晚了。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{Snatches the phone} Hey Ma. Listen, I made the appointment with Dr. Bazida, and... Excuse me? \ennotmain{To his dad} Did you know this isn't Ma?
	\switchcolumn
	\charactername{乔伊：}\notmain{抢过电话}嘿，妈。听着，我跟巴齐达医生约好了，而且……等等？\notmain{对他爸爸说}你知道这不是妈吗？
	\switchcolumn*
	\ennotmain{His dad nods. Cut to later. Joey is chopping mushrooms}
	\switchcolumn
	\notmain{他爸爸点点头。镜头切到稍后。乔伊正在切蘑菇}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Her name's Ronni. She's a pet mortician.
	\switchcolumn
	\charactername{崔布亚尼先生：}她叫罗尼。是个宠物殡葬师。
	\switchcolumn*
	\charactername{Joey:} Sure. So how long you been... \ennotmain{Goes back to chopping}
	\switchcolumn
	\charactername{乔伊：}好吧。那你们在一起……多久了？\notmain{继续切蘑菇}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Remember when you were a little kid, I used to take you to the navy yard and show you the big ships?
	\switchcolumn
	\charactername{崔布亚尼先生：}还记得你小时候，我带你去海军造船厂看那些大船吗？
	\switchcolumn*
	\charactername{Joey:} Since then?!
	\switchcolumn
	\charactername{乔伊：}从那时候就开始了？！
	\switchcolumn*
	\charactername{Mr. Tribbiani:} No, it's only been six years. I just wanted to put a nice memory in your head so you'd know that I wasn't always such a terrible guy. ...Joe. Y'ever been in love?
	\switchcolumn
	\charactername{崔布亚尼先生：}不是啦，才六年而已。我只是想让你回忆起一段美好的时光，让你知道我也不总是这么糟糕的人。……乔伊。你爱过别人吗？
	\switchcolumn*
	\charactername{Joey:} ...I d'know.
	\switchcolumn
	\charactername{乔伊：}……我不知道。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Then y'haven't. You're burning your tomatoes.
	\switchcolumn
	\charactername{崔布亚尼先生：}那你就是没爱过。你的西红柿要糊了。
	\switchcolumn*
	\charactername{Joey:} You're one to talk. \ennotmain{Puts the mushrooms in a saucepan}
	\switchcolumn
	\charactername{乔伊：}你还好意思说。\notmain{把蘑菇放进平底锅里}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Joe, your dad's in love big time. And the worst part of it is, it's with two different women.
	\switchcolumn
	\charactername{崔布亚尼先生：}乔伊，你爸爸这次是深陷爱河了。最糟糕的是，我爱上了两个不同的女人。
	\switchcolumn*
	\charactername{Joey:} Oh man. Please tell me one of 'em is Ma.
	\switchcolumn
	\charactername{乔伊：}哦，天呐。拜托告诉我其中一个是妈。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Of course, course one of 'em's Ma. What's the matter with you.
	\switchcolumn
	\charactername{崔布亚尼先生：}当然了，当然其中一个是你妈。你想什么呢。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Joey is lamenting to everyone about his dad's affair.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，乔伊正在向大家哀叹他爸爸的婚外情。}
	\switchcolumn*
	\charactername{Joey:} It's like if you woke up one day and found out your dad was leading this double life. He's like actually some spy, working for the C.I.A. \ennotmain{Considers} That'd be cool.... This blows!
	\switchcolumn
	\charactername{乔伊：}这就像有一天你醒来，发现你爸爸过着双重生活。他就像个间谍，为中央情报局工作。\notmain{想了想}那其实还挺酷的……不过现在这事太糟了！
	\switchcolumn*
	\charactername{Rachel:} I know, I mean, why can't parents just stay parents? \ennotmain{She walks over near Chandler and his gaze stays very obviously on her chest} Why do they have to become people? Why do they have... \ennotmain{Notices Chandler} Why can't you stop staring at my breasts?
	\switchcolumn
	\charactername{瑞秋：}我懂，我的意思是，为什么父母就不能一直只是父母呢？\notmain{她走到钱德勒身边，钱德勒的目光明显一直停留在她的胸部}为什么他们非要变成有自己复杂生活的“普通人”呢？为什么他们要……\notmain{注意到钱德勒的目光}你能不能别盯着我的乳房看？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Without looking up} What? \ennotmain{Looks up} What?
	\switchcolumn
	\charactername{钱德勒：}\notmain{没抬头}什么？\notmain{抬头}什么？
	\switchcolumn*
	\charactername{Rachel:} Did you not get a good enough look the other day?
	\switchcolumn
	\charactername{瑞秋：}前几天你还没看够吗？
	\switchcolumn*
	\charactername{Ross:} Alright, alright. We're all adults here, there's only one way to resolve this. Since you saw her boobies, I think, uh, you're gonna have to show her your peepee.
	\switchcolumn
	\charactername{罗斯：}好了好了。我们都是成年人了，解决这事只有一个办法。既然你看到了她的胸部，我觉得，呃，你也得让她看看你的小弟弟。
	\switchcolumn*
	\charactername{Chandler:} Y'know, I don't see that happening?
	\switchcolumn
	\charactername{钱德勒：}要我说，这事没戏。
	\switchcolumn*
	\charactername{Rachel:} C'mon, he's right. Tit for tat.
	\switchcolumn
	\charactername{瑞秋：}拜托，他说得对。一报还一报嘛。
	\switchcolumn*
	\charactername{Chandler:} Well I'm not showing you my 'tat.'
	\switchcolumn
	\charactername{钱德勒：}反正我不会让你看我的“那个”。
	\switchcolumn*
	\ennotmain{Door buzzer goes}
	\switchcolumn
	\notmain{门铃响了}
	\switchcolumn*
	\charactername{Monica:} Hello?
	\switchcolumn
	\charactername{莫妮卡：}喂？
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Intercom} It's Phoebe.
	\switchcolumn
	\charactername{菲比：}\notmain{通过对讲机}是我，菲比。
	\switchcolumn*
	\charactername{Roger:} \ennotmain{Intercom} And Rog.
	\switchcolumn
	\charactername{罗杰：}\notmain{通过对讲机}还有罗杰。
	\switchcolumn*
	\charactername{Monica:} C'mon up.
	\switchcolumn
	\charactername{莫妮卡：}上来吧。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Sarcastic} Oh, good. Rog is here.
	\switchcolumn
	\charactername{钱德勒：}\notmain{讽刺地}哦，太好了。罗杰来了。
	\switchcolumn*
	\charactername{Joey:} What's the matter with Rog?
	\switchcolumn
	\charactername{乔伊：}罗杰怎么了？
	\switchcolumn*
	\charactername{Ross:} Yeah.
	\switchcolumn
	\charactername{罗斯：}就是啊。
	\switchcolumn*
	\charactername{Chandler:} Oh, it's nothing, it's a little thing... I hate that guy.
	\switchcolumn
	\charactername{钱德勒：}哦，也没什么，就是件小事……我讨厌那家伙。
	\switchcolumn*
	\charactername{Ross:} What, so he was a little analytical. That's what he does, y'know? C'mon, he's not that bad.
	\switchcolumn
	\charactername{罗斯：}什么呀，他就是有点爱分析而已。这是他的工作嘛，你懂的？拜托，他没那么糟。
	\switchcolumn*
	\ennotmain{Cut to Chandler, Ross and Roger sitting at the table. Ross is upset}
	\switchcolumn
	\notmain{镜头切到钱德勒、罗斯和罗杰坐在桌子旁。罗斯很沮丧}
	\switchcolumn*
	\charactername{Ross:} Y'see, that's where you're wrong. Why would I marry her if I thought on any level that that she was a lesbian?
	\switchcolumn
	\charactername{罗斯：}你看，你错了。如果我哪怕有一点点觉得她是女同性恋，我怎么会娶她呢？
	\switchcolumn*
	\charactername{Roger:} I dunno. Maybe you wanted your marriage to fail.
	\switchcolumn
	\charactername{罗杰：}我不知道。也许你想让你的婚姻失败。
	\switchcolumn*
	\charactername{Ross:} Why? Why would I why? Why? Why? Why?
	\switchcolumn
	\charactername{罗斯：}为什么？我为什么要……为什么？为什么？为什么？为什么？
	\switchcolumn*
	\charactername{Roger:} I don't know. Maybe maybe low self-esteem, maybe maybe to compensate for overshadowing a sibling, maybe you...
	\switchcolumn
	\charactername{罗杰：}我不知道。也许是自卑，也许是想弥补自己盖过兄弟姐妹风头的愧疚，也许你……
	\switchcolumn*
	\charactername{Monica:} Wait-wait, go back to that sibling thing.
	\switchcolumn
	\charactername{莫妮卡：}等等等等，回到兄弟姐妹那点。
	\switchcolumn*
	\charactername{Roger:} Well, I don't know. I mean, it's conceivable that you wanted to sabotage your marriage so that the sibling would feel less of a failure in the eyes of the parents.
	\switchcolumn
	\charactername{罗杰：}嗯，我不知道。我的意思是，有可能你想破坏自己的婚姻，这样在父母眼里，你的兄弟姐妹就不会显得那么失败了。
	\switchcolumn*
	\charactername{Ross:} That that's ridiculous! I don't feel guilty for her failures!
	\switchcolumn
	\charactername{罗斯：}这……这太荒谬了！我才不为她的失败感到愧疚呢！
	\switchcolumn*
	\charactername{Monica:} Oh! So you think I'm a failure!
	\switchcolumn
	\charactername{莫妮卡：}哦！所以你觉得我是个失败者！
	\switchcolumn*
	\charactername{Phoebe:} Isn't he good?
	\switchcolumn
	\charactername{菲比：}他是不是很厉害？
	\switchcolumn*
	\charactername{Ross:} Nonono, that that's not what I was saying...
	\switchcolumn
	\charactername{罗斯：}不不不，我不是那个意思……
	\switchcolumn*
	\charactername{Monica:} Y'know, all these years, I thought you were on my side. But maybe what you were doing was sucking up to Mom and Dad so they'd keep liking you better!
	\switchcolumn
	\charactername{莫妮卡：}这么多年来，我一直以为你是站在我这边的。但也许你只是在讨好爸妈，让他们一直更喜欢你！
	\switchcolumn*
	\charactername{Ross:} Hey, I married a lesbian to make you look good!
	\switchcolumn
	\charactername{罗斯：}嘿，我娶了个女同性恋都是为了让你看起来更优秀！
	\switchcolumn*
	\ennotmain{Cut to later. Rachel is in tears}
	\switchcolumn
	\notmain{镜头切到稍后。瑞秋在哭}
	\switchcolumn*
	\charactername{Rachel:} You're right! I mean you're right! It wasn't just the Weebles, but it was the Weeble Play Palace, and and the Weebles' Cruise Ship. Oh, which had this little lifeboat for the Weebles to wobble in.
	\switchcolumn
	\charactername{瑞秋：}你说得对！你说得太对了！不只是威博玩偶，还有威博玩偶乐园，还有……还有威博玩偶游轮。哦，那游轮上还有个小救生艇，让威博玩偶在里面摇摇晃晃的。
	\switchcolumn*
	\charactername{Roger:} That's tough. Tough stuff. C'mon, Pheebs, we're gonna catch that movie, we gotta get going.
	\switchcolumn
	\charactername{罗杰：}太惨了。真的太惨了。好了，菲比，我们要去看电影了，得走了。
	\switchcolumn*
	\charactername{Phoebe:} Oh, okay. Feel better, Rachel, 'kay?
	\switchcolumn
	\charactername{菲比：}哦，好的。瑞秋，开心点，好吗？
	\switchcolumn*
	\charactername{Roger:} Geez, we're gonna be late, sweetie...
	\switchcolumn
	\charactername{罗杰：}天啊，我们要迟到了，亲爱的……
	\switchcolumn*
	\charactername{Phoebe:} Oh, okay. Listen, thanks for everything, Mon.
	\switchcolumn
	\charactername{菲比：}哦，好的。听着，莫妮卡，谢谢你的一切。
	\switchcolumn*
	\charactername{Monica:} You're welcome.
	\switchcolumn
	\charactername{莫妮卡：}不客气。
	\switchcolumn*
	\charactername{Roger:} Listen guys, it was great seeing you again. Mon, um, easy on those cookies, okay? Remember, they're just food, they're not love.
	\switchcolumn
	\charactername{罗杰：}听着，各位，很高兴再次见到你们。莫妮卡，呃，少吃点饼干，好吗？记住，它们只是食物，不是爱。
	\switchcolumn*
	\ennotmain{He shuts the door and Ross and Monica fling cookies at it}
	\switchcolumn
	\notmain{他关上门，罗斯和莫妮卡朝门扔饼干}
	\switchcolumn*
	\charactername{Monica:} Hate that guy! \ennotmain{Throws another cookie}
	\switchcolumn
	\charactername{莫妮卡：}讨厌那家伙！\notmain{又扔了一块饼干}
	\switchcolumn*
	\sense{Scene: The Hallway, Chandler and Joey are just leaving Monica and Rachel's.}
	\switchcolumn
	\sense{场景：走廊，钱德勒和乔伊正要离开莫妮卡和瑞秋的公寓。}
	\switchcolumn*
	\charactername{Joey:} Night, you guys.
	\switchcolumn
	\charactername{乔伊：}晚安，大家。
	\switchcolumn*
	\ennotmain{They notice that a woman is sitting by their door}
	\switchcolumn
	\notmain{他们注意到有个女人坐在他们的门口}
	\switchcolumn*
	\charactername{Chandler:} Oh look, it's the woman we ordered.
	\switchcolumn
	\charactername{钱德勒：}哦，看，我们点的“外卖女人”到了。
	\switchcolumn*
	\charactername{Joey:} Hey. Can, uh, can we help you?
	\switchcolumn
	\charactername{乔伊：}嘿。我们……能帮你什么吗？
	\switchcolumn*
	\charactername{Ronni:} Oh, no thanks, I'm just waiting for, uh, Joey Tribbiani.
	\switchcolumn
	\charactername{罗尼：}哦，不用，谢谢，我就是在等，呃，乔伊·崔布亚尼。
	\switchcolumn*
	\charactername{Joey:} I'm Joey Tribbiani.
	\switchcolumn
	\charactername{乔伊：}我就是乔伊·崔布亚尼。
	\switchcolumn*
	\charactername{Ronni:} Oh no, not you, big Joey. Oh my God, you're so much cuter than your pictures! \ennotmain{Joey stares at her} I-I'm, I'm Ronni....Cheese Nip?
	\switchcolumn
	\charactername{罗尼：}哦不，不是你，大乔伊。哦我的天，你比照片上可爱多了！\notmain{乔伊盯着她}我……我是罗尼……要吃奶酪脆片吗？
	\switchcolumn*
	\charactername{Chandler:} Uh, Joey's having an embolism, but I'd go for a Nip, y'know?
	\switchcolumn
	\charactername{钱德勒：}呃，乔伊已经惊得说不出话了，但我想来一片，你懂的？
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Chandler and Joey's, Ronni is talking to Chandler. Joey's dad is not around.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，罗尼正在和钱德勒聊天。乔伊的爸爸不在场。}
	\switchcolumn*
	\charactername{Ronni:} Now, y'see, most people, when their pets pass on, they want 'em sorta laid out like they're sleeping. But occasionally you get your person who wants them in a pose. Like, chasing their tail, \ennotmain{Demonstrates} or, uh, jumping to catch a frisbee.
	\switchcolumn
	\charactername{罗尼：}你看，大多数人在宠物去世后，都希望宠物摆放得像在睡觉一样。但偶尔也会有人希望宠物摆出特定的姿势。比如，追自己的尾巴，\notmain{演示}或者，呃，跳起来接飞盘。
	\switchcolumn*
	\charactername{Chandler:} Joey, if I go first, I wanna be looking for my keys.
	\switchcolumn
	\charactername{钱德勒：}乔伊，如果我走在你前面\notmain{去世}，我想摆成在找钥匙的姿势。
	\switchcolumn*
	\charactername{Ronni:} That's a good one!
	\switchcolumn
	\charactername{罗尼：}这个主意不错！
	\switchcolumn*
	\ennotmain{Joey's dad enters.}
	\switchcolumn
	\notmain{乔伊的爸爸走进来}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Hey, Joe.
	\switchcolumn
	\charactername{崔布亚尼先生：}嘿，乔伊。
	\switchcolumn*
	\charactername{Joey:} Dad, Ronni's here.
	\switchcolumn
	\charactername{乔伊：}爸，罗尼来了。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Huh?
	\switchcolumn
	\charactername{崔布亚尼先生：}哈？
	\switchcolumn*
	\charactername{Ronni:} Hi.
	\switchcolumn
	\charactername{罗尼：}你好。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Hey! Hello, babe! Wh what're what're you doing here?
	\switchcolumn
	\charactername{崔布亚尼先生：}嘿！嗨，宝贝！你……你怎么会在这里？
	\switchcolumn*
	\charactername{Ronni:} Oh, uh, well, you left your good hair at my apartment, I figured you'd need it tomorrow for your meeting. \ennotmain{Hands him the hair}
	\switchcolumn
	\charactername{罗尼：}哦，呃，你把你的假发给落在我公寓了，我想你明天开会会需要的。\notmain{递给她假发}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Thank you. Uh...
	\switchcolumn
	\charactername{崔布亚尼先生：}谢谢。呃……
	\switchcolumn*
	\charactername{Chandler:} So, who's up for a big game of Kerplunk?
	\switchcolumn
	\charactername{钱德勒：}那么，谁想来玩一局“扑通”游戏？\notmain{一种插管落球游戏}
	\switchcolumn*
	\charactername{Ronni:} Look, I uh, I shouldn'ta come. I-I'd better get going, I don't wanna miss the last train.
	\switchcolumn
	\charactername{罗尼：}那个，我……我不该来的。我……我还是走吧，我不想错过最后一班火车。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} I don't want you taking that thing.
	\switchcolumn
	\charactername{崔布亚尼先生：}我不希望你坐那玩意儿。
	\switchcolumn*
	\charactername{Ronni:} Oh, where'm I gonna stay, here?
	\switchcolumn
	\charactername{罗尼：}哦，那我住哪儿，这儿吗？
	\switchcolumn*
	\charactername{Joey:} Who-ah-ho.
	\switchcolumn
	\charactername{乔伊：}哇哦。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} We'll go to a hotel.
	\switchcolumn
	\charactername{崔布亚尼先生：}我们去酒店。
	\switchcolumn*
	\charactername{Ronni:} \ennotmain{Shrugs} We'll go to a hotel.
	\switchcolumn
	\charactername{罗尼：}\notmain{耸耸肩}那我们去酒店吧。
	\switchcolumn*
	\charactername{Joey:} No you won't.
	\switchcolumn
	\charactername{乔伊：}不行。
	\switchcolumn*
	\charactername{Ronni:} No we won't.
	\switchcolumn
	\charactername{罗尼：}那我们不去了。
	\switchcolumn*
	\charactername{Joey:} If you go to a hotel you'll be...doing stuff. I want you right here where I can keep an eye on you.
	\switchcolumn
	\charactername{乔伊：}如果你们去酒店，你们就会……做那种事。我要你们待在这里，我好盯着你们。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} You're gonna keep an eye on us?
	\switchcolumn
	\charactername{崔布亚尼先生：}你要盯着我们？
	\switchcolumn*
	\charactername{Joey:} That's right, mister, and I don't care how old you are, as long as you're under my roof you're gonna live by my rules. And that means no sleeping with your girlfriend.
	\switchcolumn
	\charactername{乔伊：}没错，先生。不管你多大年纪，只要待在我家，就得听我的规矩。规矩就是不准和你的女朋友睡觉。
	\switchcolumn*
	\charactername{Ronni:} Wow. He's strict.
	\switchcolumn
	\charactername{罗尼：}哇哦。他还挺严格的。
	\switchcolumn*
	\charactername{Joey:} Now dad, you'll be in my room, Ronni uh, you can stay in Chandler's room.
	\switchcolumn
	\charactername{乔伊：}爸，你睡我的房间，罗尼，呃，你可以睡钱德勒的房间。
	\switchcolumn*
	\charactername{Ronni:} Thanks. You're, uh, you're a good kid.
	\switchcolumn
	\charactername{罗尼：}谢谢。你……你真是个好孩子。
	\switchcolumn*
	\charactername{Chandler:} C'mon, I'll show you to my room. ...That sounds so weird when it's not followed by "No thanks, it's late."
	\switchcolumn
	\charactername{钱德勒：}来吧，我带你去我的房间。……这话如果后面不跟着“不了，谢谢，太晚了”，听起来还真怪。
	\switchcolumn*
	\charactername{Joey:} Okay. Now this is just for tonight. Starting tomorrow, you gotta make a change. This has gone on long enough.
	\switchcolumn
	\charactername{乔伊：}好了。就今晚这样。从明天开始，你必须做出改变。这事已经持续太久了。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} What kinda change?
	\switchcolumn
	\charactername{崔布亚尼先生：}什么改变？
	\switchcolumn*
	\charactername{Joey:} Well, either you break it off with Ronni
	\switchcolumn
	\charactername{乔伊：}要么你和罗尼分手。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} I can't do that!
	\switchcolumn
	\charactername{崔布亚尼先生：}我做不到！
	\switchcolumn*
	\charactername{Joey:} Then you gotta come clean with Ma! This is not right!
	\switchcolumn
	\charactername{乔伊：}那你就得跟妈坦白！这样是不对的！
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Yeah, but this is
	\switchcolumn
	\charactername{崔布亚尼先生：}可是，这样……
	\switchcolumn*
	\charactername{Joey:} I don't wanna hear it! Now go to my room!
	\switchcolumn
	\charactername{乔伊：}我不想听！现在去我的房间！
	\switchcolumn*
	\sense{Scene: Chandler and Joey's, night. Chandler and Joey are sharing the sofabed in the living room. Joey is restless.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，夜晚。钱德勒和乔伊在客厅的沙发床上睡觉。乔伊翻来覆去睡不着。}
	\switchcolumn*
	\charactername{Chandler:} Hey, Kicky. What're you doing?
	\switchcolumn
	\charactername{钱德勒：}嘿，多动鬼。你在干嘛？
	\switchcolumn*
	\charactername{Joey:} Just trying to get comfortable. I can't sleep in my underwear.
	\switchcolumn
	\charactername{乔伊：}就是想找个舒服点的姿势。我穿着内裤睡不着。
	\switchcolumn*
	\charactername{Chandler:} Well, you're gonna.
	\switchcolumn
	\charactername{钱德勒：}那也得睡。
	\switchcolumn*
	\charactername{Joey:} I've been thinking. Y'know, about how I'm always seeing girls on top of girls...
	\switchcolumn
	\charactername{乔伊：}我一直在想。你知道吗，我总是和各种各样的女人约会。我一直觉得，当对的人出现时，我会成为一个有担当的人，会和她好好走下去，你懂吗？但现在看着我爸爸，我在想……
	\switchcolumn*
	\charactername{Chandler:} Are they end to end, or tall like pancakes?
	\switchcolumn
	\charactername{钱德勒：}她们是并排躺，还是像煎饼一样叠着？
	\switchcolumn*
	\charactername{Joey:} Y'know what I mean, about how I'm always going out with all these women. And I always figured, when the right one comes along, I'd be able to be a stand-up guy and go the distance, y'know? Now I'm looking at my dad, thinking...
	\switchcolumn
	\charactername{乔伊：}你懂我的意思，就是我总是和这么多女人来往。我一直觉得，当那个对的人出现时，我会成为一个有担当的人，坚持到底，你懂吗？可现在看着我爸，我在想……
	\switchcolumn*
	\charactername{Chandler:} Hey, you're not him. You're you. When they were all over you to go into your father's pipe-fitting business, did you cave?
	\switchcolumn
	\charactername{钱德勒：}嘿，你不是他。你是你自己。当初大家都逼你继承你爸爸的管道工生意，你妥协了吗？
	\switchcolumn*
	\charactername{Joey:} No.
	\switchcolumn
	\charactername{乔伊：}没有。
	\switchcolumn*
	\charactername{Chandler:} No. You decided to go into the out-of-work actor business. Now that wasn't easy, but you did it! And I'd like to believe that when the right woman comes along, you will have the courage and the guts to say "No thanks, I'm married."
	\switchcolumn
	\charactername{钱德勒：}是啊。你选择了当一名待业演员。那可不容易，但你做到了！我愿意相信，当那个对的女人出现时，你会有勇气和魄力说“不了，谢谢，我结婚了”。
	\switchcolumn*
	\charactername{Joey:} You really think so?
	\switchcolumn
	\charactername{乔伊：}你真的这么认为？
	\switchcolumn*
	\charactername{Chandler:} Yeah. I really do.
	\switchcolumn
	\charactername{钱德勒：}嗯。我真的这么认为。
	\switchcolumn*
	\charactername{Joey:} Thanks, Chandler. \ennotmain{Snuggles up to him}
	\switchcolumn
	\charactername{乔伊：}谢谢，钱德勒。\notmain{依偎到他身边}
	\switchcolumn*
	\charactername{Chandler:} Get off!
	\switchcolumn
	\charactername{钱德勒：}滚开！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, morning. Someone knocks on the door and Monica gets it.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，早上。有人敲门，莫妮卡去开门。}
	\switchcolumn*
	\charactername{Ronni:} Hi.
	\switchcolumn
	\charactername{罗尼：}你好。
	\switchcolumn*
	\charactername{Monica:} Hi...May I help you?
	\switchcolumn
	\charactername{莫妮卡：}你好……有什么事吗？
	\switchcolumn*
	\charactername{Ronni:} Yeah, uh, Joey said I could use your shower, since, uh, Chandler's in ours?
	\switchcolumn
	\charactername{罗尼：}是啊，呃，乔伊说我可以用一下你们的淋浴，因为，呃，钱德勒在我们那边的浴室里？
	\switchcolumn*
	\charactername{Monica:} Okay...who are you?
	\switchcolumn
	\charactername{莫妮卡：}好吧……你是谁？
	\switchcolumn*
	\charactername{Ronni:} Oh, I'm Ronni. Ronni Rappelano? The mistress?
	\switchcolumn
	\charactername{罗尼：}哦，我是罗尼。罗尼·拉佩拉诺？就是那个情妇？
	\switchcolumn*
	\charactername{Monica:} Oh, c'mon in.
	\switchcolumn
	\charactername{莫妮卡：}哦，进来吧。
	\switchcolumn*
	\charactername{Ronni:} Thanks.
	\switchcolumn
	\charactername{罗尼：}谢谢。
	\switchcolumn*
	\charactername{Rachel:} Hi, I'm Rachel.
	\switchcolumn
	\charactername{瑞秋：}你好，我是瑞秋。
	\switchcolumn*
	\charactername{Ronni:} Hi.
	\switchcolumn
	\charactername{罗尼：}你好。
	\switchcolumn*
	\charactername{Rachel:} Bathroom's up there.
	\switchcolumn
	\charactername{瑞秋：}浴室在楼上。
	\switchcolumn*
	\charactername{Ronni:} Great.
	\switchcolumn
	\charactername{罗尼：}太好了。
	\switchcolumn*
	\charactername{Rachel:} Hey, listen, Ronni, how long would you say Chandler's been in the shower?
	\switchcolumn
	\charactername{瑞秋：}嘿，听着，罗尼，你觉得钱德勒已经在浴室里多久了？
	\switchcolumn*
	\charactername{Ronni:} Oh, like, uh, five minutes?
	\switchcolumn
	\charactername{罗尼：}哦，大概，呃，五分钟？
	\switchcolumn*
	\charactername{Rachel:} Perfect. Fasten your seatbelts, it's peepee time. \ennotmain{She goes into Joey and Chandler's apartment, where Mr. Tribbiani is reading the paper} Hey, Mr. Trib.
	\switchcolumn
	\charactername{瑞秋：}完美。系好安全带，该看小弟弟了。\notmain{她走进钱德勒和乔伊的公寓，崔布亚尼先生正在看报纸}嘿，崔布先生。
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Hey. Morning, dear.
	\switchcolumn
	\charactername{崔布亚尼先生：}嘿。早上好，亲爱的。
	\switchcolumn*
	\ennotmain{Rachel goes up to the door of their bathroom}
	\switchcolumn
	\notmain{瑞秋走到他们浴室的门口}
	\switchcolumn*
	\charactername{Rachel:} Chandler Bing? It's time to see your thing.
	\switchcolumn
	\charactername{瑞秋：}钱德勒·宾？该让我看你的那个了。
	\switchcolumn*
	\ennotmain{She opens the door and whips back the curtain. It's Joey. They both scream}
	\switchcolumn
	\notmain{她打开门，猛地拉开浴帘。里面是乔伊。两人都尖叫起来}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{Runs out in a towel} What's the matter with you?!
	\switchcolumn
	\charactername{乔伊：}\notmain{裹着浴巾跑出来}你有病吧？！
	\switchcolumn*
	\charactername{Rachel:} I thought it was Chandler!
	\switchcolumn
	\charactername{瑞秋：}我以为是钱德勒呢！
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Comes out of his room} What? What?
	\switchcolumn
	\charactername{钱德勒：}\notmain{从他的房间出来}怎么了？怎么了？
	\switchcolumn*
	\charactername{Rachel:} You were supposed to be in there so I could see your thing!
	\switchcolumn
	\charactername{瑞秋：}你本该在里面的，这样我就能看你的那个了！
	\switchcolumn*
	\charactername{Chandler:} Sorry, my my thing was in there with me.
	\switchcolumn
	\charactername{钱德勒：}抱歉，我的那个刚才和我一起在房间里。
	\switchcolumn*
	\sense{Scene: Central Perk, everyone is there as Phoebe enters.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，大家都在，菲比走进来。}
	\switchcolumn*
	\charactername{All:} Hey, Pheebs.
	\switchcolumn
	\charactername{众人：}嘿，菲比。
	\switchcolumn*
	\charactername{Phoebe:} Hey.
	\switchcolumn
	\charactername{菲比：}嘿。
	\switchcolumn*
	\charactername{Monica:} How's it going?
	\switchcolumn
	\charactername{莫妮卡：}怎么样了？
	\switchcolumn*
	\charactername{Phoebe:} Good. Oh oh! Roger's having a dinner thing and he wanted me to invite you guys.
	\switchcolumn
	\charactername{菲比：}挺好的。哦对了！罗杰要办一个晚宴，他想让我邀请你们大家。
	\switchcolumn*
	\ennotmain{Chandler laughs}
	\switchcolumn
	\notmain{钱德勒笑了}
	\switchcolumn*
	\charactername{Phoebe:} So what's going on?
	\switchcolumn
	\charactername{菲比：}怎么了？
	\switchcolumn*
	\charactername{Monica:} Nothing, um, it's just, um... It's Roger.
	\switchcolumn
	\charactername{莫妮卡：}没什么，呃，就是，呃……是罗杰的问题。
	\switchcolumn*
	\charactername{Ross:} I dunno, there's just something about...
	\switchcolumn
	\charactername{罗斯：}我不知道，就是觉得他有点……
	\switchcolumn*
	\charactername{Chandler:} Basically we just feel that he's...
	\switchcolumn
	\charactername{钱德勒：}基本上我们就是觉得他……
	\switchcolumn*
	\charactername{Rachel:} We hate that guy.
	\switchcolumn
	\charactername{瑞秋：}我们讨厌那家伙。
	\switchcolumn*
	\charactername{All:} Yeah. Hate him.
	\switchcolumn
	\charactername{众人：}对。讨厌他。
	\switchcolumn*
	\charactername{Ross:} We're sorry, Pheebs, we're sorry.
	\switchcolumn
	\charactername{罗斯：}对不起，菲比，对不起。
	\switchcolumn*
	\charactername{Phoebe:} Uh-huh. Okay. Okay, don't you think, maybe, though, it's just that he's so perceptive that it freaks you out?
	\switchcolumn
	\charactername{菲比：}嗯哼。好吧。好吧，不过你们不觉得，也许只是因为他太有洞察力了，所以让你们觉得不自在？
	\switchcolumn*
	\charactername{All:} ...No, we hate him.
	\switchcolumn
	\charactername{众人：}……不，我们就是讨厌他。
	\switchcolumn*
	\charactername{Rachel:} We're sorry.
	\switchcolumn
	\charactername{瑞秋：}对不起嘛。
	\switchcolumn*
	\sense{Scene: Chandler and Joey's apartment, Joey is trying to turn the sofabed back into a sofa. Someone knocks on the door and it rears up at him.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，乔伊正试图把沙发床折回沙发。有人敲门，沙发床突然弹起来撞到他。}
	\switchcolumn*
	\charactername{Joey:} Ma! What're you doing here?
	\switchcolumn
	\charactername{乔伊：}妈！你怎么来了？
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} I came to give you this \ennotmain{Gives him a bag of groceries} and this. \ennotmain{Whacks him round the ear}
	\switchcolumn
	\charactername{崔布亚尼夫人：}我来给你送这个\notmain{递给她一袋杂货}还有这个。\notmain{扇了他一耳光}
	\switchcolumn*
	\charactername{Joey:} Oww! Big ring!
	\switchcolumn
	\charactername{乔伊：}哎哟！你的戒指好大！
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} Why did you have to fill your father's head with all that garbage about making things right? Things were fine the way they were! There's chicken in there, put it away. For God's sake, Joey, really. \ennotmain{She gives the sofabed a tiny push and it folds away}
	\switchcolumn
	\charactername{崔布亚尼夫人：}你为什么非要给你爸爸灌输那些要“纠正错误”的鬼话？事情本来好好的！袋子里有鸡肉，放好。天啊，乔伊，真是的。\notmain{她轻轻推了一下沙发床，沙发床就折起来了}
	\switchcolumn*
	\charactername{Joey:} Hold on, you-you knew?
	\switchcolumn
	\charactername{乔伊：}等等，你……你一直都知道？
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} Of course I knew! What did you think? Your father is no James Bond. You should've heard some of his cover stories. "I'm sleeping over at my accountant's," I mean, what is that? Please!
	\switchcolumn
	\charactername{崔布亚尼夫人：}我当然知道！你以为呢？你爸爸又不是詹姆斯·邦德。你该听听他那些借口。“我在会计家过夜”，拜托！这也太假了吧！
	\switchcolumn*
	\charactername{Joey:} So then how could you I mean, how could you?!
	\switchcolumn
	\charactername{乔伊：}那你怎么能……我是说，你怎么能忍受？！
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} Do you remember how your father used to be? Always yelling, always yelling nothing made him happy, nothing made him happy, not that wood shop, not those stupid little ships in the bottle, nothing. Now he's happy! I mean, it's nice, he has a hobby.
	\switchcolumn
	\charactername{崔布亚尼夫人：}你还记得你爸爸以前是什么样子吗？总是大喊大叫，总是大喊大叫，什么都不能让他开心，什么都不行，那个木工房不行，那些愚蠢的瓶中船也不行，什么都不行。现在他开心了！我是说，这样挺好的，他有了个爱好。
	\switchcolumn*
	\charactername{Joey:} Ma, I don't mean to be disrespectful, but... what the hell are you talking about?! I mean, what about you?
	\switchcolumn
	\charactername{乔伊：}妈，我不是不尊重你，但是……你在胡说八道什么？！我是说，那你呢？
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} Me? I'm fine. Look, honey, in an ideal world, there'd be no her, and your father would look like Sting. And I'll tell you something else. Ever since that poodle-stuffer came along, he's been so ashamed of himself that he's been more attentive, he's been more loving... I mean, it's like every day's our anniversary.
	\switchcolumn
	\charactername{崔布亚尼夫人：}我？我挺好的。听着，亲爱的，在理想的世界里，不会有她的存在，你爸爸会长得像斯汀\notmain{英国歌手}。而且我告诉你，自从那个宠物殡葬师出现后，他一直为自己感到羞愧，所以对我更体贴了，更爱我了……我是说，每天都像我们的结婚纪念日一样。
	\switchcolumn*
	\charactername{Joey:} I'm...happy...for you?
	\switchcolumn
	\charactername{乔伊：}我……为你感到高兴？
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} Well don't be, because now everything's screwed up. I just want it the way it was.
	\switchcolumn
	\charactername{崔布亚尼夫人：}不用高兴，因为现在一切都搞砸了。我只想回到以前的样子。
	\switchcolumn*
	\charactername{Joey:} Ma, I'm sorry. I just did what I thought you'd want.
	\switchcolumn
	\charactername{乔伊：}妈，对不起。我只是做了我觉得你会希望我做的事。
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} I know you did, cookie. Oh, I know you did. So tell me. Did you see her?
	\switchcolumn
	\charactername{崔布亚尼夫人：}我知道你是好意，小饼干。哦，我知道。跟我说说。你见过她吗？
	\switchcolumn*
	\charactername{Joey:} Yeah. You're ten times prettier than she is.
	\switchcolumn
	\charactername{乔伊：}见过。你比她好看十倍。
	\switchcolumn*
	\charactername{Mrs. Tribbiani:} That's sweet. Could I take her?
	\switchcolumn
	\charactername{崔布亚尼夫人：}真甜。我能打败她吗？
	\switchcolumn*
	\charactername{Joey:} With this ring? \ennotmain{Her engagement ring.} No contest.
	\switchcolumn
	\charactername{乔伊：}就凭你这戒指？\notmain{指她的订婚戒指}稳赢。
	\switchcolumn*
	\sense{Scene: Central Perk. Phoebe is there with Roger.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆。菲比和罗杰在一起。}
	\switchcolumn*
	\charactername{Roger:} What's wrong, sweetie?
	\switchcolumn
	\charactername{罗杰：}怎么了，亲爱的？
	\switchcolumn*
	\charactername{Phoebe:} Nothing, nothing.
	\switchcolumn
	\charactername{菲比：}没什么，没什么。
	\switchcolumn*
	\charactername{Roger:} Aaaah, what's wrong, c'mon. \ennotmain{Pats his leg. She lies down and rests her head in his lap}
	\switchcolumn
	\charactername{罗杰：}啊哈，怎么了，说嘛。\notmain{拍了拍自己的腿。她躺下来，头靠在他的腿上}
	\switchcolumn*
	\charactername{Phoebe:} It's, I mean, it's nothing, I'm fine. It's my friends. They-they have a liking problem with you. In that, um, they don't.
	\switchcolumn
	\charactername{菲比：}就是，我是说，没什么，我挺好的。是我的朋友们。他们……他们对你有点“喜欢”上的问题。也就是说，呃，他们不喜欢你。
	\switchcolumn*
	\charactername{Roger:} Oh. They don't.
	\switchcolumn
	\charactername{罗杰：}哦。他们不喜欢我。
	\switchcolumn*
	\charactername{Phoebe:} But they don't see all the wonderfulness that I see. They don't see all the good stuff and all the sweet stuff. They just think you're a little...
	\switchcolumn
	\charactername{菲比：}但他们没看到我看到的所有优点。他们没看到那些好的地方和贴心的地方。他们只是觉得你有点……
	\switchcolumn*
	\charactername{Roger:} What?
	\switchcolumn
	\charactername{罗杰：}有点什么？
	\switchcolumn*
	\charactername{Phoebe:} Intense and creepy.
	\switchcolumn
	\charactername{菲比：}过于强势而且有点吓人。
	\switchcolumn*
	\charactername{Roger:} Oh.
	\switchcolumn
	\charactername{罗杰：}哦。
	\switchcolumn*
	\charactername{Phoebe:} But I don't. Me, Phoebe.
	\switchcolumn
	\charactername{菲比：}但我不觉得。我，菲比，不这么觉得。
	\switchcolumn*
	\charactername{Roger:} Well, I'm not I'm not at all surprised they feel that way.
	\switchcolumn
	\charactername{罗杰：}嗯，他们会有这种感觉我一点也不惊讶。
	\switchcolumn*
	\charactername{Phoebe:} You're not? See, that's why you're so great!
	\switchcolumn
	\charactername{菲比：}你不惊讶？你看，这就是你最棒的地方！
	\switchcolumn*
	\charactername{Roger:} Actually it's, it's quite, y'know, typical behaviour when you have this kind of dysfunctional group dynamic. Y'know, this kind of co-dependant, emotionally stunted, sitting in your stupid coffee house with your stupid big cups which, I'm sorry, might as well have nipples on them, and you're like all 'Oh, define me! Define me! Love me, I need love!'.
	\switchcolumn
	\charactername{罗杰：}其实，这很，你知道的，很典型的行为，当你身处这种功能失调的群体关系中时。你知道吗，这种相互依赖、情感发育不全的群体，坐在你们那愚蠢的咖啡馆里，拿着你们那愚蠢的大杯子——抱歉，那些杯子简直就像长了乳头一样——然后你们就整天喊着“定义我！定义我！爱我，我需要爱！”
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Joey is letting everyone in on the new developments.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，乔伊正在告诉大家最新进展。}
	\switchcolumn*
	\charactername{Monica:} So you talked to your dad, huh.
	\switchcolumn
	\charactername{莫妮卡：}所以你跟你爸爸谈过了，是吧。
	\switchcolumn*
	\charactername{Joey:} Yeah. He's gonna keep cheating on my ma like she wanted, she's gonna keep pretending she doesn't know even though she does, and my little sister Tina can't see her husband any more because he got a restraining order...which has nothing to do with anything except that I found out today.
	\switchcolumn
	\charactername{乔伊：}嗯。他会继续像妈希望的那样欺骗她，妈也会继续假装不知道，尽管她其实知道。还有我的小妹妹蒂娜，再也见不到她丈夫了，因为他被下了限制令……不过这跟这事没关系，我就是今天才知道的。
	\switchcolumn*
	\charactername{Rachel:} Wow.
	\switchcolumn
	\charactername{瑞秋：}哇哦。
	\switchcolumn*
	\charactername{Chandler:} Things sure have changed here on Waltons mountain.
	\switchcolumn
	\charactername{钱德勒：}沃尔顿山\notmain{美国经典家庭剧《沃尔顿一家》背景地}的日子变化可真大啊。
	\switchcolumn*
	\charactername{Ross:} So Joey, you okay?
	\switchcolumn
	\charactername{罗斯：}那乔伊，你还好吗？
	\switchcolumn*
	\charactername{Joey:} Yeah, I guess. It's just parents, after a certain point, you gotta let go. Even if you know better, you've gotta let them make their own mistakes.
	\switchcolumn
	\charactername{乔伊：}嗯，应该还好吧。父母嘛，到了一定年纪，你就得放手。就算你知道什么是对的，也得让他们自己犯错误。
	\switchcolumn*
	\charactername{Rachel:} Just think, in a couple of years we get to turn into them.
	\switchcolumn
	\charactername{瑞秋：}想想看，再过几年我们也会变成他们那样。
	\switchcolumn*
	\charactername{Chandler:} If I turn into my parents, I'll either be an alcoholic blond chasing after twenty-year-old boys, or... I'll end up like my mom.
	\switchcolumn
	\charactername{钱德勒：}如果我变成我父母那样，要么我会变成一个酗酒的金发美女，追着二十岁的小伙子跑，要么……我会变成我妈那样。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{entering} Hey.
	\switchcolumn
	\charactername{菲比：}\notmain{走进来}嘿。
	\switchcolumn*
	\charactername{All:} Hey, Pheebs.
	\switchcolumn
	\charactername{众人：}嘿，菲比。
	\switchcolumn*
	\charactername{Monica:} How's it going?
	\switchcolumn
	\charactername{莫妮卡：}怎么样了？
	\switchcolumn*
	\charactername{Phoebe:} Oh, okay, except I broke up with Roger.
	\switchcolumn
	\charactername{菲比：}哦，还好，就是我和罗杰分手了。
	\switchcolumn*
	\charactername{All:} Awww.
	\switchcolumn
	\charactername{众人：}啊。
	\switchcolumn*
	\charactername{Phoebe:} Yeah, right.
	\switchcolumn
	\charactername{菲比：}对啊，真的分了。
	\switchcolumn*
	\charactername{All:} Aaawwwwww!!
	\switchcolumn
	\charactername{众人：}啊啊啊！
	\switchcolumn*
	\charactername{Rachel:} What happened?
	\switchcolumn
	\charactername{瑞秋：}怎么回事？
	\switchcolumn*
	\charactername{Phoebe:} I don't know, I mean, he's a good person, and he can be really sweet, and in some ways I think he is so right for me, it's just... I hate that guy!
	\switchcolumn
	\charactername{菲比：}我不知道，我是说，他是个好人，有时候也挺贴心的，而且在某些方面我觉得他挺适合我的，只是……我讨厌那家伙！
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's. Phoebe is reading the paper and Joey enters.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓。菲比正在看报纸，乔伊走进来。}
	\switchcolumn*
	\charactername{Phoebe:} Hey, Joey. What's going on?
	\switchcolumn
	\charactername{菲比：}嘿，乔伊。怎么了？
	\switchcolumn*
	\charactername{Joey:} Clear the tracks for the boobie payback express. Next stop: Rachel Green. \ennotmain{He goes into the bathroom. We hear a scream and he comes out, closely followed by Monica in a towel}
	\switchcolumn
	\charactername{乔伊：}“胸部复仇号”列车即将进站。下一站：瑞秋·格林。\notmain{他走进浴室。传来一声尖叫，他跑出来，后面紧跟着裹着浴巾的莫妮卡}
	\switchcolumn*
	\charactername{Monica:} Joey!! What the hell were you doing?!
	\switchcolumn
	\charactername{莫妮卡：}乔伊！你到底在干什么？！
	\switchcolumn*
	\charactername{Joey:} Sorry. Wrong boobies.
	\switchcolumn
	\charactername{乔伊：}对不起。认错胸部了。
	\switchcolumn*
	\ennotmain{He leaves. Cut to Monica entering Chandler and Joey's apartment. She sneaks up to the shower door}
	\switchcolumn
	\notmain{他离开了。镜头切到莫妮卡走进钱德勒和乔伊的公寓。她偷偷溜到浴室门口}
	\switchcolumn*
	\charactername{Monica:} Hello, Joey.
	\switchcolumn
	\charactername{莫妮卡：}嘿，乔伊。
	\switchcolumn*
	\ennotmain{She whips back the curtain to reveal Joey's dad}
	\switchcolumn
	\notmain{她猛地拉开浴帘，里面是乔伊的爸爸}
	\switchcolumn*
	\charactername{Mr. Tribbiani:} Oh! ...Hello, dear. \ennotmain{She whips the curtain shut in horror}
	\switchcolumn
	\charactername{崔布亚尼先生：}哦！……嘿，亲爱的。\notmain{她惊恐地猛地拉上浴帘}
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage