\begin{paracol}{2}
	\sense{Scene: Central Perk, Ross is eyeing a beautiful woman at the counter, and Joey and Chandler are egging him on to go talk to her. No pun intended. I mean it.}
	\switchcolumn
	\sense{场景：中央咖啡馆，罗斯盯着吧台旁的一位美女看，乔伊和钱德勒在一旁怂恿他过去搭讪。声明一下，我这话没有双关意思，是认真的。}
	\switchcolumn*
	\charactername{Joey:} I'm tellin' you Ross, she wants you.
	\switchcolumn
	\charactername{乔伊：}我跟你说，罗斯，她对你有意思。
	\switchcolumn*
	\charactername{Ross:} She barely knows me. We just live in the same building.
	\switchcolumn
	\charactername{罗斯：}她几乎不认识我。我们只是住同一栋楼而已。
	\switchcolumn*
	\charactername{Chandler:} Any contact?
	\switchcolumn
	\charactername{钱德勒：}有过接触吗？
	\switchcolumn*
	\charactername{Ross:} She lent me an egg once.
	\switchcolumn
	\charactername{罗斯：}她曾经借过我一个鸡蛋。
	\switchcolumn*
	\charactername{Joey:} You're in!
	\switchcolumn
	\charactername{乔伊：}你有戏了！
	\switchcolumn*
	\charactername{Ross:} Aw, right.
	\switchcolumn
	\charactername{罗斯：}呃，是吗。
	\switchcolumn*
	\charactername{Woman:} Hi, Ross.
	\switchcolumn
	\charactername{女士：}嗨，罗斯。
	\switchcolumn*
	\charactername{Ross:} Hey. \ennotmain{stutters something incoherent}
	\switchcolumn
	\charactername{罗斯：}嘿。\notmain{结结巴巴地说了些语无伦次的话}
	\switchcolumn*
	\charactername{Chandler:} Come on, Ross, you gotta get back in the game here, ok? The Rachel thing's not happening, your ex-wife is a lesbian—I don't think we need a third...
	\switchcolumn
	\charactername{钱德勒：}拜托，罗斯，你得重新振作起来，好吗？瑞秋那边没指望了，你的前妻是个女同性恋——我觉得我们不需要第三个这种情况了……
	\switchcolumn*
	\charactername{Joey:} Excuse me, could we get an egg over here, still in the shell? Thanks.
	\switchcolumn
	\charactername{乔伊：}打扰一下，能给我们来个带壳的溏心蛋吗？谢谢。
	\switchcolumn*
	\charactername{Ross:} An egg?
	\switchcolumn
	\charactername{罗斯：}一个鸡蛋？
	\switchcolumn*
	\charactername{Joey:} Yeah, you're gonna go up to her and say, "Here's your egg back, I'm returning your egg."
	\switchcolumn
	\charactername{乔伊：}对啊，你要走到她面前说：“这是你的鸡蛋，我来还你鸡蛋了。”
	\switchcolumn*
	\charactername{Chandler:} I think it's winning.
	\switchcolumn
	\charactername{钱德勒：}我觉得这招能成。
	\switchcolumn*
	\charactername{Ross:} I think it's insane.
	\switchcolumn
	\charactername{罗斯：}我觉得这太疯狂了。
	\switchcolumn*
	\charactername{Chandler:} She'll love it. Go with the egg, my friend.
	\switchcolumn
	\charactername{钱德勒：}她会喜欢的。就拿着鸡蛋去，我的朋友。
	\switchcolumn*
	\ennotmain{Ross walks over to the woman, egg in hand.}
	\switchcolumn
	\notmain{罗斯手里拿着鸡蛋，走向那位女士。}
	\switchcolumn*
	\charactername{Joey:} Think it'll work?
	\switchcolumn
	\charactername{乔伊：}你觉得能成吗？
	\switchcolumn*
	\charactername{Chandler:} No, it's suicide. The man's got an egg.
	\switchcolumn
	\charactername{钱德勒：}不成，这简直是自寻死路。这家伙手里拿着个鸡蛋呢。
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Central Perk, Monica, Rachel, Phoebe, Joey, Chandler are there. Ross is still talking to the beautiful woman.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，莫妮卡、瑞秋、菲比、乔伊、钱德勒都在。罗斯还在和那位漂亮女士聊天。}
	\switchcolumn*
	\charactername{Monica:} You can not do this.
	\switchcolumn
	\charactername{莫妮卡：}你不能这么做。
	\switchcolumn*
	\charactername{Rachel:} Do what, do what?
	\switchcolumn
	\charactername{瑞秋：}做什么，做什么呀？
	\switchcolumn*
	\charactername{Monica:} Roger wants to take her out tomorrow night.
	\switchcolumn
	\charactername{莫妮卡：}罗杰想明天晚上约她出去。
	\switchcolumn*
	\charactername{Rachel:} No! Phoebes! Don't you remember why you dumped the guy?
	\switchcolumn
	\charactername{瑞秋：}不行！菲比！你忘了你当初为什么甩了他吗？
	\switchcolumn*
	\charactername{Phoebe:} 'Cause he was creepy, and mean, and a little frightening... alright, still, it's nice to have a date on Valentine's Day!
	\switchcolumn
	\charactername{菲比：}因为他又吓人、又刻薄，还有点让人毛骨悚然……好吧，但情人节能有个约会还是挺不错的！
	\switchcolumn*
	\charactername{Monica:} But Phoebe, you can go out with a creepy guy any night of the year. I know I do.
	\switchcolumn
	\charactername{莫妮卡：}但菲比，想约吓人的家伙，一年到头哪天不行啊。我就经常这么干。
	\switchcolumn*
	\charactername{Rachel:} Well, what are you guys doing tomorrow night?
	\switchcolumn
	\charactername{瑞秋：}那你们俩明天晚上有什么安排？
	\switchcolumn*
	\charactername{Joey:} Actually, tomorrow night kinda depends on how tonight goes.
	\switchcolumn
	\charactername{乔伊：}其实，明天晚上的安排得看今晚进展怎么样。
	\switchcolumn*
	\charactername{Chandler:} Oh, uh, listen, about tonight...
	\switchcolumn
	\charactername{钱德勒：}哦，呃，那个，关于今晚……
	\switchcolumn*
	\charactername{Joey:} No, no, no, don't you dare bail on me. The only reason she's goin' out with me is because I said I could bring a friend for her friend.
	\switchcolumn
	\charactername{乔伊：}别别别，你敢放我鸽子试试。她愿意跟我约会，唯一的原因就是我说能给她朋友带个伴儿来。
	\switchcolumn*
	\charactername{Chandler:} Yes, I know, but her friend sounds like such a...
	\switchcolumn
	\charactername{钱德勒：}我知道，但她朋友听着就像个……
	\switchcolumn*
	\charactername{Joey:} Pathetic mess? I know, but—come on, man, she's needy, she's vulnerable. I'm thinkin', cha-ching! \ennotmain{Rachel throws a roll at Joey. He picks it up and eats it.} Thanks. Look, you have not been out with a woman since Janice. You're doin' this.
	\switchcolumn
	\charactername{乔伊：}可悲的失败者？我知道，但——拜托，兄弟，她渴望陪伴，又容易动心。我琢磨着，这可是个好机会！\notmain{瑞秋扔了个面包卷给乔伊。他捡起来吃了。}谢谢。听着，自从詹妮丝之后你就没跟女人约会过了。你必须去。
	\switchcolumn*
	\charactername{Ross:} Hi. She said yes.
	\switchcolumn
	\charactername{罗斯：}嗨。她答应了。
	\switchcolumn*
	\charactername{Chandler:} Yes! Way to go, man! \ennotmain{Chandler and Ross hug. Something crunches in Ross' shirt pocket.} Still got the egg, huh?
	\switchcolumn
	\charactername{钱德勒：}太好了！干得漂亮，兄弟！\notmain{钱德勒和罗斯拥抱。罗斯衬衫口袋里传来咔嚓一声。}还拿着鸡蛋呢，哈？
	\switchcolumn*
	\sense{Scene: A Restaurant, Joey and Chandler are there, waiting for their dates to show up.}
	\switchcolumn
	\sense{场景：一家餐厅，乔伊和钱德勒在等他们的约会对象出现。}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{Looking at himself in the reflection on a knife} How do I look?
	\switchcolumn
	\charactername{乔伊：}\notmain{看着刀面上自己的倒影}我看起来怎么样？
	\switchcolumn*
	\charactername{Chandler:} Oh, uh, I... don't... care. \ennotmain{Joey's date shows up} Ok, now, remember, no trading. You get the pretty one, I get the mess.
	\switchcolumn
	\charactername{钱德勒：}哦，呃，我……不……在乎。\notmain{乔伊的约会对象来了}好了，记住，不许换。你拿漂亮的那个，我来收拾这个“烂摊子”。
	\switchcolumn*
	\charactername{Lorraine:} Hi, Joey. Well well, look what you brought. Very nice.
	\switchcolumn
	\charactername{洛林：}嗨，乔伊。哇哦，看看你带来的人。真不错嘛。
	\switchcolumn*
	\charactername{Chandler:} ...And what did you bring?
	\switchcolumn
	\charactername{钱德勒：}……那你带来的是谁啊？
	\switchcolumn*
	\charactername{Lorraine:} She's checking the coats. Joey, I'm gonna go wash the cab smell off my hands. Will you get me a white Zinfandel, and a glass of red for Janice.
	\switchcolumn
	\charactername{洛林：}她在存外套呢。乔伊，我去洗洗手，洗掉出租车的味儿。能帮我拿杯白仙粉黛葡萄酒，再给詹妮丝来杯红酒吗？
	\switchcolumn*
	\charactername{Chandler:} Janice?
	\switchcolumn
	\charactername{钱德勒：}詹妮丝？
	\switchcolumn*
	\ennotmain{Lorraine leaves. Joey shakes his head as though to say, 'It can't be the same Janice.' Janice enters.}
	\switchcolumn
	\notmain{洛林离开。乔伊摇摇头，仿佛在说“不可能是那个詹妮丝吧”。詹妮丝走了进来。}
	\switchcolumn*
	\charactername{Janice:} Oh.... my.... God.
	\switchcolumn
	\charactername{詹妮丝：}哦……我的……天呐。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{angrily} Hey, it's Janice.
	\switchcolumn
	\charactername{钱德勒：}\notmain{愤怒地}嘿，是詹妮丝啊。
	\switchcolumn*
	\sense{Scene: The bathroom at the restaurant, Chandler and Joey are talking.}
	\switchcolumn
	\sense{场景：餐厅的洗手间，钱德勒和乔伊在说话。}
	\switchcolumn*
	\charactername{Chandler:} Ok, I'm makin' a break for it, I'm goin' out the window.
	\switchcolumn
	\charactername{钱德勒：}好了，我要溜了，从窗户跳出去。
	\switchcolumn*
	\charactername{Joey:} No, no, no, don't! I've been waitin' for like, forever to go out with Lorraine. Just calm down.
	\switchcolumn
	\charactername{乔伊：}别别别，别溜！我等了好久好久才约到洛林。冷静点。
	\switchcolumn*
	\charactername{Chandler:} Calm down? Calm down? You set me up with the woman that I've dumped twice in the last five months!
	\switchcolumn
	\charactername{钱德勒：}冷静？冷静？你给我安排的约会对象，是我过去五个月里甩了两次的女人！
	\switchcolumn*
	\charactername{Joey:} \ennotmain{at the urinal} Can you stop yellin'? You're makin' me nervous, and I can't go when I'm nervous.
	\switchcolumn
	\charactername{乔伊：}\notmain{在小便池前}你能别大喊大叫吗？你让我紧张了，我一紧张就尿不出来。
	\switchcolumn*
	\charactername{Chandler:} I'm sorry, I'm sorry, you're right. \ennotmain{gets up right behind Joey and yells in his ear} Come on, do it, do it, go, come on!!!
	\switchcolumn
	\charactername{钱德勒：}对不起，对不起，你说得对。\notmain{走到乔伊正身后，对着他耳朵大喊}快啊，尿啊，尿啊，快点，快啊！！！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the girls are all there, discussing their bad luck with men.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，姑娘们都在，讨论着自己在男人身上的坏运气。}
	\switchcolumn*
	\charactername{Rachel:} Ok, ok, Roger was creepy, but he was nothing compared to Pete Carney.
	\switchcolumn
	\charactername{瑞秋：}好吧好吧，罗杰是挺吓人的，但跟皮特·卡尼比起来根本不算什么。
	\switchcolumn*
	\charactername{Monica:} Which one was Pete Carney?
	\switchcolumn
	\charactername{莫妮卡：}哪个是皮特·卡尼啊？
	\switchcolumn*
	\charactername{Rachel:} Pete the Weeper? Remember that guy who used to cry every time we had sex. \ennotmain{imitating} "Was it good for you?"
	\switchcolumn
	\charactername{瑞秋：}爱哭鬼皮特啊？就是那个每次我们上床他都要哭的家伙。\notmain{模仿}“你感觉好吗？”
	\switchcolumn*
	\charactername{Monica:} Yeah, well, I'll take a little crying any day over Howard-the-"I-win"-guy. \ennotmain{imitating} "I win! I win!" I went out with the guy for two months—I didn't get to win once.
	\switchcolumn
	\charactername{莫妮卡：}是啊，不过我宁愿每天面对一点眼泪，也不想找那个“我赢了”霍华德。\notmain{模仿}“我赢了！我赢了！”我跟他约会了两个月——一次都没赢过。
	\switchcolumn*
	\charactername{Rachel:} How did we end up with these jerks? We're good people!
	\switchcolumn
	\charactername{瑞秋：}我们怎么就总遇到这些混蛋啊？我们人都挺好的啊！
	\switchcolumn*
	\charactername{Monica:} I don't know. Maybe we're some kinda magnets.
	\switchcolumn
	\charactername{莫妮卡：}我不知道。也许我们就是某种“渣男吸铁石”吧。
	\switchcolumn*
	\charactername{Phoebe:} I know I am. That's why I can't wear a digital watch.
	\switchcolumn
	\charactername{菲比：}我肯定是。所以我才不能戴电子表。
	\switchcolumn*
	\charactername{Monica:} There's more beer, right?
	\switchcolumn
	\charactername{莫妮卡：}还有啤酒吧？
	\switchcolumn*
	\charactername{Phoebe:} Oh! You know my friend Abby who shaves her head? She said that if you want to break the bad boyfriend cycle, you can do like a cleansing ritual.
	\switchcolumn
	\charactername{菲比：}哦！你们认识我那个光头朋友艾比吗？她说如果想打破遇到渣男的循环，可以做个净化仪式。
	\switchcolumn*
	\charactername{Rachel:} Pheebes, this woman is voluntarily bald.
	\switchcolumn
	\charactername{瑞秋：}菲比，这个女人是自愿剃光头的啊。
	\switchcolumn*
	\charactername{Phoebe:} Yeah. So, we can do it tomorrow night, you guys. It's Valentine's Day. It's perfect.
	\switchcolumn
	\charactername{菲比：}对啊。所以我们明天晚上可以做，姐妹们。明天是情人节。再合适不过了。
	\switchcolumn*
	\charactername{Monica:} Ok, well, what kind of ritual?
	\switchcolumn
	\charactername{莫妮卡：}好吧，那是什么样的仪式？
	\switchcolumn*
	\charactername{Phoebe:} Ok. We can, um, we can burn the stuff they gave us.
	\switchcolumn
	\charactername{菲比：}嗯。我们可以，呃，把他们送的东西烧掉。
	\switchcolumn*
	\charactername{Rachel:} Or?
	\switchcolumn
	\charactername{瑞秋：}或者？
	\switchcolumn*
	\charactername{Phoebe:} Or...or we can chant and dance around naked, you know, with sticks.
	\switchcolumn
	\charactername{菲比：}或者……或者我们可以光着身子围着圈唱歌跳舞，拿着棍子那种。
	\switchcolumn*
	\charactername{Monica:} Burning's good.
	\switchcolumn
	\charactername{莫妮卡：}烧东西挺好的。
	\switchcolumn*
	\charactername{Rachel:} Burning's good. Yeah, I got stuff to burn.
	\switchcolumn
	\charactername{瑞秋：}烧东西挺好的。对，我有好多东西可以烧。
	\switchcolumn*
	\sense{Scene: The Restaurant, Joey, Lorraine, Chandler, and Janice are at the table. Joey and Lorraine are seated very close, Chandler and Janice have backed their chairs away from one another.}
	\switchcolumn
	\sense{场景：餐厅里，乔伊、洛林、钱德勒和詹妮丝坐在餐桌旁。乔伊和洛林坐得很近，钱德勒和詹妮丝则把椅子挪得离对方远远的。}
	\switchcolumn*
	\charactername{Lorraine:} You know, ever since I was little, I've been able to pick up quarters with my toes.
	\switchcolumn
	\charactername{洛林：}你知道吗，我从小就能用脚趾夹起25美分的硬币。
	\switchcolumn*
	\charactername{Joey:} Good for you. \ennotmain{jumps suddenly} Uh, quarters or rolls of quarters?
	\switchcolumn
	\charactername{乔伊：}真厉害。\notmain{突然跳了一下}呃，是单个硬币还是一卷硬币啊？
	\switchcolumn*
	\charactername{Janice:} By the way, Chandler. I cut you out of all my pictures. So if you want, I have a bag with just your heads.
	\switchcolumn
	\charactername{詹妮丝：}对了，钱德勒。我把所有照片里的你都剪下来了。如果你想要，我这儿有一袋就只剩你脑袋的照片。
	\switchcolumn*
	\charactername{Chandler:} That's OK.
	\switchcolumn
	\charactername{钱德勒：}不用了，谢谢。
	\switchcolumn*
	\charactername{Janice:} Oh, are you sure? Really? Because you know, you could make little puppets out of them, and you could use them in your theater of cruelty.
	\switchcolumn
	\charactername{詹妮丝：}哦，你确定吗？真的不要？因为你可以把它们做成小木偶，放在你的“残酷剧场”里用啊。
	\switchcolumn*
	\ennotmain{Lorraine whispers into Joey's ear.}
	\switchcolumn
	\notmain{洛林对着乔伊的耳朵小声说话。}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{to Lorraine} We can't do that.
	\switchcolumn
	\charactername{乔伊：}\notmain{对洛林说}我们不能那么做。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{disgusted} What? What can't you do?
	\switchcolumn
	\charactername{钱德勒：}\notmain{厌恶地}什么？什么不能做？
	\switchcolumn*
	\charactername{Joey:} Uh, can I talk to you for a second, over there?
	\switchcolumn
	\charactername{乔伊：}呃，能跟你说句话吗，到那边去？
	\switchcolumn*
	\ennotmain{Chandler and Joey leave the table.}
	\switchcolumn
	\notmain{钱德勒和乔伊离开餐桌。}
	\switchcolumn*
	\charactername{Joey:} Uh, we might be leaving now.
	\switchcolumn
	\charactername{乔伊：}呃，我们可能要走了。
	\switchcolumn*
	\charactername{Chandler:} Tell me it's "you and me" we.
	\switchcolumn
	\charactername{钱德勒：}跟我说“我们”是指你和我一起走。
	\switchcolumn*
	\charactername{Joey:} She said she wants to slather my body with stuff and then lick it off. I'm not even sure what slathering is, but I definitely want to be a part of it.
	\switchcolumn
	\charactername{乔伊：}她说她想把什么东西涂满我全身，然后舔掉。我都不知道“涂满”具体是怎么操作，但我肯定要去试试。
	\switchcolumn*
	\charactername{Chandler:} Ok, you can not do this to me.
	\switchcolumn
	\charactername{钱德勒：}好吧，你不能这么对我。
	\switchcolumn*
	\charactername{Joey:} You're right, I'm sorry. You're right.
	\switchcolumn
	\charactername{乔伊：}你说得对，对不起。你说得对。
	\switchcolumn*
	\charactername{Lorraine:} \ennotmain{to waiter} Uh, can we have three chocolate mousses to go please?
	\switchcolumn
	\charactername{洛林：}\notmain{对服务员说}呃，能给我们来三份巧克力慕斯打包吗？
	\switchcolumn*
	\charactername{Joey:} I'm outta here. Here's my credit card. Dinner's on me. I'm sorry, Chandler.
	\switchcolumn
	\charactername{乔伊：}我走了。这是我的信用卡。晚饭我请客。对不起啊，钱德勒。
	\switchcolumn*
	\charactername{Chandler:} I hope she throws up on you.
	\switchcolumn
	\charactername{钱德勒：}我希望她吐你一身。
	\switchcolumn*
	\ennotmain{Joey leaves with Lorraine. Chandler sits back down with Janice.}
	\switchcolumn
	\notmain{乔伊和洛林离开。钱德勒坐回詹妮丝对面。}
	\switchcolumn*
	\charactername{Chandler:} So...
	\switchcolumn
	\charactername{钱德勒：}那个……
	\switchcolumn*
	\charactername{Janice:} Just us.
	\switchcolumn
	\charactername{詹妮丝：}就剩我们俩了。
	\switchcolumn*
	\charactername{Chandler:} Oh, what a crappy night!
	\switchcolumn
	\charactername{钱德勒：}哦，这破夜晚真糟透了！
	\switchcolumn*
	\charactername{Janice:} Although, I have enjoyed the fact that, uh your shirt's been stickin' outta your zipper ever since you came back from the bathroom.
	\switchcolumn
	\charactername{詹妮丝：}不过，我倒是挺乐呵的，你从洗手间回来之后，衬衫就一直露在拉链外面。
	\switchcolumn*
	\charactername{Chandler:} Excuse me. \ennotmain{gets up, jumps up and down while he zips his zipper up... other patrons look at him} How ya doin'?
	\switchcolumn
	\charactername{钱德勒：}失陪一下。\notmain{站起来，一边跳上跳下一边拉拉链……其他顾客都看着他}大家好啊！
	\switchcolumn*
	\charactername{Janice:} So, do we have the best friends or what?
	\switchcolumn
	\charactername{詹妮丝：}话说，我们这朋友够意思吧？
	\switchcolumn*
	\charactername{Chandler:} Joey's not a friend. He's...a stupid man who left us his credit card. Another drink? Some dessert? A big screen TV?
	\switchcolumn
	\charactername{钱德勒：}乔伊才不是朋友呢。他就是个……留下信用卡就跑的蠢货。再来一杯？来点甜点？还是买个大屏幕电视？
	\switchcolumn*
	\charactername{Janice:} I will go for that drink.
	\switchcolumn
	\charactername{詹妮丝：}我再来一杯吧。
	\switchcolumn*
	\charactername{Chandler:} You got it. Good woman! \ennotmain{the waiter turns around, it's a man} Could we get a bottle of your most overpriced champagne?
	\switchcolumn
	\charactername{钱德勒：}没问题。真是好样的！\notmain{服务员转过身来，是个男的}能给我们来一瓶你们这儿最贵的香槟吗？
	\switchcolumn*
	\charactername{Janice:} Each.
	\switchcolumn
	\charactername{詹妮丝：}每人一瓶。
	\switchcolumn*
	\charactername{Chandler:} That's right, each. Oh, and a uh Rob Roy. \ennotmain{to Janice} I've always wanted to know...
	\switchcolumn
	\charactername{钱德勒：}没错，每人一瓶。哦，再来一杯罗布·罗伊鸡尾酒。\notmain{对詹妮丝说}我一直想问……
	\switchcolumn*
	\sense{Scene: Chandler's bedroom, Chandler wakes up, and finds someone else's hand on his chest. He rolls over and is shocked to see Janice there.}
	\switchcolumn
	\sense{场景：钱德勒的卧室，钱德勒醒来，发现有只别人的手放在他胸口。他转过身，看到詹妮丝在那儿，吓了一跳。}
	\switchcolumn*
	\charactername{Janice:} Happy Valentine's Day!
	\switchcolumn
	\charactername{詹妮丝：}情人节快乐！
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: The Hallway, Chandler is trying to get Janice out of his apartment.}
	\switchcolumn
	\sense{场景：走廊里，钱德勒正试图让詹妮丝离开他的公寓。}
	\switchcolumn*
	\charactername{Janice:} Oh, I miss you already. Can you believe this happened?
	\switchcolumn
	\charactername{詹妮丝：}哦，我已经开始想你了。你能相信这一切发生了吗？
	\switchcolumn*
	\charactername{Chandler:} No... no! And yet it did. Good-bye, Janice.
	\switchcolumn
	\charactername{钱德勒：}不……不！可它偏偏就发生了。再见，詹妮丝。
	\switchcolumn*
	\charactername{Janice:} Kiss me!
	\switchcolumn
	\charactername{詹妮丝：}吻我一下！
	\switchcolumn*
	\ennotmain{Janice kisses him. Monica comes out for the newspaper.}
	\switchcolumn
	\notmain{詹妮丝吻了他。莫妮卡出来拿报纸。}
	\switchcolumn*
	\charactername{Monica:} Oh, Chandler, sorry.
	\switchcolumn
	\charactername{莫妮卡：}哦，钱德勒，不好意思啊。
	\switchcolumn*
	\ennotmain{Janice turns around, Monica sees who it is.}
	\switchcolumn
	\notmain{詹妮丝转过身，莫妮卡看清了是谁。}
	\switchcolumn*
	\charactername{Monica:} Ohhh, Chandler, sorry! Hey, Janice.
	\switchcolumn
	\charactername{莫妮卡：}哦……钱德勒，不好意思！嘿，詹妮丝。
	\switchcolumn*
	\charactername{Janice:} Hi, Monica.
	\switchcolumn
	\charactername{詹妮丝：}嗨，莫妮卡。
	\switchcolumn*
	\charactername{Chandler:} Ok, well, this was very special.
	\switchcolumn
	\charactername{钱德勒：}好了，那啥，今天真是特别的一天。
	\switchcolumn*
	\charactername{Monica:} Rach, come see who's out here!
	\switchcolumn
	\charactername{莫妮卡：}瑞秋，快出来看看谁在这儿！
	\switchcolumn*
	\ennotmain{Rachel comes out.}
	\switchcolumn
	\notmain{瑞秋走了出来。}
	\switchcolumn*
	\charactername{Rachel:} Oh my god. Janice, hi!
	\switchcolumn
	\charactername{瑞秋：}哦我的天。詹妮丝，嗨！
	\switchcolumn*
	\charactername{Chandler:} Janice is gonna go away now.
	\switchcolumn
	\charactername{钱德勒：}詹妮丝现在要走了。
	\switchcolumn*
	\charactername{Monica:} I'll be right back.
	\switchcolumn
	\charactername{莫妮卡：}我马上回来。
	\switchcolumn*
	\ennotmain{Joey enters from the stairs.}
	\switchcolumn
	\notmain{乔伊从楼梯走进来。}
	\switchcolumn*
	\charactername{Rachel:} Oh, Joey, look who it is.
	\switchcolumn
	\charactername{瑞秋：}哦，乔伊，看看谁在这儿。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{in disbelief} Whoa.
	\switchcolumn
	\charactername{乔伊：}\notmain{难以置信地}哇哦。
	\switchcolumn*
	\charactername{Chandler:} Oh, good, Joey's home now.
	\switchcolumn
	\charactername{钱德勒：}哦，太好了，乔伊回来了。
	\switchcolumn*
	\charactername{Janice:} This is so fun. This is like a reunion in the hall.
	\switchcolumn
	\charactername{詹妮丝：}这太有意思了。简直像在走廊里开同学会。
	\switchcolumn*
	\ennotmain{Monica comes out with her cordless phone.}
	\switchcolumn
	\notmain{莫妮卡拿着无绳电话走出来。}
	\switchcolumn*
	\charactername{Monica:} Oh, hi, Ross. Yeah. There's someone I want you to say hi to. \ennotmain{to Chandler} He just happened to call.
	\switchcolumn
	\charactername{莫妮卡：}哦，嗨，罗斯。对。有个人我想让你跟她打个招呼。\notmain{对钱德勒说}他刚好打电话过来。
	\switchcolumn*
	\charactername{Janice:} Hi, Ross. Yes, it's me. How did you know? \ennotmain{she laughs obnoxiously}
	\switchcolumn
	\charactername{詹妮丝：}嗨，罗斯。对，是我。你怎么知道是我呀？\notmain{发出令人讨厌的笑声}
	\switchcolumn*
	\sense{Scene: A Chinese Restaurant, Ross is there with his date.}
	\switchcolumn
	\sense{场景：一家中餐馆，罗斯和他的约会对象在那儿。}
	\switchcolumn*
	\charactername{Ross:} I'm just sayin' if dogs do experience jet lag, then, because of the whole um, seven dog years to one human year thing, then, when a dog flies from New York to Los Angeles, he doesn't just lose three hours, he loses like a week and a half.
	\switchcolumn
	\charactername{罗斯：}我就是说，如果狗也会经历时差反应，那么因为那个，呃，七年狗龄等于一年人类年龄的说法，那当一只狗从纽约飞到洛杉矶时，它失去的不只是三个小时，而是差不多一周半的时间。
	\switchcolumn*
	\ennotmain{Ross starts to laugh, and then makes a face like 'Why did I just say that?' Ross' ex-wife, Carol, and her lesbian lover, Susan, enter the restaurant. Ross stares at them.}
	\switchcolumn
	\notmain{罗斯开始笑，然后做出一副“我刚才为啥要说这个”的表情。罗斯的前妻卡萝尔和她的女同性恋伴侣苏珊走进了餐厅。罗斯盯着她们。}
	\switchcolumn*
	\charactername{Kristin:} That's funny. Who are they?
	\switchcolumn
	\charactername{克里斯汀：}挺有意思的。她们是谁啊？
	\switchcolumn*
	\charactername{Ross:} The blond woman is my ex-wife, and the woman touching her is her... close, personal friend.
	\switchcolumn
	\charactername{罗斯：}那个金发女人是我的前妻，那个碰她的女人是她的……亲密私人朋友。
	\switchcolumn*
	\charactername{Kristin:} You mean they're lovers.
	\switchcolumn
	\charactername{克里斯汀：}你是说她们是恋人吧。
	\switchcolumn*
	\charactername{Ross:} If you wanna put a label on it.
	\switchcolumn
	\charactername{罗斯：}如果你非要这么定义的话。
	\switchcolumn*
	\charactername{Kristin:} Wow, uh, anything else I should know?
	\switchcolumn
	\charactername{克里斯汀：}哇哦，呃，还有什么我该知道的吗？
	\switchcolumn*
	\charactername{Ross:} Nope, nope, that's it.
	\switchcolumn
	\charactername{罗斯：}没了，没了，就这些。
	\switchcolumn*
	\ennotmain{Carol takes off her jacket, her pregnant belly is exposed.}
	\switchcolumn
	\notmain{卡萝尔脱掉外套，露出了怀孕的肚子。}
	\switchcolumn*
	\charactername{Ross:} Oh, and she's pregnant with my baby. I always forget that part. \ennotmain{to Carol and Susan} Helloo!
	\switchcolumn
	\charactername{罗斯：}哦，对了，她怀了我的孩子。我总把这茬儿忘了。\notmain{对卡萝尔和苏珊说}嗨！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, the girls are holding their boyfriend bonfire.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，姑娘们正在举行“前男友物品焚烧大会”。}
	\switchcolumn*
	\charactername{Phoebe:} Ok, so now we need, um sage branches and the sacramental wine.
	\switchcolumn
	\charactername{菲比：}好了，现在我们需要，呃，鼠尾草枝条和圣酒。
	\switchcolumn*
	\charactername{Monica:} All I have is, is oregano and a Fresca.
	\switchcolumn
	\charactername{莫妮卡：}我这儿只有牛至叶和福雷斯卡汽水。
	\switchcolumn*
	\charactername{Phoebe:} Um, that's ok! \ennotmain{throws it in fire} Ok. All right. Now we need the semen of a righteous man.
	\switchcolumn
	\charactername{菲比：}呃，没关系！\notmain{把东西扔进火里}好了。接下来，我们需要一个正直男人的精液。
	\switchcolumn*
	\charactername{Rachel:} Ok, Pheebs, you know what, if we had that, we wouldn't be doing the ritual in the first place.
	\switchcolumn
	\charactername{瑞秋：}好了，菲比，说真的，如果我们能弄到那个，一开始就不用做这个仪式了。
	\switchcolumn*
	\charactername{Monica:} Can we just start throwing things in?
	\switchcolumn
	\charactername{莫妮卡：}我们直接开始扔东西行不行？
	\switchcolumn*
	\charactername{Phoebe:} Ok, yeah, ok. \ennotmain{she throws the directions in} Oh, OK.
	\switchcolumn
	\charactername{菲比：}行，好，没问题。\notmain{把仪式说明扔了进去}哦，好了。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{tossing things in the fire} Ok, Barry's letters. Adam Ritter's boxer shorts.
	\switchcolumn
	\charactername{瑞秋：}\notmain{把东西扔进火里}好了，巴里的信。亚当·里特的拳击短裤。
	\switchcolumn*
	\charactername{Phoebe:} Ok, and I have the, uh receipt for my dinner with Nokululu Oon Ah Ah.
	\switchcolumn
	\charactername{菲比：}好，我这儿有和诺库鲁鲁·翁·啊·啊一起吃饭的收据。
	\switchcolumn*
	\charactername{Monica:} Look, here's a picture of Scotty Jared naked.
	\switchcolumn
	\charactername{莫妮卡：}看，这是斯科蒂·贾里德的裸照。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{looking at picture} Hey he's wearing a sweater.
	\switchcolumn
	\charactername{瑞秋：}\notmain{看着照片}嘿，他穿着毛衣呢。
	\switchcolumn*
	\charactername{Monica:} No.
	\switchcolumn
	\charactername{莫妮卡：}没有。
	\switchcolumn*
	\charactername{Rachel and Phoebe:} Eww!
	\switchcolumn
	\charactername{瑞秋和菲比：}呃！
	\switchcolumn*
	\charactername{Rachel:} And here we have the last of Paulo's grappa.
	\switchcolumn
	\charactername{瑞秋：}还有这个，保罗的格拉巴酒，就剩最后一点了。
	\switchcolumn*
	\charactername{Monica:} Hey, Rachel, isn't that stuff almost pure...
	\switchcolumn
	\charactername{莫妮卡：}嘿，瑞秋，这玩意儿是不是几乎纯……
	\switchcolumn*
	\ennotmain{Rachel throws the alcohol in the fire. A burst of flames shoots up from it.}
	\switchcolumn
	\notmain{瑞秋把酒扔进火里。火焰突然窜了起来。}
	\switchcolumn*
	\sense{Scene: Central Perk, Chandler and Joey are there. Chandler is preparing to dump Janice again.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，钱德勒和乔伊在那儿。钱德勒正准备再次甩了詹妮丝。}
	\switchcolumn*
	\charactername{Chandler:} How can I dump this woman on Valentine's day?
	\switchcolumn
	\charactername{钱德勒：}我怎么能在情人节这天甩了这个女人啊？
	\switchcolumn*
	\charactername{Joey:} I don't know. You dumped her on New Year's.
	\switchcolumn
	\charactername{乔伊：}我不知道。你新年的时候就甩过她一次了。
	\switchcolumn*
	\charactername{Chandler:} Oh, man. In my next life, I'm coming back as a toilet brush.
	\switchcolumn
	\charactername{钱德勒：}哦，天呐。下辈子我要做个马桶刷。
	\switchcolumn*
	\ennotmain{Janice enters.}
	\switchcolumn
	\notmain{詹妮丝走进来。}
	\switchcolumn*
	\charactername{Janice:} Hello, funny Valentine.
	\switchcolumn
	\charactername{詹妮丝：}嗨，有趣的情人节伴侣。
	\switchcolumn*
	\charactername{Chandler:} Hi, Just Janice.
	\switchcolumn
	\charactername{钱德勒：}嗨，就只是詹妮丝而已。
	\switchcolumn*
	\charactername{Janice:} Hello, Joey, our little matchmaker. I could just kiss you all over, and I'm gonna!
	\switchcolumn
	\charactername{詹妮丝：}嗨，乔伊，我们的小红娘。我真想把你从头到脚亲个遍，而且我就要这么做！
	\switchcolumn*
	\ennotmain{Janice kisses Joey all over. Chandler smiles.}
	\switchcolumn
	\notmain{詹妮丝把乔伊全身都亲了个遍。钱德勒笑了。}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{to Chandler} If you don't do it, I will.
	\switchcolumn
	\charactername{乔伊：}\notmain{对钱德勒说}你要是不跟她说，我就说了。
	\switchcolumn*
	\sense{Scene: The Chinese Restaurant.}
	\switchcolumn
	\sense{场景：中餐馆。}
	\switchcolumn*
	\charactername{Ross:} So, um, what do you do for a living?
	\switchcolumn
	\charactername{罗斯：}那个，呃，你是做什么工作的？
	\switchcolumn*
	\charactername{Kristin:} Well, um, for the past few years I've been working..\ennotmain{Ross is watching Carol and Susan, not listening to Kristin. Susan gets up, and has to go. Carol is left stranded}...which is funny because, that wasn't even my major.
	\switchcolumn
	\charactername{克里斯汀：}嗯，呃，过去几年我一直在做……\notmain{罗斯在看卡萝尔和苏珊，没听克里斯汀说话。苏珊站起来，必须得走了。卡萝尔一个人留在那儿。}……这挺有意思的，因为那甚至都不是我的专业。
	\switchcolumn*
	\charactername{Carol:} Oh no. I thought you said they could shoot the spot without you.
	\switchcolumn
	\charactername{卡萝尔：}哦不。我以为你说过没有你他们也能拍那个广告片段呢。
	\switchcolumn*
	\charactername{Susan:} I thought they could...I'll try to get back as soon as I can. I'm sorry. \ennotmain{Ross realizes Kristin was expecting him to laugh, so he starts to laugh hysterically.}
	\switchcolumn
	\charactername{苏珊：}我以为他们可以……我会尽快回来的。对不起。\notmain{罗斯意识到克里斯汀在等他笑，于是开始歇斯底里地大笑。}
	\switchcolumn*
	\charactername{Ross:} Now that is funny. Hey, do you think...would it be too weird if I invited Carol over to join us? 'Cause she's, she's alone now, and pregnant, and, and sad.
	\switchcolumn
	\charactername{罗斯：}这也太好笑了。嘿，你觉得……我邀请卡萝尔过来跟我们一起坐会不会太奇怪？因为她现在一个人，还怀着孕，挺可怜的。
	\switchcolumn*
	\charactername{Kristin:} \ennotmain{reluctantly} I guess.
	\switchcolumn
	\charactername{克里斯汀：}\notmain{不情愿地}应该不会吧。
	\switchcolumn*
	\charactername{Ross:} Are you sure? Great. Carol? Wanna come over and join us?
	\switchcolumn
	\charactername{罗斯：}你确定？太好了。卡萝尔？要不要过来跟我们一起坐？
	\switchcolumn*
	\charactername{Carol:} Oh, no no no. I'm fine. I'm fine.
	\switchcolumn
	\charactername{卡萝尔：}哦，不用不用不用。我没事。我挺好的。
	\switchcolumn*
	\charactername{Ross:} Come on. These people'll scooch down. You guys'll scooch, won't you? Let's try scooching! Come on. Come on. Uh, Kristen Riggs, this is Carol Willick. Carol, Kristin. Uh, Carol teaches sixth grade. And, Kristin, Kristin...\ennotmain{struggling}...does something that, funnily enough, wasn't even her major!
	\switchcolumn
	\charactername{罗斯：}来吧。这些人会挪一挪的。你们会挪的，对吧？咱们试试挪位置！快来快来。呃，克里斯汀·里格斯，这是卡萝尔·威利克。卡萝尔，这是克里斯汀。呃，卡萝尔教六年级。至于克里斯汀，克里斯汀她……\notmain{支支吾吾}……做的工作，有意思的是，跟她的专业一点关系都没有！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, firemen are there to handle the bonfire that got out of control.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，消防员来处理失控的焚烧大会。}
	\switchcolumn*
	\charactername{Fireman No. 1:} What do we got there?
	\switchcolumn
	\charactername{消防员一号：}这儿发生什么事了？
	\switchcolumn*
	\charactername{Fireman No. 2:} A piece of something: boxer shorts, greeting cards, and what looks like a half-charred picture—Wow, that guy's hairier than the Chief!
	\switchcolumn
	\charactername{消防员二号：}一堆乱七八糟的东西：拳击短裤、贺卡，还有一张看起来烧了一半的照片——哇哦，这家伙比队长还多毛！
	\switchcolumn*
	\charactername{Monica:} You know, it's a really funny story how this happened.
	\switchcolumn
	\charactername{莫妮卡：}其实这事儿说来话长，挺有意思的。
	\switchcolumn*
	\charactername{Fireman No. 3:} It's all right. It's all right. You don't have to explain. This isn't the first boyfriend bonfire that we've seen get out of control.
	\switchcolumn
	\charactername{消防员三号：}没事没事。不用解释。这种“前男友物品焚烧大会”失控的情况我们见多了。
	\switchcolumn*
	\charactername{Fireman No. 1:} You're our third call tonight.
	\switchcolumn
	\charactername{消防员一号：}你们是我们今晚接到的第三个这类报警了。
	\switchcolumn*
	\charactername{Rachel:} Really?
	\switchcolumn
	\charactername{瑞秋：}真的吗？
	\switchcolumn*
	\charactername{Fireman No. 2:} Oh, sure, Valentine's is our busiest night of the year.
	\switchcolumn
	\charactername{消防员二号：}那当然，情人节是我们一年中最忙的一晚。
	\switchcolumn*
	\sense{Scene: Central Perk.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆。}
	\switchcolumn*
	\charactername{Janice:} I brought you something.
	\switchcolumn
	\charactername{詹妮丝：}我给你带了点东西。
	\switchcolumn*
	\charactername{Chandler:} Is it loaded? Oh, little candy hearts. \ennotmain{reading the candy} Chan and Jan Forever.
	\switchcolumn
	\charactername{钱德勒：}是上了膛的武器吗？哦，是小小的爱心糖果。\notmain{读糖果上的字}钱德勒和詹妮丝永远在一起。
	\switchcolumn*
	\charactername{Janice:} I had them made special.
	\switchcolumn
	\charactername{詹妮丝：}我特意定制的。
	\switchcolumn*
	\charactername{Chandler:} Ok, Janice. Janice. Hey, Janice. Look, there's no way for me to tell you this. At least there's no new way for me to tell you this. I just don't things are gonna work out.
	\switchcolumn
	\charactername{钱德勒：}好了，詹妮丝。詹妮丝。嘿，詹妮丝。听着，我实在不知道该怎么跟你说。至少我已经没有新的说法来跟你说了。我只是觉得我们俩不会有结果的。
	\switchcolumn*
	\charactername{Janice:} That's fine.
	\switchcolumn
	\charactername{詹妮丝：}没关系。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{surprised} It is?
	\switchcolumn
	\charactername{钱德勒：}\notmain{惊讶地}没关系？
	\switchcolumn*
	\charactername{Janice:} Mmm-hmm. Because I know that this isn't the end.
	\switchcolumn
	\charactername{詹妮丝：}嗯哼。因为我知道这不是结局。
	\switchcolumn*
	\charactername{Chandler:} Oh no, you see, actually it is.
	\switchcolumn
	\charactername{钱德勒：}哦不，你看，这其实就是结局了。
	\switchcolumn*
	\charactername{Janice:} No, it isn't, because you won't let that happen. Don't you know it yet? You love me, Chandler Bing.
	\switchcolumn
	\charactername{詹妮丝：}不，不是的，因为你不会让它结束的。你还没明白吗？你爱我，钱德勒·宾。
	\switchcolumn*
	\charactername{Chandler:} Oh, no I don't.
	\switchcolumn
	\charactername{钱德勒：}哦，我才不爱你呢。
	\switchcolumn*
	\charactername{Janice:} Well then ask yourself this. Why do you think we keep ending up together? New Year's? Who invited who? Valentine's? Who asked who into whose bed?
	\switchcolumn
	\charactername{詹妮丝：}那你问问你自己。你觉得我们为什么总是能复合？新年的时候？是谁约的谁？情人节的时候？是谁邀请谁上的床？
	\switchcolumn*
	\charactername{Chandler:} I did, but...
	\switchcolumn
	\charactername{钱德勒：}是我，但……
	\switchcolumn*
	\charactername{Janice:} You seek me out. Something deep in your soul calls out to me like a foghorn. Janice, Janice. You want me. You need me. You can't live without me. And you know it. You just don't know you know it. See ya.
	\switchcolumn
	\charactername{詹妮丝：}是你主动找我的。你灵魂深处有个东西像雾号一样呼唤着我。詹妮丝，詹妮丝。你想要我。你需要我。你不能没有我。而且你心里清楚。你只是自己还没意识到而已。再见啦。
	\switchcolumn*
	\ennotmain{She kisses him passionately,then leaves.}
	\switchcolumn
	\notmain{她深情地吻了他一下，然后离开了。}
	\switchcolumn*
	\charactername{Chandler:} Call me!
	\switchcolumn
	\charactername{钱德勒：}给我打电话！
	\switchcolumn*
	\sense{Scene: The Chinese Restaurant, Ross and Carol are talking. Kristin is not there.}
	\switchcolumn
	\sense{场景：中餐馆，罗斯和卡萝尔在说话。克里斯汀不在那儿了。}
	\switchcolumn*
	\charactername{Carol:} It's not true. I never called your mother a wolverine.
	\switchcolumn
	\charactername{卡萝尔：}不是这样的。我从来没说过你妈妈像狼獾。
	\switchcolumn*
	\charactername{Ross:} You did so. I swear, I swear—\ennotmain{noticing Kristin's absence} How long has she been in the bathroom?
	\switchcolumn
	\charactername{罗斯：}你说了。我发誓，我发誓——\notmain{注意到克里斯汀不在了}她去洗手间多久了？
	\switchcolumn*
	\charactername{Carol:} Uh, I don't think she's in the bathroom. Her coat is gone.
	\switchcolumn
	\charactername{卡萝尔：}呃，我觉得她不在洗手间。她的外套不见了。
	\switchcolumn*
	\charactername{Ross:} Well maybe it's cold in there. Or maybe I screwed up the first date I had in 9 years.
	\switchcolumn
	\charactername{罗斯：}也许洗手间里太冷了吧。或者是我搞砸了我九年来的第一次约会。
	\switchcolumn*
	\charactername{Carol:} That could be it.
	\switchcolumn
	\charactername{卡萝尔：}有可能是这样。
	\switchcolumn*
	\charactername{Ross:} Oh, god. \ennotmain{He puts his head down on the grill} You know, this is still pretty hot. \ennotmain{He picks his head up, and a mushroom sticks to his head. Carol picks it off and eats it.}
	\switchcolumn
	\charactername{罗斯：}哦，天呐。\notmain{把脑袋趴在烤架上}你知道吗，这玩意儿还挺烫的。\notmain{抬起头，一颗蘑菇粘在了他头上。卡萝尔把蘑菇摘下来吃了。}
	\switchcolumn*
	\charactername{Carol:} Mushroom. Smile. They won't all be like this. Some women might even stay through dinner. Sorry, that's not funny
	\switchcolumn
	\charactername{卡萝尔：}蘑菇而已。笑一个嘛。不是所有约会都会这样的。有些女人说不定还能陪你吃完晚饭呢。抱歉，这不好笑。
	\switchcolumn*
	\charactername{Ross:} No, it's just...you know the whole "getting on with your life" thing. Well, do I have to? I mean, I'm sitting here with this cute woman, and, and, and she's perfectly nice, and, but that there's, that's it. And um, and then I'm here talkin' to you, and, and it's easy, and it's fun, and, and I don't, I don't have to...You know, here's a wacky thought. Um, what's say you and I give it another shot? No no no, I know what you're gonna say, you're a lesbian. But what do you say we just put that aside for now you know? Let's just stick a pin in it, ok? Because, we're great together, you know. You can't deny it. Besides, you're carrying my baby. I mean, how perfect is that? But see, you know, you keep sayin' that, but there's somethin' right here. I love you.
	\switchcolumn
	\charactername{罗斯：}不，我只是……你知道那种“继续过日子”的说法。可我非得这样吗？我是说，我坐在这儿，对面是个可爱的女人，她人也挺好的，但是，就是感觉少点什么。然后我现在跟你聊天，感觉很轻松，也很开心，而且我不用……你知道吗，我有个疯狂的想法。呃，要不我们再试一次？不不不，我知道你会说什么，你是女同性恋。但我们能不能先把这个放一放？先搁置一下，好吗？因为我们在一起的时候真的很合拍，你不能否认这一点。而且，你还怀着我的孩子。我是说，这多完美啊？但是，你知道，你总说那些话，可我心里就是有感觉。我爱你。
	\switchcolumn*
	\ennotmain{They kiss.}
	\switchcolumn
	\notmain{他们吻了起来。}
	\switchcolumn*
	\charactername{Carol:} Oh, I love you too. But...
	\switchcolumn
	\charactername{卡萝尔：}哦，我也爱你。但是……
	\switchcolumn*
	\charactername{Ross:} No but, no but.
	\switchcolumn
	\charactername{罗斯：}别但是，别但是。
	\switchcolumn*
	\charactername{Carol:} You know that thing you put over here with the pin in it? It's time to take the pin out. You'll find someone, I know you will. The right woman is just waiting for you.
	\switchcolumn
	\charactername{卡萝尔：}你知道你刚才说要搁置的那件事吗？现在该把别针拔下来了。你会找到合适的人的，我知道你会的。那个对的女人正在等你呢。
	\switchcolumn*
	\charactername{Ross:} That's easy for you to say, you found one already.
	\switchcolumn
	\charactername{罗斯：}你说得倒轻巧，你已经找到对的人了。
	\switchcolumn*
	\charactername{Carol:} All you need is a woman who likes men and you'll be set.
	\switchcolumn
	\charactername{卡萝尔：}你只需要找个喜欢男人的女人，就万事大吉了。
	\switchcolumn*
	\ennotmain{A beautiful woman walks by Ross, he stares at her.}
	\switchcolumn
	\notmain{一个漂亮女人从罗斯身边走过，他盯着她看。}
	\switchcolumn*
	\charactername{Carol:} Not her.
	\switchcolumn
	\charactername{卡萝尔：}不是她。
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, The girls are talking with the firemen.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，姑娘们在和消防员聊天。}
	\switchcolumn*
	\charactername{Fireman No. 3:} We get off around midnight, why don't we pick you up then?
	\switchcolumn
	\charactername{消防员三号：}我们大概午夜下班，到时候去接你们怎么样？
	\switchcolumn*
	\charactername{Rachel:} So, um, will you bring the truck?
	\switchcolumn
	\charactername{瑞秋：}那，呃，你们会开消防车来吗？
	\switchcolumn*
	\charactername{Fireman No. 3:} I'll even let you ring the bell.
	\switchcolumn
	\charactername{消防员三号：}我还让你们按警铃呢。
	\switchcolumn*
	\charactername{Rachel:} Oh, my god.
	\switchcolumn
	\charactername{瑞秋：}哦，我的天。
	\switchcolumn*
	\charactername{Phoebe:} See, there you go, the cleansing works!
	\switchcolumn
	\charactername{菲比：}看吧，我说吧，净化仪式起作用了！
	\switchcolumn*
	\charactername{Monica:} They're nice guys.
	\switchcolumn
	\charactername{莫妮卡：}他们人都挺好的。
	\switchcolumn*
	\charactername{Rachel:} Oh, they're firemen guys.
	\switchcolumn
	\charactername{瑞秋：}哦，他们可是消防员啊。
	\switchcolumn*
	\sense{Scene: Out in the hall, the firemen are talking.}
	\switchcolumn
	\sense{场景：走廊里，消防员们在说话。}
	\switchcolumn*
	\charactername{Fireman No. 1:} You guys tell them you were married?
	\switchcolumn
	\charactername{消防员一号：}你们跟她们说你们结婚了吗？
	\switchcolumn*
	\charactername{Fireman No. 2:} No way!
	\switchcolumn
	\charactername{消防员二号：}才没有呢！
	\switchcolumn*
	\charactername{Fireman No. 3:} Are you kidding? My girlfriend doesn't know, I'm not gonna tell them!
	\switchcolumn
	\charactername{消防员三号：}你在开玩笑吗？我女朋友都不知道我结婚了，我怎么会告诉她们！
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage