\begin{paracol}{2}
	\sense{Scene: Central Perk, Rachel is serving Joey, Ross, and Monica their drinks.}
	\switchcolumn
	\sense{场景：中央公园咖啡厅，瑞秋正在为乔伊、罗斯和莫妮卡端上他们的饮料。}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{to Joey} Coffee. \ennotmain{Hands it to him.}
	\switchcolumn
	\charactername{瑞秋：}\notmain{对乔伊}咖啡。\notmain{递给他。}
	\switchcolumn*
	\charactername{Joey:} Thank you.
	\switchcolumn
	\charactername{乔伊：}谢谢。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{to Ross} Cappuccino. \ennotmain{Hands it to him.}
	\switchcolumn
	\charactername{瑞秋：}\notmain{对罗斯}卡布奇诺。\notmain{递给他。}
	\switchcolumn*
	\charactername{Ross:} Grazie.
	\switchcolumn
	\charactername{罗斯：}谢谢。
	\switchcolumn*
	\charactername{Rachel:} And a nice hot cider for Monica. \ennotmain{Hands it to her.}
	\switchcolumn
	\charactername{瑞秋：}给莫妮卡一杯热乎乎的苹果酒。\notmain{递给她。}
	\switchcolumn*
	\charactername{Monica:} Aww, thank you. \ennotmain{Notices something.} Uh Rach?
	\switchcolumn
	\charactername{莫妮卡：}噢，谢谢。\notmain{注意到什么。}呃，瑞秋？
	\switchcolumn*
	\charactername{Rachel:} Yeah?
	\switchcolumn
	\charactername{瑞秋：}怎么了？
	\switchcolumn*
	\charactername{Monica:} Why does my cinamon stick have an eraser?
	\switchcolumn
	\charactername{莫妮卡：}为什么我的肉桂棒上有个橡皮擦？
	\switchcolumn*
	\charactername{Rachel:} Oh! That's why. \ennotmain{Rachel checks behind her ear, and finds a cinamon stick.} I'm sorry!
	\switchcolumn
	\charactername{瑞秋：}噢！原来如此。\notmain{瑞秋检查自己耳朵后面，找到一根肉桂棒。}对不起！
	\switchcolumn*
	\ennotmain{She takes the pencil out of Monica's coffee and Monica puts her cup down in disgust.}
	\switchcolumn
	\notmain{她把铅笔从莫妮卡的咖啡里拿出来，莫妮卡厌恶地放下杯子。}
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: Chandler's job, Chandler is typing data into his computer, he keeps typing even while taking a drink of coffee with one hand. One of his co-workers walks by.}
	\switchcolumn
	\sense{场景：钱德勒的工作地点，钱德勒正在往电脑里输入数据，他甚至在用一只手喝咖啡时也继续打字。一位同事走过。}
	\switchcolumn*
	\charactername{Woman:} Chandler.
	\switchcolumn
	\charactername{女士：}钱德勒。
	\switchcolumn*
	\charactername{Chandler:} Mrs. Tedlock. You're looking lovely today. And may I say, that is a very flattering sleeve length on you.
	\switchcolumn
	\charactername{钱德勒：}泰德洛克夫人。你今天看起来真美。我得说，那个袖子长度你穿起来非常迷人。
	\switchcolumn*
	\charactername{Mrs. Tedlock:} Yes. Well, Mr. Kostelick wants you to stop by his office at the end of the day.
	\switchcolumn
	\charactername{泰德洛克夫人：}是的。嗯，科斯特利克先生希望你今天下班前去他办公室一趟。
	\switchcolumn*
	\charactername{Chandler:} Oh, listen. If this is about those prank memos, I had nothing to do with them. Really. Nothing at all. Really. \ennotmain{Chandler tries to hide a rubber chicken from the woman.} Nothing.
	\switchcolumn
	\charactername{钱德勒：}哦，听着。如果这是关于那些恶作剧备忘录的事，我可一点关系都没有。真的。完全没有。真的。\notmain{钱德勒试图把一只橡皮鸡藏起来不让那位女士看见。}没关系。
	\switchcolumn*
	\sense{Scene: Central Perk, everyone is there but Chandler. Phoebe runs in, excitedly.}
	\switchcolumn
	\sense{场景：中央公园咖啡厅，除了钱德勒大家都在。菲比兴奋地跑进来。}
	\switchcolumn*
	\charactername{Phoebe:} Hey you guys! Chandler's coming and he says he has, like, this incredible news, so when he gets here, we could all act like, you know...
	\switchcolumn
	\charactername{菲比：}嘿，你们！钱德勒要来了，他说他有，那个，一个超级棒的消息，所以等他来了，我们可以都表现得好像，你们知道……
	\switchcolumn*
	\ennotmain{Chandler comes in.}
	\switchcolumn
	\notmain{钱德勒进来。}
	\switchcolumn*
	\charactername{Chandler:} Hey!
	\switchcolumn
	\charactername{钱德勒：}嘿！
	\switchcolumn*
	\charactername{All:} Hey!
	\switchcolumn
	\charactername{大家：}嘿！
	\switchcolumn*
	\charactername{Phoebe:} Never mind. But it was going to be really good.
	\switchcolumn
	\charactername{菲比：}算了。不过本来会很精彩的。
	\switchcolumn*
	\charactername{Ross:} What's going on?
	\switchcolumn
	\charactername{罗斯：}怎么回事？
	\switchcolumn*
	\charactername{All:} What is it?
	\switchcolumn
	\charactername{大家：}是什么事？
	\switchcolumn*
	\charactername{Chandler:} So, it's a typical day at work. I'm inputting my numbers, and big Al calls me into his office and tells me he wants to make me processing supervisor.
	\switchcolumn
	\charactername{钱德勒：}所以，就是工作中平常的一天。我正在输入我的数据，然后大个子阿尔把我叫进办公室，告诉我他想让我当处理主管。
	\switchcolumn*
	\charactername{All:} That's great!
	\switchcolumn
	\charactername{大家：}太棒了！
	\switchcolumn*
	\charactername{Chandler:} So.... I quit.
	\switchcolumn
	\charactername{钱德勒：}所以……我辞职了。
	\switchcolumn*
	\charactername{All:} Why?
	\switchcolumn
	\charactername{大家：}为什么？
	\switchcolumn*
	\charactername{Chandler:} Why? This was supposed to be a temp job!
	\switchcolumn
	\charactername{钱德勒：}为什么？这本来是个临时工作！
	\switchcolumn*
	\charactername{Monica:} Yeah, Chandler... you've been there for five years.
	\switchcolumn
	\charactername{莫妮卡：}是啊，钱德勒……你都在那里干了五年了。
	\switchcolumn*
	\charactername{Chandler:} If I took this promotion, it'd be like admitting that this is what I actually do.
	\switchcolumn
	\charactername{钱德勒：}如果我接受了这次升职，那就等于承认这就是我真正干的事。
	\switchcolumn*
	\charactername{Phoebe:} So was it a lot more money?
	\switchcolumn
	\charactername{菲比：}那么是钱多很多吗？
	\switchcolumn*
	\charactername{Chandler:} It doesn't matter. I just don't want to be one of those guys that's in his office until twelve o'clock at night worrying about the WENUS.
	\switchcolumn
	\charactername{钱德勒：}这不重要。我只是不想成为那种半夜十二点还在办公室里担心 WENUS 的人。
	\switchcolumn*
	\ennotmain{Everyone looks at him, confused.}
	\switchcolumn
	\notmain{大家都疑惑地看着他。}
	\switchcolumn*
	\charactername{Rachel:} ... the WENUS?
	\switchcolumn
	\charactername{瑞秋：}……WENUS？
	\switchcolumn*
	\charactername{Chandler:} Weekly Estimated Net Usage Systems. A processing term.
	\switchcolumn
	\charactername{钱德勒：}每周预估净使用量系统。一个处理术语。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{sarcastic} Oh. That WENUS.
	\switchcolumn
	\charactername{瑞秋：}\notmain{讽刺地}哦。那个 WENUS 啊。
	\switchcolumn*
	\charactername{Joey:} So what're you going to do?
	\switchcolumn
	\charactername{乔伊：}那你打算做什么？
	\switchcolumn*
	\charactername{Chandler:} I don't know. That's the thing. I don't know what I want to do. I just know I'm not going to figure it out working there.
	\switchcolumn
	\charactername{钱德勒：}我不知道。问题就在这儿。我不知道我想做什么。我只知道在那儿工作我是想不明白的。
	\switchcolumn*
	\charactername{Phoebe:} Oooh! I have something you can do! I have this new massage client... Steve? \ennotmain{pause} Anyway, he's opening up a restaurant and he's looking for a head chef.
	\switchcolumn
	\charactername{菲比：}噢！我有事可以让你做！我有个新按摩客户……史蒂夫？\notmain{停顿}总之，他要开一家餐厅，正在找一个主厨。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{taps Phoebe on her shoulder} Um... hi there.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{拍拍菲比的肩膀}嗯……你好啊。
	\switchcolumn*
	\charactername{Phoebe:} Hi! \ennotmain{turns back to Chandler, then to Monica} Oh, yeah, no, I know. You're a chef. I know, and I thought of you first, but um, Chandler's the one who needs a job right now, so....
	\switchcolumn
	\charactername{菲比：}嗨！\notmain{转回钱德勒，然后转向莫妮卡}哦，对，不，我知道。你是个厨师。我知道，我第一个想到的是你，但是呢，钱德勒是现在需要工作的人，所以……
	\switchcolumn*
	\charactername{Chandler:} Yeah... I just don't have that much cheffing experience. Unless it's an all-toast restaurant.
	\switchcolumn
	\charactername{钱德勒：}是啊……我没什么厨师经验。除非是个全烤面包片餐厅。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{to Monica's tapping} Yeah, yeah!
	\switchcolumn
	\charactername{菲比：}\notmain{对莫妮卡的拍打}是，是！
	\switchcolumn*
	\charactername{Monica:} Well, what kind of food is he looking for?
	\switchcolumn
	\charactername{莫妮卡：}那么，他要做什么样的菜？
	\switchcolumn*
	\charactername{Phoebe:} Well, he wants to do some ecclectic, so he's looking for someone who can, you know, create the entire menu.
	\switchcolumn
	\charactername{菲比：}嗯，他想做折衷融合风格的，所以他在找一个能够，你知道，创作整个菜单的人。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{excited} Oh my God!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{兴奋地}我的天啊！
	\switchcolumn*
	\charactername{Phoebe:} Yeah, I know! \ennotmain{turns to Chandler} So, what do you think?
	\switchcolumn
	\charactername{菲比：}是啊，我知道！\notmain{转向钱德勒}所以，你觉得怎么样？
	\switchcolumn*
	\charactername{Chandler:} Thanks, Phoebe. But I just don't really see myself in a big white hat.
	\switchcolumn
	\charactername{钱德勒：}谢谢，菲比。但我实在无法想象自己戴着那种白色高帽的样子。
	\switchcolumn*
	\charactername{Phoebe:} OK. \ennotmain{pause} Oh Monica! Guess what!
	\switchcolumn
	\charactername{菲比：}好吧。\notmain{停顿}哦，莫妮卡！猜猜怎么着！
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Chandler walks in, wearing a suit.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，钱德勒走进来，穿着一套西装。}
	\switchcolumn*
	\charactername{Chandler:} Can you see my nipples through this shirt?
	\switchcolumn
	\charactername{钱德勒：}你们能看到我衬衫下的乳头吗？
	\switchcolumn*
	\charactername{Rachel:} No. But don't worry, I'm sure they're still there.
	\switchcolumn
	\charactername{瑞秋：}看不到。不过别担心，我敢肯定它们还在那儿。
	\switchcolumn*
	\charactername{Phoebe:} Where are you going, Mr. Suity-Man?
	\switchcolumn
	\charactername{菲比：}你要去哪儿，西装先生？
	\switchcolumn*
	\charactername{Chandler:} Well, I have an appointment to see Dr. Robert Pillman, career counselor a-gogo. \ennotmain{pause} I added the "a-gogo."
	\switchcolumn
	\charactername{钱德勒：}嗯，我和罗伯特·皮尔曼博士约好了，职业咨询顾问-a-gogo。\notmain{停顿}“a-gogo”是我加的。
	\switchcolumn*
	\charactername{Rachel:} Career counselor?
	\switchcolumn
	\charactername{瑞秋：}职业咨询顾问？
	\switchcolumn*
	\charactername{Chandler:} Hey, you guys all know what you want to do.
	\switchcolumn
	\charactername{钱德勒：}嘿，你们都知道自己想做什么。
	\switchcolumn*
	\charactername{Rachel:} I don't!
	\switchcolumn
	\charactername{瑞秋：}我不知道！
	\switchcolumn*
	\charactername{Chandler:} Hey, you guys in the living room all know what you want to do. You know, you have goals. You have dreams. I don't have a dream.
	\switchcolumn
	\charactername{钱德勒：}嘿，客厅里的你们都知道自己想做什么。你们有目标。你们有梦想。我没有梦想。
	\switchcolumn*
	\charactername{Ross:} Ah, the lesser-known "I don't have a dream" speech.
	\switchcolumn
	\charactername{罗斯：}啊，那不太著名的“我没有梦想”演讲。
	\switchcolumn*
	\ennotmain{Monica enters, excited.}
	\switchcolumn
	\notmain{莫妮卡兴奋地走进来。}
	\switchcolumn*
	\charactername{Monica:} Oh, I love my life, I love my life!
	\switchcolumn
	\charactername{莫妮卡：}哦，我爱我的生活，我爱我的生活！
	\switchcolumn*
	\charactername{Phoebe:} Ooh! Brian's Song!
	\switchcolumn
	\charactername{菲比：}哦！《布赖恩之歌》！
	\switchcolumn*
	\charactername{Rachel:} The meeting with the guy went great?
	\switchcolumn
	\charactername{瑞秋：}和那家伙的会面很顺利？
	\switchcolumn*
	\charactername{Monica:} So great! He showed me where the restaurant's going to be. It's this, it's this cute little place on 10th Street. Not too big, not too small. Just right.
	\switchcolumn
	\charactername{莫妮卡：}太顺利了！他给我看了餐厅的位置。就是，第十大街上一个可爱的小地方。不大不小。刚刚好。
	\switchcolumn*
	\charactername{Chandler:} Was it formerly owned by a blonde woman and some bears?
	\switchcolumn
	\charactername{钱德勒：}它以前是不是由一个金发女人和一些熊拥有的？
	\switchcolumn*
	\charactername{Monica:} So anyway, I'm cooking dinner for him Monday night. You know, kind of like an audition. And Phoebe, he really wants you to be here, which will be great for me because then you can 'ooh' and 'ahh' and make yummy noises.
	\switchcolumn
	\charactername{莫妮卡：}总之，我周一晚上要为他做晚餐。你知道，有点像试镜。还有菲比，他真的很希望你能在场，这对我很棒，因为那样你就可以发出‘哦’‘啊’和美味的声音。
	\switchcolumn*
	\charactername{Rachel:} What are you going to make?
	\switchcolumn
	\charactername{瑞秋：}你打算做什么菜？
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{as though Rachel wasn't paying attention} Yummy noises.
	\switchcolumn
	\charactername{菲比：}\notmain{好像瑞秋没在听一样}美味的声音。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{pause} And Monica, what are you going to make?
	\switchcolumn
	\charactername{瑞秋：}\notmain{停顿}那么莫妮卡，你打算做什么？
	\switchcolumn*
	\charactername{Monica:} I don't know. I don't know. It's just going to be so great!
	\switchcolumn
	\charactername{莫妮卡：}我不知道。我不知道。但这肯定会非常棒！
	\switchcolumn*
	\charactername{Phoebe:} Ooh! I know what you could make! \ennotmain{runs over to join Monica and Rachel in the kitchen} I know! Oh, you should definitely make that thing... you know, with the stuff? \ennotmain{Monica doesn't know.} You know, that thing... with the stuff...? OK, I don't know. \ennotmain{sits down}
	\switchcolumn
	\charactername{菲比：}噢！我知道你可以做什么！\notmain{跑过去加入厨房里的莫妮卡和瑞秋}我知道！哦，你一定要做那个东西……你知道的，用那些材料？\notmain{莫妮卡不知道。}你知道，那个东西……用那些材料……？好吧，我不知道。\notmain{坐下}
	\switchcolumn*
	\charactername{Ross:} Hey guys, does anybody know a good date place in the neighborhood?
	\switchcolumn
	\charactername{罗斯：}嘿，伙计们，有谁知道附近有什么好的约会地点吗？
	\switchcolumn*
	\charactername{Joey:} How about Tony's? If you can finish a 32-ounce steak, it's free.
	\switchcolumn
	\charactername{乔伊：}托尼餐厅怎么样？如果你能吃完一份32盎司的牛排，就免费。
	\switchcolumn*
	\charactername{Ross:} OK, ahem, hey, does anybody know a good place if you're not dating a puma?
	\switchcolumn
	\charactername{罗斯：}好吧，咳咳，嘿，如果不是和一只美洲狮约会，有谁知道一个好地方吗？
	\switchcolumn*
	\charactername{Chandler:} Who are you going out with?
	\switchcolumn
	\charactername{钱德勒：}你要和谁出去？
	\switchcolumn*
	\charactername{Phoebe:} Oh, is this the bug lady?
	\switchcolumn
	\charactername{菲比：}哦，是那个虫子女士吗？
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{trying to sound like a bug} Bzzzz.... I love you, Ross.
	\switchcolumn
	\charactername{瑞秋：}\notmain{试图模仿虫子的声音}嗡嗡嗡……我爱你，罗斯。
	\switchcolumn*
	\charactername{Ross:} Her name is Celia. She's not a bug lady. She's curator of insects at the museum.
	\switchcolumn
	\charactername{罗斯：}她叫西莉亚。她不是什么虫子女士。她是博物馆的昆虫馆长。
	\switchcolumn*
	\charactername{Rachel:} So what are you guys going to do?
	\switchcolumn
	\charactername{瑞秋：}那你们俩打算做什么？
	\switchcolumn*
	\charactername{Ross:} Oh, I just thought we could go out to dinner, and then maybe bring her back to my place and I'd introduce her to my monkey.
	\switchcolumn
	\charactername{罗斯：}哦，我只是想我们可以出去吃晚饭，然后也许带她回我住的地方，把她介绍给我的猴子。
	\switchcolumn*
	\charactername{Chandler:} And he's not speaking metaphorically.
	\switchcolumn
	\charactername{钱德勒：}他可不是在打比方。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{aside to Ross} So.... back to your place...you thinking, maybe... \ennotmain{gestures with hands, back and forth} huh-huh?
	\switchcolumn
	\charactername{乔伊：}\notmain{对罗斯低声说}那么……回你住的地方……你在想，也许……\notmain{用手势比划，来回摆动}嗯嗯？
	\switchcolumn*
	\charactername{Ross:} Well, I don't know.... \ennotmain{gestures} huh-huh.... but I'm hoping \ennotmain{gestures} huh-huh.
	\switchcolumn
	\charactername{罗斯：}嗯，我不知道……\notmain{比划手势}嗯嗯……但我希望\notmain{比划手势}嗯嗯。
	\switchcolumn*
	\charactername{Joey:} I'm telling you, that monkey is a chick magnet! She's going to take one look at his furry, cute little face and it'll seal the deal.
	\switchcolumn
	\charactername{乔伊：}我跟你说，那只猴子是个女孩磁铁！她只要看一眼他那毛茸茸的可爱小脸，这事就成了。
	\switchcolumn*
	\sense{Scene: Ross's apartment, Marcel is hanging from Celia's hair, and she is screaming, trying to get him off.}
	\switchcolumn
	\sense{场景：罗斯的公寓，马塞尔吊在西莉亚的头发上，她尖叫着想把他弄下来。}
	\switchcolumn*
	\charactername{Ross:} Celia, don't worry! Don't scream! He's not going to hurt you! Soothing tones, Celia. Soothing tones! Marcel...
	\switchcolumn
	\charactername{罗斯：}西莉亚，别担心！别尖叫！他不会伤害你的！用安抚的语调，西莉亚。安抚的语调！马塞尔……
	\switchcolumn*
	\charactername{Celia:} I can't stand this! He's got his claws in my...
	\switchcolumn
	\charactername{西莉亚：}我受不了了！他的爪子抓进我的……
	\switchcolumn*
	\charactername{Ross:} Alright... \ennotmain{lifts Marcel away}
	\switchcolumn
	\charactername{罗斯：}好吧……\notmain{把马塞尔抱走}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, everyone is there but Ross and Chandler. Monica is making food, and having everyone try it.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，除了罗斯和钱德勒大家都在。莫妮卡在做食物，让大家品尝。}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Joey} OK, try this salmon mousse.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对乔伊}好，尝尝这个鲑鱼慕斯。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{tasting} Mmmm. Good.
	\switchcolumn
	\charactername{乔伊：}\notmain{品尝}嗯。不错。
	\switchcolumn*
	\charactername{Monica:} Is it better than the other salmon mousse?
	\switchcolumn
	\charactername{莫妮卡：}比另一个鲑鱼慕斯好吗？
	\switchcolumn*
	\charactername{Joey:} It's creamier.
	\switchcolumn
	\charactername{乔伊：}这个更奶油些。
	\switchcolumn*
	\charactername{Monica:} Yeah, well, is that better?
	\switchcolumn
	\charactername{莫妮卡：}是啊，那么，那样更好吗？
	\switchcolumn*
	\charactername{Joey:} I don't know. We're talking about whipped fish, Monica. I'm just happy I'm keeping it down, y'know?
	\switchcolumn
	\charactername{乔伊：}我不知道。我们说的是打发过的鱼，莫妮卡。我只是高兴我没把它吐出来，你知道吗？
	\switchcolumn*
	\ennotmain{Chandler kicks the door closed, angrily. His clothes are askew, he looks beat.}
	\switchcolumn
	\notmain{钱德勒生气地踢上门。他的衣服凌乱，看起来很疲惫。}
	\switchcolumn*
	\charactername{Rachel:} My God! What happened to you?
	\switchcolumn
	\charactername{瑞秋：}天哪！你怎么了？
	\switchcolumn*
	\charactername{Chandler:} Eight and a half hours of aptitude tests, intelligence tests, personality tests... and what do I learn? \ennotmain{he taps the results and reads them} "You are ideally suited for a career in data processing for a large multinational corporation."
	\switchcolumn
	\charactername{钱德勒：}八个半小时的资质测试、智力测试、性格测试……而我学到了什么？\notmain{他敲着结果读道}“你非常适合在大型跨国公司从事数据处理工作。”
	\switchcolumn*
	\charactername{Phoebe:} That's so great! 'Cause you already know how to do that!
	\switchcolumn
	\charactername{菲比：}这太好了！因为你已经知道怎么做了！
	\switchcolumn*
	\charactername{Chandler:} Can you believe it? I mean, don't I seem like somebody who should be doing something really cool? You know, I just always pictured myself doing something...something.
	\switchcolumn
	\charactername{钱德勒：}你们能相信吗？我是说，我看起来不像是应该做些很酷事情的人吗？你知道，我总是想象自己做点什么……有点意义的事情。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{comes up and rubs him on the chest} Oh Chandler, I know, I know... oh, hey! You can see your nipples through this shirt!
	\switchcolumn
	\charactername{瑞秋：}\notmain{走过来在他胸口揉搓}哦，钱德勒，我明白，我明白……哦，嘿！透过这件衬衫能看到你的乳头了！
	\switchcolumn*
	\charactername{Monica:} \ennotmain{brings a plate of tiny appetizers over} Here you go, maybe this'll cheer you up.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{端来一小盘开胃菜}给你，也许这个能让你高兴点。
	\switchcolumn*
	\charactername{Chandler:} Ooh, you know, I had a grape about five hours ago, so I'd better split this with you.
	\switchcolumn
	\charactername{钱德勒：}哦，你知道吗，我大约五小时前吃了一颗葡萄，所以我最好和你分着吃这个。
	\switchcolumn*
	\charactername{Monica:} It's supposed to be that small. It's a pre-appetizer. The French call it an amouz-bouche.
	\switchcolumn
	\charactername{莫妮卡：}它本来就这么小。这是开胃前菜。法语叫它 amouz-bouche。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{tastes it} Well.... it is amouz-ing...
	\switchcolumn
	\charactername{钱德勒：}\notmain{尝了一口}嗯……是挺 amouz-ing 的……\notmain{双关：有趣 / 开胃前菜}
	\switchcolumn*
	\ennotmain{Phone rings. Monica answers it.}
	\switchcolumn
	\notmain{电话响了。莫妮卡接听。}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{on phone} Hello? \ennotmain{Listens} Oh, hi Wendy! \ennotmain{Listens} Yeah, eight o'clock. \ennotmain{Listens} What did we say? Ten dollars an hour?... \ennotmain{Listens} OK, great. \ennotmain{Listens} All right, I'll see you then. Bye. \ennotmain{hangs up}
	\switchcolumn
	\charactername{莫妮卡：}\notmain{打电话}你好？\notmain{听}哦，嗨，温迪！\notmain{听}是的，八点。\notmain{听}我们说的是多少？每小时十美元？……\notmain{听}好的，很好。\notmain{听}好的，到时候见。再见。\notmain{挂断}
	\switchcolumn*
	\charactername{Phoebe:} Ten dollars an hour for what?
	\switchcolumn
	\charactername{菲比：}每小时十美元干什么？
	\switchcolumn*
	\charactername{Monica:} Oh, I asked one of the waitresses at work if she'd help me out.
	\switchcolumn
	\charactername{莫妮卡：}哦，我请我工作的餐厅里的一位女服务员来帮我忙。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{hurt} Waitressing?
	\switchcolumn
	\charactername{瑞秋：}\notmain{受伤地}做服务员？
	\switchcolumn*
	\charactername{Joey:} Uh-oh.
	\switchcolumn
	\charactername{乔伊：}哦哦。
	\switchcolumn*
	\charactername{Monica:} Well... of course I thought of you! But... but...
	\switchcolumn
	\charactername{莫妮卡：}嗯……我当然想到过你！但是……但是……
	\switchcolumn*
	\charactername{Rachel:} But, but?
	\switchcolumn
	\charactername{瑞秋：}但是，但是什么？
	\switchcolumn*
	\charactername{Monica:} But, you see, it's just... this night has to go just perfect, you know? And, well, Wendy's more of a... professional waitress.
	\switchcolumn
	\charactername{莫妮卡：}但是，你看，只是……今晚必须完美进行，你懂吗？而且，温迪更……专业一些。
	\switchcolumn*
	\charactername{Rachel:} Oh! I see. And I've sort of been maintaining my amateur status so that I can waitress in the Olympics.
	\switchcolumn
	\charactername{瑞秋：}哦！我明白了。我一直保持业余身份是为了能参加奥运会服务员比赛。
	\switchcolumn*
	\charactername{Chandler:} You know, I don't mean to brag, but I waited tables at Innsbruck in '76. \ennotmain{dead silence} Amouz-bouche? \ennotmain{holds out tray}
	\switchcolumn
	\charactername{钱德勒：}你知道，我不是吹牛，但我在76年因斯布鲁克当过服务生。\notmain{死寂}开胃前菜？\notmain{递出盘子}
	\switchcolumn*
	\sense{Scene: Ross' apartment, Girl, You'll Be A Woman Soon \ennotmain{the original, not that cruddy Urge Overkill version} is playing. Ross and Celia are kissing passionately.}
	\switchcolumn
	\sense{场景：罗斯的公寓，播放着《女孩，你很快将成为女人》\notmain{原版，不是那个糟糕的 Urge Overkill 翻唱版}。罗斯和西莉亚正在热烈接吻。}
	\switchcolumn*
	\charactername{Celia:} Talk to me.
	\switchcolumn
	\charactername{西莉亚：}跟我说话。
	\switchcolumn*
	\charactername{Ross:} OK.... um, a weird thing happened to me on the train this morning...
	\switchcolumn
	\charactername{罗斯：}好的……嗯，今天早上在火车上我遇到一件怪事……
	\switchcolumn*
	\charactername{Celia:} No no no. Talk... dirty.
	\switchcolumn
	\charactername{西莉亚：}不不不。说……下流话。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{embarrassed} Wha... what, here?
	\switchcolumn
	\charactername{罗斯：}\notmain{尴尬地}什……什么，在这里？
	\switchcolumn*
	\charactername{Celia:} Yes...
	\switchcolumn
	\charactername{西莉亚：}是的……
	\switchcolumn*
	\charactername{Ross:} Ah....
	\switchcolumn
	\charactername{罗斯：}啊……
	\switchcolumn*
	\charactername{Celia:} Say something..... hot.
	\switchcolumn
	\charactername{西莉亚：}说点……火辣的话。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{panicked} Er.... um.....
	\switchcolumn
	\charactername{罗斯：}\notmain{惊慌地}呃……嗯……
	\switchcolumn*
	\charactername{Celia:} What?
	\switchcolumn
	\charactername{西莉亚：}什么？
	\switchcolumn*
	\charactername{Ross:} Um... uh.... vulva.
	\switchcolumn
	\charactername{罗斯：}嗯……呃……阴户。
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Chandler and Joey's, Joey and Ross are there, discussing what happened last night.}
	\switchcolumn
	\sense{场景：钱德勒和乔伊的公寓，乔伊和罗斯在那里，讨论昨晚发生的事。}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{in disbelief} Vulva?
	\switchcolumn
	\charactername{乔伊：}\notmain{难以置信地}阴户？
	\switchcolumn*
	\charactername{Ross:} Alright, I panicked, alright? She took me by surprise. You know, but it wasn't a total loss. I mean, we ended up cuddling.
	\switchcolumn
	\charactername{罗斯：}好吧，我慌了，行了吧？她让我措手不及。你知道，但也不全是损失。我是说，我们最后抱在一起了。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{sarcastic} Whoaa!! You cuddled? How many times??
	\switchcolumn
	\charactername{乔伊：}\notmain{讽刺地}哇哦！！你们抱在一起了？抱了多少次？？
	\switchcolumn*
	\charactername{Ross:} Shut up! It was nice. I just... I don't think I'm the dirty-talking kind of guy, you know?
	\switchcolumn
	\charactername{罗斯：}闭嘴！感觉挺好的。我只是……我觉得我不是那种会说下流话的人，你知道吗？
	\switchcolumn*
	\charactername{Joey:} What's the big deal? You just say what you want to do to her. Or what you want her to do to you. Or what you think other people might be doing to each other. I'll tell you what. Just try something on me.
	\switchcolumn
	\charactername{乔伊：}有什么大不了的？你只要说你想对她做什么。或者你想让她对你做什么。或者你觉得别人可能在互相做什么。我告诉你。就拿我试试。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{deadpan} Please be kidding.
	\switchcolumn
	\charactername{罗斯：}\notmain{面无表情地}请告诉我你在开玩笑。
	\switchcolumn*
	\charactername{Joey:} Why not? Come on! Just, just close your eyes and tell me what you'd like to be doing right now.
	\switchcolumn
	\charactername{乔伊：}为什么不呢？来吧！就，就闭上眼睛告诉我你现在想做什么。
	\switchcolumn*
	\charactername{Ross:} OK. \ennotmain{closes eyes} I'm in my apartment...
	\switchcolumn
	\charactername{罗斯：}好吧。\notmain{闭上眼睛}我在我的公寓里……
	\switchcolumn*
	\charactername{Joey:} ....yeah... what else?
	\switchcolumn
	\charactername{乔伊：}……是啊……还有呢？
	\switchcolumn*
	\charactername{Ross:} That's it. I'm in my apartment, you're not there, we're not having this conversation. \ennotmain{gets up, walks across room}
	\switchcolumn
	\charactername{罗斯：}就这样。我在我的公寓里，你不在那儿，我们没有在进行这场对话。\notmain{站起来，穿过房间}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{walks to catch up to him} Alright, look, I'll start, OK?
	\switchcolumn
	\charactername{乔伊：}\notmain{走过去追上他}好吧，听着，我来开头，好吗？
	\switchcolumn*
	\charactername{Ross:} Joey, please.
	\switchcolumn
	\charactername{罗斯：}乔伊，别这样。
	\switchcolumn*
	\charactername{Joey:} Come on. Come on. Alright, ready, look! \ennotmain{in a low voice} Oh... Ross.... you get me so hot. I want your lips on me now.
	\switchcolumn
	\charactername{乔伊：}来吧。来吧。好了，准备好，听着！\notmain{压低声音}哦……罗斯……你让我浑身发热。我现在就想要你的嘴唇贴着我。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{impressed} Wow.
	\switchcolumn
	\charactername{罗斯：}\notmain{印象深刻地}哇。
	\switchcolumn*
	\charactername{Joey:} Alright, now you say something.
	\switchcolumn
	\charactername{乔伊：}好了，现在你说点。
	\switchcolumn*
	\charactername{Ross:} I... ahem... I really don't think so.
	\switchcolumn
	\charactername{罗斯：}我……咳咳……我真的觉得不行。
	\switchcolumn*
	\charactername{Joey:} Come on! You like this woman, right?
	\switchcolumn
	\charactername{乔伊：}来嘛！你喜欢这个女人，对吧？
	\switchcolumn*
	\charactername{Ross:} Yeah.
	\switchcolumn
	\charactername{罗斯：}是啊。
	\switchcolumn*
	\charactername{Joey:} You want to see her again, right?
	\switchcolumn
	\charactername{乔伊：}你想再见到她，对吧？
	\switchcolumn*
	\charactername{Ross:} Sure.
	\switchcolumn
	\charactername{罗斯：}当然。
	\switchcolumn*
	\charactername{Joey:} Well if you can't talk dirty to me, how're you going to talk dirty to her? Now tell me you want to caress my butt!
	\switchcolumn
	\charactername{乔伊：}好吧，如果你都不能对我说下流话，你怎么对她说下流话？现在告诉我你想抚摸我的屁股！
	\switchcolumn*
	\charactername{Ross:} OK, turn around. \ennotmain{Joey looks taken aback} I just don't want you staring at me when I'm doing this.
	\switchcolumn
	\charactername{罗斯：}好吧，转过去。\notmain{乔伊看起来吃了一惊}我只是不想你在我做这个的时候盯着我看。
	\switchcolumn*
	\charactername{Joey:} \ennotmain{turning around} Alright, alright. I'm around. Go ahead.
	\switchcolumn
	\charactername{乔伊：}\notmain{转身}好吧，好吧。我转过来了。说吧。
	\switchcolumn*
	\charactername{Ross:} Ahem... I want.... OK, I want to... feel your... hot, soft skin with my lips.
	\switchcolumn
	\charactername{罗斯：}咳咳……我想……好吧，我想……用我的嘴唇感受你……火热柔软的皮肤。
	\switchcolumn*
	\charactername{Joey:} There you go! Keep going. Keep going!
	\switchcolumn
	\charactername{乔伊：}这就对了！继续。继续！
	\switchcolumn*
	\charactername{Ross:} I, er...
	\switchcolumn
	\charactername{罗斯：}我，呃……
	\switchcolumn*
	\ennotmain{At this point, Chandler walks into the living room from his bedroom. Ross and Joey both have their backs to him, so they don't notice. Chandler sees the situation and remains quiet, watching.}
	\switchcolumn
	\notmain{这时，钱德勒从卧室走进客厅。罗斯和乔伊都背对着他，所以没注意到。钱德勒看到这情景，保持安静，看着。}
	\switchcolumn*
	\charactername{Ross:} I want to take my tongue... and...
	\switchcolumn
	\charactername{罗斯：}我想用我的舌头……然后……
	\switchcolumn*
	\ennotmain{Chandler is completely astounded.}
	\switchcolumn
	\notmain{钱德勒完全惊呆了。}
	\switchcolumn*
	\charactername{Ross:} ....and....
	\switchcolumn
	\charactername{罗斯：}……然后……
	\switchcolumn*
	\charactername{Joey:} Say it... say it!
	\switchcolumn
	\charactername{乔伊：}说出来……说出来！
	\switchcolumn*
	\charactername{Ross:} ...run it all over your body until you're... trembling with... with...
	\switchcolumn
	\charactername{罗斯：}……让它游遍你的全身直到你……颤抖着……因为……
	\switchcolumn*
	\ennotmain{Chandler leans back against the wall and Ross and Joey hear him. Ross and Joey both notice at the same time. They slowly stop, and then very slowly turn around to see Chandler staring at them.}
	\switchcolumn
	\notmain{钱德勒靠到墙上，罗斯和乔伊听到了。罗斯和乔伊同时注意到了。他们慢慢停下，然后非常缓慢地转过身，看到钱德勒正盯着他们。}
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{smiling}....with??
	\switchcolumn
	\charactername{钱德勒：}\notmain{微笑着}……因为什么？？
	\switchcolumn*
	\charactername{Ross:} \ennotmain{rushing to explain} Funny story!
	\switchcolumn
	\charactername{罗斯：}\notmain{急忙解释}说来好笑！
	\switchcolumn*
	\charactername{Joey:} You're not going to believe this!
	\switchcolumn
	\charactername{乔伊：}你不会相信的！
	\switchcolumn*
	\charactername{Chandler:} It's OK. It's OK. I was always rooting for you two kids to get together.
	\switchcolumn
	\charactername{钱德勒：}没关系。没关系。我一直都支持你们两个小家伙在一起的。
	\switchcolumn*
	\charactername{Joey:} Hey Chandler, while you were sleeping that guy from your old job called again.
	\switchcolumn
	\charactername{乔伊：}嘿，钱德勒，你睡觉的时候你原来工作地方那个人又打电话来了。
	\switchcolumn*
	\charactername{Chandler:} Again?
	\switchcolumn
	\charactername{钱德勒：}又打来了？
	\switchcolumn*
	\charactername{Joey:} And again, and again, and again... \ennotmain{phone rings, he answers} Hello? \ennotmain{hands phone to Chandler} And again.
	\switchcolumn
	\charactername{乔伊：}一遍，又一遍，又一遍……\notmain{电话响，他接听}喂？\notmain{把电话递给钱德勒}又来了。
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{on phone} Hey Mr. Kostelic! How's life on the fifteenth floor? \ennotmain{Listens} Yeah, I miss you too. \ennotmain{Listens} Yeah, it's a lot less satisfying to steal pens from your own home, you know? \ennotmain{Listens} Well, that's very generous \ennotmain{Listens} er, but look, this isn't about the money. I need something that's more than a job. I need something I can really care about.... \ennotmain{Listens} And that's on top of the yearly bonus structure you mentioned earlier? \ennotmain{Listens} Look, Al, Al... I'm not playing hardball here, OK? This is not a negotiation, this is a rejection! \ennotmain{Listens} No! No! No, stop saying numbers! I'm telling you, you've got the wrong guy! You've got the wrong guy! \ennotmain{Listens} I'll see you on Monday! \ennotmain{slams the phone down}
	\switchcolumn
	\charactername{钱德勒：}\notmain{打电话}嘿，科斯特利克先生！十五楼的生活怎么样？\notmain{听}是啊，我也想你。\notmain{听}是啊，从自己家里偷笔可没那么有满足感，你知道吗？\notmain{听}嗯，这非常慷慨\notmain{听}呃，但是听着，这不是钱的问题。我需要比一份工作更多的东西。我需要一些我真正能关心在乎的东西……\notmain{听}这个是在你之前提到的年度奖金结构之外的？\notmain{听}听着，阿尔，阿尔……我不是在玩硬的，好吗？这不是谈判，这是拒绝！\notmain{听}不！不！不，别再说数字了！我告诉你，你找错人了！你找错人了！\notmain{听}周一见！\notmain{砰地挂断电话}
	\switchcolumn*
	\sense{Scene: Chandler's new window office, he is showing Phoebe around.}
	\switchcolumn
	\sense{场景：钱德勒新的带窗办公室，他正带菲比参观。}
	\switchcolumn*
	\charactername{Chandler:} Well?
	\switchcolumn
	\charactername{钱德勒：}怎么样？
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{excited} Wow! It's huge! It's so much bigger than the cubicle. Oh, this is a cube.
	\switchcolumn
	\charactername{菲比：}\notmain{兴奋地}哇！好大！比小隔间大太多了。哦，这还是个立方体。
	\switchcolumn*
	\charactername{Chandler:} Look at this! \ennotmain{he opens the curtain to a view of New York City}
	\switchcolumn
	\charactername{钱德勒：}看这个！\notmain{他拉开窗帘，纽约市的景色映入眼帘}
	\switchcolumn*
	\charactername{Phoebe:} Oh! You have a window!
	\switchcolumn
	\charactername{菲比：}哦！你有窗户！
	\switchcolumn*
	\charactername{Chandler:} Yes indeedy! \ennotmain{they look outside} With a beautiful view of...
	\switchcolumn
	\charactername{钱德勒：}确实有！\notmain{他们看向窗外}窗外有美丽的景色……
	\switchcolumn*
	\charactername{Phoebe:} Oh look! That guy's peeing!
	\switchcolumn
	\charactername{菲比：}哦看！那个人在小便！
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{walks away from window} OK, that's enough of the view. Check this out, look at this. Sit down, sit down.
	\switchcolumn
	\charactername{钱德勒：}\notmain{从窗边走开}好吧，景色看够了。看看这个，瞧这个。坐下，坐下。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{sitting} OK.
	\switchcolumn
	\charactername{菲比：}\notmain{坐下}好的。
	\switchcolumn*
	\charactername{Chandler:} This is great! \ennotmain{he presses a button on his intercom} Helen, could you come in here for a moment?
	\switchcolumn
	\charactername{钱德勒：}这太棒了！\notmain{他按下对讲机按钮}海伦，你能进来一下吗？
	\switchcolumn*
	\ennotmain{An unamused woman walks into the office.}
	\switchcolumn
	\notmain{一位面无表情的女士走进办公室。}
	\switchcolumn*
	\charactername{Chandler:} Thank you Helen, that'll be all.
	\switchcolumn
	\charactername{钱德勒：}谢谢你海伦，没事了。
	\switchcolumn*
	\ennotmain{She leaves, obviously perturbed.}
	\switchcolumn
	\notmain{她离开，显然有些恼怒。}
	\switchcolumn*
	\charactername{Chandler:} Last time I do that, I promise.
	\switchcolumn
	\charactername{钱德勒：}我保证这是最后一次这么做了。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Monica is on the phone. Rachel walks in and overhears the conversation.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，莫妮卡在打电话。瑞秋走进来，听到了对话。}
	\switchcolumn*
	\charactername{Monica:} \ennotmain{shouting on phone} Wendy, we had a deal! \ennotmain{Listens} Yeah, you promised! Wendy! Wendy! Wendy! \ennotmain{hangs up}
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对着电话大喊}温迪，我们说好的！\notmain{听}是的，你答应过的！温迪！温迪！温迪！\notmain{挂断}
	\switchcolumn*
	\charactername{Rachel:} Who was that?
	\switchcolumn
	\charactername{瑞秋：}谁啊？
	\switchcolumn*
	\charactername{Monica:} Wendy bailed. I have no waitress.
	\switchcolumn
	\charactername{莫妮卡：}温迪放鸽子了。我没有服务员了。
	\switchcolumn*
	\charactername{Rachel:} Oh... that's too bad. Bye bye. \ennotmain{she walks away towards the door}
	\switchcolumn
	\charactername{瑞秋：}哦……那太糟了。拜拜。\notmain{她向门口走去}
	\switchcolumn*
	\charactername{Monica:} Ten dollars an hour.
	\switchcolumn
	\charactername{莫妮卡：}每小时十美元。
	\switchcolumn*
	\charactername{Rachel:} No.
	\switchcolumn
	\charactername{瑞秋：}不行。
	\switchcolumn*
	\charactername{Monica:} Twelve dollars an hour.
	\switchcolumn
	\charactername{莫妮卡：}每小时十二美元。
	\switchcolumn*
	\charactername{Rachel:} Mon. I wish I could, but I've made plans to walk around.
	\switchcolumn
	\charactername{瑞秋：}莫。我希望能帮你，但我已经计划好出去走走。
	\switchcolumn*
	\charactername{Monica:} You know, Rachel, when you ran out of your wedding, I was there for you. I put a roof over your head, and if that means nothing to you... \ennotmain{Rachel isn't buying it, desperate} twenty dollars an hour.
	\switchcolumn
	\charactername{莫妮卡：}你知道，瑞秋，当你逃婚的时候，我帮了你。我给了你住的地方，如果这对你来说毫无意义……\notmain{瑞秋不为所动，莫妮卡绝望地}每小时二十美元。
	\switchcolumn*
	\charactername{Rachel:} Done.
	\switchcolumn
	\charactername{瑞秋：}成交。
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, later. Rachel is waitressing, Monica is cooking. Phoebe walks in with Steve \ennotmain{Crystal Duck winner Jon Lovitz}.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，稍后。瑞秋在做服务员，莫妮卡在做菜。菲比带着史蒂夫\notmain{水晶鸭奖得主乔恩·洛维兹}进来。}
	\switchcolumn*
	\charactername{Rachel:} Well hello! Welcome to Monica's. May I take your coat?
	\switchcolumn
	\charactername{瑞秋：}你好！欢迎来到莫妮卡餐厅。我能帮您拿外套吗？
	\switchcolumn*
	\charactername{Monica:} Hi Steve!
	\switchcolumn
	\charactername{莫妮卡：}嗨，史蒂夫！
	\switchcolumn*
	\charactername{Steve:} Hello, Monica. \ennotmain{to Rachel} Hello, greeter girl.
	\switchcolumn
	\charactername{史蒂夫：}你好，莫妮卡。\notmain{对瑞秋}你好，迎宾小姐。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{to Steve} This is Rachel.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{对史蒂夫}这是瑞秋。
	\switchcolumn*
	\charactername{Steve:} \ennotmain{unconcerned} Yeah, OK.
	\switchcolumn
	\charactername{史蒂夫：}\notmain{不以为意地}是啊，好的。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{overemphasizing} Mmmmmm! Everything smells so delicious! You know, I can't remember a time I smelt such a delicious combination of \ennotmain{Monica signals her to stop} of, OK, smells.
	\switchcolumn
	\charactername{菲比：}\notmain{过分强调地}嗯——！每样东西闻起来都这么香！你知道，我不记得什么时候闻到过这么香……\notmain{莫妮卡示意她停下}香……好吧，气味组合。
	\switchcolumn*
	\charactername{Steve:} It's a lovely apartment.
	\switchcolumn
	\charactername{史蒂夫：}这公寓很漂亮。
	\switchcolumn*
	\charactername{Monica:} Oh, thank you. Would you like a tour?
	\switchcolumn
	\charactername{莫妮卡：}哦，谢谢。想参观一下吗？
	\switchcolumn*
	\charactername{Steve:} I was just being polite, but, alright.
	\switchcolumn
	\charactername{史蒂夫：}我只是客气一下，不过，好吧。
	\switchcolumn*
	\ennotmain{They leave on the tour and Rachel goes to follow them but Phoebe stops her and drags her into the kitchen.}
	\switchcolumn
	\notmain{他们去参观，瑞秋想跟上但菲比拦住她，把她拉进厨房。}
	\switchcolumn*
	\charactername{Rachel:} What's up?
	\switchcolumn
	\charactername{瑞秋：}怎么了？
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{whispers} In the cab, on the way over, Steve blazed up a doobie.
	\switchcolumn
	\charactername{菲比：}\notmain{小声地}在出租车上，来的路上，史蒂夫抽了根大麻烟。
	\switchcolumn*
	\charactername{Rachel:} What?
	\switchcolumn
	\charactername{瑞秋：}什么？
	\switchcolumn*
	\charactername{Phoebe:} Smoked a joint? You know, lit a bone? Weed? Hemp? Ganja?
	\switchcolumn
	\charactername{菲比：}抽大麻？你知道，点根烟？大麻？麻？印度大麻？
	\switchcolumn*
	\charactername{Rachel:} OK, OK. I'm with you, Cheech. OK.
	\switchcolumn
	\charactername{瑞秋：}好吧，好吧。我懂了，奇奇。好吧。
	\switchcolumn*
	\charactername{Steve:} \ennotmain{from the living room} Is it dry in here? \ennotmain{licks his lips}
	\switchcolumn
	\charactername{史蒂夫：}\notmain{从客厅}这里很干吗？\notmain{舔嘴唇}
	\switchcolumn*
	\charactername{Rachel:} Let me, let me get you some wine!
	\switchcolumn
	\charactername{瑞秋：}让我，让我给你拿点酒！
	\switchcolumn*
	\charactername{Monica:} Yeah, I think we're ready for our first course. \ennotmain{Steve sits, Monica brings over a tray} OK, um, these are rot-shrimp ravioli, and celantro pondou sauce... \ennotmain{Steve starts to eat them one by one, quickly}... with just a touch of mints... and... \ennotmain{he finishes}... ginger.
	\switchcolumn
	\charactername{莫妮卡：}是的，我想我们可以上前菜了。\notmain{史蒂夫坐下，莫妮卡端来一个托盘}好的，嗯，这是烤虾意式饺子，配香菜庞杜酱……\notmain{史蒂夫开始快速地把它们一个接一个吃掉}……只加了一点薄荷……和……\notmain{他吃完了}……姜。
	\switchcolumn*
	\charactername{Steve:} Well, smack my ass and call me Judy! These are fantastic!
	\switchcolumn
	\charactername{史蒂夫：}哎呀，真见鬼！太棒了！
	\switchcolumn*
	\charactername{Monica:} I'm so glad you liked them!
	\switchcolumn
	\charactername{莫妮卡：}真高兴你喜欢！
	\switchcolumn*
	\charactername{Steve:} Like 'em? I could eat a hundred of them!
	\switchcolumn
	\charactername{史蒂夫：}喜欢？我能吃一百个！
	\switchcolumn*
	\charactername{Monica:} Oh, well... um, that's all there are of these. But in about eight and a half minutes, we'll be serving some delicious onion tartlets.
	\switchcolumn
	\charactername{莫妮卡：}哦，那个……嗯，这些只有这些了。但大约八分半钟后，我们会提供一些美味的洋葱挞。
	\switchcolumn*
	\charactername{Steve:} Tartlets. Tartlets. Tartlets. The word has lost all meaning. \ennotmain{he gets up and goes into the kitchen}
	\switchcolumn
	\charactername{史蒂夫：}挞。挞。挞。这个词已经失去了所有意义。\notmain{他起身走进厨房}
	\switchcolumn*
	\charactername{Rachel:} Excuse me? Can I help you with anything?
	\switchcolumn
	\charactername{瑞秋：}打扰一下？需要我帮忙吗？
	\switchcolumn*
	\charactername{Steve:} You know, I don't know what I'm looking for.
	\switchcolumn
	\charactername{史蒂夫：}你知道，我不知道我在找什么。
	\switchcolumn*
	\ennotmain{Rachel tries to get Monica's attention to tell her Steve is stoned. She pretends to drag on a joint, and Monica thinks she's giving her the 'OK' signal. Then Rachel does it again, inhaling deeply this time. Monica waves it off as though she doesn't believe it.}
	\switchcolumn
	\notmain{瑞秋试图引起莫妮卡的注意，告诉她史蒂夫嗨了。她假装抽大麻烟，莫妮卡以为她在给她打“OK”手势。然后瑞秋又做了一次，这次深吸一口。莫妮卡挥挥手，好像不相信。}
	\switchcolumn*
	\charactername{Steve:} \ennotmain{from kitchen} Ah, cool! Taco shells! \ennotmain{Rachel motions, "You see!"} You know, these are... they're like a little corn envelope.
	\switchcolumn
	\charactername{史蒂夫：}\notmain{从厨房}啊，酷！玉米卷饼皮！\notmain{瑞秋比划着：“你看吧！”}你知道，这些是……它们就像小玉米信封。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{joining him and taking the taco shells} You know that? You don't want to spoil your appetite.
	\switchcolumn
	\charactername{莫妮卡：}\notmain{加入他，拿走玉米卷饼皮}你知道吗？别毁了你的胃口。
	\switchcolumn*
	\charactername{Steve:} \ennotmain{looking in cabinets} Hey! Sugar-O's! \ennotmain{grabs the cereal box}
	\switchcolumn
	\charactername{史蒂夫：}\notmain{看着橱柜}嘿！糖-O麦片！\notmain{抓起麦片盒}
	\switchcolumn*
	\charactername{Monica:} You know, if you just wait another... six and a half minutes...
	\switchcolumn
	\charactername{莫妮卡：}你知道，如果你再等……六分半钟……
	\switchcolumn*
	\charactername{Steve:} Macaroni and cheese! We gotta make this!
	\switchcolumn
	\charactername{史蒂夫：}通心粉和奶酪！我们得做这个！
	\switchcolumn*
	\charactername{Monica:} No, we don't. \ennotmain{reaches for box}
	\switchcolumn
	\charactername{莫妮卡：}不，不用。\notmain{伸手拿盒子}
	\switchcolumn*
	\charactername{Steve:} Oh, OK. \ennotmain{he drops the box on the floor} Oh, sorry. \ennotmain{When she bends down to pick it up he grabs a package of Gummi-bears from the cabinet.}
	\switchcolumn
	\charactername{史蒂夫：}哦，好吧。\notmain{他把盒子掉在地上}哦，对不起。\notmain{当她弯腰去捡时，他从橱柜里抓了一包小熊软糖。}
	\switchcolumn*
	\charactername{Monica:} Why don't you just have a seat here? \ennotmain{he sits at the table, then tries to secretly eat the Gummi-bears. Monica spots him.} OK... give me the Gummi-bears.
	\switchcolumn
	\charactername{莫妮卡：}你为什么不就在这里坐下呢？\notmain{他在桌旁坐下，然后试图偷偷吃小熊软糖。莫妮卡发现了他。}好吧……把小熊软糖给我。
	\switchcolumn*
	\charactername{Steve:} \ennotmain{childishly} No.
	\switchcolumn
	\charactername{史蒂夫：}\notmain{孩子气地}不给。
	\switchcolumn*
	\charactername{Monica:} Give them to me.
	\switchcolumn
	\charactername{莫妮卡：}把它们给我。
	\switchcolumn*
	\charactername{Steve:} Alright, we'll share.
	\switchcolumn
	\charactername{史蒂夫：}好吧，我们分着吃。
	\switchcolumn*
	\charactername{Monica:} No, give me the...
	\switchcolumn
	\charactername{莫妮卡：}不，给我……
	\switchcolumn*
	\charactername{Steve:} Well then you can't have any. \ennotmain{she grabs for the package, and it breaks open. Gummi-bears fly everywhere, some into the punch bowl on the table.} Bear overboard! I think he's drowning. \ennotmain{he throws some Sugar-O's into the punch bowl} Hey fellows! Grab on a Sugar-O... save yourself! \ennotmain{Mimicking the bears} "Help! I'm drowning! Help!"
	\switchcolumn
	\charactername{史蒂夫：}那你就别想吃。\notmain{她伸手去抓包装，包装破了。小熊软糖飞得到处都是，一些掉进了桌上的潘趣酒碗里。}熊落水了！我觉得他淹死了。\notmain{他把一些糖-O麦片扔进潘趣酒碗}嘿，伙计们！抓住一颗糖-O……救救自己！\notmain{模仿小熊的声音}“救命！我要淹死了！救命！”
	\switchcolumn*
	\charactername{Monica:} \ennotmain{furious} That's it! Dinner is over!
	\switchcolumn
	\charactername{莫妮卡：}\notmain{愤怒地}够了！晚餐结束！
	\switchcolumn*
	\charactername{Steve:} What?
	\switchcolumn
	\charactername{史蒂夫：}什么？
	\switchcolumn*
	\charactername{Monica:} What?
	\switchcolumn
	\charactername{莫妮卡：}什么？
	\switchcolumn*
	\charactername{Steve:} Why?
	\switchcolumn
	\charactername{史蒂夫：}为什么？
	\switchcolumn*
	\charactername{Monica:} Why? It's just that I've waited seven years for an opportunity like this, and you can't even wait four and a half minutes for a stupid onion tartlet?
	\switchcolumn
	\charactername{莫妮卡：}为什么？只是我等了七年才等到这样一个机会，而你连四分半钟都等不了，就为了一块愚蠢的洋葱挞？
	\switchcolumn*
	\ennotmain{The oven goes off.}
	\switchcolumn
	\notmain{烤箱提示音响起。}
	\switchcolumn*
	\charactername{Steve:} \ennotmain{excited} Hey!
	\switchcolumn
	\charactername{史蒂夫：}\notmain{兴奋地}嘿！
	\switchcolumn*
	\sense{Scene: Central Perk, all are there except Chandler.}
	\switchcolumn
	\sense{场景：中央公园咖啡厅，除了钱德勒大家都在。}
	\switchcolumn*
	\charactername{Joey:} What a tool!
	\switchcolumn
	\charactername{乔伊：}真是个蠢货！
	\switchcolumn*
	\charactername{Rachel:} You don't want to work for a guy like that.
	\switchcolumn
	\charactername{瑞秋：}你不想为那种人工作。
	\switchcolumn*
	\charactername{Ross:} Yeah!
	\switchcolumn
	\charactername{罗斯：}是啊！
	\switchcolumn*
	\charactername{Monica:} I know... it's just... I thought this was, you know... it.
	\switchcolumn
	\charactername{莫妮卡：}我知道……只是……我以为这次就是，你知道……那个机会。
	\switchcolumn*
	\charactername{Ross:} Look, you'll get there. You're an amazing chef.
	\switchcolumn
	\charactername{罗斯：}听着，你会成功的。你是个很棒的厨师。
	\switchcolumn*
	\charactername{Phoebe:} Yeah! You know all those yummy noises? I wasn't faking.
	\switchcolumn
	\charactername{菲比：}是啊！你知道所有那些美味的声音吗？我不是装的。
	\switchcolumn*
	\ennotmain{Ross gets up and goes over to the counter and Joey follows him.}
	\switchcolumn
	\notmain{罗斯起身走到柜台，乔伊跟着他。}
	\switchcolumn*
	\charactername{Joey:} \ennotmain{to Ross} So, er... how did it go with Celia?
	\switchcolumn
	\charactername{乔伊：}\notmain{对罗斯}那么，呃……和西莉亚怎么样了？
	\switchcolumn*
	\charactername{Ross:} Oh, I was unbelievable.
	\switchcolumn
	\charactername{罗斯：}哦，我表现得难以置信。
	\switchcolumn*
	\charactername{Joey:} All right, Ross!
	\switchcolumn
	\charactername{乔伊：}干得好，罗斯！
	\switchcolumn*
	\charactername{Ross:} I was the James Michener of dirty talk. It was the most elaborate filth you have ever heard. I mean, there were characters, plot lines, themes, a motif... at one point there were villagers.
	\switchcolumn
	\charactername{罗斯：}我是下流话界的詹姆斯·米切纳。那是有史以来最精心设计的污言秽语。我是说，有角色，有情节线，有主题，有一个主题动机……甚至一度出现了村民。
	\switchcolumn*
	\charactername{Joey:} Whoa! And the... \ennotmain{gestures with hands, back and forth} huh-huh?
	\switchcolumn
	\charactername{乔伊：}哇！那……\notmain{用手势比划，来回摆动}嗯嗯？
	\switchcolumn*
	\charactername{Ross:} Well, ahem... you know, by the time we'd finished with all the dirty talk, it was kinda late... and we were both kind of exhausted, so uh...
	\switchcolumn
	\charactername{罗斯：}嗯，咳咳……你知道，等我们说完所有下流话，已经有点晚了……而且我们都有些筋疲力尽了，所以呃……
	\switchcolumn*
	\charactername{Joey:} You cuddled.
	\switchcolumn
	\charactername{乔伊：}你们抱在一起了。
	\switchcolumn*
	\charactername{Ross:} Yeah, which was nice.
	\switchcolumn
	\charactername{罗斯：}是啊，感觉不错。
	\switchcolumn*
	\charactername{Phoebe:} You guys wanna try and catch a late movie or something?
	\switchcolumn
	\charactername{菲比：}你们想去看个夜场电影之类的吗？
	\switchcolumn*
	\charactername{Rachel:} Maybe, but shouldn't we wait for Chandler?
	\switchcolumn
	\charactername{瑞秋：}也许，但我们不该等等钱德勒吗？
	\switchcolumn*
	\charactername{Joey:} Yeah, where the hell is he?
	\switchcolumn
	\charactername{乔伊：}是啊，他到底在哪儿？
	\switchcolumn*
	\sense{Scene: Chandler's office, he's on the phone, agitated.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，他在打电话，很激动。}
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{on phone} Yes, Fran. I know what time it is, but I'm looking at the WENUS and I'm not happy!... \ennotmain{Listens} Oh, really, really, really? Well, let me tell you something... you will care about it, because I care about it! You got it? Good! \ennotmain{slams phone down, then leans back and realizes what just happened} Whooooaaaa....
	\switchcolumn
	\charactername{钱德勒：}\notmain{打电话}是的，弗兰。我知道现在几点了，但我看着 WENUS，我不高兴！……\notmain{听}哦，真的，真的，真的？好吧，让我告诉你……你会关心的，因为我关心！明白了吗？好！\notmain{砰地挂断电话，然后靠回去，意识到刚刚发生了什么}喔……
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Phoebe's massage parlour, she has Steve on the table, and is giving him an extra-painful massage.}
	\switchcolumn
	\sense{场景：菲比的按摩店，她把史蒂夫放在按摩床上，给他做一次特别痛的按摩。}
	\switchcolumn*
	\charactername{Phoebe:} How's this? \ennotmain{presses down hard}
	\switchcolumn
	\charactername{菲比：}这个感觉怎么样？\notmain{用力按压}
	\switchcolumn*
	\charactername{Steve:} Eeeee!
	\switchcolumn
	\charactername{史蒂夫：}哎哟！
	\switchcolumn*
	\charactername{Phoebe:} Sorry. How about over here? \ennotmain{presses down hard again}
	\switchcolumn
	\charactername{菲比：}抱歉。这里呢？\notmain{再次用力按压}
	\switchcolumn*
	\charactername{Steve:} Aaaaah!
	\switchcolumn
	\charactername{史蒂夫：}啊——！
	\switchcolumn*
	\charactername{Phoebe:} See, that just means it's working. Does this hurt? \ennotmain{presses down elsewhere}
	\switchcolumn
	\charactername{菲比：}看，这说明有效果。这里疼吗？\notmain{按别处}
	\switchcolumn*
	\charactername{Steve:} No.
	\switchcolumn
	\charactername{史蒂夫：}不疼。
	\switchcolumn*
	\charactername{Phoebe:} What about this? \ennotmain{she starts using her elbows on his back, he yells in pain}
	\switchcolumn
	\charactername{菲比：}这个呢？\notmain{她开始用肘部压他的背，他疼得大叫}
	\switchcolumn*
	\charactername{Steve:} Aaaaahhh!!
	\switchcolumn
	\charactername{史蒂夫：}啊——！！
	\switchcolumn*
	\charactername{Phoebe:} There you go! \ennotmain{She continues to work him over with her elbows and he continues to yell in pain.}
	\switchcolumn
	\charactername{菲比：}这就对了！\notmain{她继续用肘部给他按摩，他继续痛苦地大叫。}
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage