\begin{paracol}{2}
	\sense{Scene: Rift’s Restaurant, as seen in Mad About You, Joey and Chandler are there.}
	\switchcolumn
	\sense{场景：里夫特餐厅，出自《我为卿狂》剧集。乔伊和钱德勒在场。}
	\switchcolumn*
	\charactername{Chandler:} This is unbelievable. It’s been like a half an hour. If this was a cartoon, you’d be looking like a ham right about now.
	\switchcolumn
	\charactername{钱德勒：}真不敢相信。都快半个小时了。要是这是在动画片里，你现在看起来就像块火腿了。
	\switchcolumn*
	\ennotmain{Ursula Buffay, Phoebe’s identical twin sister, is waiting on tables in her inimitable manner.}
	\switchcolumn
	\ennotmain{菲比的同卵双胞胎姐姐厄休拉·布菲，以她独有的方式正在招待客人。}
	\switchcolumn*
	\charactername{Joey:} There’s the waitress. Excuse me, Miss. Hello, Miss?
	\switchcolumn
	\charactername{乔伊：}服务员在那儿。打扰一下，小姐。你好，小姐？
	\switchcolumn*
	\ennotmain{Ursula spins around looking puzzled, quite unable to tell where the sound is coming from.}
	\switchcolumn
	\ennotmain{厄休拉转过身，一脸困惑，完全无法分辨声音是从哪里传来的。}
	\switchcolumn*
	\charactername{Chandler:} It’s Phoebe! Hi!
	\switchcolumn
	\charactername{钱德勒：}是菲比！嗨！
	\switchcolumn*
	\ennotmain{Ursula notices Joey waving his hand, and comes over.}
	\switchcolumn
	\ennotmain{厄休拉注意到乔伊在挥手，便走了过来。}
	\switchcolumn*
	\charactername{Ursula:} Hi. Okay, will that be all?
	\switchcolumn
	\charactername{厄休拉：}嗨。好了，就这些吗？
	\switchcolumn*
	\charactername{Chandler:} Wait, wait! Wh-what are you doing here?
	\switchcolumn
	\charactername{钱德勒：}等等，等等！你…你在这干嘛？
	\switchcolumn*
	\charactername{Ursula:} Yeah, um, I was over there, then you said, "Excuse me, hello Miss," so now I’m here.
	\switchcolumn
	\charactername{厄休拉：}是啊，嗯，我刚才在那边，然后你说“打扰一下，你好小姐”，所以我现在就到这儿来了。
	\switchcolumn*
	\charactername{Joey:} No, no... how come you are working here?
	\switchcolumn
	\charactername{乔伊：}不，不…你怎么会在这工作？
	\switchcolumn*
	\charactername{Ursula:} Right, yeah, ’cause its close to where I live, and the aprons are really cute.
	\switchcolumn
	\charactername{厄休拉：}对，是的，因为这离我住的地方近，而且围裙很可爱。
	\switchcolumn*
	\charactername{Chandler:} Can we start over?
	\switchcolumn
	\charactername{钱德勒：}我们能重新开始吗？
	\switchcolumn*
	\charactername{Ursula:} Yeah. Okay great. I’m gonna be over here. \ennotmain{She wanders away.}
	\switchcolumn
	\charactername{厄休拉：}好啊。太好了。我会待在这边。\ennotmain{她走开了。}
	\switchcolumn*
	\charactername{Chandler & Joey:} No, no, no!
	\switchcolumn
	\charactername{钱德勒 & 乔伊：}不，不，不！
	\switchcolumn*
	\openingcredits
	\switchcolumn
	\openingcreditscn
	\switchcolumn*
	\sense{Scene: A wintry February day in New York City, snowplows are clearing the streets. Inside Central Perk, all three girls are paying court to Ross.}
	\switchcolumn
	\sense{场景：纽约市二月的一个冬日，扫雪车正在清理街道。中央公园咖啡馆内，三个女孩正围着罗斯说话。}
	\switchcolumn*
	\charactername{Ross:} I don’t know whether he’s testing me, or just acting out, but my monkey is out of control. But, he keeps erasing the messages on my machine, "supposedly" by accident.
	\switchcolumn
	\charactername{罗斯：}我不知道它是在考验我，还是只是在闹脾气，但我的猴子完全失控了。而且，它总是不停地“意外”删掉我答录机上的留言。
	\switchcolumn*
	\charactername{Rachel:} No, yeah, I’ve done that.
	\switchcolumn
	\charactername{瑞秋：}不，嗯，我也干过那种事。
	\switchcolumn*
	\charactername{Ross:} And then, like three days in a row he got to the newspaper before I did, and peed all over the crossword.
	\switchcolumn
	\charactername{罗斯：}然后，它连续三天比我早拿到报纸，在填字游戏上到处撒尿。
	\switchcolumn*
	\charactername{Rachel:} I’ve never done that.
	\switchcolumn
	\charactername{瑞秋：}这事我可没干过。
	\switchcolumn*
	\ennotmain{Outside in the street, Joey and Chandler arrive, to peer through the window at Phoebe, by bending down to look underneath the shop’s sign—a large steaming cup of coffee.}
	\switchcolumn
	\ennotmain{外面街上，乔伊和钱德勒到了，他们弯下腰，从咖啡馆的大咖啡杯标志下方窥视窗内的菲比。}
	\switchcolumn*
	\charactername{Chandler:} All right, now look at her and tell me she doesn’t look exactly like her sister.
	\switchcolumn
	\charactername{钱德勒：}好了，现在看着她，告诉我她和她姐姐长得不是一模一样。
	\switchcolumn*
	\charactername{Joey:} I’m sayin’ I see a difference.
	\switchcolumn
	\charactername{乔伊：}我说我觉得有区别。
	\switchcolumn*
	\charactername{Chandler:} They’re twins!
	\switchcolumn
	\charactername{钱德勒：}她们是双胞胎！
	\switchcolumn*
	\charactername{Joey:} I don’t care. Phoebe’s Phoebe. Ursula’s... hot!
	\switchcolumn
	\charactername{乔伊：}我不管。菲比就是菲比。厄休拉…很火辣！
	\switchcolumn*
	\ennotmain{Joey and Chandler come indoors.}
	\switchcolumn
	\ennotmain{乔伊和钱德勒走进室内。}
	\switchcolumn*
	\charactername{Chandler:} You know that thing, when you and I talk to each other about things?
	\switchcolumn
	\charactername{钱德勒：}你知道吗，就是我们俩互相讨论事情的时候？
	\switchcolumn*
	\charactername{Joey:} Yeah.
	\switchcolumn
	\charactername{乔伊：}嗯。
	\switchcolumn*
	\charactername{Chandler:} Let’s not do that any more.
	\switchcolumn
	\charactername{钱德勒：}我们以后别再那样了。
	\switchcolumn*
	\ennotmain{They hang up their coats and scarves, then approach their friends on the main sofa.}
	\switchcolumn
	\ennotmain{他们挂好外套和围巾，然后走向沙发上的朋友们。}
	\switchcolumn*
	\charactername{All:} Hey guys! Hey!
	\switchcolumn
	\charactername{所有人：}嘿，伙计们！嘿！
	\switchcolumn*
	\charactername{Joey:} Hey Pheebs, guess who we saw today.
	\switchcolumn
	\charactername{乔伊：}嘿，菲比，猜我们今天看见谁了。
	\switchcolumn*
	\charactername{Phoebe:} Ooh, ooh, fun! Okay... um, Liam Neeson.
	\switchcolumn
	\charactername{菲比：}哦，哦，好玩！好吧…嗯，连姆·尼森。
	\switchcolumn*
	\charactername{Joey:} Nope.
	\switchcolumn
	\charactername{乔伊：}不对。
	\switchcolumn*
	\charactername{Phoebe:} Morly Safer.
	\switchcolumn
	\charactername{菲比：}莫利·赛弗。
	\switchcolumn*
	\charactername{Joey:} Nope.
	\switchcolumn
	\charactername{乔伊：}不对。
	\switchcolumn*
	\charactername{Phoebe:} The woman who cuts my hair!
	\switchcolumn
	\charactername{菲比：}给我剪头发的那位女士！
	\switchcolumn*
	\charactername{Monica:} Okay, look, this could be a really long game.
	\switchcolumn
	\charactername{莫妮卡：}好了，听着，这游戏可能会玩很久。
	\switchcolumn*
	\charactername{Chandler:} Your sister Ursula.
	\switchcolumn
	\charactername{钱德勒：}你姐姐厄休拉。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Her face dropping} Oh, really.
	\switchcolumn
	\charactername{菲比：}\ennotmain{脸色一沉}哦，真的。
	\switchcolumn*
	\charactername{Chandler:} Yeah, yeah, she works over at that place, uh...
	\switchcolumn
	\charactername{钱德勒：}是啊，是啊，她在那个地方工作，呃…
	\switchcolumn*
	\charactername{Phoebe:} Rift’s. Yeah, I know.
	\switchcolumn
	\charactername{菲比：}里夫特餐厅。是啊，我知道。
	\switchcolumn*
	\charactername{Chandler:} Oh, you do? Because she said you guys haven’t talked in like years.
	\switchcolumn
	\charactername{钱德勒：}哦，你知道？因为她说你们好像好几年没说过话了。
	\switchcolumn*
	\charactername{Phoebe:} Hmmm? Yeah. So, um, is she fat?
	\switchcolumn
	\charactername{菲比：}嗯？是啊。那么，嗯，她胖吗？
	\switchcolumn*
	\charactername{Joey:} Not from where I was standin’.
	\switchcolumn
	\charactername{乔伊：}从我站的位置看，不胖。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Turning to Chandler} where were you standing?
	\switchcolumn
	\charactername{菲比：}\ennotmain{转向钱德勒}你当时站在哪儿？
	\switchcolumn*
	\charactername{Rachel:} Um, Pheebs, so, you guys just don’t get along?
	\switchcolumn
	\charactername{瑞秋：}嗯，菲比，所以，你们俩合不来？
	\switchcolumn*
	\charactername{Phoebe:} It’s mostly just dumb sister stuff, you know, I mean, like, everyone always thought of her as the pretty one, you know... Oh, oh, she was the first one to start walking, even though I did it... later that same day. But, to my parents, by then it was like "yeah, right, well what else is new?"
	\switchcolumn
	\charactername{菲比：}主要就是些愚蠢的姐妹矛盾，你知道，我的意思是，比如，大家都一直觉得她是漂亮的那个，你知道…哦，哦，她是先开始走路的那个，尽管我…在同一天稍晚些时候也做到了。但是，对我父母来说，那时候他们就觉得“是啊，没错，还有什么新鲜的？”
	\switchcolumn*
	\charactername{Ross:} Oh, Pheebs, I’m sorry, I’ve got to go. I’ve got Lamaze class.
	\switchcolumn
	\charactername{罗斯：}哦，菲比，抱歉，我得走了。我有拉玛泽分娩课程。
	\switchcolumn*
	\charactername{Chandler:} Oh, and I’ve got Earth Science, but I'll catch you in Gym.
	\switchcolumn
	\charactername{钱德勒：}哦，我还有地球科学课，不过我们健身房见。
	\switchcolumn*
	\charactername{Rachel:} So, is this just gonna be you and Carol?
	\switchcolumn
	\charactername{瑞秋：}那么，就只是你和卡萝尔去吗？
	\switchcolumn*
	\charactername{Ross:} No, Susan’s gonna be there too. We’ve got dads, we’ve got lesbians, the whole parenting team.
	\switchcolumn
	\charactername{罗斯：}不，苏珊也会去。我们有爸爸，有女同性恋，整个育儿团队都齐了。
	\switchcolumn*
	\charactername{Rachel:} Well, isn’t, isn’t that gonna be weird?
	\switchcolumn
	\charactername{瑞秋：}嗯，难道，难道不会很怪吗？
	\switchcolumn*
	\charactername{Ross:} No, no. \ennotmain{Distractedly putting on a jacket to go out} I mean, it mighta been at first, but by now I, I think I’m pretty comfortable with the whole situation.
	\switchcolumn
	\charactername{罗斯：}不，不会。\ennotmain{心不在焉地穿上外套准备出门}我是说，一开始可能有点，但到现在我，我觉得我对整个情况已经相当自在了。
	\switchcolumn*
	\charactername{Monica:} Ross, that’s my jacket.
	\switchcolumn
	\charactername{莫妮卡：}罗斯，那是我的外套。
	\switchcolumn*
	\charactername{Ross:} I know.
	\switchcolumn
	\charactername{罗斯：}我知道。
	\switchcolumn*
	\ennotmain{Rachel grins as Ross removes the girlie jacket, grabs his own, and rushes out.}
	\switchcolumn
	\ennotmain{罗斯脱掉那件女式外套，抓起自己的外套冲了出去，瑞秋咧嘴笑了。}
	\switchcolumn*
	\sense{Scene: The Lamaze class, several couples and one trio sit on the floor, introducing themselves to the teacher, who’s got as far as a woman sitting next to Ross, Carol, and Susan.}
	\switchcolumn
	\sense{场景：拉玛泽课程上，几对夫妇和一个三人组坐在地板上，向老师作自我介绍，老师刚问到坐在罗斯、卡萝尔和苏珊旁边的一位女士。}
	\switchcolumn*
	\charactername{Woman:} Hi, we’re the Rostins. Err, I’m J.C., and he’s Michael, and we’re having a boy, and a girl.
	\switchcolumn
	\charactername{女士：}嗨，我们是罗斯廷一家。呃，我是J.C.，他是迈克尔，我们怀的是龙凤胎。
	\switchcolumn*
	\charactername{Teacher:} Good for you. Alrighty, next?
	\switchcolumn
	\charactername{老师：}真不错。好的，下一位？
	\switchcolumn*
	\charactername{Ross:} Hi, um, I’m err, \ennotmain{has to clear his throat} I’m Ross Geller, and err ah... \ennotmain{pats Carol’s bulge} ..that’s, that’s my boy in there, and uh, \ennotmain{points} this is Carol Willick, and this... is Susan Bunch. Susan is um Carol’s, just, com... \ennotmain{embarrassment finally overwhelms the poor fellow, who becomes incoherent until} ..who’s next?
	\switchcolumn
	\charactername{罗斯：}嗨，嗯，我是呃，\ennotmain{清了清嗓子}我是罗斯·盖勒，然后呃啊…\ennotmain{拍拍卡萝尔隆起的肚子}…那，那里面是我的儿子，然后呃，\ennotmain{指向}这是卡萝尔·威立克，这位…是苏珊·邦奇。苏珊是呃卡萝尔的，就，伙…\ennotmain{尴尬终于击垮了这可怜的家伙，他开始语无伦次，直到说}…下一位是谁？
	\switchcolumn*
	\charactername{Teacher:} I’m sorry, I didn’t get... Susan is?
	\switchcolumn
	\charactername{老师：}抱歉，我没听清…苏珊是？
	\switchcolumn*
	\charactername{Ross:} Susan is Carol’s, Carol’s, Carol’s, friend...
	\switchcolumn
	\charactername{罗斯：}苏珊是卡萝尔的，卡萝尔的，卡萝尔的，朋友…
	\switchcolumn*
	\charactername{Carol:} Life partner.
	\switchcolumn
	\charactername{卡萝尔：}人生伴侣。
	\switchcolumn*
	\charactername{Ross:} Like buddies.
	\switchcolumn
	\charactername{罗斯：}就像哥们儿。
	\switchcolumn*
	\charactername{Susan:} Like lovers.
	\switchcolumn
	\charactername{苏珊：}就像爱人。
	\switchcolumn*
	\charactername{Ross:} You know how close women can get.
	\switchcolumn
	\charactername{罗斯：}你知道女人之间能有多亲密。
	\switchcolumn*
	\ennotmain{The teacher smiles, but her eyebrows go up. Susan and Carol pat each other affectionately.}
	\switchcolumn
	\ennotmain{老师笑了，但眉毛扬了起来。苏珊和卡萝尔亲昵地拍拍对方。}
	\switchcolumn*
	\charactername{Carol:} Susan and I live together.
	\switchcolumn
	\charactername{卡萝尔：}苏珊和我住在一起。
	\switchcolumn*
	\charactername{Ross:} Although I was married to her.
	\switchcolumn
	\charactername{罗斯：}虽然我和她结过婚。
	\switchcolumn*
	\charactername{Susan:} Carol, not me.
	\switchcolumn
	\charactername{苏珊：}是卡萝尔，不是我。
	\switchcolumn*
	\charactername{Ross:} Err, right.
	\switchcolumn
	\charactername{罗斯：}呃，对。
	\switchcolumn*
	\charactername{Carol:} It’s a little complicated.
	\switchcolumn
	\charactername{卡萝尔：}是有点复杂。
	\switchcolumn*
	\charactername{Ross:} A little.
	\switchcolumn
	\charactername{罗斯：}有一点。
	\switchcolumn*
	\charactername{Susan:} But we’re fine.
	\switchcolumn
	\charactername{苏珊：}但我们很好。
	\switchcolumn*
	\charactername{Ross:} Absolutely. \ennotmain{Turns back to the woman next to him.} So, twins... hah! That’s like two births. \ennotmain{He struggles again.} Ouch.
	\switchcolumn
	\charactername{罗斯：}绝对是的。\ennotmain{转回旁边的女士。}所以，双胞胎…哈！那就像两次分娩。\ennotmain{他又挣扎了一下。}哎哟。
	\switchcolumn*
	\sense{Scene : Chandler's Office, Chandler is working.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，钱德勒正在工作。}
	\switchcolumn*
	\ennotmain{Helen’s buzzer is heard on the intercom, so Chandler presses his button, too.}
	\switchcolumn
	\ennotmain{对讲机里传来海伦的蜂鸣声，钱德勒也按下了自己的按钮。}
	\switchcolumn*
	\charactername{Chandler:} And \ennotmain{he imitates the buzzer} to you too, Helen.
	\switchcolumn
	\charactername{钱德勒：}也\ennotmain{他模仿蜂鸣声}祝你，海伦。
	\switchcolumn*
	\charactername{Helen:} \ennotmain{Over the intercom} Nina Bookbinder is here to see you.
	\switchcolumn
	\charactername{海伦：}\ennotmain{通过对讲机}尼娜·布克宾德来见你。
	\switchcolumn*
	\charactername{Chandler:} Oh, okay. Send her in.
	\switchcolumn
	\charactername{钱德勒：}哦，好的。让她进来。
	\switchcolumn*
	\ennotmain{He hurriedly checks his hair in his computer screen, before taking a sporting trophy from a drawer to place ostentatiously on his desk. An attractive young woman opens the door.}
	\switchcolumn
	\ennotmain{他匆忙地在电脑屏幕上检查了一下头发，然后从抽屉里拿出一个运动奖杯，炫耀地放在桌上。一位迷人的年轻女子推门进来。}
	\switchcolumn*
	\charactername{Nina:} Hi.
	\switchcolumn
	\charactername{尼娜：}嗨。
	\switchcolumn*
	\charactername{Chandler:} Hi, Nina. Come on in.
	\switchcolumn
	\charactername{钱德勒：}嗨，尼娜。进来吧。
	\switchcolumn*
	\charactername{Nina:} You wanted to see me?
	\switchcolumn
	\charactername{尼娜：}你想见我？
	\switchcolumn*
	\charactername{Chandler:} Uh, Yes. Yes. I’ve just been going over your data here, and little thing, you’ve been post-dating your Friday numbers.
	\switchcolumn
	\charactername{钱德勒：}呃，是的。是的。我刚仔细看了你的数据，有个小问题，你一直在把周五的数据填迟日期。
	\switchcolumn*
	\charactername{Nina:} Which is bad, because?
	\switchcolumn
	\charactername{尼娜：}这为什么不好呢？
	\switchcolumn*
	\charactername{Chandler:} Well, it throws my WENUS out of whack.
	\switchcolumn
	\charactername{钱德勒：}嗯，这让我的“WENUS”出问题了。
	\switchcolumn*
	\charactername{Nina:} Your... excuse me?
	\switchcolumn
	\charactername{尼娜：}你的…什么？
	\switchcolumn*
	\charactername{Chandler:} WENUS. \ennotmain{Coughs} Weekly Estimated Net...
	\switchcolumn
	\charactername{钱德勒：}WENUS。\ennotmain{咳嗽}每周预估净…
	\switchcolumn*
	\charactername{Nina:} Oh, Net Usage Statistics, right. Gotcha, gotcha. Won’t happen again. I wouldn’t want to do anything to hurt your... "wenus."
	\switchcolumn
	\charactername{尼娜：}哦，净使用量统计，对吧。明白了，明白了。不会再犯了。我可不想做任何伤害你…“WENUS”的事。
	\switchcolumn*
	\ennotmain{Nina beams flirtatiously at Chandler, who catches her drift, but for once he’s lost for something to say &ndash; so she nods her head to tell him that he’s thinking correctly...}
	\switchcolumn
	\ennotmain{尼娜向钱德勒抛来调情的媚眼，钱德勒领会了她的意思，但这次他却一时语塞了——所以她点点头，告诉他他想得没错…}
	\switchcolumn*
	\sense{Scene: Monica and Rachel's, Ross, Chandler, and the girls are dividing some Chinese takeout, while the sitcom Family Matters is playing on the TV.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，罗斯、钱德勒和女孩们正在分中餐外卖，电视上正播放着情景喜剧《家庭事务》。}
	\switchcolumn*
	\charactername{Chandler:} It’s not just that she’s cute, okay. It’s just that... she’s really really cute.
	\switchcolumn
	\charactername{钱德勒：}不只是因为她可爱，好吧。只是…她真的非常非常可爱。
	\switchcolumn*
	\charactername{Ross:} It doesn’t matter. You don’t dip your pen in the company ink.
	\switchcolumn
	\charactername{罗斯：}这没关系。你总不能“兔子吃窝边草”吧。\ennotmain{直译：你不能把钢笔蘸到公司的墨水里。}
	\switchcolumn*
	\ennotmain{Marcel scampers about, interfering with the neatness.}
	\switchcolumn
	\ennotmain{马塞尔四处乱窜，破坏了整洁。}
	\switchcolumn*
	\charactername{Monica:} Ross, your little creature’s got the remote again.
	\switchcolumn
	\charactername{莫妮卡：}罗斯，你的小东西又把遥控器拿走了。
	\switchcolumn*
	\charactername{Ross:} Marcel, Marcel, give Rossie the remote. Marcel. Marcel, you give Rossie the remote right now... Marce... you give Rossie the remote...
	\switchcolumn
	\charactername{罗斯：}马塞尔，马塞尔，把遥控器给罗斯。马塞尔。马塞尔，你现在就把遥控器给罗斯…马塞…你把遥控器给罗斯…
	\switchcolumn*
	\ennotmain{Marcel points the remote at Monica’s television, pressing a particular combination of keys. The logo SAP appears on the screen, and suddenly the dialogue is dubbed into Spanish.}
	\switchcolumn
	\ennotmain{马塞尔用遥控器对着莫妮卡的电视，按了一个特定的组合键。屏幕上出现SAP标志，对话突然变成了西班牙语配音。}
	\switchcolumn*
	\charactername{Monica:} Great.
	\switchcolumn
	\charactername{莫妮卡：}太好了。
	\switchcolumn*
	\charactername{Ross:} Relax, I’ll fix it.
	\switchcolumn
	\charactername{罗斯：}别紧张，我来搞定。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{Looking at the television} Cool... "Urkel" in Spanish is "Urkel."
	\switchcolumn
	\charactername{瑞秋：}\ennotmain{看着电视}酷…西班牙语里的“厄克尔”还是“厄克尔”。
	\switchcolumn*
	\charactername{Ross:} \ennotmain{looking at the remote} How did he do this?
	\switchcolumn
	\charactername{罗斯：}\ennotmain{看着遥控器}它是怎么做到的？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Looking out at the balcony} So tell me something, is leaving the Christmas lights up part of your plan to keep us merry all year long?
	\switchcolumn
	\charactername{钱德勒：}\ennotmain{望向阳台}那么告诉我，留着圣诞彩灯是你让我们全年都保持快乐计划的一部分吗？
	\switchcolumn*
	\ennotmain{Rachel slowly spins around, finally noticing that the lights have outstayed their welcome.}
	\switchcolumn
	\ennotmain{瑞秋慢慢转过身，终于注意到那些彩灯已经不受欢迎地待了很久了。}
	\switchcolumn*
	\charactername{Monica:} Ah no, you see, someone was supposed to take them down around New Year’s... but obviously someone forgot.
	\switchcolumn
	\charactername{莫妮卡：}啊不，你看，本来应该有人在元旦前后把它们取下来的…但显然有人忘了。
	\switchcolumn*
	\charactername{Rachel:} Well, someone was supposed to write "Rach, take down the lights" and put it on the re... frigerate... \ennotmain{finally noticing Monica’s note stuck to the refrigerator} How long has that been there?
	\switchcolumn
	\charactername{瑞秋：}嗯，本来应该有人写上“瑞秋，取下彩灯”然后贴在冰…冰箱上…\ennotmain{终于注意到莫妮卡贴在冰箱上的便条}那东西贴在那儿多久了？
	\switchcolumn*
	\ennotmain{Joey enters, looking extremely pleased with himself.}
	\switchcolumn
	\ennotmain{乔伊进来，看起来对自己非常满意。}
	\switchcolumn*
	\charactername{Chandler:} Hey, where you been?
	\switchcolumn
	\charactername{钱德勒：}嘿，你去哪儿了？
	\switchcolumn*
	\charactername{Joey:} I went back to Riff’s. I think Ursula likes me. All I ordered was coffee, she brought me a tuna melt and four plates of curly fries.
	\switchcolumn
	\charactername{乔伊：}我又去了里夫特餐厅。我觉得厄休拉喜欢我。我只点了咖啡，她却给我端来了金枪鱼三明治和四盘卷曲薯条。
	\switchcolumn*
	\charactername{Chandler:} Score.
	\switchcolumn
	\charactername{钱德勒：}得分。
	\switchcolumn*
	\charactername{Joey:} She is so hot!
	\switchcolumn
	\charactername{乔伊：}她太火辣了！
	\switchcolumn*
	\charactername{Chandler:} Yeah, listen. Okay, before you do anything Joey-like, you might wanna run it by err... \ennotmain{he indicates Phoebe, who is helping Ross understand the remote control.}
	\switchcolumn
	\charactername{钱德勒：}是啊，听着。好吧，在你做任何乔伊风格的事情之前，你或许应该先征求一下呃…\ennotmain{他指向正在帮罗斯弄懂遥控器的菲比。}
	\switchcolumn*
	\charactername{Joey:} Pheebs?
	\switchcolumn
	\charactername{乔伊：}菲比？
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Jumping up} Yeah?
	\switchcolumn
	\charactername{菲比：}\ennotmain{跳起来}嗯？
	\switchcolumn*
	\charactername{Joey:} You think it would be okay if I asked out your sister?
	\switchcolumn
	\charactername{乔伊：}你觉得我约你姐姐出去可以吗？
	\switchcolumn*
	\charactername{Phoebe:} Why? Why would you wanna... do that? Why?
	\switchcolumn
	\charactername{菲比：}为什么？你为什么会想…那么做？为什么？
	\switchcolumn*
	\charactername{Joey:} So that if we went out on a date, she’d be there.
	\switchcolumn
	\charactername{乔伊：}这样如果我们去约会，她就会在场啊。
	\switchcolumn*
	\charactername{Phoebe:} Well, I mean, I’m not my sister’s, you know, whatever, and um... I mean, it’s true, we were one egg, once, but err, you know, we’ve grown apart, so, um... I don’t know, why not? Okay.
	\switchcolumn
	\charactername{菲比：}嗯，我的意思是，我不是我姐姐的，你知道，随便什么监护人，而且嗯…我是说，没错，我们曾经是一颗卵子，但是呃，你知道，我们已经疏远了，所以，嗯…我不知道，有何不可呢？好吧。
	\switchcolumn*
	\charactername{Joey:} Cool, thanks.
	\switchcolumn
	\charactername{乔伊：}酷，谢谢。
	\switchcolumn*
	\ennotmain{He happily gestures at Chandler that there was nothing to worry about, then exits. Rachel and Monica are concerned for poor Phoebe, who slides back down next to Ross.}
	\switchcolumn
	\ennotmain{他高兴地向钱德勒比划表示没什么好担心的，然后离开了。瑞秋和莫妮卡为可怜的菲比感到担心，菲比滑坐回罗斯旁边。}
	\switchcolumn*
	\charactername{Ross:} You okay?
	\switchcolumn
	\charactername{罗斯：}你没事吧？
	\switchcolumn*
	\charactername{Phoebe:} Yeah I’m fine.
	\switchcolumn
	\charactername{菲比：}嗯，我没事。
	\switchcolumn*
	\charactername{Ross:} You wanna watch Laverne y Shirley?
	\switchcolumn
	\charactername{罗斯：}你想看《拉维恩和雪莉》\ennotmain{西班牙语版}吗？
	\switchcolumn*
	\ennotmain{The sitcom begins with its familiar refrain, yet with a Latin lilt. Rachel and Monica do a little dance with their chopsticks, and Phoebe has to grin as Ross joins in the rhythm.}
	\switchcolumn
	\ennotmain{情景喜剧以熟悉的旋律开始，但带着拉丁风格的轻快调子。瑞秋和莫妮卡用筷子跳起了小舞，菲比看到罗斯也加入节奏，不得不咧嘴笑了。}
	\switchcolumn*
	\sense{Scene: Lamaze class. Susan is there. Each couple has a doll, for they have just finished learning how to change a diaper. As Ross rushes in, stepping on the Rostins’ pretend baby, squashing its head flat. It bleats, in protest. He performs emergency surgery, then hands the doll back to J.C.}
	\switchcolumn
	\sense{场景：拉玛泽课程。苏珊在场。每对夫妇都有一个娃娃，因为他们刚学完如何换尿布。罗斯冲进来时，踩到了罗斯廷家的假宝宝，把它脑袋踩扁了。它发出抗议的咩咩声。他进行了紧急手术，然后把娃娃递回给J.C.}
	\switchcolumn*
	\charactername{Ross:} Sorry.
	\switchcolumn
	\charactername{罗斯：}对不起。
	\switchcolumn*
	\charactername{Ross:} Hi. Sorry I’m late. Where’s, where’s Carol?
	\switchcolumn
	\charactername{罗斯：}嗨。抱歉我迟到了。卡萝尔呢，卡萝尔在哪儿？
	\switchcolumn*
	\charactername{Susan:} Stuck at school. Some parent-teacher thing. You can go. I’ll get the information.
	\switchcolumn
	\charactername{苏珊：}在学校耽搁了。家长会什么的。你可以走了。我来听课。
	\switchcolumn*
	\charactername{Ross:} No... No... No. I think I should stay, I think we should both know what’s going on.
	\switchcolumn
	\charactername{罗斯：}不…不…不。我觉得我应该留下，我觉得我们都应该知道情况。
	\switchcolumn*
	\charactername{Susan:} Oh, good. This’ll be fun.
	\switchcolumn
	\charactername{苏珊：}哦，好啊。这会很有趣。
	\switchcolumn*
	\charactername{Teacher:} Alrighty. We’re gonna start with some basic third stage breathing exercises, so Mummies, why don’t you get on your back? And... coaches, you should be supporting Mummy’s head.
	\switchcolumn
	\charactername{老师：}好的。我们开始一些基本的第三产程呼吸练习，所以妈妈们，请你们躺下好吗？还有…教练们，你们应该扶着妈妈的头。
	\switchcolumn*
	\ennotmain{Ross and Susan each gesture for the other to lie down.}
	\switchcolumn
	\ennotmain{罗斯和苏珊各自示意对方躺下。}
	\switchcolumn*
	\charactername{Ross and Susan:} What? What? What?
	\switchcolumn
	\charactername{罗斯和苏珊：}什么？什么？什么？
	\switchcolumn*
	\charactername{Susan:} I am supposed to be the mommy?
	\switchcolumn
	\charactername{苏珊：}我应该当妈妈？
	\switchcolumn*
	\charactername{Ross:} Okay, I’m gonna play my sperm card one more time.
	\switchcolumn
	\charactername{罗斯：}好吧，我要再打一次我的精子牌。
	\switchcolumn*
	\charactername{Susan:} Look, I don’t see why I should have to miss out on the coaching training just because I’m a woman.
	\switchcolumn
	\charactername{苏珊：}听着，我不明白为什么就因为我是女人，我就得错过教练培训。
	\switchcolumn*
	\charactername{Ross:} I see. So what do you propose to do?
	\switchcolumn
	\charactername{罗斯：}我明白了。那你提议怎么做？
	\switchcolumn*
	\charactername{Susan:} I will flip you for it.
	\switchcolumn
	\charactername{苏珊：}我们抛硬币决定。
	\switchcolumn*
	\charactername{Ross:} Flip me for it? No, no, no... heads, heads, heads!
	\switchcolumn
	\charactername{罗斯：}抛硬币？不，不，不…正面，正面，正面！
	\switchcolumn*
	\charactername{Susan:} \ennotmain{Triumphantly} On your back... Mom.
	\switchcolumn
	\charactername{苏珊：}\ennotmain{得意地}躺下吧…妈妈。
	\switchcolumn*
	\ennotmain{Ross gets down like all the other mothers, cradled in Susan’s lap like all the other fathers.}
	\switchcolumn
	\ennotmain{罗斯像其他妈妈一样躺下，像其他爸爸一样靠在苏珊的腿上。}
	\switchcolumn*
	\charactername{Teacher:} Alright, Mommies, take a nice deep cleansing breath.
	\switchcolumn
	\charactername{老师：}好的，妈妈们，做一个舒服的深呼吸。
	\switchcolumn*
	\ennotmain{Forgetting herself, Susan does the "Mommy" action with Ross.}
	\switchcolumn
	\ennotmain{苏珊忘了自己角色，和罗斯一起做了“妈妈”的呼吸动作。}
	\switchcolumn*
	\charactername{Teacher:} Good. Now imagine your vagina is opening like a flower.
	\switchcolumn
	\charactername{老师：}很好。现在想象你的阴道像花朵一样绽放。
	\switchcolumn*
	\ennotmain{Ross comes out of character to glare into the distance.}
	\switchcolumn
	\ennotmain{罗斯脱离角色，怒视远方。}
	\switchcolumn*
	\sense{Scene: Chandler's Office. Chandler is playing with a toy as his boss Mr. Douglas knocks and opens the door.}
	\switchcolumn
	\sense{场景：钱德勒的办公室。钱德勒正在玩一个玩具，他的老板道格拉斯先生敲门并推门进来。}
	\switchcolumn*
	\charactername{Chandler:} Mr. D, how’s it going, sir?
	\switchcolumn
	\charactername{钱德勒：}D先生，最近怎么样，先生？
	\switchcolumn*
	\charactername{Mr. Douglas:} Ohh, it’s been better. The Annual Net Usage Statistics are in.
	\switchcolumn
	\charactername{道格拉斯先生：}哦，本来可以更好。年度净使用量统计出来了。
	\switchcolumn*
	\charactername{Chandler:} And?
	\switchcolumn
	\charactername{钱德勒：}然后呢？
	\switchcolumn*
	\charactername{Mr. Douglas:} It’s pretty ugly. We haven’t seen an ANUS this bad since the seventies.
	\switchcolumn
	\charactername{道格拉斯先生：}相当难看。我们自七十年代以来就没见过这么糟糕的ANUS\ennotmain{年度净使用量统计，与“肛门”同词}。
	\switchcolumn*
	\charactername{Chandler:} So what does this mean?
	\switchcolumn
	\charactername{钱德勒：}那这意味着什么？
	\switchcolumn*
	\charactername{Mr. Douglas:} Well, we’re gonna be layin’ off people in every department.
	\switchcolumn
	\charactername{道格拉斯先生：}嗯，我们每个部门都要裁员。
	\switchcolumn*
	\charactername{Chandler:} Hey, listen, I know I came in late last week, but I slept funny, and my hair was very very &ndash;
	\switchcolumn
	\charactername{钱德勒：}嘿，听着，我知道我上周迟到了，但我睡姿不对，而且我的头发非常非常&ndash;
	\switchcolumn*
	\charactername{Mr. Douglas:} Not you. Relax. Ever have to fire anyone?
	\switchcolumn
	\charactername{道格拉斯先生：}不是你。放松点。你解雇过人吗？
	\switchcolumn*
	\sense{Scene: Chandler's Office, later that day, Nina is in his office.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，当天晚些时候，尼娜在他办公室。}
	\switchcolumn*
	\charactername{Chandler:} Nina? Nina. \ennotmain{He goes around his desk to where she is sitting.} Nina. \ennotmain{In pain} Nina.
	\switchcolumn
	\charactername{钱德勒：}尼娜？尼娜。\ennotmain{他绕到桌子那边她坐着的地方。}尼娜。\ennotmain{痛苦地}尼娜。
	\switchcolumn*
	\ennotmain{She sympathetically reaches out to fondle the inner thigh of his left leg.}
	\switchcolumn
	\ennotmain{她同情地伸出手，抚摸他左腿内侧。}
	\switchcolumn*
	\charactername{Nina:} Are you okay?
	\switchcolumn
	\charactername{尼娜：}你还好吗？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Looking down at her hand} Yes, yes I am. Err, listen, the reason that I called you in here today was, err... please don’t hate me.
	\switchcolumn
	\charactername{钱德勒：}\ennotmain{低头看着她的手}是的，是的，我很好。呃，听着，我今天叫你进来的原因是，呃…请不要恨我。
	\switchcolumn*
	\charactername{Nina:} \ennotmain{Taking her hand away} What?
	\switchcolumn
	\charactername{尼娜：}\ennotmain{把手拿开}什么？
	\switchcolumn*
	\charactername{Chandler:} \ennotmain{Suddenly bright} Would you like to have dinner sometime?
	\switchcolumn
	\charactername{钱德勒：}\ennotmain{突然高兴起来}你想找个时间一起吃晚饭吗？
	\switchcolumn*
	\ennotmain{Nina gasps in surprise and relief.}
	\switchcolumn
	\ennotmain{尼娜惊讶又宽慰地吸了口气。}
	\switchcolumn*
	\sense{Scene: Central Perk, Rachel is at the counter, serving coffee to Phoebe.}
	\switchcolumn
	\sense{场景：中央公园咖啡馆，瑞秋在柜台给菲比倒咖啡。}
	\switchcolumn*
	\charactername{Rachel:} So Pheebs, what do you want for your birthday?
	\switchcolumn
	\charactername{瑞秋：}那么菲比，你生日想要什么？
	\switchcolumn*
	\charactername{Phoebe:} Well, what I really want is for my mom to be alive and enjoy it with me.
	\switchcolumn
	\charactername{菲比：}嗯，我真正想要的是我妈妈还活着，和我一起庆祝。
	\switchcolumn*
	\charactername{Rachel:} Okay... Let me put it this way. Anything from Crabtree and Evelyn?
	\switchcolumn
	\charactername{瑞秋：}好吧…让我换个说法。想要凯柏芮或伊芙琳的什么东西吗？
	\switchcolumn*
	\charactername{Phoebe:} Ooh! Bath salts would be nice.
	\switchcolumn
	\charactername{菲比：}哦！浴盐就不错。
	\switchcolumn*
	\charactername{Rachel:} Ooh, okay... good.
	\switchcolumn
	\charactername{瑞秋：}哦，好的…很好。
	\switchcolumn*
	\ennotmain{Jamie Buchman and Fran Devanow enter the coffee house. They look about them as Jamie removes her coat and scarf.}
	\switchcolumn
	\ennotmain{杰米·布克曼和弗兰·德瓦诺走进咖啡馆。杰米脱下外套和围巾时，她们环顾四周。}
	\switchcolumn*
	\charactername{Jamie:} What is this place?
	\switchcolumn
	\charactername{杰米：}这是什么地方？
	\switchcolumn*
	\charactername{Fran:} Look, you’re cold, I have to pee, and... \ennotmain{indicating the sign} ..there’s a cup of coffee on the window. How bad could it be?
	\switchcolumn
	\charactername{弗兰：}听着，你很冷，我想上厕所，而且…\ennotmain{指向招牌}…窗户上有个咖啡杯标志。能糟到哪里去？
	\switchcolumn*
	\ennotmain{Jamie notices Phoebe sitting at the counter.}
	\switchcolumn
	\ennotmain{杰米注意到菲比坐在柜台边。}
	\switchcolumn*
	\charactername{Jamie:} I think we have an answer.
	\switchcolumn
	\charactername{杰米：}我想我们有答案了。
	\switchcolumn*
	\charactername{Fran:} What’s she doing here?
	\switchcolumn
	\charactername{弗兰：}她在这儿干嘛？
	\switchcolumn*
	\charactername{Jamie:} This could be God’s way of telling us to eat at home.
	\switchcolumn
	\charactername{杰米：}这可能是上帝在告诉我们应该在家吃饭。
	\switchcolumn*
	\charactername{Fran:} Think she got fired at Riff’s?
	\switchcolumn
	\charactername{弗兰：}你觉得她被里夫特餐厅开除了？
	\switchcolumn*
	\charactername{Jamie:} No, no, no. We were there last night. She kept... \ennotmain{shuddering at the memory} ..bringing swordfish. \ennotmain{Indicating the ladies’ bathroom} are you gonna go to the, um?
	\switchcolumn
	\charactername{杰米：}不，不，不。我们昨晚在那里。她一直…\ennotmain{回忆起来打了个寒颤}…上箭鱼。\ennotmain{指着女厕所}你要去，嗯？
	\switchcolumn*
	\charactername{Fran:} I’m gonna wait till after we order. It’s her, right.
	\switchcolumn
	\charactername{弗兰：}我要等到点完单再去。是她，对吧。
	\switchcolumn*
	\charactername{Jamie:} It looks like her.
	\switchcolumn
	\charactername{杰米：}看起来像她。
	\switchcolumn*
	\ennotmain{Phoebe walks by, ignoring the two strangers.}
	\switchcolumn
	\ennotmain{菲比走过，无视了这两个陌生人。}
	\switchcolumn*
	\charactername{Jamie:} Um, excuse me.
	\switchcolumn
	\charactername{杰米：}嗯，打扰一下。
	\switchcolumn*
	\charactername{Phoebe:} Yeah?
	\switchcolumn
	\charactername{菲比：}嗯？
	\switchcolumn*
	\charactername{Jamie:} Hi, it’s us.
	\switchcolumn
	\charactername{杰米：}嗨，是我们。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Smiling blankly} Right, and it’s me.
	\switchcolumn
	\charactername{菲比：}\ennotmain{茫然地微笑}对啊，是我。
	\switchcolumn*
	\charactername{Jamie:} So, so you’re here too?
	\switchcolumn
	\charactername{杰米：}所以，你也在这儿？
	\switchcolumn*
	\charactername{Phoebe:} Much as you are.
	\switchcolumn
	\charactername{菲比：}和你们一样。
	\switchcolumn*
	\charactername{Jamie:} \ennotmain{Without moving her lips} Your turn.
	\switchcolumn
	\charactername{杰米：}\ennotmain{嘴唇不动地}该你了。
	\switchcolumn*
	\charactername{Fran:} Err... we know what we want.
	\switchcolumn
	\charactername{弗兰：}呃…我们知道我们想要什么。
	\switchcolumn*
	\charactername{Phoebe:} \ennotmain{Philosophically} Oh, that’s good.
	\switchcolumn
	\charactername{菲比：}\ennotmain{哲学地}哦，那很好。
	\switchcolumn*
	\charactername{Jamie:} All we want is two Caffe Lattes.
	\switchcolumn
	\charactername{杰米：}我们只要两杯拿铁咖啡。
	\switchcolumn*
	\charactername{Fran:} And some biscotti cookies.
	\switchcolumn
	\charactername{弗兰：}和一些意式脆饼。
	\switchcolumn*
	\charactername{Phoebe:} Good choice.
	\switchcolumn
	\charactername{菲比：}不错的选择。
	\switchcolumn*
	\ennotmain{Phoebe turns away so that the two weird women won’t see the face she pulls, and sits down.}
	\switchcolumn
	\ennotmain{菲比转过身去，不让那两个怪女人看到她做的鬼脸，然后坐下了。}
	\switchcolumn*
	\charactername{Jamie:} Definitely her.
	\switchcolumn
	\charactername{杰米：}绝对是她。
	\switchcolumn*
	\charactername{Fran:} Yeah.
	\switchcolumn
	\charactername{弗兰：}是啊。
	\switchcolumn*
	\commercialbreak
	\switchcolumn
	\commercialbreakcn
	\switchcolumn*
	\sense{Scene: Monica and Rachel’s, Phoebe is watching a Spanish version of The Waltons. At a nearby table sit Monica knitting, Rachel winding a ball of wool, and Chandler supplying them both from a skein which is spread between his hands.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，菲比在看西班牙语版的《沃尔顿一家》。旁边的桌子旁，莫妮卡在织毛衣，瑞秋在绕毛线球，钱德勒双手撑着一绞毛线同时供应她们两个。}
	\switchcolumn*
	\ennotmain{Phoebe uses the remote to stop the Spanish by turning off the television.}
	\switchcolumn
	\ennotmain{菲比用遥控器关掉电视，停止了西班牙语。}
	\switchcolumn*
	\charactername{Monica:} I can’t believe you. You still haven’t told that girl she doesn’t have a job yet?
	\switchcolumn
	\charactername{莫妮卡：}我真不敢相信你。你还没告诉那女孩她已经被开除了？
	\switchcolumn*
	\charactername{Chandler:} Well, you still haven’t taken down the Christmas lights.
	\switchcolumn
	\charactername{钱德勒：}嗯，你还没把圣诞彩灯取下来呢。
	\switchcolumn*
	\charactername{Monica:} Congratulations, I think you’ve found the world’s thinnest argument.
	\switchcolumn
	\charactername{莫妮卡：}恭喜，我想你找到了世界上最站不住脚的论点。
	\switchcolumn*
	\charactername{Chandler:} I’m just trying to find the right moment, you know?
	\switchcolumn
	\charactername{钱德勒：}我只是想找个合适的时机，你知道吧？
	\switchcolumn*
	\charactername{Rachel:} Oh, well, that shouldn’t be so hard, now that you’re dating. \ennotmain{Imitating men at their worst} "Sweetheart, you’re fired, but how ’bout a quickie before I go to work?"
	\switchcolumn
	\charactername{瑞秋：}哦，嗯，现在既然你们在约会，那应该不难。\ennotmain{模仿最差劲的男人}“亲爱的，你被开除了，不过在我去上班前来个快餐怎么样？”
	\switchcolumn*
	\ennotmain{Joey lets himself in, carrying a large paper shopping bag.}
	\switchcolumn
	\ennotmain{乔伊自己开门进来，拿着一个大纸购物袋。}
	\switchcolumn*
	\charactername{Joey:} Hey.
	\switchcolumn
	\charactername{乔伊：}嘿。
	\switchcolumn*
	\charactername{Rachel and Chandler:} Hey.
	\switchcolumn
	\charactername{瑞秋和钱德勒：}嘿。
	\switchcolumn*
	\ennotmain{There is a loud knocking at the door through which Joey has just entered.}
	\switchcolumn
	\ennotmain{乔伊刚进来的那扇门传来了响亮的敲门声。}
	\switchcolumn*
	\charactername{Chandler:} You know, once you’re inside, you don’t have to knock any more.
	\switchcolumn
	\charactername{钱德勒：}你知道吗，一旦你进来了，就不用再敲门了。
	\switchcolumn*
	\charactername{Monica:} I’ll get it.
	\switchcolumn
	\charactername{莫妮卡：}我去开。
	\switchcolumn*
	\ennotmain{She rises, dragging Chandler along by the wool. Rachel has to leap over a chair to follow them. Monica opens the door to find Mr. Heckles standing there.}
	\switchcolumn
	\ennotmain{她站起来，毛线拖着钱德勒一起走。瑞秋必须跳过一把椅子跟上他们。莫妮卡打开门，发现赫克斯先生站在那里。}
	\switchcolumn*
	\charactername{Monica:} Oh. Hi, Mr.Heckles.
	\switchcolumn
	\charactername{莫妮卡：}哦。嗨，赫克斯先生。
	\switchcolumn*
	\charactername{Mr.Heckles:} You’re doing it again.
	\switchcolumn
	\charactername{赫克斯先生：}你们又来了。
	\switchcolumn*
	\charactername{Monica:} We’re not doing anything. We’re just sitting around talking, quietly.
	\switchcolumn
	\charactername{莫妮卡：}我们没干什么。我们只是安静地坐着聊天。
	\switchcolumn*
	\charactername{Mr.Heckles:} I can hear you through the ceiling. My cats can’t sleep.
	\switchcolumn
	\charactername{赫克斯先生：}我能透过天花板听到你们。我的猫睡不着。
	\switchcolumn*
	\charactername{Rachel:} You don’t even have cats.
	\switchcolumn
	\charactername{瑞秋：}你甚至没养猫。
	\switchcolumn*
	\charactername{Mr.Heckles:} I could have cats.
	\switchcolumn
	\charactername{赫克斯先生：}我可能会有猫。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{Closing the door} Goodbye Mr.Heckles.
	\switchcolumn
	\charactername{莫妮卡：}\ennotmain{关上门}再见，赫克斯先生。
	\switchcolumn*
	\charactername{Rachel:} We’ll try to keep it down.
	\switchcolumn
	\charactername{瑞秋：}我们会尽量小声点的。
	\switchcolumn*
	\ennotmain{The wool-bound trio returns to the table. Rachel has to rush ahead to avoid becoming tangled. Joey brings the shopping bag over to Phoebe, and takes out a nice cardigan.}
	\switchcolumn
	\ennotmain{被毛线绑住的三个人回到桌边。瑞秋不得不冲在前面以免被缠住。乔伊把购物袋拿到菲比面前，拿出一件不错的开衫。}
	\switchcolumn*
	\charactername{Joey:} Phoebe, could you do me a favour? Could you try this on? I just wanna make sure it fits.
	\switchcolumn
	\charactername{乔伊：}菲比，你能帮我个忙吗？你能试试这件吗？我只是想确认合不合身。
	\switchcolumn*
	\charactername{Phoebe:} Ooh, my first birthday present... \ennotmain{delightedly examining the cardigan in her lap} ..oh, this is really...
	\switchcolumn
	\charactername{菲比：}哦，我的第一份生日礼物…\ennotmain{高兴地检查腿上的开衫}…哦，这真是…
	\switchcolumn*
	\charactername{Joey:} Oh, no no no. It’s for Ursula. I just figured, you know, size-wise.
	\switchcolumn
	\charactername{乔伊：}哦，不不不。这是给厄休拉的。我只是想，你知道，尺寸方面。
	\switchcolumn*
	\charactername{Phoebe:} Ohhh... Sure, yeah... \ennotmain{disgustedly dropping the cardigan back into the bag} ..okay, it fits.
	\switchcolumn
	\charactername{菲比：}哦…当然，是啊…\ennotmain{厌恶地把开衫扔回袋子里}…好了，合身。
	\switchcolumn*
	\ennotmain{The others have been taking all this in.}
	\switchcolumn
	\ennotmain{其他人一直在观察这一切。}
	\switchcolumn*
	\charactername{Rachel:} Are you seein’ her again tonight?
	\switchcolumn
	\charactername{瑞秋：}你今晚又和她见面吗？
	\switchcolumn*
	\charactername{Joey:} Yep. Ice Capades.
	\switchcolumn
	\charactername{乔伊：}是的。冰上狂欢表演。
	\switchcolumn*
	\charactername{Chandler:} Wow, this is serious. I’ve never known you to pay money for any kind of capade.
	\switchcolumn
	\charactername{钱德勒：}哇，这可是认真的。我从不知道你会为任何种类的“狂欢”表演花钱。
	\switchcolumn*
	\charactername{Joey:} I don’t know. I like her, you know. She’s different. There’s uh, somethin’ about her.
	\switchcolumn
	\charactername{乔伊：}我不知道。我喜欢她，你知道。她不一样。她身上有种，呃，特别的东西。
	\switchcolumn*
	\charactername{Phoebe:} That you like, \ennotmain{snappily confronting Joey over the heads of the knitting circle} we get it. You like her. Great!
	\switchcolumn
	\charactername{菲比：}你喜欢，是吗，\ennotmain{隔着编织圈里的人，厉声对乔伊说}我们懂了。你喜欢她。太好了！
	\switchcolumn*
	\ennotmain{The circle freezes in apprehension.}
	\switchcolumn
	\ennotmain{编织圈里的人紧张得僵住了。}
	\switchcolumn*
	\charactername{Joey:} Hey, Phoebe, I asked you, and you said it was okay.
	\switchcolumn
	\charactername{乔伊：}嘿，菲比，我问过你，你说可以的。
	\switchcolumn*
	\charactername{Phoebe:} Alright, well, maybe now it’s not okay.
	\switchcolumn
	\charactername{菲比：}好吧，嗯，也许现在不行了。
	\switchcolumn*
	\charactername{Joey:} Okay... Well maybe now I’m not okay with it not being okay.
	\switchcolumn
	\charactername{乔伊：}好吧…嗯，也许现在我对“不行了”这件事感到不行了。
	\switchcolumn*
	\charactername{Phoebe:} Okay.
	\switchcolumn
	\charactername{菲比：}好吧。
	\switchcolumn*
	\ennotmain{An embarrassed silence... finally broken by}
	\switchcolumn
	\ennotmain{一阵尴尬的沉默…最后被打破}
	\switchcolumn*
	\charactername{Chandler:} Knit, good woman, knit, knit!
	\switchcolumn
	\charactername{钱德勒：}织啊，好女人，织，快织！
	\switchcolumn*
	\ennotmain{Monica frantically bursts into action as Rachel resumes winding, tangling Chandler’s wool.}
	\switchcolumn
	\ennotmain{莫妮卡慌乱地开始织起来，瑞秋继续绕线，把钱德勒的毛线弄乱了。}
	\switchcolumn*
	\sense{Scene: Chandler's Office, Chandler & Nina are locked in a passionate embrace. Someone knocks, so they hurriedly separate to stare out of the window. Chandler’s boss opens the door.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，钱德勒和尼娜正热烈拥抱。有人敲门，他们匆忙分开望向窗外。钱德勒的老板推门进来。}
	\switchcolumn*
	\charactername{Chandler:} And that’s the Chrysler Building right there.
	\switchcolumn
	\charactername{钱德勒：}那边就是克莱斯勒大厦。
	\switchcolumn*
	\charactername{Mr. Douglas:} Nina.
	\switchcolumn
	\charactername{道格拉斯先生：}尼娜。
	\switchcolumn*
	\charactername{Nina:} Mr.Douglas... \ennotmain{flirting defensively} ..cool tie.
	\switchcolumn
	\charactername{尼娜：}道格拉斯先生…\ennotmain{防御性地调情}…领带很酷。
	\switchcolumn*
	\ennotmain{She escapes, fortunately so distracting Mr. Douglas, that he misses Chandler’s expression of alarm & guilt.}
	\switchcolumn
	\ennotmain{她逃走了，幸好这让道格拉斯先生分了心，没注意到钱德勒惊慌内疚的表情。}
	\switchcolumn*
	\charactername{Mr. Douglas:} \ennotmain{Shutting the door, then pointing vaguely at Nina’s shapely departure} She’s still here.
	\switchcolumn
	\charactername{道格拉斯先生：}\ennotmain{关上门，然后含糊地指向尼娜窈窕离开的方向}她还在这儿。
	\switchcolumn*
	\charactername{Chandler:} Yes, yes she is. Didn’t I memo you on this? See, after I let her go, err, I got a call from her psychiatrist, Dr. Flanen-nen, Dr. Flanen, Dr. Flan.
	\switchcolumn
	\charactername{钱德勒：}是，是，她还在。我没给你发备忘录吗？你看，我解雇她之后，呃，我接到了她的心理医生弗拉嫩-嫩医生，弗拉嫩医生，弗兰医生的电话。
	\switchcolumn*
	\ennotmain{Thinking quickly, Chandler desperately tries to remember anything to do with schizophrenia....}
	\switchcolumn
	\ennotmain{钱德勒快速思考，拼命回想任何与精神分裂症有关的东西…}
	\switchcolumn*
	\charactername{Chandler:} And err, he informed me that uh, she took the news rather badly, in fact, he uh, mentioned the word frenzy.
	\switchcolumn
	\charactername{钱德勒：}然后呃，他告诉我，呃，她对那个消息反应相当糟糕，事实上，他呃，提到了“狂躁”这个词。
	\switchcolumn*
	\charactername{Mr. Douglas:} You’re kidding? She seems so...
	\switchcolumn
	\charactername{道格拉斯先生：}你在开玩笑？她看起来那么…
	\switchcolumn*
	\charactername{Chandler:} Oh, no, no. Nina... \ennotmain{miming fairies twinkling around his head} ..she is whooo wewee-woo whoo whoo! In fact, if you asked her right now, she would have no recollection of being fired at all, none at all.
	\switchcolumn
	\charactername{钱德勒：}哦，不，不。尼娜…\ennotmain{模仿小精灵在他脑袋周围闪烁}…她就是这样呼喂呜呼呼！事实上，如果你现在问她，她完全不记得被解雇的事了，完全不记得。
	\switchcolumn*
	\charactername{Mr. Douglas:} That’s unbelievable.
	\switchcolumn
	\charactername{道格拉斯先生：}真不可思议。
	\switchcolumn*
	\charactername{Chandler:} And yet, believable. So I decided not to fire her again until I can be assured that she will be no threat to herself, or others.
	\switchcolumn
	\charactername{钱德勒：}然而，可以相信。所以我决定暂时不再解雇她，直到我能确保她不会对自己或他人构成威胁。
	\switchcolumn*
	\charactername{Mr. Douglas:} I see. I guess you never really know what’s goin’ on inside a person’s head.
	\switchcolumn
	\charactername{道格拉斯先生：}我明白了。我想你永远无法真正知道一个人脑子里在想什么。
	\switchcolumn*
	\charactername{Chandler:} Well, I guess that’s why they call it psychology, sir.
	\switchcolumn
	\charactername{钱德勒：}嗯，我想这就是为什么他们称之为心理学，先生。
	\switchcolumn*
	\ennotmain{Mr. Douglas screws up his eyes, trying to credit what Bing has just said, but turning to follow Nina down the corridor, he realises Bing must be telling the truth, since he would not have any personal interest in the girl, would he?}
	\switchcolumn
	\ennotmain{道格拉斯先生眯起眼睛，试图相信宾刚才说的话，但转身看着尼娜沿着走廊走去，他意识到宾说的肯定是真话，因为他不会对这女孩有什么私人兴趣，对吧？}
	\switchcolumn*
	\sense{Scene: Lamaze class, Ross is again on the floor, cradled in Susan’s lap, but now Carol is cradled in his lap, and she has a pretend baby, on her lap. The teacher is showing her class a video, which is about to end.}
	\switchcolumn
	\sense{场景：拉玛泽课程，罗斯再次躺在地板上，靠在苏珊腿上，但现在卡萝尔又靠在他腿上，而她腿上有个假宝宝。老师正在给班级放视频，视频即将结束。}
	\switchcolumn*
	\charactername{Soothing male voice:} ..a sound Mom and Dad never forget. For this after all, is the miracle of birth.
	\switchcolumn
	\charactername{舒缓的男声：}…一个爸爸妈妈永远不会忘记的声音。因为这终究是生命的奇迹。
	\switchcolumn*
	\charactername{Teacher:} Lights please? And that’s having a baby. Next week is our final class.
	\switchcolumn
	\charactername{老师：}请开灯？这就是生宝宝。下周是我们的最后一节课。
	\switchcolumn*
	\ennotmain{People start getting up. Ross grabs Carol’s doll to hold it upside down like a football, slapping it with his other hand.}
	\switchcolumn
	\ennotmain{人们开始站起来。罗斯抓起卡萝尔的娃娃，像拿橄榄球一样倒提着，用另一只手拍打它。}
	\switchcolumn*
	\charactername{Ross:} Susan, go deep.
	\switchcolumn
	\charactername{罗斯：}苏珊，跑远点。
	\switchcolumn*
	\ennotmain{Susan just glares back, as Ross’s inappropriate joke falls flat. Meanwhile, a bubble is about to burst...}
	\switchcolumn
	\ennotmain{苏珊只是瞪了回去，罗斯不合适的玩笑失败了。与此同时，一个泡沫即将破裂…}
	\switchcolumn*
	\charactername{Carol:} This is impossible. It’s just impossible.
	\switchcolumn
	\charactername{卡萝尔：}这不可能。根本不可能。
	\switchcolumn*
	\charactername{Susan:} What is, honey?
	\switchcolumn
	\charactername{苏珊：}什么不可能，亲爱的？
	\switchcolumn*
	\charactername{Carol:} What that woman... did. I am not doin’ that. It’s just gonna have to stay in, that’s all, everything will be the same, it’ll just stay in.
	\switchcolumn
	\charactername{卡萝尔：}那个女人…做的事。我可做不到那样。它只能待在里面，就这样，一切照旧，它就待在里面。
	\switchcolumn*
	\charactername{Ross:} Carol, honey, shhh, shhh, everything’s gonna be alright.
	\switchcolumn
	\charactername{罗斯：}卡萝尔，亲爱的，嘘，嘘，一切都会好起来的。
	\switchcolumn*
	\charactername{Carol:} \ennotmain{Turning on Ross} OH, WHAT DO YOU KNOW? NO-ONE’S GOING UP TO YOU AND SAYING, "HI, IS THAT YOUR NOSTRIL? MIND IF WE PUSH THIS POT ROAST THROUGH IT?"
	\switchcolumn
	\charactername{卡萝尔：}\ennotmain{转向罗斯}哦，你知道什么？没人会走到你面前说，“嗨，那是你的鼻孔吗？介意我们把这块炖肉从里面推过去吗？”
	\switchcolumn*
	\charactername{Susan:} Carol, Carol, sweetie. Cleansing breath.
	\switchcolumn
	\charactername{苏珊：}卡萝尔，卡萝尔，甜心。深呼吸。
	\switchcolumn*
	\ennotmain{Both women gulp in air. Ross looks at his "football," then manipulates the head & limbs back into place, until it resembles what it represents.}
	\switchcolumn
	\ennotmain{两个女人都深吸一口气。罗斯看着他的“橄榄球”，然后把它的头和四肢摆回原位，直到它看起来像个娃娃。}
	\switchcolumn*
	\charactername{Susan:} I know it’s frightening, but, big picture. The birth part is just one day, and when it’s over, we’re all gonna be parents for the rest of our lives.
	\switchcolumn
	\charactername{苏珊：}我知道这很可怕，但是，从大局看。分娩只是一天的事，当它结束时，我们下半辈子就都是父母了。
	\switchcolumn*
	\ennotmain{Ross is staring blankly into space.}
	\switchcolumn
	\ennotmain{罗斯茫然地凝视着空中。}
	\switchcolumn*
	\charactername{Susan:} I mean, that’s what this is all about, right? Ross? Ross?
	\switchcolumn
	\charactername{苏珊：}我是说，这就是这一切的意义，对吧？罗斯？罗斯？
	\switchcolumn*
	\sense{Scene 13: Central Perk, the gang is gathered around Monica comforting her brother, who in a slight state of shock is cuddling a cushion for security.}
	\switchcolumn
	\sense{场景 13: 中央公园咖啡馆，大家围在莫妮卡身边安慰她哥哥，罗斯处于轻微震惊状态，抱着一个靠垫寻求安全感。}
	\switchcolumn*
	\charactername{Ross:} I’m gonna be a father.
	\switchcolumn
	\charactername{罗斯：}我要当爸爸了。
	\switchcolumn*
	\charactername{Rachel:} This is just occurring to you?
	\switchcolumn
	\charactername{瑞秋：}你刚意识到吗？
	\switchcolumn*
	\charactername{Ross:} I always knew I was havin’ a baby, I just never realised the baby was having me.
	\switchcolumn
	\charactername{罗斯：}我一直都知道我会有个孩子，我只是从没意识到那个孩子也“拥有”了我。
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{She comforts him too} Oh, you’re gonna be great!
	\switchcolumn
	\charactername{瑞秋：}\ennotmain{她也安慰他}哦，你会是个好爸爸的！
	\switchcolumn*
	\charactername{Ross:} Aw, how can you say that? I can’t even get Marcel to stop eating the bath mat. How am I gonna raise a kid?
	\switchcolumn
	\charactername{罗斯：}啊，你怎么能这么说？我连让马塞尔不咬浴垫都做不到。我怎么抚养一个孩子？
	\switchcolumn*
	\charactername{Chandler:} You know, Ross, some scientists are now saying that, that monkeys and babies are actually different.
	\switchcolumn
	\charactername{钱德勒：}你知道吗，罗斯，现在有些科学家说，猴子和婴儿其实不一样。
	\switchcolumn*
	\ennotmain{Joey tires of this, so he gets up to leave.}
	\switchcolumn
	\ennotmain{乔伊对此感到厌烦，所以起身离开。}
	\switchcolumn*
	\charactername{Phoebe:} Where’re you going?
	\switchcolumn
	\charactername{菲比：}你要去哪儿？
	\switchcolumn*
	\charactername{Joey:} Out.
	\switchcolumn
	\charactername{乔伊：}出去。
	\switchcolumn*
	\charactername{Phoebe:} With?
	\switchcolumn
	\charactername{菲比：}和谁？
	\switchcolumn*
	\charactername{Joey:} \ennotmain{Spreading his arms wide} Yes.
	\switchcolumn
	\charactername{乔伊：}\ennotmain{张开双臂}是的。
	\switchcolumn*
	\charactername{Phoebe:} Alright, could I just ask you one question?
	\switchcolumn
	\charactername{菲比：}好吧，我能问你一个问题吗？
	\switchcolumn*
	\ennotmain{Joey nods his head.}
	\switchcolumn
	\ennotmain{乔伊点点头。}
	\switchcolumn*
	\charactername{Phoebe:} Have you two, you know... like... you know... you know... yet?
	\switchcolumn
	\charactername{菲比：}你们两个，有没有，你知道…像…你知道…你知道…那个过？
	\switchcolumn*
	\charactername{Joey:} Well, not that it’s any of your business, but, no, we haven’t, okay?
	\switchcolumn
	\charactername{乔伊：}嗯，这不关你的事，不过，没有，我们还没有，行了吧？
	\switchcolumn*
	\ennotmain{Joey walks toward the door, then hesitates and turns back.}
	\switchcolumn
	\ennotmain{乔伊朝门口走去，然后犹豫了一下，转过身来。}
	\switchcolumn*
	\charactername{Joey:} You meant sex, right?
	\switchcolumn
	\charactername{乔伊：}你是指上床，对吧？
	\switchcolumn*
	\ennotmain{Phoebe buttons her lip, while the rest of the gang pretend they’re not there.}
	\switchcolumn
	\ennotmain{菲比闭口不言，而其他人都假装他们不在场。}
	\switchcolumn*
	\sense{Scene: Chandler's Office, Chandler is working as Nina knocks, then opens the door.}
	\switchcolumn
	\sense{场景：钱德勒的办公室，钱德勒正在工作，尼娜敲门然后推开门。}
	\switchcolumn*
	\charactername{Nina:} Do you have a sec?
	\switchcolumn
	\charactername{尼娜：}你有空吗？
	\switchcolumn*
	\charactername{Chandler:} Ah, sure, Nina. What’s up?
	\switchcolumn
	\charactername{钱德勒：}啊，当然，尼娜。什么事？
	\switchcolumn*
	\charactername{Nina:} I don’t know. For the past couple days, people have been avoiding me and giving me these really strange looks.
	\switchcolumn
	\charactername{尼娜：}我不知道。过去几天，人们一直在躲着我，还用很奇怪的眼神看我。
	\switchcolumn*
	\charactername{Chandler:} Oh, well, ah... maybe that’s because they’re ah... jealous, of us.
	\switchcolumn
	\charactername{钱德勒：}哦，嗯，啊…也许那是因为他们，啊…嫉妒我们。
	\switchcolumn*
	\charactername{Nina:} Maybe. But that doesn’t explain why they keep taking my scissors.
	\switchcolumn
	\charactername{尼娜：}也许吧。但那无法解释他们为什么总拿走我的剪刀。
	\switchcolumn*
	\charactername{Chandler:} Ah, well, maybe that’s, ah, because you’re getting a big raise.
	\switchcolumn
	\charactername{钱德勒：}啊，嗯，也许那是因为，啊，你要加一大笔薪水了。
	\switchcolumn*
	\charactername{Nina:} I am?
	\switchcolumn
	\charactername{尼娜：}我要加薪？
	\switchcolumn*
	\charactername{Chandler:} Sure, why not?
	\switchcolumn
	\charactername{钱德勒：}当然，为什么不呢？
	\switchcolumn*
	\charactername{Nina:} Oh my god! \ennotmain{Rushing over to give him a big hug} You’re amazing!
	\switchcolumn
	\charactername{尼娜：}哦，天啊！\ennotmain{冲过去给他一个大拥抱}你太棒了！
	\switchcolumn*
	\charactername{Chandler:} Oh, you don’t know. \ennotmain{Presses a button.} Helen, could you make sure we put through the paperwork on Miss Bookbinder’s raise?
	\switchcolumn
	\charactername{钱德勒：}哦，你有所不知。\ennotmain{按下按钮。}海伦，你能确保布克宾德小姐加薪的文件通过吗？
	\switchcolumn*
	\charactername{Helen:} \ennotmain{Over the intercom} So you still want me to send her psychological profile to Personnel?
	\switchcolumn
	\charactername{海伦：}\ennotmain{通过对讲机}所以你还是要我把她的心理档案送到人事部？
	\switchcolumn*
	\charactername{Nina:} What?
	\switchcolumn
	\charactername{尼娜：}什么？
	\switchcolumn*
	\charactername{Chandler:} Helen drinks. \ennotmain{Insincerely} Will you marry me?
	\switchcolumn
	\charactername{钱德勒：}海伦喝多了。\ennotmain{不真诚地}你愿意嫁给我吗？
	\switchcolumn*
	\ennotmain{Nina puts her hands on her hips, then gives Chandler a quizzical look.}
	\switchcolumn
	\ennotmain{尼娜双手叉腰，然后给了钱德勒一个疑惑的表情。}
	\switchcolumn*
	\sense{Scene: Monica and Rachel’s, Ross, Rachel, Chandler, and Phoebe are sharing a bowl of popcorn, while Monica carefully reads the instruction manual for her television set.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的公寓，罗斯、瑞秋、钱德勒和菲比正在分吃一碗爆米花，而莫妮卡仔细阅读着电视机的说明书。}
	\switchcolumn*
	\charactername{Chandler:} Well, I ended up telling her everything.
	\switchcolumn
	\charactername{钱德勒：}嗯，我最后把一切都告诉她了。
	\switchcolumn*
	\charactername{Rachel:} Oh, how’d she take it?
	\switchcolumn
	\charactername{瑞秋：}哦，她反应如何？
	\switchcolumn*
	\charactername{Chandler:} Pretty well. Except for the stapler thing. \ennotmain{He holds up a bandaged hand.} Little tip: if you’re ever in a similar situation, never ever leave your hand... \ennotmain{he mimes Nina taking her revenge} ..on the desk.
	\switchcolumn
	\charactername{钱德勒：}相当好。除了订书机那件事。\ennotmain{他举起一只包扎好的手。}小建议：如果你遇到类似情况，永远永远别把手…\ennotmain{他模仿尼娜报复的样子}…放在桌上。
	\switchcolumn*
	\charactername{Monica:} Okay, I think I get how to do this.
	\switchcolumn
	\charactername{莫妮卡：}好了，我想我知道怎么弄了。
	\switchcolumn*
	\ennotmain{Monica points the remote at her TV, and punches out a key combination from the book, but the dreaded SAP logo remains and Spanish still comes forth.}
	\switchcolumn
	\ennotmain{莫妮卡用遥控器对着电视，按说明书按下一个组合键，但可怕的SAP标志还在，西班牙语也还在播放。}
	\switchcolumn*
	\charactername{Phoebe:} Alright, so, can we turn this off? Can we just make it... make them go away? Because I can’t, I can’t watch.
	\switchcolumn
	\charactername{菲比：}好了，那么，我们能关掉这个吗？我们能不能就让它…让它们消失？因为我不能，我受不了了。
	\switchcolumn*
	\charactername{Monica:} \ennotmain{Remotely turning off the television} okay, Pheebs, they’re gone.
	\switchcolumn
	\charactername{莫妮卡：}\ennotmain{用遥控器关掉电视}好了，菲比，它们消失了。
	\switchcolumn*
	\charactername{Phoebe:} Okay.
	\switchcolumn
	\charactername{菲比：}好的。
	\switchcolumn*
	\charactername{Monica:} Are you alright?
	\switchcolumn
	\charactername{莫妮卡：}你没事吧？
	\switchcolumn*
	\charactername{Phoebe:} Yeah. It’s just, you know, it’s this whole stupid Ursula thing, it’s...
	\switchcolumn
	\charactername{菲比：}嗯。只是，你知道，就是厄休拉这档子蠢事，这…
	\switchcolumn*
	\charactername{Rachel:} Okay, Pheebs, can I ask? So, he’s going out with her. I mean, is it really so terrible?
	\switchcolumn
	\charactername{瑞秋：}好吧，菲比，我能问一下吗？所以，他在和她约会。我是说，真的那么糟吗？
	\switchcolumn*
	\charactername{Phoebe:} Um, yeah. Look, I mean, I’m not saying she’s like evil or anything. She just, you know, she’s always breaking my stuff. When I was eight, and I wouldn’t let her have my Judy Jetson thermos, so she threw it under the bus. And then, oh, and then there was Randy Brown, who was like... Have you ever had a boyfriend who was like your best friend?
	\switchcolumn
	\charactername{菲比：}嗯，是的。听着，我的意思是，我不是说她像邪恶什么的。她只是，你知道，她总是弄坏我的东西。我八岁时，我不让她用我的朱迪·杰森保温瓶，她就把它扔到了公交车底下。然后，哦，然后还有兰迪·布朗，他就像…你们有没有过像自己最好的朋友一样的男朋友？
	\switchcolumn*
	\charactername{Monica and Rachel:} \ennotmain{Wistfully, shaking their heads} No.
	\switchcolumn
	\charactername{莫妮卡和瑞秋：}\ennotmain{惆怅地，摇头}没有。
	\switchcolumn*
	\charactername{Phoebe:} Well, but that’s what he was for me. And she you know, kind of stole him away, and then... broke his heart... and then he wouldn’t even talk to me any more. Because he said he didn’t wanna be around... anything that looked like either one of us.
	\switchcolumn
	\charactername{菲比：}嗯，但对我来说他就是那样的。而她，你知道，算是把他抢走了，然后…伤透了他的心…然后他再也不理我了。因为他说他不想靠近…任何长得像我们俩其中一个的东西。
	\switchcolumn*
	\charactername{Rachel:} Oh... Oh, Pheebs.
	\switchcolumn
	\charactername{瑞秋：}哦…哦，菲比。
	\switchcolumn*
	\charactername{Phoebe:} I mean, I know Joey is not my boyfriend, or my thermos, or anything, but...
	\switchcolumn
	\charactername{菲比：}我是说，我知道乔伊不是我的男朋友，也不是我的保温瓶，或任何东西，但是…
	\switchcolumn*
	\charactername{Chandler:} You’re not gonna lose him.
	\switchcolumn
	\charactername{钱德勒：}你不会失去他的。
	\switchcolumn*
	\charactername{Monica:} Hon, you gotta talk to Joey.
	\switchcolumn
	\charactername{莫妮卡：}亲爱的，你得和乔伊谈谈。
	\switchcolumn*
	\charactername{Phoebe:} Yeah. Okay.
	\switchcolumn
	\charactername{菲比：}是啊。好吧。
	\switchcolumn*
	\charactername{Ross:} No, come on, he doesn’t know this stuff. If he knew how you felt.
	\switchcolumn
	\charactername{罗斯：}不，拜托，他不知道这些事。如果他知道你的感受。
	\switchcolumn*
	\charactername{Phoebe:} But he’s falling in love with her.
	\switchcolumn
	\charactername{菲比：}但他正在爱上她。
	\switchcolumn*
	\charactername{Rachel:} Oh please, they’ve been going out a week. They haven’t even slept together yet, I mean, that’s not serious.
	\switchcolumn
	\charactername{瑞秋：}哦拜托，他们才约会一周。他们甚至还没上过床呢，我是说，那不算认真。
	\switchcolumn*
	\charactername{Phoebe:} Okay... Okay.
	\switchcolumn
	\charactername{菲比：}好吧…好吧。
	\switchcolumn*
	\ennotmain{Monica and Ross indicate that they mean right now.}
	\switchcolumn
	\ennotmain{莫妮卡和罗斯示意他们指的是现在就去。}
	\switchcolumn*
	\charactername{Phoebe:} Oh, okay, oh.
	\switchcolumn
	\charactername{菲比：}哦，好吧，哦。
	\switchcolumn*
	\ennotmain{Phoebe gets up and walks across the hallway, but the door to Chandler and Joey’s apartment is shut. She knocks, and anxiously waits for Joey to come, but instead her identical twin sister emerges wearing one of Joey’s shirts.}
	\switchcolumn
	\ennotmain{菲比起身穿过走廊，但钱德勒和乔伊公寓的门关着。她敲门，焦急地等待乔伊开门，但开门的是她同卵双胞胎姐姐，穿着乔伊的一件衬衫。}
	\switchcolumn*
	\charactername{Ursula:} \ennotmain{Surprised} Oh.
	\switchcolumn
	\charactername{厄休拉：}\ennotmain{惊讶地}哦。
	\switchcolumn*
	\ennotmain{Phoebe reels back in shock, while Ursula defiantly leans against the doorpost as though she owns the place.}
	\switchcolumn
	\ennotmain{菲比震惊地后退，而厄休拉挑衅地靠在门框上，仿佛这是她的地盘。}
	\switchcolumn*
	\charactername{Ursula:} Yeah, um, may we help you?
	\switchcolumn
	\charactername{厄休拉：}是啊，嗯，需要我们帮忙吗？
	\switchcolumn*
	\closingcredits
	\switchcolumn
	\closingcreditscn
	\switchcolumn*
	\sense{Scene: Monica and Rachel's Balcony, Rachel is taking down the Christmas lights. Monica sees her, so she leans out of the small side window.}
	\switchcolumn
	\sense{场景：莫妮卡和瑞秋的阳台，瑞秋正在取下圣诞彩灯。莫妮卡看到她，于是从小侧窗探出身来。}
	\switchcolumn*
	\charactername{Monica:} Rachel, what are you doing? It’s freezing out here. Would you come back inside?
	\switchcolumn
	\charactername{莫妮卡：}瑞秋，你在干什么？外面冻死了。你进来好吗？
	\switchcolumn*
	\charactername{Rachel:} No no no no no. You wanted me to take them down, so... \ennotmain{she climbs onto the railing to reach the top of a pole} ..I’m takin’ ’em down. Okay? Whoa! \ennotmain{Screams.}
	\switchcolumn
	\charactername{瑞秋：}不不不不不。你想让我把它们取下来，所以…\ennotmain{她爬到栏杆上够到一根杆子的顶端}…我这就把它们取下来。行了吧？哇啊！\ennotmain{尖叫。}
	\switchcolumn*
	\ennotmain{Rachel slips, loses her balance, and falls over the edge..}
	\switchcolumn
	\ennotmain{瑞秋滑倒，失去平衡，从边缘掉了下去…}
	\switchcolumn*
	\charactername{Monica:} Oh-my-god Rachel! \ennotmain{Rushing out to look over the edge} Rachel!
	\switchcolumn
	\charactername{莫妮卡：}哦-我的天啊瑞秋！\ennotmain{冲出去从边缘往下看}瑞秋！
	\switchcolumn*
	\ennotmain{In the apartment below, Mr.Heckles is trying to relax and read his newspaper, but Rachel is helplessly dangling upside-down with her ankle wrapped up in the Christmas lights.}
	\switchcolumn
	\ennotmain{在楼下的公寓里，赫克斯先生正试图放松看报纸，但瑞秋无助地倒挂着，脚踝缠在圣诞彩灯里。}
	\switchcolumn*
	\charactername{Rachel:} \ennotmain{To Monica} I’m okay! I’m okay! \ennotmain{She knocks on Mr. Heckles's window.} Mr. Heckles, Mr. Heckles could you help me please?
	\switchcolumn
	\charactername{瑞秋：}\ennotmain{对莫妮卡}我没事！我没事！\ennotmain{她敲敲赫克斯先生的窗户。}赫克斯先生，赫克斯先生，你能帮帮我吗？
	\switchcolumn*
	\charactername{Mr.Heckles:} See, this is just the kind of thing I was talking about.
	\switchcolumn
	\charactername{赫克斯先生：}看，这就是我说的那种事。
	\switchcolumn*
	\eendtextenglish
	\switchcolumn
	\eendtextchinese
	\switchcolumn*

\end{paracol}
\newpage