\section{Lesson 65 Jumbo versus the police}

\begin{paracol}{2}

Last Christmas, the circus owner, Jimmy Gates, decided to take some presents to a children's hospital. 

\switchcolumn

去年圣诞节，马戏团老板吉米·盖茨决定送些礼物给儿童医院。

\switchcolumn*

Dressed up as Father Christmas and accompanied by a ‘guard of honour' of six pretty girls, he \ns{set off} down the main street of the city riding a baby elephant called Jumbo.

\switchcolumn

他打扮成圣诞老人，在由6个漂亮姑娘组成的“仪仗队”的陪同下，骑上一头名叫江伯的小象，沿着城里的主要街道出发了。
\nse{set off}{}{出发}

\switchcolumn*

He should have known that the police would never allow this \nw{sort of} thing.

\switchcolumn

他本该知道警察绝不会允许这类事情发生。
\nse{sort or}{}{此类事情}

\switchcolumn*

A policeman approached Jimmy and told him he ought to have gone along a side street as Jumbo was \ns{holding up} the traffic.

\switchcolumn

一个警察走过来告诉吉米，他应该走一条小路，因为江伯阻碍了交通。

\nse{hold up}{}{阻碍}

\switchcolumn*

Though Jimmy agreed to go at once, Jumbo refused to move.

\switchcolumn

虽然吉米同意马上就走，但江伯却拒绝移动。

\switchcolumn*

Fifteen policemen had to push very hard to \ns{get him off} the main street.

\switchcolumn

15个警察不得不用很大的力气把它推离主要街道。

\switchcolumn*

The police had a difficult time, but they were most amused.

\switchcolumn

警察虽然吃了苦头，但他们还是感到很有趣。

\switchcolumn*

'Jumbo must weigh a few tons,' said a policeman \nw{afterwards},'so it was fortunate that we didn't have to carry him. Of course, we should arrest him, but as he has a good record, we shall \ns{let him off} this time.'

\switchcolumn

“江伯一定有好几吨重，”一个警察事后这样说，“值得庆幸的是它没让我们抬它走。当然，我们应该逮捕它。但由于它一贯表现很好，这次我们饶了它。’

\nse{let sb. off}{}{饶恕}

\switchcolumn*

\end{paracol}

\newpage