\section{Lesson 68 Persistent}

\begin{paracol}{2}


I crossed the street to avoid meeting him, but he saw me and came running towards me. 

\switchcolumn

我穿过马路以便避开他，但他看到我并朝我跑过来。

\switchcolumn*

It was no use pretending that I had not seen him, so I waved to him. 

\switchcolumn

若再装作没看见他已是没有用了，我只好向他招手。

\switchcolumn*

I never enjoy meeting Nigel Dykes. 

\switchcolumn
我就怕遇到奈杰尔·戴克斯。
\switchcolumn*

He never has anything to do. 

\switchcolumn
他从来都是无事可做。
\switchcolumn*

No matter how busy you are, he always insists on coming with you. 

\switchcolumn

不管你多忙，他总是坚持要跟你去。

\switchcolumn*

I had to think of a way of preventing him from following me around all morning.

\switchcolumn


我得想办法不让他整个上午缠着我。

\switchcolumn*

‘Hello, Nigel,’ I said. ‘Fancy meeting you here!’

\switchcolumn

“你好,奈杰尔,想不到在这儿见到你。”我说。

\switchcolumn*

“Hi, Elizabeth,’' Nigel answered. 

\switchcolumn

“你好，伊丽莎白奈。”杰尔回答说，

\switchcolumn*

‘I was just wondering how to spend the morning ——until I saw you. 

\switchcolumn

“我正不知道怎么消磨这一上午呢,正好见到你。

\switchcolumn*

You're not busy doing anything, are you?'

\switchcolumn

你不忙，是吗? 

\switchcolumn*

‘No, not at all,’ I answered. ‘I'm going to . ..’

\switchcolumn

“不,不忙,我打算去...”我回答。

\switchcolumn*

‘Would you mind my coming with you?' he asked, before I had finished speaking. 

\switchcolumn

“我跟你一道去行吗?”没等我说完话他就问道。

\switchcolumn*

‘Not at all,' I lied, ‘but I'm going to the dentist.’

\switchcolumn

“没关系,但我准备去牙医那里。”我说了个谎。

\switchcolumn*

‘Then I'll come with you,’ he answered. 

\switchcolumn

“那我也跟你去，”他回答。

\switchcolumn*

‘There’s always plenty to read in the waiting room!'

\switchcolumn

“候诊室里总有很多东西可供阅读!”

\switchcolumn*


\end{paracol}