\section{Lesson 66 Sweet as honey!}

\begin{paracol}{2}


In 1963 a Lancaster bomber crashed on Wallis Island, a remote place in the South Pacific, a long way west of Samoa.
\switchcolumn

1963年，一架兰开斯特轰炸机在瓦立斯岛坠毁。那是南太平洋中一个很偏僻的小岛，位于萨摩亚群岛以西，距离群岛还有很长一段距离。

\switchcolumn*

The plane wasn't too badly damaged. but \ns{over the years}, the crash was forgotten and the \nw{wreck} remained \nw{undisturbed}.
\switchcolumn
飞机损坏的程度并不严重，但是，多年来这起飞机失事已被遗忘，飞机残骸也没受到破坏。
\nwe{wreck}{}{残骸}
\nwe{undisturbed}{}{}
\switchcolumn*

Then in 1989, twenty-six years after the crash, the plane was accidentally rediscovered in an \nw{aerial} survey of the island.
\switchcolumn
于是,到了1989年，飞机失事26年后，在对小岛的一次航空勘查中那架飞机被意外地发现了。
\nwe{aerial}{}{航空的}
\switchcolumn*

By this time, a Lancaster bomber in reasonable condition was rare and worth rescuing.
\switchcolumn
到了那个时候，状况良好的兰开斯特轰炸机实属罕见，值得抢救。
\switchcolumn*

The French authorities had the plane packaged and moved in parts back to France. 
\switchcolumn
法国政府让人把飞机包装起来，一部分一部分地搬回法国。
\switchcolumn*

Now a group of \nw{enthusiasts} are going to have the plane \nw{restored}.
\switchcolumn
一群热心人计划修复这架飞机。
\nwe{enthusiast}{}{热心人}
\switchcolumn*

It has four Rolls-Royce Merlin engines, but the group wil need to have only three of them rebuilt.
\switchcolumn
该飞机装配有4台罗尔斯-罗伊斯的默林发动机，但是他们只需要修复其中的3台。
\switchcolumn*

Imagine their surprise and delight when they broke open the packing cases and found that the fourth engine was sweet as honey - still in perfect condition.
\switchcolumn
想一想他们所感受到的惊奇和兴奋——当他们拆开包装箱时，他们发现第4台发动机就像蜂蜜一样甜——发动机完好无损。
\switchcolumn*

A colony of bees had turned the engine into a \textbf{hive} and it was totally preserved in \textbf{beeswax}!
\switchcolumn
一群蜜蜂把发动机当作了蜂房，发动机在蜂蜡中被完整地保存了下来。
\nwe{hive}{haɪv}{蜂房}
\nwe{preserve}{}{保护}
\nwe{beeswax}{}{蜂蜡}
\switchcolumn*


\end{paracol}

\newpage