\section{Lesson 48 The silent village}
\begin{paracol}{2}

In this much-travelled world, there are still thousands of places which are inaccessible to tourists.

\switchcolumn

\chinesetext{在这个旅游频繁的世界上，仍有成千上万个游人足迹未至的地方。}

\switchcolumn*

We always assume that villagers in remote places are friendly and hospitable.

\switchcolumn

\chinesetext{人们总是以为偏僻的地方的村民们热情好客。}

\switchcolumn*

But people who are cut off not only from foreign tourists, but even from their own countrymen can be hostile to travellers.

\switchcolumn

\chinesetext{但是，那些不但与外国旅游者隔绝，而且与本国同胞隔绝的人们有可能对游客抱有敌意。}

\switchcolumn*

Visits to really remote villages are seldom enjoyable--as my wife and I discovered during a tour through the Balkans.

\switchcolumn

\chinesetext{到真正偏僻的村庄去旅游并不是一件愉快的事情。我与妻子在一次周游巴尔干半岛时对此深有体会。}

\switchcolumn*

We had spent several days in a small town and visited a number of old churches in the vicinity.

\switchcolumn

\chinesetext{我们在一座小镇上逗留了几天，参观了附近的许多古老的教堂。}

\switchcolumn*

These attracted many visitors, for they were not only of great architectural interest, but contained a large number of beautifully preserved frescoes as well.

\switchcolumn

\chinesetext{这些教堂吸引大量游客，不仅是因为建筑风格奇特，而且还有大量保存完好的壁画。}

\switchcolumn*

On the day before our departure, several bus loads of tourists descended on the town.

\switchcolumn

\chinesetext{我们离开小镇的前一天，镇上来了几辆满载游客的公共汽车。}

\switchcolumn*

This was more than we could bear, so we decided to spend our last day exploring the countryside.

\switchcolumn

\chinesetext{人多得使我们难以忍受，于是我们决定利用最后一天去乡间一游。}

\switchcolumn*

Taking a path which led out of the town, we crossed a few fields until we came to a dense wood.

\switchcolumn

\chinesetext{我们走上了一条出镇的小路，穿过几块农田，来到一片茂密的树林。}

\switchcolumn*

We expected the path to end abruptly, but we found that it traced its way through the trees.

\switchcolumn

\chinesetext{我们原以为小路会到此突然终止。没想到它到树林中继续向前延伸。}

\switchcolumn*

We tramped through the wood for over two hours until we arrived at a deep stream.

\switchcolumn

\chinesetext{我们在树林中跋涉了两个多小时，到了一条深溪边。}

\switchcolumn*

We could see that the path continued on the other side, but we had no idea how we could get across the stream.

\switchcolumn

\chinesetext{我们可以看到小路在深溪对岸继续向前伸展，但却不知如何越过这道深溪。}

\switchcolumn*

Suddenly my wife spotted a boat moored to the bank. 

\switchcolumn

\chinesetext{突然，妻子发现岸边泊着一条小船。}

\switchcolumn*

In it there was a boatman fast asleep.

\switchcolumn

\chinesetext{船上有一船夫在呼呼大睡。}

\switchcolumn*

We gently woke him up and asked him to ferry us to the other side.

\switchcolumn

\chinesetext{我们轻轻地把他唤醒，请他把我们摆渡过溪。}

\switchcolumn*

Though he was reluctant to do so at first, we eventually persuaded him to take us.

\switchcolumn

\chinesetext{一开始，他很不愿意，但经劝说，终于同意了。}

\switchcolumn*

The path led to a tiny village perched on the steep sides of a mountain.

\switchcolumn

\chinesetext{顺着小路，我们来到一个座落在陡峭山坡上的小村庄。}

\switchcolumn*

The place consisted of a straggling unmade road which was lined on either side by small houses.

\switchcolumn

\chinesetext{这儿有一条未经修筑的弯弯曲曲的道路，路两边排列着一些矮小的农舍。}

\switchcolumn*

Even under a clear blue sky, the village looked forbidding, as all the houses were built of grey mud bricks.

\switchcolumn

\chinesetext{农舍全用灰色的土坯建成，因此，即使在晴朗的蓝天底下，村庄看上去也会令人感到难以亲近。}

\switchcolumn*

The village seemed deserted, the only sign of life being an ugly-looking black goat on a short length of rope tied to a tree in a field nearby.

\switchcolumn

\chinesetext{村里似乎无人居住，唯一的生命迹象是附近田里一只面目可憎的黑山羊，用一截短绳拴在一棵树上。}

\switchcolumn*

Sitting down on a dilapidated wooden fence near the field, we opened a couple of tins of sardines and had a picnic lunch.

\switchcolumn

\chinesetext{我们在田边一堵东倒西歪的篱笆墙上坐下来，打开几听沙丁鱼罐头，吃了一顿野外午餐。}

\switchcolumn*

All at once, I noticed that my wife seemed to be filled with alarm.

\switchcolumn

\chinesetext{突然，我注意到妻子十分惊恐。}

\switchcolumn*

Looking up I saw that we were surrounded by children in rags who were looking at us silently as we ate.

\switchcolumn

\chinesetext{我抬头一看，发现我们被一群衣衫褴褛的小孩团团围住了，他们在默不作声地看着我们吃饭。}

\switchcolumn*

We offered them food and spoke to them kindly, but they remained motionless.

\switchcolumn

\chinesetext{我们给他们东西吃，客客气气地同他们交谈，但他们却一动也不动。}

\switchcolumn*

I concluded that they were simply shy of strangers.

\switchcolumn

\chinesetext{我认为这不过是他们在陌生人面前表现出的害羞。}

\switchcolumn*

When we later walked down the main street of the village, we were followed by a silent procession of children.

\switchcolumn

\chinesetext{后来，我们在村里的主要街道上行走的时候，一队默不作声的孩子跟在我们后头。}

\switchcolumn*

The village which had seemed deserted, immediately came to life.

\switchcolumn

\chinesetext{刚才还似乎空荡荡的村庄一下子活跃了起来。}

\switchcolumn*

Faces appeared at windows.

\switchcolumn

\chinesetext{窗口露出了一张张面孔。}

\switchcolumn*

Men in shirt sleeves stood outside their houses and glared at us.

\switchcolumn

\chinesetext{只穿着衬衣的男人们站在屋子外面凶狠地盯着我们。}

\switchcolumn*

Old women in black shawls peered at us from doorways.

\switchcolumn

\chinesetext{披黑纱巾的老妇人站在门口偷偷地瞅着我们。}

\switchcolumn*

The most frightening thing of all was that not a sound could be heard.

\switchcolumn

\chinesetext{最令人害怕的是到处没有一点声音。}

\switchcolumn*

There was no doubt that we were unwelcome visitors.

\switchcolumn

\chinesetext{毫无疑问，我们的来访是不受欢迎的。}

\switchcolumn*

We needed no further warning.

\switchcolumn

\chinesetext{我们不需要进一步的警告了。}

\switchcolumn*

Turning back down the main street, we quickened our pace and made our way rapidly towards the stream where we hoped the boatman was waiting.

\switchcolumn

\chinesetext{便掉转身子，沿着那条主要街道加快步伐，快速地朝深溪边走去，希望船夫还在那儿等着我们。}

\switchcolumn*

\end{paracol}

\newpage