\section{Lesson 57 Back in the old country}
\begin{paracol}{2}

I stopped to let the car cool off and to study the map.

\switchcolumn

\chinesetext{我停下车，让汽车发动机冷却一下，同时查看一下地图。}

\switchcolumn*

I had expected to be near my objective by now, but everything still seemed alien to me.

\switchcolumn

\chinesetext{我本想离目的地已经不远，但周围一切对我仍很陌生。}

\switchcolumn*

I was only five when my father had taken me abroad, and that was eighteen years ago.

\switchcolumn

\chinesetext{我5岁那年，父亲就带我出了国，那是18年前的事了。}

\switchcolumn*

When my mother had died after a tragic accident, he did not quickly recover from the shock and loneliness.

\switchcolumn

\chinesetext{当时我母亲在一次事故中惨死，父亲未能很快从悲痛与孤独中恢复过来。}

\switchcolumn*

Everything around him was full of her presence, continually reopening the wound.

\switchcolumn

\chinesetext{他身边的一切都是母亲的影子不断勾起他的伤感。}

\switchcolumn*

So he decided to emigrate.

\switchcolumn

\chinesetext{于是他决定移居他国。}

\switchcolumn*

In the new country he became absorbed in making a new life for the two of us, so that he gradually ceased to grieve.

\switchcolumn

\chinesetext{在这个新的国家里，父亲专心致志地为我们俩开创一种新的生活，慢慢地不伤心了。}

\switchcolumn*

He did not marry again and I was brought up without a woman's care;but I lacked for nothing, for he was both father and mother to me.

\switchcolumn

\chinesetext{父亲没有再娶，因此，我在没有母亲的环境里长大成人。但我却什么都不缺，他既当父亲又当母亲。}

\switchcolumn*

He always meant to go back one day, but not to stay.

\switchcolumn

\chinesetext{他总想将来回国看看，但却不愿长期住下去。}

\switchcolumn*

His roots and mine had become too firmly embedded in the new land.

\switchcolumn

\chinesetext{因为他与我一样已经把根深深地扎在异国的土地上。}

\switchcolumn*

But he wanted to see the old folk againand to visit my mother's grave.

\switchcolumn

\chinesetext{ 但是，他想看一看家乡父老乡亲，为我的母亲扫墓。}

\switchcolumn*

He became mortally ill a few months before we had planned to go and, when he knew that he was dying, he made me promise to go on my own.

\switchcolumn

\chinesetext{就在他计划回国的前几个月，他突然身患绝症。他知道自己已奄奄一息，于是他要我答应一定单独回故乡一趟。}

\switchcolumn*

I hired a car the day after landing and bought a comprehensive book of maps, which I found most helpful on the cross-country journey, but which I did not think I should need on the last stage.

\switchcolumn

\chinesetext{我下飞机后租了一辆车，并买了一本详尽的地图册。在乡间行车途中，我觉得它非常有用，但快到家了，我倒觉得它没什么用了。}

\switchcolumn*

It was not that I actually remembered anything at all.

\switchcolumn

\chinesetext{这倒并非是我背熟了地图。}

\switchcolumn*

But my father had described over and over again what we should see at every milestone after leaving the nearest town, so that I was positive I should recognize it as familiar territory.

\switchcolumn

\chinesetext{而是父亲曾详细给我讲了，在过了离故乡最近的那个小镇后，在每一个路标处可见到些什么。因此，我相信这段路对我来说会是很熟悉的。}

\switchcolumn*

Well, I had been wrong, for I was now lost.

\switchcolumn

\chinesetext{唉，实际我错了，我现在迷路了。}

\switchcolumn*

I looked at the map and then at the milometer.

\switchcolumn

\chinesetext{我看了看地图，又查了一下里程表。}

\switchcolumn*

I had come ten miles since leaving the town and at this point, according to my father, I should be looking at farms and cottages in a valley, with the spire of the church of our village showing in the far distance.

\switchcolumn

\chinesetext{从小镇出来，我走了10英里。照父亲的说法，我面前应是一个山谷，有农场与村舍，还可远远望见老家村子里的教堂的尖顶。}

\switchcolumn*

I could see no valley, no farms, no cottages and no church spire-only a lake.

\switchcolumn

\chinesetext{可现在我却看不出山谷，看不见农舍，也看见教学尖顶，看见只是一片湖泊。}

\switchcolumn*

I decided that I must have taken a wrong turning somewhere.

\switchcolumn

\chinesetext{我想一定是什么地方拐错了弯儿。}

\switchcolumn*

So I drove back to the town and began to retrace the route, taking frequent glances at the map.

\switchcolumn

\chinesetext{于是我驾车返回小镇，重新按路线行驶。}

\switchcolumn*

I landed up at the same corner.

\switchcolumn

\chinesetext{结果又来到刚才那个拐弯处。}

\switchcolumn*

The curious thing was that the lake was not marked on the map.

\switchcolumn

\chinesetext{奇怪的是那个湖没有在地图上标出。}

\switchcolumn*

I felt as if I had stumbled into a nightmare country, as you sometimes do in dreams.

\switchcolumn

\chinesetext{我感到自己就像平时作梦那样迷迷糊糊地闯进了恶梦境地。}

\switchcolumn*

And, as in a nightmare, there was nobody in sight to help me.

\switchcolumn

\chinesetext{就像在恶梦里一样，见不到一个人可以帮助我。}

\switchcolumn*

Fortunately for me, as I was wondering what to do next, there appeared on the horizon a man on horseback, riding in my direction.

\switchcolumn

\chinesetext{不过，我是幸运的，正当我走投无路之时，从天边出现一个骑马的人向我骑来。}

\switchcolumn*

I waited till he came near, then I asked him the way to our old village.

\switchcolumn

\chinesetext{等他走近了，问他去老家的路。}

\switchcolumn*

He said that there was now no village.

\switchcolumn

\chinesetext{他说那村子已经没有了。}

\switchcolumn*

I thought he must have misunderstood me, so I repeated its name.

\switchcolumn

\chinesetext{我想他一定误解了我的意思，于是又说一遍村庄的名字。}

\switchcolumn*

This time he pointed to the lake.

\switchcolumn

\chinesetext{这次他用手指了一下那个湖。}

\switchcolumn*

The village no longer existed because it had been submerged, and all the valley too.

\switchcolumn

\chinesetext{村庄已不复存在，因为已经为水所淹，山谷也被水淹没了。}

\switchcolumn*

The lake was not a natural one, but a man-made reservoir.

\switchcolumn

\chinesetext{这不是一个天然湖泊，是一座人工修建的水库。}

\switchcolumn*

\end{paracol}

\newpage