\section{Lesson 50 New Year resolutions}
\begin{paracol}{2}

The New Year is a time for resolutions.

\switchcolumn

\chinesetext{新年是下决心的时候。}

\switchcolumn*

Mentally, at least, most of us could compile formidable lists of 'dos' and 'don'ts'.

\switchcolumn

\chinesetext{至少在大多数人的心里会编排出一份"应做什么"和"不应做什么"的令人生畏的单子。}

\switchcolumn*

The same old favourites recur year in year out with monotonous regularity.

\switchcolumn

\chinesetext{相同的决心以单调的规律年复一年地出现。}

\switchcolumn*

We resolve to get up earlier each morning, eat less, find more time to play with the children, do a thousand and one jobs about the house, be nice to people we don't like, drive carefully, and take the dog for a walk every day.

\switchcolumn

\chinesetext{我们决心每天早晨起得早些；吃得少些；多花点时间与孩子们一起做游戏；做大量的家务；对不喜欢的人友善一些；小心驾车；每天都要带着狗散步；等等。}

\switchcolumn*

Past experience has taught us that certain accomplishments are beyond attainment.

\switchcolumn

\chinesetext{以往的经验告诉我们有些事是办不到的。}

\switchcolumn*

If we remain inveterate smokers, it is only because we have so often experienced the frustration that results from failure.

\switchcolumn

\chinesetext{如果我们烟瘾大，戒不掉，那是因为屡戒屡败，失去信心。}

\switchcolumn*

Most of us fail in our efforts at sel-improvement because our schemes are too ambitious and we never have time to carry them out.

\switchcolumn

\chinesetext{我们大多数人想自我完善却遭到失败，这是因为我们的规划过于宏大，而又根本没有时间去实施。}

\switchcolumn*

We also make the fundamental error of announcing our resolutions to everybody so that we look even more foolish when we slip back into our bad old ways.

\switchcolumn

\chinesetext{我们还犯有一个根本性的错误，即把我们的决心向大家宣布。这样一旦滑回到那些老习惯上去，我们在别人的眼里会显得更加难堪。}

\switchcolumn*

Aware of these pitfalls, this year I attempted to keep my resolutions to myself.

\switchcolumn

\chinesetext{我深知这些问题，于是，今年我对自己的计划要严加保密。}

\switchcolumn*

I limited myself to two modest ambitions: to do physical exercises every morning and to read more of an evening.

\switchcolumn

\chinesetext{只给自己定下两项适中的任务：每天早上锻炼身体，每天晚上多看点书。}

\switchcolumn*

An all-night party on New Year's Eve provided me with a good excuse for not carrying out either of these new resolutions on the first day of the year, but on the second, I applied myself assiduously to the task.

\switchcolumn

\chinesetext{新年除夕举办的一次通宵晚会，使我理直气壮地在新年头一天免去了这两项任务。不过，新年第二天，我全力以赴地照着去做了。}

\switchcolumn*

The daily exercises lasted only eleven minutes and I proposed to do them early in the morning before anyone had got up.

\switchcolumn

\chinesetext{早锻炼一共只有11分钟，我打算在别人起床之前进行。}

\switchcolumn*

The self-discipline required to drag myself out of bed 11 minutes earlier than usual was considerable.

\switchcolumn

\chinesetext{这就要求我比平时早11分钟把自己从床上拽起来，这种自我约束是很艰苦的。}

\switchcolumn*

Nevertheless, I managed to creep down into the living room for two days before anyone found me out.

\switchcolumn

\chinesetext{不过开头两天我还是成功地蹑手蹑脚地来到楼下起居室，被谁也没发现。}

\switchcolumn*

After jumping about on the carpet and twisting the human frame into uncomfortable positions, I sat down at the breakfast table in an exhausted condition.

\switchcolumn

\chinesetext{我在地毯上跳来蹦过去，扭曲身子，摆出各种姿势，弄得浑身不舒服，然后坐到桌边吃早饭，一副筋疲力尽的样子。}

\switchcolumn*

It was this that betrayed me.

\switchcolumn

\chinesetext{正是这副模样泄露了我的秘密。}

\switchcolumn*

The next morning the whole family trooped in to watch the performance.

\switchcolumn

\chinesetext{第二天早晨全家人结队来到起居室看我表演。}

\switchcolumn*

That was really unsettling but I fended off the taunts and jibes of the family good-humouredly and soon everybody got used to the idea.

\switchcolumn

\chinesetext{这真叫人不好意思，但我心平气和地顶住全家人的嘲笑和奚落。不久，大家对我习以为常了。}

\switchcolumn*

However, my enthusiasm waned.

\switchcolumn

\chinesetext{而这时我的热情却减退了。}

\switchcolumn*

The time I spent at exercises gradually diminished.

\switchcolumn

\chinesetext{我花在锻炼上的时间逐渐减少。}

\switchcolumn*

Little by little the eleven minutes fell to zero.

\switchcolumn

\chinesetext{慢慢地从11分钟减到了零。}

\switchcolumn*

By January 10th, I was back to where I had started from.

\switchcolumn

\chinesetext{到了1月10日，我恢复了原来的作息时间。}

\switchcolumn*

I argued that if I spent less time exhausting myself at exercises in the morning, I would keep my mind fresh for reading when I got home from work.

\switchcolumn

\chinesetext{我辩解说，早晨少耗费精力锻炼，晚上下班回家看书时头脑更清醒些。}

\switchcolumn*

Resisting the hypnotizing effect of television, I sat in my room for a few evenings with my eyes glued to a book.

\switchcolumn

\chinesetext{有几天晚上，我极力摆脱了电视的诱惑，坐在自己的房间里，两眼盯在书上。}

\switchcolumn*

One night, however, feeling cold and lonely, I went downstairs and sat in front of the television pretending to read.

\switchcolumn

\chinesetext{可是，有一天夜里，我感到又冷又孤单，便来到楼下坐在电视机前假装看书。}

\switchcolumn*

That proved to be my undoing, for I soon got back to my old bad habit of dozing off in front of the screen.

\switchcolumn

\chinesetext{这下我可完了，因为不一会儿，我就恢复了以前的坏习惯，在屏幕前打起瞌睡来。}

\switchcolumn*

I still haven't given up my resolution to do more reading.

\switchcolumn

\chinesetext{但我还没有放弃多看些书的决心。}

\switchcolumn*

In fact, I have just bought a book entitled How to Read a Thousand Words a Minute.

\switchcolumn

\chinesetext{事实上，我刚买来一本叫《一分钟读一千字的诀窍》的书。}

\switchcolumn*

Perhaps it will solve my problem, but I just haven't had time to read it!

\switchcolumn

\chinesetext{也许这本书能解决我的问题，但我一直还没时间去看这本书！}

\switchcolumn*

\end{paracol}

\newpage