\section{Getting Along in One's Schoolwork}

\begin{paracol}{2}

\englishtext{Tom Jackson and Dave Page were \ns{heading for} the library. Lee Choy and Pedro Garcia \ns{caught up with} them.}

\switchcolumn

\nse{head for}{}{朝…进发;<非正>引向好[坏]结果;奔;走向;}
\nse{catch up with}{}{追上; 赶上;和…算旧账;使…最终尝到苦果;}

\switchcolumn*

\englishtext{"Are you \ns{going after} a book?" Lee asked Tom.}

\switchcolumn

\nse{go after}{}{追逐，追求;跟随;骛;}

\switchcolumn*

\englishtext{"Yes," said Tom. "I need to \ns{look for} another book about airplanes. I was \ns{checking my paper over}, and I \ns{found out} that I had \ns{put in} some wrong information."}

\switchcolumn

\nse{look for}{}{寻找（某人或某物）;<口>找（麻烦）;找（苦头）吃;希望得到;}
\nse{check sth. over}{}{核对，仔细检查;}
\nse{find out}{}{发现;使发作;使受惩罚;通过探询[访问]获悉（某人）不在;}

\switchcolumn*

\englishtext{"I have to \ns{look up} an article," Dave added. "My history teacher asked us to \ns{read through} a long article. \ns{Keeping up with} that course is difficult for me. I'm always \ns{falling behind}. That's because I \ns{put off} doing my assignments."}

\switchcolumn

\nse{read through}{}{仔细阅读;通读;}
\nse{keep up with}{}{跟上，保持同步;}
\nse{fall behind}{}{不能按时完成（工作;}
\nse{put off}{}{推迟...，使...延期;}

\switchcolumn*

{"So do I," said Pedro. "Right now I'm writing a paper for my science class. I \ns{tore the first paper up} because it was bad. Now I have several new ideas, and I've been \ns{trying them out} on my friend Maria. I have to \ns{hand the paper in} on Monday. I also need to \ns{brush up on} my mathematics, but I can't \ns{figure out} the meanings of some of those strange-looking signs."}


\switchcolumn

\nse{tear sth. up}{}{撕成碎片;挖开（地面等）;撕掉;撕毁;}
\nse{try sb. out on sth.}{}{在……（某事）上测试/试验某人}
\nse{hand sth. in}{}{交上; 递交; 呈送;把…扶上车;}
\nse{brush up on}{}{温习，复习;}
\nse{figure out}{}{弄懂；弄清楚；弄明白;}

\switchcolumn*

\englishtext{"I know what you mean," Dave told him. "I don't know what some of the signs \ns{stand for}, either."}

\switchcolumn

\nse{stand for}{}{代表;为…而奋斗;拥护;<口>容忍;}

\switchcolumn*

\englishtext{"I need to \ns{make up} a test," Tom said. "I missed it when I was sick. But I'll wait until I have \ns{turned in} my paper on airplanes. I keep a list of things I should do, and I \ns{cross them off} \ns{one by one} I do them."}

\switchcolumn

\nse{make up}{}{构成；形成;编造;化妆;凑足;}
\nse{turn in}{}{上床睡觉;上交;归还;面向内;}
\nse{cross sb. off}{}{划掉;}
\nse{one by one}{}{依次地，一个接一个地;}

\switchcolumn*

\englishtext{"You’re so systematic, Tom," Dave said, smiling. "You always plan everything. I should \ns{put together} a list, too, but it would be too long. I would just \ns{give up}."}

\switchcolumn

\nse{put together}{}{组成整体;综;缀合;拼;}
\nse{give up}{}{放弃；投降;}

\switchcolumn*

\englishtext{"I sometimes want to \ns{give up}, too," said Tom, "but then I think that I'll \ns{pull through} somehow. Studying so much is hard, but usually we \ns{get along} rather well. We just have to \ns{keep at} it."}

\switchcolumn

\nse{pull through}{}{<非正>恢复健康，精神状况转好，情绪转好;渡;}
\nse{get along}{}{相处;进展;前进;离去;}
\nse{keep at}{}{坚持;督促;备有;耽搁;}

\switchcolumn*

\englishtext{"Yes," Lee said, "we do. But sometimes I'd like to \ns{get away} from it all."}

\switchcolumn

\nse{get away}{}{离开，脱身;逃掉;抽身;拔身;}

\switchcolumn*

\end{paracol}

\newpage